### 2016-10-19 First_np_Paper/first_np_paper.tex
Added first draft of the first 64Cu/47Sc (n,p) paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Important note on usage                  %%
%% -----------------------                  %%
%% This file must be compiled with PDFLaTeX %%
%% Using standard LaTeX will not work!      %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
\documentclass[5p]{elsarticle}
% \documentclass[3p,times]{elsarticle}
% \documentclass[3p]{elsarticle}

\usepackage[american]{babel}
\usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% \usepackage{fixltx2e}
% \usepackage{refcount}
% \usepackage{siunitx}
% \usepackage{lastpage}
% \usepackage{textcomp}
\usepackage{mathtools}

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
\usepackage{listings}
\usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{gensymb}

% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{color}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage[section]{placeins}

\lstset{basicstyle=\small\ttfamily,columns=fullflexible}

% \usepackage{verbatim}

% \usepackage{gensymb}
% \usepackage{enumerate}
% \usepackage{float}
% \usepackage{bm}
% \usepackage{csquotes}
% \usepackage{mathtools}
% \usepackage{natbib}
% \usepackage{biblatex}

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}

%% The ecrc package defines commands needed for running heads and logos.
%% For running heads, you can set the journal name, the volume, the starting page and the authors

%% set the volume if you know. Otherwise `00'
\volume{00}

%% set the starting page if not 1
\firstpage{1}

%% Give the name of the journal
\journalname{Nuclear Instruments and Methods in Physics Research A}

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{A.S. Voyles et al.}

%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo

%% Give the abbreviation of the Journal.
\jid{nima}
% \jid{yspmi}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{Nucl Instrum Meth A}

%% Hereafter the template follows `elsarticle'.
%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.

%% Elsevier CRC generally uses a numbered reference style
%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
%% If using BibTeX, use the style file elsarticle-num.bst

%% End of ecrc-specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

% if you have landscape tables
\usepackage[figuresright]{rotating}

% put your own definitions here:
%   \newcommand{\cZ}{\cal{Z}}
%   \newtheorem{def}{Definition}[section]
%   ...

% add words to TeX's hyphenation exception list
%\hyphenation{author another created financial paper re-commend-ed Post-Script}

% declarations for front matter

\usepackage{fancyvrb}
\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\footnotesize,        % size of fonts used for the code
  breaklines=true,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
}

% Sin and Cos with auto-parentheses 
\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
\newcommand{\expp}[1]{\exp{\left( #1\right)}}
\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
\newcommand{\pp}[1]{\left( #1\right)}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\norm}[1]{\lVert #1 \rVert}

\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}

\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}

\makeatletter
% Make common definition of mean
\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}

\makeatother

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
\title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via d-D Neutron Generator}

% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via d-D Neutron Generator\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

% \dochead{Short}
%% Use \dochead if there is an article header, e.g. \dochead{Short communication}

% \title{NE290A - Homework \#04}
% \date{29 April, 2016}

% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
\author[ucb]{A.S. Voyles \corref{cor1}}
\ead{andrew.voyles@gmail.com}

\author[lbl]{M.S. Basunia}

\author[lbl]{J.C. Batchelder}

\author[llnl]{J.D. Bauer}

\author[ucb,lbl]{L.A. Bernstein}

\author[ucb]{E.F. Matthews}

\author[ucb]{M.A. Unzueta}

\author[ucb]{K.A. van Bibber}

% \author[lbl]{K. ̃Bazargan\fnref{fn2}}
% \ead{kaveh@river-valley.com}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\cortext[cor1]{Corresponding author}
% \cortext[cor2]{Principal corresponding author}
% \fntext[fn1]{This is the specimen author footnote.}
% \fntext[fn2]{Another author footnote, but a little more longer.}

\address[ucb]{Department of Nuclear Engineering, The University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
\address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
\address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}

% \author{Andrew Voyles}

% \address{Nuclear Engineering, University of California Berkeley, Berkeley, CA 94709, USA.}

\begin{abstract}

\comment{Feel free to suggest a better title.}

\comment{Need to think of any other people to be added as authors. Also, is this the proper ordering - first author, then alphabetical?}

\comment{High-level comment: is active or passive voice preferred in this field?}

Neutron activation cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production reactions have been measured at the UC Berkeley High Flux Neutron Generator, for quasi-monoenergetic 2.7645 MeV incident neutrons. Measurements were performed using activation ratio methods, measured relative to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions. The use of thin foils and high-precision gamma spectroscopy using HPGe detectors allows for precision cross section measurements, to within 6\% uncertainty. These cross section measurements show strong agreement with literature and theoretical values, but with lower uncertainty than existing measurements. This work has also provided characterization of the neutron energy distributions available at the  UC Berkeley High Flux Neutron Generator, which can be used for other low-energy neutron reaction cross section measurements in the future.

\comment{Abstract needs fleshing out.}

\end{abstract}

% \begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

% \end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

\listoftodos

%% main text 
\section{Introduction} \label{sec:intro}

A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes. One potential method for producing many of these isotopes is the use of the (n,p) reaction via d-D neutron generators. However, many of these cross sections currently have significant uncertainties. Direct neutron activation, using a d-D neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production. Neutron activation can provide several advantages over charged-particle reactions from a targetry perspective. Notably, the higher penetration of neutrons allows for the use of thick target designs, which can improve production throughput and greatly simplifies target cooling considerations. More importantly, low-energy neutron reactions can be used to prevent competing reaction channels in a charged-particle reaction which would otherwise contaminate the product specific activity.

The present work focuses on the (n,p) production cross section measurements of \ce{^{64}Cu} and \ce{^{47}Sc}. \ce{^{64}Cu} ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (with a 61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (with a 38.5\% branching ratio) to \ce{^{64}Zn}. The emitted 190-keV $\beta^-$ particle makes this an extremely attractive short-ranged therapeutic radionuclide, which also has the possibility for simultaneous PET imaging due to the positron emission branch. This combination of simultaneous imaging (for real-time dose monitoring and verification) and therapeutic properties makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols. In addition, copper radiochemistry is well-developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.

\ce{^{47}Sc} ($t_{1/2}$ = 3.35 d) undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process. This radionuclide is particularly attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}. However, due to the short half-life  and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.

Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} and \ce{^{47}Ti} from solid targetry designs, without the need for additional carrier. By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.

\section{Experiment}\label{sec:experiment}

\subsection{Neutron source}\label{sec:n_source}

\comment{Regex to replace all hard figure references with LaTeX cross-references}

Neutron activation was carried out via irradiation in the UC Berkeley High-Flux Neutron Generator (HFNG), a d-D neutron generator, seen in \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through using a electric potential-shaping nozzle, forming a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for d-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle. Within the center of the target (at 5 mm from the D-D reaction surface), samples may be inserted prior to the HFNG startup, where they are irradiated in a flux of approximately 10$^8$ neutrons/cm$^2$.  A reference model of this target setup may be seen in \autoref{fig:hfng_b}. During irradiation, the machine operates under nominal conditions of a 100-kV deuterium beam extracted at 1-2 mA.

\comment{Note: all images here were included at nearly full-size. They obviously need to be reduced in size, but I included them here larger the needed, so they wouldn't be pixelated if enlarged. Shrink away :)}

\begin{figure}
 \centering
%  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
 \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
 % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
 \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
 \label{fig:alt_HFNG}
\end{figure}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=3in]{./figures/Capture.PNG}
        \caption{The UC Berkeley High-Flux Neutron Generator,}
        \label{fig:hfng_a}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2in]{./figures/target2.png}
        \caption{Cutaway of the target chamber.}
                \label{fig:hfng_b}
    \end{subfigure}
    \caption{Note: the ion source is approximately 20 cm in diameter, for scale.}
     \label{fig:main_HFNG}
\end{figure*}

\subsection{Sample loading}\label{sec:sample_loading}

Direct activation of a thin foil can be used for high-fidelity measurement of neutron-induced reactions, through subsequent decay spectroscopy. This method can provide cross sections with far lower uncertainty than neutron time-of-flight measurements, but is heavily reliant upon precisely quantifying the neutron fluence incident upon a loaded target. To avoid the introduction of this large uncertainty, 0.5-mm thin Indium foils were co-loaded along with each target foil for irradiation, with all production cross sections thus measured relative to the well-characterized \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} dosimetry standard reactions. In addition, over the energy region spanned by the d-D emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements. The use of this well-established ratio method removes the fluence dependence from all cross-section calculations, removing the largest source of systematic uncertainty in activation.

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.3\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=2in]{./figures/foils.png}
        \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
        \label{fig:holder_a}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.3\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2in]{./figures/holder.pdf}
        \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
                \label{fig:holder_b}
    \end{subfigure}
     ~ 
    \begin{subfigure}[t]{0.3\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
        \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
                \label{fig:holder_c}
    \end{subfigure}
    \caption{}
     \label{fig:main_holders}
\end{figure*}

For the measurement of the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section, a natural abundance commercial (Goodfellow) zinc foil was cut down to 1-cm in diameter and used as a target; similarly a natural abundance commercial (Goodfellow) titanium foil was used as target for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} reaction. Target foils of 1-cm diameter and 1-mm thickness were co-loaded with a natural-abundance Indium foil of 1-cm diameter and 0.5-mm thickness in a recess cut into a 2-mm thin polyethylene holder, as seen in \autoref{fig:main_holders}. Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue which could become activated during irradiation. The recorded physical characteristics of each foil for the various irradiations are recorded in \autoref{tab:foil_specs}. In each experiment, the co-loaded foils were subjected to 3 hour irradiation at nominal operating conditions of 1.3 mA and 100 kV, to saturate the induced Indium isomer activity.

\comment{Regex to replace table hard link with LaTeX cross-reference.}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{graphicx}
\begin{table*}
\centering
\caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments. 
}
\label{tab:foil_specs}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}ccccccc@{}}
\toprule
Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (cm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
$^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ XXX $\pm$ XXX$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ XXX $\pm$ XXX$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  XXXXXX$^\dagger$\end{tabular} \\
$^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\end{tabular}                           \\
$^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ XXXXXX\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ XXXXXX\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ XXXXXXX\end{tabular}                                   \\ \bottomrule
\end{tabular}%
}
\end{table*}

\comment{Need foil data from Mauricio's 2nd Ti run}

\subsection{Determination of effective neutron energy}\label{sec:neutron_energies}

The kinematics of d-D fusion produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab frame emission angular range of 0-180\degree, with respect to the incident deuteron beam. This distribution is a function of the incident deuteron kinetic energy, and has been well-documented; the energy-angle distribution for the incident 100 keV deuterons used in the HFNG can be seen plotted in \autoref{fig:scatt_angle}.

\comment{Parenthetical citations, or just a list at the end? The Shimizu paper uses the latter as citation format.}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
 % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
 \caption{Energy-angle distribution for neutrons emitted following d-D fusion, for 100 keV incident deuterons.}
 \label{fig:scatt_angle}
\end{figure}

Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target. Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with at least several feet of standoff from the d-D reaction surface. This would greatly reduce the flux (to approximately 10$^4$ neutrons/cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production \& decay in activation measurements. Instead, samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the d-D reaction surface. This allows the samples to subtend a fairly narrow (28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately 10$^8$ neutrons/cm$^2$ ) flux for activations.

\begin{figure}
 \centering
 %trim option's parameter order: left bottom right top
 \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
 % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
 \caption{MCNP6 model of the Berkeley HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.}
 \label{fig:mcnp_vised}
\end{figure}

To determine the energy distribution of neutrons incident upon the loaded foils, MCNP6 was used to model the generator operation, and produced a neutron energy spectrum incident upon target foils co-loaded into the HFNG, seen in \autoref{fig:mcnp_flux}. This spectrum verifies the forward-focused kinematics of the d-D reaction subtended by the co-loaded sample foils.

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
 % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
 \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
 \label{fig:mcnp_flux}
\end{figure}

While this shows that the sample foils receive a very narrow energy distribution of incident neutrons, an effective neutron energy and energy bounds must be determined to constrain cross section ratio measurements. From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and average neutron energy of 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils. Due to the kinematics of d-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry, can be calculated as 2.7825 MeV. For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:

\begin{equation}
R = N_i \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
\end{equation}

\comment{Regex to replace equations with LaTeX formats, add cross-references.}

From this definition, it is possible to calculate $F\pp{E'}$, the fraction of total reactions induced up to some energy $E' < E_{max}$:

\begin{equation}\label{eqn:react_fraction}
F\pp{E'} = \dfrac{\int_0^{E'} \sigma(E) \dfrac{d\phi}{dE} dE}{\int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE}
\end{equation}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/fracplot.pdf}
 % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
 \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
 \label{fig:frac_plot}
\end{figure}

This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}. Using the flux-averaged neutron energy in the Indium foil as a centroid, this fraction of total reactions can be used to to estimate the uncertainty in effective neutron energy, which will become energy error bars in the excitation function for these reactions. Within 1 standard deviation above and below the centroid, 68.2\% of all reactions should be encompassed. Thus, the upper and lower energy uncertainties correspond to the neutron energies $E'$  such that $F\pp{E'}$ = 0.841 and $F\pp{E'}$ = 0.159, respectively. From \autoref{eqn:react_fraction},  these are found to be  F(2.7796 MeV) = 0.841 and F(2.7426 MeV) = 0.159, respectively; thus the effective neutron energy subtended by target foils is reported as $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.  This 37-keV full-energy spread verifies that, at such close distances to the d-D reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.

\subsection{Measurement of induced activities}\label{sec:spectroscopy}

After irradiation, the co-loaded targets in each experiment were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy. Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar LEPS detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments. These can be seen in \autoref{fig:hpge_a} and \autoref{fig:hpge_b}. Both detectors were calibrated for both energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector. These efficiencies, along with gamma ray intensities for each transition, are used to convert the counts in each detected gamma ray photopeak into an activity for the activated isotopes and isomeric states.

\begin{figure*}[H]
    \centering
    \begin{subfigure}[t]{0.7\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
        \caption{ Ortec 80\% HPGe detector}
        \label{fig:hpge_a}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.28\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
        \caption{Ortec planar LEPS detector}
                \label{fig:hpge_b}
    \end{subfigure}
    \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
     \label{fig:main_ge_detectors}
\end{figure*}

For all data collection, performed using the Ortec MAESTRO software, the foils were counted in their polyethylene holder, and placed against the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector. This position allows for the detectors to subtend the largest possible solid angle of the gamma rays emitted by the foils. Before data was collected, detector dead time was verified to be less than 5\%, to avoid coincidence summing effects. This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector, to reduce the dead time.  For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector, and for the case of \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities. After approximately 4 hours of spectra collection, the activated zinc foil was added back and counting resumed simultaneously with the indium foil. This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons. \ce{^{116}In} has a 54 minute half life, decaying via $\beta^-$ with a Q value of 3.278 MeV. This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times 511$  keV, which pair produce in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production. By waiting for 4 hours of counting the indium foil separately, nearly all \ce{^{116}In} will have decayed, making it safe to add the activated zinc foil without worries of significant 511 keV contamination. Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.

\begin{figure*}[H]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[width=5in]{./figures/ti_foils.png}
        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a planar LEPS detector}
        \label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[width=5in]{./figures/Sample_spectra.png}
        \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
                \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production.}
     \label{fig:main_spectra}
\end{figure*}

To verify that each peak truly corresponds to assigned transitions, spectra collection for each foil was counted in a series of 15 - 30 minute sequential data acquisitions. By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponentially decaying curve may be fit to it, to determine the half life of the transition in question. Plots of these curves for each transition in this work are seen in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511}. The fitted half lives in each of these curves has strong statistical agreement with accepted half lives from the ENDF-VII/B library, indicating that these peaks are the correctly assigned transitions.

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/336keV_curve2.png}
        \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
        \label{fig:decay_curve_336}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
        \label{fig:decay_curve_391}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[scale=0.6]{./figures/417keV_curve2.png}
        \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
                \label{fig:decay_curve_417}
    \end{subfigure}
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/511keV_curve2.png}
        \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
        \label{fig:decay_curve_511}
    \end{subfigure}%
    \caption{Decay curves used to verify photopeak transition assignment.}
     \label{fig:decay_curves}
\end{figure*}

Background-subtracted counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table*}
\centering
\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments. \color{red}{Need Mauricio data!}}
\label{tab:peak_counts}
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|ccccc}
Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\ \hline
Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\ \hline
Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\ \hline
Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\ \hline
End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\ \hline
Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\ \hline
Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &    \hrulefill       &  \hrulefill      \\ \hline
Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &    \hrulefill       &   \hrulefill     \\ \hline
Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & XXXX  
\end{tabular}%
}
\end{table*}

% % Please add the following required packages to your document preamble:
% % \usepackage{booktabs}
% % \usepackage{graphicx}
% \begin{table*}
% \centering
% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.}
% \label{tab:peak_counts}
% \resizebox{\textwidth}{!}{%
% \begin{tabular}{@{}|c|ccccc@{}}
% Reference Foil                     & natIn         & natIn       & natIn & natIn     & natIn  \\
% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\
% Target Foil                        & natZn         & natZn       & natZn & natTi     & natTi  \\
% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\
% Irradiation Time, t1 (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\
% Start of Count, t2 (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\
% End of Count, t3 (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\
% Photopeak Counts, 336 keV (115mIn) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\
% Photopeak Counts, 391 keV (113mIn) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &           &        \\
% Photopeak Counts, 511 keV (64Cu)   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &           &        \\
% Photopeak Counts, 159 keV (47Sc)   &               &             &       & 3877 $\pm$ 83 & XXXX  
% \end{tabular}%
% }
% \end{table*}

\subsection{Calculation of measured cross sections}\label{sec:calcs_sec}

Gamma spectroscopy analysis on the several days of collected spectra was used to measure the background-subtracted counts under each of the photopeaks of interest for the induced activities, as described in \autoref{sec:spectroscopy}. For a thin target consisting of \(N_T\) target nuclei, subjected to a constant monoenergetic neutron flux $\phi\pp{\bar{E}}$, the rate of production of the product nucleus will be:

\begin{equation}
R = N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} 
\end{equation}

for a reaction with cross-section  $\sigma\pp{\bar{E}}$ at effective energy $\bar{E}$. If this irradiation lasts for  some time $t_1$, and gamma ray spectroscopy of the activated samples begins at a later time $t_2$ and ends at an even later time $t_3$, then the number of product decays (with decay constant $\lambda$) which take place between $t_2$ and $t_3$ will be:

\begin{equation}
\begin{aligned}
D &= \dfrac{R}{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}}
\\
&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
\end{aligned}
\end{equation}

If this decay emits a gamma ray with branching ratio $I_\gamma$ photons emitted per decay, and is detected with an absolute efficiency (photons detected / photons emitted) of $\epsilon_\gamma$, then the number of observed decays between $t_2$ and $t_3$ will be:

% \begin{equation}
% \begin{aligned}
% N_{obs} &= D \epsilon_\gamma I_\gamma \\
% &= \? \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
% \end{aligned}
% \end{equation}

\begin{align}
N_{obs} &= D \epsilon_\gamma I_\gamma \\
&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} \nonumber
\end{align}

Rearranging in terms of the observed cross-section:

\begin{equation}
\sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}}}
\end{equation}

This model, in which subscripts $P$ indicate a quantity for either the \ce{^{64}Cu} or \ce{^{47}Sc} product, subscripts $In$ indicate a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer, can be taken in ratio, to calculate the measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production cross sections, relative to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering cross sections. Adding in a correction for the small self-attenuation of the gamma rays emitted by the activated foils, the final ratio model can be seen in \autoref{eqn:calc_eqn}:

\begin{align}\label{eqn:calc_eqn}
\sigma_P &= \sigma_{In} \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1}  \\
&\times \dfrac{e^{-\lambda_{In}t_2}-e^{-\lambda_{In}t_3}}{e^{-\lambda_{P}t_2} - e^{-\lambda_{P}t_3}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
\end{align}

where:

\begin{itemize}

\item $A$ is the integrated counts under a photopeak [counts],

\item $\sigma$ is the cross section for either the production of a product or isomer [mb],

\item $N_T$ is the initial number of target nuclei,

\item $\lambda$  is the decay constant [s$^{-1}$],

\item $t_1$ is the irradiation time [s],

\item $t_2$ is the time between the start-of-beam and the start of counting [s],

\item $t_3$ is the time  between the start-of-beam and the end of counting [s],

\item $\epsilon$ is the  detector efficiency for a particular photopeak,

\item $I_\gamma$ is the decay gamma ray branching ratio,

\item $\mu$ is the photon attenuation coefficient for a particular decay gamma ray in a foil [cm$^{-1}$],

\item and $x$ is the thickness of foil traversed by a particular decay gamma ray [cm] 
\end{itemize}

With the exception of decay constants, which are assumed to be exact, each of the parameters in this model carries statistical uncertainty in measurement. In lieu of a differential error propagation, the total statistical error $\delta_\sigma$ is taken as the quadrature sum of all of the other errors  $\delta_i$:

\begin{equation}
\delta_\sigma = \norm{ \ensuremath{\vec{\delta}} }_2 = \sqrt{\sum_{i=1}^N  \delta_i^2  }
\end{equation}

This total statistical uncertainty will be plotted as the cross-section error bar in the excitation function for these production reactions.

\subsection{Systematic errors}

XXXXXXXXXXXXXXXX

\comment{Not sure what else we need to consider for systematics...}

\section{Results}

Using the ratio methods described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of 2.7645 MeV,  + 0.0151 MeV / - 0.0219 MeV. These values are recorded in \autoref{tab:xs_results}.

\comment{Need Mauricio's Cu point w/ more sigfigs. Need Mauricio's Sc point too}

\comment{How many sig figs to round uncertainties to in table?}

\comment{Report all 3 values in table? Report a weighted average between them?}

% 
% % Please add the following required packages to your document preamble:
% % \usepackage{booktabs}
% \begin{table}[]
% \centering
% \caption{My caption}
% \label{my-label}
% \begin{tabular}{@{}cc@{}}
% \toprule
% h                                 & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                     \\ \midrule
% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{113}In}) & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
% \ce{^{47}Ti}(n,p)\ce{^{47}Sc} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
% \end{tabular}
% \end{table}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Results of cross section measurement. }
\label{tab:xs_results}
\begin{tabular}{@{}cc@{}}
\toprule
Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
\end{tabular}
\end{table}

The results for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections can also be seen plotted in Figures \ref{fig:sc_xs} and \ref{fig:cu_xs}, respectively. It is apparent that the relative cross sections measured in the present work are consistent with both the small quantity of other literature results, and are measured to within 6\% uncertainty, lower than existing measurements. In addition, the results presented in this work show strong agreement with the recommended values from both the ENDF/B-VII.1 nuclear data library and reaction modeling results from TALYS\cite{koning2005talys}.

\comment{Add in EMPIRE data points?}

\comment{Mention Shimizu data specifically? }

\comment{Add a zoomed-in view like in \autoref{fig:cu_xs}?}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/47Sc_fixed.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} relative production cross section.}
 \label{fig:sc_xs}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
 \label{fig:cu_xs}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/64cu_fixed_zoom.pdf}
 % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
 \caption{A zoomed-in view of \autoref{fig:cu_xs}.}
 \label{fig:cu_xs_zoom}
\end{figure}

\section{Summary}

Using direct activation methods for thin foils as described in this work, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections have been measured for  2.7645 MeV neutrons, to within 6\% uncertainty. These measurements are consistent with experimental data and theoretical models,  and have been measured to lower uncertainty than existing measurements. The use of d-D neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies. While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the d-D neutron emission energy spectrum.

\comment{Future work? Thermal neutron measurements? Something like the following?}

 Future work will involve the continued measurement of the (n,p) production cross sections for various other emerging therapeutic and diagnostic radioisotopes, to expand the toolset of options available for modern medical imaging and cancer therapy. This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments

 \comment{Should we specifically mention other isotopes we plan to measure?}

 \section{Acknowledgements}

 This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231. Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.

 \comment{Who else should we acknowledge?}

% \pagebreak
% 
% \onecolumn
% 
% \appendix

% \section{Data} \label{data}
% 
% % \begin{longtable}{|c|c|c|c|c|} 
% % \caption{My caption}
% % \label{tab:dummy}
% % % \begin{tabular}{|c|c|c|c|c|}
% %    \hline
% %  
% % \end{longtable}
% hello world

% 
% \section{Results} \label{equations}
% 
% Tabulated results are listed here, to avoid breaking text flow in the main text.
% 
% \begin{table}[h]
% \centering
% \caption{Transition conversion coefficients and efficiencies}
% \label{my-label2}
% \begin{tabular}{c|c|c|c|c}
% Nucleus & Transition       & E\(_\gamma\) (keV) & \(\alpha\), Conversion Coefficient  & \(\epsilon\), Intrinsic Efficiency \\ \hline
% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 0.0569           \(\pm\) 0.0008              & 1863.906   \\
%         & 4\(\rightarrow\)2 & 422.6          & 0.00887          \(\pm\) 0.00013             & 1219.507   \\
%         & 6\(\rightarrow\)4 & 575.7          & 0.00356          \(\pm\) 0.00005             & 956.569    \\ \hline
% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 0.0205          \(\pm\) 0.0003              & 1340.054   \\
%         & 4\(\rightarrow\)2 & 457.63         & 0.01154          \(\pm\) 0.00017             & 1142.505   \\
%         & 6\(\rightarrow\)4 & 582.4          & 0.00593          \(\pm\) 0.00009             & 948.705    \\ \hline
% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 0.00599         \(\pm\) 0.00009             & 926.624    \\
%         & 4\(\rightarrow\)2 & 528.25         & 0.00848         \(\pm\) 0.00012             & 1019.604   \\
%         & 6\(\rightarrow\)4 & 529.7          & 0.00842         \(\pm\) 0.00012             & 1017.470   \\ \hline
% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 0.175           \(\pm\) 0.0025              & 2085.452   \\
%         & 4\(\rightarrow\)2 & 330.88         & 0.0333         \(\pm\) 0.0005              & 1485.782   \\
%         & 6\(\rightarrow\)4 & 431.3          & 0.015          \(\pm\) 0.00021             & 1199.258  
% \end{tabular}
% \end{table}
% 
% \begin{table}[h]
% \centering
% \caption{Extracted transition intensities}
% \label{my-label}
% \begin{tabular}{c|c|c|c|c|c}
% Nucleus & Transition       & E\(_\gamma\) (keV) & \(A_{obs}\), Peak Area (a.u.)   & \(A_{source}\),  Peak Intensity (a.u.)  & \(R_i\), Relative Intensity  \\ \hline
% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 1097    \(\pm\)   136        & 0.622          \(\pm\) 0.077             & 1.000              \(\pm\) 0.175                 \\
%         & 4\(\rightarrow\)2 & 422.6          & 515     \(\pm\)   107        & 0.426          \(\pm\) 0.089             & 0.685              \(\pm\) 0.200                 \\
%         & 6\(\rightarrow\)4 & 575.7          & 144      \(\pm\)  55         & 0.151          \(\pm\) 0.058             & 0.243              \(\pm\) 0.198                 \\ \hline
% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 542     \(\pm\)   129        & 0.413          \(\pm\) 0.098             & 1.000              \(\pm\) 0.337                 \\
%         & 4\(\rightarrow\)2 & 457.63         & 357       \(\pm\) 59         & 0.316          \(\pm\) 0.052             & 0.766              \(\pm\) 0.254                 \\
%         & 6\(\rightarrow\)4 & 582.4          & 161       \(\pm\) 61         & 0.171          \(\pm\) 0.065             & 0.414              \(\pm\) 0.288                 \\ \hline
% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 822       \(\pm\) 164        & 0.892          \(\pm\) 0.178             & 1.000              \(\pm\) 0.282                 \\
%         & 4\(\rightarrow\)2 & 528.25         & 384       \(\pm\) 78         & 0.380          \(\pm\) 0.077             & 0.426              \(\pm\) 0.186                 \\
%         & 6\(\rightarrow\)4 & 529.7          & 310       \(\pm\) 104        & 0.307          \(\pm\) 0.103             & 0.344              \(\pm\) 0.229                 \\ \hline
% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 900       \(\pm\) 242        & 0.507          \(\pm\) 0.136             & 1.000              \(\pm\) 0.380                 \\
%         & 4\(\rightarrow\)2 & 330.88         & 535       \(\pm\) 127        & 0.372          \(\pm\) 0.088             & 0.734              \(\pm\) 0.307                 \\
%         & 6\(\rightarrow\)4 & 431.3          & 363       \(\pm\) 64         & 0.307          \(\pm\) 0.054             & 0.606              \(\pm\) 0.250                
% \end{tabular}
% \end{table}
%     
% \pagebreak
% 
% 
% 
% \section{Supplemental Figures} \label{fit_figures}
% 
% The remaining figures of the fitted \(\gamma\)-ray transition photopeaks are included here for reference, to avoid over-cluttering the main text.
% 
% 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit110Ru240-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{110}Ru} 240.7 keV peak and its surroundings.}
% %  \label{fig:110Ru240}
% % \end{figure}
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit110Ru422-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{110}Ru} 422.6 keV peak and its surroundings.}
% %  \label{fig:110Ru422}
% % \end{figure}
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit110Ru575-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{110}Ru} 575.7 keV peak and its surroundings.}
% %  \label{fig:110Ru575}
% % \end{figure}
% 
% 
% 
% 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit140Xe376-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{140}Xe} 376.7 keV peak and its surroundings.}
% %  \label{fig:140Xe376}
% % \end{figure}
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit140Xe457-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{140}Xe} 457.6 keV peak and its surroundings.}
% %  \label{fig:140Xe457}
% % \end{figure}
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit140Xe582-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{140}Xe} 582.3 keV peak and its surroundings.}
% %  \label{fig:140Xe582}
% % \end{figure}
% % 
% % 
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit140Ba602-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{140}Ba} 602.4 keV peak and its surroundings.}
% %  \label{fig:140Ba602}
% % \end{figure}
% % 
% % 
% % 
% % 
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit144Ba199-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{144}Ba} 199.3 keV peak and its surroundings.}
% %  \label{fig:144Ba199}
% % \end{figure}
% % 
% % 
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit144Ba330-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{144}Ba} 330.9 keV peak and its surroundings.}
% %  \label{fig:144Ba330}
% % \end{figure}
% % 
% % \begin{figure}[h]
% %  \centering
% %  \includegraphics[scale=0.7]{./hw04/fit144Ba431-cropped.pdf}
% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
% %  \caption{Fit to the \ce{^{144}Ba} 431.3 keV peak and its surroundings.}
% %  \label{fig:144Ba431}
% % \end{figure}
% 
% 
% 
%     
% \pagebreak
% 
% 
% % \appendix
% \section{Source Code} \label{source}
% 
% \begin{center}
%  \texttt{gint.py} - Implementation of the Wilhelmy statistical model, used to estimate total transition intensities in the ground state band  of primary fission fragments
% \end{center}
% 
% % \begin{lstlisting}
% % \lstloadlanguages{Python}
% 
% % \lstinputlisting[linewidth=\columnwidth,language=Python,breaklines=true,frame=single]{./hw04/gint.py}
% % % \end{lstlisting}
% 
% 
% 
% \begin{center}
%  \texttt{hw04\_04.m} - used to process and plot statistical transition intensity curves
% \end{center}
% 
%  
% %   \lstinputlisting[frame=single]{./hw04/hw04_04.m}
% 
% 
% % \begin{verbatim}[commandchars=\\\{\}]
% % \verbatiminput{./HW01/test.txt}
% % \end{verbatim}
% 
% %% The Appendices part is started with the command \appendix;
% %% appendix sections are then done as normal sections
% %% \appendix
% 
% %% \section{}
% %% \label{}
% 
% %% References
% %%
% %% Following citation commands can be used in the body text:
% %% Usage of \cite is as follows:
% %%   \cite{key}         ==>>  [#]
% %%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

% \twocolumn

%% References with BibTeX database:

% \bibliographystyle{elsarticle-num}
% \bibliographystyle{elsarticle-harv}
% \bibliographystyle{elsarticle-num-names}
% \bibliography{<your-bib-database>}
% \addcontentsline{toc}{chapter}{Bibliography}
% \bibliographystyle{elsarticle-num}
\bibliographystyle{ieeetr}
\bibliography{../../library}
% \thispagestyle{fancyTOC}

H. F. Aly et al., Microchim. Acta, vol. 59, no. 1, 1971.

K. S. Bhatki et al., J. Radioanal. Chem., vol. 2, no. 1-2, 1969.

T. H. Bokhari et al., J. Radioanal. Nucl. Chem., vol. 283, no. 2, 2010.

J. F. Briesmeister et al., Los Alamos National Laboratory, 1986.

M. B. Chadwick,et al., Nucl. Data Sheets, vol. 107, no. 12, 2006.

A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.

H. Liskien et al., Nucl. Data Tables, vol 11, 1973.

M. R. Lewis et al., J. Nucl. Med., vol. 44, no. 8, Aug. 2003.

C. Müller et al., J. Nucl. Med., vol. 55, no. 10, Oct. 2014.

N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.

L. Pietrelli et al., J. Radioanal. Nucl. Chem., vol. 157, no. 2, 1992.

S. M. Qaim et al., IAEA Technical Reports Series No. 473, 2011.

T. Shimizu, et al, Ann. Nucl. Energy, vol. 31, no. 9, pp. 975-990, 2004.

T. Shimizu, et al, Nucl. Instruments Methods Phys. Res. Sect. A Accel. Spectrometers, Detect. Assoc. Equip., vol. 527, no. 3, pp. 543-553, 2004.

D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.

\comment{Cite Cory's thesis, or upcoming NIM paper?}

\comment{Convert these to BibTeX format!}

%% Authors are advised to use a BibTeX database file for their reference list.
%% The provided style file elsarticle-num.bst formats references in the required Procedia style

%% For references without a BibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file `ecrc-template.tex'.

### 2016-12-22 First_np_Paper/first_np_paper.tex
Updated abstract section with first-round edits

@@
 %%
-\title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via d-D Neutron Generator}
-
-% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via d-D Neutron Generator\tnoteref{label1}}
+\title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\\ OR \\(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} at 2.76 MeV using a D-D Neutron Generator for Medical Isotope Studies}
+
+% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\tnoteref{label1}}
 %% \tnotetext[label1]{}
@@
 
+\author[geo,eps]{D.XXX. Rutte}
+
 \author[ucb]{M.A. Unzueta}
@@
 
-\address[ucb]{Department of Nuclear Engineering, The University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
-\address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
-\address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}
+% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
+% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
+% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}
+
+\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Berkeley CA, 94720 USA}
+\address[lbl]{Lawrence Berkeley National Laboratory,  Berkeley CA, 94720 USA}
+\address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
+\address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
+\address[eps]{Department of Earth and Planetary Sciences, University of California, Berkeley, Berkeley CA,  94720  USA}
 
@@
 
-\comment{Feel free to suggest a better title.}
-
-\comment{Need to think of any other people to be added as authors. Also, is this the proper ordering - first author, then alphabetical?}
-
-\comment{High-level comment: is active or passive voice preferred in this field?}
-
-Neutron activation cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production reactions have been measured at the UC Berkeley High Flux Neutron Generator, for quasi-monoenergetic 2.7645 MeV incident neutrons.
-Measurements were performed using activation ratio methods, measured relative to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions.
-The use of thin foils and high-precision gamma spectroscopy using HPGe detectors allows for precision cross section measurements, to within 6\% uncertainty.
-These cross section measurements show strong agreement with literature and theoretical values, but with lower uncertainty than existing measurements.
-This work has also provided characterization of the neutron energy distributions available at the  UC Berkeley High Flux Neutron Generator, which can be used for other low-energy neutron reaction cross section measurements in the future.
+\comment{Use D-D or DD as convention?}
+
+\comment{Choose a preferred title...}
+
+\comment{Need Daniel's middle initial}
+
+\comment{Should street address be included for each institution, or just city / state / zip?}
+
+Neutron activation cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production reactions have been measured for quasi-monoenergetic 2.7645 MeV incident neutrons produced by the UC Berkeley High Flux Neutron Generator, a D-D plasma-based neutron source.
+\comment{ Need to decide on number of sig figs to report, and truncate appropriately - i.e.2.76 +0.15 - 0.22 - \#s taken from text section 3]
+} Measurements were performed using activation ratio methods, measured relative to co-irradiated indium foils using the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions.
+The use of thin foils and gamma spectroscopy using an HPGe and LEPS detectors allowed for cross section determination to within 6\% uncertainty.
+These cross section measurements show good agreement with the literature and theoretical values, but with lower uncertainty than existing measurements.
+This work has resulted in a detailed characterization of the D-D plasma-based neutron source, which can be used for other low-energy neutron reaction cross section measurements in the future.
 
 \comment{Abstract needs fleshing out.}
+
+\comment{For my corresponding author email, should I list my Gmail (more permanent) or my Berkeley / LBL address (more professional)?}
 
@@
 A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes.
-One potential method for producing many of these isotopes is the use of the (n,p) reaction via d-D neutron generators.
+One potential method for producing many of these isotopes is the use of the (n,p) reaction via D-D neutron generators.
 However, many of these cross sections currently have significant uncertainties.
-Direct neutron activation, using a d-D neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production.
+Direct neutron activation, using a D-D neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production.
 Neutron activation can provide several advantages over charged-particle reactions from a targetry perspective.
@@
 
-Neutron activation was carried out via irradiation in the UC Berkeley High-Flux Neutron Generator (HFNG), a d-D neutron generator, seen in \autoref{fig:hfng_a}.
+Neutron activation was carried out via irradiation in the UC Berkeley High-Flux Neutron Generator (HFNG), a D-D neutron generator, seen in \autoref{fig:hfng_a}.
 This generator extracts deuterium ions from an RF-heated deuterium plasma through using a electric potential-shaping nozzle, forming a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for d-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle.
+This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle.
 Within the center of the target (at 5 mm from the D-D reaction surface), samples may be inserted prior to the HFNG startup, where they are irradiated in a flux of approximately 10$^8$ neutrons/cm$^2$.
@@
 To avoid the introduction of this large uncertainty, 0.5-mm thin Indium foils were co-loaded along with each target foil for irradiation, with all production cross sections thus measured relative to the well-characterized \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} dosimetry standard reactions.
-In addition, over the energy region spanned by the d-D emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements.
+In addition, over the energy region spanned by the D-D emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements.
 The use of this well-established ratio method removes the fluence dependence from all cross-section calculations, removing the largest source of systematic uncertainty in activation.
@@
 
-The kinematics of d-D fusion produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
+The kinematics of D-D fusion produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
 This distribution is a function of the incident deuteron kinetic energy, and has been well-documented; the energy-angle distribution for the incident 100 keV deuterons used in the HFNG can be seen plotted in \autoref{fig:scatt_angle}.
@@
  % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
- \caption{Energy-angle distribution for neutrons emitted following d-D fusion, for 100 keV incident deuterons.}
+ \caption{Energy-angle distribution for neutrons emitted following D-D fusion, for 100 keV incident deuterons.}
  \label{fig:scatt_angle}
@@
 Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target.
-Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with at least several feet of standoff from the d-D reaction surface.
+Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with at least several feet of standoff from the D-D reaction surface.
 This would greatly reduce the flux (to approximately 10$^4$ neutrons/cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production \& decay in activation measurements.
-Instead, samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the d-D reaction surface.
+Instead, samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the D-D reaction surface.
 This allows the samples to subtend a fairly narrow (28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately 10$^8$ neutrons/cm$^2$ ) flux for activations.
@@
 To determine the energy distribution of neutrons incident upon the loaded foils, MCNP6 was used to model the generator operation, and produced a neutron energy spectrum incident upon target foils co-loaded into the HFNG, seen in \autoref{fig:mcnp_flux}.
-This spectrum verifies the forward-focused kinematics of the d-D reaction subtended by the co-loaded sample foils.
+This spectrum verifies the forward-focused kinematics of the D-D reaction subtended by the co-loaded sample foils.
 
@@
 From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and average neutron energy of 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils.
-Due to the kinematics of d-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry, can be calculated as 2.7825 MeV.
+Due to the kinematics of D-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry, can be calculated as 2.7825 MeV.
 For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:
@@
 From \autoref{eqn:react_fraction},  these are found to be  F(2.7796 MeV) = 0.841 and F(2.7426 MeV) = 0.159, respectively; thus the effective neutron energy subtended by target foils is reported as $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
-This 37-keV full-energy spread verifies that, at such close distances to the d-D reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.
+This 37-keV full-energy spread verifies that, at such close distances to the D-D reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.
 
@@
 These measurements are consistent with experimental data and theoretical models,  and have been measured to lower uncertainty than existing measurements.
-The use of d-D neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
-While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the d-D neutron emission energy spectrum.
+The use of D-D neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
+While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the D-D neutron emission energy spectrum.
 

### 2016-12-22 First_np_Paper/first_np_paper.tex
Updated introduction section with first-round edits

@@
 
-A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes.
-One potential method for producing many of these isotopes is the use of the (n,p) reaction via D-D neutron generators.
-However, many of these cross sections currently have significant uncertainties.
+%
+% If we want to mention in-situ-production
+%
+%
+% e.g.:In-situ production (I always figured this is what is so great, correct me if I am wrong) of radioactive nuclides is an emerging method for radiation therapy in nuclear medicine (e.g., cite some recent review paper).
+It is based on doping the malignant target tissue with a stable nuclide which is then activated in-situ by neutron irradiation.
+Following decay is focused on the target tissue.
+Advantages compared to conventional radiation therapy are the reduction of damage to surrounding cells, … short range, … .
+Currently development of this technique is hampered by the lack of fundamental cross section data for various isotopes.
+
+\comment{Add an initial \enquote{punchline} to  clarify the motivation?}
+
+\comment{Per Mauricio, does 2.7 MeV count as high energy? While fast, I would consider this to still be definitely in the low-energy regime, compared to spallation, etc.}
+
+A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes, as many of these cross sections currently have not been measured, or possess significant uncertainties.
+One potential method for producing many of these isotopes is the use of (n,p) reactions via neutron beams from D-D neutron generators.
 Direct neutron activation, using a D-D neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production.
@@
 The present work focuses on the (n,p) production cross section measurements of \ce{^{64}Cu} and \ce{^{47}Sc}.
-\ce{^{64}Cu} ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (with a 61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (with a 38.5\% branching ratio) to \ce{^{64}Zn}.
-The emitted 190-keV $\beta^-$ particle makes this an extremely attractive short-ranged therapeutic radionuclide, which also has the possibility for simultaneous PET imaging due to the positron emission branch.
-This combination of simultaneous imaging (for real-time dose monitoring and verification) and therapeutic properties makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols.
-In addition, copper radiochemistry is well-developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-
-\ce{^{47}Sc} ($t_{1/2}$ = 3.35 d) undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process.
-This radionuclide is particularly attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}.
+Copper-64  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn}.
+The emitted 190-keV $\beta^-$ particle makes this an  attractive short-ranged therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging  due to the positron emission branch (for real-time dose monitoring and verification),  making \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols.
+In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
+
+Scandium-47 ($t_{1/2}$ = 3.35 d) undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process.
+This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}.
 However, due to the short half-life  and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.
 
-Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} and \ce{^{47}Ti} from solid targetry designs, without the need for additional carrier.
+\comment{Adding a short paragraph from Mauricio explaining benefits of DD generators vs other neutron sources?}
+
+\comment{Per Daniel, add a short summary of results here?}
+
+Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} and \ce{^{47}Ti} from solid target designs, without the need for additional carrier.
 By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.
+
+\comment{Should this last paragraph be moved to the results and discussion at the end of the paper?}
 

### 2016-12-23 First_np_Paper/first_np_paper.tex
Updated section 2.1 with first round edits

@@
 
-Neutron activation was carried out via irradiation in the UC Berkeley High-Flux Neutron Generator (HFNG), a D-D neutron generator, seen in \autoref{fig:hfng_a}.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through using a electric potential-shaping nozzle, forming a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle.
-Within the center of the target (at 5 mm from the D-D reaction surface), samples may be inserted prior to the HFNG startup, where they are irradiated in a flux of approximately 10$^8$ neutrons/cm$^2$.
-A reference model of this target setup may be seen in \autoref{fig:hfng_b}.
-During irradiation, the machine operates under nominal conditions of a 100-kV deuterium beam extracted at 1-2 mA.
+Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California Berkeley, seen in  \autoref{fig:hfng_a}.
+This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
+This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}.
+Within the center of the target (at 8 mm from the D-D reaction surface), samples may be inserted prior to  HFNG startup.
+\autoref{fig:hfng_b} displays the target setup.
+At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
+
+\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I’m not sure it is; yes certainly for NIM, but not sure about PRC.}
 
@@
     \end{subfigure}
-    \caption{Note: the ion source is approximately 20 cm in diameter, for scale.}
+    \caption{Note: the ion source is approximately 20 cm in diameter.}
      \label{fig:main_HFNG}

### 2016-12-23 First_np_Paper/first_np_paper.tex
Partially updated section 2.2 with first round edits, updated the foil holder illustration

@@
 
-Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California Berkeley, seen in  \autoref{fig:hfng_a}.
+Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
 This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
@@
 
-\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I’m not sure it is; yes certainly for NIM, but not sure about PRC.}
+\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I'm not sure it is; yes certainly for NIM, but not sure about PRC.}
 
@@
 
-For the measurement of the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section, a natural abundance commercial (Goodfellow) zinc foil was cut down to 1-cm in diameter and used as a target; similarly a natural abundance commercial (Goodfellow) titanium foil was used as target for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} reaction.
-Target foils of 1-cm diameter and 1-mm thickness were co-loaded with a natural-abundance Indium foil of 1-cm diameter and 0.5-mm thickness in a recess cut into a 2-mm thin polyethylene holder, as seen in \autoref{fig:main_holders}.
-Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue which could become activated during irradiation.
-The recorded physical characteristics of each foil for the various irradiations are recorded in \autoref{tab:foil_specs}.
-In each experiment, the co-loaded foils were subjected to 3 hour irradiation at nominal operating conditions of 1.3 mA and 100 kV, to saturate the induced Indium isomer activity.
+For the measurement of the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section, a natural abundance commercial zinc foil of 1 cm diameter and 1 mm thickness was used as a target; a natural abundance titanium foil of the same dimensions was used as a target for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} reaction.
+For each run the target foils were co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thin polyethylene holder, as seen in \autoref{fig:main_holders}.
+Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue that could become activated during irradiation.
+\autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations.
+In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV, to saturate the induced Indium isomer activity.
 

### 2016-12-30 First_np_Paper/first_np_paper.tex
Updated section 2.3 with first round edits

@@
 
-\author[geo,eps]{D.XXX. Rutte}
+\author[geo,eps]{D. Rutte}
 
@@
 
-\comment{Need Daniel's middle initial}
+% \comment{Need Daniel's middle initial}
 
@@
 
-The kinematics of D-D fusion produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
-This distribution is a function of the incident deuteron kinetic energy, and has been well-documented; the energy-angle distribution for the incident 100 keV deuterons used in the HFNG can be seen plotted in \autoref{fig:scatt_angle}.
+The kinematics of D-D fusion at 100 keV lab energy produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab-frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
+This distribution is a function of the incident deuteron kinetic energy, and has been well-documented \cite{Liskien_Paulsen_1973}; \autoref{fig:scatt_angle} displays the energy-angle distribution for the incident 100 keV deuterons used in the HFNG.
 
@@
 Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target.
-Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with at least several feet of standoff from the D-D reaction surface.
-This would greatly reduce the flux (to approximately 10$^4$ neutrons/cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production \& decay in activation measurements.
-Instead, samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the D-D reaction surface.
-This allows the samples to subtend a fairly narrow (28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately 10$^8$ neutrons/cm$^2$ ) flux for activations.
+Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with a distance of at least 20 cm from the D-D reaction surface.
+This would greatly reduce the flux (to approximately 10$^4$ neutrons/s\ cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production and decay in activation measurements.
+Instead, the samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the D-D reaction surface.
+This allows the samples to subtend a fairly narrow ($\sim$28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately $\sci{1.3}{7}$neutrons/s\ cm$^2$ ) flux for activations.
+
+\comment{Make global flux / fluence unification}
 
@@
 
-To determine the energy distribution of neutrons incident upon the loaded foils, MCNP6 was used to model the generator operation, and produced a neutron energy spectrum incident upon target foils co-loaded into the HFNG, seen in \autoref{fig:mcnp_flux}.
-This spectrum verifies the forward-focused kinematics of the D-D reaction subtended by the co-loaded sample foils.
+\comment{Need to replace this figure - coming from Mauricio?}
+
+To determine the energy distribution of neutrons incident upon the loaded foils following production and transport, the Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
+This spectrum illustrates the forward-focused kinematics of the D-D reaction subtended by the co-loaded sample foils.
+
+% \begin{figure}
+%  \centering
+%  \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
+%  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
+%  \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
+%  \label{fig:mcnp_flux}
+% \end{figure}
 
@@
  \centering
- \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
+ \includegraphics[scale=0.6]{./figures/mcnp_flux_new.pdf}
  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
@@
 
+\comment{Use this version, old version (mcnp-flux.pdf), or some new combination of lines?}
+
 While this shows that the sample foils receive a very narrow energy distribution of incident neutrons, an effective neutron energy and energy bounds must be determined to constrain cross section ratio measurements.
-From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and average neutron energy of 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils.
-Due to the kinematics of D-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry, can be calculated as 2.7825 MeV.
+From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils.
+Due to the kinematics of D-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.7825 MeV.
 For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:
@@
 
+% \begin{figure}
+%  \centering
+%  \includegraphics[scale=0.6]{./figures/fracplot.pdf}
+%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
+%  \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
+%  \label{fig:frac_plot}
+% \end{figure}
+
 \begin{figure}
  \centering
- \includegraphics[scale=0.6]{./figures/fracplot.pdf}
+ \includegraphics[scale=0.6]{./figures/fracplot_new.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 
+\comment{Use this version, or old version (fracplot.pdf)?}
+
 This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.
-Using the flux-averaged neutron energy in the Indium foil as a centroid, this fraction of total reactions can be used to to estimate the uncertainty in effective neutron energy, which will become energy error bars in the excitation function for these reactions.
+Using the flux-averaged neutron energy in the Indium foil as a centroid, this fraction of total reactions can be used to estimate the uncertainty in effective neutron energy, which will become energy error bars in the excitation function for these reactions.
 Within 1 standard deviation above and below the centroid, 68.2\% of all reactions should be encompassed.
@@
 \end{figure*}
+
+\comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}
 
@@
 \end{figure*}
+
+\comment{Need to update \autoref{fig:decay_curves} - figures are blurry}
 

### 2016-12-30 First_np_Paper/first_np_paper.tex
Updated section 2.4 with first round edits

@@
 After irradiation, the co-loaded targets in each experiment were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy.
-Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar LEPS detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments.
+Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar Low-Energy Photon Spectrometer (LEPS) detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments.
 These can be seen in \autoref{fig:hpge_a} and \autoref{fig:hpge_b}.
 Both detectors were calibrated for both energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
-These efficiencies, along with gamma ray intensities for each transition, are used to convert the counts in each detected gamma ray photopeak into an activity for the activated isotopes and isomeric states.
+These efficiencies, along with gamma ray intensities for each transition, are used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
 
@@
 
-For all data collection, performed using the Ortec MAESTRO software, the foils were counted in their polyethylene holder, and placed against the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector.
+The foils were counted in their polyethylene holder, and placed close to the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
 This position allows for the detectors to subtend the largest possible solid angle of the gamma rays emitted by the foils.
-Before data was collected, detector dead time was verified to be less than 5\%, to avoid coincidence summing effects.
+All data collection was performed using the Ortec MAESTRO software.
+For each experiment the detector dead time was verified to be less than 5\%, to avoid coincidence summing effects.
 This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector, to reduce the dead time.
-For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector, and for the case of \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
+For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector.
+For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
+This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons.
+\ce{^{116}In} has a 54 minute half-life, decaying via $\beta^-$ with a Q value of 3.278 MeV.
+This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times$ the 511-keV gamma, which is produced via pair production in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production.
 After approximately 4 hours of spectra collection, the activated zinc foil was added back and counting resumed simultaneously with the indium foil.
-This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons.
-\ce{^{116}In} has a 54 minute half life, decaying via $\beta^-$ with a Q value of 3.278 MeV.
-This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times 511$  keV, which pair produce in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production.
-By waiting for 4 hours of counting the indium foil separately, nearly all \ce{^{116}In} will have decayed, making it safe to add the activated zinc foil without worries of significant 511 keV contamination.
+This allowed for decay of nearly all \ce{^{116}In}, avoiding significant 511 keV contamination.
 Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
@@
 
-To verify that each peak truly corresponds to assigned transitions, spectra collection for each foil was counted in a series of 15 - 30 minute sequential data acquisitions.
-By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponentially decaying curve may be fit to it, to determine the half life of the transition in question.
+\comment{Example spectra are messy - being updated...}
+
+To verify that each peak corresponds to the assigned transitions, spectra were acquired in a sequence of 15 - 30 minute intervals.
+By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponential decay function may be fit to it, to determine the half-life of the transition in question.
 Plots of these curves for each transition in this work are seen in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511}.
-The fitted half lives in each of these curves has strong statistical agreement with accepted half lives from the ENDF-VII/B library, indicating that these peaks are the correctly assigned transitions.
+The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives from the ENSDF library, confirming the respective peak assignments.
+
+\comment{Reference original ENSDF papers?}
 
@@
 
-Background-subtracted counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
+The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
 

### 2017-02-23 First_np_Paper/first_np_paper.tex
Updated a few XS figures, added 2 comments to manuscript
Added new decay curve figure for 336keV, to test direct labeling of figures
Updated abstract and front matter with Lee edits

@@
 %% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research A}
+\journalname{Nuclear Instruments and Methods in Physics Research B}
 
@@
 %% Give the abbreviation of the Journal.
-\jid{nima}
+\jid{nimb}
 % \jid{yspmi}
@@
 %% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Nucl Instrum Meth A}
+\jnltitlelogo{Nucl Instrum Meth B}
 
@@
 %%
-\title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\\ OR \\(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} at 2.76 MeV using a D-D Neutron Generator for Medical Isotope Studies}
-
-% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\tnoteref{label1}}
+\title{Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies}
+
+% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
 %% \tnotetext[label1]{}
@@
 
-\comment{Use D-D or DD as convention?}
-
-\comment{Choose a preferred title...}
-
-% \comment{Need Daniel's middle initial}
-
-\comment{Should street address be included for each institution, or just city / state / zip?}
-
-Neutron activation cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production reactions have been measured for quasi-monoenergetic 2.7645 MeV incident neutrons produced by the UC Berkeley High Flux Neutron Generator, a D-D plasma-based neutron source.
-\comment{ Need to decide on number of sig figs to report, and truncate appropriately - i.e.2.76 +0.15 - 0.22 - \#s taken from text section 3]
-} Measurements were performed using activation ratio methods, measured relative to co-irradiated indium foils using the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions.
-The use of thin foils and gamma spectroscopy using an HPGe and LEPS detectors allowed for cross section determination to within 6\% uncertainty.
-These cross section measurements show good agreement with the literature and theoretical values, but with lower uncertainty than existing measurements.
-This work has resulted in a detailed characterization of the D-D plasma-based neutron source, which can be used for other low-energy neutron reaction cross section measurements in the future.
-
-\comment{Abstract needs fleshing out.}
+%\comment{Use DD or DD as convention?}
+
+% \comment{Need Daniel's middle initial} - he doesn't have one
+
+Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
+The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
+The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
+Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 6\% uncertainty.
+The cross section were determined with lower uncertainty than existing measurements and are found to be  in good agreement with the literature and theoretical values.
+This work highlights the utility of using D-D plasma-based neutron sources, for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
+
+\comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
 
@@
 A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes, as many of these cross sections currently have not been measured, or possess significant uncertainties.
-One potential method for producing many of these isotopes is the use of (n,p) reactions via neutron beams from D-D neutron generators.
-Direct neutron activation, using a D-D neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production.
+One potential method for producing many of these isotopes is the use of (n,p) reactions via neutron beams from DD neutron generators.
+Direct neutron activation, using a DD neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production.
 Neutron activation can provide several advantages over charged-particle reactions from a targetry perspective.
@@
 
-Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
+Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
 This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}.
-Within the center of the target (at 8 mm from the D-D reaction surface), samples may be inserted prior to  HFNG startup.
+This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}.
+Within the center of the target (at 8 mm from the DD reaction surface), samples may be inserted prior to  HFNG startup.
 \autoref{fig:hfng_b} displays the target setup.
@@
 To avoid the introduction of this large uncertainty, 0.5-mm thin Indium foils were co-loaded along with each target foil for irradiation, with all production cross sections thus measured relative to the well-characterized \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} dosimetry standard reactions.
-In addition, over the energy region spanned by the D-D emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements.
+In addition, over the energy region spanned by the DD emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements.
 The use of this well-established ratio method removes the fluence dependence from all cross-section calculations, removing the largest source of systematic uncertainty in activation.
@@
 
-The kinematics of D-D fusion at 100 keV lab energy produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab-frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
+The kinematics of DD fusion at 100 keV lab energy produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab-frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
 This distribution is a function of the incident deuteron kinetic energy, and has been well-documented \cite{Liskien_Paulsen_1973}; \autoref{fig:scatt_angle} displays the energy-angle distribution for the incident 100 keV deuterons used in the HFNG.
@@
  % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
- \caption{Energy-angle distribution for neutrons emitted following D-D fusion, for 100 keV incident deuterons.}
+ \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons.}
  \label{fig:scatt_angle}
@@
 Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target.
-Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with a distance of at least 20 cm from the D-D reaction surface.
+Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with a distance of at least 20 cm from the DD reaction surface.
 This would greatly reduce the flux (to approximately 10$^4$ neutrons/s\ cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production and decay in activation measurements.
-Instead, the samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the D-D reaction surface.
+Instead, the samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the DD reaction surface.
 This allows the samples to subtend a fairly narrow ($\sim$28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately $\sci{1.3}{7}$neutrons/s\ cm$^2$ ) flux for activations.
@@
 To determine the energy distribution of neutrons incident upon the loaded foils following production and transport, the Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
-This spectrum illustrates the forward-focused kinematics of the D-D reaction subtended by the co-loaded sample foils.
+This spectrum illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
 
@@
 From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils.
-Due to the kinematics of D-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.7825 MeV.
+Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.7825 MeV.
 For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:
@@
 From \autoref{eqn:react_fraction},  these are found to be  F(2.7796 MeV) = 0.841 and F(2.7426 MeV) = 0.159, respectively; thus the effective neutron energy subtended by target foils is reported as $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
-This 37-keV full-energy spread verifies that, at such close distances to the D-D reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.
+This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.
 
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[width=5in]{./figures/ti_foils.png}
+%         \includegraphics[width=5in]{./figures/ti_foils.png}
+        \includegraphics[width=5in]{./figures/47sc_gspectrum_alt.pdf}
         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a planar LEPS detector}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[width=5in]{./figures/Sample_spectra.png}
+%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
+        \includegraphics[width=5in]{./figures/64Cu_gspectrum_alt.pdf}
         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[scale=0.6]{./figures/336keV_curve2.png}
+        \includegraphics[scale=0.6]{./figures/336keV_curve_new.pdf}
         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \includegraphics[scale=0.6]{./figures/391keV_curve_new.pdf}
         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 
-\comment{Add in EMPIRE data points?}
+\comment{Waiting on Lee for EMPIRE, ALICE data and language discussing differences and the significance of this.}
 
@@
 These measurements are consistent with experimental data and theoretical models,  and have been measured to lower uncertainty than existing measurements.
-The use of D-D neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
-While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the D-D neutron emission energy spectrum.
+The use of DD neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
+While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the DD neutron emission energy spectrum.
 

### 2017-02-24 First_np_Paper/first_np_paper.tex
Updated introduction section with Lee edits

@@
 
-Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
+Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC-Berkeley High Flux Neutron Generator.
 The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
@@
 The cross section were determined with lower uncertainty than existing measurements and are found to be  in good agreement with the literature and theoretical values.
-This work highlights the utility of using D-D plasma-based neutron sources, for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
+This work highlights the utility of using DD plasma-based neutron sources, for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
 
@@
 
-\comment{Add an initial \enquote{punchline} to  clarify the motivation?}
-
-\comment{Per Mauricio, does 2.7 MeV count as high energy? While fast, I would consider this to still be definitely in the low-energy regime, compared to spallation, etc.}
-
-A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes, as many of these cross sections currently have not been measured, or possess significant uncertainties.
-One potential method for producing many of these isotopes is the use of (n,p) reactions via neutron beams from DD neutron generators.
-Direct neutron activation, using a DD neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production.
-Neutron activation can provide several advantages over charged-particle reactions from a targetry perspective.
-Notably, the higher penetration of neutrons allows for the use of thick target designs, which can improve production throughput and greatly simplifies target cooling considerations.
-More importantly, low-energy neutron reactions can be used to prevent competing reaction channels in a charged-particle reaction which would otherwise contaminate the product specific activity.
-
-The present work focuses on the (n,p) production cross section measurements of \ce{^{64}Cu} and \ce{^{47}Sc}.
-Copper-64  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn}.
-The emitted 190-keV $\beta^-$ particle makes this an  attractive short-ranged therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging  due to the positron emission branch (for real-time dose monitoring and verification),  making \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols.
+There has been significant interest in the past several years in exploring the use of neutron-induced reactions to create radionuclides for a wide range of applications, due to the far greater range of neutrons as compared to charged particle beams ($\sfrac{\text{g}}{\text{cm}^2}$ as compared to 10's of $\sfrac{\text{mg}}{\text{cm}^2}$), together with the fact that isotope production facilities often produce large secondary neutron fields.
+Particular interest has been paid to (n,p) and (n,$\alpha$) charge-exchange reactions since these reactions produce high-specific activity radionuclide samples without the use of chemical carriers in the separation process.
+
+Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ \enquote{DT} and D(D,n)\ce{^3He} \enquote{DD} reactions.
+While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning.
+Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
+
+In contrast, while the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to radionuclide production, the lower flux from these generators limits their production rate.
+An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
+
+The purpose of the present work is to explore the potential for using high-flux neutron generators to make high-specific activity samples of radionuclides at the mCi level for local use in the application community.
+The research group at UC-Berkeley has been developing a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed several mm from the neutron producing surface in order to maximize the utilization of each neutron for the production of a desired radionuclide \textcolor{red}{[XXXref Cory paper]}.
+The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
+In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
+While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
+
+\comment{cite Cory's paper}
+
+The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn}.
+The emitted 190-keV $\beta^-$ particle makes this an  attractive short-range therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
+This makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols.
 In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-
-Scandium-47 ($t_{1/2}$ = 3.35 d) undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process.
+The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process.
 This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}.
-However, due to the short half-life  and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.
-
-\comment{Adding a short paragraph from Mauricio explaining benefits of DD generators vs other neutron sources?}
-
-\comment{Per Daniel, add a short summary of results here?}
-
-Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} and \ce{^{47}Ti} from solid target designs, without the need for additional carrier.
+However, due to the short half-life of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.
+In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} set for use in simultaneous therapeutic and diagnostic applications.
+
+\comment{cite theranostic papers, etc}
+
+Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} and \ce{^{47}Sc} from solid target designs, without the need for additional carrier.
 By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.
-
-\comment{Should this last paragraph be moved to the results and discussion at the end of the paper?}
 
@@
         \includegraphics[height=3in]{./figures/Capture.PNG}
-        \caption{The UC Berkeley High-Flux Neutron Generator,}
+        \caption{The UC-Berkeley High-Flux Neutron Generator,}
         \label{fig:hfng_a}

### 2017-02-24 First_np_Paper/first_np_paper.tex
Updated sections 2.1 and 2.2 with Lee edits

@@
 
-Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
+% Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
 This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}.
-Within the center of the target (at 8 mm from the DD reaction surface), samples may be inserted prior to  HFNG startup.
-\autoref{fig:hfng_b} displays the target setup.
-At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
-
-\comment{Karl: Comment or question primarily to Lee: Is it conventional to put photographs of equipment in PRC? I'm not sure it is; yes certainly for NIM, but not sure about PRC.}
-
-\comment{Note: all images here were included at nearly full-size.
-They obviously need to be reduced in size, but I included them here larger the needed, so they wouldn't be pixelated if enlarged.
-Shrink away :)}
+This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
+Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
+\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
+A 100 kV deuterium beam was extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
+
+Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
+This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
+This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
+Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
+\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
+A 100 kV deuterium beam was extracted at 1.3 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
+
+% \begin{figure}
+%  \centering
+% %  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
+%  \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
+%  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
+%  \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
+%  \label{fig:alt_HFNG}
+% \end{figure}
+
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[t]{0.4\textwidth}
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[height=3in]{./figures/Capture.PNG}
+%         \caption{The UC-Berkeley High-Flux Neutron Generator,}
+%         \label{fig:hfng_a}
+%     \end{subfigure}%
+%     ~ 
+%     \begin{subfigure}[t]{0.4\textwidth}
+%         \centering
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/target2.png}
+%         \caption{Cutaway of the target chamber.}
+%                 \label{fig:hfng_b}
+%     \end{subfigure}
+%     \caption{Note: the ion source is approximately 20 cm in diameter.}
+%      \label{fig:main_HFNG}
+% \end{figure*}
 
@@
     \centering
-%  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
- \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
- % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
- \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
- \label{fig:alt_HFNG}
-\end{figure}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.4\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=3in]{./figures/Capture.PNG}
-        \caption{The UC-Berkeley High-Flux Neutron Generator,}
-        \label{fig:hfng_a}
-    \end{subfigure}%
-    ~ 
-    \begin{subfigure}[t]{0.4\textwidth}
         \centering
@@
         \includegraphics[height=2in]{./figures/target2.png}
-        \caption{Cutaway of the target chamber.}
+        \caption{Cut-away schematic of the HFNG. Note: the ion source is approximately 20 cm in diameter.}
                 \label{fig:hfng_b}
-    \end{subfigure}
-    \caption{Note: the ion source is approximately 20 cm in diameter.}
-     \label{fig:main_HFNG}
-\end{figure*}
-
-\subsection{Sample loading}\label{sec:sample_loading}
-
-Direct activation of a thin foil can be used for high-fidelity measurement of neutron-induced reactions, through subsequent decay spectroscopy.
-This method can provide cross sections with far lower uncertainty than neutron time-of-flight measurements, but is heavily reliant upon precisely quantifying the neutron fluence incident upon a loaded target.
-To avoid the introduction of this large uncertainty, 0.5-mm thin Indium foils were co-loaded along with each target foil for irradiation, with all production cross sections thus measured relative to the well-characterized \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} dosimetry standard reactions.
-In addition, over the energy region spanned by the DD emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements.
-The use of this well-established ratio method removes the fluence dependence from all cross-section calculations, removing the largest source of systematic uncertainty in activation.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.3\textwidth}
+%      \label{fig:main_HFNG}
+\end{figure}
+
+\subsection{Cross section determination by relative activation}\label{sec:sample_loading}
+
+The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards.
+\autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations.
+In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
+After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium gamma-ray detector and the decay gamma-rays were recorded in variable-time bins.
+
+\begin{figure}
     \centering
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2in]{./figures/foils.png}
-        \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
+        \includegraphics[height=2in]{./figures/holder.pdf}
+        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
         \label{fig:holder_a}
-    \end{subfigure}%
-    ~ 
-    \begin{subfigure}[t]{0.3\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[height=2in]{./figures/holder.pdf}
-        \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
-                \label{fig:holder_b}
-    \end{subfigure}
-     ~ 
-    \begin{subfigure}[t]{0.3\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
-        \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
-                \label{fig:holder_c}
-    \end{subfigure}
-    \caption{}
-     \label{fig:main_holders}
-\end{figure*}
-
-For the measurement of the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section, a natural abundance commercial zinc foil of 1 cm diameter and 1 mm thickness was used as a target; a natural abundance titanium foil of the same dimensions was used as a target for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} reaction.
-For each run the target foils were co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thin polyethylene holder, as seen in \autoref{fig:main_holders}.
+\end{figure}
+
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[t]{0.3\textwidth}
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[height=2in]{./figures/foils.png}
+%         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
+%         \label{fig:holder_a}
+%     \end{subfigure}%
+%     ~ 
+%     \begin{subfigure}[t]{0.3\textwidth}
+%         \centering
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/holder.pdf}
+%         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
+%                 \label{fig:holder_b}
+%     \end{subfigure}
+%      ~ 
+%     \begin{subfigure}[t]{0.3\textwidth}
+%         \centering
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
+%         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
+%                 \label{fig:holder_c}
+%     \end{subfigure}
+%     \caption{}
+%      \label{fig:main_holders}
+% \end{figure*}
+
+1 cm diameter, 1 mm thick natural abundance zinc and titanium targets were employed for the measurement.
+Each of these was  co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thick polyethylene holder, as seen in \autoref{fig:holder_a}, which was mounted in the HFNG target center.
 Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue that could become activated during irradiation.
-\autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations.
-In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV, to saturate the induced Indium isomer activity.
 
@@
 
-The kinematics of DD fusion at 100 keV lab energy produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab-frame emission angular range of 0-180\degree, with respect to the incident deuteron beam.
-This distribution is a function of the incident deuteron kinetic energy, and has been well-documented \cite{Liskien_Paulsen_1973}; \autoref{fig:scatt_angle} displays the energy-angle distribution for the incident 100 keV deuterons used in the HFNG.
-
-\comment{Parenthetical citations, or just a list at the end? The Shimizu paper uses the latter as citation format.}
+The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 2.2 to 2.85 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
+This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.
+
+\comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}
+
+\comment{Is the one good reference (Liskien) sufficient?}
+
+\comment{Should we say more about the neutron angular and energy distributions? Something from Cory's thesis or the NIM-A papers that are coming along?}
+
+% \comment{Parenthetical citations, or just a list at the end? The Shimizu paper uses the latter as citation format.}
 

### 2017-02-25 First_np_Paper/first_np_paper.tex
Updated sections 2.3 with Lee edits

@@
 \autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.3 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
+A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
 
@@
 
-Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target.
-Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with a distance of at least 20 cm from the DD reaction surface.
-This would greatly reduce the flux (to approximately 10$^4$ neutrons/s\ cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production and decay in activation measurements.
-Instead, the samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the DD reaction surface.
-This allows the samples to subtend a fairly narrow ($\sim$28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately $\sci{1.3}{7}$neutrons/s\ cm$^2$ ) flux for activations.
-
-\comment{Make global flux / fluence unification}
+Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (~28\degree) angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$ s) neutron flux.
+This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
 
@@
  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
- \caption{MCNP6 model of the Berkeley HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.}
+ \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
  \label{fig:mcnp_vised}
@@
 
-\comment{Need to replace this figure - coming from Mauricio?}
-
-To determine the energy distribution of neutrons incident upon the loaded foils following production and transport, the Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
+\comment{Need to replace this figure w/ non-capitalized labels - this figure needs significant work, and I would appreciate anyone who can provide a better one}
+
+The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
 This spectrum illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
@@
  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
- \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
+ \caption{MCNP6-modeled neutron energy spectrum for the HFNG.
+The solid lines show the spectrum at the location of the indium and the target foil respectively.
+The dotted and dashed lines show the same with the target itself \enquote{voided} to remove scattering contributions.
+Less than 1\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.}
  \label{fig:mcnp_flux}
@@
 
-\comment{Use this version, old version (mcnp-flux.pdf), or some new combination of lines?}
-
-While this shows that the sample foils receive a very narrow energy distribution of incident neutrons, an effective neutron energy and energy bounds must be determined to constrain cross section ratio measurements.
-From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.7825 MeV.
-For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:
+%\comment{Use this version, old version (mcnp-flux.pdf), or some new combination of lines?}
+
+While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined.
+The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
+Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV.
+For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is given by:
 
@@
 \end{equation}
+
+% This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.      - note: moved to next paragraph, for better flow.
 
@@
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
+ \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]. The red arrows indicate the energy region that corresponds to 67\% of the total activation.}
  \label{fig:frac_plot}
@@
 
-\comment{Use this version, or old version (fracplot.pdf)?}
+%\comment{Use this version, or old version (fracplot.pdf)?}
+
+\comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%}
 
 This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.
-Using the flux-averaged neutron energy in the Indium foil as a centroid, this fraction of total reactions can be used to estimate the uncertainty in effective neutron energy, which will become energy error bars in the excitation function for these reactions.
-Within 1 standard deviation above and below the centroid, 68.2\% of all reactions should be encompassed.
-Thus, the upper and lower energy uncertainties correspond to the neutron energies $E'$  such that $F\pp{E'}$ = 0.841 and $F\pp{E'}$ = 0.159, respectively.
-From \autoref{eqn:react_fraction},  these are found to be  F(2.7796 MeV) = 0.841 and F(2.7426 MeV) = 0.159, respectively; thus the effective neutron energy subtended by target foils is reported as $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
-This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.
+The fraction of total reactions in the indium foil can be used to characterize the effective neutron energy bin.
+Our approach, in analogy to the Gaussian quantity $\sigma$, will be to use a horizontal \enquote{error bar}  to represent the energy range responsible for 68.2\% of the reactions taking place.
+Using this approach, we report the effective energy bin as being $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
+This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a quasi-monoenergetic neutron flux.
+
+% \comment{Truncate sig figs later on, after discussing systematic errors.}
 

### 2017-02-28 First_np_Paper/first_np_paper.tex
Updated section 2.7 with Lee edits

@@
 
-After irradiation, the co-loaded targets in each experiment were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy.
-Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar Low-Energy Photon Spectrometer (LEPS) detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments.
-These can be seen in \autoref{fig:hpge_a} and \autoref{fig:hpge_b}.
-Both detectors were calibrated for both energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
+After irradiation, the co-loaded targets were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy.
+Two detectors were used in this measurement.
+An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay, the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer and the 391 keV gamma-ray from the \ce{^{113m}In}  isomer.
+An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} as well as the two indium isomers mentioned above.
+Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
 These efficiencies, along with gamma ray intensities for each transition, are used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
 
-\begin{figure*}[H]
-    \centering
-    \begin{subfigure}[t]{0.7\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
-        \caption{ Ortec 80\% HPGe detector}
-        \label{fig:hpge_a}
-    \end{subfigure}%
-    ~ 
-    \begin{subfigure}[t]{0.28\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
-        \caption{Ortec planar LEPS detector}
-                \label{fig:hpge_b}
-    \end{subfigure}
-    \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
-     \label{fig:main_ge_detectors}
-\end{figure*}
-
-\comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}
-
-The foils were counted in their polyethylene holder, and placed close to the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
-This position allows for the detectors to subtend the largest possible solid angle of the gamma rays emitted by the foils.
+\comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}
+
+% \begin{figure*}[H]
+%     \centering
+%     \begin{subfigure}[t]{0.7\textwidth}
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
+%         \caption{ Ortec 80\% HPGe detector}
+%         \label{fig:hpge_a}
+%     \end{subfigure}%
+%     ~ 
+%     \begin{subfigure}[t]{0.28\textwidth}
+%         \centering
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
+%         \caption{Ortec planar LEPS detector}
+%                 \label{fig:hpge_b}
+%     \end{subfigure}
+%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
+%      \label{fig:main_ge_detectors}
+% \end{figure*}
+% 
+% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}
+
+The foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
 All data collection was performed using the Ortec MAESTRO software.
-For each experiment the detector dead time was verified to be less than 5\%, to avoid coincidence summing effects.
-This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector, to reduce the dead time.
+For each experiment the detector dead time was verified to be less than 5\%.
+No summing corrections need to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
+This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
+
 For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector.
 For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons.
-\ce{^{116}In} has a 54 minute half-life, decaying via $\beta^-$ with a Q value of 3.278 MeV.
-This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times$ the 511-keV gamma, which is produced via pair production in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production.
-After approximately 4 hours of spectra collection, the activated zinc foil was added back and counting resumed simultaneously with the indium foil.
-This allowed for decay of nearly all \ce{^{116}In}, avoiding significant 511 keV contamination.
+This is due to the fact that the \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation.
+The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the \ce{^{116}In} to decay.
 Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
 
-\begin{figure*}[H]
+\begin{figure*}[ht]
     \centering
@@
         \includegraphics[width=5in]{./figures/47sc_gspectrum_alt.pdf}
-        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a planar LEPS detector}
+        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
         \label{fig:spectra_a}
@@
 
-\comment{Example spectra are messy - being updated...}
-
-To verify that each peak corresponds to the assigned transitions, spectra were acquired in a sequence of 15 - 30 minute intervals.
-By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponential decay function may be fit to it, to determine the half-life of the transition in question.
-Plots of these curves for each transition in this work are seen in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511}.
-The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives from the ENSDF library, confirming the respective peak assignments.
-
-\comment{Reference original ENSDF papers?}
+To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals.
+The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
+The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \textcolor{red}{[XXXref reference original papers for the T1/2s]}, confirming the respective peak assignments.
+
+\comment{Reference original ENSDF papers}
 
@@
 
-\comment{Need to update \autoref{fig:decay_curves} - figures are blurry}
-
+The spectra for the different samples were summed and the peak area over background was determined using gf3, part of the RadWare analysis package from Oak Ridge   \cite{radford2000radware, Radford1995}.
 The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
@@
 
+\subsection{Experimental verification of incident neutron energy}\label{sec:lee_sec}
+
+As shown in \autoref{sec:sample_loading} above, the effective neutron energy depends on the angle range subtended by the sample with respect to the incident deuteron beam.
+In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.
+This centroid of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
+The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h).
+\autoref{fig:in_heat_plot} below shows the measured activities for these 9 indium foils.
+Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
+
+% 
+% \begin{figure}
+%  \centering
+%  \includegraphics[scale=0.6]{./figures/XXX.pdf}
+%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
+%  \caption{\textcolor{red}{INSERT CAPTION HERE}}
+%  \label{fig:in_heat_plot}
+% \end{figure}
+%
+
+\comment{cire relevant NDS article for t1/2}
+
+\comment{CHECK WITH ERIC for 3x3 In info and plot}
+
 \subsection{Calculation of measured cross sections}\label{sec:calcs_sec}
 
-Gamma spectroscopy analysis on the several days of collected spectra was used to measure the background-subtracted counts under each of the photopeaks of interest for the induced activities, as described in \autoref{sec:spectroscopy}.
-For a thin target consisting of \(N_T\) target nuclei, subjected to a constant monoenergetic neutron flux $\phi\pp{\bar{E}}$, the rate of production of the product nucleus will be:
+For a thin target consisting of \(N_T\) target nuclei (with a reaction cross section $\sigma\pp{\bar{E}}$), subjected to a constant neutron flux $\phi\pp{\bar{E}}$, the rate of production ($R$) of the product nucleus will be:
 
@@
 
-for a reaction with cross-section  $\sigma\pp{\bar{E}}$ at effective energy $\bar{E}$.
-If this irradiation lasts for  some time $t_1$, and gamma ray spectroscopy of the activated samples begins at a later time $t_2$ and ends at an even later time $t_3$, then the number of product decays (with decay constant $\lambda$) which take place between $t_2$ and $t_3$ will be:
+If this irradiation lasts for  some time $t_1$, and gamma ray spectrum acquisition begins at a later time $t_2$ and ends at  $t_3$, then the number of product decays ($D$; with decay constant $\lambda$) during the acquisition will be:
 
@@
 \begin{aligned}
-D &= \dfrac{R}{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}}
+D &= \dfrac{R}{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}}
 \\
-&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
+&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}} 
 \end{aligned}
@@
 
-If this decay emits a gamma ray with branching ratio $I_\gamma$ photons emitted per decay, and is detected with an absolute efficiency (photons detected / photons emitted) of $\epsilon_\gamma$, then the number of observed decays between $t_2$ and $t_3$ will be:
+If this decay emits a gamma ray with branching ratio $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed decays between $t_2$ and $t_3$ will be:
 
@@
 N_{obs} &= D \epsilon_\gamma I_\gamma \\
-&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} \nonumber
+&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}} \nonumber
 \end{align}
 
-Rearranging in terms of the observed cross-section:
-
-\begin{equation}
-\sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}}}
+Solving this equation for the  cross-section results in:
+
+\begin{equation}\label{eqn:single_xs_eqn}
+\sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}}}
 \end{equation}
 
-This model, in which subscripts $P$ indicate a quantity for either the \ce{^{64}Cu} or \ce{^{47}Sc} product, subscripts $In$ indicate a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer, can be taken in ratio, to calculate the measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production cross sections, relative to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering cross sections.
-Adding in a correction for the small self-attenuation of the gamma rays emitted by the activated foils, the final ratio model can be seen in \autoref{eqn:calc_eqn}:
+\autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils.
+This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.
+\autoref{eqn:calc_eqn} shows the ratio of the cross sections determined using this approach, in which subscript $P$ indicates a quantity for either \ce{^{64}Cu} or \ce{^{47}Sc}, and subscript $In$ indicates a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer.
+A minor term was added to correct for the small self-attenuation of the gamma rays emitted by the activated foils:
 
 \begin{align}\label{eqn:calc_eqn}
-\sigma_P &= \sigma_{In} \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1}  \\
-&\times \dfrac{e^{-\lambda_{In}t_2}-e^{-\lambda_{In}t_3}}{e^{-\lambda_{P}t_2} - e^{-\lambda_{P}t_3}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
+\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1}  \\
+&\times \dfrac{e^{-\lambda_{In}t_3}-e^{-\lambda_{In}t_2}}{e^{-\lambda_{P}t_3} - e^{-\lambda_{P}t_2}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
 \end{align}
@@
 
-With the exception of decay constants, which are assumed to be exact, each of the parameters in this model carries statistical uncertainty in measurement.
-In lieu of a differential error propagation, the total statistical error $\delta_\sigma$ is taken as the quadrature sum of all of the other errors  $\delta_i$:
+In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
+The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately YYY MeV greater than at 2.7 MeV.
+
+\comment{cite relevant NDS article}
+
+\comment{add appropriate numbers to (n,g) cross sections}
+
+\comment{cite IRDFF somewhere?}
+
+With the exception of decay constants, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries a statistical uncertainty.
+Based on the assumption that these uncertainties are independent, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
 
@@
 
-XXXXXXXXXXXXXXXX
-
-\comment{Not sure what else we need to consider for systematics...}
+The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the \textcolor{red}{YYY\%} uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the \textcolor{red}{YYY\%} uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section.
+An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.
+However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than \textcolor{red}{YY\%}.
+Other monitor foils could be used instead of indium, with \ce{^{57}Ni}(n,p)\ce{^{57}Co} being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \textcolor{red}{[XXXref NDS]}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 77+ days.
+The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
+We believe, based on \enquote{burn marks} on the production target that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
+However, every 1 mm change in the beam radius would cause a \textcolor{red}{XXX} MeV shift in the centroid and a \textcolor{red}{YYY} MeV change in the effective energy bin.
+
+\comment{filling in missing data}
+
+\comment{Use your energy-angle figure from Lisken above to estimate these numbers. You can point to the figure in the text if you'd like.}
 
@@
 
-Using the ratio methods described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of 2.7645 MeV,  + 0.0151 MeV / - 0.0219 MeV.
+Using the ratio method described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of 2.7645 MeV,  + 0.0151 MeV / - 0.0219 MeV.
 These values are recorded in \autoref{tab:xs_results}.
@@
 
-\comment{How many sig figs to round uncertainties to in table?}
-
-\comment{Report all 3 values in table? Report a weighted average between them?}
+\comment{Truncate sig figs here - Note that the systematic uncertainty you calculated in the previous paragraph will provide a natural limit on the number of significant figures you quote for the energy window.}
+
+\comment{Report a weighted average between the solo values, insert in text}
 
@@
 \centering
-\caption{Results of cross section measurement. }
+\caption{Results of cross section measurement.
+Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
 \label{tab:xs_results}
@@
 \end{table}
+
+\comment{Truncate sig figs in En in \autoref{tab:xs_results} }
 

### 2017-02-28 First_np_Paper/first_np_paper.tex
Updated section 3 with Lee edits

@@
 \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
-\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
+\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX *\end{tabular}                   \\ \bottomrule
 \end{tabular}
@@
 
-The results for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections can also be seen plotted in Figures \ref{fig:sc_xs} and \ref{fig:cu_xs}, respectively.
-It is apparent that the relative cross sections measured in the present work are consistent with both the small quantity of other literature results, and are measured to within 6\% uncertainty, lower than existing measurements.
-In addition, the results presented in this work show strong agreement with the recommended values from both the ENDF/B-VII.1 nuclear data library and reaction modeling results from TALYS\cite{koning2005talys}.
-
-\comment{Waiting on Lee for EMPIRE, ALICE data and language discussing differences and the significance of this.}
-
-\comment{Mention Shimizu data specifically? }
-
-\comment{Add a zoomed-in view like in \autoref{fig:cu_xs}?}
+Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \textcolor{red}{[XXXXref original experimental papers]}.
+The weighted average of our measurements give \textcolor{red}{XXXXXX} for \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \textcolor{red}{YYYYYY} for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textcolor{red}{6\%}).
+However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the \textcolor{red}{XXX groups} and both the ENDF/B-VII.1\textcolor{red}{[XXXref citation]} and TALYS\textcolor{red}{[XXXref citation]} values, but significantly below the results from \textcolor{red}{YYY}.
+
+\comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
+
+% \cite{koning2005talys}.
+
+\comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}
+
+\comment{Add Shimizu data into plots , as well as 115In capture points}
+
+\comment{Change to zoomed-in view like in \autoref{fig:cu_xs} as appropriate}
 
@@
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} relative production cross section.}
+ \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section relative to indium activation.}
  \label{fig:sc_xs}
@@
 
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
- \label{fig:cu_xs}
-\end{figure}
+% \begin{figure}
+%  \centering
+%  \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
+%  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
+%  \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
+%  \label{fig:cu_xs}
+% \end{figure}
 
@@
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{A zoomed-in view of \autoref{fig:cu_xs}.}
+ \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section relative to indium activation.}
  \label{fig:cu_xs_zoom}
 \end{figure}
+
+As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
+The results from both are consistent, indicating that the contributions from thermal \enquote{room return} neutrons are negligible for samples mounted in the center of the HFNG.
+This builds confidence in our results, and highlights the potential of using the HFNG for fast neutron capture reactions via activation.
+This will be discussed in greater detail in the conclusion section below.
+
+\comment{verify this claim!}
 

### 2017-03-01 First_np_Paper/first_np_paper.tex
Finished merging Lee's edits

@@
 \usepackage{gensymb}
+
+% \usepackage{mathtools, cuted}
 
@@
 
+\author[geo,eps]{T.\textcolor{red}{???} Becker}
+
 \author[ucb,lbl]{L.A. Bernstein}
@@
 \author[ucb]{E.F. Matthews}
+
+\author[geo,eps]{P.R. Renne}
 
@@
 Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ \enquote{DT} and D(D,n)\ce{^3He} \enquote{DD} reactions.
-While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning.
+While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning\cite{Updegraff2013}.
 Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
@@
 
-\comment{cite Cory's paper}
+\comment{how can we cite Mauricio's/Cory's upcoming paper? We need a good reference for the HFNG.}
 
@@
 The emitted 190-keV $\beta^-$ particle makes this an  attractive short-range therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols.
+This makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols\cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
 In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
 The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process.
-This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}.
+This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}\cite{Qaim2011,Qaim201731}.
 However, due to the short half-life of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.
@@
 
-Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} and \ce{^{47}Sc} from solid target designs, without the need for additional carrier.
+Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu}\cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc}\cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
 By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.
@@
 
+\comment{Can someone please provide me a better version of \autoref{fig:hfng_b}, with appropriate labeling? Please use PDF or other vector image format.}
+
 \subsection{Cross section determination by relative activation}\label{sec:sample_loading}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2in]{./figures/holder.pdf}
+        \includegraphics[height=2.5in]{./figures/holder.pdf}
         \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
@@
 \begin{align}\label{eqn:calc_eqn}
-\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1}  \\
+\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1} \times \\
 &\times \dfrac{e^{-\lambda_{In}t_3}-e^{-\lambda_{In}t_2}}{e^{-\lambda_{P}t_3} - e^{-\lambda_{P}t_2}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
@@
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textcolor{red}{6\%}).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the \textcolor{red}{XXX groups} and both the ENDF/B-VII.1\textcolor{red}{[XXXref citation]} and TALYS\textcolor{red}{[XXXref citation]} values, but significantly below the results from \textcolor{red}{YYY}.
+However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the \textcolor{red}{XXX groups} and both the ENDF/B-VII.1\textcolor{red}{[XXXref citation]} and TALYS\cite{Koning2012}  values, but significantly below the results from \textcolor{red}{YYY}.
 
@@
 
-\section{Summary}
-
-Using direct activation methods for thin foils as described in this work, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections have been measured for  2.7645 MeV neutrons, to within 6\% uncertainty.
-These measurements are consistent with experimental data and theoretical models,  and have been measured to lower uncertainty than existing measurements.
-The use of DD neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
-While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the DD neutron emission energy spectrum.
-
-\comment{Future work? Thermal neutron measurements? Something like the following?}
+\section{Conclusion}
+
+Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  \textcolor{red}{2.7645 MeV +0.151/-0.219} neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
+The cross sections were measured with a  6\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections.
+The measured values of \textcolor{red}{XXXX and YYYY}, respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
+In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast (e.g., $\approx$2.7 MeV) neutrons, rather than from \enquote{room return} thermal neutrons.
+The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
+
+\comment{Truncate sig figs above, fill in values}
+
+The proximity of the target to the neutron production surface also opens the possibility of performing a measurement of the cross section over a limited energy range via mounting the samples slightly off-axis with respect to the beam.
+This could be accomplished using the 9-foil sample holder described in \autoref{sec:lee_sec} above.
+Mounting samples at each of these positions would subject the samples to neutrons with energies ranging from \textcolor{red}{XXX at the central location to YYY} at the four corners, with the other locations having intermediate energy values.
+These sorts of multi-sample measurements could be used to determine the \enquote{rising edge} of the cross sections, aiding in the development of optical models for the reactants.
+
+\comment{fill in values above}
+
+These measurements also highlight the possibility of using fast neutrons from DD and/or DT generators to produce meaningful quantities of radioisotopes for a wide range of applications via charge exchange reactions, such as (n,p) and (n,$\alpha$).
+Many applications, including diagnostic and therapeutic medical use, require mCi activity levels.
+The production of a radionuclide sample with an activity $A$ driven to secular equilibrium using a neutron source with a total flux $\phi$ and a reaction cross section $\sigma$ acting on sample of $N_{target}$ atoms is given by the expression:
+
+\begin{equation}
+A = \lambda N_{product} = \eta \phi \sigma N_{target}
+\end{equation}
+
+where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired reaction on one of the target sample atoms:
+
+% \begin{figure*}[H]
+% \hline
+% \begin{equation}
+% \eta = \int_0^E dE_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\phi} 4\pi r^2 dr d\pp{\cos{\theta}} d\theta
+% \end{equation}
+% \end{figure*}
+
+% \begin{strip}
+
+\begin{align}
+\eta &= \int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}, \nonumber\\
+\text{d}\mathbf{V} &= r^2 \text{d}r \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
+\end{align}
+% \end{strip}
+
+An optimal design for the neutron generator would also allow for the possibility of reflecting fast neutrons back onto the target to maximize their utilization for radionuclide production.
+This sort of \enquote{flux trap} has been used for the production of radionuclides in reactors, but has not to date been optimized for use with fast neutrons  at DD and/or DT neutron sources.
+The HFNG, with its self-loading target and \enquote{flux trap} geometry, has many features that make it well-suited for such isotope production purpose.
+Switching to DT operation would dramatically increase the flux as well as the production cross section, since (n,p) tends to be significantly larger at 14 MeV.
+However, the higher neutron energy would also open the (n,pn) channels.
+In the case of \ce{^{47}Sc}, this would lead to the presence of \ce{^{46}Sc} ($t_{1/2}$ = 83.79 d) in the sample, which might pose some concerns for medical applications.
+However, this is not an issue for \ce{^{64}Cu} since the (n,pn) channel leads to the production of stable \ce{^{63}Cu}.
+
+\comment{cite relevant NDS article}
+
+In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections at \textcolor{red}{2.7 MeV} incident neutron energies.
+In addition to improving the value of these measurements nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
+In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
+
+\comment{fill in values above}
 
@@
 Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.
-
- \comment{Who else should we acknowledge?}
+Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, and  DFG Research Fellowship RU 2065/1-1.
+
+ We also wish to acknowledge Glenn Jones for \textcolor{red}{XXXXXXXXXXX}.
+
+ \comment{Please provide appropriate language for Glenn Jones. Who else should we acknowledge?}
 
@@
 
-H. F. Aly et al., Microchim. Acta, vol. 59, no. 1, 1971.
-
-K. S. Bhatki et al., J. Radioanal. Chem., vol. 2, no. 1-2, 1969.
-
-T. H. Bokhari et al., J. Radioanal. Nucl. Chem., vol. 283, no. 2, 2010.
-
-J. F. Briesmeister et al., Los Alamos National Laboratory, 1986.
+% H. F. Aly et al., Microchim. Acta, vol. 59, no. 1, 1971.
+
+% K. S. Bhatki et al., J. Radioanal. Chem., vol. 2, no. 1-2, 1969.
+
+% T. H. Bokhari et al., J. Radioanal. Nucl. Chem., vol. 283, no. 2, 2010.
+
+% J. F. Briesmeister et al., Los Alamos National Laboratory, 1986.
 
@@
 
-A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.
-
-H. Liskien et al., Nucl. Data Tables, vol 11, 1973.
-
-M. R. Lewis et al., J. Nucl. Med., vol. 44, no. 8, Aug. 2003.
+% A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.
+
+% H. Liskien et al., Nucl. Data Tables, vol 11, 1973.
+
+% M. R. Lewis et al., J. Nucl. Med., vol. 44, no. 8, Aug. 2003.
 

### 2017-03-02 First_np_Paper/first_np_paper.tex
Adding citations, squashing comments

@@
 Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ \enquote{DT} and D(D,n)\ce{^3He} \enquote{DD} reactions.
-While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning\cite{Updegraff2013}.
+While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
 Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
@@
 The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn}.
+\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
 The emitted 190-keV $\beta^-$ particle makes this an  attractive short-range therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols\cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
+This makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
 In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process.
-This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc}\cite{Qaim2011,Qaim201731}.
+The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process \cite{Burrows2007}.
+This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
 However, due to the short half-life of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.
-In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} set for use in simultaneous therapeutic and diagnostic applications.
-
-\comment{cite theranostic papers, etc}
+In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} set for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
+
+% \comment{cite theranostic papers, etc}
 
@@
 
-\comment{Regex to replace all hard figure references with LaTeX cross-references}
+% \comment{Regex to replace all hard figure references with LaTeX cross-references  [F,f]igure[^s*}]     }
 
@@
 
-The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards.
+The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012}.
 \autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations.
 In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
-After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium gamma-ray detector and the decay gamma-rays were recorded in variable-time bins.
+After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and the decay gamma-rays were recorded in variable-time bins.
 
@@
 
-\comment{Regex to replace table hard link with LaTeX cross-reference.}
+% \comment{Regex to replace table hard link with LaTeX cross-reference. - match w/ [T,t]able[^*}]   }
 
@@
 \toprule
-Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (cm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
-$^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ XXX $\pm$ XXX$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ XXX $\pm$ XXX$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  XXXXXX$^\dagger$\end{tabular} \\
-$^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\end{tabular}                           \\
-$^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ XXXXXX\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ XXXXXX\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ XXXXXXX\end{tabular}                                   \\ \bottomrule
+Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (cm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
+$^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
+$^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
+$^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
 \end{tabular}%
@@
 
-\comment{Need foil data from Mauricio's 2nd Ti run}
+% \comment{Need foil data from Mauricio's 2nd Ti run}
 
@@
 
-\comment{Regex to replace equations with LaTeX formats, add cross-references.}
+\comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }
 
@@
 
-M. B. Chadwick,et al., Nucl. Data Sheets, vol. 107, no. 12, 2006.
+M. B. Chadwick,et al., Nucl. Data Sheets, vol. 107, no. 12, 2006.   (ENDF)
 
@@
 
-C. Müller et al., J. Nucl. Med., vol. 55, no. 10, Oct. 2014.
-
-N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.
-
-L. Pietrelli et al., J. Radioanal. Nucl. Chem., vol. 157, no. 2, 1992.
-
-S. M. Qaim et al., IAEA Technical Reports Series No. 473, 2011.
+% C. Müller et al., J. Nucl. Med., vol. 55, no. 10, Oct. 2014.
+
+N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.   (EXFOR)
+
+% L. Pietrelli et al., J. Radioanal. Nucl. Chem., vol. 157, no. 2, 1992.
+
+% S. M. Qaim et al., IAEA Technical Reports Series No. 473, 2011.
 
@@
 
-D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.
+% D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.
 

### 2017-03-03 First_np_Paper/first_np_paper.tex
Updated fracplot and scatt_angle figures

@@
 
+% Tweak sim for better inline text tilde
+\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
+% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}
+
 \makeatletter
@@
 
-The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 2.2 to 2.85 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
+The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 
+% 2.2 to 2.85 MeV   (thin-target Liskien values)
+% 2.18 to 2.78 MeV  (Liskien thick-target coefficient corrections to above)
+2.18 to 2.78 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
 This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.
 
-\comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}
+% \comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}
 
@@
 
-Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (~28\degree) angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$ s) neutron flux.
+Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\degree)
+% the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
+angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$ s) neutron flux.
 This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
@@
 
-\comment{Need to replace this figure w/ non-capitalized labels - this figure needs significant work, and I would appreciate anyone who can provide a better one}
+\comment{Need to replace this figure w/ non-capitalized labels - this figure needs significant improvement, and I would appreciate anyone who can provide a better one}
 
@@
 This spectrum illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
+
+\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe}
 
@@
 The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV.
+Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
 For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is given by:
@@
 
-\comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }
+% \comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }
 
@@
 
-\comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%}
+% \comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%, after using new A}
 

### 2017-03-03 First_np_Paper/first_np_paper.tex
Squashed comments, updated the 4x decay curve figures

@@
 Two detectors were used in this measurement.
-An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay, the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer and the 391 keV gamma-ray from the \ce{^{113m}In}  isomer.
-An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} as well as the two indium isomers mentioned above.
+An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay \cite{Singh2007}, the 391 keV gamma-ray from the \ce{^{113m}In}  isomer \cite{Blachot2010a}, and the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer \cite{Blachot2012}.
+An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} \cite{Burrows2007} as well as the two indium isomers mentioned above.
 Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
@@
 
-\comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[]
+\centering
+\caption{Gamma-ray properties for the decay lines measured in the present work.}
+\label{tab:decay_props}
+\begin{tabular}{@{}cccc@{}}
+\toprule
+Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
+\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 \% \emph{4}      & 12.701 h \emph{2}  \\
+\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 \% \emph{4}      & 3.3492 d \emph{6}  \\
+\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 \% \emph{17}    & 99.476 m \emph{23} \\
+\ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.8 \% \emph{4}      & 4.486 h \emph{4}   \\
+\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 \% \emph{4}      & 54.29 m \emph{17}  \\ \bottomrule
+\end{tabular}
+\end{table}
+
+% \comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}
 
@@
 For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation.
+This is due to the fact that the \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
 The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the \ce{^{116}In} to decay.
@@
 The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
-The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \textcolor{red}{[XXXref reference original papers for the T1/2s]}, confirming the respective peak assignments.
-
-\comment{Reference original ENSDF papers}
+The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \cite{Burrows2007,Singh2007,Blachot2010a,Blachot2012,Blachot2010}, confirming the respective peak assignments.
+
+% \comment{Reference original ENSDF papers}
 
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[scale=0.6]{./figures/417keV_curve2.png}
+        \includegraphics[scale=0.6]{./figures/417keV_curve_new.pdf}
         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[scale=0.6]{./figures/511keV_curve2.png}
+        \includegraphics[scale=0.6]{./figures/511keV_curve_new.pdf}
         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 This centroid of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
-The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h).
+The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
 \autoref{fig:in_heat_plot} below shows the measured activities for these 9 indium foils.
@@
 
-\comment{cire relevant NDS article for t1/2}
-
-\comment{CHECK WITH ERIC for 3x3 In info and plot}
+\comment{CHECK WITH ERIC for 3x3 In info and plot  \autoref{fig:in_heat_plot}}
 

### 2017-03-10 First_np_Paper/first_np_paper.tex
Added new 3x3 infium figure, squashed comments

@@
 
-The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012}.
+The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012,zsolnay2012technical}.
 \autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations.
@@
 \centering
-\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments. \color{red}{Need Mauricio data!}}
+\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments. }
 \label{tab:peak_counts}
@@
 Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\ \hline
+Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
 Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\ \hline
-Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\ \hline
-Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\ \hline
-End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\ \hline
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\ \hline
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &    \hrulefill       &  \hrulefill      \\ \hline
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &    \hrulefill       &   \hrulefill     \\ \hline
-Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & XXXX  
+Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
+Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
+Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
+End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
+Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ \hline
+Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 860 $\pm$ 40    & 2545 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ \hline
+Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 24464 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ \hline
+Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257  
 \end{tabular}%
@@
 
-% 
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/XXX.pdf}
-%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
-%  \caption{\textcolor{red}{INSERT CAPTION HERE}}
-%  \label{fig:in_heat_plot}
-% \end{figure}
-%
-
-\comment{CHECK WITH ERIC for 3x3 In info and plot  \autoref{fig:in_heat_plot}}
+\begin{figure}
+ \centering
+ \includegraphics[scale=0.6]{./figures/ex1.png}
+ % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
+ \caption{Relative fluxes as seen by a 3 x 3 array of indium foils.
+The central foil corresponds to the location in which target and monitor foils were mounted during the cross section measurements, verifying that the beam is centered on the middle of mounted foils.}
+ \label{fig:in_heat_plot}
+\end{figure}
+
+% \comment{CHECK WITH ERIC for 3x3 In info and plot  \autoref{fig:in_heat_plot}}
 
@@
 
-Solving this equation for the  cross-section results in:
+Solving this equation for the  cross section results in:
 
@@
 
-In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
-The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately YYY MeV greater than at 2.7 MeV.
-
-\comment{cite relevant NDS article}
-
-\comment{add appropriate numbers to (n,g) cross sections}
-
-\comment{cite IRDFF somewhere?}
+In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min \cite{Blachot2010}) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
+The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately 2,000 times greater than at 2.7 MeV  \cite{Capote2012,zsolnay2012technical}.
+
+% \comment{cite relevant NDS article}
 
@@
 
-This total statistical uncertainty will be plotted as the cross-section error bar in the excitation function for these production reactions.
+This total statistical uncertainty will be plotted as the cross section error bar in the excitation function for these production reactions.
 
@@
 Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
-\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX *\end{tabular}                   \\ \bottomrule
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \rule{0pt}{8ex}
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\ \rule{0pt}{6ex}
+\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.904 $\pm$ 1.193, \\ 26.751 $\pm$ 1.394 *\end{tabular}                   \\ \bottomrule
 \end{tabular}

### 2017-03-11 First_np_Paper/first_np_paper.tex
Added new XS figures w/ citations, squashed comments

@@
  \centering
- \includegraphics[scale=0.6]{./figures/ex1.png}
+ \includegraphics[scale=0.54]{./figures/ex1.png}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 
-The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the \textcolor{red}{YYY\%} uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the \textcolor{red}{YYY\%} uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section.
+The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the 2.586\% uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the 1.447\% uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section  \cite{Capote2012,zsolnay2012technical}.
 An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.
-However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than \textcolor{red}{YY\%}.
-Other monitor foils could be used instead of indium, with \ce{^{57}Ni}(n,p)\ce{^{57}Co} being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \textcolor{red}{[XXXref NDS]}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 77+ days.
+However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 2\%.
+Other monitor foils could be used instead of indium, with \ce{^{57}Ni}(n,p)\ce{^{57}Co} being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 77+ days.
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
@@
 
-\comment{Need Mauricio's Cu point w/ more sigfigs. Need Mauricio's Sc point too}
-
 \comment{Truncate sig figs here - Note that the systematic uncertainty you calculated in the previous paragraph will provide a natural limit on the number of significant figures you quote for the energy window.}
 
-\comment{Report a weighted average between the solo values, insert in text}
+% \comment{Report a weighted average between the solo values, insert in text}
 
@@
 Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \rule{0pt}{8ex}
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\ \rule{0pt}{6ex}
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \\[0.1ex]
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\  \\[0.1ex]
 \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.904 $\pm$ 1.193, \\ 26.751 $\pm$ 1.394 *\end{tabular}                   \\ \bottomrule
@@
 
-Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \textcolor{red}{[XXXXref original experimental papers]}.
-The weighted average of our measurements give \textcolor{red}{XXXXXX} for \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \textcolor{red}{YYYYYY} for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textcolor{red}{6\%}).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the \textcolor{red}{XXX groups} and both the ENDF/B-VII.1\textcolor{red}{[XXXref citation]} and TALYS\cite{Koning2012}  values, but significantly below the results from \textcolor{red}{YYY}.
-
-\comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
+Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
+The weighted average of our measurements give   46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In}) and  49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In})    for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.262 $\pm$  0.822 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
+However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith, Armitage, and Ikeda groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from Hussain, Gonzalez, and Shimizu \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
+
+\comment{I referenced the original publication for each data set in \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} as ''Author (Year)''.
+Is this acceptable, or should I add the parenthetical ([28], [29],[etc]) onto each entry in the figure legends as well?}
+
+% \comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
 
@@
 
-\comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}
-
-\comment{Add Shimizu data into plots , as well as 115In capture points}
-
-\comment{Change to zoomed-in view like in \autoref{fig:cu_xs} as appropriate}
+% \comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}
+
+% \comment{Add our 115In capture points? S}
+
+\comment{Is the ''zoom'' appropriate for Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}?}
 
@@
  \centering
- \includegraphics[scale=0.6]{./figures/47Sc_fixed.pdf}
+ \includegraphics[scale=0.65]{./figures/47sc_fixed_1point.pdf}
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
  \centering
- \includegraphics[scale=0.6]{./figures/64cu_fixed_zoom.pdf}
+ \includegraphics[scale=0.65]{./figures/64cu_fixed_1point.pdf}
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
 
-\comment{verify this claim!}
+\comment{The capture cross sections are actually consistent with effective 2.45 MeV neutrons (which are still fast).
+For capture of 2.76 MeV neutrons, we predict (n,p) cross sections approx.
+15 mb less than using the In(n,n') monitors.
+How can we incorporate best this?
+Please suggest language changes / additions.
+Since they  are only consistent at 2.45 MeV, I removed the points from Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}, but will happily add them back if someone thinks they serve a purpose.}
 
@@
 Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  \textcolor{red}{2.7645 MeV +0.151/-0.219} neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
-The cross sections were measured with a  6\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections.
+The cross sections were measured with a  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
 The measured values of \textcolor{red}{XXXX and YYYY}, respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
-In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast (e.g., $\approx$2.7 MeV) neutrons, rather than from \enquote{room return} thermal neutrons.
+In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast (e.g., $\approx$2.45 MeV) neutrons, rather than from \enquote{room return} thermal neutrons.
 The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
 
-\comment{Truncate sig figs above, fill in values}
+\comment{Truncate sig figs above, fill in values, use correct fast neutron energy above}
 
@@
 However, the higher neutron energy would also open the (n,pn) channels.
-In the case of \ce{^{47}Sc}, this would lead to the presence of \ce{^{46}Sc} ($t_{1/2}$ = 83.79 d) in the sample, which might pose some concerns for medical applications.
+In the case of \ce{^{47}Sc}, this would lead to the presence of \ce{^{46}Sc} ($t_{1/2}$ = 83.79 d \cite{Wu2000}) in the sample, which might pose some concerns for medical applications.
 However, this is not an issue for \ce{^{64}Cu} since the (n,pn) channel leads to the production of stable \ce{^{63}Cu}.
-
-\comment{cite relevant NDS article}
 
@@
 
- \comment{Should we specifically mention other isotopes we plan to measure?}
+%  \comment{Should we specifically mention other isotopes we plan to measure?}
 
@@
 
- We also wish to acknowledge Glenn Jones for \textcolor{red}{XXXXXXXXXXX}.
+ We also wish to acknowledge Glenn Jones for \textcolor{red}{XXXXX XXXXXX}.
 
@@
 
-M. B. Chadwick,et al., Nucl. Data Sheets, vol. 107, no. 12, 2006.   (ENDF)
-
 % A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.
@@
 
-N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.   (EXFOR)
+% N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.   (EXFOR)
 
@@
 
-T. Shimizu, et al, Ann. Nucl. Energy, vol. 31, no. 9, pp. 975-990, 2004.
-
-T. Shimizu, et al, Nucl. Instruments Methods Phys. Res. Sect. A Accel. Spectrometers, Detect. Assoc. Equip., vol. 527, no. 3, pp. 543-553, 2004.
+% T. Shimizu, et al, Ann. Nucl. Energy, vol. 31, no. 9, pp. 975-990, 2004.
+
+% T. Shimizu, et al, Nucl. Instruments Methods Phys. Res. Sect. A Accel. Spectrometers, Detect. Assoc. Equip., vol. 527, no. 3, pp. 543-553, 2004.
 
@@
 \comment{Cite Cory's thesis, or upcoming NIM paper?}
-
-\comment{Convert these to BibTeX format!}
 

### 2017-03-11 First_np_Paper/first_np_paper.tex
Finished squashing comments, sending out draft for next edits...

@@
 
-\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe}
+\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}
 
@@
 
-\comment{Use your energy-angle figure from Lisken above to estimate these numbers. You can point to the figure in the text if you'd like.}
+\comment{Can someone use the energy-angle figure from Lisken above (or another tool) to estimate these numbers?
+% You can point to the figure in the text if you'd like.
+}
 
@@
 
-\comment{Truncate sig figs here - Note that the systematic uncertainty you calculated in the previous paragraph will provide a natural limit on the number of significant figures you quote for the energy window.}
+\comment{Truncate sig figs here - Note that the systematic uncertainty  calculated in the previous paragraph will provide a natural limit on the number of significant figures to quote for the energy window.}
 
@@
 The cross sections were measured with a  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of \textcolor{red}{XXXX and YYYY}, respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
-In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast (e.g., $\approx$2.45 MeV) neutrons, rather than from \enquote{room return} thermal neutrons.
+The measured values of  26.262 $\pm$  0.822 mb and  46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
+In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast \textcolor{red}{(e.g., $\approx$2.45 MeV)} neutrons, rather than from \enquote{room return} thermal neutrons.
 The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
 
-\comment{Truncate sig figs above, fill in values, use correct fast neutron energy above}
+\comment{Truncate sig figs above, use correct fast neutron energy above}
 
@@
 
-\comment{fill in values above}
+\comment{Can someone estimate the energy of the corner foils?}
 

### 2017-04-19 First_np_Paper/first_np_paper.tex
Changed paragraphs to have 1 sentence per line, for easier merging of edits. Updated .gitignore rules
Merged in Batch's 2nd round edits

@@
 
-\author[lbl]{J.C. Batchelder}
+\author[ucb]{J.C. Batchelder}
 
@@
 
-\author[geo,eps]{T.\textcolor{red}{???} Becker}
+\author[geo]{T.A. Becker}
 
@@
 
-Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ \enquote{DT} and D(D,n)\ce{^3He} \enquote{DD} reactions.
+Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
  While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
@@
 The purpose of the present work is to explore the potential for using high-flux neutron generators to make high-specific activity samples of radionuclides at the mCi level for local use in the application community.
-The research group at UC-Berkeley has been developing a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed several mm from the neutron producing surface in order to maximize the utilization of each neutron for the production of a desired radionuclide \textcolor{red}{[XXXref Cory paper]}.
+ The research group at UC-Berkeley has been developing a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed several mm from the neutron producing surface in order to maximize the utilization of each neutron for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
  The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
@@
 While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
-
-\comment{how can we cite Mauricio's/Cory's upcoming paper? We need a good reference for the HFNG.}
 
@@
 This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-However, due to the short half-life of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium.
+However, due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
 In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} set for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
@@
 
-Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu}\cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc}\cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
+Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
 By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.
@@
 
-1 cm diameter, 1 mm thick natural abundance zinc and titanium targets were employed for the measurement.
+One cm diameter, 1 mm thick natural abundance zinc and titanium targets were employed for the measurement.
 Each of these was  co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thick polyethylene holder, as seen in \autoref{fig:holder_a}, which was mounted in the HFNG target center.
@@
 
-\comment{Is the one good reference (Liskien) sufficient?}
-
-\comment{Should we say more about the neutron angular and energy distributions? Something from Cory's thesis or the NIM-A papers that are coming along?}
+%\comment{Should we say more about the neutron angular and energy distributions? Something from Cory's thesis or the NIM-A papers that are coming along?}
 
@@
 % the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
-angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$ s) neutron flux.
+angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
 This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
@@
 
-\comment{Need to replace this figure w/ non-capitalized labels - this figure needs significant improvement, and I would appreciate anyone who can provide a better one}
+\comment{Does \autoref{fig:mcnp_vised} serve any purpose? I'm starting to think it doesn't - should we just cut it?}
 
@@
 
-\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}
+% \comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}
 
@@
  Our approach, in analogy to the Gaussian quantity $\sigma$, will be to use a horizontal \enquote{error bar}  to represent the energy range responsible for 68.2\% of the reactions taking place.
-Using this approach, we report the effective energy bin as being $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
+ Using this approach, we report the effective energy bin as being $E_n$=2.765$^{+0.015}_{-0.022}$ MeV.
 This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a quasi-monoenergetic neutron flux.
-
-% \comment{Truncate sig figs later on, after discussing systematic errors.}
+%$E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
 
@@
 Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 \% \emph{4}      & 12.701 h \emph{2}  \\
-\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 \% \emph{4}      & 3.3492 d \emph{6}  \\
-\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 \% \emph{17}    & 99.476 m \emph{23} \\
-\ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.8 \% \emph{4}      & 4.486 h \emph{4}   \\
-\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 \% \emph{4}      & 54.29 m \emph{17}  \\ \bottomrule
+\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 $\pm$ 0.4        & 12.701 h   \\
+\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 $\pm$ 0.4      & 3.3492 d   \\
+\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 $\pm$ 0.17    & 99.476 m  \\
+\ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
+\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 $\pm$ 0.4      & 54.29 m   \\ \bottomrule
 \end{tabular}
 \end{table}
+
+% Version using NDS-style uncertainties 
+%
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}[]
+% \centering
+% \caption{Gamma-ray properties for the decay lines measured in the present work.}
+% \label{tab:decay_props}
+% \begin{tabular}{@{}cccc@{}}
+% \toprule
+% Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
+% \ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 \% \emph{4}      & 12.701 h \emph{2}  \\
+% \ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 \% \emph{4}      & 3.3492 d \emph{6}  \\
+% \ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 \% \emph{17}    & 99.476 m \emph{23} \\
+% \ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.8 \% \emph{4}      & 4.486 h \emph{4}   \\
+% \ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 \% \emph{4}      & 54.29 m \emph{17}  \\ \bottomrule
+% \end{tabular}
+% \end{table}
 
@@
  No summing corrections need to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
-This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
+%This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
 
@@
 \centering
-\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments. }
+\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
 \label{tab:peak_counts}
@@
  The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
-\autoref{fig:in_heat_plot} below shows the measured activities for these 9 indium foils.
+ \autoref{fig:in_heat_plot}  shows the measured activities for these 9 indium foils.
  Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
@@
  \centering
- \includegraphics[scale=0.54]{./figures/ex1.png}
+ \includegraphics[scale=0.58]{./figures/ex2.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
-We believe, based on \enquote{burn marks} on the production target that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
-However, every 1 mm change in the beam radius would cause a \textcolor{red}{XXX} MeV shift in the centroid and a \textcolor{red}{YYY} MeV change in the effective energy bin.
-
-\comment{filling in missing data}
-
-\comment{Can someone use the energy-angle figure from Lisken above (or another tool) to estimate these numbers?
-% You can point to the figure in the text if you'd like.
-}
+ We believe, based on \enquote{burn marks} on the production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
+ However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width.
 
@@
 
-Using the ratio method described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of 2.7645 MeV,  + 0.0151 MeV / - 0.0219 MeV.
+Using the ratio method described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.765$^{+0.015}_{-0.022}$ MeV.
 These values are recorded in \autoref{tab:xs_results}.
-
-\comment{Truncate sig figs here - Note that the systematic uncertainty  calculated in the previous paragraph will provide a natural limit on the number of significant figures to quote for the energy window.}
 
@@
 
-\comment{Truncate sig figs in En in \autoref{tab:xs_results} }
-
 Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
@@
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith, Armitage, and Ikeda groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from Hussain, Gonzalez, and Shimizu \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
-
-\comment{I referenced the original publication for each data set in \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} as ''Author (Year)''.
+However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith (1975), Armitage (1967), and Ikeda (1990) groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from Hussain (1983), Gonzalez (1962), and Shimizu (2004) \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
+
+%\comment{I referenced the original publication for each data set in \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} as ''Author (Year)''.
 Is this acceptable, or should I add the parenthetical ([28], [29],[etc]) onto each entry in the figure legends as well?}
-
+%\comment{Batch - add year next to author in text}
 % \comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
@@
 
-\comment{Is the ''zoom'' appropriate for Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}?}
+% \comment{Is the ''zoom'' appropriate for Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}?}
 
@@
 Since they  are only consistent at 2.45 MeV, I removed the points from Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}, but will happily add them back if someone thinks they serve a purpose.}
+\comment{Batch - in both figs 10 and 11, our value is hard to see, esp.
+in black and white...
+How to improve this, since there are so many experimental sets?
+Bigger symbols (this makes the centroid harder to see)?
+arrow pointing to it?
+Circle it?}
 
@@
 
-Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  \textcolor{red}{2.7645 MeV +0.151/-0.219} neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
+Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.765$^{+0.015}_{-0.022}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
 The cross sections were measured with a  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
@@
 
-\comment{Truncate sig figs above, use correct fast neutron energy above}
+\comment{Use correct fast neutron energy above}
 
@@
  This could be accomplished using the 9-foil sample holder described in \autoref{sec:lee_sec} above.
-Mounting samples at each of these positions would subject the samples to neutrons with energies ranging from \textcolor{red}{XXX at the central location to YYY} at the four corners, with the other locations having intermediate energy values.
+ Mounting samples at each of these positions would subject the samples to neutrons with energies ranging from 2.765 MeV at the central location to 2.616 MeV at the four corners, with the other locations having intermediate energy values.
  These sorts of multi-sample measurements could be used to determine the \enquote{rising edge} of the cross sections, aiding in the development of optical models for the reactants.
-
-\comment{Can someone estimate the energy of the corner foils?}
 
@@
 
-In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections at \textcolor{red}{2.7 MeV} incident neutron energies.
+In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
  In addition to improving the value of these measurements nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
  In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
-
-\comment{fill in values above}
 
@@
 % \addcontentsline{toc}{chapter}{Bibliography}
-% \bibliographystyle{elsarticle-num}
-\bibliographystyle{ieeetr}
+\bibliographystyle{elsarticle-num}
+% \bibliographystyle{ieeetr}
 \bibliography{../../library}
@@
 % D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.
-
-\comment{Cite Cory's thesis, or upcoming NIM paper?}
 

### 2017-04-19 First_np_Paper/first_np_paper.tex
Updated Figure 1. Merged in Eric's 2nd round edits

@@
 %%
-\title{Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies}
-
-% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
+\title{Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}
+
+% \title{(n,p) Cross Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
 %% \tnotetext[label1]{}
@@
 \author[ucb]{A.S. Voyles \corref{cor1}}
-\ead{andrew.voyles@gmail.com}
+\ead{andrew.voyles@berkeley.edu}
 
@@
 The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 6\% uncertainty.
-The cross section were determined with lower uncertainty than existing measurements and are found to be  in good agreement with the literature and theoretical values.
-This work highlights the utility of using DD plasma-based neutron sources, for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
+Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
+The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
+This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
 
 \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
-
-\comment{For my corresponding author email, should I list my Gmail (more permanent) or my Berkeley / LBL address (more professional)?}
 
@@
 
-There has been significant interest in the past several years in exploring the use of neutron-induced reactions to create radionuclides for a wide range of applications, due to the far greater range of neutrons as compared to charged particle beams ($\sfrac{\text{g}}{\text{cm}^2}$ as compared to 10's of $\sfrac{\text{mg}}{\text{cm}^2}$), together with the fact that isotope production facilities often produce large secondary neutron fields.
+There has been significant interest in the past several years in exploring the use of neutron-induced reactions to create radionuclides for a wide range of applications.
+This interest is due to the volumetric absorption of neutrons as compared to charged particle beams (ranges of $\sfrac{\text{g}}{\text{cm}^2}$ as compared to 10's of $\sfrac{\text{mg}}{\text{cm}^2}$), together with the fact that isotope production facilities often produce large secondary neutron fields.
  Particular interest has been paid to (n,p) and (n,$\alpha$) charge-exchange reactions since these reactions produce high-specific activity radionuclide samples without the use of chemical carriers in the separation process.
@@
 Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
- While reactors produce copious quantities of neutrons, their energy spectrum is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
+ While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
  Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
 
-In contrast, while the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to radionuclide production, the lower flux from these generators limits their production rate.
+In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to (n,p) radionuclide production.
+However, the lower achievable flux from these generators limits their production rate.
  An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
 
-The purpose of the present work is to explore the potential for using high-flux neutron generators to make high-specific activity samples of radionuclides at the mCi level for local use in the application community.
- The research group at UC-Berkeley has been developing a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed several mm from the neutron producing surface in order to maximize the utilization of each neutron for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
+The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
+ The research group at UC-Berkeley has been developing a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
  The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
@@
 \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-The emitted 190-keV $\beta^-$ particle makes this an  attractive short-range therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly attractive for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
+The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
+This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
 In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity 159-keV gamma ray in the process \cite{Burrows2007}.
-This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the more well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-However, due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
-In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} set for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
+The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
+This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
+Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
+In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
 
@@
 
-Current methodology in radiochemistry has been proven to successfully recover upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
+Current methodology in radiochemistry has shown recovery of upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
 By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.
@@
 Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
+This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
+This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
 Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[height=2in]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/target2.png}
+        \includegraphics[height=2in]{./figures/cutaway.png}
         \caption{Cut-away schematic of the HFNG. Note: the ion source is approximately 20 cm in diameter.}
@@
 
-\comment{Can someone please provide me a better version of \autoref{fig:hfng_b}, with appropriate labeling? Please use PDF or other vector image format.}
+% \comment{Can someone please provide me a better version of \autoref{fig:hfng_b}, with appropriate labeling? Please use PDF or other vector image format.}
 
@@
 In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
- After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and the decay gamma-rays were recorded in variable-time bins.
+ After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and time-dependent decay gamma-ray spectra were collected.
 
@@
 The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
-This spectrum illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
+This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
 
@@
 
-From this definition, it is possible to calculate $F\pp{E'}$, the fraction of total reactions induced up to some energy $E' < E_{max}$:
+From this definition, it is possible to calculate $F\pp{E'}$, the fraction of total reactions induced by neutrons up to some energy $E' < E_{max}$:
 
@@
 % \usepackage{booktabs}
-\begin{table}[]
+\begin{table}
 \centering
@@
 
-The foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
+The irradiated foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
 All data collection was performed using the Ortec MAESTRO software.
 For each experiment the detector dead time was verified to be less than 5\%.
- No summing corrections need to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
+ No summing corrections needed to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
 %This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
@@
 For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
-The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the \ce{^{116}In} to decay.
+This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
+The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
 Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
@@
 
-The spectra for the different samples were summed and the peak area over background was determined using gf3, part of the RadWare analysis package from Oak Ridge   \cite{radford2000radware, Radford1995}.
+The spectra for the different samples were summed and the net peak areas were fitted using gf3, part of the RadWare analysis package from Oak Ridge National Laboratory   \cite{radford2000radware, Radford1995}.
 The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
@@
  In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.
- This centroid of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
+ This centroid position of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
  The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
@@
 
-If this decay emits a gamma ray with branching ratio $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed decays between $t_2$ and $t_3$ will be:
+If this decay emits a gamma ray with absolute intensity $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed decays between $t_2$ and $t_3$ will be:
 
@@
 
-\item $I_\gamma$ is the decay gamma ray branching ratio,
+\item $I_\gamma$ is the decay gamma ray absolute intensity [\%],
 
@@
 
-With the exception of decay constants, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries a statistical uncertainty.
-Based on the assumption that these uncertainties are independent, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
+With the exception of decay constants, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries am uncertainty.
+Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
 
@@
 
-This total statistical uncertainty will be plotted as the cross section error bar in the excitation function for these production reactions.
-
-\subsection{Systematic errors}
+This total  uncertainty will be plotted as the cross section error bar in the excitation function for these production reactions.
+
+\subsection{Systematic uncertainties}
 
@@
  An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.
- However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 2\%.
- Other monitor foils could be used instead of indium, with \ce{^{57}Ni}(n,p)\ce{^{57}Co} being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 77+ days.
+ However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
+ Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71+ days.
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
@@
 
-Using the ratio method described here, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.765$^{+0.015}_{-0.022}$ MeV.
+Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.765$^{+0.015}_{-0.022}$ MeV.
 These values are recorded in \autoref{tab:xs_results}.
@@
 \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\  \\[0.1ex]
-\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.904 $\pm$ 1.193, \\ 26.751 $\pm$ 1.394 *\end{tabular}                   \\ \bottomrule
+\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.904 $\pm$ 1.193, \\ 26.751 $\pm$ 1.394*\end{tabular}                   \\ \bottomrule
 \end{tabular}
@@
 Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of our measurements give   46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In}) and  49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In})    for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.262 $\pm$  0.822 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The weighted average of the measurements give   46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In}) and  49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In})    for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.262 $\pm$  0.822 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
@@
 Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.765$^{+0.015}_{-0.022}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
-The cross sections were measured with a  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
+The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
 The measured values of  26.262 $\pm$  0.822 mb and  46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.

### 2017-04-21 First_np_Paper/first_np_paper.tex
Updated Figure 2. Merged in Karl's 2nd round edits

@@
 \usepackage{subcaption}
-\usepackage{booktabs}
+\usepackage{booktabs,siunitx}
 \usepackage{gensymb}
@@
 \usepackage[section]{placeins}
+\usepackage{multirow}
 
@@
 
+\sisetup{separate-uncertainty=true,table-space-text-post = *}
+
+\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
+
+\newcommand{\subfigimg}[3][,]{%
+  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
+  \leavevmode\rlap{\usebox1}% Print image
+  \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
+  \phantom{\usebox1}% Insert appropriate spcing
+}
+
 \makeatletter
@@
 
-Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC-Berkeley High Flux Neutron Generator.
+Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
 The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
@@
 
+\comment{Karl:  \enquote{Comment to engender some discussion.
+I have a small concern here, reminiscent of what happened to our electron backstreaming paper in PRAB.
+To be publishable, even in NIMB, there has to be a crisp research question resolved, or some innovation.
+I think an angle that is missing here is that this is a new design of neutron generator, whose design maximizes the flux density (n/sec/cm2), although the total flux, while respectable, is not spectacular in itself.
+This is Lee's recent mantra, and I now understand its significance.
+Problematically, as Andrew has pointed out, we don't have the actual instrument paper published yet, so the thrust of the paper can't be too focused on the flux density issue, but a workable angle would be \enquote{given we have this new capability, this is an example of its power}.
+Let me suggest Lee provide a sentence for the abstract, and a few sentences of text in the appropriate spot.}}
+
 \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
@@
 In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to (n,p) radionuclide production.
-However, the lower achievable flux from these generators limits their production rate.
+However, the lower achievable flux from these generators limits their production capabilities.
  An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
@@
 The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
- The research group at UC-Berkeley has been developing a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
+\comment{Karl:  \enquote{A comment, hopefully not too gratuitous at this point, could be inserted here to the effect that if the promise of plasma-based DD generators is ultimately borne out, not only is it anticipated that most hospitals could have their own source affordably, but that it would open up a whole new realm of very short lifetime medical isotopes.
+Lee to be the arbiter of whether this is prudent or not.}}
+ The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
  The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
@@
 This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
+Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
 \autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
@@
 %         \includegraphics[height=3in]{./figures/Capture.PNG}
-%         \caption{The UC-Berkeley High-Flux Neutron Generator,}
+%         \caption{The UC Berkeley High-Flux Neutron Generator,}
 %         \label{fig:hfng_a}
@@
         \includegraphics[height=2in]{./figures/cutaway.png}
-        \caption{Cut-away schematic of the HFNG. Note: the ion source is approximately 20 cm in diameter.}
+        \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
                 \label{fig:hfng_b}
@@
 
-One cm diameter, 1 mm thick natural abundance zinc and titanium targets were employed for the measurement.
+One cm diameter, 1-mm thick natural abundance zinc and titanium targets were employed for the measurement.
 Each of these was  co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thick polyethylene holder, as seen in \autoref{fig:holder_a}, which was mounted in the HFNG target center.
@@
 % \usepackage{graphicx}
+
 \begin{table*}
 \centering
-\caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-}
+\caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.}
 \label{tab:foil_specs}
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}ccccccc@{}}
+\begin{tabular}{@{}ccccS[table-format=+1.2,
+                  table-figures-uncertainty=1]S[table-format=+2.2,
+                  table-figures-uncertainty=1]S[table-format=+1.3,
+                  table-figures-uncertainty=1]@{}}
 \toprule
-Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (cm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
-$^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
-$^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
-$^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
+{Foils Used} & {Metal Purity}          & {Abundance (a/o)}                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & {Thickness (mm)}                                                                                                         & {Diameter (mm)}                                                                                                           & {Mass (g)}                                                                                    \\ \midrule
+
+\multirow{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirow{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirow{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirow{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
+
+ &  & & & 0.50 \pm 0.03* & 9.98 \pm 0.15*  & 0.248 \pm 0.005* \\
+
+  &  & & & 0.49 \pm 0.03* & 9.96 \pm 0.10* &  0.241 \pm 0.005* \\
+
+   &  & & & 0.53 \pm 0.06$^\dagger$ & 10.01 \pm 0.11$^\dagger$ & 0.247 \pm 0.005$^\dagger$\\
+
+    &  & & & 0.50 \pm 0.02$^\dagger$ & 10.00 \pm 0.09$^\dagger$  & 0.248 \pm 0.005$^\dagger$ \\ \hline
+
+\multirow{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirow{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirow{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirow{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
+
+ &  & & & 1.03 \pm 0.01 & 9.76 \pm 0.17 & 0.521 \pm 0.005 \\
+
+  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
+
+\multirow{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirow{2}*{\minitab[c]{99.999\%   }} & \multirow{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirow{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
+
+  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\   \bottomrule
 \end{tabular}%
@@
 \end{table*}
+
+% \begin{table*}
+% \centering
+% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
+% }
+% \label{tab:foil_specs}
+% \resizebox{\textwidth}{!}{%
+% \begin{tabular}{ccccccc}
+% \toprule
+% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
+% 
+% 
+% 
+% 
+% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}{S[table-format=+1.2,
+%    table-figures-uncertainty=1]}0.49 \pm 0.02* \\ 0.50 \pm 0.03* \\ 0.49 \pm 0.03* \\ 0.53 \pm 0.06$^\dagger$ \\ 0.50 \pm 0.02$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.2,
+%    table-figures-uncertainty=1]}9.75 \pm 0.09* \\ 9.98 \pm 0.15* \\ 9.96 \pm 0.10* \\ 10.01 \pm 0.11$^\dagger$ \\ 10.00 \pm 0.09$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.3,
+%    table-figures-uncertainty=1]}0.248 \pm 0.005* \\ 0.248 \pm 0.005* \\ 0.241 \pm 0.005* \\ 0.247 \pm 0.005$^\dagger$\\  0.248 \pm 0.005$^\dagger$\ \end{tabular} \\ \hline
+%    
+%    
+%    
+% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}{S[table-format=+1.2,
+%    table-figures-uncertainty=1]}1.03 \pm 0.01 \\ 1.03 \pm 0.01 \\ 1.02 \pm 0.01\end{tabular}                                    & \begin{tabular}{S[table-format=+1.2,
+%    table-figures-uncertainty=1]}9.93 \pm 0.14 \\ 9.76 \pm 0.17 \\ 9.89 \pm 0.15\end{tabular}                                     & \begin{tabular}{S[table-format=+1.3,
+%    table-figures-uncertainty=1]}0.538 \pm 0.005 \\ 0.451 \pm 0.005 \\ 0.452 \pm 0.005\ \end{tabular}                           \\ \hline
+% 
+% 
+% 
+% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}{S[table-format=+1.2,
+%    table-figures-uncertainty=1]}1.16 \pm 0.02 \\ 1.15 \pm 0.02\end{tabular}                                                         &\begin{tabular}{S[table-format=+1.2,
+%    table-figures-uncertainty=1]}9.93 \pm 0.04 \\ 9.94 \pm 0.03\end{tabular}                                                          & \begin{tabular}{S[table-format=+1.3,
+%    table-figures-uncertainty=1]}0.337 \pm 0.005 \\ 0.337 \pm 0.005\ \end{tabular}                                   \\ \bottomrule
+% \end{tabular}%
+% }
+% \end{table*}
+
+% \begin{table*}
+% \centering
+% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
+% }
+% \label{tab:foil_specs}
+% \resizebox{\textwidth}{!}{%
+% \begin{tabular}{@{}ccccccc@{}}
+% \toprule
+% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
+% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
+% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
+% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
+% \end{tabular}%
+% }
+% \end{table*}
 
@@
 % the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
-angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
+angular range in a region of impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
 This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
@@
 Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
-These efficiencies, along with gamma ray intensities for each transition, are used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
+These efficiencies, along with gamma ray intensities for each transition, were used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
 
@@
 %         \includegraphics[width=5in]{./figures/ti_foils.png}
-        \includegraphics[width=5in]{./figures/47sc_gspectrum_alt.pdf}
-        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
-        \label{fig:spectra_a}
+        \subfigimg[width=5in]{a)}{./figures/47sc_gspectrum_alt.pdf}
+%         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
+% 	\caption{}
+        \refstepcounter{subfigure}\label{fig:spectra_a}
     \end{subfigure}%
@@
 %         \includegraphics[width=5in]{./figures/Sample_spectra.png}
-        \includegraphics[width=5in]{./figures/64Cu_gspectrum_alt.pdf}
-        \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-                \label{fig:spectra_b}
+        \subfigimg[width=5in]{b)}{./figures/64Cu_gspectrum_alt.pdf}
+%         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
+          \refstepcounter{subfigure}       \label{fig:spectra_b}
     \end{subfigure}
-    \caption{Example gamma spectra collected to monitor radioisotope production.}
+    \caption{Example gamma spectra collected to monitor radioisotope production.
+(a)  Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector and (b) gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
      \label{fig:main_spectra}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[scale=0.6]{./figures/336keV_curve_new.pdf}
-        \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-        \label{fig:decay_curve_336}
+        \subfigimg[scale=0.6]{a)}{./figures/336keV_curve_new.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:decay_curve_336}
     \end{subfigure}%
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \includegraphics[scale=0.6]{./figures/391keV_curve_new.pdf}
-        \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-        \label{fig:decay_curve_391}
+        \subfigimg[scale=0.6]{b)}{./figures/391keV_curve_new.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:decay_curve_391}
     \end{subfigure}%
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \includegraphics[scale=0.6]{./figures/417keV_curve_new.pdf}
-        \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                \label{fig:decay_curve_417}
+        \subfigimg[scale=0.6]{c)}{./figures/417keV_curve_new.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:decay_curve_417}
     \end{subfigure}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[scale=0.6]{./figures/511keV_curve_new.pdf}
-        \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \label{fig:decay_curve_511}
+        \subfigimg[scale=0.6]{d)}{./figures/511keV_curve_new.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:decay_curve_511}
     \end{subfigure}%
-    \caption{Decay curves used to verify photopeak transition assignment.}
+    \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
      \label{fig:decay_curves}
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{c|ccccc}
-Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
-Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
-Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
-Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
-End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ \hline
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 860 $\pm$ 40    & 2545 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ \hline
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 24464 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ \hline
-Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257  
+\begin{tabular}{l|ccccc}
+\toprule
+% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
+Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \midrule
+Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ 
+Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ 
+Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ 
+Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ 
+Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ 
+End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ 
+Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
+Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 860 $\pm$ 40    & 2545 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
+Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 24464 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
+Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257 \\ \bottomrule
 \end{tabular}%
@@
 \end{table*}
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{graphicx}
+% \begin{table*}
+% \centering
+% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
+% \label{tab:peak_counts}
+% \resizebox{\textwidth}{!}{%
+% \begin{tabular}{@{}l|
+%                   S[table-format=+5.1,table-figures-uncertainty=1]|
+%                   S[table-format=+5.1,table-figures-uncertainty=1]|
+%                   S[table-format=+5.1,table-figures-uncertainty=1]|
+%                   S[table-format=+5.1,table-figures-uncertainty=1]|
+%                   S[table-format=+5.1,table-figures-uncertainty=1]|
+%                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
+% Reference Foil                     & \multirow{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
+% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
+% Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
+% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
+% Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
+% Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
+% End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
+% Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 \pm 1490 & 74321 \pm 275 & 39895 \pm 201 & 2122 \pm 55 & 55102 \pm 268   \\ \hline
+% Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 \pm 171    & 860 \pm 40    & 2545 \pm 54 &    \hrulefill       &  \hrulefill      \\ \hline
+% Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 \pm 643   & 12852 \pm 118 & 24464 \pm 159 &    \hrulefill       &   \hrulefill     \\ \hline
+% Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 \pm 83 & 5544 \pm 257  
+% \end{tabular}%
+% }
+% \end{table*}
 
@@
  However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71+ days.
+ Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
@@
 \end{table}
+
+\comment{Karl:  \enquote{For the figures, let me suggest you make a red solid rectangle whose dimensions represent the error bars in both energy and cross section.
+Then put a large red circle around it, whose diameter is of order 10\% of the size of the whole graph, to focus the eyes.
+In the caption, mention that the size of the rectangle represents the error limits.}}
 
@@
 In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast \textcolor{red}{(e.g., $\approx$2.45 MeV)} neutrons, rather than from \enquote{room return} thermal neutrons.
+\comment{Karl: \enquote{You may wish to add a statement that this is a significant finding of this work.
+It wasn't a foregone conclusion that it would work out this way, given the several order of magnitude difference in cross section.}}
 The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
@@
 
+ \comment{Karl: \enquote{Excellent paragraph.
+You may with to say that the HFNG is now operating at 10$^9$ n/sec, with a clear path towards 10$^{10}$, and a design study is underway for such a neutron-reflector assisted HFNG for actual medical isotope production.}}
+
 In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
@@
  Future work will involve the continued measurement of the (n,p) production cross sections for various other emerging therapeutic and diagnostic radioisotopes, to expand the toolset of options available for modern medical imaging and cancer therapy.
-This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments
+This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments.
 
@@
 Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, and  DFG Research Fellowship RU 2065/1-1.
-
- We also wish to acknowledge Glenn Jones for \textcolor{red}{XXXXX XXXXXX}.
-
- \comment{Please provide appropriate language for Glenn Jones. Who else should we acknowledge?}
+Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, \textcolor{red}{NSF ARRA Grant \# XXXXXXXX}, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
+
+\comment{Add NSF Grant number from P. Renne.}
+
+We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction and commissioning of the High Flux Neutron Generator.
 

### 2017-04-21 First_np_Paper/first_np_paper.tex
Merged in Daniel's 2nd round edits

@@
 
-With the exception of decay constants, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries am uncertainty.
+With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries am uncertainty.
 Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
@@
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
- We believe, based on \enquote{burn marks} on the production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
+ We believe, based on \enquote{burn marks} on the deuteron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
  However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width.
@@
 \toprule
-Reaction                                                                            & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                       \\ \midrule
+Reaction                                                                            & $\sigma$($E_n$ = 2.765$^{+0.015}_{-0.022}$ MeV) (mb)                                                                       \\ \midrule
 \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \\[0.1ex]

### 2017-04-21 First_np_Paper/first_np_paper.tex
Removed old Figure 4 (MCNP wireframe model). Updated New Figure 8 (old figure 9). Merged in Lee's 2nd round edits

@@
 %%
-\title{Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}
+\title{Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}
 
@@
 
-Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
+Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator (HFNG).
+The HFNG is a compact neutron generator designed as a \enquote{flux-trap} that maximizes the probability that a neutron will interact with a sample loaded into a specific, central location.  
 The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
@@
 Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
+The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.765$^{+0.015}_{-0.022}$ MeV neutrons is reported as   46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.262 $\pm$  0.822 mb.
 The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
-This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
-
-\comment{Karl:  \enquote{Comment to engender some discussion.
+This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.
+
+% Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
+% The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
+% The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
+% Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
+% The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
+% This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
+
+% \comment{Karl:  \enquote{Comment to engender some discussion.
 I have a small concern here, reminiscent of what happened to our electron backstreaming paper in PRAB.
@@
 
-\comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
+% \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
 
@@
 The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
-\comment{Karl:  \enquote{A comment, hopefully not too gratuitous at this point, could be inserted here to the effect that if the promise of plasma-based DD generators is ultimately borne out, not only is it anticipated that most hospitals could have their own source affordably, but that it would open up a whole new realm of very short lifetime medical isotopes.
-Lee to be the arbiter of whether this is prudent or not.}}
  The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
@@
 
-\begin{figure}
- \centering
- %trim option's parameter order: left bottom right top
- \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
- % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
- \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
- \label{fig:mcnp_vised}
-\end{figure}
-
-\comment{Does \autoref{fig:mcnp_vised} serve any purpose? I'm starting to think it doesn't - should we just cut it?}
+% \begin{figure}
+%  \centering
+%  %trim option's parameter order: left bottom right top
+%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
+%  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
+%  \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
+%  \label{fig:mcnp_vised}
+% \end{figure}
+
+% \comment{Does \autoref{fig:mcnp_vised} serve any purpose? I'm starting to think it doesn't - should we just cut it?}
 
@@
  \centering
- \includegraphics[scale=0.58]{./figures/ex2.pdf}
+ \includegraphics[scale=0.55]{./figures/fig1_cropped.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
- We believe, based on \enquote{burn marks} on the deuteron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
+ We believe, based on \enquote{burn marks} on the neutron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
  However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width.
@@
 Then put a large red circle around it, whose diameter is of order 10\% of the size of the whole graph, to focus the eyes.
-In the caption, mention that the size of the rectangle represents the error limits.}}
+In the caption, mention that the size of the rectangle represents the error limits.}  Lee: \enquote{I would suggest that you zoom in on the energy and cross section value we measured (say 2.5-3.0 MeV and 10-70 mb).
+Use a thicker line for our data point and/or make it larger.
+- Lee}}
 
@@
 As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
- The results from both are consistent, indicating that the contributions from thermal \enquote{room return} neutrons are negligible for samples mounted in the center of the HFNG.
- This builds confidence in our results, and highlights the potential of using the HFNG for fast neutron capture reactions via activation.
+The results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
  This will be discussed in greater detail in the conclusion section below.
 
-\comment{The capture cross sections are actually consistent with effective 2.45 MeV neutrons (which are still fast).
+% \comment{The capture cross sections are actually consistent with effective 2.45 MeV neutrons (which are still fast).
 For capture of 2.76 MeV neutrons, we predict (n,p) cross sections approx.
@@
 Since they  are only consistent at 2.45 MeV, I removed the points from Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}, but will happily add them back if someone thinks they serve a purpose.}
-\comment{Batch - in both figs 10 and 11, our value is hard to see, esp.
-in black and white...
-How to improve this, since there are so many experimental sets?
-Bigger symbols (this makes the centroid harder to see)?
-arrow pointing to it?
-Circle it?}
-
-\section{Conclusion}
-
-Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.765$^{+0.015}_{-0.022}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
-The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.262 $\pm$  0.822 mb and  46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
-In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast \textcolor{red}{(e.g., $\approx$2.45 MeV)} neutrons, rather than from \enquote{room return} thermal neutrons.
-\comment{Karl: \enquote{You may wish to add a statement that this is a significant finding of this work.
-It wasn't a foregone conclusion that it would work out this way, given the several order of magnitude difference in cross section.}}
-The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
-
-\comment{Use correct fast neutron energy above}
-
-The proximity of the target to the neutron production surface also opens the possibility of performing a measurement of the cross section over a limited energy range via mounting the samples slightly off-axis with respect to the beam.
+
+\section{Discussion}
+
+The proximity of the target to the neutron production surface opens the possibility of performing a measurement of the cross section over a limited energy range via mounting the samples slightly off-axis with respect to the beam.
  This could be accomplished using the 9-foil sample holder described in \autoref{sec:lee_sec} above.
@@
 
- \comment{Karl: \enquote{Excellent paragraph.
-You may with to say that the HFNG is now operating at 10$^9$ n/sec, with a clear path towards 10$^{10}$, and a design study is underway for such a neutron-reflector assisted HFNG for actual medical isotope production.}}
-
-In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
- In addition to improving the value of these measurements nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
- In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
-
+ \section{Conclusion and Future Work}
+
+Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.765$^{+0.015}_{-0.022}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
+The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
+The measured values of  26.262 $\pm$  0.822 mb and  46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
+
+ In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
+ While this is not consistent with the average neutron energy at the target location (2.765$^{+0.015}_{-0.022}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
+ This in turn highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
+The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
+ In addition to improving the value of these measurements for nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
+
+% In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
+ It is worth noting that at the time of publication, the  HFNG is now operating at 10$^9$ n/sec, with
+a clear path towards 10$^{10}$.
+%  In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
  Future work will involve the continued measurement of the (n,p) production cross sections for various other emerging therapeutic and diagnostic radioisotopes, to expand the toolset of options available for modern medical imaging and cancer therapy.
@@
  \section{Acknowledgements}
+
+ We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
+ We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
+ Lastly, we would like to acknowledge the students in the Nuclear Reactions and Radiation (NE102) laboratory course at UC Berkeley who participated in these experiments, including Joe Corvino, Nizelle Fajardo, Scott Parker and Evan Still.
 
@@
 \comment{Add NSF Grant number from P. Renne.}
-
-We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction and commissioning of the High Flux Neutron Generator.
 

### 2017-04-21 First_np_Paper/first_np_paper.tex
Updated the zoom of the two cross-section result figures

@@
 Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.765$^{+0.015}_{-0.022}$ MeV neutrons is reported as   46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.262 $\pm$  0.822 mb.
+The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.765$^{+0.015}_{-0.022}$ MeV neutrons is reported as    49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) or 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.262 $\pm$  0.822 mb.
 The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{l|ccccc}
+% \begin{tabular}{l|ccccc}
+\begin{tabular}{lccccc}
 \toprule
@@
 Reaction                                                                            & $\sigma$($E_n$ = 2.765$^{+0.015}_{-0.022}$ MeV) (mb)                                                                       \\ \midrule
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \\[0.1ex]
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\  \\[0.1ex]
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\  \\[0.1ex]
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \\[0.1ex]
 \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.904 $\pm$ 1.193, \\ 26.751 $\pm$ 1.394*\end{tabular}                   \\ \bottomrule
@@
 Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of the measurements give   46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In}) and  49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In})    for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.262 $\pm$  0.822 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The weighted average of the measurements give   49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) and 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.262 $\pm$  0.822 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith (1975), Armitage (1967), and Ikeda (1990) groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from Hussain (1983), Gonzalez (1962), and Shimizu (2004) \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
+However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith (1975), Armitage (1967), and Ikeda (1990) groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from the Hussain (1983), Gonzalez (1962), and Shimizu (2004) groups \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
 
@@
 The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.262 $\pm$  0.822 mb and  46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
+The measured values of  26.262 $\pm$  0.822 mb and  49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) or 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
 

### 2017-04-21 First_np_Paper/first_np_paper.tex
Merged in Shamsu's 2nd round edits

@@
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.765$^{+0.015}_{-0.022}$ MeV neutrons is reported as    49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) or 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.262 $\pm$  0.822 mb.
-The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
+The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
 This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.
@@
  Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
+DT generators may also often be limited by the restricted use of tritium at many institutions.
 
@@
 Current methodology in radiochemistry has shown recovery of upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
-By expanding the base of efficient reaction pathways, great advances can be made in making production of medical radionuclides more efficient and affordable for those in need.
+By expanding the base of efficient reaction pathways, great advances are possible in making production of medical radionuclides more efficient and affordable for those in need.
+It is this desire to improve the options available for modern medical imaging and cancer therapy which has motivated the campaign of nuclear data measurements for isotope production at the UC Berkeley HFNG.
 
@@
 The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012,zsolnay2012technical}.
-  \autoref{tab:foil_specs} records physical characteristics of each foil for the various irradiations.
+  \autoref{tab:foil_specs} lists physical characteristics of each foil for the various irradiations.
 In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
@@
 
+\multirow{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirow{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirow{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirow{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
+
+ &  & & & 1.03 \pm 0.01 & 9.76 \pm 0.17 & 0.521 \pm 0.005 \\
+
+  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
+
+\multirow{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirow{2}*{\minitab[c]{99.999\%   }} & \multirow{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirow{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
+
+  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\  \hline
+
 \multirow{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirow{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirow{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirow{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
@@
 
-    &  & & & 0.50 \pm 0.02$^\dagger$ & 10.00 \pm 0.09$^\dagger$  & 0.248 \pm 0.005$^\dagger$ \\ \hline
-
-\multirow{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirow{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirow{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirow{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
-
- &  & & & 1.03 \pm 0.01 & 9.76 \pm 0.17 & 0.521 \pm 0.005 \\
-
-  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
-
-\multirow{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirow{2}*{\minitab[c]{99.999\%   }} & \multirow{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirow{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
-
-  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\   \bottomrule
+    &  & & & 0.50 \pm 0.02$^\dagger$ & 10.00 \pm 0.09$^\dagger$  & 0.248 \pm 0.005$^\dagger$ \\ \bottomrule
+
 \end{tabular}%
@@
  % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
- \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons.}
+ \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons \cite{Liskien_Paulsen_1973}.}
  \label{fig:scatt_angle}
@@
 % the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
-angular range in a region of impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
+angular range in a region of  high  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
 This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
@@
 Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
-For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is given by:
+For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:
 
 \begin{equation}
-R = N_i \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
+R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
 \end{equation}
@@
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]. The red arrows indicate the energy region that corresponds to 67\% of the total activation.}
+ \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$].
+The solid red boundaries indicate the energy region that corresponds to 68.2\% of the total activation.}
  \label{fig:frac_plot}
@@
 
-The spectra for the different samples were summed and the net peak areas were fitted using gf3, part of the RadWare analysis package from Oak Ridge National Laboratory   \cite{radford2000radware, Radford1995}.
+The spectra for each sample were summed and the net peak areas were fitted using gf3, part of the RadWare analysis package from Oak Ridge National Laboratory   \cite{radford2000radware, Radford1995}.
 The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
@@
 Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ 
-Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ 
-Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ 
-Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ 
-End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ 
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 860 $\pm$ 40    & 2545 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 24464 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
+Target Foil Mass (g)               & 0.538         & 0.521       & 0.542 & 0.337     & 0.337   \\ 
+Irradiation Time, $t_i$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ 
+Delay Time, $t_d$ (s)             & 1785         & 16185       & 2290 & 89408    & 2390   \\ 
+Counting Time, $t_c$ (s)               & 91188        & 54008       & 54002 & 86424    & 93631   \\ 
+Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 76321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
+Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 890 $\pm$ 40    & 3505 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
+Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 27164 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
 Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257 \\ \bottomrule
@@
 
-If this irradiation lasts for  some time $t_1$, and gamma ray spectrum acquisition begins at a later time $t_2$ and ends at  $t_3$, then the number of product decays ($D$; with decay constant $\lambda$) during the acquisition will be:
-
-\begin{equation}
-\begin{aligned}
-D &= \dfrac{R}{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}}
+If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
+
+\begin{align}
+N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
 \\
-&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}} 
-\end{aligned}
-\end{equation}
-
-If this decay emits a gamma ray with absolute intensity $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed decays between $t_2$ and $t_3$ will be:
+&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
+\end{align}
+
+% \begin{equation}
+% \begin{aligned}
+% N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
+% \\
+% &= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} 
+% \end{aligned}
+% \end{equation}
+
+If this decay emits a gamma ray with absolute intensity $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed gamma rays during the acquisition will be:
 
@@
 \begin{align}
-N_{obs} &= D \epsilon_\gamma I_\gamma \\
-&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}} \nonumber
+N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
+&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
 \end{align}
@@
 
-\begin{equation}\label{eqn:single_xs_eqn}
-\sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_3} - e^{-\lambda t_2}}}
-\end{equation}
+\begin{align}\label{eqn:single_xs_eqn}
+\sigma\pp{\bar{E}} = \dfrac{N_{\gamma}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
+\end{align}
+
+% \begin{equation}\label{eqn:single_xs_eqn}
+% \sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
+% \end{equation}
 
@@
 \begin{align}\label{eqn:calc_eqn}
-\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{A_P}{A_{In}} \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \dfrac{e^{\lambda_{In}t_1}-1}{e^{\lambda_{P}t_1}-1} \times \\
-&\times \dfrac{e^{-\lambda_{In}t_3}-e^{-\lambda_{In}t_2}}{e^{-\lambda_{P}t_3} - e^{-\lambda_{P}t_2}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
+\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{N_{\gamma,P}}{N_{\gamma,In}}  \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \pp{\dfrac{1 - e^{-\lambda_{In}t_i}}{1 - e^{-\lambda_{P}t_i}}} \dfrac{e^{-\lambda_{In}t_d}}{ e^{-\lambda_{P}t_d}} \times \\
+&\times \pp{\dfrac{1 - e^{-\lambda_{In}t_c}}{1 - e^{-\lambda_{P}t_c}}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
 \end{align}
@@
 
-\item $A$ is the integrated counts under a photopeak [counts],
+% \item $N_{\gamma}$ is the integrated counts under a photopeak [counts],
+\item $N_{\gamma}$ is the integrated counts under a photopeak,
 
@@
 
-\item $t_1$ is the irradiation time [s],
-
-\item $t_2$ is the time between the start-of-beam and the start of counting [s],
-
-\item $t_3$ is the time  between the start-of-beam and the end of counting [s],
+\item $t_i$ is the irradiation time [s],
+
+\item $t_d$ is the delay time (between the end-of-beam and the start of counting) [s],
+
+\item $t_c$ is the counting time   [s],
 
@@
 
-This total  uncertainty will be plotted as the cross section error bar in the excitation function for these production reactions.
+This total  uncertainty is plotted as the cross section uncertainty in \autoref{fig:sc_xs} and \autoref{fig:cu_xs_zoom}.
 
@@
 
-\comment{Karl:  \enquote{For the figures, let me suggest you make a red solid rectangle whose dimensions represent the error bars in both energy and cross section.
+% \comment{Karl:  \enquote{For the figures, let me suggest you make a red solid rectangle whose dimensions represent the error bars in both energy and cross section.
 Then put a large red circle around it, whose diameter is of order 10\% of the size of the whole graph, to focus the eyes.
@@
 \begin{equation}
-A = \lambda N_{product} = \eta \phi \sigma N_{target}
+A = \lambda N_{product} = \eta \phi \sigma N_{T}
 \end{equation}

### 2017-04-24 First_np_Paper/first_np_paper.tex
Final version, submitted for pre-publication review

@@
 Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.765$^{+0.015}_{-0.022}$ MeV neutrons is reported as    49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) or 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.262 $\pm$  0.822 mb.
+The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26 $\pm$  0.82 mb.
 The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
@@
 
-\listoftodos
+% \listoftodos
 
@@
 The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
+The neutron spectral distribution is also broadened by the temperature of the target.  
+This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
 This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
@@
  Our approach, in analogy to the Gaussian quantity $\sigma$, will be to use a horizontal \enquote{error bar}  to represent the energy range responsible for 68.2\% of the reactions taking place.
- Using this approach, we report the effective energy bin as being $E_n$=2.765$^{+0.015}_{-0.022}$ MeV.
+ Using this approach, we report the effective energy bin as being $E_n$=2.765$^{+0.014}_{-0.022}$ MeV.
 This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a quasi-monoenergetic neutron flux.
-%$E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.
+%$E_n$ = 2.7645 MeV + 0.0141 MeV / - 0.0219 MeV.
 
@@
 \ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 $\pm$ 0.17    & 99.476 m  \\
-\ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
+\ce{^{115m}In} \cite{Hansen1974} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
 \ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 $\pm$ 0.4      & 54.29 m   \\ \bottomrule
@@
  We believe, based on \enquote{burn marks} on the neutron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
- However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width.
+ However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width, which places a natural limit on the reported effective neutron energy.
 
@@
 
-Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.765$^{+0.015}_{-0.022}$ MeV.
+Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
 These values are recorded in \autoref{tab:xs_results}.
@@
 \toprule
-Reaction                                                                            & $\sigma$($E_n$ = 2.765$^{+0.015}_{-0.022}$ MeV) (mb)                                                                       \\ \midrule
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.926 $\pm$ 3.190, \\ 49.219 $\pm$ 2.709, \\ 49.011 $\pm$ 2.540\end{tabular} \\  \\[0.1ex]
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.958 $\pm$ 2.553, \\ 46.498 $\pm$ 1.745, \\ 46.841 $\pm$ 3.170\end{tabular}  \\ \\[0.1ex]
-\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.904 $\pm$ 1.193, \\ 26.751 $\pm$ 1.394*\end{tabular}                   \\ \bottomrule
+Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
+\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
+\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
 \end{tabular}
@@
 Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of the measurements give   49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) and 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.262 $\pm$  0.822 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The weighted average of the measurements give   49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) and 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26 $\pm$  0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
@@
 
-Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.765$^{+0.015}_{-0.022}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
+Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.76$^{+0.01}_{-0.02}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
 The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.262 $\pm$  0.822 mb and  49.315 $\pm$ 2.567 mb (relative to \ce{^{113}In}) or 46.415 $\pm$ 1.720 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
+The measured values of  26.26 $\pm$  0.82 mb and  49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
 
  In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
- While this is not consistent with the average neutron energy at the target location (2.765$^{+0.015}_{-0.022}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
+ While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
  This in turn highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
@@
 % In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
- It is worth noting that at the time of publication, the  HFNG is now operating at 10$^9$ n/sec, with
+ It is worth noting that at the time of publication, the  HFNG is now operating at close to 10$^9$ n/sec, with
 a clear path towards 10$^{10}$.
@@
 Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, \textcolor{red}{NSF ARRA Grant \# XXXXXXXX}, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-\comment{Add NSF Grant number from P. Renne.}
+Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
+
+% \comment{Add NSF Grant number from P. Renne.}
 

### 2017-04-26 First_np_Paper/cover_letter.tex
Added empty version of cover letter, required for submission.

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Susan R. Bumpershoot}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Ms. Terri Roberts \\
Senior Staff Recruiter \\
XYZ Corporation \\
Rt. 56 \\
Anytown, New Jersey 05867}

\begin{flushleft}
{\large\bf Susan R. Bumpershoot}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 1985 Storm Lane, Troy, NY 12180 \\
\hfill (518) 273-0014 or (518) 272-6666 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Ms. Roberts:}

\noindent PARAGRAPH ONE: State reason for letter, name the position or type 
of work you are applying for and identify source from  which  you 
learned   of   the  opening.  (i.e.  Career  Development  Center, 
newspaper, employment service, personal contact).

\noindent PARAGRAPH  TWO:  Indicate why you are interested in the position, 
the company, its products, services - above all, stress what  you 
can  do  for  the employer. If you are a recent graduate, explain 
how your academic background makes you a qualified candidate  for 
the  position.  If  you have practical work experience, point out 
specific achievements or unique qualifications. Try not to repeat 
the  same  information  the reader will find in the resume. Refer 
the reader to the enclosed resume or application which summarizes 
your  qualifications,  training,  and experiences. The purpose of 
this section is to strengthen your resume  by  providing  details 
which bring your experiences to life.

\noindent PARAGRAPH THREE: Request a personal interview and  indicate  your 
flexibility as to the time and place. Repeat your phone number in 
the letter and offer assistance to help in a speedy response. For 
example,  state that you will be in the city where the company is 
located on a certain date and would like to set up an  interview. 
Or,  state  that  you  will  call  on a certain date to set up an 
interview. End the letter by thanking  the  employer  for  taking 
time to consider your credentials.

\closing{Sincerely yours,}

\encl{}  				% Enclosures

\end{letter}

\end{document}

### 2017-04-26 First_np_Paper/first_np_paper.tex
Added keywords to abstract, for Elsevier submission. Final version.
Final version, with cover letter, as submitted for publication review.

@@
 
-% \begin{keyword}
+\begin{keyword}
 %% keywords here, in the form: keyword \sep keyword
+DD neutron generator \sep Medical Isotope Production \sep Scandium (Sc) and Copper (Cu) radioisotopes \sep Indium \sep Ratio activation \sep Theranostics
 
@@
 
-% \end{keyword}
+\end{keyword}
 
@@
 
-With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries am uncertainty.
+With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries an uncertainty.
 Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
@@
 % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{Results of cross section measurement.
+Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
+% \label{tab:xs_results}
+% \begin{tabular}{@{}cc@{}}
+% \toprule
+% Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
+% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
+% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
+% \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
+% \end{tabular}
+% \end{table}
 \begin{table}
@@
 \label{tab:xs_results}
-\begin{tabular}{@{}cc@{}}
+\begin{tabular}{@{}cS[table-format=+2.1,
+                  table-figures-uncertainty=1]@{}}
 \toprule
-Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
-\begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
-\begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
+Reaction                   & \multirow{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
+\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
+											& 49.2 \pm 2.7 \\ 
+											& 49.0 \pm 2.5 \\  \\[0.1ex]  
+\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
+											& 46.5 \pm 1.7 \\ 
+											& 46.8 \pm 3.2  \\ \\[0.1ex]    
+\multirow{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
+											& 26.7 \pm 1.4*                   \\ \bottomrule
 \end{tabular}

### 2017-06-06 First_np_Paper/arXiv/first_np_paper.tex
Added extra files for preparation of arXiv draft of paper

--- 2017-04-26 First_np_Paper/first_np_paper.tex
@@
 %% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-\documentclass[5p]{elsarticle}
+\documentclass[5p]{elsarticles}
 % \documentclass[3p,times]{elsarticle}
@@
 % \usepackage{cancel}
-\usepackage{microtype}
-\usepackage{listings}
-\usepackage{mcode}
-\usepackage [autostyle, english = american]{csquotes}
-\usepackage{longtable}
+% \usepackage{microtype}
+% \usepackage{listings}
+% \usepackage{mcode}
+\usepackage{csquotess}
+% \usepackage{longtable}
 \usepackage{subcaption}
@@
 \usepackage[section]{placeins}
-\usepackage{multirow}
-
-\lstset{basicstyle=\small\ttfamily,columns=fullflexible}
+\usepackage{multirows}
+
+% \lstset{basicstyle=\small\ttfamily,columns=fullflexible}
 
@@
 
-\lstset{ %
-  backgroundcolor=\color{white},   % choose the background color
-  basicstyle=\footnotesize,        % size of fonts used for the code
-  breaklines=true,                 % automatic line breaking only at whitespace
-  captionpos=b,                    % sets the caption-position to bottom
-  commentstyle=\color{mygreen},    % comment style
-  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-  keywordstyle=\color{blue},       % keyword style
-  stringstyle=\color{mymauve},     % string literal style
-}
+% \lstset{ %
+%   backgroundcolor=\color{white},   % choose the background color
+%   basicstyle=\footnotesize,        % size of fonts used for the code
+%   breaklines=true,                 % automatic line breaking only at whitespace
+%   captionpos=b,                    % sets the caption-position to bottom
+%   commentstyle=\color{mygreen},    % comment style
+%   escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
+%   keywordstyle=\color{blue},       % keyword style
+%   stringstyle=\color{mymauve},     % string literal style
+% }
 
@@
 %  \centering
-% %  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
-%  \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
+% %  \includegraphics[width=\columnwidth]{IMG_20160531_183154957_HDR.jpg}
+%  \includegraphics[scale=0.06]{IMG_20160531_183154957_HDR.jpg}
 %  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=3in]{./figures/Capture.PNG}
+% %         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[height=3in]{Capture.PNG}
 %         \caption{The UC Berkeley High-Flux Neutron Generator,}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/target2.png}
+% %         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[height=2in]{target2.png}
 %         \caption{Cutaway of the target chamber.}
@@
         \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/target2.png}
-        \includegraphics[height=2in]{./figures/cutaway.png}
+%         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[height=2in]{target2.png}
+        \includegraphics[height=2in]{cutaway.png}
         \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
@@
     \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2.5in]{./figures/holder.pdf}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+        \includegraphics[height=2.5in]{holder.pdf}
         \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=2in]{./figures/foils.png}
+% %         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[height=2in]{foils.png}
 %         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/holder.pdf}
+% %         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[height=2in]{holder.pdf}
 %         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
+% %         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[height=2in]{IMG_20151103_113432563.jpg}
 %         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
@@
 
-\multirow{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirow{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirow{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirow{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
+\multirows{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirows{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirows{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirows{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
 
@@
 
-\multirow{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirow{2}*{\minitab[c]{99.999\%   }} & \multirow{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirow{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
+\multirows{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirows{2}*{\minitab[c]{99.999\%   }} & \multirows{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirows{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
 
@@
 
-\multirow{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirow{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirow{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirow{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
+\multirows{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirows{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirows{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirows{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
 
@@
  \centering
- \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
+ \includegraphics[scale=0.6]{scatt_angle.pdf}
  % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
@@
 %  %trim option's parameter order: left bottom right top
-%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
+%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{mcnp_vised2.png}
 %  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
@@
 %  \centering
-%  \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
+%  \includegraphics[scale=0.6]{mcnp_flux.pdf}
 %  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
@@
  \centering
- \includegraphics[scale=0.6]{./figures/mcnp_flux_new.pdf}
+ \includegraphics[scale=0.6]{mcnp_flux_new.pdf}
  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
@@
 %  \centering
-%  \includegraphics[scale=0.6]{./figures/fracplot.pdf}
+%  \includegraphics[scale=0.6]{fracplot.pdf}
 %  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
  \centering
- \includegraphics[scale=0.6]{./figures/fracplot_new.pdf}
+ \includegraphics[scale=0.6]{fracplot_new.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
+% %         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[height=2.8in]{IMG_20160531_182618557_HDR.jpg}
 %         \caption{ Ortec 80\% HPGe detector}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
+% %         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[height=2.8in]{IMG_20160531_182635712_HDR.jpg}
 %         \caption{Ortec planar LEPS detector}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[width=5in]{./figures/ti_foils.png}
-        \subfigimg[width=5in]{a)}{./figures/47sc_gspectrum_alt.pdf}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[width=5in]{ti_foils.png}
+        \subfigimg[width=5in]{a)}{47sc_gspectrum_alt.pdf}
 %         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
@@
         \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
-        \subfigimg[width=5in]{b)}{./figures/64Cu_gspectrum_alt.pdf}
+%         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[width=5in]{Sample_spectra.png}
+        \subfigimg[width=5in]{b)}{64Cu_gspectrum_alt.pdf}
 %         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{a)}{./figures/336keV_curve_new.pdf}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+        \subfigimg[scale=0.6]{a)}{336keV_curve_new.pdf}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.6]{b)}{./figures/391keV_curve_new.pdf}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[scale=0.6]{391keV_curve2.png}
+        \subfigimg[scale=0.6]{b)}{391keV_curve_new.pdf}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
         \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.6]{c)}{./figures/417keV_curve_new.pdf}
+%         \includegraphics[width=\textwidth]{target2.png}
+        \subfigimg[scale=0.6]{c)}{417keV_curve_new.pdf}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{d)}{./figures/511keV_curve_new.pdf}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+        \subfigimg[scale=0.6]{d)}{511keV_curve_new.pdf}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil                     & \multirow{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
+% Reference Foil                     & \multirows{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
 % Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
@@
  \centering
- \includegraphics[scale=0.55]{./figures/fig1_cropped.pdf}
+ \includegraphics[scale=0.55]{fig1_cropped.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 \toprule
-Reaction                   & \multirow{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
-\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
+Reaction                   & \multirows{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
+\multirows{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
 											& 49.2 \pm 2.7 \\ 
 											& 49.0 \pm 2.5 \\  \\[0.1ex]  
-\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
+\multirows{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
 											& 46.5 \pm 1.7 \\ 
 											& 46.8 \pm 3.2  \\ \\[0.1ex]    
-\multirow{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
+\multirows{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
 											& 26.7 \pm 1.4*                   \\ \bottomrule
@@
  \centering
- \includegraphics[scale=0.65]{./figures/47sc_fixed_1point.pdf}
+ \includegraphics[scale=0.65]{47sc_fixed_1point.pdf}
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
 %  \centering
-%  \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
+%  \includegraphics[scale=0.6]{64cu_fixed.pdf}
 %  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
  \centering
- \includegraphics[scale=0.65]{./figures/64cu_fixed_1point.pdf}
+ \includegraphics[scale=0.65]{64cu_fixed_1point.pdf}
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294

### 2017-07-03 First_np_Paper/Response_to_Reviewers.tex
Created the editorial-requested Response to Reviewers

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage[ampersand]{easylist}

% \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
\newcommand{\colornote}[1]{\textcolor{red}{#1}}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Mark Breese, PhD \\
Editor \\
Nuclear Instruments and Methods in Physics Research Section B: \\
Beam Interactions with Materials and Atoms}

\begin{flushleft}
{\large\bf Andrew S. Voyles}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill The University of California, Berkeley \\
\hfill 1106B Etcheverry Hall, Berkeley, CA  94720-1730 \\
\hfill (850) 281-0217 or (510) 486-7310 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Mark,}

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.  Please find my responses detailed in \colornote{red text.}

  \vfill

 \pagebreak

 Reviewer \#1:

describes the activation measurement of 64Zn(n,p)64Cu and 47Ti(n,p)47Sc with DD neutrons from the High-Flux Neutron Generator of University of California in Berkeley relative to indium (n,n') activation foils.
The produced radioactive isotopes 64Cu, 47Sc are relevant for nuclear medicine.
64Cu is a positron emitter, while 47Sc decays by beta-minus emission.
The use of DD neutrons has the advantage that at this energy no other radioactive copper or scandium isotopes are produced.

It features a very compact double sided titanium-copper target on which high intensity deuteron beams with 100 kV impinge from nearby ion sources from opposite sides.

In the experiment a deuteron current of 1.3 mA created a flux of 1.3E7 neutrons /cm2 /s on the target. Inside the target small activation samples can be mounted only 8 mm away from the neutron producing target surface. The target foils consisted of thin metallic zinc and titanium foils in
addition to indium foils to provide a reference for a relative measurement of the activation reactions by gamma-ray spectroscopy.

The neutron spectrum produced in the target is simulated with MCNP6 and an effective energy range for neutron activation of indium is determined.
The incident neutron energy also depends on the position of the deuteron beam spot on the target. A square array of nine indium foils  with smaller diameter is used to measure the neutron beam intensity. The beam seems mostly centered on the target;an asymmetry of the neutron beam intensity in the horizontal direction is illustrated in Fig. 8.

The induced activity of the irradiated zinc, titanium and indium samples is measured using HPGe detectors calibrated with several gamma-ray calibration sources. The half-live of the different indium and 64Cu activities are measured for a verification of the identification of the gamma-ray peaks.
The measured activity of the irradiated samples is used to determine the  cross section of 64Zn(n,p)64Cu and 47Ti(n,p)47Sc relative to 115In(n,n'). Statistical uncertainties due to the counting statistics are about 4 \%. The main systematic uncertainty is due to the uncertainty of the normalizing indium cross sections. Additional systematic uncertainties are the position
and size of the deuteron beam relative to the target irradiation samples as this induces a shift in the neutron energy spectrum of the activation. Additional uncertainties like the relative gamma-ray detection efficiency are not listed. The 115In neutron capture cross section was determined to
an effective energy of 2.45 MeV which indicates that there might be some contribution of lower energy neutrons contributing to the activation yield.

As several target positions can be irradiated simultaneously a group of activation cross sections from 2.6 to 2.7 MeV can be measured. The saturation activity that can be reached is proportional to activation cross section, the number of irradiated target atoms and the neutron flux per cm2 and second. This activity should be in the mCi range to be useful for
medical use. The quantity eta (eq.10) is added to the known formula for the activation by neutron irradiation as a dimensionless neutron utilisation factor.

The paper describes an activation cross section measurement with a
novel quasimonoenergetic neutron source using deuteron beams from two sides on a compact target assembly. It is well structured and nicely written and contains most aspects of the measurement. The neutron intensity of this source (at the future 1.E10 level might have the potential
to be useful for medical radioisotope production, although this point should be more clearly made in the discussion section.

The paper ist suitable for publication in NIM B after the following items have been addressed, which should be a minor revision. The corrections relate mainly to the fact, statements are made, but not quantified with numbers that should be easily available from the data analysis.

\begin{easylist}[enumerate]
\ListProperties(Style2*=$\bullet~$,Numbers1=a,Hide2=100,FinalMark={)})
& The "neutron utilisation factor" eta is not clearly explained.
Usually "likelihood of a neutron inducing the desired reaction on one of the target sample atoms" is simply the cross section:  N$_{reac}$/ N$_{neutron}$ = sigma(Cm2) * n$_{target}$( atoms/cm2) To determine the saturation activity from an activation with a constant neutron flux this factor is not required.
The discussion section does not include the value of the saturation activity of the reported measurement, e.g. for 64Cu it should be ca. 1.5 kBq (using 1.3E7 n/(s cm2), 50 mbarn cross section and 0.5 g of nat-Zn). With some intensity improvements (factor 100-1000) which seems realistic, the mCi (37 MBq) range can be reached. This is however not stated in the
paper. The discussion of eq.(9) and (10) should be improved, and quantitative results related to the current measurement should be reported. Maybe eq.(10) is not required.:
&& \colornote{Response}
& In an activation measurement the integral of the neutron spectrum and cross section determines the yield, see. eq.(1).
The thresholds for (n,p) on Cu or Ti and (n,n') on indium are not the same. Fig. 5 shows the effective energy range for indium only. Is there systematic effect on the measured (n,p) cross sections due to the low energy tail of the neutron spectrum shown in Fig. 4 ?
The interpretation of the 115In capture cross section effective energy is not clear. Can there be an estimate made on how many thermal neutrons are in the spectrum ?
What is the meaning of the data symbols in Fig. 4  and why does the spectrum stop at the
highest flux (around 4 units) should it not drop to zero yield above the 2.75 MeV peak ?
&& \colornote{Response}
& The HPGe and LEPS detectors were calibrated at various distances with calibration sources.
How well is the relative efficiency known for the gamma-rays used in the measurement ?
This could add to the systematic uncertainty. Especially 133Ba and 152Eu as multi-line sources might require a correction for coincident summing if the distance to the sample was small.
&& \colornote{Response}
& In the description of the experiment it is never explicitely stated that deuteron beams were impinging from both sides on the target or not. Fig.1 seems to indicate that there are two deuteron ion sources, although Fig. 2 shows neutrons only coming from one side.
The authors should clarify the mode of operation.
&& \colornote{Response}
\end{easylist}

Typos:

\begin{easylist}[enumerate]
\ListProperties(Style2*=$\bullet~$,Numbers1=a,Hide2=100,FinalMark={)})
& p.1 line 45 right column "their energy spectra are often not well-suited"
&& \colornote{Response}
& p.2 line 27 left: 47Sc is not a positron emitter
&& \colornote{Response}
& p.10. line 31 Ref.[1] is incomplete.
&& \colornote{Response}
\end{easylist}

 \pagebreak

Reviewer \#2:

 This article describes the use of a modern, compact D-D neutron source to produce radioisotopes for medical and other applications. The radioisotopes 47Sc and 64Cu were chosen because they have potential for diagnostic or therapeutic medical applications, and can be produced using the (n,p) reaction that is an open reaction channel at the energy of the neutron source. The radioisotope production cross sections were measured relative to indium inelastic activation cross sections that are well determined. The authors performed a thorough and detailed analysis of the energy and angle dependence of the neutron flux, as well as properly accounting for the production and decay of the radioisotopes in determining the reaction cross sections. The resulting cross section values agree within uncertainties with some previous measurements and have smaller uncertainties than previous work. The results show the potential of using such a compact D-D neutron source for both medical
radioisotope production and nuclear research. Because the work is of interest to the NIM B audience, is thorough and well-presented, it should be published. There are however, some minor corrections to the text that are necessary, as well as some changes to the references that are needed before publication. These corrections are listed below.

\begin{easylist}[enumerate]
\ListProperties(Style2*=$\bullet~$,Numbers1=a,Hide2=100,FinalMark={)})
& P 1 "energy spectra is…" should be "energy spectra are…"

&& \colornote{Response}
& P 2 "100 kV deuterium beam" correct "kV" to "keV"

&& \colornote{Response}
& P 4 Table 1. My preference is for "at. %" rather than "a/o"

&& \colornote{Response}
& P 5 missing "to" in "subjected to this flux" and Fig. 8 - the authors should comment on the significance of the flux at right (8.35 E6) that is nearly the same as the center value.

&& \colornote{Response}
& P 8 "makes indium a better" correct to "make indium …"; "for incident" should be "for an incident"; and "The results for the production of 116In …" should be "The result…".

&& \colornote{Response}
\end{easylist}

References -

\begin{easylist}[enumerate]
\ListProperties(Style2*=$\bullet~$,Numbers1=a,Hide2=100,FinalMark={)})
& [1] - this reference needs details of the source - report, book or article and particulars

&& \colornote{Response}
& [2] - page and year of journal article are needed

&& \colornote{Response}
& [3] - a URL for access to the dissertation would benefit the reader
Along with references 2 and 3, adding Q. Ji, A. Sy, and J. W. Kwan, Rev. Sci. Instr. 81, 02B312 (2010) is needed for completeness.

&& \colornote{Response}
& [13] - page and year are needed

&& \colornote{Response}
& [25] Add "Los Alamos Report" LA-UR-13-22934

&& \colornote{Response}
& [30] Add URL - http://radware.phy.ornl.gov/gf3/gf3.html

&& \colornote{Response}
\end{easylist}

 \pagebreak

Reviewer \#3:

Excellent contribution to the field of medical radioisotope production.
I believe there is one significant omission from the discussion.
What do the authors believe will be the attainable saturation activity for the two nuclides considered?

The principle of the estimate is indicated. The numbers are missing. These numbers should be compared with foreseen need.

\begin{easylist}[enumerate]
\ListProperties(Style2*=$\bullet~$,Numbers1=a,Hide=2,FinalMark={)})
&

&& \colornote{Response}
\end{easylist}

\pagebreak

Please find our revised manuscript attached.

\closing{Sincerely yours,}

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2017-07-07 First_np_Paper/Response_to_Reviewers.tex
Added my edits, based on reviewer comments.  Sending to co-authors for feedback.

@@
 \usepackage[ampersand]{easylist}
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage{caption}
+\usepackage{amsmath}
+
+\newfloat{figure}{htbp}{figs}
 
@@
 \newcommand{\colornote}[1]{\textcolor{red}{#1}}
+\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
+\newcommand{\pp}[1]{\left( #1\right)}
 
@@
 & The "neutron utilisation factor" eta is not clearly explained.
-Usually "likelihood of a neutron inducing the desired reaction on one of the target sample atoms" is simply the cross section:  N$_{reac}$/ N$_{neutron}$ = sigma(Cm2) * n$_{target}$( atoms/cm2) To determine the saturation activity from an activation with a constant neutron flux this factor is not required.
+Usually "likelihood of a neutron inducing the desired reaction on one of the target sample atoms" is simply the cross section:  N$_{reac}$/ N$_{neutron}$ = sigma(Cm2) * n$_{target}$( atoms/cm2) To determine the saturation activity from an activation with a constant neutron flux this factor is not required.\\
 The discussion section does not include the value of the saturation activity of the reported measurement, e.g.
@@
 This is however not stated in the
-paper. The discussion of eq.(9) and (10) should be improved, and quantitative results related to the current measurement should be reported. Maybe eq.(10) is not required.:
-&& \colornote{Response}
+paper. \\ The discussion of eq.(9) and (10) should be improved, and quantitative results related to the current measurement should be reported. Maybe eq.(10) is not required.:
+&& \colornote{The point of introducing the $\eta$-factor is to qualitatively show the characteristics of compact DD generators which make them attractive for \emph{high specific-activity} isotope production.\\
+The $\int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}}$ term in $\eta$ shows the fraction (integrated over the neutron energy range seen by a target) of the total reaction cross section which produces the desired reaction channel.
+For example, if no other competing contamination reaction channels are energetically possible on [0,E], then the term would go to unity.
+As other competing contamination channels open up ((n,$\gamma$), (n,pn), (n,$\alpha$), etc), the term would drop towards 0, as more of the total reactions are stolen away from the desired channel.
+The $\int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}$ term shows the fraction of target subtended by the neutron flux.
+For externally mounted targets, or DD generators using collimated beamlines, the target subtends a much smaller fraction of the flux, essentially wasting that component of the flux.
+The proximity of targets to the DD reaction surface and the high specific activity of isotope production in a design similar to the HFNG give it a value of $\eta$ much closer to unity than other conventional DD generators.
+\\ Calculations for the theoretical saturation activities, as well as observed estimates of $\eta$ have now been added to the discussion in section 4 (see the first paragraph of P.
+10).}
 & In an activation measurement the integral of the neutron spectrum and cross section determines the yield, see. eq.(1).
@@
 Fig.
-5 shows the effective energy range for indium only.
-Is there systematic effect on the measured (n,p) cross sections due to the low energy tail of the neutron spectrum shown in Fig.
-4 ?
-The interpretation of the 115In capture cross section effective energy is not clear. Can there be an estimate made on how many thermal neutrons are in the spectrum ?
+5 shows the effective energy range for indium only.\\ Is there systematic effect on the measured (n,p) cross sections due to the low energy tail of the neutron spectrum shown in Fig.
+4 ?\\
+The interpretation of the 115In capture cross section effective energy is not clear. \\ Can there be an estimate made on how many thermal neutrons are in the spectrum ?\\
 What is the meaning of the data symbols in Fig. 4  and why does the spectrum stop at the
 highest flux (around 4 units) should it not drop to zero yield above the 2.75 MeV peak ?
-&& \colornote{Response}
+&& \colornote{In performing the cross-section measurement for (n,p) on Zn or Ti, the use of indium as a monitor serves two purposes: measuring the integral neutron flux seen by the Zn/Ti targets (though in ratio, this integral flux cancels out, which eliminates the flux as the typical largest source of systematic uncertainty), and verification of the neutron energy distribution.
+This is why Fig.
+5 only shows the energy range in indium - a similar curve for 64Zn(n,p)64Cu would have a different threshold, but would also require a well-characterized excitation function.
+Such an excitation function does not exist, which this work seeks to help remedy (at one energy).
+As a result, MCNP is used to determine the energy distribution in the Zn/Ti targets (Fig.
+4), and Fig 5.
+is used to provide appropriate ``error bars'' to report the effective energy width seen by our target foils.
+\\ The low-energy tail in Figure 5 is not well-visible, due to Figure 5 being zoomed-in to illustrate how rapidly the $F(E')$ quantity rises over the 2.7-2.8 MeV range.
+The zoomed-out version of this is seen below in  \autoref{fig:cu_xs_zoom}, which illustrates almost negligible contribution to the total activation until above 2.5 MeV neutrons.
+As an example, the entire low-energy tail from 0-2 MeV neutron only contributes 2.17\% of the total activity in Indium, and the epithermal range (0-10 keV) contributes only $\sci{1.3}{-8}$ of the total activity.\\ The 115In capture note is more of an observation than a reportable.
+The cross sections we have measured are for the effective neutron energy of 2.76 MeV.
+At this energy, the 116In activity produced would predict a 64Zn(n,p)64Cu cross section, for example, of approx 41 mb, which is approx 20\% lower than the cross sections relative to the 113mIn and 115mIn standards.
+This is because the 116In capture activity is far more sensitive to lower-energy neutron contributions than the 113mIn/115mIn inelastic scattering activities.
+As a simple exercise, one can very the effective neutron energy for the 116In capture channel until the 64Zn(n,p)64Cu cross section observed (relative to the 116In ``monitor channel'') agrees with the 113mIn/115mIn monitor channels.
+This occurs if one assumes an effective neutron energy of 2.45 MeV for 115In(n,gamma)116In.
+The point we were making in describing this observation is that it offers further proof that there are very few thermal neutrons seen by the target positions in the HFNG - otherwise, the effective neutron energy would have shifted far lower in energy than from 2.76 MeV to just 2.45 MeV.
+This low population of thermals, in turn, confirms that DD neutrons are a potentially effective method to produce radionuclides with high specific activity (very little unwanted competing nuclides produced) - the low energy of DD neutrons energetically prevents (n,pn) channels from being open for production, and the apparent tiny population of thermal/epithermal neutrons makes (n,gamma) contamination minimal, relative to the desired (n,p) channel.
+\\The thermal neutron population (0-0.0253 eV) makes up 0.00320\% of the total neutron population in the indium foils.
+Even considering epithermal neutrons (0-10 keV), they still only make up 0.0771\% of the total neutron population.
+The semilog axes of Fig.
+4 exaggerate the relative population of thermal / epithermal neutrons.\\ Since the indium/target spectra are so very similar to each other in Fig.
+4 (and the void/non-void spectra as well, above approx 2.6 MeV), the markers were added to differentiate the spectra if the manuscript were being viewed in greyscale / by a colorblind individual.
+Without distinct  markers, the various spectra are nearly indistinguishable, due to the proximity of both target and indium foils to the DD reaction surface.
+\\ The peak flux occurs at 2.777 MeV - the 2.75 MeV number quoted on P.
+3 was a typo and has been corrected.
+However, the energy of the peak flux is expected to be higher than the flux-weighted average of 2.765 MeV, as the low-energy contributions shift the flux-weighted average down in energy.
+However, the tiny shift below the peak is further evidence of how few thermal / low-energy neutrons are present.
+As for the zero yield, yes, the flux does begin turning down above the peak, and the highest-energy neutron observed is at 2.783 MeV, as noted on P.
+3 of the manuscript.
+Above 2.783 MeV, no neutrons are observed.
+However, in plotting on log axes, a value in $y$ of 0 cannot be plotted, as ln(0) is undefined.
+This is why the curve appears to stop instead of immediately dropping to zero, and the drop to zero yield may be seen in a linear y-axis version of Fig.
+4, seen in \autoref{fig:lin_xs_zoom} below.
+This nuances and detailed information about the spectral shape (in particular the rapid rise above the 2.25 MeV shoulder) of the log-y version are masked in this lin-y version, which is why the former was chosen to be included in the manuscript.}
 & The HPGe and LEPS detectors were calibrated at various distances with calibration sources.
@@
 This could add to the systematic uncertainty. Especially 133Ba and 152Eu as multi-line sources might require a correction for coincident summing if the distance to the sample was small.
-&& \colornote{Response}
+&& \colornote{Samples were counted far enough away to avoid any large coincident summing effects, and regardless, and ``no summing corrections needed to be made for the irradiated targets since all of the gammas are either non-coincident or formed in a back-to-back annihilation event'' (See P.
+5, Line 1).
+As for calibration, the relative efficiency of detectors is known to the 1-1.5\% level.
+This efficiency uncertainty is included in the total uncertainty in section 2.6 (``With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries an uncertainty.''  (P.
+8, lines 8-11))}
 & In the description of the experiment it is never explicitely stated that deuteron beams were impinging from both sides on the target or not.
@@
 The authors should clarify the mode of operation.
-&& \colornote{Response}
+&& \colornote{Two deuterium ion sources exist (to effectively double the neutron flux seen by an irradiation target), but only a single source was operated during this work.
+This has been clarified on page 1, end of section 2.1 (``While the machine's design\ldots'').}
 \end{easylist}
+
+\begin{figure}
+ \centering
+ \includegraphics[scale=0.65]{./figures/zoomed_out_fracplot.pdf}
+ % zoomed_out_fracplot.pdf: 366x294 pixel, 72dpi, 12.91x10.37 cm, bb=0 0 366 294
+ \caption{Zoomed-out version of Figure 5 from the manuscript.}
+ \label{fig:cu_xs_zoom}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[scale=0.65]{./figures/lin_mcnp_flux.pdf}
+ % zoomed_out_fracplot.pdf: 366x294 pixel, 72dpi, 12.91x10.37 cm, bb=0 0 366 294
+ \caption{Linear y-axis version of Figure 4 from the manuscript.}
+ \label{fig:lin_xs_zoom}
+\end{figure}
 
@@
 & p.1 line 45 right column "their energy spectra are often not well-suited"
-&& \colornote{Response}
+&& \colornote{Typo corrected.}
 & p.2 line 27 left: 47Sc is not a positron emitter
-&& \colornote{Response}
+&& \colornote{Roles of each radionuclide have been clarified.}
 & p.10. line 31 Ref.[1] is incomplete.
-&& \colornote{Response}
+&& \colornote{Reference updated.  See the Reviewer \#2 section for more detail.}
 \end{easylist}
@@
 
-&& \colornote{Response}
+&& \colornote{Typo corrected.}
 & P 2 "100 kV deuterium beam" correct "kV" to "keV"
 
-&& \colornote{Response}
-& P 4 Table 1. My preference is for "at. %" rather than "a/o"
+&& \colornote{Typo corrected.}
+& P 4 Table 1. My preference is for "at. \%" rather than "a/o"
 
-&& \colornote{Response}
+&& \colornote{Change implemented.}
 & P 5 missing "to" in "subjected to this flux" and Fig. 8 - the authors should comment on the significance of the flux at right (8.35 E6) that is nearly the same as the center value.
 
-&& \colornote{Response}
+&& \colornote{Change implemented.  In addition, more discussion of the small horizontal asymmetry in neutron flux is provided in the same paragraph.}
 & P 8 "makes indium a better" correct to "make indium …"; "for incident" should be "for an incident"; and "The results for the production of 116In …" should be "The result…".
 
-&& \colornote{Response}
+&& \colornote{Changes implemented.}
 \end{easylist}
@@
 
-&& \colornote{Response}
+&& \colornote{Reference Updated.
+The report is only publicly available from\\ \url{https://www.aaas.org/report/nuclear-medicine-without-nuclear-reactors-or-uranium-enrichment}, but the reference has been updated with more detail.}
 & [2] - page and year of journal article are needed
 
-&& \colornote{Response}
+&& \colornote{Article was accepted and in publication at the time of this manuscript's submission, but has now been published.  Reference updated.}
 & [3] - a URL for access to the dissertation would benefit the reader
-Along with references 2 and 3, adding Q. Ji, A. Sy, and J. W. Kwan, Rev. Sci. Instr. 81, 02B312 (2010) is needed for completeness.
 
-&& \colornote{Response}
+&& \colornote{The Elsevier-recommended \url{elsarticle-num} BibTeX style does not support a URL in a PhD Thesis citation.
+I have hacked one in, \emph{but the editors are welcome to remove it in the final processing if it does not conform to journal style standards.} If another method for referencing a URL is preferred, the Thesis is hosted by UC Berkeley at  \url{http://search.proquest.com/docview/1834600459}}
+& Along with references 2 and 3, adding Q. Ji, A. Sy, and J. W. Kwan, Rev. Sci. Instr. 81, 02B312 (2010) is needed for completeness.
+
+&& \colornote{Per Ref [2,3], the ion sources used in the HFNG are based on the similar design of the Ji (2010) article, but not identical.
+This has been noted on p.2 lines 12-13, right column (``using ion sources\ldots'') .
+}
 & [13] - page and year are needed
 
-&& \colornote{Response}
+&& \colornote{Reference updated.}
 & [25] Add "Los Alamos Report" LA-UR-13-22934
 
-&& \colornote{Response}
+&& \colornote{Reference updated.}
 & [30] Add URL - http://radware.phy.ornl.gov/gf3/gf3.html
 
-&& \colornote{Response}
+&& \colornote{See above.  URLs are not allowed in this BibTeX format; I hacked it in, but the editors are welcome to remove it in order to maintain journal style.}
 \end{easylist}
@@
 
-&& \colornote{Response}
+&& \colornote{Theoretical saturation activities (based on operating conditions at the time of the work in this manuscript) have been added to section 4 (see the first paragraph of P.
+10).
+In addition, brief discussion of the steps necessary to increase the saturation activity to the mCi level are suggested.}
 \end{easylist}

### 2017-07-07 First_np_Paper/first_np_paper.tex
Added my edits, based on reviewer comments.  Sending to co-authors for feedback.

@@
 \usepackage{gensymb}
+\usepackage[normalem]{ulem}
 
@@
 
+\newcommand{\textred}[1]{\textcolor{red}{ #1}}
+\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}
+
 \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
@@
 Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
- While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
+ While reactors produce copious quantities of neutrons, their energy spectra \redactedit{is }\textred{are} often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
  Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
@@
 The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
- The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
+ The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a,doi:10.1063/1.3267832}.
  The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
@@
 
-The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The present work features a pair of cross section measurements for the production of two \textred{emerging} non-standard \textred{medical radionuclides} \redactedit{positron emitters}: \textred{the positron emitter} \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \textred{the single-photon emission computed tomography (SPECT) tracer} \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
@@
 Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
+This generator extracts deuterium ions from an RF-heated deuterium plasma \textcolor{red}{(using ion sources similar to  designs from the Lawrence Berkeley National Laboratory \cite{doi:10.1063/1.3267832})} through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
 This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
+\textred{While the machine's design features two deuterium ion sources impinging from both sides of the target, only a single source was used in the present work.}
 Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
 \autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
+A 100 k\textred{e}V deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
 
@@
 \toprule
-{Foils Used} & {Metal Purity}          & {Abundance (a/o)}                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & {Thickness (mm)}                                                                                                         & {Diameter (mm)}                                                                                                           & {Mass (g)}                                                                                    \\ \midrule
+{Foils Used} & {Metal Purity}          & {Abundance (at.
+\%)}                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & {Thickness (mm)}                                                                                                         & {Diameter (mm)}                                                                                                           & {Mass (g)}                                                                                    \\ \midrule
 
@@
 This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
-This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
+This spectrum, peaked around 2.777 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
 
@@
 The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
+Due to \textred{geometry and} the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
 For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:
@@
  \autoref{fig:in_heat_plot}  shows the measured activities for these 9 indium foils.
- Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
+ Based on these values we are able to verify that the beam was indeed \textred{vertically} centered on the middle of the zinc and titanium samples\textred{,  with a slight asymmetry of the neutron flux in the horizontal direction, accounted for in MCNP6 modeling of the energy-differential neutron flux.
+This small asymmetry likely contributes to the effective energy bin being lower than the 2.78 MeV expected for 0\degree\ neutron emission angle in \autoref{fig:scatt_angle}}.
 
@@
 
-If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
+If the target is subjected \textred{to} this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
 
@@
  However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
+ Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, make\redactedit{s} indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
@@
 
-Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
+Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for \textred{an} incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
 These values are recorded in \autoref{tab:xs_results}.
@@
 As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
-The results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
+The result\redactedit{s} for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
  This will be discussed in greater detail in the conclusion section below.
@@
 \begin{equation}
-A = \lambda N_{product} = \eta \phi \sigma N_{T}
+A = \lambda N_{product} = \eta \phi \sigma N_{\textred{target}\redactedit{\text{T}}}
 \end{equation}
 
-where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired reaction on one of the target sample atoms:
+where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired \textred{(n,p)} reaction \textred{(as opposed to a competing elastic, inelastic, (n,x), etc.
+channel)} on one of the target sample atoms:
 
@@
 
+\textred{Assuming a neutron flux of  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target, masses of 0.533 g of natural zinc and 0.337 g of natural titanium, and cross sections of 47.5 mb for \ce{^{64}Zn}(n,p)\ce{^{64}Cu}   and 26.26  mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}, theoretical saturation activities for current operation at the time of this work are estimated to be 1.5 kBq of \ce{^{64}Cu} and 0.11 kBq of \ce{^{47}Sc}.
+This falls short of the mCi (37 MBq) level required for commercial application by a factor of 3-4 orders of magnitude, but with the operation of the second deuterium ion source, increased current, and fast neutron reflection, this goal may  well be within reach.
+Based on activities at the end of irradiation, the production rate of \ce{^{64}Cu} is 453.8 Bq, and the production rate of \ce{^{47}Sc} is 31.6 Bq.
+Thus, we can conclude that, in present operation, the HFNG has an average $\eta \approx 29.9\%$.}
+
  \section{Conclusion and Future Work}
@@
 
- In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
+ In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an \textred{effective} incident neutron energy of 2.45 MeV.
  While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.

### 2017-08-07 First_np_Paper/arXiv/first_np_paper.tex
Edited version after co-author feedback on reviewer comments.  Resubmitting this revised manuscript to NIM

@@
 % \usepackage{cancel}
-% \usepackage{microtype}
+\usepackage{microtype}
 % \usepackage{listings}
@@
 Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
- While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
+ While reactors produce copious quantities of neutrons, their energy spectra are often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
  Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
@@
 
-The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The present work features a pair of cross section measurements for the production of two emerging non-standard medical radionuclides: the positron emitter \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and the single - photon emission computed tomography (SPECT) tracer \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
@@
 Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
+This generator extracts deuterium ions from an RF-heated deuterium plasma (using ion sources similar to  designs from the Lawrence Berkeley National Laboratory \cite{doi:10.1063/1.3267832}) through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
 This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
+While the machine's design features two deuterium ion sources impinging from both sides of the target, only a single source was used in the present work.
 Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
 \autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
+A 100 keV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
 
@@
 %  \centering
-% %  \includegraphics[width=\columnwidth]{IMG_20160531_183154957_HDR.jpg}
-%  \includegraphics[scale=0.06]{IMG_20160531_183154957_HDR.jpg}
+% %  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
+%  \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
 %  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[height=3in]{Capture.PNG}
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[height=3in]{./figures/Capture.PNG}
 %         \caption{The UC Berkeley High-Flux Neutron Generator,}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{target2.png}
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/target2.png}
 %         \caption{Cutaway of the target chamber.}
@@
         \centering
-%         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{target2.png}
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/target2.png}
         \includegraphics[height=2in]{cutaway.png}
@@
     \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
         \includegraphics[height=2.5in]{holder.pdf}
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[height=2in]{foils.png}
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[height=2in]{./figures/foils.png}
 %         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{holder.pdf}
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/holder.pdf}
 %         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{IMG_20151103_113432563.jpg}
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
 %         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
@@
 \end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{ccccccc}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
-% 
-% 
-% 
-% 
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}0.49 \pm 0.02* \\ 0.50 \pm 0.03* \\ 0.49 \pm 0.03* \\ 0.53 \pm 0.06$^\dagger$ \\ 0.50 \pm 0.02$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.75 \pm 0.09* \\ 9.98 \pm 0.15* \\ 9.96 \pm 0.10* \\ 10.01 \pm 0.11$^\dagger$ \\ 10.00 \pm 0.09$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.248 \pm 0.005* \\ 0.248 \pm 0.005* \\ 0.241 \pm 0.005* \\ 0.247 \pm 0.005$^\dagger$\\  0.248 \pm 0.005$^\dagger$\ \end{tabular} \\ \hline
-%    
-%    
-%    
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.03 \pm 0.01 \\ 1.03 \pm 0.01 \\ 1.02 \pm 0.01\end{tabular}                                    & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.14 \\ 9.76 \pm 0.17 \\ 9.89 \pm 0.15\end{tabular}                                     & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.538 \pm 0.005 \\ 0.451 \pm 0.005 \\ 0.452 \pm 0.005\ \end{tabular}                           \\ \hline
-% 
-% 
-% 
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.16 \pm 0.02 \\ 1.15 \pm 0.02\end{tabular}                                                         &\begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.04 \\ 9.94 \pm 0.03\end{tabular}                                                          & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.337 \pm 0.005 \\ 0.337 \pm 0.005\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}ccccccc@{}}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \comment{Need foil data from Mauricio's 2nd Ti run}
 
@@
 %  %trim option's parameter order: left bottom right top
-%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{mcnp_vised2.png}
+%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
 %  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
@@
 This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
-This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
+This spectrum, peaked around 2.777 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
+ As expected, the  production target is the dominant source of scatter - approximately 0.78\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.
 
@@
 %  \centering
-%  \includegraphics[scale=0.6]{mcnp_flux.pdf}
+%  \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
 %  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
@@
  \caption{MCNP6-modeled neutron energy spectrum for the HFNG.
-The solid lines show the spectrum at the location of the indium and the target foil respectively.
-The dotted and dashed lines show the same with the target itself \enquote{voided} to remove scattering contributions.
-Less than 1\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.}
+The solid lines show the spectrum at the location of the indium and the activation foil.
+The dotted and dashed lines show the same with the neutron production target itself \enquote{voided} to remove scattering contributions.
+}
  \label{fig:mcnp_flux}
@@
 The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
+Due to geometry and the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
 For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:
@@
 %  \centering
-%  \includegraphics[scale=0.6]{fracplot.pdf}
+%  \includegraphics[scale=0.6]{./figures/fracplot.pdf}
 %  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[height=2.8in]{IMG_20160531_182618557_HDR.jpg}
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
 %         \caption{ Ortec 80\% HPGe detector}
@@
 %         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2.8in]{IMG_20160531_182635712_HDR.jpg}
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
 %         \caption{Ortec planar LEPS detector}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[width=5in]{ti_foils.png}
-        \subfigimg[width=5in]{a)}{47sc_gspectrum_alt.pdf}
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[width=5in]{./figures/ti_foils.png}
+        \subfigimg[width=5in]{a)}{./47sc_gspectrum_alt.pdf}
 %         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
@@
         \centering
-%         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[width=5in]{Sample_spectra.png}
-        \subfigimg[width=5in]{b)}{64Cu_gspectrum_alt.pdf}
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
+        \subfigimg[width=5in]{b)}{./64Cu_gspectrum_alt.pdf}
 %         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
         \subfigimg[scale=0.6]{a)}{336keV_curve_new.pdf}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[scale=0.6]{391keV_curve2.png}
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
         \subfigimg[scale=0.6]{b)}{391keV_curve_new.pdf}
@@
         \centering
-%         \includegraphics[width=\textwidth]{target2.png}
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
         \subfigimg[scale=0.6]{c)}{417keV_curve_new.pdf}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
         \subfigimg[scale=0.6]{d)}{511keV_curve_new.pdf}
@@
 \end{table*}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}l|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil                     & \multirows{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
-% Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
-% Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
-% Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
-% End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
-% Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 \pm 1490 & 74321 \pm 275 & 39895 \pm 201 & 2122 \pm 55 & 55102 \pm 268   \\ \hline
-% Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 \pm 171    & 860 \pm 40    & 2545 \pm 54 &    \hrulefill       &  \hrulefill      \\ \hline
-% Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 \pm 643   & 12852 \pm 118 & 24464 \pm 159 &    \hrulefill       &   \hrulefill     \\ \hline
-% Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 \pm 83 & 5544 \pm 257  
-% \end{tabular}%
-% }
-% \end{table*}
-
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}|c|ccccc@{}}
-% Reference Foil                     & natIn         & natIn       & natIn & natIn     & natIn  \\
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\
-% Target Foil                        & natZn         & natZn       & natZn & natTi     & natTi  \\
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\
-% Irradiation Time, t1 (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\
-% Start of Count, t2 (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\
-% End of Count, t3 (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\
-% Photopeak Counts, 336 keV (115mIn) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\
-% Photopeak Counts, 391 keV (113mIn) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &           &        \\
-% Photopeak Counts, 511 keV (64Cu)   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &           &        \\
-% Photopeak Counts, 159 keV (47Sc)   &               &             &       & 3877 $\pm$ 83 & XXXX  
-% \end{tabular}%
-% }
-% \end{table*}
 
@@
  \autoref{fig:in_heat_plot}  shows the measured activities for these 9 indium foils.
- Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
+ Based on these values we are able to verify that the beam was indeed vertically centered on the middle of the zinc and titanium samples,  with a slight asymmetry of the neutron flux in the horizontal direction, accounted for in MCNP6 modeling of the energy-differential neutron flux.
+This small asymmetry likely contributes to the effective energy bin being lower than the 2.78 MeV expected for 0\degree\ neutron emission angle in \autoref{fig:scatt_angle}.
 
@@
 
-If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
+If the target is subjected to this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
 
@@
  However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
+ Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, make indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
@@
 
+A much smaller systematic uncertainty arises from the fact that the two (n,p) cross sections and the reference In(n,n') cross sections have slightly different thresholds.  
+The total activity in the In produced by the low energy neutrons (below the \enquote{knee} near 2.25 MeV in  \autoref{fig:mcnp_flux}) is 2.17\%.  
+The corresponding values from TALYS for the $^{64}$Cu and $^{47}$Sc activity are 0.24\% and 0.85\%, respectively.  
+If we assume an uncertainty of $\pm$25\% in the TALYS calculations in this energy region it would introduce an additional systematic uncertainty in the $^{+10}_{-20}$ keV effective energy bin of $\pm$1.6 keV for $^{64}$Cu and $\pm$5.7 keV for $^{47}$Sc.
+As these are smaller than the precision of the existing effective energy bin, they can be considered negligible.
+
 \section{Results}
 
-Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
+Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for an incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
 These values are recorded in \autoref{tab:xs_results}.
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-% \label{tab:xs_results}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
 \begin{table}
@@
 %  \centering
-%  \includegraphics[scale=0.6]{64cu_fixed.pdf}
+%  \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
 %  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
 As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
-The results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
+The result for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
+The MCNP neutron spectrum in   \autoref{fig:mcnp_flux} confirms this - thermal and epithermal neutrons make up only 0.0771\% of the total neutron population.
  This will be discussed in greater detail in the conclusion section below.
@@
  Many applications, including diagnostic and therapeutic medical use, require mCi activity levels.
- The production of a radionuclide sample with an activity $A$ driven to secular equilibrium using a neutron source with a total flux $\phi$ and a reaction cross section $\sigma$ acting on sample of $N_{target}$ atoms is given by the expression:
+ For the production of a radionuclide sample, the saturation activity ($A_{saturation}$) is achieved at secular equilibrium:
 
  \begin{equation}
-A = \lambda N_{product} = \eta \phi \sigma N_{T}
+R_{production} = R_{decay} = \lambda N_{product}
 \end{equation}
-
-where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired reaction on one of the target sample atoms:
-
-% \begin{figure*}[H]
-% \hline
+% 
+% While the saturation activity represents the maximum activity that can be made at a generator with a given total neutron output, there may be situations where either a smaller activity is needed, or a shorter irradiation is desired.
+% In this case, it is useful to introduce a neutron utilization factor ($\eta$).
+$\eta$ is the constant of proportionality between $\Phi_n$, the neutron source output (in neutrons/second), and the saturation activity:
+% 
 % \begin{equation}
-% \eta = \int_0^E dE_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\phi} 4\pi r^2 dr d\pp{\cos{\theta}} d\theta
+% A_{saturation} = \eta \Phi_n
 % \end{equation}
-% \end{figure*}
-
-% \begin{strip}
+% 
+% $\eta$ represents the likelihood that a neutron produced in the generator will create the desired activity. 
+% It includes the overlap between the production target and the locus where the neutrons are being created, and the fraction of nuclear reactions which generate the desired activity: 
+% 
+% 
+% 
+% \begin{align}
+% \eta &= \dfrac{1}{\phi_\mathbb{R}} \int\displaylimits_{production\ target}  \dfrac{\bar{\sigma}_{desired}}{\bar{\sigma}_{total}}\phi\pp{\mathbf{r}}\rho_{target}\pp{\mathbf{r}}\text{d}\mathbf{V}, \nonumber\\
+% \text{d}\mathbf{V} &= \mathbf{r}^2 \text{d}\mathbf{r} \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
+% \end{align}
+% 
+% 
+% where $\dfrac{\bar{\sigma}_{desired}}{\bar{\sigma}_{total}}$ is the ratio of the cross section producing the radionuclide of interest over the total reaction cross section, $\rho_{target}\pp{\mathbf{r}}$ is the density of the target as a function of position, and $\phi\pp{\mathbf{r}}$ and $\phi_\mathbb{R}$ are the neutron flux (in n/cm$^2$/s) as a function of position and over all space, respectively.
+$\eta$ allows us to cast the activity produced in a given irradiation time $t_i$ as:
+% 
+% \begin{equation}
+% A\pp{t_i} = \eta \Phi_n \pp{1-e^{-\lambda t_i}}
+% \end{equation}
+% 
+% 
+% where $\Phi_n$  is the total neutron output of the source in neutrons/second.  
+% Maximizing $\eta$ would be the goal of any engineering design to produce a desired activity using a neutron generator at a minimum of cost and radiological impact.
+
+While the saturation activity represents the maximum activity that can be made at a generator with a given total neutron output, there may be situations where either a smaller activity is needed, or a shorter irradiation is desired.
+In this case, it is useful to introduce a neutron utilization factor ($\eta_x$).
+$\eta_x$ is the constant of proportionality between $R_n$, the neutron source output (in neutrons/second), and the saturation activity:
+
+\begin{equation}
+A_{saturation} = \eta_x R_n
+\end{equation}
+
+$\eta_x$ represents the likelihood that a neutron produced in the generator will create $x$, the isotope of interest. 
+It includes the overlap between the production target and the locus where the neutrons are being created, and the fraction of nuclear reactions which generate the desired activity $x$:
 
 \begin{align}
-\eta &= \int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}, \nonumber\\
-\text{d}\mathbf{V} &= r^2 \text{d}r \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
+\eta_x &= \dfrac{1}{R_n} \int\displaylimits_{production\ target} \phi\pp{\mathbf{r}}\bar{\sigma}_x\ \rho_{target}\pp{\mathbf{r}}\text{d}\mathbf{V}, \nonumber\\
+\text{d}\mathbf{V} &= \mathbf{r}^2 \text{d}\mathbf{r} \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
 \end{align}
-% \end{strip}
+
+where $\bar{\sigma}_x$ is the average cross section producing the radionuclide of interest, $\rho_{target}\pp{\mathbf{r}}$ is the density of the target as a function of position, and $\phi\pp{\mathbf{r}}$ is the neutron flux (in n/cm$^2$/s) as a function of position.
+$\eta_x$ allows us to cast the activity produced in a given irradiation time $t_i$ as:
+
+\begin{equation}
+A\pp{t_i} = \eta_x R_n \pp{1-e^{-\lambda t_i}}
+\end{equation}
+
+% where $\Phi_n$  is the total neutron output of the source in neutrons/second.  
+Maximizing $\eta_x$ would be the goal of any engineering design to produce a desired activity using a neutron generator at a minimum of cost and radiological impact.
+
+%  The production of a radionuclide sample with an activity $A$ driven to secular equilibrium using a neutron source with a total flux $\phi$ and a reaction cross section $\sigma$ acting on sample of $N_{target}$ atoms is given by the expression:
+% 
+% \begin{equation}
+% A = \lambda N_{product} = \eta \phi \sigma N_{\textred{target}\redactedit{\text{T}}}
+% \end{equation}
+% 
+% where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired \textred{(n,p)} reaction \textred{(as opposed to a competing elastic, inelastic, (n,x), etc.
+channel)} on one of the target sample atoms:
+% 
+% 
+% % \begin{figure*}[H]
+% % \hline
+% % \begin{equation}
+% % \eta = \int_0^E dE_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\phi} 4\pi r^2 dr d\pp{\cos{\theta}} d\theta
+% % \end{equation}
+% % \end{figure*}
+% 
+% 
+% % \begin{strip}
+% 
+% \begin{align}
+% \eta &= \int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}, \nonumber\\
+% \text{d}\mathbf{V} &= r^2 \text{d}r \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
+% \end{align}
+% % \end{strip}
 
@@
 
+Assuming a neutron flux of  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target, masses of 0.533 g of natural zinc and 0.337 g of natural titanium, and cross sections of 47.5 mb for \ce{^{64}Zn}(n,p)\ce{^{64}Cu}   and 26.26  mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}, theoretical saturation activities for current operation at the time of this work are estimated to be 1.5 kBq of \ce{^{64}Cu} and 0.11 kBq of \ce{^{47}Sc}.
+This falls short of the mCi (37 MBq) level required for commercial application by a factor of 3-4 orders of magnitude, but with the operation of the second deuterium ion source, increased current, and fast neutron reflection, this goal may  well be within reach.
+By increasing the activation target thickness to 1 cm (a factor of 10), switching to DT operation (a factor of 80), increasing current and running the second ion source (a factor of 60), and relying upon the higher (n,p) cross section at DT energies (a factor of approximately 3), we believe saturation activities of approximately 6 mCi of \ce{^{64}Cu} and 0.5 mCi of \ce{^{47}Sc} can be achieved.
+The activities produced at the end of irradiation averaged 453.8 Bq of \ce{^{64}Cu}, and 31.6 Bq of \ce{^{47}Sc}.
+Assuming a conservative neutron source output of $10^8$ neutrons / second, we can estimate that, in present operation, the HFNG has an average $\eta_{64Cu} \approx \sci{3.0}{-5}$ for \ce{^{64}Cu} and $\eta_{47Sc} \approx \sci{1.1}{-5}$ for  \ce{^{47}Sc}.
+This falls approximately 4 orders of magnitude short of the $\eta_x \approx 0.37$ needed for mCi-scale production.
+A factor of 10 in $\eta_x$ could easily be gained through use of targets  1-cm in thickness without worry of contaminating reaction channels opening up, but $\eta_x$ gains beyond this will require modification of operation conditions.
+
  \section{Conclusion and Future Work}
@@
 
- In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
+ In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an effective incident neutron energy of 2.45 MeV.  
  While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
@@
 % \bibliographystyle{ieeetr}
-\bibliography{../../library}
+\bibliography{./library}
 % \thispagestyle{fancyTOC}

### 2017-08-07 First_np_Paper/first_np_paper.tex
Edited version after co-author feedback on reviewer comments.  Resubmitting this revised manuscript to NIM

--- 2017-04-26 First_np_Paper/first_np_paper.tex
@@
 \end{table*}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}l|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil                     & \multirow{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
-% Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
-% Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
-% Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
-% End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
-% Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 \pm 1490 & 74321 \pm 275 & 39895 \pm 201 & 2122 \pm 55 & 55102 \pm 268   \\ \hline
-% Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 \pm 171    & 860 \pm 40    & 2545 \pm 54 &    \hrulefill       &  \hrulefill      \\ \hline
-% Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 \pm 643   & 12852 \pm 118 & 24464 \pm 159 &    \hrulefill       &   \hrulefill     \\ \hline
-% Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 \pm 83 & 5544 \pm 257  
-% \end{tabular}%
-% }
-% \end{table*}
-
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}|c|ccccc@{}}
-% Reference Foil                     & natIn         & natIn       & natIn & natIn     & natIn  \\
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\
-% Target Foil                        & natZn         & natZn       & natZn & natTi     & natTi  \\
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\
-% Irradiation Time, t1 (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\
-% Start of Count, t2 (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\
-% End of Count, t3 (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\
-% Photopeak Counts, 336 keV (115mIn) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\
-% Photopeak Counts, 391 keV (113mIn) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &           &        \\
-% Photopeak Counts, 511 keV (64Cu)   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &           &        \\
-% Photopeak Counts, 159 keV (47Sc)   &               &             &       & 3877 $\pm$ 83 & XXXX  
-% \end{tabular}%
-% }
-% \end{table*}
 

### 2017-11-11 nb_px_paper/nb_px_paper.tex
Created blank template to start the IPF Nb(p,x) paper.

--- 2017-04-26 First_np_Paper/first_np_paper.tex
@@
 %%
-\title{Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}
+\title{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on Nb and Cu}
 
-% \title{(n,p) Cross Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
 %% \tnotetext[label1]{}
@@
 
-% \title{NE290A - Homework \#04}
-% \date{29 April, 2016}
-
 % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
@@
 
-\author[lbl]{M.S. Basunia}
+% \author[lbl]{M.S. Basunia}
+% 
+% \author[ucb]{J.C. Batchelder}
+% 
+% \author[llnl]{J.D. Bauer}
+% 
+% \author[geo]{T.A. Becker}
 
-\author[ucb]{J.C. Batchelder}
+\author[ucb,lbl]{Lee A. Bernstein}
 
-\author[llnl]{J.D. Bauer}
+\author[lanl]{Eva R. Birnbaum}
 
-\author[geo]{T.A. Becker}
+\author[uwm]{Jonathan W. Engle}
 
-\author[ucb,lbl]{L.A. Bernstein}
+\author[lanl]{Francois M. Nortier}
 
-\author[ucb]{E.F. Matthews}
-
-\author[geo,eps]{P.R. Renne}
-
-\author[geo,eps]{D. Rutte}
-
-\author[ucb]{M.A. Unzueta}
-
-\author[ucb]{K.A. van Bibber}
-
-% \author[lbl]{K. ̃Bazargan\fnref{fn2}}
-% \ead{kaveh@river-valley.com}
+% \author[ucb]{M.A. Unzueta}
+% 
+% \author[ucb]{K.A. van Bibber}
 
@@
 
-\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Berkeley CA, 94720 USA}
-\address[lbl]{Lawrence Berkeley National Laboratory,  Berkeley CA, 94720 USA}
-\address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-\address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
-\address[eps]{Department of Earth and Planetary Sciences, University of California, Berkeley, Berkeley CA,  94720  USA}
-
-% \author{Andrew Voyles}
-
-% \address{Nuclear Engineering, University of California Berkeley, Berkeley, CA 94709, USA.}
+\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
+\address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
+% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
+% \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
+\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
+\address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
 
@@
 
-%\comment{Use DD or DD as convention?}
-
-% \comment{Need Daniel's middle initial} - he doesn't have one
-
-Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator (HFNG).
-The HFNG is a compact neutron generator designed as a \enquote{flux-trap} that maximizes the probability that a neutron will interact with a sample loaded into a specific, central location.  
-The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
-The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26 $\pm$  0.82 mb.
-The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
-This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.
+XXXXX
 
@@
 %% keywords here, in the form: keyword \sep keyword
-DD neutron generator \sep Medical Isotope Production \sep Scandium (Sc) and Copper (Cu) radioisotopes \sep Indium \sep Ratio activation \sep Theranostics
+Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor foils \sep Medical isotope production \sep MCNP \sep  LANL
 
@@
 
-%
-% If we want to mention in-situ-production
-%
-%
-% e.g.:In-situ production (I always figured this is what is so great, correct me if I am wrong) of radioactive nuclides is an emerging method for radiation therapy in nuclear medicine (e.g., cite some recent review paper).
-It is based on doping the malignant target tissue with a stable nuclide which is then activated in-situ by neutron irradiation.
-Following decay is focused on the target tissue.
-Advantages compared to conventional radiation therapy are the reduction of damage to surrounding cells, … short range, … .
-Currently development of this technique is hampered by the lack of fundamental cross section data for various isotopes.
-
-There has been significant interest in the past several years in exploring the use of neutron-induced reactions to create radionuclides for a wide range of applications.
-This interest is due to the volumetric absorption of neutrons as compared to charged particle beams (ranges of $\sfrac{\text{g}}{\text{cm}^2}$ as compared to 10's of $\sfrac{\text{mg}}{\text{cm}^2}$), together with the fact that isotope production facilities often produce large secondary neutron fields.
- Particular interest has been paid to (n,p) and (n,$\alpha$) charge-exchange reactions since these reactions produce high-specific activity radionuclide samples without the use of chemical carriers in the separation process.
-
-Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
- While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
- Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
-DT generators may also often be limited by the restricted use of tritium at many institutions.
-
-In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to (n,p) radionuclide production.
-However, the lower achievable flux from these generators limits their production capabilities.
- An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
-
-The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
- The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
- The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
- In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
-While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
-
-The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
-In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
-This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
-In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
-
 % \comment{cite theranostic papers, etc}
 
-Current methodology in radiochemistry has shown recovery of upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
-By expanding the base of efficient reaction pathways, great advances are possible in making production of medical radionuclides more efficient and affordable for those in need.
-It is this desire to improve the options available for modern medical imaging and cancer therapy which has motivated the campaign of nuclear data measurements for isotope production at the UC Berkeley HFNG.
+XXXXXX  \cite{Updegraff2013}.
 
-\section{Experiment}\label{sec:experiment}
+\section{Experimental methods and materials}\label{sec:experiment}
 
-\subsection{Neutron source}\label{sec:n_source}
+\subsection{Stacked-target design }\label{sec:target_design}
 
@@
 
-% Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
-\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
-
-Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
-\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
+XXXXXX
 
@@
 %     \centering
-% %  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
-%  \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
-%  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
-%  \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
-%  \label{fig:alt_HFNG}
+%         \centering
+%         \includegraphics[height=2in]{./figures/cutaway.png}
+%         \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
+%                 \label{fig:hfng_b}
 % \end{figure}
 
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.4\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=3in]{./figures/Capture.PNG}
-%         \caption{The UC Berkeley High-Flux Neutron Generator,}
-%         \label{fig:hfng_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.4\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/target2.png}
-%         \caption{Cutaway of the target chamber.}
-%                 \label{fig:hfng_b}
-%     \end{subfigure}
-%     \caption{Note: the ion source is approximately 20 cm in diameter.}
-%      \label{fig:main_HFNG}
-% \end{figure*}
+\subsection{Measurement of induced activities}\label{sec:spectroscopy}
 
-\begin{figure}
-    \centering
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/target2.png}
-        \includegraphics[height=2in]{./figures/cutaway.png}
-        \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
-                \label{fig:hfng_b}
-%      \label{fig:main_HFNG}
-\end{figure}
-
-% \comment{Can someone please provide me a better version of \autoref{fig:hfng_b}, with appropriate labeling? Please use PDF or other vector image format.}
-
-\subsection{Cross section determination by relative activation}\label{sec:sample_loading}
-
-The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012,zsolnay2012technical}.
-  \autoref{tab:foil_specs} lists physical characteristics of each foil for the various irradiations.
-In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
- After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and time-dependent decay gamma-ray spectra were collected.
-
-\begin{figure}
-    \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2.5in]{./figures/holder.pdf}
-        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
-        \label{fig:holder_a}
-\end{figure}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=2in]{./figures/foils.png}
-%         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
-%         \label{fig:holder_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/holder.pdf}
-%         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
-%                 \label{fig:holder_b}
-%     \end{subfigure}
-%      ~ 
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
-%         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
-%                 \label{fig:holder_c}
-%     \end{subfigure}
-%     \caption{}
-%      \label{fig:main_holders}
-% \end{figure*}
-
-One cm diameter, 1-mm thick natural abundance zinc and titanium targets were employed for the measurement.
-Each of these was  co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thick polyethylene holder, as seen in \autoref{fig:holder_a}, which was mounted in the HFNG target center.
-Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue that could become activated during irradiation.
+XXXXXX
 
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \usepackage{graphicx}
+\subsection{Proton dosimetry}\label{sec:spectroscopy}
 
-\begin{table*}
-\centering
-\caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.}
-\label{tab:foil_specs}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}ccccS[table-format=+1.2,
-                  table-figures-uncertainty=1]S[table-format=+2.2,
-                  table-figures-uncertainty=1]S[table-format=+1.3,
-                  table-figures-uncertainty=1]@{}}
-\toprule
-{Foils Used} & {Metal Purity}          & {Abundance (a/o)}                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & {Thickness (mm)}                                                                                                         & {Diameter (mm)}                                                                                                           & {Mass (g)}                                                                                    \\ \midrule
+% describe integral equation for converting activities to currents here
 
-\multirow{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirow{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirow{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirow{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
+XXXXXX
 
- &  & & & 1.03 \pm 0.01 & 9.76 \pm 0.17 & 0.521 \pm 0.005 \\
+\subsection{Proton transport calculations}\label{sec:proton_transport}
 
-  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
+XXXXXX
 
-\multirow{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirow{2}*{\minitab[c]{99.999\%   }} & \multirow{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirow{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
-
-  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\  \hline
-
-\multirow{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirow{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirow{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirow{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
-
- &  & & & 0.50 \pm 0.03* & 9.98 \pm 0.15*  & 0.248 \pm 0.005* \\
-
-  &  & & & 0.49 \pm 0.03* & 9.96 \pm 0.10* &  0.241 \pm 0.005* \\
-
-   &  & & & 0.53 \pm 0.06$^\dagger$ & 10.01 \pm 0.11$^\dagger$ & 0.247 \pm 0.005$^\dagger$\\
-
-    &  & & & 0.50 \pm 0.02$^\dagger$ & 10.00 \pm 0.09$^\dagger$  & 0.248 \pm 0.005$^\dagger$ \\ \bottomrule
-
-\end{tabular}%
-}
-\end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{ccccccc}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
-% 
-% 
-% 
-% 
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}0.49 \pm 0.02* \\ 0.50 \pm 0.03* \\ 0.49 \pm 0.03* \\ 0.53 \pm 0.06$^\dagger$ \\ 0.50 \pm 0.02$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.75 \pm 0.09* \\ 9.98 \pm 0.15* \\ 9.96 \pm 0.10* \\ 10.01 \pm 0.11$^\dagger$ \\ 10.00 \pm 0.09$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.248 \pm 0.005* \\ 0.248 \pm 0.005* \\ 0.241 \pm 0.005* \\ 0.247 \pm 0.005$^\dagger$\\  0.248 \pm 0.005$^\dagger$\ \end{tabular} \\ \hline
-%    
-%    
-%    
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.03 \pm 0.01 \\ 1.03 \pm 0.01 \\ 1.02 \pm 0.01\end{tabular}                                    & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.14 \\ 9.76 \pm 0.17 \\ 9.89 \pm 0.15\end{tabular}                                     & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.538 \pm 0.005 \\ 0.451 \pm 0.005 \\ 0.452 \pm 0.005\ \end{tabular}                           \\ \hline
-% 
-% 
-% 
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.16 \pm 0.02 \\ 1.15 \pm 0.02\end{tabular}                                                         &\begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.04 \\ 9.94 \pm 0.03\end{tabular}                                                          & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.337 \pm 0.005 \\ 0.337 \pm 0.005\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}ccccccc@{}}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \comment{Need foil data from Mauricio's 2nd Ti run}
-
-\subsection{Determination of effective neutron energy}\label{sec:neutron_energies}
-
-The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 
-% 2.2 to 2.85 MeV   (thin-target Liskien values)
-% 2.18 to 2.78 MeV  (Liskien thick-target coefficient corrections to above)
-2.18 to 2.78 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
-This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.
-
-% \comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}
-
-%\comment{Should we say more about the neutron angular and energy distributions? Something from Cory's thesis or the NIM-A papers that are coming along?}
-
-% \comment{Parenthetical citations, or just a list at the end? The Shimizu paper uses the latter as citation format.}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
- % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
- \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons \cite{Liskien_Paulsen_1973}.}
- \label{fig:scatt_angle}
-\end{figure}
-
-Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\degree)
-% the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
-angular range in a region of  high  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
-This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
-
-% \begin{figure}
-%  \centering
-%  %trim option's parameter order: left bottom right top
-%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
-%  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
-%  \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
-%  \label{fig:mcnp_vised}
-% \end{figure}
-
-% \comment{Does \autoref{fig:mcnp_vised} serve any purpose? I'm starting to think it doesn't - should we just cut it?}
-
-The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
-The neutron spectral distribution is also broadened by the temperature of the target.  
-This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
-This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
-
-% \comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
-%  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
-%  \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
-%  \label{fig:mcnp_flux}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/mcnp_flux_new.pdf}
- % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
- \caption{MCNP6-modeled neutron energy spectrum for the HFNG.
-The solid lines show the spectrum at the location of the indium and the target foil respectively.
-The dotted and dashed lines show the same with the target itself \enquote{voided} to remove scattering contributions.
-Less than 1\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.}
- \label{fig:mcnp_flux}
-\end{figure}
-
-%\comment{Use this version, old version (mcnp-flux.pdf), or some new combination of lines?}
-
-While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined.
-The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
-For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:
-
-\begin{equation}
-R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
-\end{equation}
-
-% \comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }
-
-From this definition, it is possible to calculate $F\pp{E'}$, the fraction of total reactions induced by neutrons up to some energy $E' < E_{max}$:
-
-\begin{equation}\label{eqn:react_fraction}
-F\pp{E'} = \dfrac{\int_0^{E'} \sigma(E) \dfrac{d\phi}{dE} dE}{\int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE}
-\end{equation}
-
-% This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.      - note: moved to next paragraph, for better flow.
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/fracplot.pdf}
-%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
-%  \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
-%  \label{fig:frac_plot}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/fracplot_new.pdf}
- % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$].
-The solid red boundaries indicate the energy region that corresponds to 68.2\% of the total activation.}
- \label{fig:frac_plot}
-\end{figure}
-
-%\comment{Use this version, or old version (fracplot.pdf)?}
-
-% \comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%, after using new A}
-
-This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.
-The fraction of total reactions in the indium foil can be used to characterize the effective neutron energy bin.
- Our approach, in analogy to the Gaussian quantity $\sigma$, will be to use a horizontal \enquote{error bar}  to represent the energy range responsible for 68.2\% of the reactions taking place.
- Using this approach, we report the effective energy bin as being $E_n$=2.765$^{+0.014}_{-0.022}$ MeV.
-This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a quasi-monoenergetic neutron flux.
-%$E_n$ = 2.7645 MeV + 0.0141 MeV / - 0.0219 MeV.
-
-\subsection{Measurement of induced activities}\label{sec:spectroscopy}
-
-After irradiation, the co-loaded targets were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy.
-Two detectors were used in this measurement.
-An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay \cite{Singh2007}, the 391 keV gamma-ray from the \ce{^{113m}In}  isomer \cite{Blachot2010a}, and the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer \cite{Blachot2012}.
-An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} \cite{Burrows2007} as well as the two indium isomers mentioned above.
-Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
-These efficiencies, along with gamma ray intensities for each transition, were used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Gamma-ray properties for the decay lines measured in the present work.}
-\label{tab:decay_props}
-\begin{tabular}{@{}cccc@{}}
-\toprule
-Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 $\pm$ 0.4        & 12.701 h   \\
-\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 $\pm$ 0.4      & 3.3492 d   \\
-\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 $\pm$ 0.17    & 99.476 m  \\
-\ce{^{115m}In} \cite{Hansen1974} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
-\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 $\pm$ 0.4      & 54.29 m   \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% Version using NDS-style uncertainties 
-%
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{Gamma-ray properties for the decay lines measured in the present work.}
-% \label{tab:decay_props}
-% \begin{tabular}{@{}cccc@{}}
-% \toprule
-% Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-% \ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 \% \emph{4}      & 12.701 h \emph{2}  \\
-% \ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 \% \emph{4}      & 3.3492 d \emph{6}  \\
-% \ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 \% \emph{17}    & 99.476 m \emph{23} \\
-% \ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.8 \% \emph{4}      & 4.486 h \emph{4}   \\
-% \ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 \% \emph{4}      & 54.29 m \emph{17}  \\ \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}
-
-% \begin{figure*}[H]
-%     \centering
-%     \begin{subfigure}[t]{0.7\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
-%         \caption{ Ortec 80\% HPGe detector}
-%         \label{fig:hpge_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.28\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
-%         \caption{Ortec planar LEPS detector}
-%                 \label{fig:hpge_b}
-%     \end{subfigure}
-%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
-%      \label{fig:main_ge_detectors}
-% \end{figure*}
-% 
-% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}
-
-The irradiated foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
-All data collection was performed using the Ortec MAESTRO software.
-For each experiment the detector dead time was verified to be less than 5\%.
- No summing corrections needed to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
-%This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
-
-For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector.
-For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
-The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
-Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
-
-\begin{figure*}[ht]
-    \centering
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[width=5in]{./figures/ti_foils.png}
-        \subfigimg[width=5in]{a)}{./figures/47sc_gspectrum_alt.pdf}
-%         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
-% 	\caption{}
-        \refstepcounter{subfigure}\label{fig:spectra_a}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
-        \subfigimg[width=5in]{b)}{./figures/64Cu_gspectrum_alt.pdf}
-%         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-          \refstepcounter{subfigure}       \label{fig:spectra_b}
-    \end{subfigure}
-    \caption{Example gamma spectra collected to monitor radioisotope production.
-(a)  Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector and (b) gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-     \label{fig:main_spectra}
-\end{figure*}
-
-To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals.
-The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
-The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \cite{Burrows2007,Singh2007,Blachot2010a,Blachot2012,Blachot2010}, confirming the respective peak assignments.
-
-% \comment{Reference original ENSDF papers}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{a)}{./figures/336keV_curve_new.pdf}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_336}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.6]{b)}{./figures/391keV_curve_new.pdf}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_391}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.6]{c)}{./figures/417keV_curve_new.pdf}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:decay_curve_417}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{d)}{./figures/511keV_curve_new.pdf}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:decay_curve_511}
-    \end{subfigure}%
-    \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:decay_curves}
-\end{figure*}
-
-The spectra for each sample were summed and the net peak areas were fitted using gf3, part of the RadWare analysis package from Oak Ridge National Laboratory   \cite{radford2000radware, Radford1995}.
-The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table*}
-\centering
-\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-\label{tab:peak_counts}
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{l|ccccc}
-\begin{tabular}{lccccc}
-\toprule
-% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \midrule
-Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ 
-Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ 
-Target Foil Mass (g)               & 0.538         & 0.521       & 0.542 & 0.337     & 0.337   \\ 
-Irradiation Time, $t_i$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ 
-Delay Time, $t_d$ (s)             & 1785         & 16185       & 2290 & 89408    & 2390   \\ 
-Counting Time, $t_c$ (s)               & 91188        & 54008       & 54002 & 86424    & 93631   \\ 
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 76321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 890 $\pm$ 40    & 3505 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 27164 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
-Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257 \\ \bottomrule
-\end{tabular}%
-}
-\end{table*}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}l|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil                     & \multirow{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
-% Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
-% Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
-% Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
-% End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
-% Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 \pm 1490 & 74321 \pm 275 & 39895 \pm 201 & 2122 \pm 55 & 55102 \pm 268   \\ \hline
-% Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 \pm 171    & 860 \pm 40    & 2545 \pm 54 &    \hrulefill       &  \hrulefill      \\ \hline
-% Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 \pm 643   & 12852 \pm 118 & 24464 \pm 159 &    \hrulefill       &   \hrulefill     \\ \hline
-% Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 \pm 83 & 5544 \pm 257  
-% \end{tabular}%
-% }
-% \end{table*}
-
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}|c|ccccc@{}}
-% Reference Foil                     & natIn         & natIn       & natIn & natIn     & natIn  \\
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\
-% Target Foil                        & natZn         & natZn       & natZn & natTi     & natTi  \\
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\
-% Irradiation Time, t1 (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\
-% Start of Count, t2 (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\
-% End of Count, t3 (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\
-% Photopeak Counts, 336 keV (115mIn) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\
-% Photopeak Counts, 391 keV (113mIn) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &           &        \\
-% Photopeak Counts, 511 keV (64Cu)   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &           &        \\
-% Photopeak Counts, 159 keV (47Sc)   &               &             &       & 3877 $\pm$ 83 & XXXX  
-% \end{tabular}%
-% }
-% \end{table*}
-
-\subsection{Experimental verification of incident neutron energy}\label{sec:lee_sec}
-
-As shown in \autoref{sec:sample_loading} above, the effective neutron energy depends on the angle range subtended by the sample with respect to the incident deuteron beam.
- In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.
- This centroid position of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
- The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
- \autoref{fig:in_heat_plot}  shows the measured activities for these 9 indium foils.
- Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.55]{./figures/fig1_cropped.pdf}
- % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Relative fluxes as seen by a 3 x 3 array of indium foils.
-The central foil corresponds to the location in which target and monitor foils were mounted during the cross section measurements, verifying that the beam is centered on the middle of mounted foils.}
- \label{fig:in_heat_plot}
-\end{figure}
-
-% \comment{CHECK WITH ERIC for 3x3 In info and plot  \autoref{fig:in_heat_plot}}
+% \begin{equation}
+% R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
+% \end{equation}
 
@@
 
-For a thin target consisting of \(N_T\) target nuclei (with a reaction cross section $\sigma\pp{\bar{E}}$), subjected to a constant neutron flux $\phi\pp{\bar{E}}$, the rate of production ($R$) of the product nucleus will be:
+%  include 1st and 2nd order bateman stuff here
 
-\begin{equation}
-R = N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} 
-\end{equation}
+XXXXXX
 
-If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
+% \begin{align}
+% N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
+% &=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
+% \end{align}
 
-\begin{align}
-N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
-\\
-&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-\end{align}
-
-% \begin{equation}
-% \begin{aligned}
-% N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
-% \\
-% &= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} 
-% \end{aligned}
-% \end{equation}
-
-If this decay emits a gamma ray with absolute intensity $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed gamma rays during the acquisition will be:
-
-% \begin{equation}
-% \begin{aligned}
-% N_{obs} &= D \epsilon_\gamma I_\gamma \\
-% &= \? \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
-% \end{aligned}
-% \end{equation}
-
-\begin{align}
-N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
-&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-\end{align}
-
-Solving this equation for the  cross section results in:
-
-\begin{align}\label{eqn:single_xs_eqn}
-\sigma\pp{\bar{E}} = \dfrac{N_{\gamma}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
-\end{align}
-
-% \begin{equation}\label{eqn:single_xs_eqn}
-% \sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
-% \end{equation}
-
-\autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils.
-This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.
- \autoref{eqn:calc_eqn} shows the ratio of the cross sections determined using this approach, in which subscript $P$ indicates a quantity for either \ce{^{64}Cu} or \ce{^{47}Sc}, and subscript $In$ indicates a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer.
-A minor term was added to correct for the small self-attenuation of the gamma rays emitted by the activated foils:
-
-\begin{align}\label{eqn:calc_eqn}
-\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{N_{\gamma,P}}{N_{\gamma,In}}  \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \pp{\dfrac{1 - e^{-\lambda_{In}t_i}}{1 - e^{-\lambda_{P}t_i}}} \dfrac{e^{-\lambda_{In}t_d}}{ e^{-\lambda_{P}t_d}} \times \\
-&\times \pp{\dfrac{1 - e^{-\lambda_{In}t_c}}{1 - e^{-\lambda_{P}t_c}}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
-\end{align}
-
-where:
-
-\begin{itemize}
-
-% \item $N_{\gamma}$ is the integrated counts under a photopeak [counts],
-\item $N_{\gamma}$ is the integrated counts under a photopeak,
-
-\item $\sigma$ is the cross section for either the production of a product or isomer [mb],
-
-\item $N_T$ is the initial number of target nuclei,
-
-\item $\lambda$  is the decay constant [s$^{-1}$],
-
-\item $t_i$ is the irradiation time [s],
-
-\item $t_d$ is the delay time (between the end-of-beam and the start of counting) [s],
-
-\item $t_c$ is the counting time   [s],
-
-\item $\epsilon$ is the  detector efficiency for a particular photopeak,
-
-\item $I_\gamma$ is the decay gamma ray absolute intensity [\%],
-
-\item $\mu$ is the photon attenuation coefficient for a particular decay gamma ray in a foil [cm$^{-1}$],
-
-\item and $x$ is the thickness of foil traversed by a particular decay gamma ray [cm] 
-\end{itemize}
-
-In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min \cite{Blachot2010}) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
- The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately 2,000 times greater than at 2.7 MeV  \cite{Capote2012,zsolnay2012technical}.
-
-% \comment{cite relevant NDS article}
-
-With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries an uncertainty.
-Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
-
-\begin{equation}
-\delta_\sigma = \norm{ \ensuremath{\vec{\delta}} }_2 = \sqrt{\sum_{i=1}^N  \delta_i^2  }
-\end{equation}
-
-This total  uncertainty is plotted as the cross section uncertainty in \autoref{fig:sc_xs} and \autoref{fig:cu_xs_zoom}.
+% \autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils.
+% This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.
 
@@
 
-The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the 2.586\% uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the 1.447\% uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section  \cite{Capote2012,zsolnay2012technical}.
- An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.
- However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
-The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
- We believe, based on \enquote{burn marks} on the neutron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
- However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width, which places a natural limit on the reported effective neutron energy.
+XXXXXX
 
@@
 
-Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
-These values are recorded in \autoref{tab:xs_results}.
+XXXXXX
 
-% \comment{Report a weighted average between the solo values, insert in text}
+% \section{Discussion}
 
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% h                                 & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                     \\ \midrule
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{113}In}) & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
-% \ce{^{47}Ti}(n,p)\ce{^{47}Sc} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
+% XXXXXX
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-% \label{tab:xs_results}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
-\begin{table}
-\centering
-\caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-\label{tab:xs_results}
-\begin{tabular}{@{}cS[table-format=+2.1,
-                  table-figures-uncertainty=1]@{}}
-\toprule
-Reaction                   & \multirow{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
-\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
-											& 49.2 \pm 2.7 \\ 
-											& 49.0 \pm 2.5 \\  \\[0.1ex]  
-\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
-											& 46.5 \pm 1.7 \\ 
-											& 46.8 \pm 3.2  \\ \\[0.1ex]    
-\multirow{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
-											& 26.7 \pm 1.4*                   \\ \bottomrule
-\end{tabular}
-\end{table}
+ \section{Conclusions}
 
-% \comment{Karl:  \enquote{For the figures, let me suggest you make a red solid rectangle whose dimensions represent the error bars in both energy and cross section.
-Then put a large red circle around it, whose diameter is of order 10\% of the size of the whole graph, to focus the eyes.
-In the caption, mention that the size of the rectangle represents the error limits.}  Lee: \enquote{I would suggest that you zoom in on the energy and cross section value we measured (say 2.5-3.0 MeV and 10-70 mb).
-Use a thicker line for our data point and/or make it larger.
-- Lee}}
-
-Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of the measurements give   49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) and 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26 $\pm$  0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith (1975), Armitage (1967), and Ikeda (1990) groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from the Hussain (1983), Gonzalez (1962), and Shimizu (2004) groups \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
-
-%\comment{I referenced the original publication for each data set in \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} as ''Author (Year)''.
-Is this acceptable, or should I add the parenthetical ([28], [29],[etc]) onto each entry in the figure legends as well?}
-%\comment{Batch - add year next to author in text}
-% \comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
-
-% \cite{koning2005talys}.
-
-% \comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}
-
-% \comment{Add our 115In capture points? S}
-
-% \comment{Is the ''zoom'' appropriate for Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}?}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.65]{./figures/47sc_fixed_1point.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section relative to indium activation.}
- \label{fig:sc_xs}
-\end{figure}
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
-%  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
-%  \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
-%  \label{fig:cu_xs}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.65]{./figures/64cu_fixed_1point.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section relative to indium activation.}
- \label{fig:cu_xs_zoom}
-\end{figure}
-
-As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
-The results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
- This will be discussed in greater detail in the conclusion section below.
-
-% \comment{The capture cross sections are actually consistent with effective 2.45 MeV neutrons (which are still fast).
-For capture of 2.76 MeV neutrons, we predict (n,p) cross sections approx.
-15 mb less than using the In(n,n') monitors.
-How can we incorporate best this?
-Please suggest language changes / additions.
-Since they  are only consistent at 2.45 MeV, I removed the points from Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}, but will happily add them back if someone thinks they serve a purpose.}
-
-\section{Discussion}
-
-The proximity of the target to the neutron production surface opens the possibility of performing a measurement of the cross section over a limited energy range via mounting the samples slightly off-axis with respect to the beam.
- This could be accomplished using the 9-foil sample holder described in \autoref{sec:lee_sec} above.
- Mounting samples at each of these positions would subject the samples to neutrons with energies ranging from 2.765 MeV at the central location to 2.616 MeV at the four corners, with the other locations having intermediate energy values.
- These sorts of multi-sample measurements could be used to determine the \enquote{rising edge} of the cross sections, aiding in the development of optical models for the reactants.
-
-These measurements also highlight the possibility of using fast neutrons from DD and/or DT generators to produce meaningful quantities of radioisotopes for a wide range of applications via charge exchange reactions, such as (n,p) and (n,$\alpha$).
- Many applications, including diagnostic and therapeutic medical use, require mCi activity levels.
- The production of a radionuclide sample with an activity $A$ driven to secular equilibrium using a neutron source with a total flux $\phi$ and a reaction cross section $\sigma$ acting on sample of $N_{target}$ atoms is given by the expression:
-
-\begin{equation}
-A = \lambda N_{product} = \eta \phi \sigma N_{T}
-\end{equation}
-
-where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired reaction on one of the target sample atoms:
-
-% \begin{figure*}[H]
-% \hline
-% \begin{equation}
-% \eta = \int_0^E dE_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\phi} 4\pi r^2 dr d\pp{\cos{\theta}} d\theta
-% \end{equation}
-% \end{figure*}
-
-% \begin{strip}
-
-\begin{align}
-\eta &= \int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}, \nonumber\\
-\text{d}\mathbf{V} &= r^2 \text{d}r \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
-\end{align}
-% \end{strip}
-
-An optimal design for the neutron generator would also allow for the possibility of reflecting fast neutrons back onto the target to maximize their utilization for radionuclide production.
- This sort of \enquote{flux trap} has been used for the production of radionuclides in reactors, but has not to date been optimized for use with fast neutrons  at DD and/or DT neutron sources.
- The HFNG, with its self-loading target and \enquote{flux trap} geometry, has many features that make it well-suited for such isotope production purpose.
- Switching to DT operation would dramatically increase the flux as well as the production cross section, since (n,p) tends to be significantly larger at 14 MeV.
- However, the higher neutron energy would also open the (n,pn) channels.
- In the case of \ce{^{47}Sc}, this would lead to the presence of \ce{^{46}Sc} ($t_{1/2}$ = 83.79 d \cite{Wu2000}) in the sample, which might pose some concerns for medical applications.
- However, this is not an issue for \ce{^{64}Cu} since the (n,pn) channel leads to the production of stable \ce{^{63}Cu}.
-
- \section{Conclusion and Future Work}
-
-Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.76$^{+0.01}_{-0.02}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
-The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.26 $\pm$  0.82 mb and  49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
-
- In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
- While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
- This in turn highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
-The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
- In addition to improving the value of these measurements for nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
-
-% In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
- It is worth noting that at the time of publication, the  HFNG is now operating at close to 10$^9$ n/sec, with
-a clear path towards 10$^{10}$.
-%  In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
- Future work will involve the continued measurement of the (n,p) production cross sections for various other emerging therapeutic and diagnostic radioisotopes, to expand the toolset of options available for modern medical imaging and cancer therapy.
-This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments.
-
-%  \comment{Should we specifically mention other isotopes we plan to measure?}
+XXXXXX
 
@@
 
- We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
- We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
- Lastly, we would like to acknowledge the students in the Nuclear Reactions and Radiation (NE102) laboratory course at UC Berkeley who participated in these experiments, including Joe Corvino, Nizelle Fajardo, Scott Parker and Evan Still.
+ Stephen Graves - consulting for methodology, guidance.
 
- This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
+%  We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
+%  We wish to thank Marc Garland and Saed Mirzadeh for discussions regarding the use of neutron generators for isotope production.
+%  We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
+%  Lastly, we would like to acknowledge the students in the Nuclear Reactions and Radiation (NE102) laboratory course at UC Berkeley who participated in these experiments, including Joe Corvino, Nizelle Fajardo, Scott Parker and Evan Still.
+%  
+%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
 Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% \comment{Add NSF Grant number from P. Renne.}
+% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
 
@@
 % 
-% \appendix
+\appendix
 
-% \section{Data} \label{data}
+\section{Decay data} \label{data}
 % 
@@
 % % \end{longtable}
-% hello world
-
-% 
-% \section{Results} \label{equations}
-% 
-% Tabulated results are listed here, to avoid breaking text flow in the main text.
-% 
-% \begin{table}[h]
-% \centering
-% \caption{Transition conversion coefficients and efficiencies}
-% \label{my-label2}
-% \begin{tabular}{c|c|c|c|c}
-% Nucleus & Transition       & E\(_\gamma\) (keV) & \(\alpha\), Conversion Coefficient  & \(\epsilon\), Intrinsic Efficiency \\ \hline
-% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 0.0569           \(\pm\) 0.0008              & 1863.906   \\
-%         & 4\(\rightarrow\)2 & 422.6          & 0.00887          \(\pm\) 0.00013             & 1219.507   \\
-%         & 6\(\rightarrow\)4 & 575.7          & 0.00356          \(\pm\) 0.00005             & 956.569    \\ \hline
-% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 0.0205          \(\pm\) 0.0003              & 1340.054   \\
-%         & 4\(\rightarrow\)2 & 457.63         & 0.01154          \(\pm\) 0.00017             & 1142.505   \\
-%         & 6\(\rightarrow\)4 & 582.4          & 0.00593          \(\pm\) 0.00009             & 948.705    \\ \hline
-% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 0.00599         \(\pm\) 0.00009             & 926.624    \\
-%         & 4\(\rightarrow\)2 & 528.25         & 0.00848         \(\pm\) 0.00012             & 1019.604   \\
-%         & 6\(\rightarrow\)4 & 529.7          & 0.00842         \(\pm\) 0.00012             & 1017.470   \\ \hline
-% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 0.175           \(\pm\) 0.0025              & 2085.452   \\
-%         & 4\(\rightarrow\)2 & 330.88         & 0.0333         \(\pm\) 0.0005              & 1485.782   \\
-%         & 6\(\rightarrow\)4 & 431.3          & 0.015          \(\pm\) 0.00021             & 1199.258  
-% \end{tabular}
-% \end{table}
-% 
-% \begin{table}[h]
-% \centering
-% \caption{Extracted transition intensities}
-% \label{my-label}
-% \begin{tabular}{c|c|c|c|c|c}
-% Nucleus & Transition       & E\(_\gamma\) (keV) & \(A_{obs}\), Peak Area (a.u.)   & \(A_{source}\),  Peak Intensity (a.u.)  & \(R_i\), Relative Intensity  \\ \hline
-% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 1097    \(\pm\)   136        & 0.622          \(\pm\) 0.077             & 1.000              \(\pm\) 0.175                 \\
-%         & 4\(\rightarrow\)2 & 422.6          & 515     \(\pm\)   107        & 0.426          \(\pm\) 0.089             & 0.685              \(\pm\) 0.200                 \\
-%         & 6\(\rightarrow\)4 & 575.7          & 144      \(\pm\)  55         & 0.151          \(\pm\) 0.058             & 0.243              \(\pm\) 0.198                 \\ \hline
-% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 542     \(\pm\)   129        & 0.413          \(\pm\) 0.098             & 1.000              \(\pm\) 0.337                 \\
-%         & 4\(\rightarrow\)2 & 457.63         & 357       \(\pm\) 59         & 0.316          \(\pm\) 0.052             & 0.766              \(\pm\) 0.254                 \\
-%         & 6\(\rightarrow\)4 & 582.4          & 161       \(\pm\) 61         & 0.171          \(\pm\) 0.065             & 0.414              \(\pm\) 0.288                 \\ \hline
-% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 822       \(\pm\) 164        & 0.892          \(\pm\) 0.178             & 1.000              \(\pm\) 0.282                 \\
-%         & 4\(\rightarrow\)2 & 528.25         & 384       \(\pm\) 78         & 0.380          \(\pm\) 0.077             & 0.426              \(\pm\) 0.186                 \\
-%         & 6\(\rightarrow\)4 & 529.7          & 310       \(\pm\) 104        & 0.307          \(\pm\) 0.103             & 0.344              \(\pm\) 0.229                 \\ \hline
-% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 900       \(\pm\) 242        & 0.507          \(\pm\) 0.136             & 1.000              \(\pm\) 0.380                 \\
-%         & 4\(\rightarrow\)2 & 330.88         & 535       \(\pm\) 127        & 0.372          \(\pm\) 0.088             & 0.734              \(\pm\) 0.307                 \\
-%         & 6\(\rightarrow\)4 & 431.3          & 363       \(\pm\) 64         & 0.307          \(\pm\) 0.054             & 0.606              \(\pm\) 0.250                
-% \end{tabular}
-% \end{table}
-%     
-% \pagebreak
+Table of decay data used for observed gamma rays. 
 % 
 % 
-% 
-% \section{Supplemental Figures} \label{fit_figures}
-% 
-% The remaining figures of the fitted \(\gamma\)-ray transition photopeaks are included here for reference, to avoid over-cluttering the main text.
+\section{Measured excitation functions} \label{fit_figures}
+
+Plots of the cross sections measured in this work are presented here, in comparison with literature data and reaction modeling codes.
 % 
@@
 % %
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru422-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 422.6 keV peak and its surroundings.}
-% %  \label{fig:110Ru422}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru575-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 575.7 keV peak and its surroundings.}
-% %  \label{fig:110Ru575}
-% % \end{figure}
-% 
-% 
-% 
-% 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe376-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 376.7 keV peak and its surroundings.}
-% %  \label{fig:140Xe376}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe457-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 457.6 keV peak and its surroundings.}
-% %  \label{fig:140Xe457}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe582-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 582.3 keV peak and its surroundings.}
-% %  \label{fig:140Xe582}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Ba602-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Ba} 602.4 keV peak and its surroundings.}
-% %  \label{fig:140Ba602}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba199-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 199.3 keV peak and its surroundings.}
-% %  \label{fig:144Ba199}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba330-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 330.9 keV peak and its surroundings.}
-% %  \label{fig:144Ba330}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba431-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 431.3 keV peak and its surroundings.}
-% %  \label{fig:144Ba431}
-% % \end{figure}
-% 
-% 
-% 
-%     
-% \pagebreak
-% 
-% 
-% % \appendix
-% \section{Source Code} \label{source}
-% 
-% \begin{center}
-%  \texttt{gint.py} - Implementation of the Wilhelmy statistical model, used to estimate total transition intensities in the ground state band  of primary fission fragments
-% \end{center}
-% 
-% % \begin{lstlisting}
-% % \lstloadlanguages{Python}
-% 
-% % \lstinputlisting[linewidth=\columnwidth,language=Python,breaklines=true,frame=single]{./hw04/gint.py}
-% % % \end{lstlisting}
-% 
-% 
-% 
-% \begin{center}
-%  \texttt{hw04\_04.m} - used to process and plot statistical transition intensity curves
-% \end{center}
-% 
-%  
-% %   \lstinputlisting[frame=single]{./hw04/hw04_04.m}
-% 
-% 
-% % \begin{verbatim}[commandchars=\\\{\}]
-% % \verbatiminput{./HW01/test.txt}
-% % \end{verbatim}
-% 
-% %% The Appendices part is started with the command \appendix;
-% %% appendix sections are then done as normal sections
-% %% \appendix
-% 
-% %% \section{}
-% %% \label{}
-% 
-% %% References
-% %%
-% %% Following citation commands can be used in the body text:
-% %% Usage of \cite is as follows:
-% %%   \cite{key}         ==>>  [#]
-% %%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
 
@@
 % \thispagestyle{fancyTOC}
-
-% H. F. Aly et al., Microchim. Acta, vol. 59, no. 1, 1971.
-
-% K. S. Bhatki et al., J. Radioanal. Chem., vol. 2, no. 1-2, 1969.
-
-% T. H. Bokhari et al., J. Radioanal. Nucl. Chem., vol. 283, no. 2, 2010.
-
-% J. F. Briesmeister et al., Los Alamos National Laboratory, 1986.
-
-% A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.
-
-% H. Liskien et al., Nucl. Data Tables, vol 11, 1973.
-
-% M. R. Lewis et al., J. Nucl. Med., vol. 44, no. 8, Aug. 2003.
-
-% C. Müller et al., J. Nucl. Med., vol. 55, no. 10, Oct. 2014.
-
-% N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.   (EXFOR)
-
-% L. Pietrelli et al., J. Radioanal. Nucl. Chem., vol. 157, no. 2, 1992.
-
-% S. M. Qaim et al., IAEA Technical Reports Series No. 473, 2011.
-
-% T. Shimizu, et al, Ann. Nucl. Energy, vol. 31, no. 9, pp. 975-990, 2004.
-
-% T. Shimizu, et al, Nucl. Instruments Methods Phys. Res. Sect. A Accel. Spectrometers, Detect. Assoc. Equip., vol. 527, no. 3, pp. 543-553, 2004.
-
-% D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.
 

### 2017-11-16 nb_px_paper/nb_px_paper.tex
Finished first draft of Introduction section.

@@
 %% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-\documentclass[5p]{elsarticle}
+% \documentclass[5p]{elsarticle}
+% Good for final formatting  - two column
+% 
 % \documentclass[3p,times]{elsarticle}
-% \documentclass[3p]{elsarticle}
+\documentclass[3p]{elsarticle}
+% Good for proofing - single column
+%
 
@@
 \usepackage{multirow}
+
+\usepackage{lineno}
 
@@
 
+\author[uwm]{Stephen A. Graves}
+
 \author[lanl]{Francois M. Nortier}
@@
 %%
+%%  To-do list for comments
+%%
+\listoftodos
+
+%%
 %% Start line numbering here if you want
 %%
-% \linenumbers
-
-% \listoftodos
+\linenumbers
 
@@
 
-XXXXXX  \cite{Updegraff2013}.
+Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S.
+alone - a multi-billion dollar industry which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases \cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
+The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{18}F} \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many of the non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}.
+\comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?  I find conflicting descriptions in the literature.}
+ The future of nuclear medicine would appear to be the paradigm of personalized medicine - targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope of the same element, to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
+Candidate isotopes to fill these needs have been identified based on their decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields, to facilitate production in sufficient quantities for cell studies.
+
+However, one significant obstacle exists for both high-fidelity measurements of emerging medical radionuclides, as well as conventional isotope production: well-characterized  dosimetry standards.  
+This is particularly true for intermediate-energy charged particle beams, where there is currently a paucity of such well-characterized data. 
+Indeed, the development of new dosimetry standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
+Charged particle dosimetry data currently exists for low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but experimental data used for this evaluation is sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6-15\%) \cite{gul2001charged}.
+While work is needed to improve upon existing dosimetry data, the development of new dosimetry reactions can expand the available range of options for the monitoring of charged particle beams.
+
+Activation is one of the most fundamental techniques utilized in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field.
+While the specifics have branched into ever-more-detailed probes into the world of the nucleus, activation, at heart, deals with the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
+Monitor reactions have  historically been part of such activation experiments, and in the context of charged particle induced reactions, serve two valuable purposes, depending upon the energy regime in question.
+Between the reaction's energetic threshold  and the tail of its compound peak, the magnitude and shape of a monitor reaction's excitation function is rapidly changing with increasing incident particle energy.
+In this energy regime, a monitor reaction can be used to assign an energy bin to a thin irradiated target, especially when comparing between monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
+This is extremely useful, as it allows one to screen for and eliminate systematic errors based on energy assignment, though this sensitivity to energy precludes their reliability as a beam current monitor.
+
+Moving to the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
+In this regime, the monitor reaction offers little-to-no energy sensitivity. 
+In return for giving up the ability to assign energy positions, monitor reactions in the pre-equilibrium regime become extremely useful for monitoring the integral beam current incident upon the target.
+While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or electrically-isolated target in a Faraday cup), these measure the integrated current incident upon an entire target assembly.
+For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energy positions in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
+In these experiments, a series of monitor foils at each energy position allow one to measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude.
+Both of these purposes make well-characterized dosimetry an invaluable asset to any activation experiment.
+
+In practice, nearly any radioisotope can serve as a reaction monitor. 
+However, several characteristics are hallmarks of a reaction monitor worthy to be classified as a dosimetry standard.
+The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide has  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay radiation able to used to uniquely identify it during post-activation assay.
+Generally, this means selecting a radionuclide with a number of distinct gamma rays, as gamma spectroscopy is commonly used to identify and quantify reaction products.
+The decay radiation should preferably have high intensities, so that they show up as strong peaks during spectroscopy, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
+
+Care should be taken to avoid cases where a radionuclide which is one decay off of stability populates excited states in the excited daughter nucleus also populated in the decay to the daughter state from the opposite side of the valley of stability.
+This produces decay gamma rays with nearly exactly the same energy, making it difficult to disentangle production from both sides of stability.
+For example, $^\text{nat}$Ti(p,x)\ce{^{48}V} is commonly used as dosimetry for 5 \textless\ E \textless\ 30 MeV protons.
+The characteristic decay lines in \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) are the 983.525 keV ($I_\gamma=99.98\%$) and 1312.106 keV ($I_\gamma=98.2\%$) gammas, which are also seen in the decay of \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}), yielding  a 983.526 keV ($I_\gamma=100.1\%$) and 1312.120 keV ($I_\gamma=100.1\%$) line \cite{Burrows2006}.
+Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV,$I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
+However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma rays from another isobar nucleus.
+
+Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
+It is preferred that the nucleus have a lifetime which is sufficiently long-lived to ensure that it may be quantified  conveniently and leisurely after end-of-beam without the majority if it decaying away.
+In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
+For proper quantification, it is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
+A precise and well-established half-life is needed to properly correct for decay losses during production, as well as in between end-of-beam and the start of decay spectroscopy, but these are generally well-characterized.
+In practice, the weakest components of decay data are often the gamma ray intensities, which can routinely have uncertainties of 5\% or more.
+Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma ray intensity can make a significant reduction in measured cross section uncertainties.
+It is also of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
+This is typically mostly a concern for secondary neutrons produced through (z,xn) reactions on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
+Any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often a laborious task to separate out the fraction of secondary particles contributing to the total activation.
+
+Finally, from a targetry  perspective, it is preferable to use a target that is readily commercially available at an affordable price and is generally chemically inert - any significant chemical changes during target preparation (rapid oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
+Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
+For charged particle reactions, a thin target is desired for dosimetry, as thicker targets will cause more energy degradation and broaden the energy spectrum downstream of the target.
+% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
+
+% The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
+%  The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a,doi:10.1063/1.3267832}.
+%  The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
+%  In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
+% While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
+% 
+% 
+% The present work features a pair of cross section measurements for the production of two emerging non-standard medical radionuclides: the positron emitter \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and the single - photon emission computed tomography (SPECT) tracer \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+% \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
+% The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
+% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
+% In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
+% The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
+% This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
+% Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
+% In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
+
+% \comment{cite theranostic papers, etc}
+
+One monitor reaction which satisfies these requirements is that of a new, intermediate-energy proton dosimetry standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
+Niobium is naturally monoisotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
+\ce{^{90}Mo} also has excellent decay properties - its fairly long-lived half-life ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
+In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
+
+The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo} ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) via the $^\text{nat}$Nb(p,x) reaction. 
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 32 other (p,x) production cross sections between 40 -- 90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
+These include the non-standard positron emission tomography (PET) emitters \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}),  \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}), the $\beta^-$-therapy agent  \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}),  and the Auger-therapy agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
+
+  \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
+
+In addition to the interest in the production of \ce{^{90}Mo} as an intermediate-energy dosimetry standard, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of a number of isomer-to-ground state ratios.
+These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$ m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$ d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$ h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$ d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$ h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$ h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$ m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$ h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
+
+This measurement has taken place using a set of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here.
+By expanding the available set of dosimetry standards and well-characterized isotope production excitation functions, great advances are possible for improving the  available options for modern medical imaging and cancer therapy.
 
@@
 
-\subsection{Proton dosimetry}\label{sec:spectroscopy}
+\subsection{Proton dosimetry}\label{sec:dosimetry}
 
@@
 
- Stephen Graves - consulting for methodology, guidance.
+%  Stephen Graves - consulting for methodology, guidance.
+
+ Michael Gallegos and Don Dry in the C-NR Countroom, David Reass and Mike Connors at IPF, and the LANSCE Accelerator Operations staff
 

### 2017-11-20 nb_px_paper/nb_px_paper.tex
Added Amanda as coauthor, mostly finished section 2.1

@@
 % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-\author[ucb]{A.S. Voyles \corref{cor1}}
+\author[ucb]{Andrew S. Voyles \corref{cor1}}
 \ead{andrew.voyles@berkeley.edu}
@@
 
-\author[uwm]{Stephen A. Graves}
+\author[iowa]{Stephen A. Graves}
+
+\author[ucb]{Amanda M. Lewis}
 
@@
 \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
+\address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
 
@@
 
-XXXXXX
+The well-known stacked-target design was utilized for this work, in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Graves2016}.
+For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
+Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized - for each foil, length and width measurements were taken at four different locations using a Mitutoyo caliper, thickness measurements were taken at four different locations using a Mitutoyo micrometer, and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
+Using these length, width, and mass readings, the areal density (in mg/cm$^2$) for each foil was calculated, along with the propagated uncertainty in areal density.
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape - each piece of tape consists of 43.2 \micro m of a silicone adhesive on 25.4 \micro m of a polyimide backing.
+The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame, and one \ce{^{nat}Al}, one \ce{^{nat}Cu}, and \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
+These foil packet bundles were lowered into the beam line by inserting them into a  water-cooled production target box.
+% These six foil packet bundles were inserted into one of six  
+The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor - after end-of-beam (EoB), $\beta$ particles emitted from these activated stainless steel foils may be used to develop Gafchromic film, revealing the spatial profile of the beam entering and exiting the stack.
+After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
+The specifications of the target stack design for this work is presented in \autoref{tab:stack_table}.
 
-% \begin{figure}
-%     \centering
-%         \centering
-%         \includegraphics[height=2in]{./figures/cutaway.png}
-%         \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
-%                 \label{fig:hfng_b}
-% \end{figure}
+This target stack was assembled and
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.1,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
+ % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
+ \caption{Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place.
+The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell.
+The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.
+}
+ \label{fig:target_stack}
+\end{figure}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[h]
+\centering
+\caption{Specifications of the  target stack design in the present work.
+The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here.
+The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$, but their areal densities are not listed here due to the variance minimization techniques described in this work.}
+\label{tab:stack_table}
+\begin{tabular}{@{}llll@{}}
+\toprule
+% Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
+Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
+SS profile monitor & 249.8 \micro m         & 194.555                                      & 0.290                      \\
+Al-1               & 25.0 \micro m          & 6.519                                        & 0.724                      \\
+Cu-1               & 61.3 \micro m          & 53.736                                       & 0.053                      \\
+Nb-1               & 30.0 \micro m          & 23.205                                       & 0.073                      \\
+Al Degrader 01     & 4.96 mm           & -                                            & -                          \\
+Al-2               & 25.5 \micro m          & 6.484                                        & 0.364                      \\
+Cu-2               & 61.8 \micro m          & 53.849                                       & 0.169                      \\
+Nb-2               & 30.8 \micro m          & 22.905                                       & 0.166                      \\
+Al Degrader 02     & 4.55 mm           & -                                            & -                          \\
+Al-3               & 25.8 \micro m          & 6.472                                        & 0.314                      \\
+Cu-3               & 61.5 \micro m          & 53.984                                       & 0.113                      \\
+Nb-3               & 31.0 \micro m          & 22.906                                       & 0.235                      \\
+Al Degrader 03     & 3.52 mm           & -                                            & -                          \\
+Al-4               & 26.3 \micro m          & 6.505                                        & 0.407                      \\
+Cu-4               & 61.3 \micro m          & 53.463                                       & 0.221                      \\
+Nb-4               & 30.8 \micro m          & 22.550                                       & 0.245                      \\
+Al Degrader 04     & 3.47 mm           & -                                            & -                          \\
+Al-5               & 26.5 \micro m          & 6.479                                        & 0.296                      \\
+Cu-5               & 61.5 \micro m          & 53.572                                       & 0.108                      \\
+Nb-5               & 30.8 \micro m          & 22.110                                       & 0.248                      \\
+Al Degrader 05     & 3.46 mm           & -                                            & -                          \\
+Al-6               & 26.3 \micro m          & 6.475                                        & 0.624                      \\
+Cu-6               & 62.0 \micro m          & 53.836                                       & 0.318                      \\
+Nb-6               & 31.3 \micro m          & 22.120                                       & 0.130                      \\
+SS profile monitor & 124.4 \micro m         & 101.336                                      & 0.226                      \\ \bottomrule
+\end{tabular}
+\end{table}
 

### 2017-11-21 nb_px_paper/nb_px_paper.tex
Finished section 2.1

@@
 
+Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A$\approx$ 190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
 In addition to the interest in the production of \ce{^{90}Mo} as an intermediate-energy dosimetry standard, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of a number of isomer-to-ground state ratios.
@@
 
-This target stack was assembled and
+\comment{Confirm beam parameters below, from notebook}
+
+This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
+The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a \textred{100 \micro s pulse at a frequency of 1 Hz}, for an anticipated integral current of 205.9 nAh.
+The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
+At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
+The activated foils were cleaned of all surface contamination, and transported to a counting lab for decay spectroscopy, which started approximately 7 hours following end-of-beam.
 

### 2017-11-23 nb_px_paper/nb_px_paper.tex
Added data tables to decay appendix, added figures to figure appendices

@@
 % \usepackage{mathtools}
-% \usepackage{natbib}
+\usepackage{natbib}
 % \usepackage{biblatex}
@@
 
-% \biboptions{}
+\biboptions{sort&compress}
 
@@
 The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here.
-The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$, but their areal densities are not listed here due to the variance minimization techniques described in this work.}
+The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$, but their areal densities are not listed here due to the variance minimization techniques utilized  in this work.}
 \label{tab:stack_table}
@@
 
-XXXXXX
+\comment{get citation data for UNISAMPO}
+
+Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma ray spectroscopy.
+For consistency, a single detector was used in this measurement, an ORTEC GEM Series  High-Purity Germanium (HPGe) detector.
+The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
+Samples were counted at fixed positions ranging 4.5 - 83.5  cm from the front face of the detector, with a series of standard calibration sources used to determine in-house energy, efficiency, and pileup calibrations for each position.
+The foils were counted for a period of 2 weeks following EoB, to accurately quantify all induced activities.
+An example gamma ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
+For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \textred{(add UNISMPO citation)}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=6in]{./figures/sample_gspec.pdf}
+ % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
+ \caption{Example gamma spectra, collected from an activated Nb foil at approximately 80 MeV, to monitor radioisotope production.
+While the majority of observed reaction products are visible in this spectrum, it is particularly noteworthy that the \ce{^{90}Mo} decay lines which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction are high in intensity and clearly isolated from surrounding peaks, greatly aiding its activity quantification.}
+ \label{fig:gspec}
+\end{figure}
+
+Following  acquisition, each observed peak in the collected spectra was
+
+identify all peaks, first observable in mass chain  = cumulative, all others are indepp
+
+These efficiencies, along with gamma ray intensities for each transition, were used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
 
@@
 
+ \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers.}
+
 %  We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
@@
 % % \end{longtable}
-Table of decay data used for observed gamma rays. 
+Table of decay data used for observed gamma rays \cite{Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012}.
+
+\comment{add citation for NDS A=22,24,93}
+
+\comment{I had to remove about 30 of the lines I used from this table (removing the weakest lines in nuclides with even more lines than shown here, but never removing lines in nuclides with only 2 or less), as even splitting the data into 2 tables created tables too large to fit on a single page.
+My purpose here was 1) to show that I used multiple lines to quantify each nuclide (increasing confidence in results), and 2) to list all the used \ce{^{90}Mo} lines, since they form the basis of it as a monitor.
+Is this good as is, or should it be pared down even more?}
+
+% Preview source code for paragraph 0
+
+\begin{table}[ht]
+\centering
+\caption{Decay data for gamma rays observed in \ce{^{nat}Al}(p,x) and \ce{^{nat}Cu}(p,x).}
+\label{tab:nudat_table_monitors}
+\begin{tabular}{@{}llll@{}}
+\toprule
+% \begin{tabular}{|c|c|c|c|}
+% \hline 
+Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
+\midrule
+\ce{^{22}Na} & 2.6018(22) y & 1274.537 & 99.940(14)\\
+
+\ce{^{24}Na} & 14.997(12) h & 1368.626 & 99.9936(15)\\
+
+\ce{^{51}Cr} & 27.704(3) d & 320.0824 & 9.910(10)\\
+
+\ce{^{52m}Mn} & 21.1(2) m & 1434.0600 & 98.2(5)\\
+
+\ce{^{52}Mn} & 5.591(3) d & 744.233 & 90.0(12)\\
+
+ & 5.591(3) d & 935.544 & 94.5(13)\\
+
+ & 5.591(3) d & 1246.278 & 4.21(7)\\
+
+ & 5.591(3) d & 1434.092 & 100.0(14)\\
+
+\ce{^{54}Mn} & 312.20(20) & 834.848 & 99.9760(10)\\
+
+\ce{^{55}Co} & 17.53(3) h & 477.2 & 20.2(17)\\
+
+ & 17.53(3) h & 931.1 & 75.0(35)\\
+
+ & 17.53(3) h & 1316.6 & 7.1(3)\\
+
+ & 17.53(3) h & 1408.5 & 16.9(8)\\
+
+\ce{^{56}Ni} & 6.075(10) d & 158.38 & 98.8(10)\\
+
+ & 6.075(10) d & 269.50 & 36.5(8)\\
+
+ & 6.075(10) d & 480.44 & 36.5(8)\\
+
+ & 6.075(10) d & 749.95 & 49.5(12)\\
+
+ & 6.075(10) d & 811.85 & 86.0(9)\\
+
+ & 6.075(10) d & 1561.80 & 14.0(6)\\
+
+\ce{^{56}Co} & 77.236(26) d & 846.770 & 99.9399(2)\\
+
+%  & 77.236(26) d & 977.372 & 1.421(6)\\
+
+ & 77.236(26) d & 1037.843 & 14.05(4)\\
+
+ & 77.236(26) d & 1238.288 & 66.46(12)\\
+
+ & 77.236(26) d & 1360.212 & 4.283(12)\\
+
+ & 77.236(26) d & 1771.357 & 15.41(6)\\
+
+\ce{^{57}Ni} & 35.60(6) h & 127.164 & 16.7(5)\\
+
+ & 35.60(6) h & 1377.63 & 81.7(24)\\
+
+ & 35.60(6) h & 1757.55 & 5.75(20)\\
+
+ & 35.60(6) h & 1919.52 & 12.3(4)\\
+
+\ce{^{57}Co} & 271.74(6) d & 122.06065 & 85.60(17)\\
+
+ & 271.74(6) d & 136.47356 & 10.68(8)\\
+
+\ce{^{58}Co} & 70.86(6) d & 810.7593 & 99.450(10)\\
+
+ & 70.86(6) d & 863.951 & 0.686(10)\\
+
+%  & 70.86(6) d & 1674.725 & 0.517(10)\\
+
+\ce{^{59}Fe} & 44.495(9) d & 1099.245 & 56.5(18)\\
+
+ & 44.495(9) d & 1291.590 & 43.2(14)\\
+
+\ce{^{60}Co} & 5.2714(5) y & 1173.228 & 99.85(3)\\
+
+ & 5.2714(5) y & 1332.492 & 99.9826(6)\\
+
+\ce{^{61}Cu} & 3.339(8) h & 282.956 & 12.2(2.2)\\
+
+ & 3.339(8) h & 373.050 & 2.1(4)\\
+
+%  & 3.339(8) h & 588.605 & 1.17(21)\\
+
+ & 3.339(8) h & 656.008 & 10.8(20)\\
+
+ & 3.339(8) h & 1185.234 & 3.7(7)\\
+
+\ce{^{62}Zn} & 9.193(15) h & 243.36 & 2.52(23)\\
+
+ & 9.193(15) h & 246.95 & 1.90(18)\\
+
+ & 9.193(15) h & 260.43 & 1.35(13)\\
+
+%  & 9.193(15) h & 304.88 & 0.29(3)\\
+
+%  & 9.193(15) h & 349.60 & 0.45(4)\\
+
+ & 9.193(15) h & 394.03 & 2.24(17)\\
+
+ & 9.193(15) h & 548.35 & 15.3(14)\\
+
+ & 9.193(15) h & 596.56 & 26.0(20)\\
+
+%  & 9.193(15) h & 637.41 & 0.25(3)\\
+
+\ce{^{64}Cu} & 12.701(2) h & 1345.77 & 0.475(11)\\
+
+\ce{^{65}Zn} & 243.93(9) d & 1115.539 & 50.04(10)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\caption{Decay data for gamma rays observed in \ce{^{nat}Nb}(p,x).}
+\label{tab:nudat_table_nb}
+\begin{tabular}{@{}llll@{}}
+\toprule
+% \begin{tabular}{|c|c|c|c|}
+% \hline 
+Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
+\midrule
+\ce{^{82m}Rb} & 6.472(6) h & 554.35 & 62.4(9)\\
+
+ & 6.472(6) h & 619.11 & 37.98(9)\\
+
+%  & 6.472(6) h & 698.37 & 26.3(7)\\
+
+ & 6.472(6) h & 776.52 & 84.39(21)\\
+
+ & 6.472(6) h & 1044.08 & 32.07(8)\\
+
+%  & 6.472(6) h & 1317.43 & 23.7(6)\\
+
+\ce{^{83}Sr} & 32.41(3) h & 418.37 & 4.2(3)\\
+
+ & 32.41(3) h & 762.65 & 26.7(22)\\
+
+\ce{^{85m}Y} & 4.86(13) h & 231.7 & 22.8(22)\\
+
+\ce{^{85}Y} & 2.68(5) h & 231.65 & 84(9)\\
+
+ & 2.68(5) h & 913.89 & 9.0(9)\\
+
+\ce{^{86}Zr} & 16.5(1) h & 242.8 & 95.84(2)\\
+
+ & 16.5(1) h & 612.0 & 5.8(3)\\
+
+% \ce{^{86}Y} & 14.74(2) h & 187.87 & 1.26(4)\\
+\ce{^{86}Y}  & 14.74(2) h & 443.13 & 16.9(5)\\
+
+%  & 14.74(2) h & 190.80 & 1.01(3)\\
+
+%  & 14.74(2) h & 307.00 & 3.47(8)\\
+
+%  & 14.74(2) h & 443.13 & 16.9(5)\\
+
+%  & 14.74(2) h & 580.57 & 4.78(14)\\
+
+%  & 14.74(2) h & 608.29 & 2.01(15)\\
+
+ & 14.74(2) h & 627.72 & 32.6(1)\\
+
+%  & 14.74(2) h & 703.33 & 15.4(4)\\
+
+%  & 14.74(2) h & 709.90 & 2.62(8)\\
+
+%  & 14.74(2) h & 767.63 & 2.4(3)\\
+
+%  & 14.74(2) h & 835.67 & 4.4(6)\\
+
+%  & 14.74(2) h & 1024.04 & 3.79(17)\\
+
+ & 14.74(2) h & 1076.63 & 82.5(4)\\
+
+ & 14.74(2) h & 1153.05 & 30.5(9)\\
+
+%  & 14.74(2) h & 1163.03 & 1.18(4)\\
+%  
+%  & 14.74(2) h & 1253.11 & 1.53(5)\\
+
+%  & 14.74(2) h & 1349.15 & 2.95(9)\\
+
+ & 14.74(2) h & 1854.38 & 17.2(5)\\
+
+ & 14.74(2) h & 1920.72 & 20.8(7)\\
+
+\ce{^{87}Zr} & 1.68(1) h & 380.79 & 62.79(10)\\
+
+ & 1.68(1) h & 1227.0 & 2.80(4)\\
+
+\ce{^{87m}Y} & 13.37(1) h & 380.79 & 78.05(8)\\
+
+\ce{^{87}Y} & 79.8(3) h & 388.5276 & 82.2(7)\\
+
+ & 79.8(3) h & 484.805 & 89.8(9)\\
+
+\ce{^{88}Zr} & 83.4(3) d & 392.87 & 97.29(14)\\
+
+\ce{^{88}Y} & 106.627(21) d & 898.042 & 93.7(3)\\
+
+ & 106.627(21) d & 1836.063 & 99.2(3)\\
+
+\ce{^{89m}Nb} & 66(2) m & 588.0 & 95.57(13)\\
+
+\ce{^{89}Nb} & 2.03(7) h & 1511.4 & 1.9(4)\\
+
+ & 2.03(7) h & 1627.2 & 3.5(7)\\
+
+ & 2.03(7) h & 1833.4 & 3.3(7)\\
+
+\ce{^{89}Zr} & 78.41(12) h & 909.15 & 99.04(3)\\
+
+ & 78.41(12) h & 1713.0 & 0.745(13)\\
+
+%  & 78.41(12) h & 1744.5 & 0.123(4)\\
+
+\ce{^{90}Mo} & 5.56(9) h & 122.370 & 64(3)\\
+
+ & 5.56(9) h & 162.93 & 6.0(6)\\
+
+ & 5.56(9) h & 203.13 & 6.4(6)\\
+
+ & 5.56(9) h & 257.34 & 78(4)\\
+
+ & 5.56(9) h & 323.20 & 6.3(6)\\
+
+ & 5.56(9) h & 472.2 & 1.42(16)\\
+
+ & 5.56(9) h & 941.5 & 5.5(7)\\
+
+\ce{^{90}Nb} & 14.6(5) h & 132.716 & 4.13(4)\\
+
+ & 14.6(5) h & 141.178 & 66.8(7)\\
+
+%  & 14.6(5) h & 890.64 & 1.80(4)\\
+
+ & 14.6(5) h & 1611.76 & 2.38(7)\\
+
+%  & 14.6(5) h & 1913.194 & 1.280(17)\\
+
+\ce{^{91m}Nb} & 60.86(22) d & 104.62 & 0.574(1)\\
+
+ & 60.86(22) d & 1204.67 & 2.0(3)\\
+
+\ce{^{92m}Nb} & 10.15(2) d & 912.6 & 1.78(10)\\
+
+ & 10.15(2) d & 934.44 & 99.15(4)\\
+
+\ce{^{93m}Mo} & 6.85(7) d & 263.049 & 57.4(11)\\
+
+ & 6.85(7) d & 684.693 & 99.9(8)\\
+
+ & 6.85(7) d & 1477.138 & 99.1(11)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 % 
@@
 
-Plots of the cross sections measured in this work are presented here, in comparison with literature data and reaction modeling codes.
+Plots of the cross sections measured in this work are presented here, in comparison with literature data and reaction modeling codes \cite{Koning2012,Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}.
+
+\comment{add EMPIRE citation here!}
+
+\comment{add TENDL citation here!}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/51Cr.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:51Cr}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.465]{}{./figures/52gMn.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:52gMn}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/54Mn.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:54Mn}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/55Co.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:55Co}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.465]{}{./figures/56Ni.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:56Ni}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/57Co.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:57Co}
+    \end{subfigure}%
+%     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+     \label{fig:xs_curves_p1}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/57Ni.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:57Ni}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.47]{}{./figures/58Co.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:58Co}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.465]{}{./figures/59Fe.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:59Fe}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/60Co.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:60Co}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/61Cu.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:61Cu}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/64Cu.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:64Cu}
+    \end{subfigure}%
+%     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+     \label{fig:xs_curves_p2}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/82mRb.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:82mRb}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.47]{}{./figures/83Sr.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:83Sr}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/85Y.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:85Y}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/86Y.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:86Y}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/86Zr.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:86Zr}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/87Y.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:87Y}
+    \end{subfigure}%
+%     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+     \label{fig:xs_curves_p3}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/87Zr.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:87Zr}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.47]{}{./figures/88Y.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:88Y}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/88Zr.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:88Zr}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/89Nb.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:89Nb}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/89Zr.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:89Zr}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.465]{}{./figures/90Mo.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:90Mo}
+    \end{subfigure}%
+%     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+     \label{fig:xs_curves_p4}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/90Nb.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:90Nb}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.47]{}{./figures/91mNb.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:91mNb}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/92mNb.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:92mNb}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/93mMo.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:93mMo}
+    \end{subfigure}%
+%     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+     \label{fig:xs_curves_p5}
+\end{figure*}
+
+% 
+% 
+\section{Measured isomer-to-ground state branching ratios } \label{ibr_figures}
+
+Plots of the isomer-to-ground state ratios measured in this work are presented here, in comparison with literature data and reaction modeling codes \cite{MICHEL1997153,Ditroi2008,Titarenko2011,Graves2016}.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/52Mn_IBR.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:52Mn_IBR}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.47]{}{./figures/58Co_IBR.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:58Co_IBR}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/85Y_IBR.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:85Y_IBR}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.47]{}{./figures/87Y_IBR.pdf}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:87Y_IBR}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[scale=0.47]{}{./figures/89Nb_IBR.pdf}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:89Nb_IBR}
+    \end{subfigure}
+     \label{fig:ibr_curves}
+\end{figure*}
+
 % 

### 2017-11-25 nb_px_paper/nb_px_paper.tex
Finished section 2.2

@@
 
+\newcommand{\etal}{\emph{et al.}}
+
 % Tweak sim for better inline text tilde
@@
 
-Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A$\approx$ 190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
+Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A $\approx$ 190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
 In addition to the interest in the production of \ce{^{90}Mo} as an intermediate-energy dosimetry standard, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of a number of isomer-to-ground state ratios.
@@
 
+While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work follows their established methods for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.
+
 \subsection{Stacked-target design }\label{sec:target_design}
@@
 
-The well-known stacked-target design was utilized for this work, in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Graves2016}.
+The well-known stacked-target design was utilized for this work, in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation.
 For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
@@
 % \usepackage{booktabs}
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
  \centering
@@
 
-Following  acquisition, each observed peak in the collected spectra was
-
-identify all peaks, first observable in mass chain  = cumulative, all others are indepp
-
-These efficiencies, along with gamma ray intensities for each transition, were used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
+Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
+The calibrated detector efficiencies, along with gamma ray intensities for each transition, were used to convert the net  counts in each fitted gamma ray photopeak into an activity for the activated isotopes and isomeric states.
+For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+As nearly all of the product nuclei created in this work have multiple high-intensity gamma rays, each product nuclei had measurements of its present activity at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma rays.
+The measured activity for each gamma ray possesses a total propagated uncertainty which is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma ray branching ratio data.
+
+\comment{Add 1st and 2nd order bateman stuff here, maybe cite Cetnar2006 also }
+
+Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly produced by decay down a mass chain.
+To this end, it is useful to differentiate between the types of cross sections reported in this work. 
+For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its decay precursors and any other independent cross sections leading to that nucleus.
+In addition, cumulative cross sections will be reported whenever it is impossible to use decay spectroscopy to distinguish direct production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, independent cross sections ($\sigma_i$) will be reported, leaving solely direct nucleus production by subtracting out the feeding of decay precursors.
+
+To convert these activities into cross sections, corrections must be made for the decay of the various reaction products in  between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB.
+The use of  multiple gamma rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma ray observation.
+For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points to the well-known radioactive decay law.
+% \begin{equation}
+% A\pp{t} = A_0 e^{-\lambda t}
+% \end{equation}
+Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ would be reported as as well.
+As with the gamma ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+In the case of independent cross sections, a similar process was followed, instead regressing to the solutions to the Bateman equation:
+\begin{equation}
+A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_i\pp{0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
+\end{equation}
+While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
+\begin{equation}
+A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
+\end{equation}
+In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, that the feeding contributions from decay could be separated and an independent cross section reported.
+After quantifying the cumulative EoB activities at the top of a mass chain, and all subsequent independent EoB activities, these would be later used to report the various cross sections for all observed reaction products and isomeric states.
 
@@
 % % \end{longtable}
-Table of decay data used for observed gamma rays \cite{Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012}.
+Table of decay data  for observed gamma rays. 
+The  values for lifetime and gamma ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012}.
 
@@
 
-Plots of the cross sections measured in this work are presented here, in comparison with literature data and reaction modeling codes \cite{Koning2012,Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}.
+Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \textred{(cite me!)}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Koning2012}.
 

### 2017-11-26 nb_px_paper/nb_px_paper.tex
Finished section 2.3

@@
 %%
-\title{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on Nb and Cu}
+\title{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu}
 
@@
 The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame, and one \ce{^{nat}Al}, one \ce{^{nat}Cu}, and \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
-These foil packet bundles were lowered into the beam line by inserting them into a  water-cooled production target box.
+These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
 % These six foil packet bundles were inserted into one of six  
@@
 As with the gamma ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-In the case of independent cross sections, a similar process was followed, instead regressing to the solutions to the Bateman equation:
+In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation:
 \begin{equation}
@@
 In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, that the feeding contributions from decay could be separated and an independent cross section reported.
-After quantifying the cumulative EoB activities at the top of a mass chain, and all subsequent independent EoB activities, these would be later used to report the various cross sections for all observed reaction products and isomeric states.
+After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
 
@@
 
-XXXXXX
+As discussed previously, accurate proton dosimetry is the most important factor in performing high-fidelity cross section measurements.
+At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline possess resolution of 100 nAh.
+For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional dosimetry is thus needed to accurately normalize quantified EoB activities into cross sections.
+To this end, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
+These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions have been well-characterized for accurate proton fluence measurement \cite{gul2001charged}.
+The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
+Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution is expected for all monitor and target foils.
+As a result, the integral form of the well-known activation equation is used to accurately determine proton fluence ($I \Delta t $) in each monitor foil by convolving the IAEA recommended cross section values with the proton energy distribution:
+% \begin{equation}
+% A_0 = I\ \rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE
+% \end{equation}
+\begin{equation}
+I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
+\end{equation}
+where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy E, and $\frac{d\phi}{dE}$ is the differential proton fluence.
+Using this formalism, the quantified EoB activities for each monitor reaction may be converted into a measured proton fluence at each energy position.
+
+\comment{Add missing citations here}
+
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in proton fluence.
+Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
+The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
+The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
+Fortunately, the recommended cross section values for each monitor reaction tend to match one of the   selected experimental data sets used in their evaluation almost perfectly.
+Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
+For the monitor reactions employed in this work, these data sets are G.
+Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \textred{(insert Steyn citation here)}, M.
+Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S.
+Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.
 

### 2017-12-02 nb_px_paper/nb_px_paper.tex
Started section 2.4

@@
 %% keywords here, in the form: keyword \sep keyword
-Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor foils \sep Medical isotope production \sep MCNP \sep  LANL
+Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
 
@@
 The use of  multiple gamma rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma ray observation.
-For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points to the well-known radioactive decay law.
+For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
 % \begin{equation}
@@
 
-XXXXXX
+Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
+These estimates of average beam energy in each foil are useful for the preliminary stack design, as the A\&Z calculation provide reasonable approximations of 1-D proton transport due to its treatment of ionization and multiple Coulomb scattering.
+However, for final energy determination and analysis, a more rigorous method of proton transport is needed.
+The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, and is used to calculate a full proton energy distribution for each stack position   \cite{Goorley2012}.
+In addition, MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to reactions, as well as production of secondary particles.
+As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated - $10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
+The ability to model the full energy distribution in each target position is vital for stacked target irradiations, due to the progressively larger energy straggling towards the rear of the stack.
+The initial proton beam has a finite energy spread (an approximately 0.1 MeV Gaussian width at 100 MeV), and since stopping power for charged particles is inversely proportional to their energy, the low-energy tail of the energy distribution is degraded more in each stack element than the high-energy tail.
+This effect compounds as one moves towards the rear of the stack, with the effect of a significantly broadened low-energy tail relative to the high-energy tail, and a progressively larger net shift of the centroid to a lower energy than the peak of the energy distribution.
+% For each foil in the target stack, 
+To account for this increasing energy uncertainty, a suitably representative energy must be established for  each foil in the target stack.
+In this work, the flux-weighted average proton  energy, $\langle E \rangle$, in each foil is calculated to represent the energy centroid for protons in a target stack component, based on the energy distributions $\frac{d\phi}{dE}$ from MCNP6 modeling of proton transport:
+\begin{equation}
+\langle E \rangle = \dfrac{{\displaystyle\int E \dfrac{d\phi}{dE} dE}}{{\displaystyle\int \dfrac{d\phi}{dE} dE}}
+\end{equation}
+Likewise, to represent the energy uncertainty for each stack position, the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution is chosen for each energy position reported.
+While most experimental uncertainties are reported at the 1$\sigma$ level, the $\approx2.3\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy center-of-mass.
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{h}
+ \label{fig:h}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[scale=.8]{./figures/Nb_ptallies.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{hh}
+ \label{fig:hh}
+\end{figure}
+
+comment that  peak-to-tail ratio increases
 
@@
  Michael Gallegos and Don Dry in the C-NR Countroom, David Reass and Mike Connors at IPF, and the LANSCE Accelerator Operations staff
+
+ This research used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
 

### 2017-12-05 nb_px_paper/nb_px_paper.tex
Finished section 2.4

@@
 
-The well-known stacked-target design was utilized for this work, in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation.
+The well-known stacked-target design was utilized for this work, in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
 For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
@@
 Using these length, width, and mass readings, the areal density (in mg/cm$^2$) for each foil was calculated, along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape - each piece of tape consists of 43.2 \micro m of a silicone adhesive on 25.4 \micro m of a polyimide backing.
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape - each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.793 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.607 mg/cm$^2$).
 The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame, and one \ce{^{nat}Al}, one \ce{^{nat}Cu}, and \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
@@
 
-\begin{figure}[h]
+\begin{figure}
  \centering
@@
 % \usepackage{booktabs}
-\begin{table}[ht]
+\begin{table}
 \centering
@@
 
-\begin{figure}[ht]
+\begin{figure}
  \centering
@@
 As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated - $10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
+
 The ability to model the full energy distribution in each target position is vital for stacked target irradiations, due to the progressively larger energy straggling towards the rear of the stack.
@@
 To account for this increasing energy uncertainty, a suitably representative energy must be established for  each foil in the target stack.
-In this work, the flux-weighted average proton  energy, $\langle E \rangle$, in each foil is calculated to represent the energy centroid for protons in a target stack component, based on the energy distributions $\frac{d\phi}{dE}$ from MCNP6 modeling of proton transport:
+In this work, the flux-weighted average proton  energy in each foil, $\langle E \rangle$,  represents the energy centroid for protons in a target stack component, calculated using the energy distributions $\frac{d\phi}{dE}$ from MCNP6 modeling of proton transport:
 \begin{equation}
@@
 
-\begin{figure}[ht]
+Based on the recent work of Graves \etal, the \enquote{variance minimization} techniques they outline have been employed here, to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
+This method is based on the assumption that the independent measurements of proton fluence from the 5 monitor reactions used in this work should all be consistent at each energy position.
+If the monitor reaction cross sections and MCNP6 - modeled energy distributions are both accurate, then any disagreement in the  observed proton fluences is due to a systematic uncertainty in the stack design, namely, the areal densities of the stack components \cite{Graves2016,Marus2015}.
+This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
+
+To correct for this, variance minimization techniques were employed here to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
+Due to the difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values, but this had negligible impact on improving monitor reaction disagreement.
+This is due to the minor impact that their areal density has on beam degradation, relative to the thick 6061 aluminum degraders (nominal 3-5 mg/cm$^2$, relative to nominal 1000-1400 mg/cm$^2$).
+As such,  the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
+This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
+The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position, approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
+This energy corresponds to a 6061 aluminum areal density of 2.53\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
+
+The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
+As expected, the 2.53\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
+In addition, as one moves to the rear energy positions, the disagreement in the independent proton fluence measurements is reduced.
+It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
+This phenomenon is observed for the \ce{^{nat}Cu}(p,x)\ce{^{56}Co} monitor reaction as well, though to a much smaller degree.
+In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
+Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils.
+The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively - the fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
+This serves as an example of the importance of selecting monitor reaction products inaccessible through (n,x) channels, as noted previously.
+However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of the secondary neutron flux.
+
+\begin{figure}
  \centering
@@
  % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{h}
- \label{fig:h}
+ \caption{Result of variance minimization, performed by varying the degrader density in MCNP6 simulations of the target stack.
+A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.53\% greater than nominal.
+The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
+ \label{fig:variation_curve}
 \end{figure}
 
-\begin{figure}[ht]
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.59]{a)}{./figures/before_minimization_plot.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:before_minimization}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.59]{b)}{./figures/after_minimization_plot.pdf}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:after_minimization}
+    \end{subfigure}%
+    \caption{Results of variance minimization through enhancement of 6061 aluminum effective areal density by 2.53\%.
+A noticeable reduction of variance in measured proton fluence is seen, in particular at the low-energy rear positions of the stack.
+The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} monitor channels is caused by activation through (n,x) reactions from the secondary neutron flux.
+By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
+     \label{fig:variance_mins}
+\end{figure*}
+
+Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the 6 irradiated Nb foils in \autoref{fig:Nb_ptallies}.
+As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as result of the beam energy degradation.
+In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail-ratio increases as more  secondary protons are produced upstream.
+As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.
+
+An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the  \ce{^{nat}Al}(p,x)\ce{^{24}Na} observed fluence (the upper set of points), and the uncertainty-weighted average fluence from the  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn} and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions (the lower set of points).
+To determine the final fluence assignments for the Nb foils, uncertainty-weighted linear regression was used to fit the various fluence measurements, minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
+As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
+% The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections
+
+\begin{figure}
+ \centering
+ \includegraphics[scale=.8]{./figures/fluence_plot.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Final weighted-fit proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions.
+A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence.
+A clear loss of fluence  is visible, dropping by approximately 8.1\% from the incident fluence of 202.2 nAh over the length of the target stack.
+This is due to a combination of beam utilization, as well as scattering.}
+ \label{fig:fluence_plot}
+\end{figure}
+
+\begin{figure}
  \centering
@@
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{hh}
- \label{fig:hh}
+ \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
+The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
+As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
+ \label{fig:Nb_ptallies}
 \end{figure}
-
-comment that  peak-to-tail ratio increases
 
@@
 XXXXXX
+
+\comment{Double check this equation from my scratch work at LBL}
 
@@
 % \section{Discussion}
+
+\comment{Feel free to suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
 

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Finished section 3

@@
 
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in proton fluence.
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
 Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
@@
 
-XXXXXX
-
-\comment{Double check this equation from my scratch work at LBL}
+Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various Nb(p,x) reactions observed in decay spectroscopy.
+While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged cross sections, over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
+For both the cumulative and independent activities quantified, cross sections were calculated as:
+\begin{equation}
+\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
+\end{equation}
+where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
+The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified in the $2\sigma$ confidence interval in \autoref{fig:fluence_plot}).
 
@@
 
-\subsection{Systematic uncertainties}
-
-XXXXXX
+% \subsection{Systematic uncertainties}
+% 
+% XXXXXX
 
@@
 
-XXXXXX
+After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
+In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
+This blister   shows the location where the primary proton beam was incident upon the foil, and serves to build confidence that the beam was not stopped before reaching the last foil in the stack.
+Based on the \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the average fluence at each energy position (seen in \autoref{fig:fluence_plot}), a fluence of 202.2$\pm$5.4 nAh was calculated to be incident upon the target stack, which shows excellent agreement with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
+This incident fluence dropped by approximately 8.1\% to  185.9 $\pm$3.4 nAh over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
+This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the 6061 aluminum degraders) from scattering of the beam.
+
+Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40 - 90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
+In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb} were  extracted from these data as well, which are recorded in \autoref{tab:ibr_table}.
+Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1-7\%), proton fluence ($\pm$2-3\%), and foil areal density ($\pm$0.1-0.6\%).
+
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{My caption}
+% \label{my-label}
+% \small
+% \begin{tabular}{@{}lllllll@{}}
+% \toprule
+% E$_\text{p}$ (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+% 82mRb      & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 83Sr       & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85cum Y    & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85gY       & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85mY       & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 86Zr       & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
+% 86Y        & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+% 87Zr       & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
+% 87cum Y    & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
+% 87gY       & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
+% 87mY       & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
+% 88Zr       & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
+% 88Y        & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
+% 89cum Nb   & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
+% 89gNb      & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
+% 89mNb      & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
+% 89Zr       & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
+% 90Mo       & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
+% 90Nb       & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
+% 91mNb      & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
+% 92mNb      & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
+% 93mMo      & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
+% \end{tabular}
+% \end{table}
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}[]
+% \centering
+% \caption{My caption}
+% \label{my-label}
+% \small
+% \begin{tabular}{@{}llllllll@{}}
+% \toprule
+%       &            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ 
+%       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+% 82mRb & $\sigma_c$ & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
+% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+% 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
+% 87 Y  & $\sigma_c$ & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
+% 87gY  & $\sigma_i$ & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
+% 87mY  & $\sigma_i$ & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
+% 88Zr  & $\sigma_c$ & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
+% 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
+% 89 Nb & $\sigma_c$ & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
+% 89gNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
+% 89mNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
+% 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
+% 90Mo  & $\sigma_c$ & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
+% 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
+% 91mNb & $\sigma_c$ & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
+% 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
+% 93mMo & $\sigma_c$ & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
+% \end{tabular}
+% \end{table}
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}[]
+% \centering
+% \caption{My caption}
+% \label{my-label}
+% \small
+% \begin{tabular}{@{}llllllll@{}}
+% \toprule
+%       &            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){3-8} 
+%       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+% \ce{^{82m}Rb} & $\sigma_c$ & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
+% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+% 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
+% 87 Y  & $\sigma_c$ & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
+% 87gY  & $\sigma_i$ & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
+% 87mY  & $\sigma_i$ & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
+% 88Zr  & $\sigma_c$ & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
+% 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
+% 89 Nb & $\sigma_c$ & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
+% 89gNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
+% 89mNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
+% 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
+% 90Mo  & $\sigma_c$ & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
+% 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
+% 91mNb & $\sigma_c$ & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
+% 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
+% 93mMo & $\sigma_c$ & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
+% \end{tabular}
+% \end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+\label{tab:cu_rp_table}
+\small
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & \hrulefill              & \hrulefill              \\
+\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & \hrulefill              & \hrulefill              \\
+\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & \hrulefill              & \hrulefill              \\
+\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & \hrulefill              & \hrulefill              \\
+\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & \hrulefill              \\
+\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & \hrulefill              \\
+\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & \hrulefill              & \hrulefill              \\
+\ce{^{57}Ni}\,($\sigma_c$)    & $1.416\pm0.039$         & $1.164\pm0.030$         & $1.370\pm0.033$         & $2.074\pm0.051$         & $1.543\pm0.035$         & $0.02638\pm0.00077$     \\
+\ce{^{57}Co}\,($\sigma_i$)    & $38.78\pm0.99$          & $34.42\pm0.84$          & $35.06\pm0.81$          & $47.3\pm1.1$            & $47.0\pm1.1$            & $3.227\pm0.081$         \\
+\ce{^{58}Co}\,($\sigma_c$)    & $55.7\pm3.5$            & $53.2\pm4.1$            & $41.8\pm2.9$            & $32.8\pm2.5$            & $38.4\pm3.4$            & $62.7\pm3.4$            \\
+\ce{^{58g}Co}\,($\sigma_i$)   & $13.6\pm2.3$            & $10.5\pm1.9$            & $5.9\pm1.6$             & $7.6\pm1.3$             & $7.0\pm1.7$             & $1.13\pm0.31$           \\
+\ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
+\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & $0.93\pm0.15$           \\
+\ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
+\ce{^{61}Cu}\,($\sigma_c$)    & $48.8\pm1.5$            & $54.4\pm1.7$            & $63.7\pm2.1$            & $70.3\pm2.1$            & $79.5\pm2.7$            & $158.2\pm3.2$           \\
+\ce{^{64}Cu}\,($\sigma_c$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
+\end{tabular}
+}
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Nb}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+\label{tab:nb_rp_table}
+\small
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+\ce{^{82m}Rb}\,($\sigma_c$)   & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{83}Sr}\,($\sigma_c$)    & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{85}Y}\,($\sigma_c$)     & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{85g}Y}\,($\sigma_i$)    & $2.286\pm0.057$         & $2.01\pm0.15$           & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{85m}Y}\,($\sigma_i$)    & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{86}Zr}\,($\sigma_c$)    & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
+\ce{^{86}Y}\,($\sigma_i$)     & $32.25\pm0.89$          & $40.3\pm1.1$            & $39.0\pm1.0$            & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+\ce{^{87}Zr}\,($\sigma_c$)    & $45.8\pm5.8$            & $27.1\pm1.7$            & $31.5\pm1.5$            & $48.5\pm2.9$            & $37.7\pm1.6$            & $1.13\pm0.10$           \\
+\ce{^{87}Y}\,($\sigma_i$)     & $106.3\pm5.8$           & $52.9\pm1.7$            & $59.6\pm1.5$            & $87.8\pm2.9$            & $66.3\pm1.6$            & $2.93\pm0.10$           \\
+\ce{^{87g}Y}\,($\sigma_i$)    & $27.0\pm5.4$            & $7.1\pm1.2$             & $6.41\pm0.55$           & $5.6\pm2.1$             & $2.59\pm0.45$           & $0.949\pm0.045$         \\
+\ce{^{87m}Y}\,($\sigma_i$)    & $79.2\pm2.0$            & $45.8\pm1.2$            & $53.2\pm1.4$            & $82.1\pm2.0$            & $63.7\pm1.5$            & $1.983\pm0.093$         \\
+\ce{^{88}Zr}\,($\sigma_c$)    & $153.7\pm3.9$           & $140.0\pm3.5$           & $61.0\pm1.7$            & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.8\pm1.3$            \\
+\ce{^{88}Y}\,($\sigma_i$)     & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.0\pm1.3$             & $9.96\pm0.33$           \\
+\ce{^{89}Nb}\,($\sigma_c$)    & \hrulefill              & \hrulefill              & $176\pm12$          & $209.0\pm4.3$           & \hrulefill              & \hrulefill              \\
+\ce{^{89g}Nb}\,($\sigma_i$)   & \hrulefill              & \hrulefill              & $142\pm12$          & $181.7\pm4.1$           & \hrulefill              & \hrulefill              \\
+\ce{^{89m}Nb}\,($\sigma_i$)   & \hrulefill              & \hrulefill              & $33.9\pm2.0$            & $27.3\pm1.4$            & \hrulefill              & \hrulefill              \\
+\ce{^{89}Zr}\,($\sigma_i$)   & $203.8\pm5.3$           & $235.4\pm6.6$           & $287.5\pm6.8$           & $250.3\pm5.8$           & $54.6\pm1.1$            & $15.61\pm0.31$          \\
+\ce{^{90}Mo}\,($\sigma_c$)    & $20.6\pm0.7$            & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.4\pm1.9$            & $120.3\pm2.9$           & $24.38\pm0.71$          \\
+\ce{^{90}Nb}\,($\sigma_i$)    & $152.9\pm4.7$           & $169.3\pm4.8$           & $204.7\pm5.8$           & $265.2\pm7.8$           & $363.4\pm9.8$           & $165.2\pm4.5$           \\
+\ce{^{91m}Nb}\,($\sigma_c$)   & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $67.0\pm4.2$            \\
+\ce{^{92m}Nb}\,($\sigma_c$)   & $42.2\pm1.2$            & $45.7\pm1.2$            & $48.8\pm1.2$            & $51.6\pm1.3$            & $54.5\pm1.4$            & $60.4\pm1.2$            \\
+\ce{^{93m}Mo}\,($\sigma_c$)   & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
+\end{tabular}
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Nb}(p,x) and \ce{^{nat}Cu}(p,x) reaction products observed in this work.}
+\label{tab:ibr_table}
+\small
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                               & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.027$         & $0.581\pm0.038$         & $0.598\pm0.083$         & $0.81\pm0.12$         & \hrulefill              & \hrulefill              \\
+\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.068$         & $0.804\pm0.091$         & $0.858\pm0.084$         & $0.767\pm0.086$         & $0.82\pm0.11$         & $0.982\pm0.075$    \vspace{1em}     \\ 
+E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.029$         & $0.724\pm0.072$         & $0.736\pm0.072$         & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.045$         & $0.865\pm0.036$         & $0.893\pm0.032$         & $0.936\pm0.038$         & $0.961\pm0.032$         & $0.676\pm0.040$         \\
+\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & \hrulefill              & \hrulefill              & $0.193\pm0.018$         & $0.1304\pm0.0074$         & \hrulefill              & \hrulefill              \\ \bottomrule
+\end{tabular}
+}
+\end{table}
+
+These results have several notable takeaways.
+The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the smallest uncertainties to date.
+Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40 - 90 MeV region than for \ce{^{nat}Cu}(p,x) -  less than 3 existing measurements have been performed for the majority of the reactions presented here.
+Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of 3 data points in this energy region.
+Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the smallest uncertainties of existing literature data.
+
+Furthermore, this work presents the first measurements of several observables in these mass regions.
+This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40 - 90 MeV region.
+We also present here the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn} ($2^+$) and  \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}  ($6^+$), as well as their  isomer branching ratio via \ce{^{nat}Cu}(p,x).
+The cumulative cross section from these data are consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
+Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($t\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).
+
+Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured in this energy region at the 2-3\% uncertainty level.
+This is important, as it presents the first step towards characterizing this reaction for use as a proton dosimetry standard below 100 MeV.
+The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
+\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed, which makes activity quantification trivial.
+In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which are easily able to be used for the identification and quantification of produced \ce{^{90}Mo}.
+Finally, the production of \ce{^{90}Mo}  in the 40 - 90 MeV region is well-fed, with a peak cross section of approximately 120 mb, which creates a strong signal for activity quantification.
+While additional measurements are needed to improve the characterization of this excitation function, this clearly presents the first step towards the use of \ce{^{90}Mo} as a clean and precise monitor for charged particle dosimetry in irradiations up to approximately 24 hours in duration.
+
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
+These include the non-standard PET emitters \ce{^{57}Ni},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, the $\beta^-$-therapy agent  \ce{^{64}Cu},  and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
+
+\ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a PET emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
+\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} - indeed, the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
+The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
+Lower-energy production via \ce{^{nat}Co}(p,3n) at 24-40 MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
+
+\ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET emitter, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Nickles2003,Qaim2008,QaimSyedM2011}.
+In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which emits no observable gamma rays or x-rays though decay, necessitating an imaging isotope to be paired with for quantification of its uptake and biodistribution  \cite{Herzog1993}.
+Conventional production of \ce{^{86}Y} proceeds through low-energy (7 - 14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), lest it suffer contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
+Alternatively, production at 33-43 MeV via \ce{^{88}Sr}(p,3n) has been proposed - this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
+Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often extremely difficult to separate out.
+Unfortunately, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% of all radio-yttrium activities produced.
+This is because the dominant radio-yttrium activity in 40-90 MeV \ce{^{nat}Nb}(p,x) is  \ce{^{87}Y}, the largest obstacle to high-specific activity production of  \ce{^{86}Y} due to the unnecessary patient dose it contributes,  its comparable half-life, and the single neutron difference making efficient separations nearly impossible.
+However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
+Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51-61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
+
+\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived PET emitter, whose long lifetime makes it useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
+Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9 - 14 MeV, which offers an extremely high-purity route on a monoisotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
+Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 50 -75\% radio-zirconium purity in the 50 - 90 MeV region.
+
+\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging PET emitter with a moderate lifetime, making it suited for immune studies including tumor uptake studies    \cite{Busse2002,Radchenko2012}.
+It is typically produced using 8 - 15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{89}Nb}, and requires an enriched target (51.45\% natural abundance), but produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
+\ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
+\ce{^{90}Nb} may be produced directly with an approximately 360 mb peak cross section and 87\% radio-niobium purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radio-molybdenum purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold.
+
+Moving away from the potential PET emitters, \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
+The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the PET branch gives  \ce{^{64}Cu}  the possibility for real-time dose monitoring and verification.
+This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
+Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8 - 14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radio-copper purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
+\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20 - 30 MeV protons, and necessitates an enriched target (18.45\% natural abundance), lest the various other radio-coppers contaminate \ce{^{64}Cu}  purity \cite{Hilgers2003a,Szelecsenyi2005}.
+More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
+\ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
+
+Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is an emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators for PET studies \cite{Kovacs1991}.
+It is commonly produced via \ce{^{82}Kr}(p,n) at 10 - 15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
+Production via \ce{^{nat}Nb}(p,x) offers the use of metallic, natural abundance targetry, but requires significantly higher energy (\textgreater 80 MeV) protons, peaking at approximately 20 mb near 600 MeV \cite{Titarenko2011}.
+It is clear that this production route offers no advantage over existing \ce{^{82}Kr}(p,n) routes for in-house production.
+
+\comment{Make sure to comment on comparison with EMPIRE / TALYS  / TENDL here, after Amanda finishes modeling work.}
 
@@
 
-\comment{Feel free to suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
+\comment{Feel free to expand / suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
 
@@
 
+\comment{Placeholder to reserve space for pre-equilibrium / spin discussion.}
+
  \section{Conclusions}
 
-XXXXXX
+In summation, we present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV, as well as 5 independent measurements of isomer branching ratios.
+Nearly all cross sections have been reported with smaller uncertainties than previous measurements, and we report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
 
@@
 
- \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers.}
+ \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers, as well as anyone else that you feel should be acknowledged here.}
 
@@
 
+\comment{Fix a few figure labels (c/i) based on Jon;s email}
+
 \begin{figure*}

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Finished sections 4 & 5

@@
 Nearly all cross sections have been reported with smaller uncertainties than previous measurements, and we report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
+We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
 
@@
 
- Michael Gallegos and Don Dry in the C-NR Countroom, David Reass and Mike Connors at IPF, and the LANSCE Accelerator Operations staff
+ The authors would like to particularly acknowledge the assistance and support of  Michael Gallegos and Don Dry in the LANL C-NR Countroom, David Reass and Mike Connors at LANSCE-IPF, and the LANSCE Accelerator Operations staff.
 

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Squashed my comments

@@
 
-\comment{Confirm beam parameters below, from notebook}
-
 This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
-The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a \textred{100 \micro s pulse at a frequency of 1 Hz}, for an anticipated integral current of 205.9 nAh.
+The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
 The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
@@
 
-\comment{get citation data for UNISAMPO}
-
 Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma ray spectroscopy.
@@
 An example gamma ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \textred{(add UNISMPO citation)}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
+For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
 
@@
 The measured activity for each gamma ray possesses a total propagated uncertainty which is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma ray branching ratio data.
-
-\comment{Add 1st and 2nd order bateman stuff here, maybe cite Cetnar2006 also }
 
@@
 As with the gamma ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation:
+In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
 \begin{equation}
@@
 
-\comment{Add missing citations here}
-
 The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
@@
 For the monitor reactions employed in this work, these data sets are G.
-Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \textred{(insert Steyn citation here)}, M.
+Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \cite{Steyn1990}, M.
 Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S.
@@
 \ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
-\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & $0.93\pm0.15$           \\
+\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & \hrulefill        \\
 \ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
@@
 Table of decay data  for observed gamma rays. 
-The  values for lifetime and gamma ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012}.
-
-\comment{add citation for NDS A=22,24,93}
+The  values for lifetime and gamma ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
 
@@
 
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \textred{(cite me!)}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Koning2012}.
-
-\comment{add EMPIRE citation here!}
-
-\comment{add TENDL citation here!}
-
-\comment{Fix a few figure labels (c/i) based on Jon;s email}
+Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Herman2007,Koning2012}.
+
+% \comment{Fix a few figure labels (c/i) based on Jon;s email}
 

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Finished first draft.  Sending to co-authors for first round edits.

@@
 
-XXXXX
+A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
+The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
+Through this, a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
+The cross sections were measured using the well-characterized \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
+The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with significantly less uncertainty than previous measurements, through the use of variance minimization techniques to reduce proton energy uncertainties.
+This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
+Comparisons against the reaction modeling codes EMPIRE and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 
@@
 %% keywords here, in the form: keyword \sep keyword
-Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
+Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
 
@@
 \label{tab:stack_table}
+\small
 \begin{tabular}{@{}llll@{}}

### 2018-02-02 nb_px_paper/nb_px_paper.tex
Merged in Lee's edits for Section 1.

@@
 The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{18}F} \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many of the non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}.
-\comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?  I find conflicting descriptions in the literature.}
+\comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
+I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: }
  The future of nuclear medicine would appear to be the paradigm of personalized medicine - targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope of the same element, to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
@@
 
-However, one significant obstacle exists for both high-fidelity measurements of emerging medical radionuclides, as well as conventional isotope production: well-characterized  dosimetry standards.  
-This is particularly true for intermediate-energy charged particle beams, where there is currently a paucity of such well-characterized data. 
+One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  dosimetry standards.
+This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
 Indeed, the development of new dosimetry standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
 Charged particle dosimetry data currently exists for low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but experimental data used for this evaluation is sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6-15\%) \cite{gul2001charged}.
-While work is needed to improve upon existing dosimetry data, the development of new dosimetry reactions can expand the available range of options for the monitoring of charged particle beams.
+While work is needed to improve upon existing dosimetry data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
 
 Activation is one of the most fundamental techniques utilized in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field.
-While the specifics have branched into ever-more-detailed probes into the world of the nucleus, activation, at heart, deals with the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
+All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
+\comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
 Monitor reactions have  historically been part of such activation experiments, and in the context of charged particle induced reactions, serve two valuable purposes, depending upon the energy regime in question.
-Between the reaction's energetic threshold  and the tail of its compound peak, the magnitude and shape of a monitor reaction's excitation function is rapidly changing with increasing incident particle energy.
-In this energy regime, a monitor reaction can be used to assign an energy bin to a thin irradiated target, especially when comparing between monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
-This is extremely useful, as it allows one to screen for and eliminate systematic errors based on energy assignment, though this sensitivity to energy precludes their reliability as a beam current monitor.
+Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of a monitor reaction's excitation function is rapidly changing with increasing incident particle energy, making it useful for assigning the incident particle energy bin in a thin irradiated target.
+This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
+This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy assignment, though this sensitivity to energy precludes their reliability as a beam current monitor.
 
@@
 In this regime, the monitor reaction offers little-to-no energy sensitivity. 
-In return for giving up the ability to assign energy positions, monitor reactions in the pre-equilibrium regime become extremely useful for monitoring the integral beam current incident upon the target.
-While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or electrically-isolated target in a Faraday cup), these measure the integrated current incident upon an entire target assembly.
-For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energy positions in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
+However,  in the pre-equilibrium regime, monitor reactions become extremely useful for determining the integral beam current. 
+While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon an entire target assembly.
+For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
 In these experiments, a series of monitor foils at each energy position allow one to measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude.
@@
 However, several characteristics are hallmarks of a reaction monitor worthy to be classified as a dosimetry standard.
-The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide has  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay radiation able to used to uniquely identify it during post-activation assay.
-Generally, this means selecting a radionuclide with a number of distinct gamma rays, as gamma spectroscopy is commonly used to identify and quantify reaction products.
-The decay radiation should preferably have high intensities, so that they show up as strong peaks during spectroscopy, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
-
-Care should be taken to avoid cases where a radionuclide which is one decay off of stability populates excited states in the excited daughter nucleus also populated in the decay to the daughter state from the opposite side of the valley of stability.
-This produces decay gamma rays with nearly exactly the same energy, making it difficult to disentangle production from both sides of stability.
-For example, $^\text{nat}$Ti(p,x)\ce{^{48}V} is commonly used as dosimetry for 5 \textless\ E \textless\ 30 MeV protons.
-The characteristic decay lines in \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) are the 983.525 keV ($I_\gamma=99.98\%$) and 1312.106 keV ($I_\gamma=98.2\%$) gammas, which are also seen in the decay of \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}), yielding  a 983.526 keV ($I_\gamma=100.1\%$) and 1312.120 keV ($I_\gamma=100.1\%$) line \cite{Burrows2006}.
+The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma rays which can be used to uniquely identify it during post-activation assay.
+Generally, this means selecting a radionuclide with a number of distinct gamma rays.
+The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
+
+Care should be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
+For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
 Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV,$I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
@@
 Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
-It is preferred that the nucleus have a lifetime which is sufficiently long-lived to ensure that it may be quantified  conveniently and leisurely after end-of-beam without the majority if it decaying away.
+Ideally, the nucleus has a lifetime which is sufficiently long-lived to ensure that it may be quantified  conveniently and leisurely after end-of-beam without the majority if it decaying away.
 In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
 For proper quantification, it is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
-A precise and well-established half-life is needed to properly correct for decay losses during production, as well as in between end-of-beam and the start of decay spectroscopy, but these are generally well-characterized.
+This includes a precise and well-established half-life,  needed to  correct for decay losses, as well as well-characterized decay gamma-ray intensities.
 In practice, the weakest components of decay data are often the gamma ray intensities, which can routinely have uncertainties of 5\% or more.
 Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma ray intensity can make a significant reduction in measured cross section uncertainties.
-It is also of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
+Lastly, and perhaps most importantly for high-energy dosimetry applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
 This is typically mostly a concern for secondary neutrons produced through (z,xn) reactions on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
@@
 
-Finally, from a targetry  perspective, it is preferable to use a target that is readily commercially available at an affordable price and is generally chemically inert - any significant chemical changes during target preparation (rapid oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
+Finally, from a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert - any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
 Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
@@
 One monitor reaction which satisfies these requirements is that of a new, intermediate-energy proton dosimetry standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
-Niobium is naturally monoisotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
+Niobium is naturally mono-isotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
 \ce{^{90}Mo} also has excellent decay properties - its fairly long-lived half-life ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
@@
 
+In addition to being a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
 Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A $\approx$ 190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
-In addition to the interest in the production of \ce{^{90}Mo} as an intermediate-energy dosimetry standard, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of a number of isomer-to-ground state ratios.
 These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$ m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$ d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$ h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$ d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$ h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$ h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$ m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$ h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
 
-This measurement has taken place using a set of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here.
-By expanding the available set of dosimetry standards and well-characterized isotope production excitation functions, great advances are possible for improving the  available options for modern medical imaging and cancer therapy.
+The measurements described in this paper involve the use of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here.
+By expanding the available set of dosimetry standards and well-characterized isotope production excitation functions, this work should help optimize medical isotope production modalities, making more options   available for modern medical imaging and cancer therapy.
 
@@
 
-The well-known stacked-target design was utilized for this work, in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
+A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
 For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
@@
 \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived PET emitter, whose long lifetime makes it useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
-Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9 - 14 MeV, which offers an extremely high-purity route on a monoisotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
+Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9 - 14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
 Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 50 -75\% radio-zirconium purity in the 50 - 90 MeV region.

### 2018-02-02 nb_px_paper/nb_px_paper.tex
Finished merging in Lee's 1st-round revisions.

@@
 
+\newcommand{\cmmnt}[1]{}
+
 \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
@@
 However, several characteristics are hallmarks of a reaction monitor worthy to be classified as a dosimetry standard.
-The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma rays which can be used to uniquely identify it during post-activation assay.
-Generally, this means selecting a radionuclide with a number of distinct gamma rays.
+The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
+Generally, this means selecting a radionuclide with a number of distinct gamma-rays.
 The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
@@
 For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
-Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV,$I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
-However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma rays from another isobar nucleus.
+Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV,$I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
+However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
 
@@
 This includes a precise and well-established half-life,  needed to  correct for decay losses, as well as well-characterized decay gamma-ray intensities.
-In practice, the weakest components of decay data are often the gamma ray intensities, which can routinely have uncertainties of 5\% or more.
-Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma ray intensity can make a significant reduction in measured cross section uncertainties.
+In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
+Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
 Lastly, and perhaps most importantly for high-energy dosimetry applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
@@
 % In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-% The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
-% This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
+% The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma-ray in the process \cite{Burrows2007}.
+% This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma-ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
 % Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
@@
 The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
+The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
 The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
@@
 The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here.
-The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$, but their areal densities are not listed here due to the variance minimization techniques utilized  in this work.}
+The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
+Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal \cite{Graves2016}}
 \label{tab:stack_table}
@@
 
-Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma ray spectroscopy.
+Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma-ray spectroscopy.
 For consistency, a single detector was used in this measurement, an ORTEC GEM Series  High-Purity Germanium (HPGe) detector.
 The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
-Samples were counted at fixed positions ranging 4.5 - 83.5  cm from the front face of the detector, with a series of standard calibration sources used to determine in-house energy, efficiency, and pileup calibrations for each position.
-The foils were counted for a period of 2 weeks following EoB, to accurately quantify all induced activities.
-An example gamma ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
+Samples were counted at fixed positions ranging 4.5 - 83.5  cm from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
+The foils were counted  for a period of 2 weeks following EoB, to accurately quantify all induced activities,  with dead time never exceeding 5\%.
+An example gamma-ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
 For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
@@
  % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
- \caption{Example gamma spectra, collected from an activated Nb foil at approximately 80 MeV, to monitor radioisotope production.
-While the majority of observed reaction products are visible in this spectrum, it is particularly noteworthy that the \ce{^{90}Mo} decay lines which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction are high in intensity and clearly isolated from surrounding peaks, greatly aiding its activity quantification.}
+ \caption{A gamma spectrum, collected from an activated Nb foil at approximately 80 MeV.
+While the majority of observed reaction products are visible in this spectrum,  the \ce{^{90}Mo} decay lines, which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction, are high in intensity and clearly isolated from surrounding peaks.}
  \label{fig:gspec}
@@
 Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
-The calibrated detector efficiencies, along with gamma ray intensities for each transition, were used to convert the net  counts in each fitted gamma ray photopeak into an activity for the activated isotopes and isomeric states.
+The calibrated detector efficiencies, along with gamma-ray intensities for each transition, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
 For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-As nearly all of the product nuclei created in this work have multiple high-intensity gamma rays, each product nuclei had measurements of its present activity at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma rays.
-The measured activity for each gamma ray possesses a total propagated uncertainty which is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma ray branching ratio data.
-
-Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly produced by decay down a mass chain.
+As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
+The measured activity for each gamma-ray possesses a total propagated uncertainty which is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
+
+Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly by decay down a mass chain.
 To this end, it is useful to differentiate between the types of cross sections reported in this work. 
@@
 In addition, cumulative cross sections will be reported whenever it is impossible to use decay spectroscopy to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, independent cross sections ($\sigma_i$) will be reported, leaving solely direct nucleus production by subtracting out the feeding of decay precursors.
-
-To convert these activities into cross sections, corrections must be made for the decay of the various reaction products in  between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB.
-The use of  multiple gamma rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma ray observation.
+For all remaining observed reaction products in the mass chain, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction.
+
+To convert these activities into cross sections, corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB.
+The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
 For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
@@
 Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ would be reported as as well.
-As with the gamma ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
 In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
@@
 \end{equation}
+where $j$ refers to a precursor nucleus populating a specific end-product.  
 While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
@@
 \end{equation}
-In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, that the feeding contributions from decay could be separated and an independent cross section reported.
+In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
 After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
@@
 
-As discussed previously, accurate proton dosimetry is the most important factor in performing high-fidelity cross section measurements.
-At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline possess resolution of 100 nAh.
+An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
+At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
 For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional dosimetry is thus needed to accurately normalize quantified EoB activities into cross sections.
@@
 However, for final energy determination and analysis, a more rigorous method of proton transport is needed.
-The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, and is used to calculate a full proton energy distribution for each stack position   \cite{Goorley2012}.
+The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
 In addition, MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to reactions, as well as production of secondary particles.
-As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated - $10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
+As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.
+$10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
 
@@
 The initial proton beam has a finite energy spread (an approximately 0.1 MeV Gaussian width at 100 MeV), and since stopping power for charged particles is inversely proportional to their energy, the low-energy tail of the energy distribution is degraded more in each stack element than the high-energy tail.
-This effect compounds as one moves towards the rear of the stack, with the effect of a significantly broadened low-energy tail relative to the high-energy tail, and a progressively larger net shift of the centroid to a lower energy than the peak of the energy distribution.
+This effect compounds  towards the rear of the stack, creating a significantly broadened low-energy tail, and a progressively larger net shift of the centroid to a lower energy. 
 % For each foil in the target stack, 
@@
 Likewise, to represent the energy uncertainty for each stack position, the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution is chosen for each energy position reported.
-While most experimental uncertainties are reported at the 1$\sigma$ level, the $\approx2.3\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy center-of-mass.
-
-Based on the recent work of Graves \etal, the \enquote{variance minimization} techniques they outline have been employed here, to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
+While most experimental uncertainties are reported at the 1$\sigma$ level, the $\approx2.3\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy centroid value.
+
+The \enquote{variance minimization} techniques  described by  Graves \etal,  have been employed here to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
 This method is based on the assumption that the independent measurements of proton fluence from the 5 monitor reactions used in this work should all be consistent at each energy position.
@@
 
-To correct for this, variance minimization techniques were employed here to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
-Due to the difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values, but this had negligible impact on improving monitor reaction disagreement.
-This is due to the minor impact that their areal density has on beam degradation, relative to the thick 6061 aluminum degraders (nominal 3-5 mg/cm$^2$, relative to nominal 1000-1400 mg/cm$^2$).
+Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
+Due to the difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
+This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to the thick 6061 aluminum degraders (nominal 3-5 mg/cm$^2$, relative to nominal 1000-1400 mg/cm$^2$).
 As such,  the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
 This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
-The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position, approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
+The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position.
+This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
 This energy corresponds to a 6061 aluminum areal density of 2.53\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
@@
 As expected, the 2.53\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
-In addition, as one moves to the rear energy positions, the disagreement in the independent proton fluence measurements is reduced.
+In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
 It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
@@
 Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils.
-The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively - the fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
+The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively.
+The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
 This serves as an example of the importance of selecting monitor reaction products inaccessible through (n,x) channels, as noted previously.
-However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of the secondary neutron flux.
+However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.
 
@@
  % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Result of variance minimization, performed by varying the degrader density in MCNP6 simulations of the target stack.
+ \caption{Result of the variance minimization performed by adjusting the degrader density in MCNP6 simulations of the target stack.
 A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.53\% greater than nominal.
@@
     \end{subfigure}%
-    \caption{Results of variance minimization through enhancement of 6061 aluminum effective areal density by 2.53\%.
-A noticeable reduction of variance in measured proton fluence is seen, in particular at the low-energy rear positions of the stack.
+    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.53\%.
+A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
 The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} monitor channels is caused by activation through (n,x) reactions from the secondary neutron flux.
-By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
+By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.\comment{Lee: I think you should make the fonts ridiculously larger.
+}}
      \label{fig:variance_mins}
@@
 Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the 6 irradiated Nb foils in \autoref{fig:Nb_ptallies}.
-As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as result of the beam energy degradation.
+As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
 In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail-ratio increases as more  secondary protons are produced upstream.
@@
 An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the  \ce{^{nat}Al}(p,x)\ce{^{24}Na} observed fluence (the upper set of points), and the uncertainty-weighted average fluence from the  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn} and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions (the lower set of points).
-To determine the final fluence assignments for the Nb foils, uncertainty-weighted linear regression was used to fit the various fluence measurements, minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
+To determine the final fluence assignments for the Nb foils, uncertainty-weighted linear regression was used to fit the various fluence measurements.
+This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
 As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
@@
 
-Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various Nb(p,x) reactions observed in decay spectroscopy.
+Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
 While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged cross sections, over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
@@
 where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
+The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
 The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified in the $2\sigma$ confidence interval in \autoref{fig:fluence_plot}).
@@
 For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
-In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb} were  extracted from these data as well, which are recorded in \autoref{tab:ibr_table}.
+In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb} were  extracted and are recorded in \autoref{tab:ibr_table}.
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
@@
 % E$_\text{p}$ (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% 82mRb      & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 83Sr       & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85cum Y    & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85gY       & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85mY       & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 86Zr       & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
-% 86Y        & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+% 82mRb      & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 83Sr       & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85cum Y    & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85gY       & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85mY       & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 86Zr       & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 86Y        & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 % 87Zr       & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
@@
 % 88Y        & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
-% 89cum Nb   & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
-% 89gNb      & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
-% 89mNb      & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
+% 89cum Nb   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $175.52\pm12.44$        & $208.99\pm4.33$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 89gNb      & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $141.58\pm12.28$        & $181.73\pm4.08$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 89mNb      & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.94\pm1.97$          & $27.26\pm1.45$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 % 89Zr       & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
@@
 % 90Nb       & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
-% 91mNb      & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
+% 91mNb      & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $66.96\pm4.16$          \\
 % 92mNb      & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
@@
 %       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% 82mRb & $\sigma_c$ & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
-% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+% 82mRb & $\sigma_c$ & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 % 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
@@
 % 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
-% 89 Nb & $\sigma_c$ & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
-% 89gNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
-% 89mNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
+% 89 Nb & $\sigma_c$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $175.52\pm12.44$        & $208.99\pm4.33$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 89gNb & $\sigma_i$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $141.58\pm12.28$        & $181.73\pm4.08$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 89mNb & $\sigma_i$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.94\pm1.97$          & $27.26\pm1.45$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 % 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
@@
 % 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
-% 91mNb & $\sigma_c$ & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
+% 91mNb & $\sigma_c$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $66.96\pm4.16$          \\
 % 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
@@
 %       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% \ce{^{82m}Rb} & $\sigma_c$ & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
-% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+% \ce{^{82m}Rb} & $\sigma_c$ & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 % 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
@@
 E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & \hrulefill              & \hrulefill              \\
-\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & \hrulefill              & \hrulefill              \\
-\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & \hrulefill              & \hrulefill              \\
-\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & \hrulefill              & \hrulefill              \\
-\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & \hrulefill              \\
-\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & \hrulefill              \\
-\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & \hrulefill              & \hrulefill              \\
+\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & --\cmmnt{\hrulefill}              \\
+\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & --\cmmnt{\hrulefill}              \\
+\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 \ce{^{57}Ni}\,($\sigma_c$)    & $1.416\pm0.039$         & $1.164\pm0.030$         & $1.370\pm0.033$         & $2.074\pm0.051$         & $1.543\pm0.035$         & $0.02638\pm0.00077$     \\
@@
 \ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
-\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & \hrulefill        \\
+\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & --\cmmnt{\hrulefill}        \\
 \ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
@@
 E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{82m}Rb}\,($\sigma_c$)   & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
-\ce{^{83}Sr}\,($\sigma_c$)    & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-\ce{^{85}Y}\,($\sigma_c$)     & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-\ce{^{85g}Y}\,($\sigma_i$)    & $2.286\pm0.057$         & $2.01\pm0.15$           & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
-\ce{^{85m}Y}\,($\sigma_i$)    & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
-\ce{^{86}Zr}\,($\sigma_c$)    & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
-\ce{^{86}Y}\,($\sigma_i$)     & $32.25\pm0.89$          & $40.3\pm1.1$            & $39.0\pm1.0$            & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
+\ce{^{82m}Rb}\,($\sigma_c$)   & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{83}Sr}\,($\sigma_c$)    & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{85}Y}\,($\sigma_c$)     & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{85g}Y}\,($\sigma_i$)    & $2.286\pm0.057$         & $2.01\pm0.15$           & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{85m}Y}\,($\sigma_i$)    & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{86}Zr}\,($\sigma_c$)    & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{86}Y}\,($\sigma_i$)     & $32.25\pm0.89$          & $40.3\pm1.1$            & $39.0\pm1.0$            & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 \ce{^{87}Zr}\,($\sigma_c$)    & $45.8\pm5.8$            & $27.1\pm1.7$            & $31.5\pm1.5$            & $48.5\pm2.9$            & $37.7\pm1.6$            & $1.13\pm0.10$           \\
@@
 \ce{^{88}Y}\,($\sigma_i$)     & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.0\pm1.3$             & $9.96\pm0.33$           \\
-\ce{^{89}Nb}\,($\sigma_c$)    & \hrulefill              & \hrulefill              & $176\pm12$          & $209.0\pm4.3$           & \hrulefill              & \hrulefill              \\
-\ce{^{89g}Nb}\,($\sigma_i$)   & \hrulefill              & \hrulefill              & $142\pm12$          & $181.7\pm4.1$           & \hrulefill              & \hrulefill              \\
-\ce{^{89m}Nb}\,($\sigma_i$)   & \hrulefill              & \hrulefill              & $33.9\pm2.0$            & $27.3\pm1.4$            & \hrulefill              & \hrulefill              \\
+\ce{^{89}Nb}\,($\sigma_c$)    & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $176\pm12$          & $209.0\pm4.3$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{89g}Nb}\,($\sigma_i$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $142\pm12$          & $181.7\pm4.1$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{89m}Nb}\,($\sigma_i$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.9\pm2.0$            & $27.3\pm1.4$            & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 \ce{^{89}Zr}\,($\sigma_i$)   & $203.8\pm5.3$           & $235.4\pm6.6$           & $287.5\pm6.8$           & $250.3\pm5.8$           & $54.6\pm1.1$            & $15.61\pm0.31$          \\
@@
 \ce{^{90}Nb}\,($\sigma_i$)    & $152.9\pm4.7$           & $169.3\pm4.8$           & $204.7\pm5.8$           & $265.2\pm7.8$           & $363.4\pm9.8$           & $165.2\pm4.5$           \\
-\ce{^{91m}Nb}\,($\sigma_c$)   & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $67.0\pm4.2$            \\
+\ce{^{91m}Nb}\,($\sigma_c$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $67.0\pm4.2$            \\
 \ce{^{92m}Nb}\,($\sigma_c$)   & $42.2\pm1.2$            & $45.7\pm1.2$            & $48.8\pm1.2$            & $51.6\pm1.3$            & $54.5\pm1.4$            & $60.4\pm1.2$            \\
@@
 E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.027$         & $0.581\pm0.038$         & $0.598\pm0.083$         & $0.81\pm0.12$         & \hrulefill              & \hrulefill              \\
+\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.027$         & $0.581\pm0.038$         & $0.598\pm0.083$         & $0.81\pm0.12$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 \ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.068$         & $0.804\pm0.091$         & $0.858\pm0.084$         & $0.767\pm0.086$         & $0.82\pm0.11$         & $0.982\pm0.075$    \vspace{1em}     \\ 
 E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.029$         & $0.724\pm0.072$         & $0.736\pm0.072$         & \hrulefill              & \hrulefill              & \hrulefill              \\
+\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.029$         & $0.724\pm0.072$         & $0.736\pm0.072$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 \ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.045$         & $0.865\pm0.036$         & $0.893\pm0.032$         & $0.936\pm0.038$         & $0.961\pm0.032$         & $0.676\pm0.040$         \\
-\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & \hrulefill              & \hrulefill              & $0.193\pm0.018$         & $0.1304\pm0.0074$         & \hrulefill              & \hrulefill              \\ \bottomrule
+\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $0.193\pm0.018$         & $0.1304\pm0.0074$         &      --\cmmnt{\hrulefill}         & --\cmmnt{\hrulefill}              \\ \bottomrule
 \end{tabular}
@@
 This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40 - 90 MeV region.
-We also present here the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn} ($2^+$) and  \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}  ($6^+$), as well as their  isomer branching ratio via \ce{^{nat}Cu}(p,x).
-The cumulative cross section from these data are consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
+It also represents  the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn} ($2^+$) and  \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}  ($6^+$), as well as their  isomer branching ratio via \ce{^{nat}Cu}(p,x).
+The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
 Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($t\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).
 
-Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured in this energy region at the 2-3\% uncertainty level.
+Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 2-3\% uncertainty level.
 This is important, as it presents the first step towards characterizing this reaction for use as a proton dosimetry standard below 100 MeV.
@@
 \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed, which makes activity quantification trivial.
-In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which are easily able to be used for the identification and quantification of produced \ce{^{90}Mo}.
-Finally, the production of \ce{^{90}Mo}  in the 40 - 90 MeV region is well-fed, with a peak cross section of approximately 120 mb, which creates a strong signal for activity quantification.
-While additional measurements are needed to improve the characterization of this excitation function, this clearly presents the first step towards the use of \ce{^{90}Mo} as a clean and precise monitor for charged particle dosimetry in irradiations up to approximately 24 hours in duration.
+In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
+Finally, the production of \ce{^{90}Mo}  in the 40 - 90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
+This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise monitor for charged particle dosimetry in irradiations up to approximately 24 hours in duration.
 
@@
 \ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET emitter, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Nickles2003,Qaim2008,QaimSyedM2011}.
-In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which emits no observable gamma rays or x-rays though decay, necessitating an imaging isotope to be paired with for quantification of its uptake and biodistribution  \cite{Herzog1993}.
-Conventional production of \ce{^{86}Y} proceeds through low-energy (7 - 14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), lest it suffer contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
+In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} cow and emits no observable gamma-rays or x-rays though decay, necessitating an imaging isotope to be paired with for quantification of its uptake and biodistribution  \cite{Herzog1993}.
+Conventional production of \ce{^{86}Y} proceeds through low-energy (7 - 14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
 Alternatively, production at 33-43 MeV via \ce{^{88}Sr}(p,3n) has been proposed - this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
 Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often extremely difficult to separate out.
-Unfortunately, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% of all radio-yttrium activities produced.
-This is because the dominant radio-yttrium activity in 40-90 MeV \ce{^{nat}Nb}(p,x) is  \ce{^{87}Y}, the largest obstacle to high-specific activity production of  \ce{^{86}Y} due to the unnecessary patient dose it contributes,  its comparable half-life, and the single neutron difference making efficient separations nearly impossible.
+As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% of all radio-yttrium activities produced.
+This is because the dominant radio-yttrium activity in 40-90 MeV \ce{^{nat}Nb}(p,x) is  \ce{^{87}Y}, the largest obstacle to high-specific activity production of  \ce{^{86}Y} due to the unnecessary patient dose it contributes,  its comparable half-life, and the fact that separation is impractical.
 However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
@@
 
-\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived PET emitter, whose long lifetime makes it useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
+\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived PET emitter, whose  lifetime makes it useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
 Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9 - 14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
@@
 
-\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging PET emitter with a moderate lifetime, making it suited for immune studies including tumor uptake studies    \cite{Busse2002,Radchenko2012}.
+\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging PET emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
 It is typically produced using 8 - 15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{89}Nb}, and requires an enriched target (51.45\% natural abundance), but produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
@@
 \ce{^{90}Nb} may be produced directly with an approximately 360 mb peak cross section and 87\% radio-niobium purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radio-molybdenum purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold.
+However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity target impossible.
 
@@
 
-In summation, we present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV, as well as 5 independent measurements of isomer branching ratios.
-Nearly all cross sections have been reported with smaller uncertainties than previous measurements, and we report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
+In summation, we present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios.
+Nearly all cross sections have been reported with smaller uncertainties than previous measurements.
+We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
 We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
@@
 % % \end{longtable}
-Table of decay data  for observed gamma rays. 
-The  values for lifetime and gamma ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
+Table of decay data  for observed gamma-rays. 
+The  values for lifetime and gamma-ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
 
@@
 \centering
-\caption{Decay data for gamma rays observed in \ce{^{nat}Al}(p,x) and \ce{^{nat}Cu}(p,x).}
+\caption{Decay data for gamma-rays observed in \ce{^{nat}Al}(p,x) and \ce{^{nat}Cu}(p,x).}
 \label{tab:nudat_table_monitors}
@@
 \centering
-\caption{Decay data for gamma rays observed in \ce{^{nat}Nb}(p,x).}
+\caption{Decay data for gamma-rays observed in \ce{^{nat}Nb}(p,x).}
 \label{tab:nudat_table_nb}

### 2018-02-03 nb_px_paper/nb_px_paper.tex
Started merging Stephen's 1st round revisions.

@@
 The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
-Through this, a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
-The cross sections were measured using the well-characterized \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
-The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with significantly less uncertainty than previous measurements, through the use of variance minimization techniques to reduce proton energy uncertainties.
+A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 -- 89.74 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
+Cross sections were measured using the well-characterized \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
+Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
+The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
 This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
 Comparisons against the reaction modeling codes EMPIRE and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+
+\comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
+
+\comment{Stephen: Unless you've already discussed this with co-authors, I would have someone from LANL (i.e. Meiring) instead or in addition.  Add one following discussion.}
 
@@
 Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S.
-alone - a multi-billion dollar industry which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases \cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
-The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{18}F} \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many of the non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}.
+alone,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases \cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
+The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many of the non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}.
 \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
-I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: }
- The future of nuclear medicine would appear to be the paradigm of personalized medicine - targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope of the same element, to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
-Candidate isotopes to fill these needs have been identified based on their decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields, to facilitate production in sufficient quantities for cell studies.
+I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: In this context, I would make this definition based on what machines in the US are routinely used for medical isotope production - based on this, I agree with 200 MeV.
+}
+ The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
+Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
+Candidate isotopes to meet these needs have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
+These studies will serve to facilitate the production of pre-clinical quantities of radioactivity.
 
@@
 While work is needed to improve upon existing dosimetry data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
+\comment{Stephen: I'm having a hard time following this paragraph.
+Some of your syntax overlaps significantly with nuclear medicine \& medical physics terminology with different intended meanings.
+For example 'dosimetry' is typically taken to mean the measurement of absorbed energy per unit mass (J/kg) and associated measurements/specifications.
+Another example, 'dosimetry standard' is used quite often when referring to NIST air kerma reference standards which are the bedrock of Accredited Dosimetry Calibration Lab (ADCL) measurements.
+As you are more familiar with classic Nuclear Physics writing, perhaps you better know how this language will be interpreted.
+}
 

### 2018-02-16 nb_px_paper/nb_px_paper.tex
Finished adding Stephen's revisions.

@@
 
+\comment{Comment on the Si production here?}
+
+\comment{Add CoH to codes also, and add extra physics language with Lee.}
+
 % Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
@@
 Indeed, the development of new dosimetry standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
-Charged particle dosimetry data currently exists for low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but experimental data used for this evaluation is sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6-15\%) \cite{gul2001charged}.
+Charged particle dosimetry data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6-15\%) \cite{gul2001charged}.
 While work is needed to improve upon existing dosimetry data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
@@
 
-Activation is one of the most fundamental techniques utilized in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field.
+Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field.
 All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
 \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
-Monitor reactions have  historically been part of such activation experiments, and in the context of charged particle induced reactions, serve two valuable purposes, depending upon the energy regime in question.
-Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of a monitor reaction's excitation function is rapidly changing with increasing incident particle energy, making it useful for assigning the incident particle energy bin in a thin irradiated target.
+Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
+\comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
+Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of a monitor reaction's excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
 This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
-This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy assignment, though this sensitivity to energy precludes their reliability as a beam current monitor.
+This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this sensitivity to energy precludes their reliability as a beam current monitor.
 
@@
 In these experiments, a series of monitor foils at each energy position allow one to measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude.
+\comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
 Both of these purposes make well-characterized dosimetry an invaluable asset to any activation experiment.
 
-In practice, nearly any radioisotope can serve as a reaction monitor. 
-However, several characteristics are hallmarks of a reaction monitor worthy to be classified as a dosimetry standard.
+In theory, nearly any radioisotope can serve as a reaction monitor, but those desired to be classified as a dosimetry standard possess several hallmark characteristics.
 The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
@@
 
+\comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
 Care should be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
 For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
-Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV,$I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
+Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
 However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
@@
 Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
+
+From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert - any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
+Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
+For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
+However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectroscopy.
+For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
+Thickness selection will be subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
+% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
+
+\comment{Stephen:  This is also a discussion point.
+If you're trying to introduce the purpose of this paper, i.e.
+the establishment of a new monitor reaction, I would try to condense paragraphs 3-9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction.
+The rest of this content can be included in the discussion if you feel it is necessary.}
 Lastly, and perhaps most importantly for high-energy dosimetry applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
@@
 Any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often a laborious task to separate out the fraction of secondary particles contributing to the total activation.
-
-Finally, from a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert - any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
-Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
-For charged particle reactions, a thin target is desired for dosimetry, as thicker targets will cause more energy degradation and broaden the energy spectrum downstream of the target.
-% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
 
@@
 Niobium is naturally mono-isotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
-\ce{^{90}Mo} also has excellent decay properties - its fairly long-lived half-life ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
+\ce{^{90}Mo} also has excellent decay properties - its fairly long-lived lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
 In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
@@
 In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 32 other (p,x) production cross sections between 40 -- 90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
-These include the non-standard positron emission tomography (PET) emitters \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}),  \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}), the $\beta^-$-therapy agent  \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}),  and the Auger-therapy agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
+These include the non-standard positron emission tomography (PET) agent \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
 
   \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
+
+  \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}
 
@@
 For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
-Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized - for each foil, length and width measurements were taken at four different locations using a Mitutoyo caliper, thickness measurements were taken at four different locations using a Mitutoyo micrometer, and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
+Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized - for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
 Using these length, width, and mass readings, the areal density (in mg/cm$^2$) for each foil was calculated, along with the propagated uncertainty in areal density.
 The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape - each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.793 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.607 mg/cm$^2$).
-The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame, and one \ce{^{nat}Al}, one \ce{^{nat}Cu}, and \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
+The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
+One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
 These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
@@
 The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor - after end-of-beam (EoB), $\beta$ particles emitted from these activated stainless steel foils may be used to develop Gafchromic film, revealing the spatial profile of the beam entering and exiting the stack.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor - after end-of-beam (EoB), decay radiation emitted from these activated stainless steel foils may be used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
-The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
+The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
 At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
-The activated foils were cleaned of all surface contamination, and transported to a counting lab for decay spectroscopy, which started approximately 7 hours following end-of-beam.
+The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectroscopy, which started approximately 7 hours following end-of-beam.
 
@@
 Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
-SS profile monitor & 249.8 \micro m         & 194.555                                      & 0.290                      \\
-Al-1               & 25.0 \micro m          & 6.519                                        & 0.724                      \\
-Cu-1               & 61.3 \micro m          & 53.736                                       & 0.053                      \\
-Nb-1               & 30.0 \micro m          & 23.205                                       & 0.073                      \\
+SS profile monitor & 249.8 \micro m         & 194.56                                      & 0.29                      \\
+Al-1               & 25.0 \micro m          & 6.52                                        & 0.72                      \\
+Cu-1               & 61.3 \micro m          & 53.74                                       & 0.15                      \\
+Nb-1               & 30.0 \micro m          & 23.21                                       & 0.17                      \\
 Al Degrader 01     & 4.96 mm           & -                                            & -                          \\
-Al-2               & 25.5 \micro m          & 6.484                                        & 0.364                      \\
-Cu-2               & 61.8 \micro m          & 53.849                                       & 0.169                      \\
-Nb-2               & 30.8 \micro m          & 22.905                                       & 0.166                      \\
+Al-2               & 25.5 \micro m          & 6.48                                        & 0.36                      \\
+Cu-2               & 61.8 \micro m          & 53.85                                       & 0.17                      \\
+Nb-2               & 30.8 \micro m          & 22.91                                       & 0.17                      \\
 Al Degrader 02     & 4.55 mm           & -                                            & -                          \\
-Al-3               & 25.8 \micro m          & 6.472                                        & 0.314                      \\
-Cu-3               & 61.5 \micro m          & 53.984                                       & 0.113                      \\
-Nb-3               & 31.0 \micro m          & 22.906                                       & 0.235                      \\
+Al-3               & 25.8 \micro m          & 6.47                                        & 0.31                      \\
+Cu-3               & 61.5 \micro m          & 53.98                                       & 0.11                      \\
+Nb-3               & 31.0 \micro m          & 22.91                                       & 0.24                      \\
 Al Degrader 03     & 3.52 mm           & -                                            & -                          \\
-Al-4               & 26.3 \micro m          & 6.505                                        & 0.407                      \\
-Cu-4               & 61.3 \micro m          & 53.463                                       & 0.221                      \\
-Nb-4               & 30.8 \micro m          & 22.550                                       & 0.245                      \\
+Al-4               & 26.3 \micro m          & 6.51                                        & 0.41                      \\
+Cu-4               & 61.3 \micro m          & 53.46                                       & 0.22                      \\
+Nb-4               & 30.8 \micro m          & 22.55                                       & 0.25                      \\
 Al Degrader 04     & 3.47 mm           & -                                            & -                          \\
-Al-5               & 26.5 \micro m          & 6.479                                        & 0.296                      \\
-Cu-5               & 61.5 \micro m          & 53.572                                       & 0.108                      \\
-Nb-5               & 30.8 \micro m          & 22.110                                       & 0.248                      \\
+Al-5               & 26.5 \micro m          & 6.48                                        & 0.29                      \\
+Cu-5               & 61.5 \micro m          & 53.57                                       & 0.11                      \\
+Nb-5               & 30.8 \micro m          & 22.11                                       & 0.25                      \\
 Al Degrader 05     & 3.46 mm           & -                                            & -                          \\
-Al-6               & 26.3 \micro m          & 6.475                                        & 0.624                      \\
-Cu-6               & 62.0 \micro m          & 53.836                                       & 0.318                      \\
-Nb-6               & 31.3 \micro m          & 22.120                                       & 0.130                      \\
-SS profile monitor & 124.4 \micro m         & 101.336                                      & 0.226                      \\ \bottomrule
+Al-6               & 26.3 \micro m          & 6.48                                        & 0.62                      \\
+Cu-6               & 62.0 \micro m          & 53.84                                       & 0.32                      \\
+Nb-6               & 31.3 \micro m          & 22.12                                       & 0.13                      \\
+SS profile monitor & 124.4 \micro m         & 101.34                                      & 0.23                      \\ \bottomrule
 \end{tabular}
@@
 
-Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma-ray spectroscopy.
-For consistency, a single detector was used in this measurement, an ORTEC GEM Series  High-Purity Germanium (HPGe) detector.
+For consistency, a single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
 The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
-Samples were counted at fixed positions ranging 4.5 - 83.5  cm from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
+Samples were counted at fixed positions ranging 4.5 - 83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
 The foils were counted  for a period of 2 weeks following EoB, to accurately quantify all induced activities,  with dead time never exceeding 5\%.
 An example gamma-ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
+For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
+%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
 
@@
 
+\comment{Stephen:  Still not a huge fan of the dosimetry terminology, but I would defer to the preference of those with more experience in the field. }
+
 % describe integral equation for converting activities to currents here
@@
 Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution is expected for all monitor and target foils.
-As a result, the integral form of the well-known activation equation is used to accurately determine proton fluence ($I \Delta t $) in each monitor foil by convolving the IAEA recommended cross section values with the proton energy distribution:
+As a result, the integral form of the well-known activation equation is used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
+%by convolving the IAEA recommended cross section values with the proton energy distribution:
 % \begin{equation}
@@
 \end{equation}
-where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy E, and $\frac{d\phi}{dE}$ is the differential proton fluence.
+where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy $E$, and $\frac{d\phi}{dE}$ is the differential proton fluence.
 Using this formalism, the quantified EoB activities for each monitor reaction may be converted into a measured proton fluence at each energy position.
@@
 The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
-Fortunately, the recommended cross section values for each monitor reaction tend to match one of the   selected experimental data sets used in their evaluation almost perfectly.
+Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental data sets used in their evaluation.
 Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
@@
 
-The \enquote{variance minimization} techniques  described by  Graves \etal,  have been employed here to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
+The \enquote{variance minimization} techniques  described by  Graves \etal\  have been employed here to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
 This method is based on the assumption that the independent measurements of proton fluence from the 5 monitor reactions used in this work should all be consistent at each energy position.
@@
 In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
+\comment{Insert text here to describe our Na22 / Si production hypothesis.  }
 It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
@@
 The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
+ \comment{Stephen: Half-width figure: Larger text and axes tick-marks would be nice. }
  \label{fig:variation_curve}
@@
 This is due to a combination of beam utilization, as well as scattering.}
+ \comment{Stephen:  Half-width figure: Larger text and axes tick-marks would be nice. }
  \label{fig:fluence_plot}
@@
 As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
+ \comment{Stephen: Half-width figure: Larger text and axes tick-marks would be nice. }
  \label{fig:Nb_ptallies}
@@
 In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
-This blister   shows the location where the primary proton beam was incident upon the foil, and serves to build confidence that the beam was not stopped before reaching the last foil in the stack.
+\comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
+This blister   shows the location where the primary proton beam was incident upon the foil.
 Based on the \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the average fluence at each energy position (seen in \autoref{fig:fluence_plot}), a fluence of 202.2$\pm$5.4 nAh was calculated to be incident upon the target stack, which shows excellent agreement with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
 This incident fluence dropped by approximately 8.1\% to  185.9 $\pm$3.4 nAh over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
-This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the 6061 aluminum degraders) from scattering of the beam.
+This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
 
@@
 The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1-7\%), proton fluence ($\pm$2-3\%), and foil areal density ($\pm$0.1-0.6\%).
+\comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
 
@@
 \ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
+\ce{^{52m}Mn}\,($\sigma_c$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
 \ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & --\cmmnt{\hrulefill}              \\
@@
 These results have several notable takeaways.
-The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the smallest uncertainties to date.
+The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
 Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40 - 90 MeV region than for \ce{^{nat}Cu}(p,x) -  less than 3 existing measurements have been performed for the majority of the reactions presented here.
 Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of 3 data points in this energy region.
-Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the smallest uncertainties of existing literature data.
+Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
 
@@
 This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40 - 90 MeV region.
-It also represents  the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn} ($2^+$) and  \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}  ($6^+$), as well as their  isomer branching ratio via \ce{^{nat}Cu}(p,x).
+It also represents  the first measurement of the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, as well as the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).
 The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
-Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($t\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).
+Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).
 
@@
 Finally, the production of \ce{^{90}Mo}  in the 40 - 90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
+Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40 - 90 MeV region.
 This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise monitor for charged particle dosimetry in irradiations up to approximately 24 hours in duration.
@@
 In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard PET emitters \ce{^{57}Ni},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, the $\beta^-$-therapy agent  \ce{^{64}Cu},  and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
-
-\ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a PET emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
-\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} - indeed, the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
+These include the non-standard positron emitters \ce{^{57}Ni},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, the $\beta^-$-therapy agent  \ce{^{64}Cu},  and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
+
+\ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a positron emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
+\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} - indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
+%ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
+ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
 The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
@@
 
-\ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET emitter, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Nickles2003,Qaim2008,QaimSyedM2011}.
-In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} cow and emits no observable gamma-rays or x-rays though decay, necessitating an imaging isotope to be paired with for quantification of its uptake and biodistribution  \cite{Herzog1993}.
+\ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET isotope, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011}.
+In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} cow and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
+Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
 Conventional production of \ce{^{86}Y} proceeds through low-energy (7 - 14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
@@
 Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often extremely difficult to separate out.
-As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% of all radio-yttrium activities produced.
-This is because the dominant radio-yttrium activity in 40-90 MeV \ce{^{nat}Nb}(p,x) is  \ce{^{87}Y}, the largest obstacle to high-specific activity production of  \ce{^{86}Y} due to the unnecessary patient dose it contributes,  its comparable half-life, and the fact that separation is impractical.
+\comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
+As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% radioisotopic purity.
+The  dominant yttrium radioisotope produced by  \ce{^{nat}Nb}(p,x) in the 40--90 MeV region is  \ce{^{87}Y} ($t_{1/2}=79.8\pm0.3$ h, $\epsilon^-$=100\% to \ce{^{87m}Sr} \cite{Johnson2015}).
 However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
-Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51-61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
-
-\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived PET emitter, whose  lifetime makes it useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
+% Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51-61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
+
+\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived positron emitter useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
 Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9 - 14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
-Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 50 -75\% radio-zirconium purity in the 50 - 90 MeV region.
+Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 10--20\% radioisotopic purity in the 50--90 MeV region.
 
 \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging PET emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
-It is typically produced using 8 - 15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{89}Nb}, and requires an enriched target (51.45\% natural abundance), but produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
+It is typically produced using 8 - 15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
 \ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
-\ce{^{90}Nb} may be produced directly with an approximately 360 mb peak cross section and 87\% radio-niobium purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radio-molybdenum purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold.
-However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity target impossible.
-
-Moving away from the potential PET emitters, \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the PET branch gives  \ce{^{64}Cu}  the possibility for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
-Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8 - 14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radio-copper purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20 - 30 MeV protons, and necessitates an enriched target (18.45\% natural abundance), lest the various other radio-coppers contaminate \ce{^{64}Cu}  purity \cite{Hilgers2003a,Szelecsenyi2005}.
+\ce{^{90}Nb} may be produced directly with an approximately 360 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
+However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
+
+% Moving away from the potential PET emitters, 
+\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
+The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the PET branch gives  \ce{^{64}Cu}  the possibility for real-time dose monitoring and verification \cite{Lewis2003,Bandari2014,mp500671j}.
+% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
+Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
+\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20 - 30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003a,Szelecsenyi2005}.
 More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
-\ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
-
-Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is an emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators for PET studies \cite{Kovacs1991}.
+% \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
+
+Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is a diagnostic and emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators
+% for PET studies
+\cite{Kovacs1991}.
 It is commonly produced via \ce{^{82}Kr}(p,n) at 10 - 15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
@@
 
+\comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
+
 % XXXXXX
@@
 
-In summation, we present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios.
-Nearly all cross sections have been reported with smaller uncertainties than previous measurements.
+We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios.
+Nearly all cross sections have been reported with higher precision than previous measurements.
 We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
@@
  This research used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
+
+%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
+Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
+% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
+
+This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
+Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.
 

### 2018-02-16 nb_px_paper/nb_px_paper.tex
Updated manuscript to use PRC document template class.

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Important note on usage                  %%
-%% -----------------------                  %%
-%% This file must be compiled with PDFLaTeX %%
-%% Using standard LaTeX will not work!      %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-% \documentclass[5p]{elsarticle}
-% Good for final formatting  - two column
-% 
-% \documentclass[3p,times]{elsarticle}
-\documentclass[3p]{elsarticle}
-% Good for proofing - single column
-%
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.1 distribution.
+%   Version 4.1r of REVTeX, August 2010
+%
+%   Copyright (c) 2009, 2010 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.1
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+superscriptaddress,
+onecolumn,
+linenumbers,
+notitlepage,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%showpacs,preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ aps,
+prc,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-1}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%                                          %%
+% %% Important note on usage                  %%
+% %% -----------------------                  %%
+% %% This file must be compiled with PDFLaTeX %%
+% %% Using standard LaTeX will not work!      %%
+% %%                                          %%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
+% % \documentclass[5p]{elsarticle}
+% % Good for final formatting  - two column
+% % 
+% % \documentclass[3p,times]{elsarticle}
+% \documentclass[3p]{elsarticle}
+% % Good for proofing - single column
+% %
 
@@
 \usepackage [autostyle, english = american]{csquotes}
-\usepackage{longtable}
+% \usepackage{longtable}
 \usepackage{subcaption}
@@
 
-\usepackage{lineno}
+% \usepackage{lineno}
+
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
 
@@
 % \usepackage{mathtools}
-\usepackage{natbib}
+\usepackage[sort&compress]{natbib}
 % \usepackage{biblatex}
 
-%% The `ecrc' package must be called to make the CRC functionality available
-\usepackage{ecrc}
-
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-%% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research B}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{A.S. Voyles et al.}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{nimb}
-% \jid{yspmi}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Nucl Instrum Meth B}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-\biboptions{sort&compress}
+% %% The `ecrc' package must be called to make the CRC functionality available
+% \usepackage{ecrc}
+% 
+% %% The ecrc package defines commands needed for running heads and logos.
+% %% For running heads, you can set the journal name, the volume, the starting page and the authors
+% 
+% %% set the volume if you know. Otherwise `00'
+% \volume{00}
+% 
+% %% set the starting page if not 1
+% \firstpage{1}
+% 
+% %% Give the name of the journal
+% \journalname{Nuclear Instruments and Methods in Physics Research B}
+% 
+% %% Give the author list to appear in the running head
+% %% Example \runauth{C.V. Radhakrishnan et al.}
+% \runauth{A.S. Voyles et al.}
+% 
+% %% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
+% %% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
+% %% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
+% %% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
+% 
+% %% Give the abbreviation of the Journal.
+% \jid{nimb}
+% % \jid{yspmi}
+% 
+% %% Give a short journal name for the dummy logo (if needed)
+% \jnltitlelogo{Nucl Instrum Meth B}
+% 
+% %% Hereafter the template follows `elsarticle'.
+% %% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
+% 
+% %% Elsevier CRC generally uses a numbered reference style
+% %% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
+% %% If using BibTeX, use the style file elsarticle-num.bst
+% 
+% %% End of ecrc-specific commands
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %% The amssymb package provides various useful mathematical symbols
+% \usepackage{amssymb}
+% %% The amsthm package provides extended theorem environments
+% \usepackage{amsthm}
+% 
+% %% The lineno packages adds line numbers. Start line numbering with
+% %% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+% %% for the whole article with \linenumbers after \end{frontmatter}.
+% %% \usepackage{lineno}
+% 
+% %% natbib.sty is loaded by default. However, natbib options can be
+% %% provided with \biboptions{...} command. Following options are
+% %% valid:
+% 
+% %%   round  -  round parentheses are used (default)
+% %%   square -  square brackets are used   [option]
+% %%   curly  -  curly braces are used      {option}
+% %%   angle  -  angle brackets are used    <option>
+% %%   semicolon  -  multiple citations separated by semi-colon
+% %%   colon  - same as semicolon, an earlier confusion
+% %%   comma  -  separated by comma
+% %%   numbers-  selects numerical citations
+% %%   super  -  numerical citations as superscripts
+% %%   sort   -  sorts multiple citations according to order in ref. list
+% %%   sort&compress   -  like sort, but also compresses numerical citations
+% %%   compress - compresses without sorting
+% %%
+% %% \biboptions{comma,round}
+
+% \biboptions{sort&compress}
 
@@
 
-\begin{frontmatter}
+% \begin{frontmatter}
+
+%\preprint{APS/123-QED}
+
+\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
+% \thanks{A footnote to the article title}%
+
+\author{Andrew S. Voyles}
+ \email{andrew.voyles@berkeley.edu}
+\affiliation{%
+ Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
+%  Authors' institution and/or address\\
+%  This line break forced with \textbackslash\textbackslash
+}% 
+\author{Lee A. Bernstein}
+\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
+\affiliation{%
+ Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
+%  Authors' institution and/or address\\
+%  This line break forced with \textbackslash\textbackslash
+}%
+\author{Eva R. Birnbaum}
+\affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+\author{Jonathan W. Engle}
+ \email{jwengle@wisc.edu}
+\affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
+\author{Stephen A. Graves}
+\affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
+\author{Toshihiko ??? Kawano}
+\affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+%  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
+\author{Amanda M. Lewis}%
+% \author{Eric F. Matthews}%
+%  \email{Second.Author@institution.edu}
+\affiliation{%
+ Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
+%  Authors' institution and/or address\\
+%  This line break forced with \textbackslash\textbackslash
+}%
+\author{Francois M. Nortier}
+\affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}
+
+% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
+% \author[ucb]{Andrew S. Voyles \corref{cor1}}
+% \ead{andrew.voyles@berkeley.edu}
+
+% \author[lbl]{M.S. Basunia}
+% 
+% \author[ucb]{J.C. Batchelder}
+% 
+% \author[llnl]{J.D. Bauer}
+% 
+% \author[geo]{T.A. Becker}
+
+% \author[ucb,lbl]{Lee A. Bernstein}
+
+% \author[lanl]{Eva R. Birnbaum}
+
+% \author[uwm]{Jonathan W. Engle}
+
+% \author[iowa]{Stephen A. Graves}
+
+% \author[ucb]{Amanda M. Lewis}
+
+% \author[lanl]{Francois M. Nortier}
+
+% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
+% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
+% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
+% % \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
+% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
+% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
+% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
+
+% \collaboration{MUSO Collaboration}%\noaffiliation
+% 
+% \author{Charlie Author}
+% %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
+% \affiliation{
+%  Second institution and/or address\\
+%  This line break forced% with \\
+% }%
+% \affiliation{
+%  Third institution, the second for Charlie Author
+% }%
+% \author{Delta Author}
+% \affiliation{%
+%  Authors' institution and/or address\\
+%  This line break forced with \textbackslash\textbackslash
+% }%
+% 
+% \collaboration{CLEO Collaboration}%\noaffiliation
+
+\date{\today}% It is always \today, today,
+             %  but any date may be explicitly specified
 
@@
 %%
-\title{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu}
+% \title{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu}
 
@@
 
-% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-\author[ucb]{Andrew S. Voyles \corref{cor1}}
-\ead{andrew.voyles@berkeley.edu}
-
-% \author[lbl]{M.S. Basunia}
-% 
-% \author[ucb]{J.C. Batchelder}
-% 
-% \author[llnl]{J.D. Bauer}
-% 
-% \author[geo]{T.A. Becker}
-
-\author[ucb,lbl]{Lee A. Bernstein}
-
-\author[lanl]{Eva R. Birnbaum}
-
-\author[uwm]{Jonathan W. Engle}
-
-\author[iowa]{Stephen A. Graves}
-
-\author[ucb]{Amanda M. Lewis}
-
-\author[lanl]{Francois M. Nortier}
+% 
+% % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
+% \author[ucb]{Andrew S. Voyles \corref{cor1}}
+% \ead{andrew.voyles@berkeley.edu}
+% 
+% % \author[lbl]{M.S. Basunia}
+% % 
+% % \author[ucb]{J.C. Batchelder}
+% % 
+% % \author[llnl]{J.D. Bauer}
+% % 
+% % \author[geo]{T.A. Becker}
+% 
+% 
+% \author[ucb,lbl]{Lee A. Bernstein}
+% 
+% 
+% \author[lanl]{Eva R. Birnbaum}
+% 
+% \author[uwm]{Jonathan W. Engle}
+% 
+% \author[iowa]{Stephen A. Graves}
+% 
+% \author[ucb]{Amanda M. Lewis}
+% 
+% 
+% \author[lanl]{Francois M. Nortier}
 
@@
 
-\cortext[cor1]{Corresponding author}
+% \cortext[cor1]{Corresponding author}
 % \cortext[cor2]{Principal corresponding author}
@@
 
-\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
-\address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
-% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-% \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
-\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
-\address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
-\address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
+% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
+% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
+% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
+% % \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
+% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
+% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
+% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
 
@@
 
-\comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
-
-\comment{Stephen: Unless you've already discussed this with co-authors, I would have someone from LANL (i.e. Meiring) instead or in addition.  Add one following discussion.}
-
-\comment{Comment on the Si production here?}
-
-\comment{Add CoH to codes also, and add extra physics language with Lee.}
+% \begin{description}
+% \item[Usage]
+% Secondary publications and information retrieval purposes.
+% \item[PACS numbers]
+% May be entered using the \verb+\pacs{#1}+ command.
+% \item[Structure]
+% You may use the \texttt{description} environment to structure your abstract;
+% use the optional argument of the \verb+\item+ command to give the category of each item. 
+% \end{description}
+\end{abstract}
+
+% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
+                             % Classification Scheme.
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+
+% \begin{abstract}
+
+\maketitle
 
@@
 
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
+% \end{abstract}
+
+% \begin{keyword}
+% %% keywords here, in the form: keyword \sep keyword
+% Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
+% 
+% %% MSC codes here, in the form: \MSC code \sep code
+% %% or \MSC[2008] code \sep code (2000 is the default)
+% 
+% \end{keyword}
+
+% \end{frontmatter}
 
@@
 %%
-\linenumbers
+% \linenumbers
 
@@
 \section{Introduction} \label{sec:intro}
+
+Referring to abstract:
+\comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
+
+\comment{Stephen: Unless you've already discussed this with co-authors, I would have someone from LANL (i.e. Meiring) instead or in addition.  Add one following discussion.}
+
+\comment{Comment on the Si production here?}
+
+\comment{Add CoH to codes also, and add extra physics language with Lee.}
 
@@
  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
- \caption{Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place.
+ \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place.
 The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell.
@@
 }
- \label{fig:target_stack}
 \end{figure}
@@
 % \addcontentsline{toc}{chapter}{Bibliography}
-\bibliographystyle{elsarticle-num}
+% \bibliographystyle{elsarticle-num}
+\bibliographystyle{apsrev4-1}
 % \bibliographystyle{ieeetr}

### 2018-02-17 nb_px_paper/nb_px_paper.tex
Started addressing hyphen/en-dash/em-dash usage, various comments.

@@
 
-\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
+\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40-90 MeV) on natural Nb}% Force line breaks with \\
 % \thanks{A footnote to the article title}%
@@
 The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
-A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 -- 89.74 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
-Cross sections were measured using the well-characterized \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
+A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
+Cross sections were measured using the well-characterized 
+% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
+\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
 Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
+\textred{The \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, }
 The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
-This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
-Comparisons against the reaction modeling codes EMPIRE and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    
+% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
+\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
+Comparisons against the reaction modeling codes CoH$_3$, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 
@@
 
-\maketitle
-
-% Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
-% The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
-% The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-% Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-% The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
-% This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
-
-% \comment{Karl:  \enquote{Comment to engender some discussion.
-I have a small concern here, reminiscent of what happened to our electron backstreaming paper in PRAB.
-To be publishable, even in NIMB, there has to be a crisp research question resolved, or some innovation.
-I think an angle that is missing here is that this is a new design of neutron generator, whose design maximizes the flux density (n/sec/cm2), although the total flux, while respectable, is not spectacular in itself.
-This is Lee's recent mantra, and I now understand its significance.
-Problematically, as Andrew has pointed out, we don't have the actual instrument paper published yet, so the thrust of the paper can't be too focused on the flux density issue, but a workable angle would be \enquote{given we have this new capability, this is an example of its power}.
-Let me suggest Lee provide a sentence for the abstract, and a few sentences of text in the appropriate spot.}}
-
-% \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
-
 % \end{abstract}
@@
 % \end{frontmatter}
+
+\maketitle
 
@@
 Referring to abstract:
-\comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
-
-\comment{Stephen: Unless you've already discussed this with co-authors, I would have someone from LANL (i.e. Meiring) instead or in addition.  Add one following discussion.}
-
-\comment{Comment on the Si production here?}
-
-\comment{Add CoH to codes also, and add extra physics language with Lee.}
+% \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
+
+\comment{Comment on the Si production here?  (see red text)}
+
+\comment{Add extra physics language with Lee.}
 
@@
 
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Herman2007,Koning2012}.
+Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH$_3$,EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
+
+\comment{Add in CoH3 model output from Toshihiko to all plots}
 

### 2018-02-23 nb_px_paper/nb_px_paper.tex
Corrected hyphen/en-dash/em-dash usage. Squashed various comments.

@@
 % \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
-\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
+\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence determination, with all activities quantified using high-purity germanium spectroscopy.
 Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
-\textred{The \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, }
+\textred{The \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded from proton fluence determination due to the production of \ce{^{22,24}Na} contamination by \ce{^{nat}Si}(p,x) activation of the silicone adhesive used for sealing foil packets.}}
 The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
@@
 alone,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases \cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
-The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many of the non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}.
+The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many
+% of the 
+non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
 \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
@@
 Indeed, the development of new dosimetry standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
-Charged particle dosimetry data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6-15\%) \cite{gul2001charged}.
+Charged particle dosimetry data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
 While work is needed to improve upon existing dosimetry data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
@@
 For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
-In these experiments, a series of monitor foils at each energy position allow one to measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude.
-\comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
+In these experiments, a series of monitor foils at each energy position allows one to indirectly measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
+% \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
 Both of these purposes make well-characterized dosimetry an invaluable asset to any activation experiment.
@@
 
-From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert - any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
+From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert --- any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
 Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
@@
 If you're trying to introduce the purpose of this paper, i.e.
-the establishment of a new monitor reaction, I would try to condense paragraphs 3-9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction.
+the establishment of a new monitor reaction, I would try to condense paragraphs 3--9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction.
 The rest of this content can be included in the discussion if you feel it is necessary.}
@@
 
-% The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
-%  The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a,doi:10.1063/1.3267832}.
-%  The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
-%  In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
-% While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
-% 
-% 
-% The present work features a pair of cross section measurements for the production of two emerging non-standard medical radionuclides: the positron emitter \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and the single - photon emission computed tomography (SPECT) tracer \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-% \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-% The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
-% In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-% The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma-ray in the process \cite{Burrows2007}.
-% This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma-ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-% Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
-% In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
-
-% \comment{cite theranostic papers, etc}
-
 One monitor reaction which satisfies these requirements is that of a new, intermediate-energy proton dosimetry standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
 Niobium is naturally mono-isotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
-\ce{^{90}Mo} also has excellent decay properties - its fairly long-lived lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
+\ce{^{90}Mo} also has excellent decay properties --- its fairly long-lived lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
 In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
@@
 The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo} ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) via the $^\text{nat}$Nb(p,x) reaction. 
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 32 other (p,x) production cross sections between 40 -- 90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 32 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
 These include the non-standard positron emission tomography (PET) agent \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
@@
 For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
-Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized - for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
+Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
 Using these length, width, and mass readings, the areal density (in mg/cm$^2$) for each foil was calculated, along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape - each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.793 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.607 mg/cm$^2$).
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
 The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
@@
 The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor - after end-of-beam (EoB), decay radiation emitted from these activated stainless steel foils may be used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-beam (EoB), decay radiation emitted from these activated stainless steel foils may be used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
-The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
+The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV --- this energy profile was used for all later analysis.
 At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
@@
 The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
-Samples were counted at fixed positions ranging 4.5 - 83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
+Samples were counted at fixed positions ranging 4.5--83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
 The foils were counted  for a period of 2 weeks following EoB, to accurately quantify all induced activities,  with dead time never exceeding 5\%.
@@
 This method is based on the assumption that the independent measurements of proton fluence from the 5 monitor reactions used in this work should all be consistent at each energy position.
-If the monitor reaction cross sections and MCNP6 - modeled energy distributions are both accurate, then any disagreement in the  observed proton fluences is due to a systematic uncertainty in the stack design, namely, the areal densities of the stack components \cite{Graves2016,Marus2015}.
+If the monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, then any disagreement in the  observed proton fluences is due to a systematic uncertainty in the stack design, namely, the areal densities of the stack components \cite{Graves2016,Marus2015}.
 This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
@@
 Due to the difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
-This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to the thick 6061 aluminum degraders (nominal 3-5 mg/cm$^2$, relative to nominal 1000-1400 mg/cm$^2$).
+This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to the thick 6061 aluminum degraders (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$).
 As such,  the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
@@
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1-7\%), proton fluence ($\pm$2-3\%), and foil areal density ($\pm$0.1-0.6\%).
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1--7\%), proton fluence ($\pm$2--3\%), and foil areal density ($\pm$0.1--0.6\%).
 \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
@@
 The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40 - 90 MeV region than for \ce{^{nat}Cu}(p,x) -  less than 3 existing measurements have been performed for the majority of the reactions presented here.
+Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90 MeV region than for \ce{^{nat}Cu}(p,x) ---  less than 3 existing measurements have been performed for the majority of the reactions presented here.
 Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of 3 data points in this energy region.
@@
 Furthermore, this work presents the first measurements of several observables in these mass regions.
-This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40 - 90 MeV region.
+This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region.
 It also represents  the first measurement of the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, as well as the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).
@@
 
-Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 2-3\% uncertainty level.
+Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 2--3\% uncertainty level.
 This is important, as it presents the first step towards characterizing this reaction for use as a proton dosimetry standard below 100 MeV.
@@
 In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-Finally, the production of \ce{^{90}Mo}  in the 40 - 90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
-Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40 - 90 MeV region.
+Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
+Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
 This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise monitor for charged particle dosimetry in irradiations up to approximately 24 hours in duration.
@@
 \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a positron emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
-\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} - indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
+\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} --- indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
 %ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
@@
 The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
-Lower-energy production via \ce{^{nat}Co}(p,3n) at 24-40 MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
+Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40 MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
 
@@
 Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
-Conventional production of \ce{^{86}Y} proceeds through low-energy (7 - 14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
-Alternatively, production at 33-43 MeV via \ce{^{88}Sr}(p,3n) has been proposed - this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
-Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often extremely difficult to separate out.
-\comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
+Conventional production of \ce{^{86}Y} proceeds through low-energy (7--14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
+Alternatively, production at 33--43 MeV via \ce{^{88}Sr}(p,3n) has been proposed --- this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
+Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often impractical to separate out by radiochemical means.
+% \comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
 As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% radioisotopic purity.
@@
 However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
-% Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51-61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
+% Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51--61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
 
 \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived positron emitter useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
-Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9 - 14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
+Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9--14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
 Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 10--20\% radioisotopic purity in the 50--90 MeV region.
@@
 \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging PET emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
-It is typically produced using 8 - 15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
+It is typically produced using 8--15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
 \ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
@@
 Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20 - 30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003a,Szelecsenyi2005}.
+\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003a,Szelecsenyi2005}.
 More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
@@
 \cite{Kovacs1991}.
-It is commonly produced via \ce{^{82}Kr}(p,n) at 10 - 15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
+It is commonly produced via \ce{^{82}Kr}(p,n) at 10--15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
 Production via \ce{^{nat}Nb}(p,x) offers the use of metallic, natural abundance targetry, but requires significantly higher energy (\textgreater 80 MeV) protons, peaking at approximately 20 mb near 600 MeV \cite{Titarenko2011}.
@@
 We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
@@
  The authors would like to particularly acknowledge the assistance and support of  Michael Gallegos and Don Dry in the LANL C-NR Countroom, David Reass and Mike Connors at LANSCE-IPF, and the LANSCE Accelerator Operations staff.
+
+We gratefully acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics.
+This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
+This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy
+Additional support has been provided by the U.S. Nuclear Regulatory Commission.
 
@@
 
-This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.
-
- \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers, as well as anyone else that you feel should be acknowledged here.}
+% This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
+% Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.
+
+%  \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers, as well as anyone else that you feel should be acknowledged here.}
 

### 2018-03-07 nb_px_paper/nb_px_paper.tex
Shortened introduction section. Squashed various comments.

@@
 
-\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40-90 MeV) on natural Nb}% Force line breaks with \\
+\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
 % \thanks{A footnote to the article title}%
@@
 A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
-The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
+The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
 A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
@@
 Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
-\textred{The \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded from proton fluence determination due to the production of \ce{^{22,24}Na} contamination by \ce{^{nat}Si}(p,x) activation of the silicone adhesive used for sealing foil packets.}}
 The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
@@
 \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-Comparisons against the reaction modeling codes CoH$_3$, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+Comparisons against the reaction modeling codes  CoH, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+% \textred{
+Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded from proton fluence determination.
+% }
+% \textred{
+To avoid inadvertently reporting enhanced proton fluence, the use of silicone adhesives for aluminum monitor foils is strongly discouraged.
+% }
 
@@
 
-Referring to abstract:
-% \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
-
-\comment{Comment on the Si production here?  (see red text)}
-
-\comment{Add extra physics language with Lee.}
+% Referring to abstract:
+% % \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
+% 
+% 
+% \comment{Comment on the Si production here?  (see red text)}
+% 
+% \comment{Add extra physics language with Lee.}
 
@@
 non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
-\comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
+% \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
 I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: In this context, I would make this definition based on what machines in the US are routinely used for medical isotope production - based on this, I agree with 200 MeV.
@@
 
-One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  dosimetry standards.
+One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.
 This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
-Indeed, the development of new dosimetry standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
-Charged particle dosimetry data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
-While work is needed to improve upon existing dosimetry data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
-\comment{Stephen: I'm having a hard time following this paragraph.
+Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}.
+Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
+While work is needed to improve upon existing monitor reaction data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
+This work in particular seeks to improve this range of options by characterizing a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as BLIP, IPF, or iThemba LABS.
+% \comment{Stephen: I'm having a hard time following this paragraph.
 Some of your syntax overlaps significantly with nuclear medicine \& medical physics terminology with different intended meanings.
@@
 
-Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field.
-All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
-\comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
+Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}.
+% All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
+% \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
 Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
-\comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
-Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of a monitor reaction's excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
+% \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
+Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
 This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
-This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this sensitivity to energy precludes their reliability as a beam current monitor.
-
-Moving to the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
-In this regime, the monitor reaction offers little-to-no energy sensitivity. 
-However,  in the pre-equilibrium regime, monitor reactions become extremely useful for determining the integral beam current. 
-While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon an entire target assembly.
-For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
-In these experiments, a series of monitor foils at each energy position allows one to indirectly measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
+This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.
+In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
+This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
+While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
+% For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
+% In these experiments, a
+A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
 % \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
-Both of these purposes make well-characterized dosimetry an invaluable asset to any activation experiment.
-
-In theory, nearly any radioisotope can serve as a reaction monitor, but those desired to be classified as a dosimetry standard possess several hallmark characteristics.
-The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
-Generally, this means selecting a radionuclide with a number of distinct gamma-rays.
-The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
-
-\comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
+Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.
+
+In theory, nearly any radioisotope can serve as a reaction monitor, but those desired to be classified as a monitor reaction standard possess several hallmark characteristics.
+% The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
+Primarily, this means selecting a radionuclide with a number of distinct gamma-rays with high intensities,  which can be used to uniquely identify it during post-activation assay.  
+% The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
+% \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
 Care should be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
 For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
-Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
-However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
-
-Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
-Ideally, the nucleus has a lifetime which is sufficiently long-lived to ensure that it may be quantified  conveniently and leisurely after end-of-beam without the majority if it decaying away.
-In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
+% Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
+% However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
+% Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
+Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
+% and leisurely 
+following end-of-beam.
+% without the majority if it decaying away.
+% In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
 For proper quantification, it is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
 This includes a precise and well-established half-life,  needed to  correct for decay losses, as well as well-characterized decay gamma-ray intensities.
-In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
-Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
-
-From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert --- any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current.
-Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
-For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
-However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectroscopy.
-For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
+% In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
+% Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
+From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily available
+% readily commercially available at an affordable price and is 
+generally chemically inert --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current.
+% Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
+% For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
+% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectroscopy.
+% For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
 Thickness selection will be subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
 % These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
-
-\comment{Stephen:  This is also a discussion point.
+% \comment{Stephen:  This is also a discussion point.
 If you're trying to introduce the purpose of this paper, i.e.
@@
 The rest of this content can be included in the discussion if you feel it is necessary.}
-Lastly, and perhaps most importantly for high-energy dosimetry applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
-This is typically mostly a concern for secondary neutrons produced through (z,xn) reactions on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
-Any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often a laborious task to separate out the fraction of secondary particles contributing to the total activation.
-
-One monitor reaction which satisfies these requirements is that of a new, intermediate-energy proton dosimetry standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
+Lastly, and perhaps most importantly for high-energy monitor reaction applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
+Typically, this is  mostly a concern for secondary neutrons produced through (z,xn) reactions, 
+% on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
+% Any
+but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often a laborious task to separate out the fraction of secondary particles contributing to the total activation.
+
+One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
 Niobium is naturally mono-isotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
@@
 The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo} ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) via the $^\text{nat}$Nb(p,x) reaction. 
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 32 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
 These include the non-standard positron emission tomography (PET) agent \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
 
-  \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
-
-  \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}
+%   \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
+%   
+%   \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}
 
@@
 The measurements described in this paper involve the use of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here.
-By expanding the available set of dosimetry standards and well-characterized isotope production excitation functions, this work should help optimize medical isotope production modalities, making more options   available for modern medical imaging and cancer therapy.
+By expanding the available set of monitor reaction standards and well-characterized isotope production excitation functions, this work should help optimize medical isotope production modalities, making more options   available for modern medical imaging and cancer therapy.
 
@@
 
-\subsection{Proton dosimetry}\label{sec:dosimetry}
-
-\comment{Stephen:  Still not a huge fan of the dosimetry terminology, but I would defer to the preference of those with more experience in the field. }
+\subsection{Proton fluence determination}\label{sec:dosimetry}
+
+% \comment{Stephen:  Still not a huge fan of the dosimetry terminology, but I would defer to the preference of those with more experience in the field. }
 
@@
 At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
-For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional dosimetry is thus needed to accurately normalize quantified EoB activities into cross sections.
+For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
 To this end, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
@@
 Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 2--3\% uncertainty level.
-This is important, as it presents the first step towards characterizing this reaction for use as a proton dosimetry standard below 100 MeV.
+This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
 The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
@@
 Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
-This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise monitor for charged particle dosimetry in irradiations up to approximately 24 hours in duration.
+This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.
 
@@
 
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH$_3$,EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
-
-\comment{Add in CoH3 model output from Toshihiko to all plots}
+Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH,EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
+
+\comment{Add in CoH model output from Toshihiko to all plots}
 

### 2018-03-07 dissertation/chap3.tex
Made temporray chapter 3 to hold language introducing Nb paper.

\chapter{Prexy Salaam}

\section{Faceplate Marginalia}

Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field. 
All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
% \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
% \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of a monitor reaction's excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this sensitivity to energy precludes their reliability as a beam current monitor.

Moving to the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
In this regime, the monitor reaction offers little-to-no energy sensitivity. 
However,  in the pre-equilibrium regime, monitor reactions become extremely useful for determining the integral beam current. 
While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon an entire target assembly.
For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
In these experiments, a series of monitor foils at each energy position allows one to indirectly measure the integral current at each position in the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
% \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.

In theory, nearly any radioisotope can serve as a reaction monitor, but those desired to be classified as a monitor reaction standard possess several hallmark characteristics.
The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.  
Generally, this means selecting a radionuclide with a number of distinct gamma-rays.
The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.

% \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
Care should be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.

Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
Ideally, the nucleus has a lifetime which is sufficiently long-lived to ensure that it may be quantified  conveniently and leisurely after end-of-beam without the majority if it decaying away.
In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
For proper quantification, it is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
This includes a precise and well-established half-life,  needed to  correct for decay losses, as well as well-characterized decay gamma-ray intensities.
In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.

From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily commercially available at an affordable price and is generally chemically inert --- any significant chemical changes during target preparation (significant oxidation, etc) will affect the target's areal density, systematically changing the measured integral current. 
Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectroscopy.
For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
Thickness selection will be subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction

% \comment{Stephen:  This is also a discussion point. If you're trying to introduce the purpose of this paper, i.e. the establishment of a new monitor reaction, I would try to condense paragraphs 3--9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction. The rest of this content can be included in the discussion if you feel it is necessary.}
Lastly, and perhaps most importantly for high-energy monitor reaction applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
This is typically mostly a concern for secondary neutrons produced through (z,xn) reactions on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
Any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often a laborious task to separate out the fraction of secondary particles contributing to the total activation.

\subsection{Promenade Exeter}

Inertia breakup Brookline.  Hebrew, prexy, and Balfour.  Salaam
applaud, puff teakettle.

\begin{quote}
Ugh servant Eulerian knowledge Prexy Lyman zig wiggly.  Promenade
adduce.  Yugoslavia piccolo Exeter.  Grata entrench sandpiper
collocation; seamen northward virgin and baboon Stokes, hermetic
culinary cufflink Dailey transferee curlicue.  Camille, Whittaker
harness shatter.  Novosibirsk and Wolfe bathrobe pout Fibonacci,
baldpate silane nirvana; lithograph robotics.  Krakow, downpour
effeminate Volstead?
\end{quote}

Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.
Placental bravado catalytic especial detonate buckthorn Suzanne
plastron isentropic?  Glory characteristic.  Denature?  Pigeonhole
sportsman grin historic stockpile.  Doctrinaire marginalia and art.
Sony tomography.  Aviv censor seventh, conjugal.  Faceplate emittance
borough airline.  Salutary.  Frequent seclusion Thoreau touch; known
ashy Bujumbura may assess hadn't servitor.  Wash, Doff, and Algorithm.

\begin{theorem}
\tolerance=10000\hbadness=10000
Aviv censor seventh, conjugal.  Faceplate emittance borough airline.  
Salutary.
\end{theorem}

Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.
Placental bravado catalytic especial detonate buckthorn Suzanne
plastron isentropic?  Glory characteristic.  Denature?  Pigeonhole
sportsman grin historic stockpile. Doctrinaire marginalia and art.
Sony tomography.  Aviv censor seventh, conjugal.  Faceplate emittance
borough airline.  Salutary.  Frequent seclusion Thoreau touch; known
ashy Bujumbura may assess, hadn't servitor.  Wash, Doff, Algorithm.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
1-2-3 & yes & no \\
\hline
Multiplan & yes & yes \\
\hline
Wordstar & no & no \\
\hline
\end{tabular}
\end{center}
\caption{Pigeonhole sportsman grin  historic stockpile.}
\end{table}
Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.
Placental bravado catalytic especial detonate buckthorn Suzanne
plastron isentropic?  Glory characteristic.  Denature?  Pigeonhole
sportsman grin historic stockpile. Doctrinaire marginalia and art.
Sony tomography.

\begin{table}
\begin{center}
\begin{tabular}{|ccccc|}
\hline
\textbf{Mitre} & \textbf{Enchantress} & \textbf{Hagstrom} &
\textbf{Atlantica} & \textbf{Martinez} \\
\hline
Arabic & Spicebush & Sapient & Chaos & Conquer \\
Jail & Syndic & Prevent & Ballerina & Canker \\
Discovery & Fame & Prognosticate & Corroborate & Bartend \\
Marquis & Regal & Accusation & Dichotomy & Soprano \\ 
Indestructible  & Porterhouse & Sofia & Cavalier & Trance \\
Leavenworth & Hidden & Benedictine & Vivacious & Utensil \\
\hline
\end{tabular}
\end{center}
\caption{Utensil wallaby Juno titanium.}
\end{table}

Aviv censor seventh, conjugal.  Faceplate emittance borough airline.
Salutary.  Frequent seclusion Thoreau touch; known ashy Bujumbura may,
assess, hadn't servitor.  Wash\cite{cmusic}, Doff, and Algorithm.

\begin{figure}
\[ \begin{picture}(90,50)
  \put(0,0){\circle*{5}}
  \put(0,0){\vector(1,1){31.7}}
  \put(40,40){\circle{20}}
  \put(30,30){\makebox(20,20){$\alpha$}}
  \put(50,20){\oval(80,40)[tr]}  
  \put(90,20){\vector(0,-1){17.5}}
  \put(90,0){\circle*{5}}
\end{picture}
 \]
\caption{Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.  
Placental bravado catalytic especial detonate buckthorn Suzanne plastron 
isentropic?  Glory characteristic.  Denature?  Pigeonhole sportsman grin.}
\end{figure}

Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.
Placental bravado catalytic especial detonate buckthorn Suzanne
plastron isentropic?  Glory characteristic.  Denature?  Pigeonhole
sportsman grin historic stockpile. Doctrinaire marginalia and art.
Sony tomography.  Aviv censor seventh, conjugal.  Faceplate emittance
borough airline.\cite{fm} Salutary.  Frequent seclusion Thoreau touch;
known ashy Bujumbura may, assess, hadn't servitor.  Wash, Doff, and
Algorithm.

\begin{itemize}
\item Davidson witting and grammatic.  Jukes foundry mesh sting speak,
Gillespie, Birmingham Bentley.  Hedgehog, swollen McGuire; gnat.
Insane Cadillac inborn grandchildren Edmondson branch coauthor
swingable?  Lap Kenney Gainesville infiltrate.  Leap and dump?
Spoilage bluegrass.  Diesel aboard Donaldson affectionate cod?
Vermiculite pemmican labour Greenberg derriere Hindu.  Stickle ferrule
savage jugging spidery and animism.
\item Hoofmark and Avogadro ionosphere.  
\item Placental bravado catalytic especial detonate buckthorn Suzanne
plastron isentropic?
\item Glory characteristic.  Denature?  Pigeonhole sportsman grin
historic stockpile.
\item Doctrinaire marginalia and art.  Sony tomography.  
\item Aviv censor seventh, conjugal.
\item Faceplate emittance borough airline.  
\item Salutary.  Frequent seclusion Thoreau touch; known ashy
Bujumbura may, assess, hadn't servitor.  Wash, Doff, and Algorithm.
\end{itemize}

Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.
Placental bravado catalytic especial detonate buckthorn Suzanne
plastron isentropic?  Glory characteristic.  Denature?  Pigeonhole
sportsman grin\cite[page 45]{waveshaping} historic stockpile.
Doctrinaire marginalia and art. Sony tomography.  Aviv censor seventh,
conjugal. Faceplate emittance borough airline.  Salutary.  Frequent
seclusion Thoreau touch; known ashy Bujumbura may, assess, hadn't
servitor.  Wash, Doff, and Algorithm.

\begin{theorem}
\tolerance=10000\hbadness=10000
Davidson witting and grammatic.  Hoofmark and Avogadro ionosphere.  
Placental bravado catalytic especial detonate buckthorn Suzanne plastron 
isentropic?
\end{theorem}

### 2018-03-07 nb_px_paper/nb_px_paper.tex
Moving back to NIM-B template.

@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.1 distribution.
-%   Version 4.1r of REVTeX, August 2010
-%
-%   Copyright (c) 2009, 2010 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
-\documentclass[%
- reprint,
-superscriptaddress,
-onecolumn,
-linenumbers,
-notitlepage,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%showpacs,preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps,
-prc,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%                                          %%
-% %% Important note on usage                  %%
-% %% -----------------------                  %%
-% %% This file must be compiled with PDFLaTeX %%
-% %% Using standard LaTeX will not work!      %%
-% %%                                          %%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-% % \documentclass[5p]{elsarticle}
-% % Good for final formatting  - two column
+% % ****** Start of file apssamp.tex ******
 % %
-% % \documentclass[3p,times]{elsarticle}
-% \documentclass[3p]{elsarticle}
-% % Good for proofing - single column
+% %   This file is part of the APS files in the REVTeX 4.1 distribution.
+% %   Version 4.1r of REVTeX, August 2010
 % %
+% %   Copyright (c) 2009, 2010 The American Physical Society.
+% %
+% %   See the REVTeX 4 README file for restrictions and more information.
+% %
+% % TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% % as well as the rest of the prerequisites for REVTeX 4.1
+% %
+% % See the REVTeX 4 README file
+% % It also requires running BibTeX. The commands are as follows:
+% %
+% %  1)  latex apssamp.tex
+% %  2)  bibtex apssamp
+% %  3)  latex apssamp.tex
+% %  4)  latex apssamp.tex
+% %
+% \documentclass[%
+%  reprint,
+% superscriptaddress,
+% onecolumn,
+% linenumbers,
+% notitlepage,
+% %groupedaddress,
+% %unsortedaddress,
+% %runinaddress,
+% %frontmatterverbose, 
+% %preprint,
+% %showpacs,preprintnumbers,
+% %nofootinbib,
+% %nobibnotes,
+% %bibnotes,
+%  amsmath,amssymb,
+%  aps,
+% prc,
+% %prb,
+% %rmp,
+% %prstab,
+% %prstper,
+% %floatfix,
+% ]{revtex4-1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Important note on usage                  %%
+%% -----------------------                  %%
+%% This file must be compiled with PDFLaTeX %%
+%% Using standard LaTeX will not work!      %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
+% \documentclass[5p]{elsarticle}
+% Good for final formatting  - two column
+% 
+% \documentclass[3p,times]{elsarticle}
+% Final formatting
+\documentclass[3p]{elsarticle}
+% Good for proofing - single column
+%
 
@@
 
-% \usepackage{lineno}
+\usepackage{lineno}
 
@@
 % \usepackage{mathtools}
-\usepackage[sort&compress]{natbib}
+% \usepackage[sort&compress]{natbib}
 % \usepackage{biblatex}
 
-% %% The `ecrc' package must be called to make the CRC functionality available
-% \usepackage{ecrc}
-% 
-% %% The ecrc package defines commands needed for running heads and logos.
-% %% For running heads, you can set the journal name, the volume, the starting page and the authors
-% 
-% %% set the volume if you know. Otherwise `00'
-% \volume{00}
-% 
-% %% set the starting page if not 1
-% \firstpage{1}
-% 
-% %% Give the name of the journal
-% \journalname{Nuclear Instruments and Methods in Physics Research B}
-% 
-% %% Give the author list to appear in the running head
-% %% Example \runauth{C.V. Radhakrishnan et al.}
-% \runauth{A.S. Voyles et al.}
-% 
-% %% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-% %% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-% %% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-% %% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-% 
-% %% Give the abbreviation of the Journal.
-% \jid{nimb}
-% % \jid{yspmi}
-% 
-% %% Give a short journal name for the dummy logo (if needed)
-% \jnltitlelogo{Nucl Instrum Meth B}
-% 
-% %% Hereafter the template follows `elsarticle'.
-% %% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-% 
-% %% Elsevier CRC generally uses a numbered reference style
-% %% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-% %% If using BibTeX, use the style file elsarticle-num.bst
-% 
-% %% End of ecrc-specific commands
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %% The amssymb package provides various useful mathematical symbols
-% \usepackage{amssymb}
-% %% The amsthm package provides extended theorem environments
-% \usepackage{amsthm}
-% 
-% %% The lineno packages adds line numbers. Start line numbering with
-% %% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-% %% for the whole article with \linenumbers after \end{frontmatter}.
-% %% \usepackage{lineno}
-% 
-% %% natbib.sty is loaded by default. However, natbib options can be
-% %% provided with \biboptions{...} command. Following options are
-% %% valid:
-% 
-% %%   round  -  round parentheses are used (default)
-% %%   square -  square brackets are used   [option]
-% %%   curly  -  curly braces are used      {option}
-% %%   angle  -  angle brackets are used    <option>
-% %%   semicolon  -  multiple citations separated by semi-colon
-% %%   colon  - same as semicolon, an earlier confusion
-% %%   comma  -  separated by comma
-% %%   numbers-  selects numerical citations
-% %%   super  -  numerical citations as superscripts
-% %%   sort   -  sorts multiple citations according to order in ref. list
-% %%   sort&compress   -  like sort, but also compresses numerical citations
-% %%   compress - compresses without sorting
-% %%
-% %% \biboptions{comma,round}
-
-% \biboptions{sort&compress}
+%% The `ecrc' package must be called to make the CRC functionality available
+\usepackage{ecrc}
+
+%% The ecrc package defines commands needed for running heads and logos.
+%% For running heads, you can set the journal name, the volume, the starting page and the authors
+
+%% set the volume if you know. Otherwise `00'
+\volume{00}
+
+%% set the starting page if not 1
+\firstpage{1}
+
+%% Give the name of the journal
+\journalname{Nuclear Instruments and Methods in Physics Research B}
+
+%% Give the author list to appear in the running head
+%% Example \runauth{C.V. Radhakrishnan et al.}
+\runauth{A.S. Voyles et al.}
+
+%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
+%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
+%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
+%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
+
+%% Give the abbreviation of the Journal.
+\jid{nimb}
+% \jid{yspmi}
+
+%% Give a short journal name for the dummy logo (if needed)
+\jnltitlelogo{Nucl Instrum Meth B}
+
+%% Hereafter the template follows `elsarticle'.
+%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
+
+%% Elsevier CRC generally uses a numbered reference style
+%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
+%% If using BibTeX, use the style file elsarticle-num.bst
+
+%% End of ecrc-specific commands
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+%% The amsthm package provides extended theorem environments
+\usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%
+%% \biboptions{comma,round}
+
+\biboptions{sort&compress}
 
@@
 
-% \begin{frontmatter}
+\begin{frontmatter}
 
@@
 
-\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
-% \thanks{A footnote to the article title}%
-
-\author{Andrew S. Voyles}
- \email{andrew.voyles@berkeley.edu}
-\affiliation{%
- Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
-%  Authors' institution and/or address\\
-%  This line break forced with \textbackslash\textbackslash
-}% 
-\author{Lee A. Bernstein}
-\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
-\affiliation{%
- Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
-%  Authors' institution and/or address\\
-%  This line break forced with \textbackslash\textbackslash
-}%
-\author{Eva R. Birnbaum}
-\affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-\author{Jonathan W. Engle}
- \email{jwengle@wisc.edu}
-\affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
-\author{Stephen A. Graves}
-\affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
-\author{Toshihiko ??? Kawano}
-\affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-%  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
-\author{Amanda M. Lewis}%
-% \author{Eric F. Matthews}%
-%  \email{Second.Author@institution.edu}
-\affiliation{%
- Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
-%  Authors' institution and/or address\\
-%  This line break forced with \textbackslash\textbackslash
-}%
-\author{Francois M. Nortier}
-\affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}
+% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
+% % \thanks{A footnote to the article title}%
+% 
+% \author{Andrew S. Voyles}
+%  \email{andrew.voyles@berkeley.edu}
+% \affiliation{%
+%  Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
+% %  Authors' institution and/or address\\
+% %  This line break forced with \textbackslash\textbackslash
+% }% 
+% \author{Lee A. Bernstein}
+% \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
+% \affiliation{%
+%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
+% %  Authors' institution and/or address\\
+% %  This line break forced with \textbackslash\textbackslash
+% }%
+% \author{Eva R. Birnbaum}
+% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+% \author{Jonathan W. Engle}
+%  \email{jwengle@wisc.edu}
+% \affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
+% \author{Stephen A. Graves}
+% \affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
+% \author{Toshihiko ??? Kawano}
+% \affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+% %  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
+% \author{Amanda M. Lewis}%
+% % \author{Eric F. Matthews}%
+% %  \email{Second.Author@institution.edu}
+% \affiliation{%
+%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
+% %  Authors' institution and/or address\\
+% %  This line break forced with \textbackslash\textbackslash
+% }%
+% \author{Francois M. Nortier}
+% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}
 
 % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-% \author[ucb]{Andrew S. Voyles \corref{cor1}}
-% \ead{andrew.voyles@berkeley.edu}
+\author[ucb]{Andrew S. Voyles \corref{cor1}}
+\ead{andrew.voyles@berkeley.edu}
 
@@
 
-% \author[ucb,lbl]{Lee A. Bernstein}
-
-% \author[lanl]{Eva R. Birnbaum}
-
-% \author[uwm]{Jonathan W. Engle}
-
-% \author[iowa]{Stephen A. Graves}
-
-% \author[ucb]{Amanda M. Lewis}
-
-% \author[lanl]{Francois M. Nortier}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
-% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
-% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-% % \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
-% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
-% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
-% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
-
-% \collaboration{MUSO Collaboration}%\noaffiliation
-% 
-% \author{Charlie Author}
-% %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
-% \affiliation{
-%  Second institution and/or address\\
-%  This line break forced% with \\
-% }%
-% \affiliation{
-%  Third institution, the second for Charlie Author
-% }%
-% \author{Delta Author}
-% \affiliation{%
-%  Authors' institution and/or address\\
-%  This line break forced with \textbackslash\textbackslash
-% }%
-% 
-% \collaboration{CLEO Collaboration}%\noaffiliation
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-% \title{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu}
+\author[lbl,ucb]{Lee A. Bernstein}
+
+\author[lanl]{Eva R. Birnbaum}
+
+\author[uwm]{Jonathan W. Engle}
+\ead{jwengle@wisc.edu}
+
+\author[iowa]{Stephen A. Graves}
+
+\author[tlanl]{Toshihiko ??? Kawano}
+
+\author[ucb]{Amanda M. Lewis}
+
+\author[lanl]{Francois M. Nortier}
+
+\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
+\address[lbl]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
+% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
+% \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
+\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
+\address[lanl]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+\address[iowa]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
+\address[tlanl]{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+
+% % \collaboration{MUSO Collaboration}%\noaffiliation
+% % 
+% % \author{Charlie Author}
+% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
+% % \affiliation{
+% %  Second institution and/or address\\
+% %  This line break forced% with \\
+% % }%
+% % \affiliation{
+% %  Third institution, the second for Charlie Author
+% % }%
+% % \author{Delta Author}
+% % \affiliation{%
+% %  Authors' institution and/or address\\
+% %  This line break forced with \textbackslash\textbackslash
+% % }%
+% % 
+% % \collaboration{CLEO Collaboration}%\noaffiliation
+% 
+% \date{\today}% It is always \today, today,
+%              %  but any date may be explicitly specified
+% 
+% %% Title, authors and addresses
+% 
+% %% use the tnoteref command within \title for footnotes;
+% %% use the tnotetext command for the associated footnote;
+% %% use the fnref command within \author or \address for footnotes;
+% %% use the fntext command for the associated footnote;
+% %% use the corref command within \author for corresponding author footnotes;
+% %% use the cortext command for the associated footnote;
+% %% use the ead command for the email address,
+% %% and the form \ead[url] for the home page:
+% %%
+\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}
 
@@
 
-% \begin{keyword}
-% %% keywords here, in the form: keyword \sep keyword
-% Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
 % 
@@
 % 
-% \end{keyword}
-
-% \end{frontmatter}
-
-\maketitle
+\end{keyword}
+
+\end{frontmatter}
+
+% \maketitle
 
@@
 %%
-% \linenumbers
+\linenumbers
 
@@
 At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
-The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectroscopy, which started approximately 7 hours following end-of-beam.
+The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectroscopy, which started approximately 6 hours following end-of-beam.
 
@@
 The calibrated detector efficiencies, along with gamma-ray intensities for each transition, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
-For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of Appendix \ref{data}.
 As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
@@
 % \addcontentsline{toc}{chapter}{Bibliography}
-% \bibliographystyle{elsarticle-num}
-\bibliographystyle{apsrev4-1}
+\bibliographystyle{elsarticle-num}
+% \bibliographystyle{apsrev4-1}
 % \bibliographystyle{ieeetr}

### 2018-03-16 nb_px_paper/nb_px_paper.tex
Revising analysis, up through section 2.3.

@@
 
-\newcommand{\subfigimg}[3][,]{%
+% \newcounter{subfigure}[figure]
+
+\newcommand{\subfigimg}[4][,]{%
   \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
   \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
+  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
   \phantom{\usebox1}% Insert appropriate spcing
 }
+% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}
 
@@
 
-\author[tlanl]{Toshihiko ??? Kawano}
+\author[tlanl]{Toshihiko \textred{???} Kawano}
 
@@
 Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
-The calibrated detector efficiencies, along with gamma-ray intensities for each transition, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
-For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of Appendix \ref{data}.
+The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
+For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+Data for photon attenuation coefficients are taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
 As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
@@
 In addition, cumulative cross sections will be reported whenever it is impossible to use decay spectroscopy to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction.
 
@@
 As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
+In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
 \begin{equation}
-A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_i\pp{0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
+A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_{i,0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
 \end{equation}
@@
 Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-These estimates of average beam energy in each foil are useful for the preliminary stack design, as the A\&Z calculation provide reasonable approximations of 1-D proton transport due to its treatment of ionization and multiple Coulomb scattering.
-However, for final energy determination and analysis, a more rigorous method of proton transport is needed.
+These estimates of average beam energy in each foil are useful for the preliminary stack design, as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering.
+However, for final energy and fluence determinations, a more rigorous method of proton transport is needed.
 The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
-In addition, MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to reactions, as well as production of secondary particles.
+In addition, MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
 As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.
@@
 This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
-This energy corresponds to a 6061 aluminum areal density of 2.53\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
+This energy corresponds to a 6061 aluminum areal density of 2.52\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
 
 The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
-As expected, the 2.53\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
+As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
 In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
@@
  \caption{Result of the variance minimization performed by adjusting the degrader density in MCNP6 simulations of the target stack.
-A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.53\% greater than nominal.
+A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.52\% greater than nominal.
 The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.59]{a)}{./figures/before_minimization_plot.pdf}
+        \subfigimg[scale=0.59]{a)}{./figures/before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.59]{b)}{./figures/after_minimization_plot.pdf}
+        \subfigimg[scale=0.59]{b)}{./figures/after_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
     \end{subfigure}%
-    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.53\%.
-A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
-The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} monitor channels is caused by activation through (n,x) reactions from the secondary neutron flux.
-By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.\comment{Lee: I think you should make the fonts ridiculously larger.
-}}
+    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%.
+A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
      \label{fig:variance_mins}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:before_subtraction}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.59]{b)}{./figures/after_subtraction_plot.pdf}{80}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:after_subtraction}
+    \end{subfigure}%
+    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by activation through (n,x) reactions from the secondary neutron flux.
+By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
+     \label{fig:na_subtraction}
 \end{figure*}
@@
 
-Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40 - 90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
+Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40--90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
 For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
@@
 
-\comment{Make sure to comment on comparison with EMPIRE / TALYS  / TENDL here, after Amanda finishes modeling work.}
+% \comment{Make sure to comment on comparison with EMPIRE / TALYS  / TENDL here, after Amanda finishes modeling work.}
+
+In this work, cumulative cross sections are reported for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectroscopy to distinguish direct production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
+The reactions with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
+The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
+All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
+
+The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
+% \cite{add_level_density_models_here}. 
+The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it.
+% \cite{add_level_density_models_here}.
+The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
+
+% \def\arraystretch{1.5}
+\begin{table}
+ \caption{Default settings for the reactions codes}
+ \label{tab:defaults}
+ \resizebox{\textwidth}{!}{%
+\begin{tabular}{ c c c c}
+
+ \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
+ EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
+ TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
+  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
+
+\end{tabular}
+}
+\end{table}
+
+The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
+Only total channel residual cross sections with experimental data through the full rise and fall of the peak, that have only one reaction channel, and that are at least 1\% of the total reaction cross section are discussed in detail.
+Residual production cross sections that do not exhibit the full rise and fall of the peak, which is identified as the compound portion of the cross section, do not provide enough information to analyze the calculations.
+Some residuals, such as \ce{^{88}Zr}, can be produced by multiple reaction channels, in this case by (p,$\alpha$2n) and by (p,2n4n).
+Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
+Very small channels, with cross sections less than 1\% of the total reaction cross section are excluded because the modeling of their cross sections is sensitive  to that of the more dominant  channels.
+There are three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section --- \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
+
+The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70 MeV}, is well within the compound regime for the entire energy region of this experiment.
+The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
+The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50 MeV, and the data clearly show the full rise, peak, and fall of the compound cross section.
+In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011\cite{Titarenko2011}.
+
+In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak at higher energies.
+For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
+For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
+
+The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
+For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
+The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
+\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the three codes are all consistent, but  too small, in magnitude.
+
+The \ce{^{90}Nb} production cross section exhibits a persistent \enquote{pre-equilibrium} tail that keeps the channel open  well after the compound cross section has fallen away. 
+TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
+EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
 
@@
 
-\comment{Placeholder to reserve space for pre-equilibrium / spin discussion.}
+% \comment{Placeholder to reserve space for pre-equilibrium / spin discussion.}
 
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/51Cr.pdf}
+        \subfigimg[scale=0.47]{}{./figures/51Cr.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.465]{}{./figures/52gMn.pdf}
+        \subfigimg[scale=0.465]{}{./figures/52gMn.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/54Mn.pdf}
+        \subfigimg[scale=0.47]{}{./figures/54Mn.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/55Co.pdf}
+        \subfigimg[scale=0.47]{}{./figures/55Co.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.465]{}{./figures/56Ni.pdf}
+        \subfigimg[scale=0.465]{}{./figures/56Ni.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/57Co.pdf}
+        \subfigimg[scale=0.47]{}{./figures/57Co.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/57Ni.pdf}
+        \subfigimg[scale=0.47]{}{./figures/57Ni.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/58Co.pdf}
+        \subfigimg[scale=0.47]{}{./figures/58Co.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.465]{}{./figures/59Fe.pdf}
+        \subfigimg[scale=0.465]{}{./figures/59Fe.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/60Co.pdf}
+        \subfigimg[scale=0.47]{}{./figures/60Co.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/61Cu.pdf}
+        \subfigimg[scale=0.47]{}{./figures/61Cu.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/64Cu.pdf}
+        \subfigimg[scale=0.47]{}{./figures/64Cu.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/82mRb.pdf}
+        \subfigimg[scale=0.47]{}{./figures/82mRb.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/83Sr.pdf}
+        \subfigimg[scale=0.47]{}{./figures/83Sr.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/85Y.pdf}
+        \subfigimg[scale=0.47]{}{./figures/85Y.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/86Y.pdf}
+        \subfigimg[scale=0.47]{}{./figures/86Y.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/86Zr.pdf}
+        \subfigimg[scale=0.47]{}{./figures/86Zr.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/87Y.pdf}
+        \subfigimg[scale=0.47]{}{./figures/87Y.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/87Zr.pdf}
+        \subfigimg[scale=0.47]{}{./figures/87Zr.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/88Y.pdf}
+        \subfigimg[scale=0.47]{}{./figures/88Y.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/88Zr.pdf}
+        \subfigimg[scale=0.47]{}{./figures/88Zr.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/89Nb.pdf}
+        \subfigimg[scale=0.47]{}{./figures/89Nb.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/89Zr.pdf}
+        \subfigimg[scale=0.47]{}{./figures/89Zr.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.465]{}{./figures/90Mo.pdf}
+        \subfigimg[scale=0.465]{}{./figures/90Mo.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/90Nb.pdf}
+        \subfigimg[scale=0.47]{}{./figures/90Nb.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/91mNb.pdf}
+        \subfigimg[scale=0.47]{}{./figures/91mNb.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/92mNb.pdf}
+        \subfigimg[scale=0.47]{}{./figures/92mNb.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/93mMo.pdf}
+        \subfigimg[scale=0.47]{}{./figures/93mMo.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/52Mn_IBR.pdf}
+        \subfigimg[scale=0.47]{}{./figures/52Mn_IBR.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/58Co_IBR.pdf}
+        \subfigimg[scale=0.47]{}{./figures/58Co_IBR.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/85Y_IBR.pdf}
+        \subfigimg[scale=0.47]{}{./figures/85Y_IBR.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/87Y_IBR.pdf}
+        \subfigimg[scale=0.47]{}{./figures/87Y_IBR.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/89Nb_IBR.pdf}
+        \subfigimg[scale=0.47]{}{./figures/89Nb_IBR.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}

### 2018-03-16 nb_px_paper/nb_px_paper.tex
Merged in Lee's comments on the Amanda physics discussion.

@@
 
-A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
-The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
+Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
+However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions needed to establish beam characteristics in this energy range needed to perform quantitative cross section measurements.
+To address this need, a target stack consisting of thin Nb, Cu, and Al monitor foils using a 100 MeV proton beam at the Los Alamos National Laboratory's Isotope Production Facility was irradiated in order to establish \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} as a reaction monitor for intermediate energy protons and to benchmark state-of-the-art reaction model codes in this energy region.
+% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
+% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
 A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
@@
 For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
-The reactions with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
+This, in turn, offers the opportunity to use these data to gain insight into the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
+The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
 The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
+The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study pre-equilibrium reaction mechanisms.
 All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
@@
 % \cite{add_level_density_models_here}. 
-The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it.
+The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
 % \cite{add_level_density_models_here}.
@@
 
-The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
-Only total channel residual cross sections with experimental data through the full rise and fall of the peak, that have only one reaction channel, and that are at least 1\% of the total reaction cross section are discussed in detail.
-Residual production cross sections that do not exhibit the full rise and fall of the peak, which is identified as the compound portion of the cross section, do not provide enough information to analyze the calculations.
-Some residuals, such as \ce{^{88}Zr}, can be produced by multiple reaction channels, in this case by (p,$\alpha$2n) and by (p,2n4n).
-Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
-Very small channels, with cross sections less than 1\% of the total reaction cross section are excluded because the modeling of their cross sections is sensitive  to that of the more dominant  channels.
-There are three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section --- \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
+% The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
+% Only total channel residual 
+Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
+% that have only one reaction channel, and that are 
+and at least 1\% of the total reaction cross section.
+% are discussed in detail. 
+% Residual production
+Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
+% the compound portion of the cross section
+being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
+% Some residuals, such as 
+Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2n4n)  are also not discussed in depth. 
+% Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
+% Very small channels, 
+We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
+% are excluded because the modeling of their cross sections is 
+because their behavior is extremely sensitive  to  more dominant  channels.
+The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
 
@@
 
-In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak at higher energies.
+In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
 For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
@@
 
-The \ce{^{90}Nb} production cross section exhibits a persistent \enquote{pre-equilibrium} tail that keeps the channel open  well after the compound cross section has fallen away. 
+The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
 TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.

### 2018-03-18 nb_px_paper/nb_px_paper.tex
Updated variance minimization, Na22/24 subtraction, and final fluence plot.

@@
 % \textred{
-Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded from proton fluence determination.
+Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
 % }
@@
  \centering
- \includegraphics[scale=0.1,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
+ \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
@@
 
-The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
-As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
-In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
-\comment{Insert text here to describe our Na22 / Si production hypothesis.  }
-It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
-This phenomenon is observed for the \ce{^{nat}Cu}(p,x)\ce{^{56}Co} monitor reaction as well, though to a much smaller degree.
-In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
-Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils.
-The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively.
-The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
-This serves as an example of the importance of selecting monitor reaction products inaccessible through (n,x) channels, as noted previously.
-However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.
-
 \begin{figure}
  \centering
- \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.5\linewidth]{./figures/variation_curve-crop.pdf}
+
  % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
@@
 The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
- \comment{Stephen: Half-width figure: Larger text and axes tick-marks would be nice. }
  \label{fig:variation_curve}
@@
 
-\begin{figure*}
+\begin{figure}
     \centering
@@
     \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%.
-A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
+A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
+Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
      \label{fig:variance_mins}
-\end{figure*}
-
-\begin{figure*}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[scale=0.57]{a)}{./figures/Na22_activity_compare.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:Na22_activity_compare}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.49\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[scale=0.57]{b)}{./figures/Na24_activity_compare.pdf}{180}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:Na24_activity_compare}
+    \end{subfigure}%
+    \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
+At low energies, experimentally observed apparent \ce{^{22,24}Na} activities in each Al foil packet are consistent with IAEA recommendations, but diverge at higher energies as the \ce{^{nat}Si}(p,x)\ce{^{22}Na} exit channels begin to open up.
+\ce{^{22,24}Na} activities consistent with TENDL-2015 estimates are observed in each Nb and Cu foil packet as well, confirming that contamination may be attributed to activation of silicone adhesives.}
+     \label{fig:Na_activity_compare}
+\end{figure}
+
+The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
+As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
+In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
+% \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
+It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0 MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
+This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6 MeV), though to a much smaller degree.
+In both cases, this disparity is caused by the fact that the Kapton tape used for sealing foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
+\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\% \ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3 MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6 MeV).
+\ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
+In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
+The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.
+
+These compensating factors  contribute to \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} production being competitive with the \ce{^{nat}Al}(p,x)\ce{^{22}Na} production route.
+This is made made obvious when comparing the total measured activities of \ce{^{22}Na} and \ce{^{24}Na} in each Al foil packet (which combines both Al- and Si-based production routes), relative to the expected EoB activities for each reaction channel, presented in \autoref{fig:Na_activity_compare}.
+Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
+Several observations are immediately obvious.
+At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.
+At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90 MeV.
+For the \ce{^{24}Na} production, we see a similar behavior, though since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude, only a minor increase in apparent \ce{^{24}Na} activity is seen.
+The measured EoB \ce{^{22}Na} and \ce{^{24}Na} activities seen  in all Cu and Nb foil positions are also shown here, which are seen to be consistent with the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{22}Na} yields.
+The observed \ce{^{24}Na} activities also follow the shape of the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{24}Na} yields, albeit smaller in magnitude at the higher energy positions.
+
+While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
+The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to the number of assumptions involved in such a calculation.
+The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
+These have been taken as 10\% (stoichiometric basis) and 4.79 mg/cm$^2$ (based on bulk density), respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
+In principle, it would be possible  to subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
+The results of this  may be seen in \autoref{fig:na_subtraction} --- following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
+While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
+Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
+While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
+% In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
+% Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils.
+% The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively.
+% The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
+This serves as a pointed example of the importance of selecting monitor reaction products inaccessible through channels aside from the primary reaction (\ce{^{nat}Al}(p,x)\ce{^{22,24}Na}, in this case ), as noted previously.
+% However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.
+
+% Avoud using al and silicone
+
+\begin{figure}
     \centering
@@
     \end{subfigure}%
-    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by activation through (n,x) reactions from the secondary neutron flux.
+    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.
+Following subtraction of \ce{^{22,24}Na} activities observed in the silicone adhesive of Nb and Cu foils in the same energy \enquote{compartment}, the consistency of the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction improves  dramatically.
 By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
      \label{fig:na_subtraction}
-\end{figure*}
+\end{figure}
 
@@
 As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
-In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail-ratio increases as more  secondary protons are produced upstream.
+In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail ratio increases as more  secondary protons are produced upstream.
 As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.
@@
  \centering
- \includegraphics[scale=.8]{./figures/fluence_plot.pdf}
+ \includegraphics[width=0.5\linewidth]{./figures/Nb_ptallies.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
+The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
+As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
+ \label{fig:Nb_ptallies}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
@@
 This is due to a combination of beam utilization, as well as scattering.}
- \comment{Stephen:  Half-width figure: Larger text and axes tick-marks would be nice. }
  \label{fig:fluence_plot}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=.8]{./figures/Nb_ptallies.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
-The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
-As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
- \comment{Stephen: Half-width figure: Larger text and axes tick-marks would be nice. }
- \label{fig:Nb_ptallies}
 \end{figure}
@@
 In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
-\comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
+% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
 This blister   shows the location where the primary proton beam was incident upon the foil.
@@
 Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003a,Szelecsenyi2005}.
+\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
 More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
@@
 
+First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
+We intend to do the same for our next proton irradiation at LBL.
+
+We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
+This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
+
 % XXXXXX

### 2018-03-18 nb_px_paper/nb_px_paper.tex
Finished final revisions through Section 2.

@@
 
-An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the  \ce{^{nat}Al}(p,x)\ce{^{24}Na} observed fluence (the upper set of points), and the uncertainty-weighted average fluence from the  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn} and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions (the lower set of points).
-To determine the final fluence assignments for the Nb foils, uncertainty-weighted linear regression was used to fit the various fluence measurements.
-This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
-As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
+An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
+Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
+In the interest of surety of because they are consistent, the uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
+Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
+These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport model, as well as an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
+Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly more aggressive fluence loss throughout the stack.
+These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
+% This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
+% As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
 % The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections
@@
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final weighted-fit proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions.
-A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence.
-A clear loss of fluence  is visible, dropping by approximately 8.1\% from the incident fluence of 202.2 nAh over the length of the target stack.
+ \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions.
+%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
+  A clear loss of fluence  is visible, dropping by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.
 This is due to a combination of beam utilization, as well as scattering.}
@@
 The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
-The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified in the $2\sigma$ confidence interval in \autoref{fig:fluence_plot}).
+The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).
 
@@
 This blister   shows the location where the primary proton beam was incident upon the foil.
-Based on the \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the average fluence at each energy position (seen in \autoref{fig:fluence_plot}), a fluence of 202.2$\pm$5.4 nAh was calculated to be incident upon the target stack, which shows excellent agreement with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
-This incident fluence dropped by approximately 8.1\% to  185.9 $\pm$3.4 nAh over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
+Based on the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the mean fluence at each energy position (seen in \autoref{fig:fluence_plot}).
+A fluence of 198.8$\pm$6.7 nAh was calculated to be incident upon the target stack using the MCNP6 fluence model, and a  fluence of 196.9$\pm$11.3 nAh using the linear fit model, both of which are consistent with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
+As fluence loss in the target box's entrance window scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance will underestimate the nominal fluence incident upon the box.
+This incident fluence dropped by approximately 8.9\% to  180.9 $\pm$5.4 nAh (and by 7.2\% to  182.7 $\pm$13.5 nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
 This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

### 2018-03-20 nb_px_paper/nb_px_paper.tex
Updated all independent Cu cross section figures to final draft version.

@@
 %%
-\listoftodos
+% \listoftodos
 
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.59]{a)}{./figures/before_minimization_plot.pdf}{50}
+    \begin{subfigure}[t]{0.50\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{a)}{./figures/before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
     \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
+     \begin{subfigure}[t]{0.50\textwidth}
         \centering
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.59]{b)}{./figures/after_minimization_plot.pdf}{50}
+        \subfigimg[width=\linewidth]{b)}{./figures/after_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.57]{a)}{./figures/Na22_activity_compare.pdf}{50}
+    \begin{subfigure}[t]{0.50\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.57]{b)}{./figures/Na24_activity_compare.pdf}{180}
+        \subfigimg[width=\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
+    \begin{subfigure}[t]{0.50\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.59]{b)}{./figures/after_subtraction_plot.pdf}{80}
+        \subfigimg[width=\linewidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
 This blister   shows the location where the primary proton beam was incident upon the foil.
-Based on the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the mean fluence at each energy position (seen in \autoref{fig:fluence_plot}).
+The \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used to determine the uncertainty-weighted mean fluence at each energy position (seen in \autoref{fig:fluence_plot}).
 A fluence of 198.8$\pm$6.7 nAh was calculated to be incident upon the target stack using the MCNP6 fluence model, and a  fluence of 196.9$\pm$11.3 nAh using the linear fit model, both of which are consistent with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
 As fluence loss in the target box's entrance window scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 8.9\% to  180.9 $\pm$5.4 nAh (and by 7.2\% to  182.7 $\pm$13.5 nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
+This incident fluence dropped by approximately 8.9\% to  180.9$\pm$5.4 nAh (and by 7.2\% to  182.7$\pm$13.5 nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
 This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
@@
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1--7\%), proton fluence ($\pm$2--3\%), and foil areal density ($\pm$0.1--0.6\%).
-\comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--7\%), proton fluence ($\pm$4--6\%), and foil areal density ($\pm$0.1--0.6\%).
+% \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
 
@@
 \ce{^{52m}Mn}\,($\sigma_c$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & --\cmmnt{\hrulefill}              \\
+\ce{^{54}Mn}\,($\sigma_i$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & --\cmmnt{\hrulefill}              \\
 \ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & --\cmmnt{\hrulefill}              \\
@@
 \ce{^{61}Cu}\,($\sigma_c$)    & $48.8\pm1.5$            & $54.4\pm1.7$            & $63.7\pm2.1$            & $70.3\pm2.1$            & $79.5\pm2.7$            & $158.2\pm3.2$           \\
-\ce{^{64}Cu}\,($\sigma_c$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
+\ce{^{64}Cu}\,($\sigma_i$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
 \end{tabular}
@@
 \ce{^{89}Zr}\,($\sigma_i$)   & $203.8\pm5.3$           & $235.4\pm6.6$           & $287.5\pm6.8$           & $250.3\pm5.8$           & $54.6\pm1.1$            & $15.61\pm0.31$          \\
-\ce{^{90}Mo}\,($\sigma_c$)    & $20.6\pm0.7$            & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.4\pm1.9$            & $120.3\pm2.9$           & $24.38\pm0.71$          \\
+\ce{^{90}Mo}\,($\sigma_i$)    & $20.6\pm0.7$            & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.4\pm1.9$            & $120.3\pm2.9$           & $24.38\pm0.71$          \\
 \ce{^{90}Nb}\,($\sigma_i$)    & $152.9\pm4.7$           & $169.3\pm4.8$           & $204.7\pm5.8$           & $265.2\pm7.8$           & $363.4\pm9.8$           & $165.2\pm4.5$           \\
 \ce{^{91m}Nb}\,($\sigma_c$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $67.0\pm4.2$            \\
-\ce{^{92m}Nb}\,($\sigma_c$)   & $42.2\pm1.2$            & $45.7\pm1.2$            & $48.8\pm1.2$            & $51.6\pm1.3$            & $54.5\pm1.4$            & $60.4\pm1.2$            \\
-\ce{^{93m}Mo}\,($\sigma_c$)   & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
+\ce{^{92m}Nb}\,($\sigma_i$)   & $42.2\pm1.2$            & $45.7\pm1.2$            & $48.8\pm1.2$            & $51.6\pm1.3$            & $54.5\pm1.4$            & $60.4\pm1.2$            \\
+\ce{^{93m}Mo}\,($\sigma_i$)   & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
 \end{tabular}
@@
 
-Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 2--3\% uncertainty level.
+Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
 This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
@@
 \ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
-\ce{^{90}Nb} may be produced directly with an approximately 360 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
+\ce{^{90}Nb} may be produced directly with an approximately 370 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
 However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
@@
 
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{./figures/86Y.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
+ \label{fig:86Y}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
+ \label{fig:90Mo}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
+ \label{fig:90Nb}
+\end{figure}
+
 In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
@@
 
-\comment{Feel free to expand / suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
-
-\comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
-
-First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
+% \comment{Feel free to expand / suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
+
+% \comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
+
+Finally, we wish to urge caution in future stacked-target activation experiments by avoiding the use of silicone adhesive-based tapes for foil containment, especially when paired with the use of Al monitor foils.
+Acrylic-based tape options are commercially available, and are immune from (p,x) production of \ce{^{22,24}Na} activities, due to being of too low-Z for these reaction channels to be possible.
+Even with subtraction of \ce{^{22,24}Na} activities though irradiating a Kapton tape \enquote{blank} or similar, we observe the Al monitor channels to measure consistently higher proton fluence than via Cu monitor channels, by 5--8\%.
+If Al monitors are used in conjunction with silicone-based tapes, even with subtraction of excess \ce{^{22}Na} activities, a systematically enhanced fluence may be determined, leading to cross sections reported with inaccurately diminished magnitude.
+Furthermore, since data for monitor reactions are often self-referencing, the propagated impact of this systematic enhancement in fluence may have far-reaching consequences for both medical isotope production, as well as for  the evaluated nuclear data libraries, which use these proton activation experiments as input.
+
+% First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
 We intend to do the same for our next proton irradiation at LBL.
-
-We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
+% 
+% We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
 This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
@@
 We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
 Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
@@
 % % \end{longtable}
-Table of decay data  for observed gamma-rays. 
-The  values for lifetime and gamma-ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
-
-\comment{I had to remove about 30 of the lines I used from this table (removing the weakest lines in nuclides with even more lines than shown here, but never removing lines in nuclides with only 2 or less), as even splitting the data into 2 tables created tables too large to fit on a single page.
+% Table of decay data  for observed gamma-rays. 
+The   lifetimes and gamma-ray branching ratios  listed in these tables were used for all calculations of measured cross sections reported in this work, and have been taken from the most recent edition of  Nuclear Data Sheets for a particular mass chain  \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
+
+% \comment{I had to remove about 30 of the lines I used from this table (removing the weakest lines in nuclides with even more lines than shown here, but never removing lines in nuclides with only 2 or less), as even splitting the data into 2 tables created tables too large to fit on a single page.
 My purpose here was 1) to show that I used multiple lines to quantify each nuclide (increasing confidence in results), and 2) to list all the used \ce{^{90}Mo} lines, since they form the basis of it as a monitor.
@@
 
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH,EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
-
-\comment{Add in CoH model output from Toshihiko to all plots}
+Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH-3.5.1, EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
+
+% \comment{Add in CoH model output from Toshihiko to all plots}
 
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/51Cr.pdf}{50}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/51Cr.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
     \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
+     \begin{subfigure}[t]{0.495\textwidth}
         \centering
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.465]{}{./figures/52gMn.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/52Mn.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:52Mn}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/52gMn.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
          \refstepcounter{subfigure}\label{fig:52gMn}
     \end{subfigure}%
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[width=\linewidth]{}{./figures/52mMn.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:52mMn}
+    \end{subfigure}%
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \begin{subfigure}[t]{0.495\textwidth}
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/54Mn.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/54Mn.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
     \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/55Co.pdf}{50}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/55Co.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
         \refstepcounter{subfigure} \label{fig:55Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.465]{}{./figures/56Ni.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:56Ni}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/57Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:57Co}
     \end{subfigure}%
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/57Ni.pdf}{50}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/56Ni.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:56Ni}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/57Co.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:57Co}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/57Ni.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/58Co.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/58Co.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \begin{subfigure}[t]{0.495\textwidth}
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.465]{}{./figures/59Fe.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/58gCo.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:59Fe}
+                 \refstepcounter{subfigure}\label{fig:58gCo}
     \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/60Co.pdf}{50}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/58mCo.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:60Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/61Cu.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:61Cu}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/64Cu.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:64Cu}
+        \refstepcounter{subfigure} \label{fig:58mCo}
     \end{subfigure}%
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/82mRb.pdf}{50}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/59Fe.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:59Fe}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/60Co.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:60Co}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/61Cu.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:61Cu}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/64Cu.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:64Cu}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/82mRb.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/83Sr.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/83Sr.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
          \refstepcounter{subfigure}\label{fig:83Sr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/85Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/86Y.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:86Y}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/86Zr.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:86Zr}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/87Y.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Y}
     \end{subfigure}%
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/87Zr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:87Zr}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/88Y.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Y}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/85Y.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:85Y}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/85gY.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:85gY}
     \end{subfigure}%
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \begin{subfigure}[t]{0.495\textwidth}
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/88Zr.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/85mY.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:88Zr}
+                 \refstepcounter{subfigure}\label{fig:85mY}
     \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/89Nb.pdf}{50}
+%      \begin{subfigure}[t]{0.495\textwidth}
+%         \centering
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \subfigimg[width=\linewidth]{}{./figures/86Y.pdf}{50}
+% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+%                  \refstepcounter{subfigure}\label{fig:86Y}
+%     \end{subfigure}
+%     \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/86Zr.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:89Nb}
+        \refstepcounter{subfigure} \label{fig:86Zr}
     \end{subfigure}%
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \begin{subfigure}[t]{0.495\textwidth}
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/89Zr.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/87Y.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89Zr}
+                 \refstepcounter{subfigure}\label{fig:87Y}
     \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.465]{}{./figures/90Mo.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:90Mo}
-    \end{subfigure}%
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:87gY}
+    \end{subfigure}
 %     \caption{Decay curves used to verify photopeak transition assignment.
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/90Nb.pdf}{50}
+%      \begin{subfigure}[t]{0.495\textwidth}
+%         \centering
+% %         \includegraphics[width=\textwidth]{./figures/target2.png}
+%         \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
+% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+%                  \refstepcounter{subfigure}\label{fig:87gY}
+%     \end{subfigure}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/87mY.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:87mY}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/87Zr.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:87Zr}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/88Y.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:90Nb}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
+         \refstepcounter{subfigure}\label{fig:88Y}
+    \end{subfigure}%
+     \begin{subfigure}[t]{0.495\textwidth}
         \centering
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/91mNb.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/88Zr.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:91mNb}
+         \refstepcounter{subfigure}\label{fig:88Zr}
     \end{subfigure}%
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/92mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:92mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/93mMo.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:93mMo}
+         \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[width=\linewidth]{}{./figures/89Nb.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:89Nb}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         \refstepcounter{subfigure}\label{fig:89gNb}
     \end{subfigure}%
@@
 (a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p5}
+     \label{fig:xs_curves_p8}
 \end{figure*}
 
+\begin{figure*}
+    \centering    
+%          \begin{subfigure}[t]{0.495\textwidth}
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+%         \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+%          \refstepcounter{subfigure}\label{fig:89gNb}
+%     \end{subfigure}%
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/89mNb.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:89mNb}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/89Zr.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:89Zr}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\textwidth]{./figures/target2.png}
+        \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
+%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+                 \refstepcounter{subfigure}\label{fig:91mNb}
+    \end{subfigure}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
+%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+        \refstepcounter{subfigure} \label{fig:92mNb}
+    \end{subfigure}%
+    \\
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         \refstepcounter{subfigure}\label{fig:93mMo}
+    \end{subfigure}%
+%     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+     \label{fig:xs_curves_p7}
+\end{figure*}
+
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[t]{0.495\textwidth}
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+%          \refstepcounter{subfigure}\label{fig:93mMo}
+%     \end{subfigure}%
+% %      \begin{subfigure}[t]{0.495\textwidth}
+% %         \centering
+% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% % %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+% %         \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
+% % %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+% %          \refstepcounter{subfigure}\label{fig:91mNb}
+% %     \end{subfigure}%
+% %     \\
+% %     \begin{subfigure}[t]{0.495\textwidth}
+% %         \centering
+% % %         \includegraphics[width=\textwidth]{./figures/target2.png}
+% %         \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
+% % %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
+% %                  \refstepcounter{subfigure}\label{fig:92mNb}
+% %     \end{subfigure}
+% %      \begin{subfigure}[t]{0.495\textwidth}
+% %         \centering
+% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
+% % %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+% %         \refstepcounter{subfigure} \label{fig:93mMo}
+% %     \end{subfigure}%
+% %     \caption{Decay curves used to verify photopeak transition assignment.
+(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+%      \label{fig:xs_curves_p5}
+% \end{figure*}
+
 % 
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/52Mn_IBR.pdf}{50}
+    \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/52Mn_IBR.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.47]{}{./figures/58Co_IBR.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/58Co_IBR.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \begin{subfigure}[t]{0.495\textwidth}
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/85Y_IBR.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/85Y_IBR.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
@@
     \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.47]{}{./figures/87Y_IBR.pdf}{50}
+     \begin{subfigure}[t]{0.495\textwidth}
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \subfigimg[width=\linewidth]{}{./figures/87Y_IBR.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
@@
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \begin{subfigure}[t]{0.495\textwidth}
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.47]{}{./figures/89Nb_IBR.pdf}{50}
+        \subfigimg[width=\linewidth]{}{./figures/89Nb_IBR.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}

### 2018-03-20 nb_px_paper/nb_px_paper.tex
Final draft.  Sent to co-authors for final comments.

@@
 E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{52m}Mn}\,($\sigma_c$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{54}Mn}\,($\sigma_i$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & --\cmmnt{\hrulefill}              \\
-\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & --\cmmnt{\hrulefill}              \\
-\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{57}Ni}\,($\sigma_c$)    & $1.416\pm0.039$         & $1.164\pm0.030$         & $1.370\pm0.033$         & $2.074\pm0.051$         & $1.543\pm0.035$         & $0.02638\pm0.00077$     \\
-\ce{^{57}Co}\,($\sigma_i$)    & $38.78\pm0.99$          & $34.42\pm0.84$          & $35.06\pm0.81$          & $47.3\pm1.1$            & $47.0\pm1.1$            & $3.227\pm0.081$         \\
-\ce{^{58}Co}\,($\sigma_c$)    & $55.7\pm3.5$            & $53.2\pm4.1$            & $41.8\pm2.9$            & $32.8\pm2.5$            & $38.4\pm3.4$            & $62.7\pm3.4$            \\
-\ce{^{58g}Co}\,($\sigma_i$)   & $13.6\pm2.3$            & $10.5\pm1.9$            & $5.9\pm1.6$             & $7.6\pm1.3$             & $7.0\pm1.7$             & $1.13\pm0.31$           \\
-\ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
-\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & --\cmmnt{\hrulefill}        \\
-\ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
-\ce{^{61}Cu}\,($\sigma_c$)    & $48.8\pm1.5$            & $54.4\pm1.7$            & $63.7\pm2.1$            & $70.3\pm2.1$            & $79.5\pm2.7$            & $158.2\pm3.2$           \\
-\ce{^{64}Cu}\,($\sigma_i$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
+\ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
+\ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
+\ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
+\ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
+\ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
+\ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
+\ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
+\ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
+\ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
+\ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
+\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
 \end{tabular}
@@
 E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{82m}Rb}\,($\sigma_c$)   & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{83}Sr}\,($\sigma_c$)    & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{85}Y}\,($\sigma_c$)     & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{85g}Y}\,($\sigma_i$)    & $2.286\pm0.057$         & $2.01\pm0.15$           & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{85m}Y}\,($\sigma_i$)    & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{86}Zr}\,($\sigma_c$)    & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{86}Y}\,($\sigma_i$)     & $32.25\pm0.89$          & $40.3\pm1.1$            & $39.0\pm1.0$            & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{87}Zr}\,($\sigma_c$)    & $45.8\pm5.8$            & $27.1\pm1.7$            & $31.5\pm1.5$            & $48.5\pm2.9$            & $37.7\pm1.6$            & $1.13\pm0.10$           \\
-\ce{^{87}Y}\,($\sigma_i$)     & $106.3\pm5.8$           & $52.9\pm1.7$            & $59.6\pm1.5$            & $87.8\pm2.9$            & $66.3\pm1.6$            & $2.93\pm0.10$           \\
-\ce{^{87g}Y}\,($\sigma_i$)    & $27.0\pm5.4$            & $7.1\pm1.2$             & $6.41\pm0.55$           & $5.6\pm2.1$             & $2.59\pm0.45$           & $0.949\pm0.045$         \\
-\ce{^{87m}Y}\,($\sigma_i$)    & $79.2\pm2.0$            & $45.8\pm1.2$            & $53.2\pm1.4$            & $82.1\pm2.0$            & $63.7\pm1.5$            & $1.983\pm0.093$         \\
-\ce{^{88}Zr}\,($\sigma_c$)    & $153.7\pm3.9$           & $140.0\pm3.5$           & $61.0\pm1.7$            & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.8\pm1.3$            \\
-\ce{^{88}Y}\,($\sigma_i$)     & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.0\pm1.3$             & $9.96\pm0.33$           \\
-\ce{^{89}Nb}\,($\sigma_c$)    & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $176\pm12$          & $209.0\pm4.3$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{89g}Nb}\,($\sigma_i$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $142\pm12$          & $181.7\pm4.1$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{89m}Nb}\,($\sigma_i$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.9\pm2.0$            & $27.3\pm1.4$            & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{89}Zr}\,($\sigma_i$)   & $203.8\pm5.3$           & $235.4\pm6.6$           & $287.5\pm6.8$           & $250.3\pm5.8$           & $54.6\pm1.1$            & $15.61\pm0.31$          \\
-\ce{^{90}Mo}\,($\sigma_i$)    & $20.6\pm0.7$            & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.4\pm1.9$            & $120.3\pm2.9$           & $24.38\pm0.71$          \\
-\ce{^{90}Nb}\,($\sigma_i$)    & $152.9\pm4.7$           & $169.3\pm4.8$           & $204.7\pm5.8$           & $265.2\pm7.8$           & $363.4\pm9.8$           & $165.2\pm4.5$           \\
-\ce{^{91m}Nb}\,($\sigma_c$)   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $67.0\pm4.2$            \\
-\ce{^{92m}Nb}\,($\sigma_i$)   & $42.2\pm1.2$            & $45.7\pm1.2$            & $48.8\pm1.2$            & $51.6\pm1.3$            & $54.5\pm1.4$            & $60.4\pm1.2$            \\
-\ce{^{93m}Mo}\,($\sigma_i$)   & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
+\ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
+\ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
+\ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
+\ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
+\ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
+\ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
+\ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
+\ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
+\ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
+\ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
+\ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
+\ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
 \end{tabular}
@@
 E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.027$         & $0.581\pm0.038$         & $0.598\pm0.083$         & $0.81\pm0.12$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.068$         & $0.804\pm0.091$         & $0.858\pm0.084$         & $0.767\pm0.086$         & $0.82\pm0.11$         & $0.982\pm0.075$    \vspace{1em}     \\ 
+\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
 E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.029$         & $0.724\pm0.072$         & $0.736\pm0.072$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.045$         & $0.865\pm0.036$         & $0.893\pm0.032$         & $0.936\pm0.038$         & $0.961\pm0.032$         & $0.676\pm0.040$         \\
-\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $0.193\pm0.018$         & $0.1304\pm0.0074$         &      --\cmmnt{\hrulefill}         & --\cmmnt{\hrulefill}              \\ \bottomrule
+\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
+\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
 \end{tabular}
@@
 % Table of decay data  for observed gamma-rays. 
-The   lifetimes and gamma-ray branching ratios  listed in these tables were used for all calculations of measured cross sections reported in this work, and have been taken from the most recent edition of  Nuclear Data Sheets for a particular mass chain  \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
+The   lifetimes and gamma-ray branching ratios  listed in these tables were used for all calculations of measured cross sections reported in this work, and have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain  \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
 

### 2018-03-23 nb_px_paper/cover_letter.tex
Created cover letter for NIM submission.

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{booktabs,siunitx}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Editorial Board \\
Nuclear Instruments and Methods in Physics Research Section B: \\
Beam Interactions with Materials and Atoms}

\begin{flushleft}
{\large\bf Andrew S. Voyles}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill The University of California, Berkeley \\
\hfill 1106B Etcheverry Hall, Berkeley, CA  94720-1730 \\
\hfill (presently) +47 486 43 444 \\ 
\hfill (normally) +1 (850) 281-0217 or +1 (510) 486-7310 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{To whom it may concern:}

  \renewcommand*{\thefootnote}{\alph{footnote}}

\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40--90 MeV) on natural Nb}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.  This manuscript describes an original work conducted by myself, the first and corresponding author, along with my co-authors and collaborators Lee A. Bernstein\footnotemark[1]\footnotemark[2], Eva R. Birnbaum\footnotemark[3], Jonathan W. Engle\footnotemark[4], Stephen A. Graves\footnotemark[5], Toshihiko Kawano\footnotemark[6], Amanda M. Lewis\footnotemark[2], and Francois M. Nortier\footnotemark[3].

\footnotetext[1]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
\footnotetext[2]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
\footnotetext[3]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
\footnotetext[4]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
\footnotetext[5]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
\footnotetext[6]{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}

\noindent This work described in this manuscript is a measurement of 38 unique cross sections spanning 40--90 MeV for the \ce{^{nat}Nb}(p,x) and \ce{^{nat}Cu}(p,x) reactions, along with 5 independent measurements of isomer branching ratios for pairs of radioisotope isomer/ground states. This is part of a recent, ongoing effort at UC Berkeley and Lawrence Berkeley National Laboratory to address the gaps in existing nuclear data which have been identified by the applications community, focusing in particular on the production of novel and emerging medical radioisotopes. The primary motivation for this work is to provide the most comprehensive characterization of the \ce{Nb}(p,4n)\ce{^{90}Mo} reaction, which has been proposed as a new monitor reaction standard for the in-beam measurement  of proton fluence in energetic (\textgreater 40 MeV) proton beams.

\noindent The methodology used to measure these cross sections involved a stacked-target activation of thin (25--50 \SI{}{\micro\meter}) metal foils,  at the Los Alamos National Laboratory's Isotope Production Facility (LANL-IPF). Target foils of natural Niobium metal were irradiated with a nominal 100 MeV proton beam, along with Copper and Aluminum monitor foils at each energy position.   This stack design allows for measurement of cross sections at multiple energies within a single irradiation. Our work also makes use of the ``variance minimization'' techniques described by S.A. Graves, \emph{et. al.}\footnotemark[7] to significantly reduce the systematic uncertainties associated with energy assignment, typical in many stacked-target irradiations.

\footnotetext[7]{S.A. Graves, \emph{et. al.}, NIM B: 386, 44--53 (2016), doi:10.1016/j.nimb.2016.09.018}

\noindent Several major novel contributions are reported in the present work. Most notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level. 
This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.
In addition, the \ce{^{nat}Nb}(p,x) measurements in this work fill in the extremely sparse data in this energy region, and have been measured with the highest precision relative to existing literature data. 
Indeed, nearly all cross sections for both \ce{^{nat}Nb}(p,x) and \ce{^{nat}Cu}(p,x) have been reported with higher precision than previous measurements.
We also report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
We  use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
Finally, we present evidence for \ce{^{22,24}Na} contamination of the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reaction channels, due to activation of silicon via \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}  in the silicone-based adhesive used for sealing foils.
This phenomenon has been observed as an unattributable systematic enhancement of apparent \ce{^{22,24}Na}-based fluence monitors in prior work. 
We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid unintentionally reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
% Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

%%

% Furthermore, this work presents the first measurements of several observables in these mass regions.
% This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region.
% It also represents  the first measurement of the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, as well as the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
% The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).

% Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
% This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
% \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed, which makes activity quantification trivial.
% In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
% Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
% Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.

%%

\noindent The attached manuscript is an original work which bears no significant overlap with any journal or conference papers published by any of the authors herein. Previous measurements exist in the literature for nearly all of the cross sections presented in this work, though our measurements nearly exclusively have the highest precision to date.
% in the energy region for this work. 
The most recent previous measurements of the \ce{^{nat}Cu}(p,x) reactions are generally by  S.A. Graves, \emph{et. al.}\footnotemark[7], and E. Garrido, \emph{et. al.}\footnotemark[8], and the most recent previous measurements of the \ce{^{nat}Nb}(p,x) reactions are generally by Y.E. Titarenko, \emph{et. al.}\footnotemark[9], and G.F. Steyn, \emph{et. al.}\footnotemark[10]

Several notable experts have been proposed as potential reviewers for this manuscript: Md. Uddin of the Atomic Energy Research Establishment, Bangladesh (\url{md.shuzauddin@yahoo.com}), Steve Wender of Los Alamos National Laboratory  (\url{wender@lanl.gov}), Ron Nelson of Los Alamos National Laboratory  	   (\url{rnelson@lanl.gov	}), Steven Yates of the University of Kentucky	  (\url{yates@uky.edu	}), Arjan Plompen of the Belgian Joint Research Centre	   (\url{Arjan.Plompen@ec.europa.eu	}), Roland Beyer of Helmholtz-Zentrum Dresden-Rossendorf	  (\url{roland.beyer@hzdr.de	}), and Zsolt Revay of the Technical University of Munich	  (\url{zsolt.revay@frm2.tum.de	}).  All of these individuals are highly experienced in the nuclear data community, and have many years of experience in nuclear reaction evaluation and cross section measurements.

As a physicist with a background in ion beam interactions and accelerator physics, I believe that Mark Breese would be the best-qualified editor to handle this paper during the review process. In addition, I have worked with him previously for the publication of a recent article\footnotemark[11], and had a very smooth experience - it would be a pleasure to work with him once more. However, any of the editorial staff with the technical background to properly evaluate the manuscript would be welcome on our end.  This would primarily involve a familiarity with activation experiments and nuclear spectroscopy.

\footnotetext[8]{E. Garrido, \emph{et. al.}, NIM B: 383 Supplement C, 191--212 (2016), doi:10.1016/j.nimb.2016.07.011}
\footnotetext[9]{Y.E. Titarenko, \emph{et. al.}, Phys. At. Nucl., 74, 4, 537 (2011), doi:10.1134/S106377881104017X}
\footnotetext[10]{G.F. Steyn, \emph{et. al.},  J. Korean Phys. Soc., 59, 23, 1991--1994 (2011), doi:10.3938/jkps.59.1991}
\footnotetext[11]{A.S. Voyles, \emph{et. al.}, NIM B: 410, 230--239, (2017) doi:10.1016/j.nimb.2017.08.021}

If I may make one personal request, it would mean a great deal to me if the processing of this manuscript can be expedited in any way, to be able to get it to the referees as quickly as possible without any loss of integrity to the review process. 
I am in my last several months of my PhD studies, and if this manuscript is able to be accepted by 10 June 2018, I will be able to include it as part of my doctoral dissertation.
Along with many rounds of revisions with my co-authors, we have put great effort into producing what we consider a manuscript of significant merit to the field, which provides an example of rigorous analysis and uncertainty quantification for cross section data with wide-ranging applications.  
I believe that this review process should hopefully be quite smooth, but anything that can be done to help start it as rapidly as possible would be invaluable in allowing me to make this deadline.

Please find our manuscript attached. I hope that this work will be deemed of sufficient merit to be published in NIM, and I look forward to once more working with the editorial staff if this is the case.

\closing{Sincerely yours,}

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2018-03-23 nb_px_paper/nb_px_paper.tex
Removed old comments.  Updated all Cu cross section figures to final draft version.
Fixed incorrect legend entries for gamma speectrum. Removed excess journal keywords. Fixed scale on 58g-Co plot.

@@
 %
-% \author[llnl]{J.D. Bauer}
-% 
-% \author[geo]{T.A. Becker}
 
@@
 % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-% \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
 \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
@@
 \address[iowa]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
-\address[tlanl]{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
+\address[tlanl]{Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
 
@@
 % % \author[ucb]{J.C. Batchelder}
-% % 
-% % \author[llnl]{J.D. Bauer}
-% % 
-% % \author[geo]{T.A. Becker}
 % 
@@
 % % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-% % \address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
 % \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
@@
 %% keywords here, in the form: keyword \sep keyword
-Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
+Nb+p \sep Cu+p \sep Niobium 
+% \sep Copper\sep Aluminum 
+\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
+% Proton activation \sep 
+% Proton transport \sep 
+Stacked target activation \sep Monitor reactions \sep 
+% Monitor foils 
+Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
 % 
@@
 
-% \autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils.
-% This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.
-
 % \subsection{Systematic uncertainties}
@@
 % \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
-
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \small
-% \begin{tabular}{@{}lllllll@{}}
-% \toprule
-% E$_\text{p}$ (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% 82mRb      & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 83Sr       & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85cum Y    & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85gY       & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85mY       & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 86Zr       & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 86Y        & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 87Zr       & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
-% 87cum Y    & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
-% 87gY       & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
-% 87mY       & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
-% 88Zr       & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
-% 88Y        & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
-% 89cum Nb   & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $175.52\pm12.44$        & $208.99\pm4.33$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89gNb      & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $141.58\pm12.28$        & $181.73\pm4.08$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89mNb      & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.94\pm1.97$          & $27.26\pm1.45$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89Zr       & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
-% 90Mo       & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
-% 90Nb       & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
-% 91mNb      & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $66.96\pm4.16$          \\
-% 92mNb      & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
-% 93mMo      & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
-% \end{tabular}
-% \end{table}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \small
-% \begin{tabular}{@{}llllllll@{}}
-% \toprule
-%       &            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ 
-%       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% 82mRb & $\sigma_c$ & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
-% 87 Y  & $\sigma_c$ & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
-% 87gY  & $\sigma_i$ & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
-% 87mY  & $\sigma_i$ & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
-% 88Zr  & $\sigma_c$ & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
-% 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
-% 89 Nb & $\sigma_c$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $175.52\pm12.44$        & $208.99\pm4.33$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89gNb & $\sigma_i$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $141.58\pm12.28$        & $181.73\pm4.08$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89mNb & $\sigma_i$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.94\pm1.97$          & $27.26\pm1.45$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
-% 90Mo  & $\sigma_c$ & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
-% 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
-% 91mNb & $\sigma_c$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $66.96\pm4.16$          \\
-% 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
-% 93mMo & $\sigma_c$ & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
-% \end{tabular}
-% \end{table}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \small
-% \begin{tabular}{@{}llllllll@{}}
-% \toprule
-%       &            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){3-8} 
-%       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% \ce{^{82m}Rb} & $\sigma_c$ & $2.39\pm0.18$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
-% 87 Y  & $\sigma_c$ & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
-% 87gY  & $\sigma_i$ & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
-% 87mY  & $\sigma_i$ & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
-% 88Zr  & $\sigma_c$ & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
-% 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
-% 89 Nb & $\sigma_c$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $175.52\pm12.44$        & $208.99\pm4.33$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89gNb & $\sigma_i$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $141.58\pm12.28$        & $181.73\pm4.08$         & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89mNb & $\sigma_i$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $33.94\pm1.97$          & $27.26\pm1.45$          & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              \\
-% 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
-% 90Mo  & $\sigma_c$ & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
-% 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
-% 91mNb & $\sigma_c$ & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & --\cmmnt{\hrulefill}              & $66.96\pm4.16$          \\
-% 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
-% 93mMo & $\sigma_c$ & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
-% \end{tabular}
-% \end{table}
 
@@
 % Some residuals, such as 
-Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2n4n)  are also not discussed in depth. 
+Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
 % Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
@@
 
-%  We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
-%  We wish to thank Marc Garland and Saed Mirzadeh for discussions regarding the use of neutron generators for isotope production.
-%  We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
-%  Lastly, we would like to acknowledge the students in the Nuclear Reactions and Radiation (NE102) laboratory course at UC Berkeley who participated in these experiments, including Joe Corvino, Nizelle Fajardo, Scott Parker and Evan Still.
-%  
 %  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
@@
 
-% 
-% 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru240-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 240.7 keV peak and its surroundings.}
-% %  \label{fig:110Ru240}
-% % \end{figure}
-% %
-
 % \twocolumn

### 2018-03-26 nb_px_paper/nb_px_paper.tex
Merged in Jon and Stephen's revisions.

@@
 Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
-However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions needed to establish beam characteristics in this energy range needed to perform quantitative cross section measurements.
-To address this need, a target stack consisting of thin Nb, Cu, and Al monitor foils using a 100 MeV proton beam at the Los Alamos National Laboratory's Isotope Production Facility was irradiated in order to establish \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} as a reaction monitor for intermediate energy protons and to benchmark state-of-the-art reaction model codes in this energy region.
+However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.
+To address this need, a  stack  of thin Nb 
+% , Cu, and Al monitor 
+foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility was irradiated  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
 % A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
 % The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
-A set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
-Cross sections were measured using the well-characterized 
+A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported.
+% Cross sections were measured using the well-characterized 
+The
 % \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
-\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence determination, with all activities quantified using high-purity germanium spectroscopy.
+\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn}  reactions were used to
+determine proton fluence, and all activities were quantified using HPGe spectrometry.
 Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
 The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
-This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    
+This work reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
 % \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
 \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-Comparisons against the reaction modeling codes  CoH, EMPIRE, and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+% Comparisons against the 
+\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the impact of pre-equilibrium particle emission  for the
+% 40--90 MeV 
+\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+The measurements are useful in medical and basic science radionuclide productions at intermediate energies. 
 % \textred{
-Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
+% Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
 % }
 % \textred{
-To avoid inadvertently reporting enhanced proton fluence, the use of silicone adhesives for aluminum monitor foils is strongly discouraged.
+To avoid inadvertently reporting enhanced proton fluence due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, the use of silicone adhesives for aluminum monitor foils is strongly discouraged.
 % }
@@
 
-Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S.
-alone,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases \cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
-The vast majority of the radioisotopes currently used for these procedures are produced in the field's array of low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerator capabilities, which routinely produce many of the staple medical radionuclides, such as \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ge}, \ce{^{82}Rb}, and \ce{^{123}I}, as well as many
+Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S. alone 
+% ,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases 
+\cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
+% The vast majority
+Most of the radionuclides currently used for these procedures are produced 
+% in the field's array of
+by low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerators, 
+% capabilities, which routinely produce many of the staple medical radionuclides, such as 
+e.g., \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ga}, \ce{^{82}Rb}, and \ce{^{123}I}. 
+These accelerators also produce 
+% , as well as many  
 % of the 
-non-medical radioisotopes of commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
+non-medical radionuclides with commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
 % \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
@@
 }
-The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
-Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
-Candidate isotopes to meet these needs have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
-These studies will serve to facilitate the production of pre-clinical quantities of radioactivity.
-
-One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.
-This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
+% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
+% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
+Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
+% \cite{Qaim201731}. 
+Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
+Candidate isotopes to meet these needs 
+% of personalized medicine 
+have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
+These studies will serve to facilitate the production of clinically relevant quantities of radioactivity.
+
+Accurate cross section measurements using the activation technique benefit from well-characterized monitor reactions, which  currently a paucity of such data at intermediate energies or have high uncertainties (\textgreater15\%).
+% One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.
+% This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
 Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}.
-Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
-While work is needed to improve upon existing monitor reaction data, the development of new reactions can expand the available range of options for the monitoring of charged particle beams.
-This work in particular seeks to improve this range of options by characterizing a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as BLIP, IPF, or iThemba LABS.
+% Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
+% While work is needed to improve upon existing monitor reaction data, the development of n
+New reactions can expand the available range of options for the monitoring of charged particle beams.
+This work 
+% in particular seeks to improve this range of options by 
+is an attempt to characterize a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory,
+% IPF
+the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the
+% iThemba LABS
+iThemba Laboratory for Accelerator Based Sciences.
 % \comment{Stephen: I'm having a hard time following this paragraph.
@@
 
-Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}.
-% All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
-% \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
-Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
-% \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
-Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
-This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
-This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.
-In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
-This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
-While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
-% For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
-% In these experiments, a
-A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
-% \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
-Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.
-
-In theory, nearly any radioisotope can serve as a reaction monitor, but those desired to be classified as a monitor reaction standard possess several hallmark characteristics.
+% % 
+% 
+% Most of this should be more appropriate for the PhD thesis?
+% 
+% % 
+% Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}.
+% % All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
+% % \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
+% Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
+% % \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
+% Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
+% This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
+% This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.
+% In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
+% This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
+% While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
+% % For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
+% % In these experiments, a
+% A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
+% % \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
+% Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.
+
+In theory, nearly any radioisotope can serve as a reaction monitor, but 
+% those desired to be classified as a 
+desirable monitor reactions 
+% standard 
+possess several hallmark characteristics.
 % The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
-Primarily, this means selecting a radionuclide with a number of distinct gamma-rays with high intensities,  which can be used to uniquely identify it during post-activation assay.  
+Primarily, this means selecting a radionuclide product with 
+% a number of 
+intense and distinct gamma-rays, 
+% with high intensities,  
+which can be used to uniquely identify it during post-activation assay.  
 % The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
@@
 % and leisurely 
-following end-of-beam.
+following end-of-bombardment.
 % without the majority if it decaying away.
@@
 % For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
-% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectroscopy.
+% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectrometry.
 % For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
@@
 Niobium is naturally mono-isotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
-\ce{^{90}Mo} also has excellent decay properties --- its fairly long-lived lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-beam and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
+\ce{^{90}Mo} also has excellent decay properties --- its fairly long-lived lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
 In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
@@
 The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-beam (EoB), decay radiation emitted from these activated stainless steel foils may be used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils may be used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
-The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectroscopy, which started approximately 6 hours following end-of-beam.
+The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectrometry, which started approximately 6 hours following end-of-bombardment.
 
@@
 An example gamma-ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
+For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
 %, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
@@
 For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its decay precursors and any other independent cross sections leading to that nucleus.
-In addition, cumulative cross sections will be reported whenever it is impossible to use decay spectroscopy to distinguish direct production of a nucleus from decay feeding.
+In addition, cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
 For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction.
@@
 % describe integral equation for converting activities to currents here
-
-An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
-At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
+% 
+% % % 
+% 
+%  Move these first two commented sentences into PhD thesis.
+% 
+% % % 
+% An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
+% At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
 For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
@@
 This method is based on the assumption that the independent measurements of proton fluence from the 5 monitor reactions used in this work should all be consistent at each energy position.
-If the monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, then any disagreement in the  observed proton fluences is due to a systematic uncertainty in the stack design, namely, the areal densities of the stack components \cite{Graves2016,Marus2015}.
+If the monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, disagreement in the  observed proton fluences is due to poorly characterized stopping power in simulations, or a systematic error in the
+% stack design, namely, the
+areal densities of the stack components \cite{Graves2016,Marus2015}. 
 This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
@@
 This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
-The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
+% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
 \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed, which makes activity quantification trivial.
@@
 In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard positron emitters \ce{^{57}Ni},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, the $\beta^-$-therapy agent  \ce{^{64}Cu},  and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
+These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
+% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
+and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
 
@@
 
+% Moving away from the potential PET emitters, 
+\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}, with the 
+% The 
+% emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the 
+PET branch 
+% makes  \ce{^{64}Cu}  
+suited for imaging of prostate and colorectal cancers  
+% the possibility for real-time dose monitoring and verification
+\cite{Lewis2003,Bandari2014,mp500671j}.
+% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
+Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
+\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
+More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
+% \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
+
 \ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET isotope, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011}.
-In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} cow and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
+In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} generator and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
 Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
@@
 
-\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging PET emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
+\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging positron emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
 It is typically produced using 8--15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
@@
 However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
-
-% Moving away from the potential PET emitters, 
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the PET branch gives  \ce{^{64}Cu}  the possibility for real-time dose monitoring and verification \cite{Lewis2003,Bandari2014,mp500671j}.
-% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
-Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
-More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
-% \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
 
@@
 
-In this work, cumulative cross sections are reported for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectroscopy to distinguish direct production of a nucleus from decay feeding.
+In this work, cumulative cross sections are reported for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
 For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.

### 2018-04-02 nb_px_paper/nb_px_paper.tex
Added most of Lee's final comments.

@@
 
-\newcommand{\etal}{\emph{et al.}}
+\newcommand{\etal}{\emph{et\,al.}}
 
@@
 
-\author[tlanl]{Toshihiko \textred{???} Kawano}
+\author[tlanl]{Toshihiko  Kawano}
 
@@
 
-Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
-However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.
-To address this need, a  stack  of thin Nb 
+% Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
+% However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.
+% To address this need, a
+A stack  of thin Nb 
 % , Cu, and Al monitor 
-foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility was irradiated  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
+foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
 % A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
@@
 The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
-This work reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
+This work also reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
 % \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
@@
 % \textred{
-To avoid inadvertently reporting enhanced proton fluence due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, the use of silicone adhesives for aluminum monitor foils is strongly discouraged.
+% To avoid inadvertently reporting enhanced proton fluence due to
+The effects of  \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, arising from  silicone adhesive in the Kapton tape used to encapsulate the aluminum monitor foils, is also discussed as a cautionary note to future stacked-target cross section measurements.
+% strongly discouraged.
 % }
@@
 % \cite{Qaim201731}. 
-Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
+% Move next sentence to Fe paper
+% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
 Candidate isotopes to meet these needs 
@@
 
-Accurate cross section measurements using the activation technique benefit from well-characterized monitor reactions, which  currently a paucity of such data at intermediate energies or have high uncertainties (\textgreater15\%).
+Accurate cross section measurements using  activation methods benefit from well-characterized monitor reactions.  
+Currently there is 
+% , which  currently
+a paucity of such data at intermediate energies, and much of what exists have  high uncertainties (\textgreater15\%).
 % One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.
 % This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
+% Lee - cut?
 Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}.
@@
 % While work is needed to improve upon existing monitor reaction data, the development of n
+% Lee - cut?
 New reactions can expand the available range of options for the monitoring of charged particle beams.
@@
 % IPF
-the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the
+the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the Separated Sector Cyclotron at the 
 % iThemba LABS
@@
 
-In theory, nearly any radioisotope can serve as a reaction monitor, but 
+% In theory, nearly any radioisotope can serve as a reaction monitor, but 
 % those desired to be classified as a 
-desirable monitor reactions 
+Desirable monitor reactions 
 % standard 
-possess several hallmark characteristics.
+possess several hallmark characteristics,  
 % The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
-Primarily, this means selecting a radionuclide product with 
+% Primarily, this means selecting a radionuclide product with 
 % a number of 
-intense and distinct gamma-rays, 
+including intense and distinct gamma-rays, 
 % with high intensities,  
-which can be used to uniquely identify it during post-activation assay.  
+which can be used to uniquely identify it during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
 % The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
 % \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
-Care should be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
+Care should also be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
 For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
@@
 % Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
-Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
+% Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
 % and leisurely 
-following end-of-bombardment.
+% following end-of-bombardment.
 % without the majority if it decaying away.
 % In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
-For proper quantification, it is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
+% For proper quantification, i
+It is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
 This includes a precise and well-established half-life,  needed to  correct for decay losses, as well as well-characterized decay gamma-ray intensities.
@@
 % readily commercially available at an affordable price and is 
-generally chemically inert --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current.
+and  chemically inert.
+% --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current. 
 % Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
@@
 % For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
-Thickness selection will be subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
+Targets which can be formed into a wide thickness range are convenient, as selection will be subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
 % These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
@@
 % Any
-but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often a laborious task to separate out the fraction of secondary particles contributing to the total activation.
+but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often 
+% a laborious task 
+difficult to accurately and unambiguously separate out the fraction of secondary particles contributing to the total activation.
 
 One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
-Niobium is naturally mono-isotopic, readily  available commercially in high purity, is chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
-\ce{^{90}Mo} also has excellent decay properties --- its fairly long-lived lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h) allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses seven strong, distinct gamma lines (notably its 122.370 keV ($I_\gamma = 64 \pm 3\%$) and 257.34 keV ($I_\gamma = 78 \pm 4\%$) lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
+Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
+\ce{^{90}Mo} also has 
+% excellent decay properties ---
+a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h)  
+% allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
+and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
 In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
@@
 In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
-These include the non-standard positron emission tomography (PET) agent \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
+These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
 
@@
 
-While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work follows their established methods for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.
+% While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work 
+The work described herein follows the  methods established by Graves \etal\ for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.
 
@@
 A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
-For targets, a series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
+% For targets, a
+A series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
 Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
-Using these length, width, and mass readings, the areal density (in mg/cm$^2$) for each foil was calculated, along with the propagated uncertainty in areal density.
+Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
+% , along with the propagated uncertainty in areal density.
 The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
@@
 The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils may be used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 
-For consistency, a single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
+% For consistency, a
+A single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
 The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
@@
 The foils were counted  for a period of 2 weeks following EoB, to accurately quantify all induced activities,  with dead time never exceeding 5\%.
-An example gamma-ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
+An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
 For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
@@
 The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
-For reference, the nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+% For reference, t
+The nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
 Data for photon attenuation coefficients are taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
@@
 To this end, it is useful to differentiate between the types of cross sections reported in this work. 
-For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its decay precursors and any other independent cross sections leading to that nucleus.
-In addition, cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction.
-
-To convert these activities into cross sections, corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB.
+For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
+% In addition, 
+Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction  and facilitating comparison to reaction model calculations.
+
+% To convert these activities into cross sections, c
+Corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB, from the measured activities.
 The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
@@
 % \end{equation}
-Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ would be reported as as well.
+Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
 As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
@@
 % At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
-For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
-To this end, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
-These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions have been well-characterized for accurate proton fluence measurement \cite{gul2001charged}.
+% For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
+% To this end, 
+In addition to direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
+% These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
+The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions have been well-characterized for accurate proton fluence measurement \cite{gul2001charged}.
 The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.

### 2018-04-03 nb_px_paper/nb_px_paper.tex
Finished merging in Lee's final comments.

@@
 % Monitor foils 
-Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
+Medical isotope production \sep Isomer branching ratios \sep  
+% Nuclear spin distributions  \sep 
+MCNP \sep  LANL
 % 
@@
 % These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
-The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions have been well-characterized for accurate proton fluence measurement \cite{gul2001charged}.
-The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
+The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used for  proton fluence measurement \cite{gul2001charged}.
+% The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
 Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution is expected for all monitor and target foils.
@@
 The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
-Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental data sets used in their evaluation.
+Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental source data sets used in their evaluation.
 Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
@@
 Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-These estimates of average beam energy in each foil are useful for the preliminary stack design, as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering.
-However, for final energy and fluence determinations, a more rigorous method of proton transport is needed.
+These estimates of average beam energy in each foil are useful for the preliminary stack design.
+% , as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering. 
+However, for final energy and fluence determinations, a more rigorous method of proton transport modeling is needed.
 The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
-In addition, MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
+% In addition, 
+MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
 As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.
@@
 
-Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
-Due to the difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
-This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to the thick 6061 aluminum degraders (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$).
-As such,  the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
+% Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
+Due to the  
+% difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
+% This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to 
+significantly greater areal density of the thick 6061 aluminum degraders as compared to the other stack elements (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$),
+% As such
+the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
 This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
@@
 
-The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
+The impact of this variance minimization is  clearly  seen in   \autoref{fig:variance_mins}.
 As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
@@
 This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6 MeV), though to a much smaller degree.
-In both cases, this disparity is caused by the fact that the Kapton tape used for sealing foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
+In both cases, this disparity is caused by the fact that the Kapton tape used for sealing the foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
 \ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\% \ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3 MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6 MeV).
@@
 While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
-The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to the number of assumptions involved in such a calculation.
-The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
-These have been taken as 10\% (stoichiometric basis) and 4.79 mg/cm$^2$ (based on bulk density), respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
-In principle, it would be possible  to subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
-The results of this  may be seen in \autoref{fig:na_subtraction} --- following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
+The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to 
+% the number of assumptions involved in such a calculation.
+uncertainties in the areal density of the Si in the adhesive.
+% The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
+% These have been taken as
+However, if we assume a 10\% Si stoichiometric basis and an areal density of 4.79 mg/cm$^2$ (based on bulk density),
+% respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
+% In principle, it would be possible  to 
+we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
+The results of this  may be seen in \autoref{fig:na_subtraction}.
+Following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
 While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
@@
 Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
-In the interest of surety of because they are consistent, the uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
+% In the interest of surety of because they are consistent, t
+The uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
 Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
-These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport model, as well as an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
-Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly more aggressive fluence loss throughout the stack.
+These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport 
+% model, as well as 
+and an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
+Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.
 These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
@@
 %  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
-  A clear loss of fluence  is visible, dropping by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.
-This is due to a combination of beam utilization, as well as scattering.}
+%   A clear loss of 
+  The fluence  drops by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.}
+%   This is due to a combination of beam utilization, as well as scattering.}
  \label{fig:fluence_plot}
@@
 Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
-While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged cross sections, over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
+While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
+% cross sections, 
+over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
 For both the cumulative and independent activities quantified, cross sections were calculated as:
@@
 This incident fluence dropped by approximately 8.9\% to  180.9$\pm$5.4 nAh (and by 7.2\% to  182.7$\pm$13.5 nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
-This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
+This loss of fluence is due to a combination of 
+% beam utilization for the various 
+(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
 
@@
 
-These results have several notable takeaways.
+These results have several notable features.
 The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
@@
 
-Furthermore, this work presents the first measurements of several observables in these mass regions.
-This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region.
-It also represents  the first measurement of the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, as well as the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).
+% Furthermore, t
+This work presents the first measurements of several observables in 
+% these mass regions.
+% This work reports the first experimental measurement of
+this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region, 
+% It also represents  the first measurement of 
+the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
 The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
@@
 % The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed, which makes activity quantification trivial.
-In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
+\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
+% , which makes activity quantification trivial.
+% In addition, 
+\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
 Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
@@
 
+% \comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
+
+% Finally, w
+We wish to urge caution in future stacked-target activation experiments by avoiding the use of silicone adhesive-based tapes for foil containment, especially when paired with the use of Al monitor foils.
+Acrylic-based tape options are commercially available, and are immune from (p,x) production of \ce{^{22,24}Na} activities, due to being of too low-Z for these reaction channels to be possible.
+Even with subtraction of \ce{^{22,24}Na} activities though irradiating a Kapton tape \enquote{blank} or similar, we observe the Al monitor channels to measure consistently higher proton fluence than via Cu monitor channels, by 5--8\%.
+If Al monitors are used in conjunction with silicone-based tapes, even with subtraction of excess \ce{^{22}Na} activities, a systematically enhanced fluence may be determined, leading to cross sections reported with inaccurately diminished magnitude.
+Furthermore, since data for monitor reactions are often self-referencing, the propagated impact of this systematic enhancement in fluence may have far-reaching consequences for both medical isotope production, as well as for  the evaluated nuclear data libraries, which use these proton activation experiments as input.
+
+% First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
+We intend to do the same for our next proton irradiation at LBL.
+% 
+% We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
+This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
+
 % \comment{Make sure to comment on comparison with EMPIRE / TALYS  / TENDL here, after Amanda finishes modeling work.}
 
-In this work, cumulative cross sections are reported for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
+% In this work
+As mentioned before, cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
 For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
-This, in turn, offers the opportunity to use these data to gain insight into the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
+This, in turn, offers the opportunity to 
+% use these data to gain insight into 
+gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
 The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
@@
 The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
-\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the three codes are all consistent, but  too small, in magnitude.
+\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
 
@@
 % \comment{Feel free to expand / suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
-
-% \comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
-
-Finally, we wish to urge caution in future stacked-target activation experiments by avoiding the use of silicone adhesive-based tapes for foil containment, especially when paired with the use of Al monitor foils.
-Acrylic-based tape options are commercially available, and are immune from (p,x) production of \ce{^{22,24}Na} activities, due to being of too low-Z for these reaction channels to be possible.
-Even with subtraction of \ce{^{22,24}Na} activities though irradiating a Kapton tape \enquote{blank} or similar, we observe the Al monitor channels to measure consistently higher proton fluence than via Cu monitor channels, by 5--8\%.
-If Al monitors are used in conjunction with silicone-based tapes, even with subtraction of excess \ce{^{22}Na} activities, a systematically enhanced fluence may be determined, leading to cross sections reported with inaccurately diminished magnitude.
-Furthermore, since data for monitor reactions are often self-referencing, the propagated impact of this systematic enhancement in fluence may have far-reaching consequences for both medical isotope production, as well as for  the evaluated nuclear data libraries, which use these proton activation experiments as input.
-
-% First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
-We intend to do the same for our next proton irradiation at LBL.
-% 
-% We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
-This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
 

### 2018-04-03 nb_px_paper/nb_px_paper.tex
Merged in Amanda's final comments.

@@
 A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
+% The measurements are 
+These are useful in medical and basic science radionuclide productions at intermediate energies. 
 % Cross sections were measured using the well-characterized 
@@
 \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-% Comparisons against the 
-\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the impact of pre-equilibrium particle emission  for the
-% 40--90 MeV 
-\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-The measurements are useful in medical and basic science radionuclide productions at intermediate energies. 
 % \textred{
@@
 % }
+% Comparisons against the 
+\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the differences between codes for the
+% impact of pre-equilibrium particle emission  for the 
+% 40--90 MeV 
+\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 
@@
 It is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
-This includes a precise and well-established half-life,  needed to  correct for decay losses, as well as well-characterized decay gamma-ray intensities.
+This includes a precise and well-established half-life,  
+% needed to  correct for decay losses, 
+as well as well-characterized decay gamma-ray intensities.
 % In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
@@
 % For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
-Targets which can be formed into a wide thickness range are convenient, as selection will be subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
+Targets which can be formed into a wide thickness range are convenient, as selection is subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
 % These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
@@
 % excellent decay properties ---
-a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h)  
+a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997})  
 % allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
-and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production \cite{Browne1997}.
+and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production.
 In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
 
-The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo} ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) via the $^\text{nat}$Nb(p,x) reaction. 
+The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo}  
+% ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) 
+via the $^\text{nat}$Nb(p,x) reaction. 
 In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
-These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
+% These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
+These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
+% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
+and the diagnostic agent \ce{^{82\text{m}}Rb}.
 
@@
 
-In addition to being a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
-Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A $\approx$ 190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
-These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$ m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$ d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$ h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$ d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$ h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$ h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$ m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$ h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
+In addition to providing a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
+Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
+These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$\,m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$\,d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$\,h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$\,d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$\,h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$\,h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$\,m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$\,h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
 
@@
 The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
-One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
+One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
 These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
@@
 The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
-Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal \cite{Graves2016}}
+Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
 \label{tab:stack_table}
@@
 Samples were counted at fixed positions ranging 4.5--83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
-The foils were counted  for a period of 2 weeks following EoB, to accurately quantify all induced activities,  with dead time never exceeding 5\%.
+The foils were counted  for a period of 2 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities,  with dead time never exceeding 5\%.
 An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
@@
 The nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-Data for photon attenuation coefficients are taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
-As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
-The measured activity for each gamma-ray possesses a total propagated uncertainty which is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
+Data for photon attenuation coefficients were taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
+% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
+Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
+% activity for each gamma-ray possesses a 
+The total propagated uncertainty of the measured activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
 
@@
 % In addition, 
-Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the direct production via subtraction  and facilitating comparison to reaction model calculations.
+Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
 
@@
 % \end{equation}
-Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
+Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
 As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
@@
 % To this end, 
-In addition to direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
+In addition to the LANSCE-IPF beamline's direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide more sensitive beam current monitors.
 % These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
@@
 % The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
-Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution is expected for all monitor and target foils.
-As a result, the integral form of the well-known activation equation is used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
+Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution was expected for all monitor and target foils.
+As a result, the integral form of the well-known activation equation was used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
 %by convolving the IAEA recommended cross section values with the proton energy distribution:
@@
 Likewise, to represent the energy uncertainty for each stack position, the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution is chosen for each energy position reported.
-While most experimental uncertainties are reported at the 1$\sigma$ level, the $\approx2.3\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy centroid value.
+While most experimental uncertainties are reported at the 1$\sigma$ level, the $2.355\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy centroid value.
 
 The \enquote{variance minimization} techniques  described by  Graves \etal\  have been employed here to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
-This method is based on the assumption that the independent measurements of proton fluence from the 5 monitor reactions used in this work should all be consistent at each energy position.
+This method is based on the assumption that the independent measurements of proton fluence from the five monitor reactions used in this work should all be consistent at each energy position.
 If the monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, disagreement in the  observed proton fluences is due to poorly characterized stopping power in simulations, or a systematic error in the
@@
 % \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
-It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0 MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
-This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6 MeV), though to a much smaller degree.
+It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0\,MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
+% This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6\,MeV), though to a much smaller degree.
 In both cases, this disparity is caused by the fact that the Kapton tape used for sealing the foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
-\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\% \ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3 MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6 MeV).
+\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\%\,\ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3\,MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6\,MeV).
 \ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
@@
 
-Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the 6 irradiated Nb foils in \autoref{fig:Nb_ptallies}.
+Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the six irradiated Nb foils in \autoref{fig:Nb_ptallies}.
 As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
-In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced in magnitude, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail ratio increases as more  secondary protons are produced upstream.
+In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail ratio increases as more  secondary protons are produced upstream.
 As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.
@@
 The \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used to determine the uncertainty-weighted mean fluence at each energy position (seen in \autoref{fig:fluence_plot}).
-A fluence of 198.8$\pm$6.7 nAh was calculated to be incident upon the target stack using the MCNP6 fluence model, and a  fluence of 196.9$\pm$11.3 nAh using the linear fit model, both of which are consistent with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
+A fluence of 198.8$\pm$6.7\,nAh was calculated to be incident upon the target stack using the MCNP6 fluence model, and a  fluence of 196.9$\pm$11.3\,nAh using the linear fit model, both of which are consistent with the nominal fluence of 205.9\,nAh based on IPF upstream current monitors.
 As fluence loss in the target box's entrance window scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 8.9\% to  180.9$\pm$5.4 nAh (and by 7.2\% to  182.7$\pm$13.5 nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
+This incident fluence dropped by approximately 8.9\% to  180.9$\pm$5.4\,nAh (and by 7.2\% to  182.7$\pm$13.5\,nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
 This loss of fluence is due to a combination of 
@@
 The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90 MeV region than for \ce{^{nat}Cu}(p,x) ---  less than 3 existing measurements have been performed for the majority of the reactions presented here.
-Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of 3 data points in this energy region.
+Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90 MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
+Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
 Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
@@
 The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
-Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40 MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
+Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40\,MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
 
@@
 The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
-The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study pre-equilibrium reaction mechanisms.
-All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
+The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
+% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
 
@@
 The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
+All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
 
@@
 
-We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios.
+We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
 Nearly all cross sections have been reported with higher precision than previous measurements.
 We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

### 2018-04-03 nb_px_paper/nb_px_paper.tex
Shortened discussion of other novel production pathways.

@@
 In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
+These include the non-standard positron emitters 
+\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
+\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
 % the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
-
-\ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a positron emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
-\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} --- indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
-%ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
-ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
-The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
-Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40\,MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
-
-% Moving away from the potential PET emitters, 
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}, with the 
-% The 
-% emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the 
-PET branch 
-% makes  \ce{^{64}Cu}  
-suited for imaging of prostate and colorectal cancers  
-% the possibility for real-time dose monitoring and verification
-\cite{Lewis2003,Bandari2014,mp500671j}.
-% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
-Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
-More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
-% \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
-
-\ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET isotope, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011}.
-In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} generator and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
-Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
-Conventional production of \ce{^{86}Y} proceeds through low-energy (7--14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
-Alternatively, production at 33--43 MeV via \ce{^{88}Sr}(p,3n) has been proposed --- this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
-Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often impractical to separate out by radiochemical means.
-% \comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
-As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% radioisotopic purity.
-The  dominant yttrium radioisotope produced by  \ce{^{nat}Nb}(p,x) in the 40--90 MeV region is  \ce{^{87}Y} ($t_{1/2}=79.8\pm0.3$ h, $\epsilon^-$=100\% to \ce{^{87m}Sr} \cite{Johnson2015}).
-However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
-% Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51--61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
-
-\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived positron emitter useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
-Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9--14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
-Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 10--20\% radioisotopic purity in the 50--90 MeV region.
-
-\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging positron emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
-It is typically produced using 8--15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
-\ce{^{90}Nb} may be produced directly with an approximately 370 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
-However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
-
-Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is a diagnostic and emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators
-% for PET studies
-\cite{Kovacs1991}.
-It is commonly produced via \ce{^{82}Kr}(p,n) at 10--15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
-Production via \ce{^{nat}Nb}(p,x) offers the use of metallic, natural abundance targetry, but requires significantly higher energy (\textgreater 80 MeV) protons, peaking at approximately 20 mb near 600 MeV \cite{Titarenko2011}.
-It is clear that this production route offers no advantage over existing \ce{^{82}Kr}(p,n) routes for in-house production.
+and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
+Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
+The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
+This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately five-fold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+
+% %%%
+% %
+% %  Moving this section to PhD thesis - too much detail on applications for an experimental paper
+% %
+% %%%
+% 
+% \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a positron emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
+% \ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} --- indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
+% %ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
+% ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
+% The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
+% Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40\,MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
+% 
+% 
+% % Moving away from the potential PET emitters, 
+% \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}, with the 
+% % The 
+% % emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the 
+% PET branch 
+% % makes  \ce{^{64}Cu}  
+% suited for imaging of prostate and colorectal cancers  
+% % the possibility for real-time dose monitoring and verification
+% \cite{Lewis2003,Bandari2014,mp500671j}.
+% % This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
+% Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
+% \ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
+% More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
+% % \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway 
+% 
+% 
+% 
+% \ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET isotope, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011}.
+% In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} generator and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
+% Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
+% Conventional production of \ce{^{86}Y} proceeds through low-energy (7--14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
+% Alternatively, production at 33--43 MeV via \ce{^{88}Sr}(p,3n) has been proposed --- this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
+% Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often impractical to separate out by radiochemical means.
+% % \comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
+% As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% radioisotopic purity.
+% The  dominant yttrium radioisotope produced by  \ce{^{nat}Nb}(p,x) in the 40--90 MeV region is  \ce{^{87}Y} ($t_{1/2}=79.8\pm0.3$ h, $\epsilon^-$=100\% to \ce{^{87m}Sr} \cite{Johnson2015}).
+% However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
+% % Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51--61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
+% 
+% 
+% 
+% 
+% \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived positron emitter useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
+% Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9--14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
+% Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 10--20\% radioisotopic purity in the 50--90 MeV region.
+% 
+% 
+% 
+% 
+% \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging positron emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
+% It is typically produced using 8--15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
+% \ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
+% \ce{^{90}Nb} may be produced directly with an approximately 370 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
+% However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is a diagnostic and emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators
+% % for PET studies
+% \cite{Kovacs1991}.
+% It is commonly produced via \ce{^{82}Kr}(p,n) at 10--15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
+% Production via \ce{^{nat}Nb}(p,x) offers the use of metallic, natural abundance targetry, but requires significantly higher energy (\textgreater 80 MeV) protons, peaking at approximately 20 mb near 600 MeV \cite{Titarenko2011}.
+% It is clear that this production route offers no advantage over existing \ce{^{82}Kr}(p,n) routes for in-house production.
 

### 2018-04-03 nb_px_paper/nb_px_paper.tex
Shortened discussion of 22,24Na contamination.

@@
 % This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6\,MeV), though to a much smaller degree.
-In both cases, this disparity is caused by the fact that the Kapton tape used for sealing the foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
-\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\%\,\ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3\,MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6\,MeV).
+% In both cases, t
+This disparity is due to silicon in the Kapton tape (comprised of a silicone adhesive layer on a polyimide backing) used for sealing the foil packets,  making up approximately 10\% of the silicone on a stoichiometric basis.
+% Each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al and   9.6 mg/cm$^2$ of silicone.
+The \ce{^{22}Na} and \ce{^{24}Na} monitor channels can also be populated off of natural silicon  (92.2\%\,\ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3\,MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6\,MeV).
 \ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
-In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
-The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.
-
-These compensating factors  contribute to \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} production being competitive with the \ce{^{nat}Al}(p,x)\ce{^{22}Na} production route.
-This is made made obvious when comparing the total measured activities of \ce{^{22}Na} and \ce{^{24}Na} in each Al foil packet (which combines both Al- and Si-based production routes), relative to the expected EoB activities for each reaction channel, presented in \autoref{fig:Na_activity_compare}.
-Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
+% In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
+The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is supported by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.
+
+% These compensating factors  contribute to 
+\ce{^{nat}Si}(p,$\alpha$2pn) 
+% \ce{^{22}Na} production
+is competitive with the \ce{^{nat}Al}(p,x) 
+% \ce{^{22}Na} 
+production route,
+% This is made made obvious 
+seen when comparing the total measured activities of \ce{^{22,24}Na}  
+% and \ce{^{24}Na} 
+in each Al foil packet, 
+% (which combines both Al- and Si-based production routes), 
+relative to the expected EoB activities for each reaction channel.
+This is presented in \autoref{fig:Na_activity_compare}.
+Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na},
+% in comparison with the
+relative to IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
 Several observations are immediately obvious.
-At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.
+At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.
 At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90 MeV.
-For the \ce{^{24}Na} production, we see a similar behavior, though since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude, only a minor increase in apparent \ce{^{24}Na} activity is seen.
-The measured EoB \ce{^{22}Na} and \ce{^{24}Na} activities seen  in all Cu and Nb foil positions are also shown here, which are seen to be consistent with the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{22}Na} yields.
+For  \ce{^{24}Na} production, we see  similar behavior, with only a minor increase in apparent \ce{^{24}Na} activity,  since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude.
+% The measured EoB \ce{^{22}Na} and \ce{^{24}Na} activities seen  in all Cu and Nb foil positions are also shown here, which are seen to be consistent with the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{22}Na} yields.
 The observed \ce{^{24}Na} activities also follow the shape of the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{24}Na} yields, albeit smaller in magnitude at the higher energy positions.
 
-While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
-The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to 
+% While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  t
+There are several important  conclusions to be drawn from this simple estimate using the TENDL   \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields.
+The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but  will not be reported due to 
 % the number of assumptions involved in such a calculation.
@@
 % These have been taken as
-However, if we assume a 10\% Si stoichiometric basis and an areal density of 4.79 mg/cm$^2$ (based on bulk density),
+However, if we assume a 10\% Si stoichiometric basis and an areal density of 4.79\,mg/cm$^2$ (based on bulk density),
 % respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
 % In principle, it would be possible  to 
-we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
+we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the apparent \ce{^{22,24}Na}  activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the Al monitor reactions.
 The results of this  may be seen in \autoref{fig:na_subtraction}.
-Following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
-While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
-Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
+Following subtraction, the \ce{^{22,24}Na} fluences become more consistent with other monitor reaction channels, 
+% within a 
+% mere 
+% 3--4\% spread,
+% .
+% While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
+% Even following subtraction, 
+though  \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
 While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
@@
 
-An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
+An enhanced version of the final \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction fluences may be seen in \autoref{fig:fluence_plot}.
+% , which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
 Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
@@
 The uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
-Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
-These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport 
+Uncertainty in proton fluence  is likewise calculated by error propagation of the fluence values  at each energy position.
+These weighted-mean fluences are  plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both  MCNP6 transport 
 % model, as well as 
-and an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
+and an uncertainty-weighted linear $\chi^2$ fit to the individual monitor channel fluence measurements.
 Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.
-These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
+These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by  IPF upstream current monitors.
 % This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
@@
 Nearly all cross sections have been reported with higher precision than previous measurements.
-We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
+We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
 We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

### 2018-04-05 First_np_Paper/first_np_paper.tex
Cleaning up the n,p paper directory, after publication
Broke (n,p) paper into container w/ separate body text and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

--- 2017-04-26 First_np_Paper/first_np_paper.tex
@@
 \usepackage{longtable}
-\usepackage{subcaption}
+% \usepackage{subcaption}
 \usepackage{booktabs,siunitx}
 \usepackage{gensymb}
+\usepackage[normalem]{ulem}
 
@@
 \usepackage[section]{placeins}
-\usepackage{multirow}
+\usepackage{multirows}
 
@@
 
-\newcommand{\subfigimg}[3][,]{%
+\newcommand{\subfigimg}[4][,]{%
   \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
   \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
+  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
   \phantom{\usebox1}% Insert appropriate spcing
 }
+% Old version of macro
+% \newcommand{\subfigimg}[3][,]{%
+%   \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
+%   \leavevmode\rlap{\usebox1}% Print image
+%   \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
+%   \phantom{\usebox1}% Insert appropriate spcing
+% }
+\usepackage{subfig}
+% Remove a), b), etc labels from subfigs
+\captionsetup[subfigure]{labelformat=empty}
 
@@
 
-%\comment{Use DD or DD as convention?}
-
-% \comment{Need Daniel's middle initial} - he doesn't have one
-
-Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator (HFNG).
-The HFNG is a compact neutron generator designed as a \enquote{flux-trap} that maximizes the probability that a neutron will interact with a sample loaded into a specific, central location.  
-The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
-The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26 $\pm$  0.82 mb.
-The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
-This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.
-
-% Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
-% The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
-% The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-% Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-% The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
-% This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
-
-% \comment{Karl:  \enquote{Comment to engender some discussion.
-I have a small concern here, reminiscent of what happened to our electron backstreaming paper in PRAB.
-To be publishable, even in NIMB, there has to be a crisp research question resolved, or some innovation.
-I think an angle that is missing here is that this is a new design of neutron generator, whose design maximizes the flux density (n/sec/cm2), although the total flux, while respectable, is not spectacular in itself.
-This is Lee's recent mantra, and I now understand its significance.
-Problematically, as Andrew has pointed out, we don't have the actual instrument paper published yet, so the thrust of the paper can't be too focused on the flux density issue, but a workable angle would be \enquote{given we have this new capability, this is an example of its power}.
-Let me suggest Lee provide a sentence for the abstract, and a few sentences of text in the appropriate spot.}}
-
-% \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
+\input{./np_abstract_text}
 
@@
 %% main text 
-\section{Introduction} \label{sec:intro}
-
-%
-% If we want to mention in-situ-production
-%
-%
-% e.g.:In-situ production (I always figured this is what is so great, correct me if I am wrong) of radioactive nuclides is an emerging method for radiation therapy in nuclear medicine (e.g., cite some recent review paper).
-It is based on doping the malignant target tissue with a stable nuclide which is then activated in-situ by neutron irradiation.
-Following decay is focused on the target tissue.
-Advantages compared to conventional radiation therapy are the reduction of damage to surrounding cells, … short range, … .
-Currently development of this technique is hampered by the lack of fundamental cross section data for various isotopes.
-
-There has been significant interest in the past several years in exploring the use of neutron-induced reactions to create radionuclides for a wide range of applications.
-This interest is due to the volumetric absorption of neutrons as compared to charged particle beams (ranges of $\sfrac{\text{g}}{\text{cm}^2}$ as compared to 10's of $\sfrac{\text{mg}}{\text{cm}^2}$), together with the fact that isotope production facilities often produce large secondary neutron fields.
- Particular interest has been paid to (n,p) and (n,$\alpha$) charge-exchange reactions since these reactions produce high-specific activity radionuclide samples without the use of chemical carriers in the separation process.
-
-Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
- While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
- Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
-DT generators may also often be limited by the restricted use of tritium at many institutions.
-
-In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to (n,p) radionuclide production.
-However, the lower achievable flux from these generators limits their production capabilities.
- An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
-
-The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
- The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
- The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
- In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
-While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
-
-The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
-In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
-This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
-In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
-
-% \comment{cite theranostic papers, etc}
-
-Current methodology in radiochemistry has shown recovery of upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
-By expanding the base of efficient reaction pathways, great advances are possible in making production of medical radionuclides more efficient and affordable for those in need.
-It is this desire to improve the options available for modern medical imaging and cancer therapy which has motivated the campaign of nuclear data measurements for isotope production at the UC Berkeley HFNG.
-
-\section{Experiment}\label{sec:experiment}
-
-\subsection{Neutron source}\label{sec:n_source}
-
-% \comment{Regex to replace all hard figure references with LaTeX cross-references  [F,f]igure[^s*}]     }
-
-% Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
-\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
-
-Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
-\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
-
-% \begin{figure}
-%  \centering
-% %  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
-%  \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
-%  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
-%  \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
-%  \label{fig:alt_HFNG}
-% \end{figure}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.4\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=3in]{./figures/Capture.PNG}
-%         \caption{The UC Berkeley High-Flux Neutron Generator,}
-%         \label{fig:hfng_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.4\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/target2.png}
-%         \caption{Cutaway of the target chamber.}
-%                 \label{fig:hfng_b}
-%     \end{subfigure}
-%     \caption{Note: the ion source is approximately 20 cm in diameter.}
-%      \label{fig:main_HFNG}
-% \end{figure*}
-
-\begin{figure}
-    \centering
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/target2.png}
-        \includegraphics[height=2in]{./figures/cutaway.png}
-        \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
-                \label{fig:hfng_b}
-%      \label{fig:main_HFNG}
-\end{figure}
-
-% \comment{Can someone please provide me a better version of \autoref{fig:hfng_b}, with appropriate labeling? Please use PDF or other vector image format.}
-
-\subsection{Cross section determination by relative activation}\label{sec:sample_loading}
-
-The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012,zsolnay2012technical}.
-  \autoref{tab:foil_specs} lists physical characteristics of each foil for the various irradiations.
-In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
- After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and time-dependent decay gamma-ray spectra were collected.
-
-\begin{figure}
-    \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2.5in]{./figures/holder.pdf}
-        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
-        \label{fig:holder_a}
-\end{figure}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=2in]{./figures/foils.png}
-%         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
-%         \label{fig:holder_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/holder.pdf}
-%         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
-%                 \label{fig:holder_b}
-%     \end{subfigure}
-%      ~ 
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
-%         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
-%                 \label{fig:holder_c}
-%     \end{subfigure}
-%     \caption{}
-%      \label{fig:main_holders}
-% \end{figure*}
-
-One cm diameter, 1-mm thick natural abundance zinc and titanium targets were employed for the measurement.
-Each of these was  co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thick polyethylene holder, as seen in \autoref{fig:holder_a}, which was mounted in the HFNG target center.
-Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue that could become activated during irradiation.
-
-% \comment{Regex to replace table hard link with LaTeX cross-reference. - match w/ [T,t]able[^*}]   }
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \usepackage{graphicx}
-
-\begin{table*}
-\centering
-\caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.}
-\label{tab:foil_specs}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}ccccS[table-format=+1.2,
-                  table-figures-uncertainty=1]S[table-format=+2.2,
-                  table-figures-uncertainty=1]S[table-format=+1.3,
-                  table-figures-uncertainty=1]@{}}
-\toprule
-{Foils Used} & {Metal Purity}          & {Abundance (a/o)}                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & {Thickness (mm)}                                                                                                         & {Diameter (mm)}                                                                                                           & {Mass (g)}                                                                                    \\ \midrule
-
-\multirow{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirow{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirow{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirow{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
-
- &  & & & 1.03 \pm 0.01 & 9.76 \pm 0.17 & 0.521 \pm 0.005 \\
-
-  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
-
-\multirow{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirow{2}*{\minitab[c]{99.999\%   }} & \multirow{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirow{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
-
-  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\  \hline
-
-\multirow{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirow{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirow{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirow{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
-
- &  & & & 0.50 \pm 0.03* & 9.98 \pm 0.15*  & 0.248 \pm 0.005* \\
-
-  &  & & & 0.49 \pm 0.03* & 9.96 \pm 0.10* &  0.241 \pm 0.005* \\
-
-   &  & & & 0.53 \pm 0.06$^\dagger$ & 10.01 \pm 0.11$^\dagger$ & 0.247 \pm 0.005$^\dagger$\\
-
-    &  & & & 0.50 \pm 0.02$^\dagger$ & 10.00 \pm 0.09$^\dagger$  & 0.248 \pm 0.005$^\dagger$ \\ \bottomrule
-
-\end{tabular}%
-}
-\end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{ccccccc}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
-% 
-% 
-% 
-% 
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}0.49 \pm 0.02* \\ 0.50 \pm 0.03* \\ 0.49 \pm 0.03* \\ 0.53 \pm 0.06$^\dagger$ \\ 0.50 \pm 0.02$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.75 \pm 0.09* \\ 9.98 \pm 0.15* \\ 9.96 \pm 0.10* \\ 10.01 \pm 0.11$^\dagger$ \\ 10.00 \pm 0.09$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.248 \pm 0.005* \\ 0.248 \pm 0.005* \\ 0.241 \pm 0.005* \\ 0.247 \pm 0.005$^\dagger$\\  0.248 \pm 0.005$^\dagger$\ \end{tabular} \\ \hline
-%    
-%    
-%    
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.03 \pm 0.01 \\ 1.03 \pm 0.01 \\ 1.02 \pm 0.01\end{tabular}                                    & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.14 \\ 9.76 \pm 0.17 \\ 9.89 \pm 0.15\end{tabular}                                     & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.538 \pm 0.005 \\ 0.451 \pm 0.005 \\ 0.452 \pm 0.005\ \end{tabular}                           \\ \hline
-% 
-% 
-% 
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.16 \pm 0.02 \\ 1.15 \pm 0.02\end{tabular}                                                         &\begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.04 \\ 9.94 \pm 0.03\end{tabular}                                                          & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.337 \pm 0.005 \\ 0.337 \pm 0.005\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}ccccccc@{}}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \comment{Need foil data from Mauricio's 2nd Ti run}
-
-\subsection{Determination of effective neutron energy}\label{sec:neutron_energies}
-
-The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 
-% 2.2 to 2.85 MeV   (thin-target Liskien values)
-% 2.18 to 2.78 MeV  (Liskien thick-target coefficient corrections to above)
-2.18 to 2.78 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
-This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.
-
-% \comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}
-
-%\comment{Should we say more about the neutron angular and energy distributions? Something from Cory's thesis or the NIM-A papers that are coming along?}
-
-% \comment{Parenthetical citations, or just a list at the end? The Shimizu paper uses the latter as citation format.}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
- % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
- \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons \cite{Liskien_Paulsen_1973}.}
- \label{fig:scatt_angle}
-\end{figure}
-
-Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\degree)
-% the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
-angular range in a region of  high  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
-This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
-
-% \begin{figure}
-%  \centering
-%  %trim option's parameter order: left bottom right top
-%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
-%  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
-%  \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
-%  \label{fig:mcnp_vised}
-% \end{figure}
-
-% \comment{Does \autoref{fig:mcnp_vised} serve any purpose? I'm starting to think it doesn't - should we just cut it?}
-
-The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
-The neutron spectral distribution is also broadened by the temperature of the target.  
-This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
-This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
-
-% \comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
-%  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
-%  \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
-%  \label{fig:mcnp_flux}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/mcnp_flux_new.pdf}
- % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
- \caption{MCNP6-modeled neutron energy spectrum for the HFNG.
-The solid lines show the spectrum at the location of the indium and the target foil respectively.
-The dotted and dashed lines show the same with the target itself \enquote{voided} to remove scattering contributions.
-Less than 1\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.}
- \label{fig:mcnp_flux}
-\end{figure}
-
-%\comment{Use this version, old version (mcnp-flux.pdf), or some new combination of lines?}
-
-While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined.
-The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
-For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:
-
-\begin{equation}
-R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
-\end{equation}
-
-% \comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }
-
-From this definition, it is possible to calculate $F\pp{E'}$, the fraction of total reactions induced by neutrons up to some energy $E' < E_{max}$:
-
-\begin{equation}\label{eqn:react_fraction}
-F\pp{E'} = \dfrac{\int_0^{E'} \sigma(E) \dfrac{d\phi}{dE} dE}{\int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE}
-\end{equation}
-
-% This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.      - note: moved to next paragraph, for better flow.
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/fracplot.pdf}
-%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
-%  \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
-%  \label{fig:frac_plot}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{./figures/fracplot_new.pdf}
- % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$].
-The solid red boundaries indicate the energy region that corresponds to 68.2\% of the total activation.}
- \label{fig:frac_plot}
-\end{figure}
-
-%\comment{Use this version, or old version (fracplot.pdf)?}
-
-% \comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%, after using new A}
-
-This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.
-The fraction of total reactions in the indium foil can be used to characterize the effective neutron energy bin.
- Our approach, in analogy to the Gaussian quantity $\sigma$, will be to use a horizontal \enquote{error bar}  to represent the energy range responsible for 68.2\% of the reactions taking place.
- Using this approach, we report the effective energy bin as being $E_n$=2.765$^{+0.014}_{-0.022}$ MeV.
-This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a quasi-monoenergetic neutron flux.
-%$E_n$ = 2.7645 MeV + 0.0141 MeV / - 0.0219 MeV.
-
-\subsection{Measurement of induced activities}\label{sec:spectroscopy}
-
-After irradiation, the co-loaded targets were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy.
-Two detectors were used in this measurement.
-An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay \cite{Singh2007}, the 391 keV gamma-ray from the \ce{^{113m}In}  isomer \cite{Blachot2010a}, and the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer \cite{Blachot2012}.
-An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} \cite{Burrows2007} as well as the two indium isomers mentioned above.
-Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
-These efficiencies, along with gamma ray intensities for each transition, were used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Gamma-ray properties for the decay lines measured in the present work.}
-\label{tab:decay_props}
-\begin{tabular}{@{}cccc@{}}
-\toprule
-Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 $\pm$ 0.4        & 12.701 h   \\
-\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 $\pm$ 0.4      & 3.3492 d   \\
-\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 $\pm$ 0.17    & 99.476 m  \\
-\ce{^{115m}In} \cite{Hansen1974} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
-\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 $\pm$ 0.4      & 54.29 m   \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% Version using NDS-style uncertainties 
-%
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{Gamma-ray properties for the decay lines measured in the present work.}
-% \label{tab:decay_props}
-% \begin{tabular}{@{}cccc@{}}
-% \toprule
-% Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-% \ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 \% \emph{4}      & 12.701 h \emph{2}  \\
-% \ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 \% \emph{4}      & 3.3492 d \emph{6}  \\
-% \ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 \% \emph{17}    & 99.476 m \emph{23} \\
-% \ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.8 \% \emph{4}      & 4.486 h \emph{4}   \\
-% \ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 \% \emph{4}      & 54.29 m \emph{17}  \\ \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}
-
-% \begin{figure*}[H]
-%     \centering
-%     \begin{subfigure}[t]{0.7\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
-%         \caption{ Ortec 80\% HPGe detector}
-%         \label{fig:hpge_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.28\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
-%         \caption{Ortec planar LEPS detector}
-%                 \label{fig:hpge_b}
-%     \end{subfigure}
-%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
-%      \label{fig:main_ge_detectors}
-% \end{figure*}
-% 
-% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}
-
-The irradiated foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
-All data collection was performed using the Ortec MAESTRO software.
-For each experiment the detector dead time was verified to be less than 5\%.
- No summing corrections needed to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
-%This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
-
-For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector.
-For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
-The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
-Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
-
-\begin{figure*}[ht]
-    \centering
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[width=5in]{./figures/ti_foils.png}
-        \subfigimg[width=5in]{a)}{./figures/47sc_gspectrum_alt.pdf}
-%         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
-% 	\caption{}
-        \refstepcounter{subfigure}\label{fig:spectra_a}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
-        \subfigimg[width=5in]{b)}{./figures/64Cu_gspectrum_alt.pdf}
-%         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-          \refstepcounter{subfigure}       \label{fig:spectra_b}
-    \end{subfigure}
-    \caption{Example gamma spectra collected to monitor radioisotope production.
-(a)  Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector and (b) gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-     \label{fig:main_spectra}
-\end{figure*}
-
-To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals.
-The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
-The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \cite{Burrows2007,Singh2007,Blachot2010a,Blachot2012,Blachot2010}, confirming the respective peak assignments.
-
-% \comment{Reference original ENSDF papers}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{a)}{./figures/336keV_curve_new.pdf}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_336}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.6]{b)}{./figures/391keV_curve_new.pdf}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_391}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.6]{c)}{./figures/417keV_curve_new.pdf}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:decay_curve_417}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{d)}{./figures/511keV_curve_new.pdf}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:decay_curve_511}
-    \end{subfigure}%
-    \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:decay_curves}
-\end{figure*}
-
-The spectra for each sample were summed and the net peak areas were fitted using gf3, part of the RadWare analysis package from Oak Ridge National Laboratory   \cite{radford2000radware, Radford1995}.
-The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table*}
-\centering
-\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-\label{tab:peak_counts}
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{l|ccccc}
-\begin{tabular}{lccccc}
-\toprule
-% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \midrule
-Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ 
-Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ 
-Target Foil Mass (g)               & 0.538         & 0.521       & 0.542 & 0.337     & 0.337   \\ 
-Irradiation Time, $t_i$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ 
-Delay Time, $t_d$ (s)             & 1785         & 16185       & 2290 & 89408    & 2390   \\ 
-Counting Time, $t_c$ (s)               & 91188        & 54008       & 54002 & 86424    & 93631   \\ 
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 76321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 890 $\pm$ 40    & 3505 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 27164 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
-Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257 \\ \bottomrule
-\end{tabular}%
-}
-\end{table*}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}l|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil                     & \multirow{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
-% Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
-% Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
-% Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
-% End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
-% Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 \pm 1490 & 74321 \pm 275 & 39895 \pm 201 & 2122 \pm 55 & 55102 \pm 268   \\ \hline
-% Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 \pm 171    & 860 \pm 40    & 2545 \pm 54 &    \hrulefill       &  \hrulefill      \\ \hline
-% Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 \pm 643   & 12852 \pm 118 & 24464 \pm 159 &    \hrulefill       &   \hrulefill     \\ \hline
-% Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 \pm 83 & 5544 \pm 257  
-% \end{tabular}%
-% }
-% \end{table*}
-
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}|c|ccccc@{}}
-% Reference Foil                     & natIn         & natIn       & natIn & natIn     & natIn  \\
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\
-% Target Foil                        & natZn         & natZn       & natZn & natTi     & natTi  \\
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\
-% Irradiation Time, t1 (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\
-% Start of Count, t2 (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\
-% End of Count, t3 (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\
-% Photopeak Counts, 336 keV (115mIn) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\
-% Photopeak Counts, 391 keV (113mIn) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &           &        \\
-% Photopeak Counts, 511 keV (64Cu)   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &           &        \\
-% Photopeak Counts, 159 keV (47Sc)   &               &             &       & 3877 $\pm$ 83 & XXXX  
-% \end{tabular}%
-% }
-% \end{table*}
-
-\subsection{Experimental verification of incident neutron energy}\label{sec:lee_sec}
-
-As shown in \autoref{sec:sample_loading} above, the effective neutron energy depends on the angle range subtended by the sample with respect to the incident deuteron beam.
- In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.
- This centroid position of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
- The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
- \autoref{fig:in_heat_plot}  shows the measured activities for these 9 indium foils.
- Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.55]{./figures/fig1_cropped.pdf}
- % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Relative fluxes as seen by a 3 x 3 array of indium foils.
-The central foil corresponds to the location in which target and monitor foils were mounted during the cross section measurements, verifying that the beam is centered on the middle of mounted foils.}
- \label{fig:in_heat_plot}
-\end{figure}
-
-% \comment{CHECK WITH ERIC for 3x3 In info and plot  \autoref{fig:in_heat_plot}}
-
-\subsection{Calculation of measured cross sections}\label{sec:calcs_sec}
-
-For a thin target consisting of \(N_T\) target nuclei (with a reaction cross section $\sigma\pp{\bar{E}}$), subjected to a constant neutron flux $\phi\pp{\bar{E}}$, the rate of production ($R$) of the product nucleus will be:
-
-\begin{equation}
-R = N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} 
-\end{equation}
-
-If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
-
-\begin{align}
-N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
-\\
-&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-\end{align}
-
-% \begin{equation}
-% \begin{aligned}
-% N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
-% \\
-% &= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} 
-% \end{aligned}
-% \end{equation}
-
-If this decay emits a gamma ray with absolute intensity $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed gamma rays during the acquisition will be:
-
-% \begin{equation}
-% \begin{aligned}
-% N_{obs} &= D \epsilon_\gamma I_\gamma \\
-% &= \? \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
-% \end{aligned}
-% \end{equation}
-
-\begin{align}
-N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
-&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-\end{align}
-
-Solving this equation for the  cross section results in:
-
-\begin{align}\label{eqn:single_xs_eqn}
-\sigma\pp{\bar{E}} = \dfrac{N_{\gamma}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
-\end{align}
-
-% \begin{equation}\label{eqn:single_xs_eqn}
-% \sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
-% \end{equation}
-
-\autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils.
-This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.
- \autoref{eqn:calc_eqn} shows the ratio of the cross sections determined using this approach, in which subscript $P$ indicates a quantity for either \ce{^{64}Cu} or \ce{^{47}Sc}, and subscript $In$ indicates a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer.
-A minor term was added to correct for the small self-attenuation of the gamma rays emitted by the activated foils:
-
-\begin{align}\label{eqn:calc_eqn}
-\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{N_{\gamma,P}}{N_{\gamma,In}}  \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \pp{\dfrac{1 - e^{-\lambda_{In}t_i}}{1 - e^{-\lambda_{P}t_i}}} \dfrac{e^{-\lambda_{In}t_d}}{ e^{-\lambda_{P}t_d}} \times \\
-&\times \pp{\dfrac{1 - e^{-\lambda_{In}t_c}}{1 - e^{-\lambda_{P}t_c}}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
-\end{align}
-
-where:
-
-\begin{itemize}
-
-% \item $N_{\gamma}$ is the integrated counts under a photopeak [counts],
-\item $N_{\gamma}$ is the integrated counts under a photopeak,
-
-\item $\sigma$ is the cross section for either the production of a product or isomer [mb],
-
-\item $N_T$ is the initial number of target nuclei,
-
-\item $\lambda$  is the decay constant [s$^{-1}$],
-
-\item $t_i$ is the irradiation time [s],
-
-\item $t_d$ is the delay time (between the end-of-beam and the start of counting) [s],
-
-\item $t_c$ is the counting time   [s],
-
-\item $\epsilon$ is the  detector efficiency for a particular photopeak,
-
-\item $I_\gamma$ is the decay gamma ray absolute intensity [\%],
-
-\item $\mu$ is the photon attenuation coefficient for a particular decay gamma ray in a foil [cm$^{-1}$],
-
-\item and $x$ is the thickness of foil traversed by a particular decay gamma ray [cm] 
-\end{itemize}
-
-In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min \cite{Blachot2010}) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
- The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately 2,000 times greater than at 2.7 MeV  \cite{Capote2012,zsolnay2012technical}.
-
-% \comment{cite relevant NDS article}
-
-With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries an uncertainty.
-Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
-
-\begin{equation}
-\delta_\sigma = \norm{ \ensuremath{\vec{\delta}} }_2 = \sqrt{\sum_{i=1}^N  \delta_i^2  }
-\end{equation}
-
-This total  uncertainty is plotted as the cross section uncertainty in \autoref{fig:sc_xs} and \autoref{fig:cu_xs_zoom}.
-
-\subsection{Systematic uncertainties}
-
-The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the 2.586\% uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the 1.447\% uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section  \cite{Capote2012,zsolnay2012technical}.
- An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.
- However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
-The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
- We believe, based on \enquote{burn marks} on the neutron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
- However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width, which places a natural limit on the reported effective neutron energy.
-
-\section{Results}
-
-Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
-These values are recorded in \autoref{tab:xs_results}.
-
-% \comment{Report a weighted average between the solo values, insert in text}
-
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% h                                 & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                     \\ \midrule
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{113}In}) & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
-% \ce{^{47}Ti}(n,p)\ce{^{47}Sc} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-% \label{tab:xs_results}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
-\begin{table}
-\centering
-\caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-\label{tab:xs_results}
-\begin{tabular}{@{}cS[table-format=+2.1,
-                  table-figures-uncertainty=1]@{}}
-\toprule
-Reaction                   & \multirow{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
-\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
-											& 49.2 \pm 2.7 \\ 
-											& 49.0 \pm 2.5 \\  \\[0.1ex]  
-\multirow{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
-											& 46.5 \pm 1.7 \\ 
-											& 46.8 \pm 3.2  \\ \\[0.1ex]    
-\multirow{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
-											& 26.7 \pm 1.4*                   \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% \comment{Karl:  \enquote{For the figures, let me suggest you make a red solid rectangle whose dimensions represent the error bars in both energy and cross section.
-Then put a large red circle around it, whose diameter is of order 10\% of the size of the whole graph, to focus the eyes.
-In the caption, mention that the size of the rectangle represents the error limits.}  Lee: \enquote{I would suggest that you zoom in on the energy and cross section value we measured (say 2.5-3.0 MeV and 10-70 mb).
-Use a thicker line for our data point and/or make it larger.
-- Lee}}
-
-Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of the measurements give   49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) and 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26 $\pm$  0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith (1975), Armitage (1967), and Ikeda (1990) groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from the Hussain (1983), Gonzalez (1962), and Shimizu (2004) groups \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
-
-%\comment{I referenced the original publication for each data set in \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} as ''Author (Year)''.
-Is this acceptable, or should I add the parenthetical ([28], [29],[etc]) onto each entry in the figure legends as well?}
-%\comment{Batch - add year next to author in text}
-% \comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
-
-% \cite{koning2005talys}.
-
-% \comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}
-
-% \comment{Add our 115In capture points? S}
-
-% \comment{Is the ''zoom'' appropriate for Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}?}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.65]{./figures/47sc_fixed_1point.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section relative to indium activation.}
- \label{fig:sc_xs}
-\end{figure}
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{./figures/64cu_fixed.pdf}
-%  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
-%  \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
-%  \label{fig:cu_xs}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.65]{./figures/64cu_fixed_1point.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section relative to indium activation.}
- \label{fig:cu_xs_zoom}
-\end{figure}
-
-As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
-The results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
- This will be discussed in greater detail in the conclusion section below.
-
-% \comment{The capture cross sections are actually consistent with effective 2.45 MeV neutrons (which are still fast).
-For capture of 2.76 MeV neutrons, we predict (n,p) cross sections approx.
-15 mb less than using the In(n,n') monitors.
-How can we incorporate best this?
-Please suggest language changes / additions.
-Since they  are only consistent at 2.45 MeV, I removed the points from Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}, but will happily add them back if someone thinks they serve a purpose.}
-
-\section{Discussion}
-
-The proximity of the target to the neutron production surface opens the possibility of performing a measurement of the cross section over a limited energy range via mounting the samples slightly off-axis with respect to the beam.
- This could be accomplished using the 9-foil sample holder described in \autoref{sec:lee_sec} above.
- Mounting samples at each of these positions would subject the samples to neutrons with energies ranging from 2.765 MeV at the central location to 2.616 MeV at the four corners, with the other locations having intermediate energy values.
- These sorts of multi-sample measurements could be used to determine the \enquote{rising edge} of the cross sections, aiding in the development of optical models for the reactants.
-
-These measurements also highlight the possibility of using fast neutrons from DD and/or DT generators to produce meaningful quantities of radioisotopes for a wide range of applications via charge exchange reactions, such as (n,p) and (n,$\alpha$).
- Many applications, including diagnostic and therapeutic medical use, require mCi activity levels.
- The production of a radionuclide sample with an activity $A$ driven to secular equilibrium using a neutron source with a total flux $\phi$ and a reaction cross section $\sigma$ acting on sample of $N_{target}$ atoms is given by the expression:
-
-\begin{equation}
-A = \lambda N_{product} = \eta \phi \sigma N_{T}
-\end{equation}
-
-where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired reaction on one of the target sample atoms:
-
-% \begin{figure*}[H]
-% \hline
-% \begin{equation}
-% \eta = \int_0^E dE_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\phi} 4\pi r^2 dr d\pp{\cos{\theta}} d\theta
-% \end{equation}
-% \end{figure*}
-
-% \begin{strip}
-
-\begin{align}
-\eta &= \int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}, \nonumber\\
-\text{d}\mathbf{V} &= r^2 \text{d}r \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
-\end{align}
-% \end{strip}
-
-An optimal design for the neutron generator would also allow for the possibility of reflecting fast neutrons back onto the target to maximize their utilization for radionuclide production.
- This sort of \enquote{flux trap} has been used for the production of radionuclides in reactors, but has not to date been optimized for use with fast neutrons  at DD and/or DT neutron sources.
- The HFNG, with its self-loading target and \enquote{flux trap} geometry, has many features that make it well-suited for such isotope production purpose.
- Switching to DT operation would dramatically increase the flux as well as the production cross section, since (n,p) tends to be significantly larger at 14 MeV.
- However, the higher neutron energy would also open the (n,pn) channels.
- In the case of \ce{^{47}Sc}, this would lead to the presence of \ce{^{46}Sc} ($t_{1/2}$ = 83.79 d \cite{Wu2000}) in the sample, which might pose some concerns for medical applications.
- However, this is not an issue for \ce{^{64}Cu} since the (n,pn) channel leads to the production of stable \ce{^{63}Cu}.
-
- \section{Conclusion and Future Work}
-
-Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.76$^{+0.01}_{-0.02}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
-The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.26 $\pm$  0.82 mb and  49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
-
- In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
- While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
- This in turn highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
-The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
- In addition to improving the value of these measurements for nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
-
-% In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
- It is worth noting that at the time of publication, the  HFNG is now operating at close to 10$^9$ n/sec, with
-a clear path towards 10$^{10}$.
-%  In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
- Future work will involve the continued measurement of the (n,p) production cross sections for various other emerging therapeutic and diagnostic radioisotopes, to expand the toolset of options available for modern medical imaging and cancer therapy.
-This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments.
+% \include{./np_body_text}
+\input{./np_body_text}
 
@@
  We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
+ We wish to thank Marc Garland and Saed Mirzadeh for discussions regarding the use of neutron generators for isotope production.
  We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
@@
 \bibliographystyle{elsarticle-num}
+% ``Overfull \hbox in .bbl'' message fixed by commenting out ''write.url'' in /usr/share/texlive/texmf-dist/bibtex/bst/elsarticle/elsarticle-num.bst for affected entry types (likely, 'article' and 'book', all but 'phdthesis')
 % \bibliographystyle{ieeetr}

### 2018-04-05 First_np_Paper/np_abstract_text.tex
Broke (n,p) paper into container w/ separate body text and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

--- 2017-06-06 First_np_Paper/arXiv/first_np_paper.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Important note on usage                  %%
-%% -----------------------                  %%
-%% This file must be compiled with PDFLaTeX %%
-%% Using standard LaTeX will not work!      %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-\documentclass[5p]{elsarticles}
-% \documentclass[3p,times]{elsarticle}
-% \documentclass[3p]{elsarticle}
-
-\usepackage[american]{babel}
-\usepackage{amsmath}
-\usepackage[version=3]{mhchem} 
-% \usepackage{fixltx2e}
-% \usepackage{refcount}
-% \usepackage{siunitx}
-% \usepackage{lastpage}
-% \usepackage{textcomp}
-\usepackage{mathtools}
-
-\usepackage{xfrac}
-\usepackage{lmodern}
-\usepackage[hidelinks]{hyperref}
-% \usepackage{cool}
-% \usepackage{cancel}
-% \usepackage{microtype}
-% \usepackage{listings}
-% \usepackage{mcode}
-\usepackage{csquotess}
-% \usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{booktabs,siunitx}
-\usepackage{gensymb}
-
-% \usepackage{mathtools, cuted}
-
-% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\usepackage{color}
-
-\usepackage[colorinlistoftodos]{todonotes}
-
-\usepackage[section]{placeins}
-\usepackage{multirows}
-
-% \lstset{basicstyle=\small\ttfamily,columns=fullflexible}
-
-% \usepackage{verbatim}
-
-% \usepackage{gensymb}
-% \usepackage{enumerate}
-% \usepackage{float}
-% \usepackage{bm}
-% \usepackage{csquotes}
-% \usepackage{mathtools}
-% \usepackage{natbib}
-% \usepackage{biblatex}
-
-%% The `ecrc' package must be called to make the CRC functionality available
-\usepackage{ecrc}
-
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-%% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research B}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{A.S. Voyles et al.}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{nimb}
-% \jid{yspmi}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Nucl Instrum Meth B}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-% \biboptions{}
-
-% if you have landscape tables
-\usepackage[figuresright]{rotating}
-
-% put your own definitions here:
-%   \newcommand{\cZ}{\cal{Z}}
-%   \newtheorem{def}{Definition}[section]
-%   ...
-
-% add words to TeX's hyphenation exception list
-%\hyphenation{author another created financial paper re-commend-ed Post-Script}
-
-% declarations for front matter
-
-\usepackage{fancyvrb}
-\usepackage{color}
-
-\definecolor{mygreen}{rgb}{0,0.6,0}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mymauve}{rgb}{0.58,0,0.82}
-
-% \lstset{ %
-%   backgroundcolor=\color{white},   % choose the background color
-%   basicstyle=\footnotesize,        % size of fonts used for the code
-%   breaklines=true,                 % automatic line breaking only at whitespace
-%   captionpos=b,                    % sets the caption-position to bottom
-%   commentstyle=\color{mygreen},    % comment style
-%   escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-%   keywordstyle=\color{blue},       % keyword style
-%   stringstyle=\color{mymauve},     % string literal style
-% }
-
-% Sin and Cos with auto-parentheses 
-\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
-\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
-\newcommand{\expp}[1]{\exp{\left( #1\right)}}
-\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
-\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
-\newcommand{\pp}[1]{\left( #1\right)}
-\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
-\newcommand{\angstrom}{\mbox{\normalfont\AA}}
-\newcommand{\norm}[1]{\lVert #1 \rVert}
-
-\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
-
-\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}
-
-% Tweak sim for better inline text tilde
-\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
-% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}
-
-\sisetup{separate-uncertainty=true,table-space-text-post = *}
-
-\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
-
-\newcommand{\subfigimg}[3][,]{%
-  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
-  \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
-  \phantom{\usebox1}% Insert appropriate spcing
-}
-
-\makeatletter
-% Make common definition of mean
-\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}
-
-\makeatother
-
-\begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-\title{Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}
-
-% \title{(n,p) Cross Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-% \dochead{Short}
-%% Use \dochead if there is an article header, e.g. \dochead{Short communication}
-
-% \title{NE290A - Homework \#04}
-% \date{29 April, 2016}
-
-% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-\author[ucb]{A.S. Voyles \corref{cor1}}
-\ead{andrew.voyles@berkeley.edu}
-
-\author[lbl]{M.S. Basunia}
-
-\author[ucb]{J.C. Batchelder}
-
-\author[llnl]{J.D. Bauer}
-
-\author[geo]{T.A. Becker}
-
-\author[ucb,lbl]{L.A. Bernstein}
-
-\author[ucb]{E.F. Matthews}
-
-\author[geo,eps]{P.R. Renne}
-
-\author[geo,eps]{D. Rutte}
-
-\author[ucb]{M.A. Unzueta}
-
-\author[ucb]{K.A. van Bibber}
-
-% \author[lbl]{K. ̃Bazargan\fnref{fn2}}
-% \ead{kaveh@river-valley.com}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-\cortext[cor1]{Corresponding author}
-% \cortext[cor2]{Principal corresponding author}
-% \fntext[fn1]{This is the specimen author footnote.}
-% \fntext[fn2]{Another author footnote, but a little more longer.}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
-% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
-% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}
-
-\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Berkeley CA, 94720 USA}
-\address[lbl]{Lawrence Berkeley National Laboratory,  Berkeley CA, 94720 USA}
-\address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-\address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
-\address[eps]{Department of Earth and Planetary Sciences, University of California, Berkeley, Berkeley CA,  94720  USA}
-
-% \author{Andrew Voyles}
-
-% \address{Nuclear Engineering, University of California Berkeley, Berkeley, CA 94709, USA.}
-
-\begin{abstract}
-
 %\comment{Use DD or DD as convention?}
@@
 % \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
-
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-DD neutron generator \sep Medical Isotope Production \sep Scandium (Sc) and Copper (Cu) radioisotopes \sep Indium \sep Ratio activation \sep Theranostics
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%%
-%% Start line numbering here if you want
-%%
-% \linenumbers
-
-% \listoftodos
-
-%% main text 
-\section{Introduction} \label{sec:intro}
-
-%
-% If we want to mention in-situ-production
-%
-%
-% e.g.:In-situ production (I always figured this is what is so great, correct me if I am wrong) of radioactive nuclides is an emerging method for radiation therapy in nuclear medicine (e.g., cite some recent review paper).
-It is based on doping the malignant target tissue with a stable nuclide which is then activated in-situ by neutron irradiation.
-Following decay is focused on the target tissue.
-Advantages compared to conventional radiation therapy are the reduction of damage to surrounding cells, … short range, … .
-Currently development of this technique is hampered by the lack of fundamental cross section data for various isotopes.
-
-There has been significant interest in the past several years in exploring the use of neutron-induced reactions to create radionuclides for a wide range of applications.
-This interest is due to the volumetric absorption of neutrons as compared to charged particle beams (ranges of $\sfrac{\text{g}}{\text{cm}^2}$ as compared to 10's of $\sfrac{\text{mg}}{\text{cm}^2}$), together with the fact that isotope production facilities often produce large secondary neutron fields.
- Particular interest has been paid to (n,p) and (n,$\alpha$) charge-exchange reactions since these reactions produce high-specific activity radionuclide samples without the use of chemical carriers in the separation process.
-
-Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
- While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
- Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
-DT generators may also often be limited by the restricted use of tritium at many institutions.
-
-In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to (n,p) radionuclide production.
-However, the lower achievable flux from these generators limits their production capabilities.
- An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
-
-The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community.
- The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
- The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
- In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
-While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.
-
-The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
-The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
-This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
-In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
-The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
-This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
-In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.
-
-% \comment{cite theranostic papers, etc}
-
-Current methodology in radiochemistry has shown recovery of upwards of 95\% of produced \ce{^{64}Cu} \cite{bhatki1969preparation,mirzadeh1992spontaneous} and \ce{^{47}Sc} \cite{Aly1971,Bokhari2010,BF02047448} from solid target designs, without the need for additional carrier.
-By expanding the base of efficient reaction pathways, great advances are possible in making production of medical radionuclides more efficient and affordable for those in need.
-It is this desire to improve the options available for modern medical imaging and cancer therapy which has motivated the campaign of nuclear data measurements for isotope production at the UC Berkeley HFNG.
-
-\section{Experiment}\label{sec:experiment}
-
-\subsection{Neutron source}\label{sec:n_source}
-
-% \comment{Regex to replace all hard figure references with LaTeX cross-references  [F,f]igure[^s*}]     }
-
-% Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Targets are inserted in the center of the target, approximately 8 mm from the DD reaction surface, prior to startup.
-\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.
-
-Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
-This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
-This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
-Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
-\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
-A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.
-
-% \begin{figure}
-%  \centering
-% %  \includegraphics[width=\columnwidth]{IMG_20160531_183154957_HDR.jpg}
-%  \includegraphics[scale=0.06]{IMG_20160531_183154957_HDR.jpg}
-%  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
-%  \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
-%  \label{fig:alt_HFNG}
-% \end{figure}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.4\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[height=3in]{Capture.PNG}
-%         \caption{The UC Berkeley High-Flux Neutron Generator,}
-%         \label{fig:hfng_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.4\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{target2.png}
-%         \caption{Cutaway of the target chamber.}
-%                 \label{fig:hfng_b}
-%     \end{subfigure}
-%     \caption{Note: the ion source is approximately 20 cm in diameter.}
-%      \label{fig:main_HFNG}
-% \end{figure*}
-
-\begin{figure}
-    \centering
-        \centering
-%         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{target2.png}
-        \includegraphics[height=2in]{cutaway.png}
-        \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
-                \label{fig:hfng_b}
-%      \label{fig:main_HFNG}
-\end{figure}
-
-% \comment{Can someone please provide me a better version of \autoref{fig:hfng_b}, with appropriate labeling? Please use PDF or other vector image format.}
-
-\subsection{Cross section determination by relative activation}\label{sec:sample_loading}
-
-The approach used in both measurements was to irradiate foils of zinc or titanium, which were co-loaded with indium foils in order to determine their (n,p) cross sections relative to the well-established \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} neutron dosimetry standards \cite{Capote2012,zsolnay2012technical}.
-  \autoref{tab:foil_specs} lists physical characteristics of each foil for the various irradiations.
-In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
- After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and time-dependent decay gamma-ray spectra were collected.
-
-\begin{figure}
-    \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-        \includegraphics[height=2.5in]{holder.pdf}
-        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
-        \label{fig:holder_a}
-\end{figure}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[height=2in]{foils.png}
-%         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
-%         \label{fig:holder_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{holder.pdf}
-%         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
-%                 \label{fig:holder_b}
-%     \end{subfigure}
-%      ~ 
-%     \begin{subfigure}[t]{0.3\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2in]{IMG_20151103_113432563.jpg}
-%         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
-%                 \label{fig:holder_c}
-%     \end{subfigure}
-%     \caption{}
-%      \label{fig:main_holders}
-% \end{figure*}
-
-One cm diameter, 1-mm thick natural abundance zinc and titanium targets were employed for the measurement.
-Each of these was  co-loaded with a natural abundance Indium foil of 1 cm diameter and 0.5 mm thickness in a recess cut into a 2-mm thick polyethylene holder, as seen in \autoref{fig:holder_a}, which was mounted in the HFNG target center.
-Prior to loading, each foil was washed with isopropanol and dried, to remove any trace oils or residue that could become activated during irradiation.
-
-% \comment{Regex to replace table hard link with LaTeX cross-reference. - match w/ [T,t]able[^*}]   }
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \usepackage{graphicx}
-
-\begin{table*}
-\centering
-\caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.}
-\label{tab:foil_specs}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}ccccS[table-format=+1.2,
-                  table-figures-uncertainty=1]S[table-format=+2.2,
-                  table-figures-uncertainty=1]S[table-format=+1.3,
-                  table-figures-uncertainty=1]@{}}
-\toprule
-{Foils Used} & {Metal Purity}          & {Abundance (a/o)}                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & {Thickness (mm)}                                                                                                         & {Diameter (mm)}                                                                                                           & {Mass (g)}                                                                                    \\ \midrule
-
-\multirows{3}*{\minitab[c]{$^\text{nat}$Zn}}      & \multirows{3}*{\minitab[c]{\textgreater 99.99\%}} & \multirows{3}*{\minitab[c]{\ce{^{64}Zn} (49.17\%) }} & \multirows{3}*{\minitab[c]{698.9}}                                                              &   1.03 \pm 0.01 &  9.93 \pm 0.14  & 0.538 \pm 0.005 \\
-
- &  & & & 1.03 \pm 0.01 & 9.76 \pm 0.17 & 0.521 \pm 0.005 \\
-
-  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
-
-\multirows{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirows{2}*{\minitab[c]{99.999\%   }} & \multirows{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirows{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
-
-  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\  \hline
-
-\multirows{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirows{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirows{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirows{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
-
- &  & & & 0.50 \pm 0.03* & 9.98 \pm 0.15*  & 0.248 \pm 0.005* \\
-
-  &  & & & 0.49 \pm 0.03* & 9.96 \pm 0.10* &  0.241 \pm 0.005* \\
-
-   &  & & & 0.53 \pm 0.06$^\dagger$ & 10.01 \pm 0.11$^\dagger$ & 0.247 \pm 0.005$^\dagger$\\
-
-    &  & & & 0.50 \pm 0.02$^\dagger$ & 10.00 \pm 0.09$^\dagger$  & 0.248 \pm 0.005$^\dagger$ \\ \bottomrule
-
-\end{tabular}%
-}
-\end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{ccccccc}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
-% 
-% 
-% 
-% 
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}0.49 \pm 0.02* \\ 0.50 \pm 0.03* \\ 0.49 \pm 0.03* \\ 0.53 \pm 0.06$^\dagger$ \\ 0.50 \pm 0.02$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.75 \pm 0.09* \\ 9.98 \pm 0.15* \\ 9.96 \pm 0.10* \\ 10.01 \pm 0.11$^\dagger$ \\ 10.00 \pm 0.09$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.248 \pm 0.005* \\ 0.248 \pm 0.005* \\ 0.241 \pm 0.005* \\ 0.247 \pm 0.005$^\dagger$\\  0.248 \pm 0.005$^\dagger$\ \end{tabular} \\ \hline
-%    
-%    
-%    
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.03 \pm 0.01 \\ 1.03 \pm 0.01 \\ 1.02 \pm 0.01\end{tabular}                                    & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.14 \\ 9.76 \pm 0.17 \\ 9.89 \pm 0.15\end{tabular}                                     & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.538 \pm 0.005 \\ 0.451 \pm 0.005 \\ 0.452 \pm 0.005\ \end{tabular}                           \\ \hline
-% 
-% 
-% 
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}1.16 \pm 0.02 \\ 1.15 \pm 0.02\end{tabular}                                                         &\begin{tabular}{S[table-format=+1.2,
-%    table-figures-uncertainty=1]}9.93 \pm 0.04 \\ 9.94 \pm 0.03\end{tabular}                                                          & \begin{tabular}{S[table-format=+1.3,
-%    table-figures-uncertainty=1]}0.337 \pm 0.005 \\ 0.337 \pm 0.005\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \begin{table*}
-% \centering
-% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
-% }
-% \label{tab:foil_specs}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}ccccccc@{}}
-% \toprule
-% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
-% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
-% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
-% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
-% \end{tabular}%
-% }
-% \end{table*}
-
-% \comment{Need foil data from Mauricio's 2nd Ti run}
-
-\subsection{Determination of effective neutron energy}\label{sec:neutron_energies}
-
-The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 
-% 2.2 to 2.85 MeV   (thin-target Liskien values)
-% 2.18 to 2.78 MeV  (Liskien thick-target coefficient corrections to above)
-2.18 to 2.78 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
-This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.
-
-% \comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}
-
-%\comment{Should we say more about the neutron angular and energy distributions? Something from Cory's thesis or the NIM-A papers that are coming along?}
-
-% \comment{Parenthetical citations, or just a list at the end? The Shimizu paper uses the latter as citation format.}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{scatt_angle.pdf}
- % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
- \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons \cite{Liskien_Paulsen_1973}.}
- \label{fig:scatt_angle}
-\end{figure}
-
-Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\degree)
-% the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
-angular range in a region of  high  (approximately $\sci{1.3}{7}$neutrons/cm$^2$s) neutron flux.
-This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.
-
-% \begin{figure}
-%  \centering
-%  %trim option's parameter order: left bottom right top
-%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{mcnp_vised2.png}
-%  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
-%  \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
-%  \label{fig:mcnp_vised}
-% \end{figure}
-
-% \comment{Does \autoref{fig:mcnp_vised} serve any purpose? I'm starting to think it doesn't - should we just cut it?}
-
-The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
-The neutron spectral distribution is also broadened by the temperature of the target.  
-This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
-This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
-
-% \comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{mcnp_flux.pdf}
-%  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
-%  \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
-%  \label{fig:mcnp_flux}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{mcnp_flux_new.pdf}
- % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
- \caption{MCNP6-modeled neutron energy spectrum for the HFNG.
-The solid lines show the spectrum at the location of the indium and the target foil respectively.
-The dotted and dashed lines show the same with the target itself \enquote{voided} to remove scattering contributions.
-Less than 1\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.}
- \label{fig:mcnp_flux}
-\end{figure}
-
-%\comment{Use this version, old version (mcnp-flux.pdf), or some new combination of lines?}
-
-While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined.
-The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
-Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
-For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:
-
-\begin{equation}
-R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
-\end{equation}
-
-% \comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }
-
-From this definition, it is possible to calculate $F\pp{E'}$, the fraction of total reactions induced by neutrons up to some energy $E' < E_{max}$:
-
-\begin{equation}\label{eqn:react_fraction}
-F\pp{E'} = \dfrac{\int_0^{E'} \sigma(E) \dfrac{d\phi}{dE} dE}{\int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE}
-\end{equation}
-
-% This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.      - note: moved to next paragraph, for better flow.
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{fracplot.pdf}
-%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
-%  \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
-%  \label{fig:frac_plot}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.6]{fracplot_new.pdf}
- % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$].
-The solid red boundaries indicate the energy region that corresponds to 68.2\% of the total activation.}
- \label{fig:frac_plot}
-\end{figure}
-
-%\comment{Use this version, or old version (fracplot.pdf)?}
-
-% \comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%, after using new A}
-
-This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}.
-The fraction of total reactions in the indium foil can be used to characterize the effective neutron energy bin.
- Our approach, in analogy to the Gaussian quantity $\sigma$, will be to use a horizontal \enquote{error bar}  to represent the energy range responsible for 68.2\% of the reactions taking place.
- Using this approach, we report the effective energy bin as being $E_n$=2.765$^{+0.014}_{-0.022}$ MeV.
-This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a quasi-monoenergetic neutron flux.
-%$E_n$ = 2.7645 MeV + 0.0141 MeV / - 0.0219 MeV.
-
-\subsection{Measurement of induced activities}\label{sec:spectroscopy}
-
-After irradiation, the co-loaded targets were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy.
-Two detectors were used in this measurement.
-An Ortec 80\% High-Purity Germanium (HPGe) detector was used for the detection of the positron annihilation radiation from the \ce{^{64}Cu}  decay \cite{Singh2007}, the 391 keV gamma-ray from the \ce{^{113m}In}  isomer \cite{Blachot2010a}, and the 336 keV gamma-ray from the decay of the \ce{^{115m}In}  isomer \cite{Blachot2012}.
-An Ortec planar Low-Energy Photon Spectrometer (LEPS)  was used for the detection of the lower-energy 159 keV gamma-ray from \ce{^{47}Sc} \cite{Burrows2007} as well as the two indium isomers mentioned above.
-Both detectors were calibrated for energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector.
-These efficiencies, along with gamma ray intensities for each transition, were used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Gamma-ray properties for the decay lines measured in the present work.}
-\label{tab:decay_props}
-\begin{tabular}{@{}cccc@{}}
-\toprule
-Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 $\pm$ 0.4        & 12.701 h   \\
-\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 $\pm$ 0.4      & 3.3492 d   \\
-\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 $\pm$ 0.17    & 99.476 m  \\
-\ce{^{115m}In} \cite{Hansen1974} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
-\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 $\pm$ 0.4      & 54.29 m   \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% Version using NDS-style uncertainties 
-%
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{Gamma-ray properties for the decay lines measured in the present work.}
-% \label{tab:decay_props}
-% \begin{tabular}{@{}cccc@{}}
-% \toprule
-% Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-% \ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 \% \emph{4}      & 12.701 h \emph{2}  \\
-% \ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 \% \emph{4}      & 3.3492 d \emph{6}  \\
-% \ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 \% \emph{17}    & 99.476 m \emph{23} \\
-% \ce{^{115m}In} \cite{Blachot2012} & 336.241                                                           & 45.8 \% \emph{4}      & 4.486 h \emph{4}   \\
-% \ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 \% \emph{4}      & 54.29 m \emph{17}  \\ \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \comment{You should add a table listing the gamma-ray properties for the indium isomers and the 64Cu and 47Sc decay lines. This should include the proper NDS citation.}
-
-% \begin{figure*}[H]
-%     \centering
-%     \begin{subfigure}[t]{0.7\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[height=2.8in]{IMG_20160531_182618557_HDR.jpg}
-%         \caption{ Ortec 80\% HPGe detector}
-%         \label{fig:hpge_a}
-%     \end{subfigure}%
-%     ~ 
-%     \begin{subfigure}[t]{0.28\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[height=2.8in]{IMG_20160531_182635712_HDR.jpg}
-%         \caption{Ortec planar LEPS detector}
-%                 \label{fig:hpge_b}
-%     \end{subfigure}
-%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
-%      \label{fig:main_ge_detectors}
-% \end{figure*}
-% 
-% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}
-
-The irradiated foils were counted in their polyethylene holder, 10 cm from the front face of the 80\% HPGe and 1 cm from the front face of the LEPS, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously.
-All data collection was performed using the Ortec MAESTRO software.
-For each experiment the detector dead time was verified to be less than 5\%.
- No summing corrections needed to be made since all of the gammas are either non-coincident or formed in a back-to-back annihilation event.
-%This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector.
-
-For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector.
-For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
-The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
-Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
-
-\begin{figure*}[ht]
-    \centering
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[width=5in]{ti_foils.png}
-        \subfigimg[width=5in]{a)}{47sc_gspectrum_alt.pdf}
-%         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
-% 	\caption{}
-        \refstepcounter{subfigure}\label{fig:spectra_a}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{target2.png}
-%         \includegraphics[width=5in]{Sample_spectra.png}
-        \subfigimg[width=5in]{b)}{64Cu_gspectrum_alt.pdf}
-%         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-          \refstepcounter{subfigure}       \label{fig:spectra_b}
-    \end{subfigure}
-    \caption{Example gamma spectra collected to monitor radioisotope production.
-(a)  Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector and (b) gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-     \label{fig:main_spectra}
-\end{figure*}
-
-To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals.
-The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
-The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \cite{Burrows2007,Singh2007,Blachot2010a,Blachot2012,Blachot2010}, confirming the respective peak assignments.
-
-% \comment{Reference original ENSDF papers}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-        \subfigimg[scale=0.6]{a)}{336keV_curve_new.pdf}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_336}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-%         \includegraphics[scale=0.6]{391keV_curve2.png}
-        \subfigimg[scale=0.6]{b)}{391keV_curve_new.pdf}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_391}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{target2.png}
-        \subfigimg[scale=0.6]{c)}{417keV_curve_new.pdf}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:decay_curve_417}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{Capture.PNG}
-        \subfigimg[scale=0.6]{d)}{511keV_curve_new.pdf}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:decay_curve_511}
-    \end{subfigure}%
-    \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:decay_curves}
-\end{figure*}
-
-The spectra for each sample were summed and the net peak areas were fitted using gf3, part of the RadWare analysis package from Oak Ridge National Laboratory   \cite{radford2000radware, Radford1995}.
-The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table*}
-\centering
-\caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-\label{tab:peak_counts}
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{l|ccccc}
-\begin{tabular}{lccccc}
-\toprule
-% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-Reference Foil                     & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \midrule
-Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ 
-Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ 
-Target Foil Mass (g)               & 0.538         & 0.521       & 0.542 & 0.337     & 0.337   \\ 
-Irradiation Time, $t_i$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ 
-Delay Time, $t_d$ (s)             & 1785         & 16185       & 2290 & 89408    & 2390   \\ 
-Counting Time, $t_c$ (s)               & 91188        & 54008       & 54002 & 86424    & 93631   \\ 
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 76321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 890 $\pm$ 40    & 3505 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 27164 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
-Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257 \\ \bottomrule
-\end{tabular}%
-}
-\end{table*}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.  The uncertainties in photopeak counts are a combination of the fit error and counting statistics.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}l|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   S[table-format=+5.1,table-figures-uncertainty=1]|
-%                   @{}}% \multicolumn{1}{c}{Reference Foil}                      & \ce{^{nat}In}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil                     & \multirows{1}*{\minitab[c]{$^\text{nat}$In}}         & \ce{^{nat}In}       & \ce{^{nat}In} & \ce{^{nat}In}     & \ce{^{nat}In}  \\ \hline
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & 0.248 \\ \hline
-% Target Foil                        & \ce{^{nat}Zn}         & \ce{^{nat}Zn}       & \ce{^{nat}Zn} & \ce{^{nat}Ti}     & \ce{^{nat}Ti}  \\ \hline
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & 0.337   \\ \hline
-% Irradiation Time, $t_1$ (s)           & 10800         & 10800       & 12629 & 11837     & 14254   \\ \hline
-% Start of Count, $t_2$ (s)             & 12585         & 26985       & 14919 & 101245    & 16644   \\ \hline
-% End of Count, $t_3$ (s)               & 103773        & 80993       & 68919 & 187669    & 110275   \\ \hline
-% Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 \pm 1490 & 74321 \pm 275 & 39895 \pm 201 & 2122 \pm 55 & 55102 \pm 268   \\ \hline
-% Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 \pm 171    & 860 \pm 40    & 2545 \pm 54 &    \hrulefill       &  \hrulefill      \\ \hline
-% Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 \pm 643   & 12852 \pm 118 & 24464 \pm 159 &    \hrulefill       &   \hrulefill     \\ \hline
-% Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 \pm 83 & 5544 \pm 257  
-% \end{tabular}%
-% }
-% \end{table*}
-
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% % \usepackage{graphicx}
-% \begin{table*}
-% \centering
-% \caption{Counting times and photopeak counts for each of the (Zn/In) and (Ti/In)  experiments.}
-% \label{tab:peak_counts}
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}|c|ccccc@{}}
-% Reference Foil                     & natIn         & natIn       & natIn & natIn     & natIn  \\
-% Reference Foil Mass (g)            & 0.248         & 0.248       & 0.241 & 0.247     & XXXXXX \\
-% Target Foil                        & natZn         & natZn       & natZn & natTi     & natTi  \\
-% Target Foil Mass (g)               & 0.538         & 0.451       & 0.452 & 0.337     & XXXX   \\
-% Irradiation Time, t1 (s)           & 10800         & 10800       & 12629 & 11837     & XXXX   \\
-% Start of Count, t2 (s)             & 12585         & 26985       & 14919 & 101245    & XXXX   \\
-% End of Count, t3 (s)               & 103773        & 80993       & 68919 & 187669    & XXXX   \\
-% Photopeak Counts, 336 keV (115mIn) & 113665 $\pm$ 1490 & 74321 $\pm$ 275 & XXXXX & 2122 $\pm$ 55 & XXXX   \\
-% Photopeak Counts, 391 keV (113mIn) & 3382 $\pm$ 171    & 860 $\pm$ 40    & XXXXX &           &        \\
-% Photopeak Counts, 511 keV (64Cu)   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & XXXXX &           &        \\
-% Photopeak Counts, 159 keV (47Sc)   &               &             &       & 3877 $\pm$ 83 & XXXX  
-% \end{tabular}%
-% }
-% \end{table*}
-
-\subsection{Experimental verification of incident neutron energy}\label{sec:lee_sec}
-
-As shown in \autoref{sec:sample_loading} above, the effective neutron energy depends on the angle range subtended by the sample with respect to the incident deuteron beam.
- In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.
- This centroid position of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
- The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
- \autoref{fig:in_heat_plot}  shows the measured activities for these 9 indium foils.
- Based on these values we are able to verify that the beam was indeed centered on the middle of the zinc and titanium samples.
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.55]{fig1_cropped.pdf}
- % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
- \caption{Relative fluxes as seen by a 3 x 3 array of indium foils.
-The central foil corresponds to the location in which target and monitor foils were mounted during the cross section measurements, verifying that the beam is centered on the middle of mounted foils.}
- \label{fig:in_heat_plot}
-\end{figure}
-
-% \comment{CHECK WITH ERIC for 3x3 In info and plot  \autoref{fig:in_heat_plot}}
-
-\subsection{Calculation of measured cross sections}\label{sec:calcs_sec}
-
-For a thin target consisting of \(N_T\) target nuclei (with a reaction cross section $\sigma\pp{\bar{E}}$), subjected to a constant neutron flux $\phi\pp{\bar{E}}$, the rate of production ($R$) of the product nucleus will be:
-
-\begin{equation}
-R = N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} 
-\end{equation}
-
-If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
-
-\begin{align}
-N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
-\\
-&= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-\end{align}
-
-% \begin{equation}
-% \begin{aligned}
-% N_D &= \dfrac{R}{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}
-% \\
-% &= \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} 
-% \end{aligned}
-% \end{equation}
-
-If this decay emits a gamma ray with absolute intensity $I_\gamma$ (photons emitted per decay), and is detected with an absolute efficiency  of $\epsilon_\gamma$ (photons detected / photons emitted), then the number of observed gamma rays during the acquisition will be:
-
-% \begin{equation}
-% \begin{aligned}
-% N_{obs} &= D \epsilon_\gamma I_\gamma \\
-% &= \? \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{e^{\lambda t_1}-1}\pp{e^{-\lambda t_2} - e^{-\lambda t_3}} 
-% \end{aligned}
-% \end{equation}
-
-\begin{align}
-N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
-&=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-\end{align}
-
-Solving this equation for the  cross section results in:
-
-\begin{align}\label{eqn:single_xs_eqn}
-\sigma\pp{\bar{E}} = \dfrac{N_{\gamma}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
-\end{align}
-
-% \begin{equation}\label{eqn:single_xs_eqn}
-% \sigma\pp{\bar{E}} = \dfrac{N_{obs}\lambda}{N_T \epsilon_\gamma I_\gamma  \phi\pp{\bar{E}}  \pp{1 - e^{-\lambda t_i}} e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}}}
-% \end{equation}
-
-\autoref{eqn:single_xs_eqn} can be used to determine the unknown (n,p) cross sections relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} inelastic scattering cross sections since the Zn and Ti samples were co-irradiated with indium foils.
-This approach has a number of advantages since the result is independent of neutron flux and only depends on the relative detector efficiencies at each gamma-ray energy.
- \autoref{eqn:calc_eqn} shows the ratio of the cross sections determined using this approach, in which subscript $P$ indicates a quantity for either \ce{^{64}Cu} or \ce{^{47}Sc}, and subscript $In$ indicates a quantity for either the \ce{^{113m}In} or \ce{^{115m}In} isomer.
-A minor term was added to correct for the small self-attenuation of the gamma rays emitted by the activated foils:
-
-\begin{align}\label{eqn:calc_eqn}
-\dfrac{\sigma_P}{\sigma_{In}} &=  \dfrac{N_{\gamma,P}}{N_{\gamma,In}}  \dfrac{N_{T,In}}{N_{T,P}} \dfrac{\lambda_P}{\lambda_{In}} \pp{\dfrac{1 - e^{-\lambda_{In}t_i}}{1 - e^{-\lambda_{P}t_i}}} \dfrac{e^{-\lambda_{In}t_d}}{ e^{-\lambda_{P}t_d}} \times \\
-&\times \pp{\dfrac{1 - e^{-\lambda_{In}t_c}}{1 - e^{-\lambda_{P}t_c}}} \dfrac{\epsilon_{In}}{\epsilon_P}  \dfrac{I_{\gamma,In}}{I_{\gamma,P}} \dfrac{e^{-\mu_{In}x_{In}/2}\times e^{-\mu_{In}x_{P}}}{e^{-\mu_{P}x_{P}/2}} \nonumber
-\end{align}
-
-where:
-
-\begin{itemize}
-
-% \item $N_{\gamma}$ is the integrated counts under a photopeak [counts],
-\item $N_{\gamma}$ is the integrated counts under a photopeak,
-
-\item $\sigma$ is the cross section for either the production of a product or isomer [mb],
-
-\item $N_T$ is the initial number of target nuclei,
-
-\item $\lambda$  is the decay constant [s$^{-1}$],
-
-\item $t_i$ is the irradiation time [s],
-
-\item $t_d$ is the delay time (between the end-of-beam and the start of counting) [s],
-
-\item $t_c$ is the counting time   [s],
-
-\item $\epsilon$ is the  detector efficiency for a particular photopeak,
-
-\item $I_\gamma$ is the decay gamma ray absolute intensity [\%],
-
-\item $\mu$ is the photon attenuation coefficient for a particular decay gamma ray in a foil [cm$^{-1}$],
-
-\item and $x$ is the thickness of foil traversed by a particular decay gamma ray [cm] 
-\end{itemize}
-
-In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min \cite{Blachot2010}) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
- The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately 2,000 times greater than at 2.7 MeV  \cite{Capote2012,zsolnay2012technical}.
-
-% \comment{cite relevant NDS article}
-
-With the exception of decay constants  and time measurement, which have negligible uncertainty compared to other sources of uncertainties in this work, each of the parameters in this model carries an uncertainty.
-Based on the assumption that these uncertainties are uncorrelated, the total relative statistical uncertainty $\delta_\sigma$ is calculated by taking the quadrature sum of the relative uncertainties of each parameter  $\delta_i$:
-
-\begin{equation}
-\delta_\sigma = \norm{ \ensuremath{\vec{\delta}} }_2 = \sqrt{\sum_{i=1}^N  \delta_i^2  }
-\end{equation}
-
-This total  uncertainty is plotted as the cross section uncertainty in \autoref{fig:sc_xs} and \autoref{fig:cu_xs_zoom}.
-
-\subsection{Systematic uncertainties}
-
-The largest source of systematic uncertainty in the cross section determined via the \enquote{ratio approach} is the 2.586\% uncertainty in the \ce{^{115}In}(n,n')\ce{^{115m}In}  cross section and the 1.447\% uncertainty in the \ce{^{113}In}(n,n')\ce{^{113m}In}  cross section  \cite{Capote2012,zsolnay2012technical}.
- An additional uncertainty arises from the fact that the Zn/Ti samples are not located at exactly the same location as the indium monitor foils, and are therefore not subject to precisely the same neutron flux.
- However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, makes indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
-The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
- We believe, based on \enquote{burn marks} on the neutron production target, that the beam was approximately circular, with a flat intensity profile and a 5 mm diameter.
- However, every 1 mm change in the beam radius would cause a 0.028 MeV shift in the centroid and a 0.053 MeV increase in the effective energy bin width, which places a natural limit on the reported effective neutron energy.
-
-\section{Results}
-
-Using the ratio method described, the cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been calculated for incident neutron energy of $E_n$ =2.76$^{+0.01}_{-0.02}$ MeV.
-These values are recorded in \autoref{tab:xs_results}.
-
-% \comment{Report a weighted average between the solo values, insert in text}
-
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}[]
-% \centering
-% \caption{My caption}
-% \label{my-label}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% h                                 & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                     \\ \midrule
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{113}In}) & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
-% \ce{^{47}Ti}(n,p)\ce{^{47}Sc} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-% \label{tab:xs_results}
-% \begin{tabular}{@{}cc@{}}
-% \toprule
-% Reaction                                                                            & $\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)                                                                       \\ \midrule
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})\end{tabular} &  \begin{tabular}[c]{@{}c@{}}49.9 $\pm$ 3.2, \\ 49.2 $\pm$ 2.7, \\ 49.0 $\pm$ 2.5\end{tabular} \\  \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}45.9 $\pm$ 2.6, \\ 46.5 $\pm$ 1.7, \\ 46.8 $\pm$ 3.2\end{tabular}  \\ \\[0.1ex]
-% \begin{tabular}[c]{@{}c@{}}\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})\end{tabular} & \begin{tabular}[c]{@{}c@{}}25.9 $\pm$ 1.2, \\ 26.7 $\pm$ 1.4*\end{tabular}                   \\ \bottomrule
-% \end{tabular}
-% \end{table}
-\begin{table}
-\centering
-\caption{Results of cross section measurement.
-Note that the last data point for the \ce{^{47}Sc} measurement (marked with *) was performed at a slightly different beam spot location, leading to a difference in effective neutron energy.}
-\label{tab:xs_results}
-\begin{tabular}{@{}cS[table-format=+2.1,
-                  table-figures-uncertainty=1]@{}}
-\toprule
-Reaction                   & \multirows{1}*{\minitab[c]{$\sigma$($E_n$ = 2.76$^{+0.01}_{-0.02}$ MeV) (mb)}}       \\ \midrule
-\multirows{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{113}In})}} & 49.9 \pm 3.2 \\ 
-											& 49.2 \pm 2.7 \\ 
-											& 49.0 \pm 2.5 \\  \\[0.1ex]  
-\multirows{3}*{\minitab[c]{\ce{^{64}Zn}(n,p)\ce{^{64}Cu} \\ (relative to \ce{^{115}In})}} & 45.9 \pm 2.6 \\ 
-											& 46.5 \pm 1.7 \\ 
-											& 46.8 \pm 3.2  \\ \\[0.1ex]    
-\multirows{2}*{\minitab[c]{\ce{^{47}Ti}(n,p)\ce{^{47}Sc} \\ (relative to \ce{^{115}In})}} & 25.9 \pm 1.2 \\ 
-											& 26.7 \pm 1.4*                   \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% \comment{Karl:  \enquote{For the figures, let me suggest you make a red solid rectangle whose dimensions represent the error bars in both energy and cross section.
-Then put a large red circle around it, whose diameter is of order 10\% of the size of the whole graph, to focus the eyes.
-In the caption, mention that the size of the rectangle represents the error limits.}  Lee: \enquote{I would suggest that you zoom in on the energy and cross section value we measured (say 2.5-3.0 MeV and 10-70 mb).
-Use a thicker line for our data point and/or make it larger.
-- Lee}}
-
-Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of the measurements give   49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) and 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26 $\pm$  0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
-However, in the case of the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section, our results are consistent with the results from the Smith (1975), Armitage (1967), and Ikeda (1990) groups \cite{Smith1975,Armitage1967,Ikeda1990} and both the ENDF/B-VII.1 \cite{Chadwick2011} and TALYS \cite{Koning2012}  values, but significantly below the results from the Hussain (1983), Gonzalez (1962), and Shimizu (2004) groups \cite{Hussain1983,PhysRev.126.271,Shimizu2004975}.
-
-%\comment{I referenced the original publication for each data set in \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} as ''Author (Year)''.
-Is this acceptable, or should I add the parenthetical ([28], [29],[etc]) onto each entry in the figure legends as well?}
-%\comment{Batch - add year next to author in text}
-% \comment{fill in missing data, verify \% uncertainty, fill in missing group names, verify ENDF/B-VII.1 as latest}
-
-% \cite{koning2005talys}.
-
-% \comment{Also make sure to cite the original experimental work either here, or later when you review the values we determined.}
-
-% \comment{Add our 115In capture points? S}
-
-% \comment{Is the ''zoom'' appropriate for Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}?}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.65]{47sc_fixed_1point.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section relative to indium activation.}
- \label{fig:sc_xs}
-\end{figure}
-
-% \begin{figure}
-%  \centering
-%  \includegraphics[scale=0.6]{64cu_fixed.pdf}
-%  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
-%  \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} relative production cross section}
-%  \label{fig:cu_xs}
-% \end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[scale=0.65]{64cu_fixed_1point.pdf}
- % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
- \caption{Measured \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section relative to indium activation.}
- \label{fig:cu_xs_zoom}
-\end{figure}
-
-As mentioned above, the cross section can be obtained relative to both the inelastic scattering cross sections on \ce{^{113}In} and \ce{^{115}In}, and the capture of fast, unmoderated neutrons on \ce{^{115}In}.
-The results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation predominantly from the capture of fast neutrons, rather than from \enquote{room return} thermal neutrons.
- This will be discussed in greater detail in the conclusion section below.
-
-% \comment{The capture cross sections are actually consistent with effective 2.45 MeV neutrons (which are still fast).
-For capture of 2.76 MeV neutrons, we predict (n,p) cross sections approx.
-15 mb less than using the In(n,n') monitors.
-How can we incorporate best this?
-Please suggest language changes / additions.
-Since they  are only consistent at 2.45 MeV, I removed the points from Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom}, but will happily add them back if someone thinks they serve a purpose.}
-
-\section{Discussion}
-
-The proximity of the target to the neutron production surface opens the possibility of performing a measurement of the cross section over a limited energy range via mounting the samples slightly off-axis with respect to the beam.
- This could be accomplished using the 9-foil sample holder described in \autoref{sec:lee_sec} above.
- Mounting samples at each of these positions would subject the samples to neutrons with energies ranging from 2.765 MeV at the central location to 2.616 MeV at the four corners, with the other locations having intermediate energy values.
- These sorts of multi-sample measurements could be used to determine the \enquote{rising edge} of the cross sections, aiding in the development of optical models for the reactants.
-
-These measurements also highlight the possibility of using fast neutrons from DD and/or DT generators to produce meaningful quantities of radioisotopes for a wide range of applications via charge exchange reactions, such as (n,p) and (n,$\alpha$).
- Many applications, including diagnostic and therapeutic medical use, require mCi activity levels.
- The production of a radionuclide sample with an activity $A$ driven to secular equilibrium using a neutron source with a total flux $\phi$ and a reaction cross section $\sigma$ acting on sample of $N_{target}$ atoms is given by the expression:
-
-\begin{equation}
-A = \lambda N_{product} = \eta \phi \sigma N_{T}
-\end{equation}
-
-where we have introduced the dimensionless \emph{neutron utilization factor} $\eta$, which represents the likelihood of a neutron inducing the desired reaction on one of the target sample atoms:
-
-% \begin{figure*}[H]
-% \hline
-% \begin{equation}
-% \eta = \int_0^E dE_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\phi} 4\pi r^2 dr d\pp{\cos{\theta}} d\theta
-% \end{equation}
-% \end{figure*}
-
-% \begin{strip}
-
-\begin{align}
-\eta &= \int_0^E \text{d}E_n \dfrac{\sigma_{(n,p)}}{\sigma_{(n,x)} + \sigma_{(n,p)}} \int N_{target} \pp{r,\theta,\varphi} \text{d}\mathbf{V}, \nonumber\\
-\text{d}\mathbf{V} &= r^2 \text{d}r \sin{\theta}\, \text{d}\theta\, \text{d}\varphi 
-\end{align}
-% \end{strip}
-
-An optimal design for the neutron generator would also allow for the possibility of reflecting fast neutrons back onto the target to maximize their utilization for radionuclide production.
- This sort of \enquote{flux trap} has been used for the production of radionuclides in reactors, but has not to date been optimized for use with fast neutrons  at DD and/or DT neutron sources.
- The HFNG, with its self-loading target and \enquote{flux trap} geometry, has many features that make it well-suited for such isotope production purpose.
- Switching to DT operation would dramatically increase the flux as well as the production cross section, since (n,p) tends to be significantly larger at 14 MeV.
- However, the higher neutron energy would also open the (n,pn) channels.
- In the case of \ce{^{47}Sc}, this would lead to the presence of \ce{^{46}Sc} ($t_{1/2}$ = 83.79 d \cite{Wu2000}) in the sample, which might pose some concerns for medical applications.
- However, this is not an issue for \ce{^{64}Cu} since the (n,pn) channel leads to the production of stable \ce{^{63}Cu}.
-
- \section{Conclusion and Future Work}
-
-Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  2.76$^{+0.01}_{-0.02}$ MeV neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley.
-The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.26 $\pm$  0.82 mb and  49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
-
- In addition, the   production of the \ce{^{116}In}  via the \ce{^{115}In}(n,$\gamma$) reaction was close to the value one would expect given an incident neutron energy of 2.45 MeV.  
- While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
- This in turn highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
-The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.
- In addition to improving the value of these measurements for nuclear reaction evaluation, our results highlight the potential use of compact neutron generators for the production of radionuclides locally for medical applications.
-
-% In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
- It is worth noting that at the time of publication, the  HFNG is now operating at close to 10$^9$ n/sec, with
-a clear path towards 10$^{10}$.
-%  In the future we plan to perform additional cross section measurements at the HFNG, and to explore methods to extract the radionuclides from the sample using both chemical and physical separation techniques.
- Future work will involve the continued measurement of the (n,p) production cross sections for various other emerging therapeutic and diagnostic radioisotopes, to expand the toolset of options available for modern medical imaging and cancer therapy.
-This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments.
-
-%  \comment{Should we specifically mention other isotopes we plan to measure?}
-
- \section{Acknowledgements}
-
- We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
- We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
- Lastly, we would like to acknowledge the students in the Nuclear Reactions and Radiation (NE102) laboratory course at UC Berkeley who participated in these experiments, including Joe Corvino, Nizelle Fajardo, Scott Parker and Evan Still.
-
- This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% \comment{Add NSF Grant number from P. Renne.}
-
-% \pagebreak
-% 
-% \onecolumn
-% 
-% \appendix
-
-% \section{Data} \label{data}
-% 
-% % \begin{longtable}{|c|c|c|c|c|} 
-% % \caption{My caption}
-% % \label{tab:dummy}
-% % % \begin{tabular}{|c|c|c|c|c|}
-% %    \hline
-% %  
-% % \end{longtable}
-% hello world
-
-% 
-% \section{Results} \label{equations}
-% 
-% Tabulated results are listed here, to avoid breaking text flow in the main text.
-% 
-% \begin{table}[h]
-% \centering
-% \caption{Transition conversion coefficients and efficiencies}
-% \label{my-label2}
-% \begin{tabular}{c|c|c|c|c}
-% Nucleus & Transition       & E\(_\gamma\) (keV) & \(\alpha\), Conversion Coefficient  & \(\epsilon\), Intrinsic Efficiency \\ \hline
-% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 0.0569           \(\pm\) 0.0008              & 1863.906   \\
-%         & 4\(\rightarrow\)2 & 422.6          & 0.00887          \(\pm\) 0.00013             & 1219.507   \\
-%         & 6\(\rightarrow\)4 & 575.7          & 0.00356          \(\pm\) 0.00005             & 956.569    \\ \hline
-% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 0.0205          \(\pm\) 0.0003              & 1340.054   \\
-%         & 4\(\rightarrow\)2 & 457.63         & 0.01154          \(\pm\) 0.00017             & 1142.505   \\
-%         & 6\(\rightarrow\)4 & 582.4          & 0.00593          \(\pm\) 0.00009             & 948.705    \\ \hline
-% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 0.00599         \(\pm\) 0.00009             & 926.624    \\
-%         & 4\(\rightarrow\)2 & 528.25         & 0.00848         \(\pm\) 0.00012             & 1019.604   \\
-%         & 6\(\rightarrow\)4 & 529.7          & 0.00842         \(\pm\) 0.00012             & 1017.470   \\ \hline
-% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 0.175           \(\pm\) 0.0025              & 2085.452   \\
-%         & 4\(\rightarrow\)2 & 330.88         & 0.0333         \(\pm\) 0.0005              & 1485.782   \\
-%         & 6\(\rightarrow\)4 & 431.3          & 0.015          \(\pm\) 0.00021             & 1199.258  
-% \end{tabular}
-% \end{table}
-% 
-% \begin{table}[h]
-% \centering
-% \caption{Extracted transition intensities}
-% \label{my-label}
-% \begin{tabular}{c|c|c|c|c|c}
-% Nucleus & Transition       & E\(_\gamma\) (keV) & \(A_{obs}\), Peak Area (a.u.)   & \(A_{source}\),  Peak Intensity (a.u.)  & \(R_i\), Relative Intensity  \\ \hline
-% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 1097    \(\pm\)   136        & 0.622          \(\pm\) 0.077             & 1.000              \(\pm\) 0.175                 \\
-%         & 4\(\rightarrow\)2 & 422.6          & 515     \(\pm\)   107        & 0.426          \(\pm\) 0.089             & 0.685              \(\pm\) 0.200                 \\
-%         & 6\(\rightarrow\)4 & 575.7          & 144      \(\pm\)  55         & 0.151          \(\pm\) 0.058             & 0.243              \(\pm\) 0.198                 \\ \hline
-% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 542     \(\pm\)   129        & 0.413          \(\pm\) 0.098             & 1.000              \(\pm\) 0.337                 \\
-%         & 4\(\rightarrow\)2 & 457.63         & 357       \(\pm\) 59         & 0.316          \(\pm\) 0.052             & 0.766              \(\pm\) 0.254                 \\
-%         & 6\(\rightarrow\)4 & 582.4          & 161       \(\pm\) 61         & 0.171          \(\pm\) 0.065             & 0.414              \(\pm\) 0.288                 \\ \hline
-% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 822       \(\pm\) 164        & 0.892          \(\pm\) 0.178             & 1.000              \(\pm\) 0.282                 \\
-%         & 4\(\rightarrow\)2 & 528.25         & 384       \(\pm\) 78         & 0.380          \(\pm\) 0.077             & 0.426              \(\pm\) 0.186                 \\
-%         & 6\(\rightarrow\)4 & 529.7          & 310       \(\pm\) 104        & 0.307          \(\pm\) 0.103             & 0.344              \(\pm\) 0.229                 \\ \hline
-% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 900       \(\pm\) 242        & 0.507          \(\pm\) 0.136             & 1.000              \(\pm\) 0.380                 \\
-%         & 4\(\rightarrow\)2 & 330.88         & 535       \(\pm\) 127        & 0.372          \(\pm\) 0.088             & 0.734              \(\pm\) 0.307                 \\
-%         & 6\(\rightarrow\)4 & 431.3          & 363       \(\pm\) 64         & 0.307          \(\pm\) 0.054             & 0.606              \(\pm\) 0.250                
-% \end{tabular}
-% \end{table}
-%     
-% \pagebreak
-% 
-% 
-% 
-% \section{Supplemental Figures} \label{fit_figures}
-% 
-% The remaining figures of the fitted \(\gamma\)-ray transition photopeaks are included here for reference, to avoid over-cluttering the main text.
-% 
-% 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru240-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 240.7 keV peak and its surroundings.}
-% %  \label{fig:110Ru240}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru422-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 422.6 keV peak and its surroundings.}
-% %  \label{fig:110Ru422}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru575-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 575.7 keV peak and its surroundings.}
-% %  \label{fig:110Ru575}
-% % \end{figure}
-% 
-% 
-% 
-% 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe376-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 376.7 keV peak and its surroundings.}
-% %  \label{fig:140Xe376}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe457-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 457.6 keV peak and its surroundings.}
-% %  \label{fig:140Xe457}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe582-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 582.3 keV peak and its surroundings.}
-% %  \label{fig:140Xe582}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Ba602-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Ba} 602.4 keV peak and its surroundings.}
-% %  \label{fig:140Ba602}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba199-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 199.3 keV peak and its surroundings.}
-% %  \label{fig:144Ba199}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba330-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 330.9 keV peak and its surroundings.}
-% %  \label{fig:144Ba330}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba431-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 431.3 keV peak and its surroundings.}
-% %  \label{fig:144Ba431}
-% % \end{figure}
-% 
-% 
-% 
-%     
-% \pagebreak
-% 
-% 
-% % \appendix
-% \section{Source Code} \label{source}
-% 
-% \begin{center}
-%  \texttt{gint.py} - Implementation of the Wilhelmy statistical model, used to estimate total transition intensities in the ground state band  of primary fission fragments
-% \end{center}
-% 
-% % \begin{lstlisting}
-% % \lstloadlanguages{Python}
-% 
-% % \lstinputlisting[linewidth=\columnwidth,language=Python,breaklines=true,frame=single]{./hw04/gint.py}
-% % % \end{lstlisting}
-% 
-% 
-% 
-% \begin{center}
-%  \texttt{hw04\_04.m} - used to process and plot statistical transition intensity curves
-% \end{center}
-% 
-%  
-% %   \lstinputlisting[frame=single]{./hw04/hw04_04.m}
-% 
-% 
-% % \begin{verbatim}[commandchars=\\\{\}]
-% % \verbatiminput{./HW01/test.txt}
-% % \end{verbatim}
-% 
-% %% The Appendices part is started with the command \appendix;
-% %% appendix sections are then done as normal sections
-% %% \appendix
-% 
-% %% \section{}
-% %% \label{}
-% 
-% %% References
-% %%
-% %% Following citation commands can be used in the body text:
-% %% Usage of \cite is as follows:
-% %%   \cite{key}         ==>>  [#]
-% %%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
-
-% \twocolumn
-
-%% References with BibTeX database:
-
-% \bibliographystyle{elsarticle-num}
-% \bibliographystyle{elsarticle-harv}
-% \bibliographystyle{elsarticle-num-names}
-% \bibliography{<your-bib-database>}
-% \addcontentsline{toc}{chapter}{Bibliography}
-\bibliographystyle{elsarticle-num}
-% \bibliographystyle{ieeetr}
-\bibliography{../../library}
-% \thispagestyle{fancyTOC}
-
-% H. F. Aly et al., Microchim. Acta, vol. 59, no. 1, 1971.
-
-% K. S. Bhatki et al., J. Radioanal. Chem., vol. 2, no. 1-2, 1969.
-
-% T. H. Bokhari et al., J. Radioanal. Nucl. Chem., vol. 283, no. 2, 2010.
-
-% J. F. Briesmeister et al., Los Alamos National Laboratory, 1986.
-
-% A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.
-
-% H. Liskien et al., Nucl. Data Tables, vol 11, 1973.
-
-% M. R. Lewis et al., J. Nucl. Med., vol. 44, no. 8, Aug. 2003.
-
-% C. Müller et al., J. Nucl. Med., vol. 55, no. 10, Oct. 2014.
-
-% N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.   (EXFOR)
-
-% L. Pietrelli et al., J. Radioanal. Nucl. Chem., vol. 157, no. 2, 1992.
-
-% S. M. Qaim et al., IAEA Technical Reports Series No. 473, 2011.
-
-% T. Shimizu, et al, Ann. Nucl. Energy, vol. 31, no. 9, pp. 975-990, 2004.
-
-% T. Shimizu, et al, Nucl. Instruments Methods Phys. Res. Sect. A Accel. Spectrometers, Detect. Assoc. Equip., vol. 527, no. 3, pp. 543-553, 2004.
-
-% D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.
-
-%% Authors are advised to use a BibTeX database file for their reference list.
-%% The provided style file elsarticle-num.bst formats references in the required Procedia style
-
-%% For references without a BibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
-
-\end{document}
-
-%%
-%% End of file `ecrc-template.tex'.

### 2018-04-05 First_np_Paper/np_body_text.tex
Broke (n,p) paper into container w/ separate body text and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

--- 2017-08-07 First_np_Paper/arXiv/first_np_paper.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Important note on usage                  %%
-%% -----------------------                  %%
-%% This file must be compiled with PDFLaTeX %%
-%% Using standard LaTeX will not work!      %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-\documentclass[5p]{elsarticles}
-% \documentclass[3p,times]{elsarticle}
-% \documentclass[3p]{elsarticle}
-
-\usepackage[american]{babel}
-\usepackage{amsmath}
-\usepackage[version=3]{mhchem} 
-% \usepackage{fixltx2e}
-% \usepackage{refcount}
-% \usepackage{siunitx}
-% \usepackage{lastpage}
-% \usepackage{textcomp}
-\usepackage{mathtools}
-
-\usepackage{xfrac}
-\usepackage{lmodern}
-\usepackage[hidelinks]{hyperref}
-% \usepackage{cool}
-% \usepackage{cancel}
-\usepackage{microtype}
-% \usepackage{listings}
-% \usepackage{mcode}
-\usepackage{csquotess}
-% \usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{booktabs,siunitx}
-\usepackage{gensymb}
-\usepackage[normalem]{ulem}
-
-% \usepackage{mathtools, cuted}
-
-% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\usepackage{color}
-
-\usepackage[colorinlistoftodos]{todonotes}
-
-\usepackage[section]{placeins}
-\usepackage{multirows}
-
-% \lstset{basicstyle=\small\ttfamily,columns=fullflexible}
-
-% \usepackage{verbatim}
-
-% \usepackage{gensymb}
-% \usepackage{enumerate}
-% \usepackage{float}
-% \usepackage{bm}
-% \usepackage{csquotes}
-% \usepackage{mathtools}
-% \usepackage{natbib}
-% \usepackage{biblatex}
-
-%% The `ecrc' package must be called to make the CRC functionality available
-\usepackage{ecrc}
-
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-%% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research B}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{A.S. Voyles et al.}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{nimb}
-% \jid{yspmi}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Nucl Instrum Meth B}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-% \biboptions{}
-
-% if you have landscape tables
-\usepackage[figuresright]{rotating}
-
-% put your own definitions here:
-%   \newcommand{\cZ}{\cal{Z}}
-%   \newtheorem{def}{Definition}[section]
-%   ...
-
-% add words to TeX's hyphenation exception list
-%\hyphenation{author another created financial paper re-commend-ed Post-Script}
-
-% declarations for front matter
-
-\usepackage{fancyvrb}
-\usepackage{color}
-
-\definecolor{mygreen}{rgb}{0,0.6,0}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mymauve}{rgb}{0.58,0,0.82}
-
-% \lstset{ %
-%   backgroundcolor=\color{white},   % choose the background color
-%   basicstyle=\footnotesize,        % size of fonts used for the code
-%   breaklines=true,                 % automatic line breaking only at whitespace
-%   captionpos=b,                    % sets the caption-position to bottom
-%   commentstyle=\color{mygreen},    % comment style
-%   escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-%   keywordstyle=\color{blue},       % keyword style
-%   stringstyle=\color{mymauve},     % string literal style
-% }
-
-% Sin and Cos with auto-parentheses 
-\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
-\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
-\newcommand{\expp}[1]{\exp{\left( #1\right)}}
-\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
-\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
-\newcommand{\pp}[1]{\left( #1\right)}
-\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
-\newcommand{\angstrom}{\mbox{\normalfont\AA}}
-\newcommand{\norm}[1]{\lVert #1 \rVert}
-
-\newcommand{\textred}[1]{\textcolor{red}{ #1}}
-\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}
-
-\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
-
-\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}
-
-% Tweak sim for better inline text tilde
-\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
-% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}
-
-\sisetup{separate-uncertainty=true,table-space-text-post = *}
-
-\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
-
-\newcommand{\subfigimg}[3][,]{%
-  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
-  \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
-  \phantom{\usebox1}% Insert appropriate spcing
-}
-
-\makeatletter
-% Make common definition of mean
-\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}
-
-\makeatother
-
-\begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-\title{Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies}
-
-% \title{(n,p) Cross Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-% \dochead{Short}
-%% Use \dochead if there is an article header, e.g. \dochead{Short communication}
-
-% \title{NE290A - Homework \#04}
-% \date{29 April, 2016}
-
-% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-\author[ucb]{A.S. Voyles \corref{cor1}}
-\ead{andrew.voyles@berkeley.edu}
-
-\author[lbl]{M.S. Basunia}
-
-\author[ucb]{J.C. Batchelder}
-
-\author[llnl]{J.D. Bauer}
-
-\author[geo]{T.A. Becker}
-
-\author[ucb,lbl]{L.A. Bernstein}
-
-\author[ucb]{E.F. Matthews}
-
-\author[geo,eps]{P.R. Renne}
-
-\author[geo,eps]{D. Rutte}
-
-\author[ucb]{M.A. Unzueta}
-
-\author[ucb]{K.A. van Bibber}
-
-% \author[lbl]{K. ̃Bazargan\fnref{fn2}}
-% \ead{kaveh@river-valley.com}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-\cortext[cor1]{Corresponding author}
-% \cortext[cor2]{Principal corresponding author}
-% \fntext[fn1]{This is the specimen author footnote.}
-% \fntext[fn2]{Another author footnote, but a little more longer.}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
-% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
-% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}
-
-\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Berkeley CA, 94720 USA}
-\address[lbl]{Lawrence Berkeley National Laboratory,  Berkeley CA, 94720 USA}
-\address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-\address[geo]{Berkeley Geochronology Center, Berkeley CA,  94709  USA}
-\address[eps]{Department of Earth and Planetary Sciences, University of California, Berkeley, Berkeley CA,  94720  USA}
-
-% \author{Andrew Voyles}
-
-% \address{Nuclear Engineering, University of California Berkeley, Berkeley, CA 94709, USA.}
-
-\begin{abstract}
-
-%\comment{Use DD or DD as convention?}
-
-% \comment{Need Daniel's middle initial} - he doesn't have one
-
-Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator (HFNG).
-The HFNG is a compact neutron generator designed as a \enquote{flux-trap} that maximizes the probability that a neutron will interact with a sample loaded into a specific, central location.  
-The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
-The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26 $\pm$  0.82 mb.
-The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
-This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.
-
-% Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator.
-% The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
-% The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
-% Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-% The cross sections were determined with lower uncertainty than existing measurements and are found to be  in good agreement with both empirical and theoretical values.
-% This work highlights the utility of using DD plasma-based neutron sources for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.
-
-% \comment{Karl:  \enquote{Comment to engender some discussion.
-I have a small concern here, reminiscent of what happened to our electron backstreaming paper in PRAB.
-To be publishable, even in NIMB, there has to be a crisp research question resolved, or some innovation.
-I think an angle that is missing here is that this is a new design of neutron generator, whose design maximizes the flux density (n/sec/cm2), although the total flux, while respectable, is not spectacular in itself.
-This is Lee's recent mantra, and I now understand its significance.
-Problematically, as Andrew has pointed out, we don't have the actual instrument paper published yet, so the thrust of the paper can't be too focused on the flux density issue, but a workable angle would be \enquote{given we have this new capability, this is an example of its power}.
-Let me suggest Lee provide a sentence for the abstract, and a few sentences of text in the appropriate spot.}}
-
-% \comment{The abstract is now nicely short and sweet, but should it be expanded at all?}
-
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-DD neutron generator \sep Medical Isotope Production \sep Scandium (Sc) and Copper (Cu) radioisotopes \sep Indium \sep Ratio activation \sep Theranostics
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%%
-%% Start line numbering here if you want
-%%
-% \linenumbers
-
-% \listoftodos
-
-%% main text 
 \section{Introduction} \label{sec:intro}
@@
 %         \includegraphics[height=2in]{./figures/target2.png}
-        \includegraphics[height=2in]{cutaway.png}
+        \includegraphics[height=2in]{./figures/cutaway.png}
         \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \includegraphics[height=2.5in]{holder.pdf}
+        \includegraphics[height=2.5in]{./figures/holder.pdf}
         \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
@@
  \centering
- \includegraphics[scale=0.6]{scatt_angle.pdf}
+ \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
  % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
@@
  \centering
- \includegraphics[scale=0.6]{mcnp_flux_new.pdf}
+ \includegraphics[scale=0.6]{./figures/mcnp_flux_new.pdf}
  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
@@
  \centering
- \includegraphics[scale=0.6]{fracplot_new.pdf}
+ \includegraphics[scale=0.6]{./figures/fracplot_new.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
 The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
-Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
+% Example spectra for each production pathway can be seen in Figures \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
+Example spectra for each production pathway can be seen in Figures \autoref{fig:main_spectra}a and \autoref{fig:main_spectra}b.
+
+% \newcommand{\subfigimg}[3][,]{%
+%   \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
+%   \leavevmode\rlap{\usebox1}% Print image
+%   \rlap{\hspace*{50pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
+%   \phantom{\usebox1}% Insert appropriate spcing
+% }
 
@@
     \centering
-    \begin{subfigure}[t]{\textwidth}
+    \subfloat{
         \centering
@@
 %         \includegraphics[width=5in]{./figures/ti_foils.png}
-        \subfigimg[width=5in]{a)}{./47sc_gspectrum_alt.pdf}
+        \subfigimg[width=5in]{a)}{./figures/47sc_gspectrum_alt.pdf}{50}
+%          \subfigimg[width=\linewidth]{}{./figures/51Cr.pdf}{50}
 %         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
 % 	\caption{}
-        \refstepcounter{subfigure}\label{fig:spectra_a}
-    \end{subfigure}%
+%         \refstepcounter{subfloat}
+        \label{fig:spectra_a}
+    }%
     \\
-    \begin{subfigure}[t]{\textwidth}
+    \subfloat{
         \centering
@@
 %         \includegraphics[width=5in]{./figures/Sample_spectra.png}
-        \subfigimg[width=5in]{b)}{./64Cu_gspectrum_alt.pdf}
+        \subfigimg[width=5in]{b)}{./figures/64Cu_gspectrum_alt.pdf}{50}
 %         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
-          \refstepcounter{subfigure}       \label{fig:spectra_b}
-    \end{subfigure}
+%           \refstepcounter{subfloat}      
+          \label{fig:spectra_b}
+    }
     \caption{Example gamma spectra collected to monitor radioisotope production.
@@
 To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals.
-The resulting time series displayed in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511} allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
+The resulting time series displayed in Figures \ref{fig:decay_curves}a - \ref{fig:decay_curves}d allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
 The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives \cite{Burrows2007,Singh2007,Blachot2010a,Blachot2012,Blachot2010}, confirming the respective peak assignments.
@@
     \centering
-    \begin{subfigure}[t]{0.49\textwidth}
+    \subfloat{
         \centering
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{a)}{336keV_curve_new.pdf}
+        \subfigimg[width=0.495\textwidth]{a)}{./figures/336keV_curve_new.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_336}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[scale=0.6]{b)}{391keV_curve_new.pdf}
+%          \refstepcounter{subfloat}
+         \label{fig:decay_curve_336}
+%          
+         \subfigimg[width=0.495\textwidth]{b)}{./figures/391keV_curve_new.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:decay_curve_391}
-    \end{subfigure}%
+%          \refstepcounter{subfloat}
+         \label{fig:decay_curve_391}
+    }%
+%      \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+%         \subfigimg[width=0.495\textwidth]{b)}{./figures/391keV_curve_new.pdf}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+% %          \refstepcounter{subfloat}
+%          \label{fig:decay_curve_391}
+%     }%
     \\
-    \begin{subfigure}[t]{0.49\textwidth}
+    \subfloat{
         \centering
 %         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[scale=0.6]{c)}{417keV_curve_new.pdf}
+        \subfigimg[width=.495\textwidth]{c)}{./figures/417keV_curve_new.pdf}{50}
 %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:decay_curve_417}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.49\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[scale=0.6]{d)}{511keV_curve_new.pdf}
+%                  \refstepcounter{subfloat}
+                 \label{fig:decay_curve_417}
+%                  
+	\subfigimg[width=0.495\textwidth]{d)}{./figures/511keV_curve_new.pdf}{50}
 %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:decay_curve_511}
-    \end{subfigure}%
+%         \refstepcounter{subfloat} 
+        \label{fig:decay_curve_511}
+    }
+%      \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \subfigimg[width=0.495\textwidth]{d)}{./figures/511keV_curve_new.pdf}{50}
+% %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+% %         \refstepcounter{subfloat} 
+%         \label{fig:decay_curve_511}
+%     }%
     \caption{Decay curves used to verify photopeak transition assignment.
@@
  \centering
- \includegraphics[scale=0.55]{fig1_cropped.pdf}
+ \includegraphics[scale=0.55]{./figures/fig1_cropped.pdf}
  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
@@
  \centering
- \includegraphics[scale=0.65]{47sc_fixed_1point.pdf}
+ \includegraphics[scale=0.65]{./figures/47sc_fixed_1point.pdf}
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
  \centering
- \includegraphics[scale=0.65]{64cu_fixed_1point.pdf}
+ \includegraphics[scale=0.65]{./figures/64cu_fixed_1point.pdf}
  % 47Sc_fixed.pdf: 375x294 pixel, 72dpi, 13.23x10.37 cm, bb=0 0 375 294
@@
 This will focus on radionuclides which permit more customized and precise dose deposition, as well as patient-specific treatments.
-
-%  \comment{Should we specifically mention other isotopes we plan to measure?}
-
- \section{Acknowledgements}
-
- We would like to particularly point out the crucial role played by Cory Waltz in the design and commissioning of the HFNG.
- We acknowledge Glenn Jones of G\&J Jones Enterprises of Dublin, CA for the construction  of the High Flux Neutron Generator. 
- Lastly, we would like to acknowledge the students in the Nuclear Reactions and Radiation (NE102) laboratory course at UC Berkeley who participated in these experiments, including Joe Corvino, Nizelle Fajardo, Scott Parker and Evan Still.
-
- This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% \comment{Add NSF Grant number from P. Renne.}
-
-% \pagebreak
-% 
-% \onecolumn
-% 
-% \appendix
-
-% \section{Data} \label{data}
-% 
-% % \begin{longtable}{|c|c|c|c|c|} 
-% % \caption{My caption}
-% % \label{tab:dummy}
-% % % \begin{tabular}{|c|c|c|c|c|}
-% %    \hline
-% %  
-% % \end{longtable}
-% hello world
-
-% 
-% \section{Results} \label{equations}
-% 
-% Tabulated results are listed here, to avoid breaking text flow in the main text.
-% 
-% \begin{table}[h]
-% \centering
-% \caption{Transition conversion coefficients and efficiencies}
-% \label{my-label2}
-% \begin{tabular}{c|c|c|c|c}
-% Nucleus & Transition       & E\(_\gamma\) (keV) & \(\alpha\), Conversion Coefficient  & \(\epsilon\), Intrinsic Efficiency \\ \hline
-% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 0.0569           \(\pm\) 0.0008              & 1863.906   \\
-%         & 4\(\rightarrow\)2 & 422.6          & 0.00887          \(\pm\) 0.00013             & 1219.507   \\
-%         & 6\(\rightarrow\)4 & 575.7          & 0.00356          \(\pm\) 0.00005             & 956.569    \\ \hline
-% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 0.0205          \(\pm\) 0.0003              & 1340.054   \\
-%         & 4\(\rightarrow\)2 & 457.63         & 0.01154          \(\pm\) 0.00017             & 1142.505   \\
-%         & 6\(\rightarrow\)4 & 582.4          & 0.00593          \(\pm\) 0.00009             & 948.705    \\ \hline
-% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 0.00599         \(\pm\) 0.00009             & 926.624    \\
-%         & 4\(\rightarrow\)2 & 528.25         & 0.00848         \(\pm\) 0.00012             & 1019.604   \\
-%         & 6\(\rightarrow\)4 & 529.7          & 0.00842         \(\pm\) 0.00012             & 1017.470   \\ \hline
-% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 0.175           \(\pm\) 0.0025              & 2085.452   \\
-%         & 4\(\rightarrow\)2 & 330.88         & 0.0333         \(\pm\) 0.0005              & 1485.782   \\
-%         & 6\(\rightarrow\)4 & 431.3          & 0.015          \(\pm\) 0.00021             & 1199.258  
-% \end{tabular}
-% \end{table}
-% 
-% \begin{table}[h]
-% \centering
-% \caption{Extracted transition intensities}
-% \label{my-label}
-% \begin{tabular}{c|c|c|c|c|c}
-% Nucleus & Transition       & E\(_\gamma\) (keV) & \(A_{obs}\), Peak Area (a.u.)   & \(A_{source}\),  Peak Intensity (a.u.)  & \(R_i\), Relative Intensity  \\ \hline
-% \ce{^{110}Ru}   & 2\(\rightarrow\)0 & 240.7          & 1097    \(\pm\)   136        & 0.622          \(\pm\) 0.077             & 1.000              \(\pm\) 0.175                 \\
-%         & 4\(\rightarrow\)2 & 422.6          & 515     \(\pm\)   107        & 0.426          \(\pm\) 0.089             & 0.685              \(\pm\) 0.200                 \\
-%         & 6\(\rightarrow\)4 & 575.7          & 144      \(\pm\)  55         & 0.151          \(\pm\) 0.058             & 0.243              \(\pm\) 0.198                 \\ \hline
-% \ce{^{140}Xe}   & 2\(\rightarrow\)0 & 376.657        & 542     \(\pm\)   129        & 0.413          \(\pm\) 0.098             & 1.000              \(\pm\) 0.337                 \\
-%         & 4\(\rightarrow\)2 & 457.63         & 357       \(\pm\) 59         & 0.316          \(\pm\) 0.052             & 0.766              \(\pm\) 0.254                 \\
-%         & 6\(\rightarrow\)4 & 582.4          & 161       \(\pm\) 61         & 0.171          \(\pm\) 0.065             & 0.414              \(\pm\) 0.288                 \\ \hline
-% \ce{^{140}Ba}   & 2\(\rightarrow\)0 & 602.35         & 822       \(\pm\) 164        & 0.892          \(\pm\) 0.178             & 1.000              \(\pm\) 0.282                 \\
-%         & 4\(\rightarrow\)2 & 528.25         & 384       \(\pm\) 78         & 0.380          \(\pm\) 0.077             & 0.426              \(\pm\) 0.186                 \\
-%         & 6\(\rightarrow\)4 & 529.7          & 310       \(\pm\) 104        & 0.307          \(\pm\) 0.103             & 0.344              \(\pm\) 0.229                 \\ \hline
-% \ce{^{144}Ba}   & 2\(\rightarrow\)0 & 199.326        & 900       \(\pm\) 242        & 0.507          \(\pm\) 0.136             & 1.000              \(\pm\) 0.380                 \\
-%         & 4\(\rightarrow\)2 & 330.88         & 535       \(\pm\) 127        & 0.372          \(\pm\) 0.088             & 0.734              \(\pm\) 0.307                 \\
-%         & 6\(\rightarrow\)4 & 431.3          & 363       \(\pm\) 64         & 0.307          \(\pm\) 0.054             & 0.606              \(\pm\) 0.250                
-% \end{tabular}
-% \end{table}
-%     
-% \pagebreak
-% 
-% 
-% 
-% \section{Supplemental Figures} \label{fit_figures}
-% 
-% The remaining figures of the fitted \(\gamma\)-ray transition photopeaks are included here for reference, to avoid over-cluttering the main text.
-% 
-% 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru240-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 240.7 keV peak and its surroundings.}
-% %  \label{fig:110Ru240}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru422-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 422.6 keV peak and its surroundings.}
-% %  \label{fig:110Ru422}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit110Ru575-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{110}Ru} 575.7 keV peak and its surroundings.}
-% %  \label{fig:110Ru575}
-% % \end{figure}
-% 
-% 
-% 
-% 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe376-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 376.7 keV peak and its surroundings.}
-% %  \label{fig:140Xe376}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe457-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 457.6 keV peak and its surroundings.}
-% %  \label{fig:140Xe457}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Xe582-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Xe} 582.3 keV peak and its surroundings.}
-% %  \label{fig:140Xe582}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit140Ba602-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{140}Ba} 602.4 keV peak and its surroundings.}
-% %  \label{fig:140Ba602}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba199-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 199.3 keV peak and its surroundings.}
-% %  \label{fig:144Ba199}
-% % \end{figure}
-% % 
-% % 
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba330-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 330.9 keV peak and its surroundings.}
-% %  \label{fig:144Ba330}
-% % \end{figure}
-% % 
-% % \begin{figure}[h]
-% %  \centering
-% %  \includegraphics[scale=0.7]{./hw04/fit144Ba431-cropped.pdf}
-% %  % fit110Ru240.ps: 570x750 pixel, 72dpi, 20.11x26.46 cm, bb=0 0 570 750
-% %  \caption{Fit to the \ce{^{144}Ba} 431.3 keV peak and its surroundings.}
-% %  \label{fig:144Ba431}
-% % \end{figure}
-% 
-% 
-% 
-%     
-% \pagebreak
-% 
-% 
-% % \appendix
-% \section{Source Code} \label{source}
-% 
-% \begin{center}
-%  \texttt{gint.py} - Implementation of the Wilhelmy statistical model, used to estimate total transition intensities in the ground state band  of primary fission fragments
-% \end{center}
-% 
-% % \begin{lstlisting}
-% % \lstloadlanguages{Python}
-% 
-% % \lstinputlisting[linewidth=\columnwidth,language=Python,breaklines=true,frame=single]{./hw04/gint.py}
-% % % \end{lstlisting}
-% 
-% 
-% 
-% \begin{center}
-%  \texttt{hw04\_04.m} - used to process and plot statistical transition intensity curves
-% \end{center}
-% 
-%  
-% %   \lstinputlisting[frame=single]{./hw04/hw04_04.m}
-% 
-% 
-% % \begin{verbatim}[commandchars=\\\{\}]
-% % \verbatiminput{./HW01/test.txt}
-% % \end{verbatim}
-% 
-% %% The Appendices part is started with the command \appendix;
-% %% appendix sections are then done as normal sections
-% %% \appendix
-% 
-% %% \section{}
-% %% \label{}
-% 
-% %% References
-% %%
-% %% Following citation commands can be used in the body text:
-% %% Usage of \cite is as follows:
-% %%   \cite{key}         ==>>  [#]
-% %%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
-
-% \twocolumn
-
-%% References with BibTeX database:
-
-% \bibliographystyle{elsarticle-num}
-% \bibliographystyle{elsarticle-harv}
-% \bibliographystyle{elsarticle-num-names}
-% \bibliography{<your-bib-database>}
-% \addcontentsline{toc}{chapter}{Bibliography}
-\bibliographystyle{elsarticle-num}
-% \bibliographystyle{ieeetr}
-\bibliography{./library}
-% \thispagestyle{fancyTOC}
-
-% H. F. Aly et al., Microchim. Acta, vol. 59, no. 1, 1971.
-
-% K. S. Bhatki et al., J. Radioanal. Chem., vol. 2, no. 1-2, 1969.
-
-% T. H. Bokhari et al., J. Radioanal. Nucl. Chem., vol. 283, no. 2, 2010.
-
-% J. F. Briesmeister et al., Los Alamos National Laboratory, 1986.
-
-% A. J. Koning et al., AIP Conference Proceedings, 2005, vol. 769, no. 2.
-
-% H. Liskien et al., Nucl. Data Tables, vol 11, 1973.
-
-% M. R. Lewis et al., J. Nucl. Med., vol. 44, no. 8, Aug. 2003.
-
-% C. Müller et al., J. Nucl. Med., vol. 55, no. 10, Oct. 2014.
-
-% N. Otuka et al., Nucl. Data Sheets, vol. 120, 2014.   (EXFOR)
-
-% L. Pietrelli et al., J. Radioanal. Nucl. Chem., vol. 157, no. 2, 1992.
-
-% S. M. Qaim et al., IAEA Technical Reports Series No. 473, 2011.
-
-% T. Shimizu, et al, Ann. Nucl. Energy, vol. 31, no. 9, pp. 975-990, 2004.
-
-% T. Shimizu, et al, Nucl. Instruments Methods Phys. Res. Sect. A Accel. Spectrometers, Detect. Assoc. Equip., vol. 527, no. 3, pp. 543-553, 2004.
-
-% D. Updegraff et al., ''Nuclear Medicine without Nuclear Reactors or Uranium Enrichment,'' 2013.
-
-%% Authors are advised to use a BibTeX database file for their reference list.
-%% The provided style file elsarticle-num.bst formats references in the required Procedia style
-
-%% For references without a BibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
-
-\end{document}
-
-%%
-%% End of file `ecrc-template.tex'.

### 2018-04-05 nb_px_paper/nb_abstract_text.tex
Broke Nb(p,x) paper into container w/ separate body text, appendices, and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

--- 2018-04-03 nb_px_paper/nb_px_paper.tex
@@
-% % ****** Start of file apssamp.tex ******
-% %
-% %   This file is part of the APS files in the REVTeX 4.1 distribution.
-% %   Version 4.1r of REVTeX, August 2010
-% %
-% %   Copyright (c) 2009, 2010 The American Physical Society.
-% %
-% %   See the REVTeX 4 README file for restrictions and more information.
-% %
-% % TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% % as well as the rest of the prerequisites for REVTeX 4.1
-% %
-% % See the REVTeX 4 README file
-% % It also requires running BibTeX. The commands are as follows:
-% %
-% %  1)  latex apssamp.tex
-% %  2)  bibtex apssamp
-% %  3)  latex apssamp.tex
-% %  4)  latex apssamp.tex
-% %
-% \documentclass[%
-%  reprint,
-% superscriptaddress,
-% onecolumn,
-% linenumbers,
-% notitlepage,
-% %groupedaddress,
-% %unsortedaddress,
-% %runinaddress,
-% %frontmatterverbose, 
-% %preprint,
-% %showpacs,preprintnumbers,
-% %nofootinbib,
-% %nobibnotes,
-% %bibnotes,
-%  amsmath,amssymb,
-%  aps,
-% prc,
-% %prb,
-% %rmp,
-% %prstab,
-% %prstper,
-% %floatfix,
-% ]{revtex4-1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Important note on usage                  %%
-%% -----------------------                  %%
-%% This file must be compiled with PDFLaTeX %%
-%% Using standard LaTeX will not work!      %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-% \documentclass[5p]{elsarticle}
-% Good for final formatting  - two column
-% 
-% \documentclass[3p,times]{elsarticle}
-% Final formatting
-\documentclass[3p]{elsarticle}
-% Good for proofing - single column
-%
-
-\usepackage[american]{babel}
-\usepackage{amsmath}
-\usepackage[version=3]{mhchem} 
-% \usepackage{fixltx2e}
-% \usepackage{refcount}
-% \usepackage{siunitx}
-% \usepackage{lastpage}
-% \usepackage{textcomp}
-\usepackage{mathtools}
-
-\usepackage{xfrac}
-\usepackage{lmodern}
-\usepackage[hidelinks]{hyperref}
-% \usepackage{cool}
-% \usepackage{cancel}
-\usepackage{microtype}
-\usepackage{listings}
-\usepackage{mcode}
-\usepackage [autostyle, english = american]{csquotes}
-% \usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{booktabs,siunitx}
-\usepackage{gensymb}
-\usepackage[normalem]{ulem}
-
-% \usepackage{mathtools, cuted}
-
-% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\usepackage{color}
-
-\usepackage[colorinlistoftodos]{todonotes}
-
-\usepackage[section]{placeins}
-\usepackage{multirow}
-
-\usepackage{lineno}
-
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-
-\lstset{basicstyle=\small\ttfamily,columns=fullflexible}
-
-% \usepackage{verbatim}
-
-% \usepackage{gensymb}
-% \usepackage{enumerate}
-% \usepackage{float}
-% \usepackage{bm}
-% \usepackage{csquotes}
-% \usepackage{mathtools}
-% \usepackage[sort&compress]{natbib}
-% \usepackage{biblatex}
-
-%% The `ecrc' package must be called to make the CRC functionality available
-\usepackage{ecrc}
-
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-%% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research B}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{A.S. Voyles et al.}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{nimb}
-% \jid{yspmi}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Nucl Instrum Meth B}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-\biboptions{sort&compress}
-
-% if you have landscape tables
-\usepackage[figuresright]{rotating}
-
-% put your own definitions here:
-%   \newcommand{\cZ}{\cal{Z}}
-%   \newtheorem{def}{Definition}[section]
-%   ...
-
-% add words to TeX's hyphenation exception list
-%\hyphenation{author another created financial paper re-commend-ed Post-Script}
-
-% declarations for front matter
-
-\usepackage{fancyvrb}
-\usepackage{color}
-
-\definecolor{mygreen}{rgb}{0,0.6,0}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mymauve}{rgb}{0.58,0,0.82}
-
-\lstset{ %
-  backgroundcolor=\color{white},   % choose the background color
-  basicstyle=\footnotesize,        % size of fonts used for the code
-  breaklines=true,                 % automatic line breaking only at whitespace
-  captionpos=b,                    % sets the caption-position to bottom
-  commentstyle=\color{mygreen},    % comment style
-  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-  keywordstyle=\color{blue},       % keyword style
-  stringstyle=\color{mymauve},     % string literal style
-}
-
-% Sin and Cos with auto-parentheses 
-\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
-\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
-\newcommand{\expp}[1]{\exp{\left( #1\right)}}
-\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
-\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
-\newcommand{\pp}[1]{\left( #1\right)}
-\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
-\newcommand{\angstrom}{\mbox{\normalfont\AA}}
-\newcommand{\norm}[1]{\lVert #1 \rVert}
-
-\newcommand{\textred}[1]{\textcolor{red}{ #1}}
-\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}
-
-\newcommand{\cmmnt}[1]{}
-
-\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
-
-\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}
-
-\newcommand{\etal}{\emph{et\,al.}}
-
-% Tweak sim for better inline text tilde
-\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
-% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}
-
-\sisetup{separate-uncertainty=true,table-space-text-post = *}
-
-\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
-
-% \newcounter{subfigure}[figure]
-
-\newcommand{\subfigimg}[4][,]{%
-  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
-  \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
-  \phantom{\usebox1}% Insert appropriate spcing
-}
-% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}
-
-\makeatletter
-% Make common definition of mean
-\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}
-
-\makeatother
-
-\begin{document}
-
-\begin{frontmatter}
-
-%\preprint{APS/123-QED}
-
-% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
-% % \thanks{A footnote to the article title}%
-% 
-% \author{Andrew S. Voyles}
-%  \email{andrew.voyles@berkeley.edu}
-% \affiliation{%
-%  Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% }% 
-% \author{Lee A. Bernstein}
-% \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
-% \affiliation{%
-%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% }%
-% \author{Eva R. Birnbaum}
-% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-% \author{Jonathan W. Engle}
-%  \email{jwengle@wisc.edu}
-% \affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
-% \author{Stephen A. Graves}
-% \affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
-% \author{Toshihiko ??? Kawano}
-% \affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-% %  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
-% \author{Amanda M. Lewis}%
-% % \author{Eric F. Matthews}%
-% %  \email{Second.Author@institution.edu}
-% \affiliation{%
-%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% }%
-% \author{Francois M. Nortier}
-% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}
-
-% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-\author[ucb]{Andrew S. Voyles \corref{cor1}}
-\ead{andrew.voyles@berkeley.edu}
-
-% \author[lbl]{M.S. Basunia}
-% 
-% \author[ucb]{J.C. Batchelder}
-%
-
-\author[lbl,ucb]{Lee A. Bernstein}
-
-\author[lanl]{Eva R. Birnbaum}
-
-\author[uwm]{Jonathan W. Engle}
-\ead{jwengle@wisc.edu}
-
-\author[iowa]{Stephen A. Graves}
-
-\author[tlanl]{Toshihiko  Kawano}
-
-\author[ucb]{Amanda M. Lewis}
-
-\author[lanl]{Francois M. Nortier}
-
-\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
-\address[lbl]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
-% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
-\address[lanl]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-\address[iowa]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
-\address[tlanl]{Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-
-% % \collaboration{MUSO Collaboration}%\noaffiliation
-% % 
-% % \author{Charlie Author}
-% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
-% % \affiliation{
-% %  Second institution and/or address\\
-% %  This line break forced% with \\
-% % }%
-% % \affiliation{
-% %  Third institution, the second for Charlie Author
-% % }%
-% % \author{Delta Author}
-% % \affiliation{%
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% % }%
-% % 
-% % \collaboration{CLEO Collaboration}%\noaffiliation
-% 
-% \date{\today}% It is always \today, today,
-%              %  but any date may be explicitly specified
-% 
-% %% Title, authors and addresses
-% 
-% %% use the tnoteref command within \title for footnotes;
-% %% use the tnotetext command for the associated footnote;
-% %% use the fnref command within \author or \address for footnotes;
-% %% use the fntext command for the associated footnote;
-% %% use the corref command within \author for corresponding author footnotes;
-% %% use the cortext command for the associated footnote;
-% %% use the ead command for the email address,
-% %% and the form \ead[url] for the home page:
-% %%
-\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}
-
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-% \dochead{Short}
-%% Use \dochead if there is an article header, e.g. \dochead{Short communication}
-
-% 
-% % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-% \author[ucb]{Andrew S. Voyles \corref{cor1}}
-% \ead{andrew.voyles@berkeley.edu}
-% 
-% % \author[lbl]{M.S. Basunia}
-% % 
-% % \author[ucb]{J.C. Batchelder}
-% 
-% 
-% \author[ucb,lbl]{Lee A. Bernstein}
-% 
-% 
-% \author[lanl]{Eva R. Birnbaum}
-% 
-% \author[uwm]{Jonathan W. Engle}
-% 
-% \author[iowa]{Stephen A. Graves}
-% 
-% \author[ucb]{Amanda M. Lewis}
-% 
-% 
-% \author[lanl]{Francois M. Nortier}
-
-% \author[ucb]{M.A. Unzueta}
-% 
-% \author[ucb]{K.A. van Bibber}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-% \cortext[cor1]{Corresponding author}
-% \cortext[cor2]{Principal corresponding author}
-% \fntext[fn1]{This is the specimen author footnote.}
-% \fntext[fn2]{Another author footnote, but a little more longer.}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
-% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
-% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
-% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
-% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
-% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
-% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
-
-\begin{abstract}
-
 % Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
@@
 % \end{description}
-\end{abstract}
-
-% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-
-% \begin{abstract}
-
-% \end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-Nb+p \sep Cu+p \sep Niobium 
-% \sep Copper\sep Aluminum 
-\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
-% Proton activation \sep 
-% Proton transport \sep 
-Stacked target activation \sep Monitor reactions \sep 
-% Monitor foils 
-Medical isotope production \sep Isomer branching ratios \sep  
-% Nuclear spin distributions  \sep 
-MCNP \sep  LANL
-% 
-% %% MSC codes here, in the form: \MSC code \sep code
-% %% or \MSC[2008] code \sep code (2000 is the default)
-% 
-\end{keyword}
-
-\end{frontmatter}
-
-% \maketitle
-
-%%
-%%  To-do list for comments
-%%
-% \listoftodos
-
-%%
-%% Start line numbering here if you want
-%%
-\linenumbers
-
-%% main text 
-\section{Introduction} \label{sec:intro}
-
-% Referring to abstract:
-% % \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
-% 
-% 
-% \comment{Comment on the Si production here?  (see red text)}
-% 
-% \comment{Add extra physics language with Lee.}
-
-% \comment{cite theranostic papers, etc}
-
-Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S. alone 
-% ,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases 
-\cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
-% The vast majority
-Most of the radionuclides currently used for these procedures are produced 
-% in the field's array of
-by low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerators, 
-% capabilities, which routinely produce many of the staple medical radionuclides, such as 
-e.g., \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ga}, \ce{^{82}Rb}, and \ce{^{123}I}. 
-These accelerators also produce 
-% , as well as many  
-% of the 
-non-medical radionuclides with commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
-% \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
-I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: In this context, I would make this definition based on what machines in the US are routinely used for medical isotope production - based on this, I agree with 200 MeV.
-}
-% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
-% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
-Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
-% \cite{Qaim201731}. 
-% Move next sentence to Fe paper
-% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
-Candidate isotopes to meet these needs 
-% of personalized medicine 
-have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
-These studies will serve to facilitate the production of clinically relevant quantities of radioactivity.
-
-Accurate cross section measurements using  activation methods benefit from well-characterized monitor reactions.  
-Currently there is 
-% , which  currently
-a paucity of such data at intermediate energies, and much of what exists have  high uncertainties (\textgreater15\%).
-% One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.
-% This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
-% Lee - cut?
-Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}.
-% Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
-% While work is needed to improve upon existing monitor reaction data, the development of n
-% Lee - cut?
-New reactions can expand the available range of options for the monitoring of charged particle beams.
-This work 
-% in particular seeks to improve this range of options by 
-is an attempt to characterize a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory,
-% IPF
-the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the Separated Sector Cyclotron at the 
-% iThemba LABS
-iThemba Laboratory for Accelerator Based Sciences.
-% \comment{Stephen: I'm having a hard time following this paragraph.
-Some of your syntax overlaps significantly with nuclear medicine \& medical physics terminology with different intended meanings.
-For example 'dosimetry' is typically taken to mean the measurement of absorbed energy per unit mass (J/kg) and associated measurements/specifications.
-Another example, 'dosimetry standard' is used quite often when referring to NIST air kerma reference standards which are the bedrock of Accredited Dosimetry Calibration Lab (ADCL) measurements.
-As you are more familiar with classic Nuclear Physics writing, perhaps you better know how this language will be interpreted.
-}
-
-% % 
-% 
-% Most of this should be more appropriate for the PhD thesis?
-% 
-% % 
-% Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}.
-% % All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
-% % \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
-% Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
-% % \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
-% Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
-% This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
-% This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.
-% In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
-% This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
-% While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
-% % For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
-% % In these experiments, a
-% A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
-% % \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
-% Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.
-
-% In theory, nearly any radioisotope can serve as a reaction monitor, but 
-% those desired to be classified as a 
-Desirable monitor reactions 
-% standard 
-possess several hallmark characteristics,  
-% The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
-% Primarily, this means selecting a radionuclide product with 
-% a number of 
-including intense and distinct gamma-rays, 
-% with high intensities,  
-which can be used to uniquely identify it during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
-% The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
-% \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
-Care should also be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
-For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
-% Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
-% However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
-% Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
-% Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
-% and leisurely 
-% following end-of-bombardment.
-% without the majority if it decaying away.
-% In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
-% For proper quantification, i
-It is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
-This includes a precise and well-established half-life,  
-% needed to  correct for decay losses, 
-as well as well-characterized decay gamma-ray intensities.
-% In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
-% Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
-From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily available
-% readily commercially available at an affordable price and is 
-and  chemically inert.
-% --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current. 
-% Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
-% For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
-% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectrometry.
-% For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
-Targets which can be formed into a wide thickness range are convenient, as selection is subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
-% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
-% \comment{Stephen:  This is also a discussion point.
-If you're trying to introduce the purpose of this paper, i.e.
-the establishment of a new monitor reaction, I would try to condense paragraphs 3--9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction.
-The rest of this content can be included in the discussion if you feel it is necessary.}
-Lastly, and perhaps most importantly for high-energy monitor reaction applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
-Typically, this is  mostly a concern for secondary neutrons produced through (z,xn) reactions, 
-% on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
-% Any
-but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often 
-% a laborious task 
-difficult to accurately and unambiguously separate out the fraction of secondary particles contributing to the total activation.
-
-One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
-Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
-\ce{^{90}Mo} also has 
-% excellent decay properties ---
-a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997})  
-% allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
-and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production.
-In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
-
-The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo}  
-% ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) 
-via the $^\text{nat}$Nb(p,x) reaction. 
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
-% These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
-These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
-% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the diagnostic agent \ce{^{82\text{m}}Rb}.
-
-%   \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
-%   
-%   \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}
-
-In addition to providing a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
-Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
-These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$\,m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$\,d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$\,h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$\,d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$\,h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$\,h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$\,m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$\,h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
-
-The measurements described in this paper involve the use of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here.
-By expanding the available set of monitor reaction standards and well-characterized isotope production excitation functions, this work should help optimize medical isotope production modalities, making more options   available for modern medical imaging and cancer therapy.
-
-\section{Experimental methods and materials}\label{sec:experiment}
-
-% While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work 
-The work described herein follows the  methods established by Graves \etal\ for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.
-
-\subsection{Stacked-target design }\label{sec:target_design}
-
-% \comment{Regex to replace all hard figure references with LaTeX cross-references  [F,f]igure[^s*}]     }
-
-A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
-% For targets, a
-A series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
-Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
-Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
-% , along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
-The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
-One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
-These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
-% These six foil packet bundles were inserted into one of six  
-The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
-After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
-The specifications of the target stack design for this work is presented in \autoref{tab:stack_table}.
-
-This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
-The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
-The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
-The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV --- this energy profile was used for all later analysis.
-At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
-The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectrometry, which started approximately 6 hours following end-of-bombardment.
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
- % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
- \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place.
-The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell.
-The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.
-}
-\end{figure}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Specifications of the  target stack design in the present work.
-The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here.
-The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
-Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
-\label{tab:stack_table}
-\small
-\begin{tabular}{@{}llll@{}}
-\toprule
-% Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
-Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
-SS profile monitor & 249.8 \micro m         & 194.56                                      & 0.29                      \\
-Al-1               & 25.0 \micro m          & 6.52                                        & 0.72                      \\
-Cu-1               & 61.3 \micro m          & 53.74                                       & 0.15                      \\
-Nb-1               & 30.0 \micro m          & 23.21                                       & 0.17                      \\
-Al Degrader 01     & 4.96 mm           & -                                            & -                          \\
-Al-2               & 25.5 \micro m          & 6.48                                        & 0.36                      \\
-Cu-2               & 61.8 \micro m          & 53.85                                       & 0.17                      \\
-Nb-2               & 30.8 \micro m          & 22.91                                       & 0.17                      \\
-Al Degrader 02     & 4.55 mm           & -                                            & -                          \\
-Al-3               & 25.8 \micro m          & 6.47                                        & 0.31                      \\
-Cu-3               & 61.5 \micro m          & 53.98                                       & 0.11                      \\
-Nb-3               & 31.0 \micro m          & 22.91                                       & 0.24                      \\
-Al Degrader 03     & 3.52 mm           & -                                            & -                          \\
-Al-4               & 26.3 \micro m          & 6.51                                        & 0.41                      \\
-Cu-4               & 61.3 \micro m          & 53.46                                       & 0.22                      \\
-Nb-4               & 30.8 \micro m          & 22.55                                       & 0.25                      \\
-Al Degrader 04     & 3.47 mm           & -                                            & -                          \\
-Al-5               & 26.5 \micro m          & 6.48                                        & 0.29                      \\
-Cu-5               & 61.5 \micro m          & 53.57                                       & 0.11                      \\
-Nb-5               & 30.8 \micro m          & 22.11                                       & 0.25                      \\
-Al Degrader 05     & 3.46 mm           & -                                            & -                          \\
-Al-6               & 26.3 \micro m          & 6.48                                        & 0.62                      \\
-Cu-6               & 62.0 \micro m          & 53.84                                       & 0.32                      \\
-Nb-6               & 31.3 \micro m          & 22.12                                       & 0.13                      \\
-SS profile monitor & 124.4 \micro m         & 101.34                                      & 0.23                      \\ \bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Measurement of induced activities}\label{sec:spectroscopy}
-
-% For consistency, a
-A single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
-The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
-Samples were counted at fixed positions ranging 4.5--83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
-The foils were counted  for a period of 2 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities,  with dead time never exceeding 5\%.
-An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
-%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
-
-\begin{figure}
- \centering
- \includegraphics[width=6in]{./figures/sample_gspec.pdf}
- % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
- \caption{A gamma spectrum, collected from an activated Nb foil at approximately 80 MeV.
-While the majority of observed reaction products are visible in this spectrum,  the \ce{^{90}Mo} decay lines, which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction, are high in intensity and clearly isolated from surrounding peaks.}
- \label{fig:gspec}
-\end{figure}
-
-Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
-The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
-% For reference, t
-The nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-Data for photon attenuation coefficients were taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
-% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
-Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
-% activity for each gamma-ray possesses a 
-The total propagated uncertainty of the measured activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
-
-Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly by decay down a mass chain.
-To this end, it is useful to differentiate between the types of cross sections reported in this work. 
-For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
-% In addition, 
-Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
-
-% To convert these activities into cross sections, c
-Corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB, from the measured activities.
-The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
-For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
-% \begin{equation}
-% A\pp{t} = A_0 e^{-\lambda t}
-% \end{equation}
-Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
-As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
-\begin{equation}
-A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_{i,0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
-\end{equation}
-where $j$ refers to a precursor nucleus populating a specific end-product.  
-While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
-\begin{equation}
-A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
-\end{equation}
-In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
-After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
-
-% \comment{Regex to replace table hard link with LaTeX cross-reference. - match w/ [T,t]able[^*}]   }
-
-\subsection{Proton fluence determination}\label{sec:dosimetry}
-
-% \comment{Stephen:  Still not a huge fan of the dosimetry terminology, but I would defer to the preference of those with more experience in the field. }
-
-% describe integral equation for converting activities to currents here
-% 
-% % % 
-% 
-%  Move these first two commented sentences into PhD thesis.
-% 
-% % % 
-% An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
-% At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
-% For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
-% To this end, 
-In addition to the LANSCE-IPF beamline's direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide more sensitive beam current monitors.
-% These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
-The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used for  proton fluence measurement \cite{gul2001charged}.
-% The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
-Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution was expected for all monitor and target foils.
-As a result, the integral form of the well-known activation equation was used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
-%by convolving the IAEA recommended cross section values with the proton energy distribution:
-% \begin{equation}
-% A_0 = I\ \rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE
-% \end{equation}
-\begin{equation}
-I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
-\end{equation}
-where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy $E$, and $\frac{d\phi}{dE}$ is the differential proton fluence.
-Using this formalism, the quantified EoB activities for each monitor reaction may be converted into a measured proton fluence at each energy position.
-
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
-Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
-The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
-The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
-Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental source data sets used in their evaluation.
-Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
-For the monitor reactions employed in this work, these data sets are G.
-Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \cite{Steyn1990}, M.
-Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S.
-Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.
-
-\subsection{Proton transport calculations}\label{sec:proton_transport}
-
-Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-These estimates of average beam energy in each foil are useful for the preliminary stack design.
-% , as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering. 
-However, for final energy and fluence determinations, a more rigorous method of proton transport modeling is needed.
-The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
-% In addition, 
-MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
-As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.
-$10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
-
-The ability to model the full energy distribution in each target position is vital for stacked target irradiations, due to the progressively larger energy straggling towards the rear of the stack.
-The initial proton beam has a finite energy spread (an approximately 0.1 MeV Gaussian width at 100 MeV), and since stopping power for charged particles is inversely proportional to their energy, the low-energy tail of the energy distribution is degraded more in each stack element than the high-energy tail.
-This effect compounds  towards the rear of the stack, creating a significantly broadened low-energy tail, and a progressively larger net shift of the centroid to a lower energy. 
-% For each foil in the target stack, 
-To account for this increasing energy uncertainty, a suitably representative energy must be established for  each foil in the target stack.
-In this work, the flux-weighted average proton  energy in each foil, $\langle E \rangle$,  represents the energy centroid for protons in a target stack component, calculated using the energy distributions $\frac{d\phi}{dE}$ from MCNP6 modeling of proton transport:
-\begin{equation}
-\langle E \rangle = \dfrac{{\displaystyle\int E \dfrac{d\phi}{dE} dE}}{{\displaystyle\int \dfrac{d\phi}{dE} dE}}
-\end{equation}
-Likewise, to represent the energy uncertainty for each stack position, the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution is chosen for each energy position reported.
-While most experimental uncertainties are reported at the 1$\sigma$ level, the $2.355\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy centroid value.
-
-The \enquote{variance minimization} techniques  described by  Graves \etal\  have been employed here to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
-This method is based on the assumption that the independent measurements of proton fluence from the five monitor reactions used in this work should all be consistent at each energy position.
-If the monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, disagreement in the  observed proton fluences is due to poorly characterized stopping power in simulations, or a systematic error in the
-% stack design, namely, the
-areal densities of the stack components \cite{Graves2016,Marus2015}. 
-This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
-
-% Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
-Due to the  
-% difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
-% This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to 
-significantly greater areal density of the thick 6061 aluminum degraders as compared to the other stack elements (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$),
-% As such
-the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
-This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
-The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position.
-This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
-This energy corresponds to a 6061 aluminum areal density of 2.52\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
-
-\begin{figure}
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.5\linewidth]{./figures/variation_curve-crop.pdf}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Result of the variance minimization performed by adjusting the degrader density in MCNP6 simulations of the target stack.
-A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.52\% greater than nominal.
-The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
- \label{fig:variation_curve}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/before_minimization_plot.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:before_minimization}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/after_minimization_plot.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:after_minimization}
-    \end{subfigure}%
-    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%.
-A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
-Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
-     \label{fig:variance_mins}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:Na22_activity_compare}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:Na24_activity_compare}
-    \end{subfigure}%
-    \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
-At low energies, experimentally observed apparent \ce{^{22,24}Na} activities in each Al foil packet are consistent with IAEA recommendations, but diverge at higher energies as the \ce{^{nat}Si}(p,x)\ce{^{22}Na} exit channels begin to open up.
-\ce{^{22,24}Na} activities consistent with TENDL-2015 estimates are observed in each Nb and Cu foil packet as well, confirming that contamination may be attributed to activation of silicone adhesives.}
-     \label{fig:Na_activity_compare}
-\end{figure}
-
-The impact of this variance minimization is  clearly  seen in   \autoref{fig:variance_mins}.
-As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
-In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
-% \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
-It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0\,MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
-% This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6\,MeV), though to a much smaller degree.
-In both cases, this disparity is caused by the fact that the Kapton tape used for sealing the foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
-\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\%\,\ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3\,MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6\,MeV).
-\ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
-In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
-The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.
-
-These compensating factors  contribute to \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} production being competitive with the \ce{^{nat}Al}(p,x)\ce{^{22}Na} production route.
-This is made made obvious when comparing the total measured activities of \ce{^{22}Na} and \ce{^{24}Na} in each Al foil packet (which combines both Al- and Si-based production routes), relative to the expected EoB activities for each reaction channel, presented in \autoref{fig:Na_activity_compare}.
-Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
-Several observations are immediately obvious.
-At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.
-At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90 MeV.
-For the \ce{^{24}Na} production, we see a similar behavior, though since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude, only a minor increase in apparent \ce{^{24}Na} activity is seen.
-The measured EoB \ce{^{22}Na} and \ce{^{24}Na} activities seen  in all Cu and Nb foil positions are also shown here, which are seen to be consistent with the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{22}Na} yields.
-The observed \ce{^{24}Na} activities also follow the shape of the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{24}Na} yields, albeit smaller in magnitude at the higher energy positions.
-
-While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
-The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to 
-% the number of assumptions involved in such a calculation.
-uncertainties in the areal density of the Si in the adhesive.
-% The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
-% These have been taken as
-However, if we assume a 10\% Si stoichiometric basis and an areal density of 4.79 mg/cm$^2$ (based on bulk density),
-% respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
-% In principle, it would be possible  to 
-we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
-The results of this  may be seen in \autoref{fig:na_subtraction}.
-Following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
-While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
-Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
-While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
-% In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
-% Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils.
-% The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively.
-% The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
-This serves as a pointed example of the importance of selecting monitor reaction products inaccessible through channels aside from the primary reaction (\ce{^{nat}Al}(p,x)\ce{^{22,24}Na}, in this case ), as noted previously.
-% However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.
-
-% Avoud using al and silicone
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:before_subtraction}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:after_subtraction}
-    \end{subfigure}%
-    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.
-Following subtraction of \ce{^{22,24}Na} activities observed in the silicone adhesive of Nb and Cu foils in the same energy \enquote{compartment}, the consistency of the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction improves  dramatically.
-By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
-     \label{fig:na_subtraction}
-\end{figure}
-
-Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the six irradiated Nb foils in \autoref{fig:Nb_ptallies}.
-As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
-In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail ratio increases as more  secondary protons are produced upstream.
-As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.
-
-An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
-Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
-% In the interest of surety of because they are consistent, t
-The uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
-Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
-These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport 
-% model, as well as 
-and an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
-Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.
-These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
-% This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
-% As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
-% The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/Nb_ptallies.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
-The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
-As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
- \label{fig:Nb_ptallies}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions.
-%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
-%   A clear loss of 
-  The fluence  drops by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.}
-%   This is due to a combination of beam utilization, as well as scattering.}
- \label{fig:fluence_plot}
-\end{figure}
-
-% \begin{equation}
-% R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
-% \end{equation}
-
-\subsection{Calculation of measured cross sections}\label{sec:calcs_sec}
-
-%  include 1st and 2nd order bateman stuff here
-
-Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
-While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
-% cross sections, 
-over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
-For both the cumulative and independent activities quantified, cross sections were calculated as:
-\begin{equation}
-\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
-\end{equation}
-where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
-The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
-The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).
-
-% \begin{align}
-% N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
-% &=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-% \end{align}
-
-% \subsection{Systematic uncertainties}
-% 
-% XXXXXX
-
-\section{Results}
-
-After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
-In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
-% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
-This blister   shows the location where the primary proton beam was incident upon the foil.
-The \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used to determine the uncertainty-weighted mean fluence at each energy position (seen in \autoref{fig:fluence_plot}).
-A fluence of 198.8$\pm$6.7\,nAh was calculated to be incident upon the target stack using the MCNP6 fluence model, and a  fluence of 196.9$\pm$11.3\,nAh using the linear fit model, both of which are consistent with the nominal fluence of 205.9\,nAh based on IPF upstream current monitors.
-As fluence loss in the target box's entrance window scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 8.9\% to  180.9$\pm$5.4\,nAh (and by 7.2\% to  182.7$\pm$13.5\,nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
-This loss of fluence is due to a combination of 
-% beam utilization for the various 
-(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
-
-Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40--90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
-In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb} were  extracted and are recorded in \autoref{tab:ibr_table}.
-Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--7\%), proton fluence ($\pm$4--6\%), and foil areal density ($\pm$0.1--0.6\%).
-% \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:cu_rp_table}
-\small
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
-\ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
-\ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
-\ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
-\ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
-\ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
-\ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
-\ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
-\ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
-\ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
-\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Nb}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:nb_rp_table}
-\small
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
-\ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
-\ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
-\ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
-\ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
-\ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
-\ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
-\ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
-\ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
-\ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
-\ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
-\ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Nb}(p,x) and \ce{^{nat}Cu}(p,x) reaction products observed in this work.}
-\label{tab:ibr_table}
-\small
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                               & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
-E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
-\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-These results have several notable features.
-The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90 MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
-Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
-Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
-
-% Furthermore, t
-This work presents the first measurements of several observables in 
-% these mass regions.
-% This work reports the first experimental measurement of
-this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region, 
-% It also represents  the first measurement of 
-the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
-The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
-Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).
-
-Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
-This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
-% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
-% , which makes activity quantification trivial.
-% In addition, 
-\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
-Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
-This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.
-
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
-% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
-
-\ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a positron emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
-\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} --- indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
-%ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
-ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
-The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
-Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40\,MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
-
-% Moving away from the potential PET emitters, 
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}, with the 
-% The 
-% emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the 
-PET branch 
-% makes  \ce{^{64}Cu}  
-suited for imaging of prostate and colorectal cancers  
-% the possibility for real-time dose monitoring and verification
-\cite{Lewis2003,Bandari2014,mp500671j}.
-% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
-Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
-More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
-% \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
-
-\ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET isotope, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011}.
-In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} generator and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
-Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
-Conventional production of \ce{^{86}Y} proceeds through low-energy (7--14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
-Alternatively, production at 33--43 MeV via \ce{^{88}Sr}(p,3n) has been proposed --- this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
-Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often impractical to separate out by radiochemical means.
-% \comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
-As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% radioisotopic purity.
-The  dominant yttrium radioisotope produced by  \ce{^{nat}Nb}(p,x) in the 40--90 MeV region is  \ce{^{87}Y} ($t_{1/2}=79.8\pm0.3$ h, $\epsilon^-$=100\% to \ce{^{87m}Sr} \cite{Johnson2015}).
-However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
-% Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51--61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
-
-\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived positron emitter useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
-Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9--14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
-Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 10--20\% radioisotopic purity in the 50--90 MeV region.
-
-\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging positron emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
-It is typically produced using 8--15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
-\ce{^{90}Nb} may be produced directly with an approximately 370 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
-However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
-
-Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is a diagnostic and emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators
-% for PET studies
-\cite{Kovacs1991}.
-It is commonly produced via \ce{^{82}Kr}(p,n) at 10--15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
-Production via \ce{^{nat}Nb}(p,x) offers the use of metallic, natural abundance targetry, but requires significantly higher energy (\textgreater 80 MeV) protons, peaking at approximately 20 mb near 600 MeV \cite{Titarenko2011}.
-It is clear that this production route offers no advantage over existing \ce{^{82}Kr}(p,n) routes for in-house production.
-
-% \comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
-
-% Finally, w
-We wish to urge caution in future stacked-target activation experiments by avoiding the use of silicone adhesive-based tapes for foil containment, especially when paired with the use of Al monitor foils.
-Acrylic-based tape options are commercially available, and are immune from (p,x) production of \ce{^{22,24}Na} activities, due to being of too low-Z for these reaction channels to be possible.
-Even with subtraction of \ce{^{22,24}Na} activities though irradiating a Kapton tape \enquote{blank} or similar, we observe the Al monitor channels to measure consistently higher proton fluence than via Cu monitor channels, by 5--8\%.
-If Al monitors are used in conjunction with silicone-based tapes, even with subtraction of excess \ce{^{22}Na} activities, a systematically enhanced fluence may be determined, leading to cross sections reported with inaccurately diminished magnitude.
-Furthermore, since data for monitor reactions are often self-referencing, the propagated impact of this systematic enhancement in fluence may have far-reaching consequences for both medical isotope production, as well as for  the evaluated nuclear data libraries, which use these proton activation experiments as input.
-
-% First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
-We intend to do the same for our next proton irradiation at LBL.
-% 
-% We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
-This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
-
-% \comment{Make sure to comment on comparison with EMPIRE / TALYS  / TENDL here, after Amanda finishes modeling work.}
-
-% In this work
-As mentioned before, cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
-This, in turn, offers the opportunity to 
-% use these data to gain insight into 
-gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
-The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
-The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
-The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
-% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
-% \cite{add_level_density_models_here}. 
-The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
-% \cite{add_level_density_models_here}.
-The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
-All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-% \def\arraystretch{1.5}
-\begin{table}
- \caption{Default settings for the reactions codes}
- \label{tab:defaults}
- \resizebox{\textwidth}{!}{%
-\begin{tabular}{ c c c c}
-
- \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
- EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
- TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
-
-\end{tabular}
-}
-\end{table}
-
-% The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
-% Only total channel residual 
-Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
-% that have only one reaction channel, and that are 
-and at least 1\% of the total reaction cross section.
-% are discussed in detail. 
-% Residual production
-Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
-% the compound portion of the cross section
-being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
-% Some residuals, such as 
-Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
-% Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
-% Very small channels, 
-We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
-% are excluded because the modeling of their cross sections is 
-because their behavior is extremely sensitive  to  more dominant  channels.
-The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
-
-The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70 MeV}, is well within the compound regime for the entire energy region of this experiment.
-The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
-The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50 MeV, and the data clearly show the full rise, peak, and fall of the compound cross section.
-In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011\cite{Titarenko2011}.
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/86Y.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
- \label{fig:86Y}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:90Mo}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:90Nb}
-\end{figure}
-
-In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
-For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
-For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
-
-The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
-For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
-The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
-\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
-
-The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
-TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
-EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
-
-% \section{Discussion}
-
-% \comment{Feel free to expand / suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
-
-% XXXXXX
-
-% \comment{Placeholder to reserve space for pre-equilibrium / spin discussion.}
-
- \section{Conclusions}
-
-We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
-Nearly all cross sections have been reported with higher precision than previous measurements.
-We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
-
- \section{Acknowledgements}
-
-%  Stephen Graves - consulting for methodology, guidance.
-
- The authors would like to particularly acknowledge the assistance and support of  Michael Gallegos and Don Dry in the LANL C-NR Countroom, David Reass and Mike Connors at LANSCE-IPF, and the LANSCE Accelerator Operations staff.
-
-We gratefully acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics.
-This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
-This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy
-Additional support has been provided by the U.S. Nuclear Regulatory Commission.
-
-This research used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
-
-%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-% Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.
-
-%  \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers, as well as anyone else that you feel should be acknowledged here.}
-
-%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% \pagebreak
-% 
-% \onecolumn
-% 
-\appendix
-
-\section{Decay data} \label{data}
-% 
-% % \begin{longtable}{|c|c|c|c|c|} 
-% % \caption{My caption}
-% % \label{tab:dummy}
-% % % \begin{tabular}{|c|c|c|c|c|}
-% %    \hline
-% %  
-% % \end{longtable}
-% Table of decay data  for observed gamma-rays. 
-The   lifetimes and gamma-ray branching ratios  listed in these tables were used for all calculations of measured cross sections reported in this work, and have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain  \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
-
-% \comment{I had to remove about 30 of the lines I used from this table (removing the weakest lines in nuclides with even more lines than shown here, but never removing lines in nuclides with only 2 or less), as even splitting the data into 2 tables created tables too large to fit on a single page.
-My purpose here was 1) to show that I used multiple lines to quantify each nuclide (increasing confidence in results), and 2) to list all the used \ce{^{90}Mo} lines, since they form the basis of it as a monitor.
-Is this good as is, or should it be pared down even more?}
-
-% Preview source code for paragraph 0
-
-\begin{table}[ht]
-\centering
-\caption{Decay data for gamma-rays observed in \ce{^{nat}Al}(p,x) and \ce{^{nat}Cu}(p,x).}
-\label{tab:nudat_table_monitors}
-\begin{tabular}{@{}llll@{}}
-\toprule
-% \begin{tabular}{|c|c|c|c|}
-% \hline 
-Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
-\midrule
-\ce{^{22}Na} & 2.6018(22) y & 1274.537 & 99.940(14)\\
-
-\ce{^{24}Na} & 14.997(12) h & 1368.626 & 99.9936(15)\\
-
-\ce{^{51}Cr} & 27.704(3) d & 320.0824 & 9.910(10)\\
-
-\ce{^{52m}Mn} & 21.1(2) m & 1434.0600 & 98.2(5)\\
-
-\ce{^{52}Mn} & 5.591(3) d & 744.233 & 90.0(12)\\
-
- & 5.591(3) d & 935.544 & 94.5(13)\\
-
- & 5.591(3) d & 1246.278 & 4.21(7)\\
-
- & 5.591(3) d & 1434.092 & 100.0(14)\\
-
-\ce{^{54}Mn} & 312.20(20) & 834.848 & 99.9760(10)\\
-
-\ce{^{55}Co} & 17.53(3) h & 477.2 & 20.2(17)\\
-
- & 17.53(3) h & 931.1 & 75.0(35)\\
-
- & 17.53(3) h & 1316.6 & 7.1(3)\\
-
- & 17.53(3) h & 1408.5 & 16.9(8)\\
-
-\ce{^{56}Ni} & 6.075(10) d & 158.38 & 98.8(10)\\
-
- & 6.075(10) d & 269.50 & 36.5(8)\\
-
- & 6.075(10) d & 480.44 & 36.5(8)\\
-
- & 6.075(10) d & 749.95 & 49.5(12)\\
-
- & 6.075(10) d & 811.85 & 86.0(9)\\
-
- & 6.075(10) d & 1561.80 & 14.0(6)\\
-
-\ce{^{56}Co} & 77.236(26) d & 846.770 & 99.9399(2)\\
-
-%  & 77.236(26) d & 977.372 & 1.421(6)\\
-
- & 77.236(26) d & 1037.843 & 14.05(4)\\
-
- & 77.236(26) d & 1238.288 & 66.46(12)\\
-
- & 77.236(26) d & 1360.212 & 4.283(12)\\
-
- & 77.236(26) d & 1771.357 & 15.41(6)\\
-
-\ce{^{57}Ni} & 35.60(6) h & 127.164 & 16.7(5)\\
-
- & 35.60(6) h & 1377.63 & 81.7(24)\\
-
- & 35.60(6) h & 1757.55 & 5.75(20)\\
-
- & 35.60(6) h & 1919.52 & 12.3(4)\\
-
-\ce{^{57}Co} & 271.74(6) d & 122.06065 & 85.60(17)\\
-
- & 271.74(6) d & 136.47356 & 10.68(8)\\
-
-\ce{^{58}Co} & 70.86(6) d & 810.7593 & 99.450(10)\\
-
- & 70.86(6) d & 863.951 & 0.686(10)\\
-
-%  & 70.86(6) d & 1674.725 & 0.517(10)\\
-
-\ce{^{59}Fe} & 44.495(9) d & 1099.245 & 56.5(18)\\
-
- & 44.495(9) d & 1291.590 & 43.2(14)\\
-
-\ce{^{60}Co} & 5.2714(5) y & 1173.228 & 99.85(3)\\
-
- & 5.2714(5) y & 1332.492 & 99.9826(6)\\
-
-\ce{^{61}Cu} & 3.339(8) h & 282.956 & 12.2(2.2)\\
-
- & 3.339(8) h & 373.050 & 2.1(4)\\
-
-%  & 3.339(8) h & 588.605 & 1.17(21)\\
-
- & 3.339(8) h & 656.008 & 10.8(20)\\
-
- & 3.339(8) h & 1185.234 & 3.7(7)\\
-
-\ce{^{62}Zn} & 9.193(15) h & 243.36 & 2.52(23)\\
-
- & 9.193(15) h & 246.95 & 1.90(18)\\
-
- & 9.193(15) h & 260.43 & 1.35(13)\\
-
-%  & 9.193(15) h & 304.88 & 0.29(3)\\
-
-%  & 9.193(15) h & 349.60 & 0.45(4)\\
-
- & 9.193(15) h & 394.03 & 2.24(17)\\
-
- & 9.193(15) h & 548.35 & 15.3(14)\\
-
- & 9.193(15) h & 596.56 & 26.0(20)\\
-
-%  & 9.193(15) h & 637.41 & 0.25(3)\\
-
-\ce{^{64}Cu} & 12.701(2) h & 1345.77 & 0.475(11)\\
-
-\ce{^{65}Zn} & 243.93(9) d & 1115.539 & 50.04(10)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\centering
-\caption{Decay data for gamma-rays observed in \ce{^{nat}Nb}(p,x).}
-\label{tab:nudat_table_nb}
-\begin{tabular}{@{}llll@{}}
-\toprule
-% \begin{tabular}{|c|c|c|c|}
-% \hline 
-Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
-\midrule
-\ce{^{82m}Rb} & 6.472(6) h & 554.35 & 62.4(9)\\
-
- & 6.472(6) h & 619.11 & 37.98(9)\\
-
-%  & 6.472(6) h & 698.37 & 26.3(7)\\
-
- & 6.472(6) h & 776.52 & 84.39(21)\\
-
- & 6.472(6) h & 1044.08 & 32.07(8)\\
-
-%  & 6.472(6) h & 1317.43 & 23.7(6)\\
-
-\ce{^{83}Sr} & 32.41(3) h & 418.37 & 4.2(3)\\
-
- & 32.41(3) h & 762.65 & 26.7(22)\\
-
-\ce{^{85m}Y} & 4.86(13) h & 231.7 & 22.8(22)\\
-
-\ce{^{85}Y} & 2.68(5) h & 231.65 & 84(9)\\
-
- & 2.68(5) h & 913.89 & 9.0(9)\\
-
-\ce{^{86}Zr} & 16.5(1) h & 242.8 & 95.84(2)\\
-
- & 16.5(1) h & 612.0 & 5.8(3)\\
-
-% \ce{^{86}Y} & 14.74(2) h & 187.87 & 1.26(4)\\
-\ce{^{86}Y}  & 14.74(2) h & 443.13 & 16.9(5)\\
-
-%  & 14.74(2) h & 190.80 & 1.01(3)\\
-
-%  & 14.74(2) h & 307.00 & 3.47(8)\\
-
-%  & 14.74(2) h & 443.13 & 16.9(5)\\
-
-%  & 14.74(2) h & 580.57 & 4.78(14)\\
-
-%  & 14.74(2) h & 608.29 & 2.01(15)\\
-
- & 14.74(2) h & 627.72 & 32.6(1)\\
-
-%  & 14.74(2) h & 703.33 & 15.4(4)\\
-
-%  & 14.74(2) h & 709.90 & 2.62(8)\\
-
-%  & 14.74(2) h & 767.63 & 2.4(3)\\
-
-%  & 14.74(2) h & 835.67 & 4.4(6)\\
-
-%  & 14.74(2) h & 1024.04 & 3.79(17)\\
-
- & 14.74(2) h & 1076.63 & 82.5(4)\\
-
- & 14.74(2) h & 1153.05 & 30.5(9)\\
-
-%  & 14.74(2) h & 1163.03 & 1.18(4)\\
-%  
-%  & 14.74(2) h & 1253.11 & 1.53(5)\\
-
-%  & 14.74(2) h & 1349.15 & 2.95(9)\\
-
- & 14.74(2) h & 1854.38 & 17.2(5)\\
-
- & 14.74(2) h & 1920.72 & 20.8(7)\\
-
-\ce{^{87}Zr} & 1.68(1) h & 380.79 & 62.79(10)\\
-
- & 1.68(1) h & 1227.0 & 2.80(4)\\
-
-\ce{^{87m}Y} & 13.37(1) h & 380.79 & 78.05(8)\\
-
-\ce{^{87}Y} & 79.8(3) h & 388.5276 & 82.2(7)\\
-
- & 79.8(3) h & 484.805 & 89.8(9)\\
-
-\ce{^{88}Zr} & 83.4(3) d & 392.87 & 97.29(14)\\
-
-\ce{^{88}Y} & 106.627(21) d & 898.042 & 93.7(3)\\
-
- & 106.627(21) d & 1836.063 & 99.2(3)\\
-
-\ce{^{89m}Nb} & 66(2) m & 588.0 & 95.57(13)\\
-
-\ce{^{89}Nb} & 2.03(7) h & 1511.4 & 1.9(4)\\
-
- & 2.03(7) h & 1627.2 & 3.5(7)\\
-
- & 2.03(7) h & 1833.4 & 3.3(7)\\
-
-\ce{^{89}Zr} & 78.41(12) h & 909.15 & 99.04(3)\\
-
- & 78.41(12) h & 1713.0 & 0.745(13)\\
-
-%  & 78.41(12) h & 1744.5 & 0.123(4)\\
-
-\ce{^{90}Mo} & 5.56(9) h & 122.370 & 64(3)\\
-
- & 5.56(9) h & 162.93 & 6.0(6)\\
-
- & 5.56(9) h & 203.13 & 6.4(6)\\
-
- & 5.56(9) h & 257.34 & 78(4)\\
-
- & 5.56(9) h & 323.20 & 6.3(6)\\
-
- & 5.56(9) h & 472.2 & 1.42(16)\\
-
- & 5.56(9) h & 941.5 & 5.5(7)\\
-
-\ce{^{90}Nb} & 14.6(5) h & 132.716 & 4.13(4)\\
-
- & 14.6(5) h & 141.178 & 66.8(7)\\
-
-%  & 14.6(5) h & 890.64 & 1.80(4)\\
-
- & 14.6(5) h & 1611.76 & 2.38(7)\\
-
-%  & 14.6(5) h & 1913.194 & 1.280(17)\\
-
-\ce{^{91m}Nb} & 60.86(22) d & 104.62 & 0.574(1)\\
-
- & 60.86(22) d & 1204.67 & 2.0(3)\\
-
-\ce{^{92m}Nb} & 10.15(2) d & 912.6 & 1.78(10)\\
-
- & 10.15(2) d & 934.44 & 99.15(4)\\
-
-\ce{^{93m}Mo} & 6.85(7) d & 263.049 & 57.4(11)\\
-
- & 6.85(7) d & 684.693 & 99.9(8)\\
-
- & 6.85(7) d & 1477.138 & 99.1(11)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-% 
-% 
-\section{Measured excitation functions} \label{fit_figures}
-
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH-3.5.1, EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
-
-% \comment{Add in CoH model output from Toshihiko to all plots}
-
-% \comment{Fix a few figure labels (c/i) based on Jon;s email}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/51Cr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:51Cr}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/52Mn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:52Mn}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/52gMn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:52gMn}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/52mMn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:52mMn}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/54Mn.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:54Mn}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/55Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:55Co}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p1}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/56Ni.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:56Ni}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/57Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:57Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/57Ni.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:57Ni}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58Co.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:58Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58gCo.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:58gCo}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/58mCo.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:58mCo}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p2}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/59Fe.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:59Fe}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/60Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:60Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/61Cu.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:61Cu}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/64Cu.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:64Cu}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/82mRb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:82mRb}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/83Sr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:83Sr}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p3}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/85gY.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:85gY}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85mY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85mY}
-    \end{subfigure}
-%      \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/86Y.pdf}{50}
-% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-%                  \refstepcounter{subfigure}\label{fig:86Y}
-%     \end{subfigure}
-%     \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/86Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:86Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87Y}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87gY}
-    \end{subfigure}
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p4}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-%      \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
-% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-%                  \refstepcounter{subfigure}\label{fig:87gY}
-%     \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87mY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87mY}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/87Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/88Y.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Y}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/88Zr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Zr}
-    \end{subfigure}%
-    \\
-         \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89Nb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:89Nb}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:89gNb}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p8}
-\end{figure*}
-
-\begin{figure*}
-    \centering    
-%          \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-%          \refstepcounter{subfigure}\label{fig:89gNb}
-%     \end{subfigure}%
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/89Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:89Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:91mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:92mNb}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:93mMo}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p7}
-\end{figure*}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-%          \refstepcounter{subfigure}\label{fig:93mMo}
-%     \end{subfigure}%
-% %      \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% % %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-% %         \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
-% % %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-% %          \refstepcounter{subfigure}\label{fig:91mNb}
-% %     \end{subfigure}%
-% %     \\
-% %     \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\textwidth]{./figures/target2.png}
-% %         \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
-% % %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-% %                  \refstepcounter{subfigure}\label{fig:92mNb}
-% %     \end{subfigure}
-% %      \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-% % %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-% %         \refstepcounter{subfigure} \label{fig:93mMo}
-% %     \end{subfigure}%
-% %     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-%      \label{fig:xs_curves_p5}
-% \end{figure*}
-
-% 
-% 
-\section{Measured isomer-to-ground state branching ratios } \label{ibr_figures}
-
-Plots of the isomer-to-ground state ratios measured in this work are presented here, in comparison with literature data and reaction modeling codes \cite{MICHEL1997153,Ditroi2008,Titarenko2011,Graves2016}.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/52Mn_IBR.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:52Mn_IBR}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58Co_IBR.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:58Co_IBR}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85Y_IBR.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y_IBR}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/87Y_IBR.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Y_IBR}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89Nb_IBR.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89Nb_IBR}
-    \end{subfigure}
-     \label{fig:ibr_curves}
-\end{figure*}
-
-% \twocolumn
-
-%% References with BibTeX database:
-
-% \bibliographystyle{elsarticle-num}
-% \bibliographystyle{elsarticle-harv}
-% \bibliographystyle{elsarticle-num-names}
-% \bibliography{<your-bib-database>}
-% \addcontentsline{toc}{chapter}{Bibliography}
-\bibliographystyle{elsarticle-num}
-% \bibliographystyle{apsrev4-1}
-% \bibliographystyle{ieeetr}
-\bibliography{../../library}
-% \thispagestyle{fancyTOC}
-
-%% Authors are advised to use a BibTeX database file for their reference list.
-%% The provided style file elsarticle-num.bst formats references in the required Procedia style
-
-%% For references without a BibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
-
-\end{document}
-
-%%
-%% End of file `ecrc-template.tex'.

### 2018-04-05 nb_px_paper/nb_body_text.tex
Broke Nb(p,x) paper into container w/ separate body text, appendices, and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

--- 2018-04-03 nb_px_paper/nb_px_paper.tex
@@
-% % ****** Start of file apssamp.tex ******
-% %
-% %   This file is part of the APS files in the REVTeX 4.1 distribution.
-% %   Version 4.1r of REVTeX, August 2010
-% %
-% %   Copyright (c) 2009, 2010 The American Physical Society.
-% %
-% %   See the REVTeX 4 README file for restrictions and more information.
-% %
-% % TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% % as well as the rest of the prerequisites for REVTeX 4.1
-% %
-% % See the REVTeX 4 README file
-% % It also requires running BibTeX. The commands are as follows:
-% %
-% %  1)  latex apssamp.tex
-% %  2)  bibtex apssamp
-% %  3)  latex apssamp.tex
-% %  4)  latex apssamp.tex
-% %
-% \documentclass[%
-%  reprint,
-% superscriptaddress,
-% onecolumn,
-% linenumbers,
-% notitlepage,
-% %groupedaddress,
-% %unsortedaddress,
-% %runinaddress,
-% %frontmatterverbose, 
-% %preprint,
-% %showpacs,preprintnumbers,
-% %nofootinbib,
-% %nobibnotes,
-% %bibnotes,
-%  amsmath,amssymb,
-%  aps,
-% prc,
-% %prb,
-% %rmp,
-% %prstab,
-% %prstper,
-% %floatfix,
-% ]{revtex4-1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Important note on usage                  %%
-%% -----------------------                  %%
-%% This file must be compiled with PDFLaTeX %%
-%% Using standard LaTeX will not work!      %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
-% \documentclass[5p]{elsarticle}
-% Good for final formatting  - two column
-% 
-% \documentclass[3p,times]{elsarticle}
-% Final formatting
-\documentclass[3p]{elsarticle}
-% Good for proofing - single column
-%
-
-\usepackage[american]{babel}
-\usepackage{amsmath}
-\usepackage[version=3]{mhchem} 
-% \usepackage{fixltx2e}
-% \usepackage{refcount}
-% \usepackage{siunitx}
-% \usepackage{lastpage}
-% \usepackage{textcomp}
-\usepackage{mathtools}
-
-\usepackage{xfrac}
-\usepackage{lmodern}
-\usepackage[hidelinks]{hyperref}
-% \usepackage{cool}
-% \usepackage{cancel}
-\usepackage{microtype}
-\usepackage{listings}
-\usepackage{mcode}
-\usepackage [autostyle, english = american]{csquotes}
-% \usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{booktabs,siunitx}
-\usepackage{gensymb}
-\usepackage[normalem]{ulem}
-
-% \usepackage{mathtools, cuted}
-
-% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\usepackage{color}
-
-\usepackage[colorinlistoftodos]{todonotes}
-
-\usepackage[section]{placeins}
-\usepackage{multirow}
-
-\usepackage{lineno}
-
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-
-\lstset{basicstyle=\small\ttfamily,columns=fullflexible}
-
-% \usepackage{verbatim}
-
-% \usepackage{gensymb}
-% \usepackage{enumerate}
-% \usepackage{float}
-% \usepackage{bm}
-% \usepackage{csquotes}
-% \usepackage{mathtools}
-% \usepackage[sort&compress]{natbib}
-% \usepackage{biblatex}
-
-%% The `ecrc' package must be called to make the CRC functionality available
-\usepackage{ecrc}
-
-%% The ecrc package defines commands needed for running heads and logos.
-%% For running heads, you can set the journal name, the volume, the starting page and the authors
-
-%% set the volume if you know. Otherwise `00'
-\volume{00}
-
-%% set the starting page if not 1
-\firstpage{1}
-
-%% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research B}
-
-%% Give the author list to appear in the running head
-%% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{A.S. Voyles et al.}
-
-%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
-%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
-%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
-%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo
-
-%% Give the abbreviation of the Journal.
-\jid{nimb}
-% \jid{yspmi}
-
-%% Give a short journal name for the dummy logo (if needed)
-\jnltitlelogo{Nucl Instrum Meth B}
-
-%% Hereafter the template follows `elsarticle'.
-%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.
-
-%% Elsevier CRC generally uses a numbered reference style
-%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
-%% If using BibTeX, use the style file elsarticle-num.bst
-
-%% End of ecrc-specific commands
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%
-%% \biboptions{comma,round}
-
-\biboptions{sort&compress}
-
-% if you have landscape tables
-\usepackage[figuresright]{rotating}
-
-% put your own definitions here:
-%   \newcommand{\cZ}{\cal{Z}}
-%   \newtheorem{def}{Definition}[section]
-%   ...
-
-% add words to TeX's hyphenation exception list
-%\hyphenation{author another created financial paper re-commend-ed Post-Script}
-
-% declarations for front matter
-
-\usepackage{fancyvrb}
-\usepackage{color}
-
-\definecolor{mygreen}{rgb}{0,0.6,0}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mymauve}{rgb}{0.58,0,0.82}
-
-\lstset{ %
-  backgroundcolor=\color{white},   % choose the background color
-  basicstyle=\footnotesize,        % size of fonts used for the code
-  breaklines=true,                 % automatic line breaking only at whitespace
-  captionpos=b,                    % sets the caption-position to bottom
-  commentstyle=\color{mygreen},    % comment style
-  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-  keywordstyle=\color{blue},       % keyword style
-  stringstyle=\color{mymauve},     % string literal style
-}
-
-% Sin and Cos with auto-parentheses 
-\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
-\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
-\newcommand{\expp}[1]{\exp{\left( #1\right)}}
-\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
-\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
-\newcommand{\pp}[1]{\left( #1\right)}
-\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
-\newcommand{\angstrom}{\mbox{\normalfont\AA}}
-\newcommand{\norm}[1]{\lVert #1 \rVert}
-
-\newcommand{\textred}[1]{\textcolor{red}{ #1}}
-\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}
-
-\newcommand{\cmmnt}[1]{}
-
-\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
-
-\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}
-
-\newcommand{\etal}{\emph{et\,al.}}
-
-% Tweak sim for better inline text tilde
-\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
-% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}
-
-\sisetup{separate-uncertainty=true,table-space-text-post = *}
-
-\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
-
-% \newcounter{subfigure}[figure]
-
-\newcommand{\subfigimg}[4][,]{%
-  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
-  \leavevmode\rlap{\usebox1}% Print image
-  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
-  \phantom{\usebox1}% Insert appropriate spcing
-}
-% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}
-
-\makeatletter
-% Make common definition of mean
-\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}
-
-\makeatother
-
-\begin{document}
-
-\begin{frontmatter}
-
-%\preprint{APS/123-QED}
-
-% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
-% % \thanks{A footnote to the article title}%
-% 
-% \author{Andrew S. Voyles}
-%  \email{andrew.voyles@berkeley.edu}
-% \affiliation{%
-%  Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% }% 
-% \author{Lee A. Bernstein}
-% \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
-% \affiliation{%
-%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% }%
-% \author{Eva R. Birnbaum}
-% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-% \author{Jonathan W. Engle}
-%  \email{jwengle@wisc.edu}
-% \affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
-% \author{Stephen A. Graves}
-% \affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
-% \author{Toshihiko ??? Kawano}
-% \affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-% %  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
-% \author{Amanda M. Lewis}%
-% % \author{Eric F. Matthews}%
-% %  \email{Second.Author@institution.edu}
-% \affiliation{%
-%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% }%
-% \author{Francois M. Nortier}
-% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}
-
-% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-\author[ucb]{Andrew S. Voyles \corref{cor1}}
-\ead{andrew.voyles@berkeley.edu}
-
-% \author[lbl]{M.S. Basunia}
-% 
-% \author[ucb]{J.C. Batchelder}
-%
-
-\author[lbl,ucb]{Lee A. Bernstein}
-
-\author[lanl]{Eva R. Birnbaum}
-
-\author[uwm]{Jonathan W. Engle}
-\ead{jwengle@wisc.edu}
-
-\author[iowa]{Stephen A. Graves}
-
-\author[tlanl]{Toshihiko  Kawano}
-
-\author[ucb]{Amanda M. Lewis}
-
-\author[lanl]{Francois M. Nortier}
-
-\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
-\address[lbl]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
-% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
-\address[lanl]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-\address[iowa]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
-\address[tlanl]{Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
-
-% % \collaboration{MUSO Collaboration}%\noaffiliation
-% % 
-% % \author{Charlie Author}
-% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
-% % \affiliation{
-% %  Second institution and/or address\\
-% %  This line break forced% with \\
-% % }%
-% % \affiliation{
-% %  Third institution, the second for Charlie Author
-% % }%
-% % \author{Delta Author}
-% % \affiliation{%
-% %  Authors' institution and/or address\\
-% %  This line break forced with \textbackslash\textbackslash
-% % }%
-% % 
-% % \collaboration{CLEO Collaboration}%\noaffiliation
-% 
-% \date{\today}% It is always \today, today,
-%              %  but any date may be explicitly specified
-% 
-% %% Title, authors and addresses
-% 
-% %% use the tnoteref command within \title for footnotes;
-% %% use the tnotetext command for the associated footnote;
-% %% use the fnref command within \author or \address for footnotes;
-% %% use the fntext command for the associated footnote;
-% %% use the corref command within \author for corresponding author footnotes;
-% %% use the cortext command for the associated footnote;
-% %% use the ead command for the email address,
-% %% and the form \ead[url] for the home page:
-% %%
-\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}
-
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-% \dochead{Short}
-%% Use \dochead if there is an article header, e.g. \dochead{Short communication}
-
-% 
-% % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
-% \author[ucb]{Andrew S. Voyles \corref{cor1}}
-% \ead{andrew.voyles@berkeley.edu}
-% 
-% % \author[lbl]{M.S. Basunia}
-% % 
-% % \author[ucb]{J.C. Batchelder}
-% 
-% 
-% \author[ucb,lbl]{Lee A. Bernstein}
-% 
-% 
-% \author[lanl]{Eva R. Birnbaum}
-% 
-% \author[uwm]{Jonathan W. Engle}
-% 
-% \author[iowa]{Stephen A. Graves}
-% 
-% \author[ucb]{Amanda M. Lewis}
-% 
-% 
-% \author[lanl]{Francois M. Nortier}
-
-% \author[ucb]{M.A. Unzueta}
-% 
-% \author[ucb]{K.A. van Bibber}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-% \cortext[cor1]{Corresponding author}
-% \cortext[cor2]{Principal corresponding author}
-% \fntext[fn1]{This is the specimen author footnote.}
-% \fntext[fn2]{Another author footnote, but a little more longer.}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
-% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
-% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}
-
-% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
-% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
-% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
-% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
-% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
-% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}
-
-\begin{abstract}
-
-% Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
-% However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.
-% To address this need, a
-A stack  of thin Nb 
-% , Cu, and Al monitor 
-foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
-% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
-% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
-A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
-% The measurements are 
-These are useful in medical and basic science radionuclide productions at intermediate energies. 
-% Cross sections were measured using the well-characterized 
-The
-% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
-\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn}  reactions were used to
-determine proton fluence, and all activities were quantified using HPGe spectrometry.
-Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
-The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
-This work also reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
-% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
-\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-% \textred{
-% Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
-% }
-% \textred{
-% To avoid inadvertently reporting enhanced proton fluence due to
-The effects of  \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, arising from  silicone adhesive in the Kapton tape used to encapsulate the aluminum monitor foils, is also discussed as a cautionary note to future stacked-target cross section measurements.
-% strongly discouraged.
-% }
-% Comparisons against the 
-\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the differences between codes for the
-% impact of pre-equilibrium particle emission  for the 
-% 40--90 MeV 
-\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-
-% \begin{description}
-% \item[Usage]
-% Secondary publications and information retrieval purposes.
-% \item[PACS numbers]
-% May be entered using the \verb+\pacs{#1}+ command.
-% \item[Structure]
-% You may use the \texttt{description} environment to structure your abstract;
-% use the optional argument of the \verb+\item+ command to give the category of each item. 
-% \end{description}
-\end{abstract}
-
-% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-
-% \begin{abstract}
-
-% \end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-Nb+p \sep Cu+p \sep Niobium 
-% \sep Copper\sep Aluminum 
-\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
-% Proton activation \sep 
-% Proton transport \sep 
-Stacked target activation \sep Monitor reactions \sep 
-% Monitor foils 
-Medical isotope production \sep Isomer branching ratios \sep  
-% Nuclear spin distributions  \sep 
-MCNP \sep  LANL
-% 
-% %% MSC codes here, in the form: \MSC code \sep code
-% %% or \MSC[2008] code \sep code (2000 is the default)
-% 
-\end{keyword}
-
-\end{frontmatter}
-
-% \maketitle
-
-%%
-%%  To-do list for comments
-%%
-% \listoftodos
-
-%%
-%% Start line numbering here if you want
-%%
-\linenumbers
-
 %% main text 
@@
 % a number of 
-including intense and distinct gamma-rays, 
+including intense, distinct gamma-rays, 
 % with high intensities,  
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
+% \begin{figure*}
+%     \centering
+%     \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \subfigimg[width=0.5\textwidth]{a)}{./figures/336keV_curve_new.pdf}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+% %          \refstepcounter{subfloat}
+%          \label{fig:decay_curve_336}
+% %          
+%          \subfigimg[width=0.5\textwidth]{b)}{./figures/391keV_curve_new.pdf}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+% %          \refstepcounter{subfloat}
+%          \label{fig:decay_curve_391}
+%     }%
+
+\begin{figure}
+    \centering
+    \subfloat{
         \centering
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/before_minimization_plot.pdf}{50}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:before_minimization}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
+         %         \refstepcounter{subfigure}
+         \label{fig:before_minimization}
+   \hspace{-5pt}}%
+     \subfloat{
         \centering
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/after_minimization_plot.pdf}{50}
+        \subfigimg[width=0.5\textwidth]{b)}{./figures/after_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:after_minimization}
-    \end{subfigure}%
+         %         \refstepcounter{subfigure}
+         \label{fig:after_minimization}
+   \hspace{-5pt}}%
     \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%.
@@
     \centering
-    \begin{subfigure}[t]{0.50\textwidth}
+    \subfloat{
         \centering
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
+        \hspace{-5pt}\subfigimg[width=0.5\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:Na22_activity_compare}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
+         %         \refstepcounter{subfigure}
+%          \label{fig:Na22_activity_compare}
+   \hspace{-5pt}}%
+     \subfloat{
         \centering
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
+        \subfigimg[width=0.5\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:Na24_activity_compare}
-    \end{subfigure}%
+         %         \refstepcounter{subfigure}
+         \label{fig:Na24_activity_compare}
+   \hspace{-5pt}}%
     \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
@@
     \centering
-    \begin{subfigure}[t]{0.50\textwidth}
+    \subfloat{
         \centering
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:before_subtraction}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
+         %         \refstepcounter{subfigure}
+         \label{fig:before_subtraction}
+   \hspace{-5pt}}%
+     \subfloat{
         \centering
@@
 %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
+        \subfigimg[width=0.5\textwidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:after_subtraction}
-    \end{subfigure}%
+         %         \refstepcounter{subfigure}
+         \label{fig:after_subtraction}
+   \hspace{-5pt}}%
     \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.
@@
 Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
-
- \section{Acknowledgements}
-
-%  Stephen Graves - consulting for methodology, guidance.
-
- The authors would like to particularly acknowledge the assistance and support of  Michael Gallegos and Don Dry in the LANL C-NR Countroom, David Reass and Mike Connors at LANSCE-IPF, and the LANSCE Accelerator Operations staff.
-
-We gratefully acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics.
-This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
-This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy
-Additional support has been provided by the U.S. Nuclear Regulatory Commission.
-
-This research used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
-
-%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-% Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.
-
-%  \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers, as well as anyone else that you feel should be acknowledged here.}
-
-%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S.
-Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
-% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.
-
-% \pagebreak
-% 
-% \onecolumn
-% 
-\appendix
-
-\section{Decay data} \label{data}
-% 
-% % \begin{longtable}{|c|c|c|c|c|} 
-% % \caption{My caption}
-% % \label{tab:dummy}
-% % % \begin{tabular}{|c|c|c|c|c|}
-% %    \hline
-% %  
-% % \end{longtable}
-% Table of decay data  for observed gamma-rays. 
-The   lifetimes and gamma-ray branching ratios  listed in these tables were used for all calculations of measured cross sections reported in this work, and have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain  \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
-
-% \comment{I had to remove about 30 of the lines I used from this table (removing the weakest lines in nuclides with even more lines than shown here, but never removing lines in nuclides with only 2 or less), as even splitting the data into 2 tables created tables too large to fit on a single page.
-My purpose here was 1) to show that I used multiple lines to quantify each nuclide (increasing confidence in results), and 2) to list all the used \ce{^{90}Mo} lines, since they form the basis of it as a monitor.
-Is this good as is, or should it be pared down even more?}
-
-% Preview source code for paragraph 0
-
-\begin{table}[ht]
-\centering
-\caption{Decay data for gamma-rays observed in \ce{^{nat}Al}(p,x) and \ce{^{nat}Cu}(p,x).}
-\label{tab:nudat_table_monitors}
-\begin{tabular}{@{}llll@{}}
-\toprule
-% \begin{tabular}{|c|c|c|c|}
-% \hline 
-Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
-\midrule
-\ce{^{22}Na} & 2.6018(22) y & 1274.537 & 99.940(14)\\
-
-\ce{^{24}Na} & 14.997(12) h & 1368.626 & 99.9936(15)\\
-
-\ce{^{51}Cr} & 27.704(3) d & 320.0824 & 9.910(10)\\
-
-\ce{^{52m}Mn} & 21.1(2) m & 1434.0600 & 98.2(5)\\
-
-\ce{^{52}Mn} & 5.591(3) d & 744.233 & 90.0(12)\\
-
- & 5.591(3) d & 935.544 & 94.5(13)\\
-
- & 5.591(3) d & 1246.278 & 4.21(7)\\
-
- & 5.591(3) d & 1434.092 & 100.0(14)\\
-
-\ce{^{54}Mn} & 312.20(20) & 834.848 & 99.9760(10)\\
-
-\ce{^{55}Co} & 17.53(3) h & 477.2 & 20.2(17)\\
-
- & 17.53(3) h & 931.1 & 75.0(35)\\
-
- & 17.53(3) h & 1316.6 & 7.1(3)\\
-
- & 17.53(3) h & 1408.5 & 16.9(8)\\
-
-\ce{^{56}Ni} & 6.075(10) d & 158.38 & 98.8(10)\\
-
- & 6.075(10) d & 269.50 & 36.5(8)\\
-
- & 6.075(10) d & 480.44 & 36.5(8)\\
-
- & 6.075(10) d & 749.95 & 49.5(12)\\
-
- & 6.075(10) d & 811.85 & 86.0(9)\\
-
- & 6.075(10) d & 1561.80 & 14.0(6)\\
-
-\ce{^{56}Co} & 77.236(26) d & 846.770 & 99.9399(2)\\
-
-%  & 77.236(26) d & 977.372 & 1.421(6)\\
-
- & 77.236(26) d & 1037.843 & 14.05(4)\\
-
- & 77.236(26) d & 1238.288 & 66.46(12)\\
-
- & 77.236(26) d & 1360.212 & 4.283(12)\\
-
- & 77.236(26) d & 1771.357 & 15.41(6)\\
-
-\ce{^{57}Ni} & 35.60(6) h & 127.164 & 16.7(5)\\
-
- & 35.60(6) h & 1377.63 & 81.7(24)\\
-
- & 35.60(6) h & 1757.55 & 5.75(20)\\
-
- & 35.60(6) h & 1919.52 & 12.3(4)\\
-
-\ce{^{57}Co} & 271.74(6) d & 122.06065 & 85.60(17)\\
-
- & 271.74(6) d & 136.47356 & 10.68(8)\\
-
-\ce{^{58}Co} & 70.86(6) d & 810.7593 & 99.450(10)\\
-
- & 70.86(6) d & 863.951 & 0.686(10)\\
-
-%  & 70.86(6) d & 1674.725 & 0.517(10)\\
-
-\ce{^{59}Fe} & 44.495(9) d & 1099.245 & 56.5(18)\\
-
- & 44.495(9) d & 1291.590 & 43.2(14)\\
-
-\ce{^{60}Co} & 5.2714(5) y & 1173.228 & 99.85(3)\\
-
- & 5.2714(5) y & 1332.492 & 99.9826(6)\\
-
-\ce{^{61}Cu} & 3.339(8) h & 282.956 & 12.2(2.2)\\
-
- & 3.339(8) h & 373.050 & 2.1(4)\\
-
-%  & 3.339(8) h & 588.605 & 1.17(21)\\
-
- & 3.339(8) h & 656.008 & 10.8(20)\\
-
- & 3.339(8) h & 1185.234 & 3.7(7)\\
-
-\ce{^{62}Zn} & 9.193(15) h & 243.36 & 2.52(23)\\
-
- & 9.193(15) h & 246.95 & 1.90(18)\\
-
- & 9.193(15) h & 260.43 & 1.35(13)\\
-
-%  & 9.193(15) h & 304.88 & 0.29(3)\\
-
-%  & 9.193(15) h & 349.60 & 0.45(4)\\
-
- & 9.193(15) h & 394.03 & 2.24(17)\\
-
- & 9.193(15) h & 548.35 & 15.3(14)\\
-
- & 9.193(15) h & 596.56 & 26.0(20)\\
-
-%  & 9.193(15) h & 637.41 & 0.25(3)\\
-
-\ce{^{64}Cu} & 12.701(2) h & 1345.77 & 0.475(11)\\
-
-\ce{^{65}Zn} & 243.93(9) d & 1115.539 & 50.04(10)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\centering
-\caption{Decay data for gamma-rays observed in \ce{^{nat}Nb}(p,x).}
-\label{tab:nudat_table_nb}
-\begin{tabular}{@{}llll@{}}
-\toprule
-% \begin{tabular}{|c|c|c|c|}
-% \hline 
-Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
-\midrule
-\ce{^{82m}Rb} & 6.472(6) h & 554.35 & 62.4(9)\\
-
- & 6.472(6) h & 619.11 & 37.98(9)\\
-
-%  & 6.472(6) h & 698.37 & 26.3(7)\\
-
- & 6.472(6) h & 776.52 & 84.39(21)\\
-
- & 6.472(6) h & 1044.08 & 32.07(8)\\
-
-%  & 6.472(6) h & 1317.43 & 23.7(6)\\
-
-\ce{^{83}Sr} & 32.41(3) h & 418.37 & 4.2(3)\\
-
- & 32.41(3) h & 762.65 & 26.7(22)\\
-
-\ce{^{85m}Y} & 4.86(13) h & 231.7 & 22.8(22)\\
-
-\ce{^{85}Y} & 2.68(5) h & 231.65 & 84(9)\\
-
- & 2.68(5) h & 913.89 & 9.0(9)\\
-
-\ce{^{86}Zr} & 16.5(1) h & 242.8 & 95.84(2)\\
-
- & 16.5(1) h & 612.0 & 5.8(3)\\
-
-% \ce{^{86}Y} & 14.74(2) h & 187.87 & 1.26(4)\\
-\ce{^{86}Y}  & 14.74(2) h & 443.13 & 16.9(5)\\
-
-%  & 14.74(2) h & 190.80 & 1.01(3)\\
-
-%  & 14.74(2) h & 307.00 & 3.47(8)\\
-
-%  & 14.74(2) h & 443.13 & 16.9(5)\\
-
-%  & 14.74(2) h & 580.57 & 4.78(14)\\
-
-%  & 14.74(2) h & 608.29 & 2.01(15)\\
-
- & 14.74(2) h & 627.72 & 32.6(1)\\
-
-%  & 14.74(2) h & 703.33 & 15.4(4)\\
-
-%  & 14.74(2) h & 709.90 & 2.62(8)\\
-
-%  & 14.74(2) h & 767.63 & 2.4(3)\\
-
-%  & 14.74(2) h & 835.67 & 4.4(6)\\
-
-%  & 14.74(2) h & 1024.04 & 3.79(17)\\
-
- & 14.74(2) h & 1076.63 & 82.5(4)\\
-
- & 14.74(2) h & 1153.05 & 30.5(9)\\
-
-%  & 14.74(2) h & 1163.03 & 1.18(4)\\
-%  
-%  & 14.74(2) h & 1253.11 & 1.53(5)\\
-
-%  & 14.74(2) h & 1349.15 & 2.95(9)\\
-
- & 14.74(2) h & 1854.38 & 17.2(5)\\
-
- & 14.74(2) h & 1920.72 & 20.8(7)\\
-
-\ce{^{87}Zr} & 1.68(1) h & 380.79 & 62.79(10)\\
-
- & 1.68(1) h & 1227.0 & 2.80(4)\\
-
-\ce{^{87m}Y} & 13.37(1) h & 380.79 & 78.05(8)\\
-
-\ce{^{87}Y} & 79.8(3) h & 388.5276 & 82.2(7)\\
-
- & 79.8(3) h & 484.805 & 89.8(9)\\
-
-\ce{^{88}Zr} & 83.4(3) d & 392.87 & 97.29(14)\\
-
-\ce{^{88}Y} & 106.627(21) d & 898.042 & 93.7(3)\\
-
- & 106.627(21) d & 1836.063 & 99.2(3)\\
-
-\ce{^{89m}Nb} & 66(2) m & 588.0 & 95.57(13)\\
-
-\ce{^{89}Nb} & 2.03(7) h & 1511.4 & 1.9(4)\\
-
- & 2.03(7) h & 1627.2 & 3.5(7)\\
-
- & 2.03(7) h & 1833.4 & 3.3(7)\\
-
-\ce{^{89}Zr} & 78.41(12) h & 909.15 & 99.04(3)\\
-
- & 78.41(12) h & 1713.0 & 0.745(13)\\
-
-%  & 78.41(12) h & 1744.5 & 0.123(4)\\
-
-\ce{^{90}Mo} & 5.56(9) h & 122.370 & 64(3)\\
-
- & 5.56(9) h & 162.93 & 6.0(6)\\
-
- & 5.56(9) h & 203.13 & 6.4(6)\\
-
- & 5.56(9) h & 257.34 & 78(4)\\
-
- & 5.56(9) h & 323.20 & 6.3(6)\\
-
- & 5.56(9) h & 472.2 & 1.42(16)\\
-
- & 5.56(9) h & 941.5 & 5.5(7)\\
-
-\ce{^{90}Nb} & 14.6(5) h & 132.716 & 4.13(4)\\
-
- & 14.6(5) h & 141.178 & 66.8(7)\\
-
-%  & 14.6(5) h & 890.64 & 1.80(4)\\
-
- & 14.6(5) h & 1611.76 & 2.38(7)\\
-
-%  & 14.6(5) h & 1913.194 & 1.280(17)\\
-
-\ce{^{91m}Nb} & 60.86(22) d & 104.62 & 0.574(1)\\
-
- & 60.86(22) d & 1204.67 & 2.0(3)\\
-
-\ce{^{92m}Nb} & 10.15(2) d & 912.6 & 1.78(10)\\
-
- & 10.15(2) d & 934.44 & 99.15(4)\\
-
-\ce{^{93m}Mo} & 6.85(7) d & 263.049 & 57.4(11)\\
-
- & 6.85(7) d & 684.693 & 99.9(8)\\
-
- & 6.85(7) d & 1477.138 & 99.1(11)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-% 
-% 
-\section{Measured excitation functions} \label{fit_figures}
-
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH-3.5.1, EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
-
-% \comment{Add in CoH model output from Toshihiko to all plots}
-
-% \comment{Fix a few figure labels (c/i) based on Jon;s email}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/51Cr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:51Cr}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/52Mn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:52Mn}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/52gMn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:52gMn}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/52mMn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:52mMn}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/54Mn.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:54Mn}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/55Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:55Co}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p1}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/56Ni.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:56Ni}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/57Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:57Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/57Ni.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:57Ni}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58Co.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:58Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58gCo.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:58gCo}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/58mCo.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:58mCo}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p2}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/59Fe.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:59Fe}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/60Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:60Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/61Cu.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:61Cu}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/64Cu.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:64Cu}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/82mRb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:82mRb}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/83Sr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:83Sr}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p3}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/85gY.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:85gY}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85mY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85mY}
-    \end{subfigure}
-%      \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/86Y.pdf}{50}
-% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-%                  \refstepcounter{subfigure}\label{fig:86Y}
-%     \end{subfigure}
-%     \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/86Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:86Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87Y}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87gY}
-    \end{subfigure}
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p4}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-%      \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
-% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-%                  \refstepcounter{subfigure}\label{fig:87gY}
-%     \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87mY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87mY}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/87Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/88Y.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Y}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/88Zr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Zr}
-    \end{subfigure}%
-    \\
-         \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89Nb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:89Nb}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:89gNb}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p8}
-\end{figure*}
-
-\begin{figure*}
-    \centering    
-%          \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-%          \refstepcounter{subfigure}\label{fig:89gNb}
-%     \end{subfigure}%
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/89Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:89Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:91mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:92mNb}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:93mMo}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p7}
-\end{figure*}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-%          \refstepcounter{subfigure}\label{fig:93mMo}
-%     \end{subfigure}%
-% %      \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% % %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-% %         \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
-% % %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-% %          \refstepcounter{subfigure}\label{fig:91mNb}
-% %     \end{subfigure}%
-% %     \\
-% %     \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\textwidth]{./figures/target2.png}
-% %         \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
-% % %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-% %                  \refstepcounter{subfigure}\label{fig:92mNb}
-% %     \end{subfigure}
-% %      \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-% % %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-% %         \refstepcounter{subfigure} \label{fig:93mMo}
-% %     \end{subfigure}%
-% %     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-%      \label{fig:xs_curves_p5}
-% \end{figure*}
-
-% 
-% 
-\section{Measured isomer-to-ground state branching ratios } \label{ibr_figures}
-
-Plots of the isomer-to-ground state ratios measured in this work are presented here, in comparison with literature data and reaction modeling codes \cite{MICHEL1997153,Ditroi2008,Titarenko2011,Graves2016}.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/52Mn_IBR.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:52Mn_IBR}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58Co_IBR.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:58Co_IBR}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85Y_IBR.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y_IBR}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/87Y_IBR.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Y_IBR}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89Nb_IBR.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89Nb_IBR}
-    \end{subfigure}
-     \label{fig:ibr_curves}
-\end{figure*}
-
-% \twocolumn
-
-%% References with BibTeX database:
-
-% \bibliographystyle{elsarticle-num}
-% \bibliographystyle{elsarticle-harv}
-% \bibliographystyle{elsarticle-num-names}
-% \bibliography{<your-bib-database>}
-% \addcontentsline{toc}{chapter}{Bibliography}
-\bibliographystyle{elsarticle-num}
-% \bibliographystyle{apsrev4-1}
-% \bibliographystyle{ieeetr}
-\bibliography{../../library}
-% \thispagestyle{fancyTOC}
-
-%% Authors are advised to use a BibTeX database file for their reference list.
-%% The provided style file elsarticle-num.bst formats references in the required Procedia style
-
-%% For references without a BibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-% \bibitem{}
-
-% \end{thebibliography}
-
-\end{document}
-
-%%
-%% End of file `ecrc-template.tex'.

### 2018-04-05 nb_px_paper/nb_px_paper.tex
Broke Nb(p,x) paper into container w/ separate body text, appendices, and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

--- 2018-04-03 nb_px_paper/nb_px_paper.tex
@@
 % \usepackage{longtable}
-\usepackage{subcaption}
+% \usepackage{subcaption}
 \usepackage{booktabs,siunitx}
@@
 
-\usepackage{lineno}
+% \usepackage{lineno}
 
@@
 \usepackage{bm}% bold math
+
+% Prevent ''overfull hbox'' warnings for < 5pt overflow 
+% \hfuzz=10pt 
+% \hfuzz\maxdimen
 
@@
 \newcommand{\subfigimg}[4][,]{%
-  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
+  \setbox1=\hbox{\noindent\includegraphics[#1]{#3}}% Store image in box
   \leavevmode\rlap{\usebox1}% Print image
@@
 
+\usepackage{subfig}
+% Remove a), b), etc labels from subfigs
+\captionsetup[subfigure]{labelformat=empty}
+
 \makeatletter
@@
 \makeatother
+
+\hyphenation{gamma-rays}
 
@@
 
-% Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
-% However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.
-% To address this need, a
-A stack  of thin Nb 
-% , Cu, and Al monitor 
-foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
-% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
-% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
-A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
-% The measurements are 
-These are useful in medical and basic science radionuclide productions at intermediate energies. 
-% Cross sections were measured using the well-characterized 
-The
-% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
-\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn}  reactions were used to
-determine proton fluence, and all activities were quantified using HPGe spectrometry.
-Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
-The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
-This work also reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
-% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
-\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-% \textred{
-% Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
-% }
-% \textred{
-% To avoid inadvertently reporting enhanced proton fluence due to
-The effects of  \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, arising from  silicone adhesive in the Kapton tape used to encapsulate the aluminum monitor foils, is also discussed as a cautionary note to future stacked-target cross section measurements.
-% strongly discouraged.
-% }
-% Comparisons against the 
-\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the differences between codes for the
-% impact of pre-equilibrium particle emission  for the 
-% 40--90 MeV 
-\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-
-% \begin{description}
-% \item[Usage]
-% Secondary publications and information retrieval purposes.
-% \item[PACS numbers]
-% May be entered using the \verb+\pacs{#1}+ command.
-% \item[Structure]
-% You may use the \texttt{description} environment to structure your abstract;
-% use the optional argument of the \verb+\item+ command to give the category of each item. 
-% \end{description}
+\input{./nb_abstract_text}
+
 \end{abstract}
@@
 %%
-\linenumbers
-
-%% main text 
-\section{Introduction} \label{sec:intro}
-
-% Referring to abstract:
-% % \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
-% 
-% 
-% \comment{Comment on the Si production here?  (see red text)}
-% 
-% \comment{Add extra physics language with Lee.}
-
-% \comment{cite theranostic papers, etc}
-
-Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S. alone 
-% ,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases 
-\cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
-% The vast majority
-Most of the radionuclides currently used for these procedures are produced 
-% in the field's array of
-by low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerators, 
-% capabilities, which routinely produce many of the staple medical radionuclides, such as 
-e.g., \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ga}, \ce{^{82}Rb}, and \ce{^{123}I}. 
-These accelerators also produce 
-% , as well as many  
-% of the 
-non-medical radionuclides with commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
-% \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
-I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: In this context, I would make this definition based on what machines in the US are routinely used for medical isotope production - based on this, I agree with 200 MeV.
-}
-% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
-% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
-Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
-% \cite{Qaim201731}. 
-% Move next sentence to Fe paper
-% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
-Candidate isotopes to meet these needs 
-% of personalized medicine 
-have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
-These studies will serve to facilitate the production of clinically relevant quantities of radioactivity.
-
-Accurate cross section measurements using  activation methods benefit from well-characterized monitor reactions.  
-Currently there is 
-% , which  currently
-a paucity of such data at intermediate energies, and much of what exists have  high uncertainties (\textgreater15\%).
-% One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.
-% This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
-% Lee - cut?
-Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}.
-% Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}.
-% While work is needed to improve upon existing monitor reaction data, the development of n
-% Lee - cut?
-New reactions can expand the available range of options for the monitoring of charged particle beams.
-This work 
-% in particular seeks to improve this range of options by 
-is an attempt to characterize a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory,
-% IPF
-the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the Separated Sector Cyclotron at the 
-% iThemba LABS
-iThemba Laboratory for Accelerator Based Sciences.
-% \comment{Stephen: I'm having a hard time following this paragraph.
-Some of your syntax overlaps significantly with nuclear medicine \& medical physics terminology with different intended meanings.
-For example 'dosimetry' is typically taken to mean the measurement of absorbed energy per unit mass (J/kg) and associated measurements/specifications.
-Another example, 'dosimetry standard' is used quite often when referring to NIST air kerma reference standards which are the bedrock of Accredited Dosimetry Calibration Lab (ADCL) measurements.
-As you are more familiar with classic Nuclear Physics writing, perhaps you better know how this language will be interpreted.
-}
-
-% % 
-% 
-% Most of this should be more appropriate for the PhD thesis?
-% 
-% % 
-% Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}.
-% % All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
-% % \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
-% Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
-% % \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
-% Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
-% This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
-% This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.
-% In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
-% This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
-% While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
-% % For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
-% % In these experiments, a
-% A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
-% % \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
-% Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.
-
-% In theory, nearly any radioisotope can serve as a reaction monitor, but 
-% those desired to be classified as a 
-Desirable monitor reactions 
-% standard 
-possess several hallmark characteristics,  
-% The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.
-% Primarily, this means selecting a radionuclide product with 
-% a number of 
-including intense and distinct gamma-rays, 
-% with high intensities,  
-which can be used to uniquely identify it during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
-% The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
-% \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
-Care should also be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
-For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
-% Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
-% However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
-% Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
-% Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
-% and leisurely 
-% following end-of-bombardment.
-% without the majority if it decaying away.
-% In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
-% For proper quantification, i
-It is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
-This includes a precise and well-established half-life,  
-% needed to  correct for decay losses, 
-as well as well-characterized decay gamma-ray intensities.
-% In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
-% Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
-From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily available
-% readily commercially available at an affordable price and is 
-and  chemically inert.
-% --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current. 
-% Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
-% For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
-% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectrometry.
-% For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
-Targets which can be formed into a wide thickness range are convenient, as selection is subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
-% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
-% \comment{Stephen:  This is also a discussion point.
-If you're trying to introduce the purpose of this paper, i.e.
-the establishment of a new monitor reaction, I would try to condense paragraphs 3--9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction.
-The rest of this content can be included in the discussion if you feel it is necessary.}
-Lastly, and perhaps most importantly for high-energy monitor reaction applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
-Typically, this is  mostly a concern for secondary neutrons produced through (z,xn) reactions, 
-% on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
-% Any
-but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often 
-% a laborious task 
-difficult to accurately and unambiguously separate out the fraction of secondary particles contributing to the total activation.
-
-One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
-Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
-\ce{^{90}Mo} also has 
-% excellent decay properties ---
-a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997})  
-% allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
-and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production.
-In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
-
-The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo}  
-% ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) 
-via the $^\text{nat}$Nb(p,x) reaction. 
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
-% These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
-These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
-% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the diagnostic agent \ce{^{82\text{m}}Rb}.
-
-%   \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
-%   
-%   \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}
-
-In addition to providing a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
-Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
-These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$\,m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$\,d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$\,h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$\,d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$\,h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$\,h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$\,m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$\,h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
-
-The measurements described in this paper involve the use of multiple monitor reactions in conjunction with statistical calculations and proton transport simulations to reduce systematic uncertainties in beam energy assignments, leading to some of the first and most precise measurements  for many of the excitation functions reported here.
-By expanding the available set of monitor reaction standards and well-characterized isotope production excitation functions, this work should help optimize medical isotope production modalities, making more options   available for modern medical imaging and cancer therapy.
-
-\section{Experimental methods and materials}\label{sec:experiment}
-
-% While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work 
-The work described herein follows the  methods established by Graves \etal\ for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.
-
-\subsection{Stacked-target design }\label{sec:target_design}
-
-% \comment{Regex to replace all hard figure references with LaTeX cross-references  [F,f]igure[^s*}]     }
-
-A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
-% For targets, a
-A series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
-Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
-Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
-% , along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
-The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
-One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
-These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
-% These six foil packet bundles were inserted into one of six  
-The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
-After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
-The specifications of the target stack design for this work is presented in \autoref{tab:stack_table}.
-
-This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
-The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
-The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
-The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV --- this energy profile was used for all later analysis.
-At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
-The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectrometry, which started approximately 6 hours following end-of-bombardment.
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
- % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
- \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place.
-The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell.
-The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.
-}
-\end{figure}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Specifications of the  target stack design in the present work.
-The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here.
-The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
-Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
-\label{tab:stack_table}
-\small
-\begin{tabular}{@{}llll@{}}
-\toprule
-% Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
-Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
-SS profile monitor & 249.8 \micro m         & 194.56                                      & 0.29                      \\
-Al-1               & 25.0 \micro m          & 6.52                                        & 0.72                      \\
-Cu-1               & 61.3 \micro m          & 53.74                                       & 0.15                      \\
-Nb-1               & 30.0 \micro m          & 23.21                                       & 0.17                      \\
-Al Degrader 01     & 4.96 mm           & -                                            & -                          \\
-Al-2               & 25.5 \micro m          & 6.48                                        & 0.36                      \\
-Cu-2               & 61.8 \micro m          & 53.85                                       & 0.17                      \\
-Nb-2               & 30.8 \micro m          & 22.91                                       & 0.17                      \\
-Al Degrader 02     & 4.55 mm           & -                                            & -                          \\
-Al-3               & 25.8 \micro m          & 6.47                                        & 0.31                      \\
-Cu-3               & 61.5 \micro m          & 53.98                                       & 0.11                      \\
-Nb-3               & 31.0 \micro m          & 22.91                                       & 0.24                      \\
-Al Degrader 03     & 3.52 mm           & -                                            & -                          \\
-Al-4               & 26.3 \micro m          & 6.51                                        & 0.41                      \\
-Cu-4               & 61.3 \micro m          & 53.46                                       & 0.22                      \\
-Nb-4               & 30.8 \micro m          & 22.55                                       & 0.25                      \\
-Al Degrader 04     & 3.47 mm           & -                                            & -                          \\
-Al-5               & 26.5 \micro m          & 6.48                                        & 0.29                      \\
-Cu-5               & 61.5 \micro m          & 53.57                                       & 0.11                      \\
-Nb-5               & 30.8 \micro m          & 22.11                                       & 0.25                      \\
-Al Degrader 05     & 3.46 mm           & -                                            & -                          \\
-Al-6               & 26.3 \micro m          & 6.48                                        & 0.62                      \\
-Cu-6               & 62.0 \micro m          & 53.84                                       & 0.32                      \\
-Nb-6               & 31.3 \micro m          & 22.12                                       & 0.13                      \\
-SS profile monitor & 124.4 \micro m         & 101.34                                      & 0.23                      \\ \bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Measurement of induced activities}\label{sec:spectroscopy}
-
-% For consistency, a
-A single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
-The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
-Samples were counted at fixed positions ranging 4.5--83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
-The foils were counted  for a period of 2 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities,  with dead time never exceeding 5\%.
-An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
-%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
-
-\begin{figure}
- \centering
- \includegraphics[width=6in]{./figures/sample_gspec.pdf}
- % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
- \caption{A gamma spectrum, collected from an activated Nb foil at approximately 80 MeV.
-While the majority of observed reaction products are visible in this spectrum,  the \ce{^{90}Mo} decay lines, which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction, are high in intensity and clearly isolated from surrounding peaks.}
- \label{fig:gspec}
-\end{figure}
-
-Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
-The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
-% For reference, t
-The nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-Data for photon attenuation coefficients were taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
-% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
-Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
-% activity for each gamma-ray possesses a 
-The total propagated uncertainty of the measured activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
-
-Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly by decay down a mass chain.
-To this end, it is useful to differentiate between the types of cross sections reported in this work. 
-For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
-% In addition, 
-Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
-
-% To convert these activities into cross sections, c
-Corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB, from the measured activities.
-The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
-For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
-% \begin{equation}
-% A\pp{t} = A_0 e^{-\lambda t}
-% \end{equation}
-Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
-As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
-In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
-\begin{equation}
-A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_{i,0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
-\end{equation}
-where $j$ refers to a precursor nucleus populating a specific end-product.  
-While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
-\begin{equation}
-A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
-\end{equation}
-In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
-After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
-
-% \comment{Regex to replace table hard link with LaTeX cross-reference. - match w/ [T,t]able[^*}]   }
-
-\subsection{Proton fluence determination}\label{sec:dosimetry}
-
-% \comment{Stephen:  Still not a huge fan of the dosimetry terminology, but I would defer to the preference of those with more experience in the field. }
-
-% describe integral equation for converting activities to currents here
-% 
-% % % 
-% 
-%  Move these first two commented sentences into PhD thesis.
-% 
-% % % 
-% An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
-% At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
-% For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
-% To this end, 
-In addition to the LANSCE-IPF beamline's direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide more sensitive beam current monitors.
-% These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
-The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used for  proton fluence measurement \cite{gul2001charged}.
-% The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
-Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution was expected for all monitor and target foils.
-As a result, the integral form of the well-known activation equation was used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
-%by convolving the IAEA recommended cross section values with the proton energy distribution:
-% \begin{equation}
-% A_0 = I\ \rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE
-% \end{equation}
-\begin{equation}
-I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
-\end{equation}
-where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy $E$, and $\frac{d\phi}{dE}$ is the differential proton fluence.
-Using this formalism, the quantified EoB activities for each monitor reaction may be converted into a measured proton fluence at each energy position.
-
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
-Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
-The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
-The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
-Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental source data sets used in their evaluation.
-Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
-For the monitor reactions employed in this work, these data sets are G.
-Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \cite{Steyn1990}, M.
-Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S.
-Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.
-
-\subsection{Proton transport calculations}\label{sec:proton_transport}
-
-Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-These estimates of average beam energy in each foil are useful for the preliminary stack design.
-% , as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering. 
-However, for final energy and fluence determinations, a more rigorous method of proton transport modeling is needed.
-The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
-% In addition, 
-MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
-As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.
-$10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
-
-The ability to model the full energy distribution in each target position is vital for stacked target irradiations, due to the progressively larger energy straggling towards the rear of the stack.
-The initial proton beam has a finite energy spread (an approximately 0.1 MeV Gaussian width at 100 MeV), and since stopping power for charged particles is inversely proportional to their energy, the low-energy tail of the energy distribution is degraded more in each stack element than the high-energy tail.
-This effect compounds  towards the rear of the stack, creating a significantly broadened low-energy tail, and a progressively larger net shift of the centroid to a lower energy. 
-% For each foil in the target stack, 
-To account for this increasing energy uncertainty, a suitably representative energy must be established for  each foil in the target stack.
-In this work, the flux-weighted average proton  energy in each foil, $\langle E \rangle$,  represents the energy centroid for protons in a target stack component, calculated using the energy distributions $\frac{d\phi}{dE}$ from MCNP6 modeling of proton transport:
-\begin{equation}
-\langle E \rangle = \dfrac{{\displaystyle\int E \dfrac{d\phi}{dE} dE}}{{\displaystyle\int \dfrac{d\phi}{dE} dE}}
-\end{equation}
-Likewise, to represent the energy uncertainty for each stack position, the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution is chosen for each energy position reported.
-While most experimental uncertainties are reported at the 1$\sigma$ level, the $2.355\sigma$ FWHM is used here to ensure at the 98\% confidence interval that this width includes  the \enquote{true} energy centroid value.
-
-The \enquote{variance minimization} techniques  described by  Graves \etal\  have been employed here to further reduce the uncertainty in proton energy assignments     \cite{Graves2016}.
-This method is based on the assumption that the independent measurements of proton fluence from the five monitor reactions used in this work should all be consistent at each energy position.
-If the monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, disagreement in the  observed proton fluences is due to poorly characterized stopping power in simulations, or a systematic error in the
-% stack design, namely, the
-areal densities of the stack components \cite{Graves2016,Marus2015}. 
-This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
-
-% Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
-Due to the  
-% difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
-% This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to 
-significantly greater areal density of the thick 6061 aluminum degraders as compared to the other stack elements (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$),
-% As such
-the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
-This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
-The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position.
-This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
-This energy corresponds to a 6061 aluminum areal density of 2.52\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
-
-\begin{figure}
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.5\linewidth]{./figures/variation_curve-crop.pdf}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Result of the variance minimization performed by adjusting the degrader density in MCNP6 simulations of the target stack.
-A flux-weighted average proton energy of 41.34 MeV entering the last energy position creates a clear minimum in observed reaction fluence variance, corresponding to an areal density 2.52\% greater than nominal.
-The variance minimum occurring at a lower incident energy than nominal MCNP6 and A\&Z calculations indicates that there exists an additional systematic beam degradation not accounted for in modeling of proton transport in the stack design.}
- \label{fig:variation_curve}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/before_minimization_plot.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:before_minimization}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/after_minimization_plot.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:after_minimization}
-    \end{subfigure}%
-    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%.
-A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
-Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
-     \label{fig:variance_mins}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:Na22_activity_compare}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:Na24_activity_compare}
-    \end{subfigure}%
-    \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
-At low energies, experimentally observed apparent \ce{^{22,24}Na} activities in each Al foil packet are consistent with IAEA recommendations, but diverge at higher energies as the \ce{^{nat}Si}(p,x)\ce{^{22}Na} exit channels begin to open up.
-\ce{^{22,24}Na} activities consistent with TENDL-2015 estimates are observed in each Nb and Cu foil packet as well, confirming that contamination may be attributed to activation of silicone adhesives.}
-     \label{fig:Na_activity_compare}
-\end{figure}
-
-The impact of this variance minimization is  clearly  seen in   \autoref{fig:variance_mins}.
-As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
-In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
-% \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
-It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0\,MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
-% This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6\,MeV), though to a much smaller degree.
-In both cases, this disparity is caused by the fact that the Kapton tape used for sealing the foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
-\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\%\,\ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3\,MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6\,MeV).
-\ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
-In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
-The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.
-
-These compensating factors  contribute to \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} production being competitive with the \ce{^{nat}Al}(p,x)\ce{^{22}Na} production route.
-This is made made obvious when comparing the total measured activities of \ce{^{22}Na} and \ce{^{24}Na} in each Al foil packet (which combines both Al- and Si-based production routes), relative to the expected EoB activities for each reaction channel, presented in \autoref{fig:Na_activity_compare}.
-Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections.
-Several observations are immediately obvious.
-At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.
-At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90 MeV.
-For the \ce{^{24}Na} production, we see a similar behavior, though since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude, only a minor increase in apparent \ce{^{24}Na} activity is seen.
-The measured EoB \ce{^{22}Na} and \ce{^{24}Na} activities seen  in all Cu and Nb foil positions are also shown here, which are seen to be consistent with the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{22}Na} yields.
-The observed \ce{^{24}Na} activities also follow the shape of the TENDL-2015 \ce{^{nat}Si}(p,x)\ce{^{24}Na} yields, albeit smaller in magnitude at the higher energy positions.
-
-While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
-The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to 
-% the number of assumptions involved in such a calculation.
-uncertainties in the areal density of the Si in the adhesive.
-% The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
-% These have been taken as
-However, if we assume a 10\% Si stoichiometric basis and an areal density of 4.79 mg/cm$^2$ (based on bulk density),
-% respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
-% In principle, it would be possible  to 
-we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
-The results of this  may be seen in \autoref{fig:na_subtraction}.
-Following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
-While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
-Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
-While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
-% In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
-% Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils.
-% The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively.
-% The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
-This serves as a pointed example of the importance of selecting monitor reaction products inaccessible through channels aside from the primary reaction (\ce{^{nat}Al}(p,x)\ce{^{22,24}Na}, in this case ), as noted previously.
-% However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.
-
-% Avoud using al and silicone
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:before_subtraction}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.50\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:after_subtraction}
-    \end{subfigure}%
-    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.
-Following subtraction of \ce{^{22,24}Na} activities observed in the silicone adhesive of Nb and Cu foils in the same energy \enquote{compartment}, the consistency of the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction improves  dramatically.
-By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
-     \label{fig:na_subtraction}
-\end{figure}
-
-Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the six irradiated Nb foils in \autoref{fig:Nb_ptallies}.
-As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.
-In addition, as the beam becomes more degraded, the magnitude of the peak of each energy distribution (as well as the integral of each distribution) is reduced, as beam fluence is lost due to scattering, and the peak-to-low-energy-tail ratio increases as more  secondary protons are produced upstream.
-As with the monitor foils, these distributions were used to calculate the  energy centroid  (as the  flux-weighted average proton  energy) and  uncertainty (as the FWHM of the distribution) for the final proton energy assignment of each Nb foil.
-
-An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
-Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
-% In the interest of surety of because they are consistent, t
-The uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
-Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
-These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport 
-% model, as well as 
-and an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
-Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.
-These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
-% This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
-% As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
-% The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/Nb_ptallies.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
-The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
-As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
- \label{fig:Nb_ptallies}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions.
-%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
-%   A clear loss of 
-  The fluence  drops by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.}
-%   This is due to a combination of beam utilization, as well as scattering.}
- \label{fig:fluence_plot}
-\end{figure}
-
-% \begin{equation}
-% R = N_T \int_0^{E_{max}} \sigma(E) \dfrac{d\phi}{dE} dE
-% \end{equation}
-
-\subsection{Calculation of measured cross sections}\label{sec:calcs_sec}
-
-%  include 1st and 2nd order bateman stuff here
-
-Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
-While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
-% cross sections, 
-over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
-For both the cumulative and independent activities quantified, cross sections were calculated as:
-\begin{equation}
-\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
-\end{equation}
-where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
-The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
-The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).
-
-% \begin{align}
-% N_{\gamma} &= N_D \epsilon_\gamma I_\gamma \\
-% &=  \epsilon_\gamma I_\gamma  \dfrac{N_T \sigma\pp{\bar{E}} \phi\pp{\bar{E}} }{\lambda}\pp{1 - e^{-\lambda t_i}}  e^{-\lambda t_d} \pp{1 - e^{-\lambda t_c}} \nonumber
-% \end{align}
-
-% \subsection{Systematic uncertainties}
-% 
-% XXXXXX
-
-\section{Results}
-
-After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
-In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
-% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
-This blister   shows the location where the primary proton beam was incident upon the foil.
-The \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used to determine the uncertainty-weighted mean fluence at each energy position (seen in \autoref{fig:fluence_plot}).
-A fluence of 198.8$\pm$6.7\,nAh was calculated to be incident upon the target stack using the MCNP6 fluence model, and a  fluence of 196.9$\pm$11.3\,nAh using the linear fit model, both of which are consistent with the nominal fluence of 205.9\,nAh based on IPF upstream current monitors.
-As fluence loss in the target box's entrance window scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 8.9\% to  180.9$\pm$5.4\,nAh (and by 7.2\% to  182.7$\pm$13.5\,nAh using the linear fit model) over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
-This loss of fluence is due to a combination of 
-% beam utilization for the various 
-(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
-
-Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40--90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
-In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb} were  extracted and are recorded in \autoref{tab:ibr_table}.
-Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--7\%), proton fluence ($\pm$4--6\%), and foil areal density ($\pm$0.1--0.6\%).
-% \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:cu_rp_table}
-\small
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
-\ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
-\ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
-\ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
-\ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
-\ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
-\ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
-\ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
-\ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
-\ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
-\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Nb}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:nb_rp_table}
-\small
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
-\ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
-\ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
-\ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
-\ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
-\ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
-\ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
-\ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
-\ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
-\ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
-\ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
-\ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
-\end{tabular}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Nb}(p,x) and \ce{^{nat}Cu}(p,x) reaction products observed in this work.}
-\label{tab:ibr_table}
-\small
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                               & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
-E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
-\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-These results have several notable features.
-The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90 MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
-Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
-Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
-
-% Furthermore, t
-This work presents the first measurements of several observables in 
-% these mass regions.
-% This work reports the first experimental measurement of
-this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region, 
-% It also represents  the first measurement of 
-the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
-The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
-Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).
-
-Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
-This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
-% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
-% , which makes activity quantification trivial.
-% In addition, 
-\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
-Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
-This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.
-
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
-% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the Auger-therapy agent \ce{^{82\text{m}}Rb}.
-
-\ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}), while useful on its own as a positron emitter, stands poised as a particularly promising candidate for theranostic pairing with the soft $\beta^-$ emitter \ce{^{66}Ni} ($t_{1/2}=54.6\pm0.3$ h, $\beta^-$=100\% to \ce{^{66}Cu} \cite{Browne2010a}) \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}.
-\ce{^{nat}Cu}(p,x)\ce{^{57}Ni} would seem to be an intriguing production pathway, due to the ready availability of Cu metal as target, combined with the fact that production in this pathway strongly favors \ce{^{57}Ni} over \ce{^{56}Ni} --- indeed, the \ce{^{57}Ni}/\ce{^{56}Ni}
-%ratio of cross sections is approximately 70 at 61.58 MeV, and varies from 11-18 at the 70-90 MeV positions.
-ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
-The traditional route for \ce{^{57}Ni} production is via \ce{^{nat}Co}(p,3n)\ce{^{57}Ni}, but at moderate energies, suffers from more  \ce{^{56}Ni} contamination than \ce{^{nat}Cu}(p,x)  ($\sigma_\text{57Ni} / \sigma_\text{56Ni}\approx$ 10 at maximum).
-Lower-energy production via \ce{^{nat}Co}(p,3n) at 24--40\,MeV is below threshold for \ce{^{56}Ni}, but has a peak cross section of approximately 10 mb, making \ce{^{nat}Cu}(p,x) the superior production route for moderate-energy accelerators  \cite{MICHEL1997153,Ditrói2013}.
-
-% Moving away from the potential PET emitters, 
-\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}, with the 
-% The 
-% emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, and the 
-PET branch 
-% makes  \ce{^{64}Cu}  
-suited for imaging of prostate and colorectal cancers  
-% the possibility for real-time dose monitoring and verification
-\cite{Lewis2003,Bandari2014,mp500671j}.
-% This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,Bandari2014,mp500671j}.
-Several production routes currently exist: \ce{^{64}Ni}(p,n)  uses 8--14 MeV protons on the expensive enriched target \ce{^{64}Ni} (0.9255\% natural abundance), but offers a high radioisotopic purity assuming a highly enriched target \cite{Szelecsenyi1993,Aslam2009}.
-\ce{^{68}Zn}(p,$\alpha$n) requires more energetic 20--30 MeV protons, and necessitates an enriched target (18.45\% natural abundance) to avoid the co-production of radio-copper impurities \cite{Hilgers2003,Szelecsenyi2005}.
-More recently, the use of compact DD neutron generators for \ce{^{nat}Zn}(n,p) production has been proposed, with the promise of mCi-scale production with high specific activity  \cite{Voyles2017}.
-% \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} could be another potential production pathway
-
-\ce{^{86}Y} ($t_{1/2}=14.74\pm0.02$ h, $\epsilon$=100\% to \ce{^{86}Sr}  \cite{NEGRET20151}) is another novel  emerging  PET isotope, whose longer half-life has poised it for applications as a tracer for slower metabolic processes, as well as in   pharmacokinetics studies \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011}.
-In particular, it is highly desired to form a theranostic pair with the widely-employed $\beta^-$ therapy agent \ce{^{90}Y} ($t_{1/2}=64.00\pm0.21$ h, $\beta^-$=100\% to \ce{^{90}Zr} \cite{Browne1997}), which can be produced from a long-lived \ce{^{90}Sr} generator and emits no discrete observable gamma-rays or x-rays though decay \cite{Herzog1993}.
-Although a weak positron branch exists and bremsstrahlung scintigraphy is commonly used for clinical imaging of the \ce{^{90}Y} biodistribution, theranostics  necessitate an imaging isotope to be paired for quantification of its uptake and biodistribution  \cite{Nickles2004}.
-Conventional production of \ce{^{86}Y} proceeds through low-energy (7--14 MeV) irradiation via \ce{^{86}Sr}(p,n), which requires an enriched  \ce{^{86}Sr} target (9.86\% natural abundance), in order to eliminate contamination from (p,n) on the other stable \ce{^{84,87,88}Sr} isotopes  \cite{Rosch1993}.
-Alternatively, production at 33--43 MeV via \ce{^{88}Sr}(p,3n) has been proposed --- this pathway also requires an enriched target (82.58\% natural abundance) for the same reason, but contamination with other Y co-activities will be even more pronounced than via (p,n), due to the opening of (p,n) and (p,2n) channels on all stable Sr isotopes \cite{doi:10.1139/v67-193,levkovski1991cross}.
-Minimizing activity from other isotopes of the element in question is essential for producing radionuclides in high specific activity, as these competing isotopes are often impractical to separate out by radiochemical means.
-% \comment{Stephen:  impossible by radiochemical means, and impossible by affordable/practical means.\\Substitute for ``difficult'' post-discussion.}
-As a result, it would appear that \ce{^{nat}Nb}(p,x) is a poor route for  \ce{^{86}Y} production in this respect, as it only reaches a maximum of approximately 35\% radioisotopic purity.
-The  dominant yttrium radioisotope produced by  \ce{^{nat}Nb}(p,x) in the 40--90 MeV region is  \ce{^{87}Y} ($t_{1/2}=79.8\pm0.3$ h, $\epsilon^-$=100\% to \ce{^{87m}Sr} \cite{Johnson2015}).
-However,  \ce{^{87}Y} itself has application as a generator for  \ce{^{87m}Sr} ($t_{1/2}=2.815\pm0.012$ h, IT=99.70\% to \ce{^{87}Sr} \cite{Johnson2015}), which is used for imaging studies of metastatic bone cancers, especially when in a theranostic pair with the established therapy agent \ce{^{89}Sr} ($t_{1/2}=50.563\pm0.0025$ d, $\beta^-$=100\% to \ce{^{89}Y} \cite{Singh2013}) \cite{Kiselev1974,Kandil2009}.
-% Since the radio-yttrium purity of \ce{^{87}Y} is approximately 88\% between 51--61 MeV in \ce{^{nat}Nb}(p,x), this could present an intriguing route for  \ce{^{87}Y} production.
-
-\ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h, $\epsilon$=100\% to \ce{^{89}Y}  \cite{Singh2013}) is a long-lived positron emitter useful as a tracer for slow biological processes, immune studies, and imaging of liver and  breast cancers \cite{Verel2003,Dijkers2009,Dijkers2010}.
-Current production focuses on \ce{^{89}Y}(p,n)\ce{^{89}Zr} between 9--14 MeV, which offers an extremely high-purity route on a mono-isotopic target and a strong population of \ce{^{89}Zr}, with a peak cross section of nearly 800 mb   \cite{PhysRevC.38.1624,Omara2009}.
-Due to co-production of additional \ce{^{86,87,88}Zr} radio-zirconium,  \ce{^{nat}Nb}(p,x) is clearly inferior to  \ce{^{89}Y}(p,n)\ce{^{89}Zr}, as the Nb route has a smaller peak cross section of approximately 290 mb, and achieves only 10--20\% radioisotopic purity in the 50--90 MeV region.
-
-\ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h, $\epsilon$=100\% to \ce{^{90}Zr}  \cite{Browne1997}) is an emerging positron emitter with a moderate lifetime, making it suited for immune and tumor uptake studies    \cite{Busse2002,Radchenko2012}.
-It is typically produced using 8--15 MeV protons via \ce{^{90}Zr}(p,n)\ce{^{90}Nb}, using an enriched target (51.45\% natural abundance) for high radioisotopic purity, and produces a product with minimal contamination and a peak cross section of approximately 750 mb  \cite{Busse2002}.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Nb} offers a possible alternative pathway using a natural target, at the expense of a smaller peak cross section.
-\ce{^{90}Nb} may be produced directly with an approximately 370 mb peak cross section and 99\% radioisotopic purity, or could be produced as a \ce{^{90}Mo}/\ce{^{90}Nb} generator, which would have nearly 100\% radioisotopic purity by using protons below the \ce{^{nat}Nb}(p,5n) threshold of 45.76 MeV.
-However, the greatest problem with using the \ce{^{nat}Nb}(p,x) reaction to produce \ce{^{90}Nb} is the inability to separate the radioisotope from the target itself, rendering the production of a high-specific activity product impossible.
-
-Finally, \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h, $\epsilon$=100\% to \ce{^{82}Kr}  \cite{Tuli2003}) is a diagnostic and emerging Auger-therapy agent, typically seen as a contaminant in \ce{^{82}Sr}/\ce{^{82}Rb} generators
-% for PET studies
-\cite{Kovacs1991}.
-It is commonly produced via \ce{^{82}Kr}(p,n) at 10--15 MeV, using an enriched \ce{^{82}Kr} gaseous target, with a peak cross section of approximately 400 mb at 12 MeV \cite{Kovacs1991}.
-Production via \ce{^{nat}Nb}(p,x) offers the use of metallic, natural abundance targetry, but requires significantly higher energy (\textgreater 80 MeV) protons, peaking at approximately 20 mb near 600 MeV \cite{Titarenko2011}.
-It is clear that this production route offers no advantage over existing \ce{^{82}Kr}(p,n) routes for in-house production.
-
-% \comment{Make sure to comment on avoiding the use of silicone-based adhesives for Al monitor foils.}
-
-% Finally, w
-We wish to urge caution in future stacked-target activation experiments by avoiding the use of silicone adhesive-based tapes for foil containment, especially when paired with the use of Al monitor foils.
-Acrylic-based tape options are commercially available, and are immune from (p,x) production of \ce{^{22,24}Na} activities, due to being of too low-Z for these reaction channels to be possible.
-Even with subtraction of \ce{^{22,24}Na} activities though irradiating a Kapton tape \enquote{blank} or similar, we observe the Al monitor channels to measure consistently higher proton fluence than via Cu monitor channels, by 5--8\%.
-If Al monitors are used in conjunction with silicone-based tapes, even with subtraction of excess \ce{^{22}Na} activities, a systematically enhanced fluence may be determined, leading to cross sections reported with inaccurately diminished magnitude.
-Furthermore, since data for monitor reactions are often self-referencing, the propagated impact of this systematic enhancement in fluence may have far-reaching consequences for both medical isotope production, as well as for  the evaluated nuclear data libraries, which use these proton activation experiments as input.
-
-% First off, at the next planned stack irradiation at IPF, we would strongly encourage that a Kapton "blank" (no foil in the packet) be irradiated to confirm this.
-We intend to do the same for our next proton irradiation at LBL.
-% 
-% We would highly encourage people to be careful about the small details, notably using a silicone-based adhesive for any future Al monitor foils.
-This has potentially far-reaching consequences, unless a non-silicon-based Kapton (such as the acrylic adhesive versions) is instead used.
-
-% \comment{Make sure to comment on comparison with EMPIRE / TALYS  / TENDL here, after Amanda finishes modeling work.}
-
-% In this work
-As mentioned before, cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
-This, in turn, offers the opportunity to 
-% use these data to gain insight into 
-gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
-The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
-The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
-The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
-% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
-% \cite{add_level_density_models_here}. 
-The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
-% \cite{add_level_density_models_here}.
-The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
-All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-% \def\arraystretch{1.5}
-\begin{table}
- \caption{Default settings for the reactions codes}
- \label{tab:defaults}
- \resizebox{\textwidth}{!}{%
-\begin{tabular}{ c c c c}
-
- \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
- EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
- TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
-
-\end{tabular}
-}
-\end{table}
-
-% The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
-% Only total channel residual 
-Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
-% that have only one reaction channel, and that are 
-and at least 1\% of the total reaction cross section.
-% are discussed in detail. 
-% Residual production
-Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
-% the compound portion of the cross section
-being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
-% Some residuals, such as 
-Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
-% Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
-% Very small channels, 
-We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
-% are excluded because the modeling of their cross sections is 
-because their behavior is extremely sensitive  to  more dominant  channels.
-The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
-
-The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70 MeV}, is well within the compound regime for the entire energy region of this experiment.
-The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
-The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50 MeV, and the data clearly show the full rise, peak, and fall of the compound cross section.
-In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011\cite{Titarenko2011}.
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/86Y.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
- \label{fig:86Y}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:90Mo}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:90Nb}
-\end{figure}
-
-In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
-For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
-For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
-
-The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
-For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
-The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
-\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
-
-The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
-TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
-EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
-
-% \section{Discussion}
-
-% \comment{Feel free to expand / suggest / add other language describing medical radionuclide applications, or radiochemical separations here.}
-
-% XXXXXX
-
-% \comment{Placeholder to reserve space for pre-equilibrium / spin discussion.}
-
- \section{Conclusions}
-
-We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
-Nearly all cross sections have been reported with higher precision than previous measurements.
-We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
-We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
+% \linenumbers
+
+\input{./nb_body_text}
 
@@
 
-\section{Decay data} \label{data}
-% 
-% % \begin{longtable}{|c|c|c|c|c|} 
-% % \caption{My caption}
-% % \label{tab:dummy}
-% % % \begin{tabular}{|c|c|c|c|c|}
-% %    \hline
-% %  
-% % \end{longtable}
-% Table of decay data  for observed gamma-rays. 
-The   lifetimes and gamma-ray branching ratios  listed in these tables were used for all calculations of measured cross sections reported in this work, and have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain  \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
-
-% \comment{I had to remove about 30 of the lines I used from this table (removing the weakest lines in nuclides with even more lines than shown here, but never removing lines in nuclides with only 2 or less), as even splitting the data into 2 tables created tables too large to fit on a single page.
-My purpose here was 1) to show that I used multiple lines to quantify each nuclide (increasing confidence in results), and 2) to list all the used \ce{^{90}Mo} lines, since they form the basis of it as a monitor.
-Is this good as is, or should it be pared down even more?}
-
-% Preview source code for paragraph 0
-
-\begin{table}[ht]
-\centering
-\caption{Decay data for gamma-rays observed in \ce{^{nat}Al}(p,x) and \ce{^{nat}Cu}(p,x).}
-\label{tab:nudat_table_monitors}
-\begin{tabular}{@{}llll@{}}
-\toprule
-% \begin{tabular}{|c|c|c|c|}
-% \hline 
-Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
-\midrule
-\ce{^{22}Na} & 2.6018(22) y & 1274.537 & 99.940(14)\\
-
-\ce{^{24}Na} & 14.997(12) h & 1368.626 & 99.9936(15)\\
-
-\ce{^{51}Cr} & 27.704(3) d & 320.0824 & 9.910(10)\\
-
-\ce{^{52m}Mn} & 21.1(2) m & 1434.0600 & 98.2(5)\\
-
-\ce{^{52}Mn} & 5.591(3) d & 744.233 & 90.0(12)\\
-
- & 5.591(3) d & 935.544 & 94.5(13)\\
-
- & 5.591(3) d & 1246.278 & 4.21(7)\\
-
- & 5.591(3) d & 1434.092 & 100.0(14)\\
-
-\ce{^{54}Mn} & 312.20(20) & 834.848 & 99.9760(10)\\
-
-\ce{^{55}Co} & 17.53(3) h & 477.2 & 20.2(17)\\
-
- & 17.53(3) h & 931.1 & 75.0(35)\\
-
- & 17.53(3) h & 1316.6 & 7.1(3)\\
-
- & 17.53(3) h & 1408.5 & 16.9(8)\\
-
-\ce{^{56}Ni} & 6.075(10) d & 158.38 & 98.8(10)\\
-
- & 6.075(10) d & 269.50 & 36.5(8)\\
-
- & 6.075(10) d & 480.44 & 36.5(8)\\
-
- & 6.075(10) d & 749.95 & 49.5(12)\\
-
- & 6.075(10) d & 811.85 & 86.0(9)\\
-
- & 6.075(10) d & 1561.80 & 14.0(6)\\
-
-\ce{^{56}Co} & 77.236(26) d & 846.770 & 99.9399(2)\\
-
-%  & 77.236(26) d & 977.372 & 1.421(6)\\
-
- & 77.236(26) d & 1037.843 & 14.05(4)\\
-
- & 77.236(26) d & 1238.288 & 66.46(12)\\
-
- & 77.236(26) d & 1360.212 & 4.283(12)\\
-
- & 77.236(26) d & 1771.357 & 15.41(6)\\
-
-\ce{^{57}Ni} & 35.60(6) h & 127.164 & 16.7(5)\\
-
- & 35.60(6) h & 1377.63 & 81.7(24)\\
-
- & 35.60(6) h & 1757.55 & 5.75(20)\\
-
- & 35.60(6) h & 1919.52 & 12.3(4)\\
-
-\ce{^{57}Co} & 271.74(6) d & 122.06065 & 85.60(17)\\
-
- & 271.74(6) d & 136.47356 & 10.68(8)\\
-
-\ce{^{58}Co} & 70.86(6) d & 810.7593 & 99.450(10)\\
-
- & 70.86(6) d & 863.951 & 0.686(10)\\
-
-%  & 70.86(6) d & 1674.725 & 0.517(10)\\
-
-\ce{^{59}Fe} & 44.495(9) d & 1099.245 & 56.5(18)\\
-
- & 44.495(9) d & 1291.590 & 43.2(14)\\
-
-\ce{^{60}Co} & 5.2714(5) y & 1173.228 & 99.85(3)\\
-
- & 5.2714(5) y & 1332.492 & 99.9826(6)\\
-
-\ce{^{61}Cu} & 3.339(8) h & 282.956 & 12.2(2.2)\\
-
- & 3.339(8) h & 373.050 & 2.1(4)\\
-
-%  & 3.339(8) h & 588.605 & 1.17(21)\\
-
- & 3.339(8) h & 656.008 & 10.8(20)\\
-
- & 3.339(8) h & 1185.234 & 3.7(7)\\
-
-\ce{^{62}Zn} & 9.193(15) h & 243.36 & 2.52(23)\\
-
- & 9.193(15) h & 246.95 & 1.90(18)\\
-
- & 9.193(15) h & 260.43 & 1.35(13)\\
-
-%  & 9.193(15) h & 304.88 & 0.29(3)\\
-
-%  & 9.193(15) h & 349.60 & 0.45(4)\\
-
- & 9.193(15) h & 394.03 & 2.24(17)\\
-
- & 9.193(15) h & 548.35 & 15.3(14)\\
-
- & 9.193(15) h & 596.56 & 26.0(20)\\
-
-%  & 9.193(15) h & 637.41 & 0.25(3)\\
-
-\ce{^{64}Cu} & 12.701(2) h & 1345.77 & 0.475(11)\\
-
-\ce{^{65}Zn} & 243.93(9) d & 1115.539 & 50.04(10)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\centering
-\caption{Decay data for gamma-rays observed in \ce{^{nat}Nb}(p,x).}
-\label{tab:nudat_table_nb}
-\begin{tabular}{@{}llll@{}}
-\toprule
-% \begin{tabular}{|c|c|c|c|}
-% \hline 
-Nuclide & Half-life & E$_\gamma$ (keV) & I$_\gamma$ (\%)\\
-\midrule
-\ce{^{82m}Rb} & 6.472(6) h & 554.35 & 62.4(9)\\
-
- & 6.472(6) h & 619.11 & 37.98(9)\\
-
-%  & 6.472(6) h & 698.37 & 26.3(7)\\
-
- & 6.472(6) h & 776.52 & 84.39(21)\\
-
- & 6.472(6) h & 1044.08 & 32.07(8)\\
-
-%  & 6.472(6) h & 1317.43 & 23.7(6)\\
-
-\ce{^{83}Sr} & 32.41(3) h & 418.37 & 4.2(3)\\
-
- & 32.41(3) h & 762.65 & 26.7(22)\\
-
-\ce{^{85m}Y} & 4.86(13) h & 231.7 & 22.8(22)\\
-
-\ce{^{85}Y} & 2.68(5) h & 231.65 & 84(9)\\
-
- & 2.68(5) h & 913.89 & 9.0(9)\\
-
-\ce{^{86}Zr} & 16.5(1) h & 242.8 & 95.84(2)\\
-
- & 16.5(1) h & 612.0 & 5.8(3)\\
-
-% \ce{^{86}Y} & 14.74(2) h & 187.87 & 1.26(4)\\
-\ce{^{86}Y}  & 14.74(2) h & 443.13 & 16.9(5)\\
-
-%  & 14.74(2) h & 190.80 & 1.01(3)\\
-
-%  & 14.74(2) h & 307.00 & 3.47(8)\\
-
-%  & 14.74(2) h & 443.13 & 16.9(5)\\
-
-%  & 14.74(2) h & 580.57 & 4.78(14)\\
-
-%  & 14.74(2) h & 608.29 & 2.01(15)\\
-
- & 14.74(2) h & 627.72 & 32.6(1)\\
-
-%  & 14.74(2) h & 703.33 & 15.4(4)\\
-
-%  & 14.74(2) h & 709.90 & 2.62(8)\\
-
-%  & 14.74(2) h & 767.63 & 2.4(3)\\
-
-%  & 14.74(2) h & 835.67 & 4.4(6)\\
-
-%  & 14.74(2) h & 1024.04 & 3.79(17)\\
-
- & 14.74(2) h & 1076.63 & 82.5(4)\\
-
- & 14.74(2) h & 1153.05 & 30.5(9)\\
-
-%  & 14.74(2) h & 1163.03 & 1.18(4)\\
-%  
-%  & 14.74(2) h & 1253.11 & 1.53(5)\\
-
-%  & 14.74(2) h & 1349.15 & 2.95(9)\\
-
- & 14.74(2) h & 1854.38 & 17.2(5)\\
-
- & 14.74(2) h & 1920.72 & 20.8(7)\\
-
-\ce{^{87}Zr} & 1.68(1) h & 380.79 & 62.79(10)\\
-
- & 1.68(1) h & 1227.0 & 2.80(4)\\
-
-\ce{^{87m}Y} & 13.37(1) h & 380.79 & 78.05(8)\\
-
-\ce{^{87}Y} & 79.8(3) h & 388.5276 & 82.2(7)\\
-
- & 79.8(3) h & 484.805 & 89.8(9)\\
-
-\ce{^{88}Zr} & 83.4(3) d & 392.87 & 97.29(14)\\
-
-\ce{^{88}Y} & 106.627(21) d & 898.042 & 93.7(3)\\
-
- & 106.627(21) d & 1836.063 & 99.2(3)\\
-
-\ce{^{89m}Nb} & 66(2) m & 588.0 & 95.57(13)\\
-
-\ce{^{89}Nb} & 2.03(7) h & 1511.4 & 1.9(4)\\
-
- & 2.03(7) h & 1627.2 & 3.5(7)\\
-
- & 2.03(7) h & 1833.4 & 3.3(7)\\
-
-\ce{^{89}Zr} & 78.41(12) h & 909.15 & 99.04(3)\\
-
- & 78.41(12) h & 1713.0 & 0.745(13)\\
-
-%  & 78.41(12) h & 1744.5 & 0.123(4)\\
-
-\ce{^{90}Mo} & 5.56(9) h & 122.370 & 64(3)\\
-
- & 5.56(9) h & 162.93 & 6.0(6)\\
-
- & 5.56(9) h & 203.13 & 6.4(6)\\
-
- & 5.56(9) h & 257.34 & 78(4)\\
-
- & 5.56(9) h & 323.20 & 6.3(6)\\
-
- & 5.56(9) h & 472.2 & 1.42(16)\\
-
- & 5.56(9) h & 941.5 & 5.5(7)\\
-
-\ce{^{90}Nb} & 14.6(5) h & 132.716 & 4.13(4)\\
-
- & 14.6(5) h & 141.178 & 66.8(7)\\
-
-%  & 14.6(5) h & 890.64 & 1.80(4)\\
-
- & 14.6(5) h & 1611.76 & 2.38(7)\\
-
-%  & 14.6(5) h & 1913.194 & 1.280(17)\\
-
-\ce{^{91m}Nb} & 60.86(22) d & 104.62 & 0.574(1)\\
-
- & 60.86(22) d & 1204.67 & 2.0(3)\\
-
-\ce{^{92m}Nb} & 10.15(2) d & 912.6 & 1.78(10)\\
-
- & 10.15(2) d & 934.44 & 99.15(4)\\
-
-\ce{^{93m}Mo} & 6.85(7) d & 263.049 & 57.4(11)\\
-
- & 6.85(7) d & 684.693 & 99.9(8)\\
-
- & 6.85(7) d & 1477.138 & 99.1(11)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-% 
-% 
-\section{Measured excitation functions} \label{fit_figures}
-
-Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes CoH-3.5.1, EMPIRE-3.2.3, and TALYS-1.8 \cite{KAWANO2010,Herman2007,Koning2012}.
-
-% \comment{Add in CoH model output from Toshihiko to all plots}
-
-% \comment{Fix a few figure labels (c/i) based on Jon;s email}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/51Cr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:51Cr}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/52Mn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:52Mn}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/52gMn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:52gMn}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/52mMn.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:52mMn}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/54Mn.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:54Mn}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/55Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:55Co}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p1}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/56Ni.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:56Ni}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/57Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:57Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/57Ni.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:57Ni}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58Co.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:58Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58gCo.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:58gCo}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/58mCo.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:58mCo}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p2}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/59Fe.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:59Fe}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/60Co.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:60Co}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/61Cu.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:61Cu}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/64Cu.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:64Cu}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/82mRb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:82mRb}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/83Sr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:83Sr}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p3}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/85gY.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:85gY}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85mY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85mY}
-    \end{subfigure}
-%      \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/86Y.pdf}{50}
-% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-%                  \refstepcounter{subfigure}\label{fig:86Y}
-%     \end{subfigure}
-%     \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/86Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:86Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87Y.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87Y}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87gY}
-    \end{subfigure}
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p4}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-%      \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\textwidth]{./figures/target2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/87gY.pdf}{50}
-% %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-%                  \refstepcounter{subfigure}\label{fig:87gY}
-%     \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/87mY.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:87mY}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/87Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/88Y.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Y}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/88Zr.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:88Zr}
-    \end{subfigure}%
-    \\
-         \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89Nb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:89Nb}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:89gNb}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p8}
-\end{figure*}
-
-\begin{figure*}
-    \centering    
-%          \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-%         \subfigimg[width=\linewidth]{}{./figures/89gNb.pdf}{50}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-%          \refstepcounter{subfigure}\label{fig:89gNb}
-%     \end{subfigure}%
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/89Zr.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:89Zr}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:91mNb}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:92mNb}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:93mMo}
-    \end{subfigure}%
-%     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-     \label{fig:xs_curves_p7}
-\end{figure*}
-
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[t]{0.495\textwidth}
-%         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-%          \refstepcounter{subfigure}\label{fig:93mMo}
-%     \end{subfigure}%
-% %      \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% % %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-% %         \subfigimg[width=\linewidth]{}{./figures/91mNb.pdf}{50}
-% % %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-% %          \refstepcounter{subfigure}\label{fig:91mNb}
-% %     \end{subfigure}%
-% %     \\
-% %     \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\textwidth]{./figures/target2.png}
-% %         \subfigimg[width=\linewidth]{}{./figures/92mNb.pdf}{50}
-% % %         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-% %                  \refstepcounter{subfigure}\label{fig:92mNb}
-% %     \end{subfigure}
-% %      \begin{subfigure}[t]{0.495\textwidth}
-% %         \centering
-% % %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \subfigimg[width=\linewidth]{}{./figures/93mMo.pdf}{50}
-% % %         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-% %         \refstepcounter{subfigure} \label{fig:93mMo}
-% %     \end{subfigure}%
-% %     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-%      \label{fig:xs_curves_p5}
-% \end{figure*}
-
-% 
-% 
-\section{Measured isomer-to-ground state branching ratios } \label{ibr_figures}
-
-Plots of the isomer-to-ground state ratios measured in this work are presented here, in comparison with literature data and reaction modeling codes \cite{MICHEL1997153,Ditroi2008,Titarenko2011,Graves2016}.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/52Mn_IBR.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         \refstepcounter{subfigure}\label{fig:52Mn_IBR}
-    \end{subfigure}%
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=\linewidth]{}{./figures/58Co_IBR.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         \refstepcounter{subfigure}\label{fig:58Co_IBR}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/85Y_IBR.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:85Y_IBR}
-    \end{subfigure}
-     \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \subfigimg[width=\linewidth]{}{./figures/87Y_IBR.pdf}{50}
-%         \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
-        \refstepcounter{subfigure} \label{fig:87Y_IBR}
-    \end{subfigure}%
-    \\
-    \begin{subfigure}[t]{0.495\textwidth}
-        \centering
-%         \includegraphics[width=\textwidth]{./figures/target2.png}
-        \subfigimg[width=\linewidth]{}{./figures/89Nb_IBR.pdf}{50}
-%         \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
-                 \refstepcounter{subfigure}\label{fig:89Nb_IBR}
-    \end{subfigure}
-     \label{fig:ibr_curves}
-\end{figure*}
+\input{./nb_appendix_text}
 
@@
 \bibliographystyle{elsarticle-num}
+% ``Overfull \hbox in .bbl'' message fixed by commenting out ''write.url'' in /usr/share/texlive/texmf-dist/bibtex/bst/elsarticle/elsarticle-num.bst for affected entry types (likely, 'article' and 'book', all but 'phdthesis')
 % \bibliographystyle{apsrev4-1}

### 2018-04-05 First_np_Paper/np_body_text.tex
Updated section labels, to avoid conflicts in dissertation.

@@
-\section{Introduction} \label{sec:intro}
+\section{Introduction} \label{sec:intro_np}
 
@@
 
-\section{Experiment}\label{sec:experiment}
+\section{Experiment}\label{sec:experiment_np}
 
@@
 
-\subsection{Measurement of induced activities}\label{sec:spectroscopy}
+\subsection{Measurement of induced activities}\label{sec:spectroscopy_np}
 
@@
 
-\subsection{Calculation of measured cross sections}\label{sec:calcs_sec}
+\subsection{Calculation of measured cross sections}\label{sec:calcs_sec_np}
 
@@
 
-Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for the production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
+Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for  production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
 The weighted average of the measurements give   49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) and 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26 $\pm$  0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.

### 2018-04-05 nb_px_paper/nb_body_text.tex
Fixed Nb(p,x) fit of appendix tables and figures.  Fixed usage of micro symbol to avoid breaking typsetting.

@@
 
-Accurate cross section measurements using  activation methods benefit from well-characterized monitor reactions.  
+Accurate cross section measurements using  activation methods benefit from well- characterized monitor reactions.  
 Currently there is 
@@
 One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
-Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
+Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 \mmicro m.  
 \ce{^{90}Mo} also has 
@@
 % For targets, a
-A series of nominal 25 \micro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \micro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \micro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
+A series of nominal 25 \mmicro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \mmicro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \mmicro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
 Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
@@
 % , along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \micro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \micro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
 The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
@@
 This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
-The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
+The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \mmicro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
 The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
@@
 \caption{Specifications of the  target stack design in the present work.
-The proton beam enters the stack upstream of the 249.8 \micro m SS profile monitor, and is transported through the stack in the order presented here.
+The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here.
 The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
@@
 Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
-SS profile monitor & 249.8 \micro m         & 194.56                                      & 0.29                      \\
-Al-1               & 25.0 \micro m          & 6.52                                        & 0.72                      \\
-Cu-1               & 61.3 \micro m          & 53.74                                       & 0.15                      \\
-Nb-1               & 30.0 \micro m          & 23.21                                       & 0.17                      \\
+SS profile monitor & 249.8 \mmicro m         & 194.56                                      & 0.29                      \\
+Al-1               & 25.0 \mmicro m          & 6.52                                        & 0.72                      \\
+Cu-1               & 61.3 \mmicro m          & 53.74                                       & 0.15                      \\
+Nb-1               & 30.0 \mmicro m          & 23.21                                       & 0.17                      \\
 Al Degrader 01     & 4.96 mm           & -                                            & -                          \\
-Al-2               & 25.5 \micro m          & 6.48                                        & 0.36                      \\
-Cu-2               & 61.8 \micro m          & 53.85                                       & 0.17                      \\
-Nb-2               & 30.8 \micro m          & 22.91                                       & 0.17                      \\
+Al-2               & 25.5 \mmicro m          & 6.48                                        & 0.36                      \\
+Cu-2               & 61.8 \mmicro m          & 53.85                                       & 0.17                      \\
+Nb-2               & 30.8 \mmicro m          & 22.91                                       & 0.17                      \\
 Al Degrader 02     & 4.55 mm           & -                                            & -                          \\
-Al-3               & 25.8 \micro m          & 6.47                                        & 0.31                      \\
-Cu-3               & 61.5 \micro m          & 53.98                                       & 0.11                      \\
-Nb-3               & 31.0 \micro m          & 22.91                                       & 0.24                      \\
+Al-3               & 25.8 \mmicro m          & 6.47                                        & 0.31                      \\
+Cu-3               & 61.5 \mmicro m          & 53.98                                       & 0.11                      \\
+Nb-3               & 31.0 \mmicro m          & 22.91                                       & 0.24                      \\
 Al Degrader 03     & 3.52 mm           & -                                            & -                          \\
-Al-4               & 26.3 \micro m          & 6.51                                        & 0.41                      \\
-Cu-4               & 61.3 \micro m          & 53.46                                       & 0.22                      \\
-Nb-4               & 30.8 \micro m          & 22.55                                       & 0.25                      \\
+Al-4               & 26.3 \mmicro m          & 6.51                                        & 0.41                      \\
+Cu-4               & 61.3 \mmicro m          & 53.46                                       & 0.22                      \\
+Nb-4               & 30.8 \mmicro m          & 22.55                                       & 0.25                      \\
 Al Degrader 04     & 3.47 mm           & -                                            & -                          \\
-Al-5               & 26.5 \micro m          & 6.48                                        & 0.29                      \\
-Cu-5               & 61.5 \micro m          & 53.57                                       & 0.11                      \\
-Nb-5               & 30.8 \micro m          & 22.11                                       & 0.25                      \\
+Al-5               & 26.5 \mmicro m          & 6.48                                        & 0.29                      \\
+Cu-5               & 61.5 \mmicro m          & 53.57                                       & 0.11                      \\
+Nb-5               & 30.8 \mmicro m          & 22.11                                       & 0.25                      \\
 Al Degrader 05     & 3.46 mm           & -                                            & -                          \\
-Al-6               & 26.3 \micro m          & 6.48                                        & 0.62                      \\
-Cu-6               & 62.0 \micro m          & 53.84                                       & 0.32                      \\
-Nb-6               & 31.3 \micro m          & 22.12                                       & 0.13                      \\
-SS profile monitor & 124.4 \micro m         & 101.34                                      & 0.23                      \\ \bottomrule
+Al-6               & 26.3 \mmicro m          & 6.48                                        & 0.62                      \\
+Cu-6               & 62.0 \mmicro m          & 53.84                                       & 0.32                      \\
+Nb-6               & 31.3 \mmicro m          & 22.12                                       & 0.13                      \\
+SS profile monitor & 124.4 \mmicro m         & 101.34                                      & 0.23                      \\ \bottomrule
 \end{tabular}
@@
 \small
+\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lllllll@{}}
@@
 \end{tabular}
+}
 \end{table}
@@
 
-Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
 This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.

### 2018-04-05 fe_px_paper/fe_body_text.tex
Broke Fe(p,x) paper up into container and text files, following same conventions as the Nb and HFNG restructuring.

\section{\label{sec:level1}First-level heading}

This sample document demonstrates proper use of REV\TeX~4.1 (and
\LaTeXe) in mansucripts prepared for submission to APS
journals. Further information can be found in the REV\TeX~4.1
documentation included in the distribution or available at
\url{http://authors.aps.org/revtex4/}.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended. Note that top-level section headings are
automatically uppercased. If a specific letter or word should appear in
lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
in the word ``via'' above.

\subsection{\label{sec:level2}Second-level heading: Formatting}

This file may be formatted in either the \texttt{preprint} or
\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
Either format may be used for submission purposes. \texttt{letter} sized paper should
be used when submitting to APS journals.

\subsubsection{Wide text (A level-3 head)}
The \texttt{widetext} environment will make the text the width of the
full page, as on page~\pageref{eq:wideeq}. (Note the use the
\verb+\pageref{#1}+ command to refer to the page number.) 
\paragraph{Note (Fourth-level head is run in)}
The width-changing commands only take effect in two-column formatting. 
There is no effect if text is in a single column.

\subsection{\label{sec:citeref}Citations and References}
A citation in text uses the command \verb+\cite{#1}+ or
\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
An entry in the bibliography is a reference to another document.

\subsubsection{Citations}
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
the entire repertoire of commands in that package are available for your document;
see the \verb+natbib+ documentation for further details. Please note that
REV\TeX\ requires version 8.31a or later of \verb+natbib+.

\paragraph{Syntax}
The argument of \verb+\cite+ may be a single \emph{key}, 
or may consist of a comma-separated list of keys.
The citation \emph{key} may contain 
letters, numbers, the dash (-) character, or the period (.) character. 
New with natbib 8.3 is an extension to the syntax that allows for 
a star (*) form and two optional arguments on the citation key itself.
The syntax of the \verb+\cite+ command is thus (informally stated)
\begin{quotation}\flushleft\leftskip1em
\verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
\end{quotation}\noindent
where \emph{optarg+key} signifies 
\begin{quotation}\flushleft\leftskip1em
\emph{key}, or\\
\texttt{*}\emph{key}, or\\
\texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
\texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
\end{quotation}\noindent
where \emph{pre} and \emph{post} is whatever text you wish to place 
at the beginning and end, respectively, of the bibliographic reference
(see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
(Keep in mind that no automatic space or punctuation is applied.)
It is highly recommended that you put the entire \emph{pre} or \emph{post} portion 
within its own set of braces, for example: 
\verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.

The star (*) modifier to the \emph{key} signifies that the reference is to be 
merged with the previous reference into a single bibliographic entry, 
a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]). 
When references are merged in this way, they are separated by a semicolon instead of 
the period (full stop) that would otherwise appear.

\paragraph{Eliding repeated information}
When a reference is merged, some of its fields may be elided: for example, 
when the author matches that of the previous reference, it is omitted. 
If both author and journal match, both are omitted.
If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
as exemplified by Ref.~[\onlinecite{epr}]. 
These rules embody common editorial practice in APS and AIP journals and will only
be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.

\paragraph{The options of the cite command itself}
Please note that optional arguments to the \emph{key} change the reference in the bibliography, 
not the citation in the body of the document. 
For the latter, use the optional arguments of the \verb+\cite+ command itself:
\verb+\cite+ \texttt{*}\allowbreak
\texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
\texttt{[}\emph{post-cite}\texttt{]}\allowbreak
\verb+{+\emph{key-list}\verb+}+.

### 2018-04-06 nb_px_paper/nb_body_text.tex
Pushing fix for missing /mmicro macro?

@@
 % While the reactions and mass region being explored in this work differ from the recent work of Graves \etal, much of the analysis described in the present work 
-The work described herein follows the  methods established by Graves \etal\ for the measurement of cross sections in stacked target irradiations   \cite{Graves2016}.
+The work described herein follows the  methods established by Graves \etal\ 
+% for the measurement of cross sections in stacked target irradiations   
+for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Graves2016}.
 
@@
 
-Using this variance minimized degrader density, the final incident proton energy energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the six irradiated Nb foils in \autoref{fig:Nb_ptallies}.
+Using this variance minimized degrader density, the final incident proton  energy distributions $\frac{d\phi}{dE}$ from MCNP6 simulation are shown for the six irradiated Nb foils in \autoref{fig:Nb_ptallies}.
 As expected, the energy distribution becomes increasingly more broadened at the lower energy positions, as a result of the beam energy degradation.

### 2018-04-06 nb_px_paper/nb_body_text.tex
Merging minor typographical changes from Eva's comments.

@@
 % of the 
-non-medical radionuclides with commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
+non-medical radionuclides with commercial value, such as  \ce{^{22}Na}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
 % \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?
@@
 % with high intensities,  
-which can be used to uniquely identify it during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
+which can be used for unique identification during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
 % The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics.
@@
 % needed to  correct for decay losses, 
-as well as well-characterized decay gamma-ray intensities.
+and well-characterized decay gamma-ray intensities.
 % In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
@@
  \caption{\label{fig:target_stack}Photograph of the assembled IPF target stack, before the stack's o-ring lid was sealed in place.
-The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via robotic manipulators in the IPF hot cell.
+The baling wire handles affixed to each bunch of Al+Cu+Nb foils are visible in each energy position, to facilitate removal of activated foils via  manipulators in the IPF hot cell.
 The circular Inconel beam entrance aperture is visible in the bottom center of the photograph.
@@
  % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
- \caption{A gamma spectrum, collected from an activated Nb foil at approximately 80 MeV.
+ \caption{A gamma spectrum collected from an activated Nb foil at approximately 80 MeV.
 While the majority of observed reaction products are visible in this spectrum,  the \ce{^{90}Mo} decay lines, which form the basis of the \ce{^{93}Nb}(p,x)\ce{^{90}Mo} monitor reaction, are high in intensity and clearly isolated from surrounding peaks.}
@@
 % (which combines both Al- and Si-based production routes), 
-relative to the expected EoB activities for each reaction channel.
-This is presented in \autoref{fig:Na_activity_compare}.
+relative to the expected EoB activities for each reaction channel 
+% This is presented in 
+(\autoref{fig:Na_activity_compare}).
 Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na},
@@
 % In principle, it would be possible  to 
-we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the apparent \ce{^{22,24}Na}  activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the Al monitor reactions.
-The results of this  may be seen in \autoref{fig:na_subtraction}.
+we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the apparent \ce{^{22,24}Na}  activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the Al monitor reactions, shown
+% The results of this  may be seen 
+in \autoref{fig:na_subtraction}.
 Following subtraction, the \ce{^{22,24}Na} fluences become more consistent with other monitor reaction channels, 
@@
 
-An enhanced version of the final \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction fluences may be seen in \autoref{fig:fluence_plot}.
+An enhanced version of the final \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction fluences is shown in \autoref{fig:fluence_plot}.
 % , which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
@@
 \small
-\resizebox{\textwidth}{!}{%
+% Disable next line for journal submission
+% \resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lllllll@{}}
@@
 \end{tabular}
-}
+% }
 \end{table}
@@
 
-The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70 MeV}, is well within the compound regime for the entire energy region of this experiment.
+The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70 MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
 The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
-The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50 MeV, and the data clearly show the full rise, peak, and fall of the compound cross section.
-In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011\cite{Titarenko2011}.
+The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50 MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
+In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011 \cite{Titarenko2011}.
+
+The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
+TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
+EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
 
@@
 
-The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
-TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
-EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
-
 % \section{Discussion}

### 2018-04-16 First_np_Paper/np_abstract_text.tex
Belatedly added the final journal edits to my local draft.

@@
 Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
-The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26 $\pm$  0.82 mb.
+The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3\,$\pm$\,2.6 mb (relative to \ce{^{113}In}) or 46.4\,$\pm$\,1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26\,$\pm$\, 0.82 mb.
 The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.

### 2018-04-16 First_np_Paper/np_body_text.tex
Enlarged half-width figure axis labels, for inclusion in dissertation.

@@
  While reactors produce copious quantities of neutrons, their energy spectra are often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
- Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
+ Similarly, while the higher energy 14--15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides.
 DT generators may also often be limited by the restricted use of tritium at many institutions.
 
-In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2-3 MeV, is ideally suited to (n,p) radionuclide production.
+In contrast,  the neutron spectrum from a DD reaction, which ranges from approximately 2--3 MeV, is ideally suited to (n,p) radionuclide production.
 However, the lower achievable flux from these generators limits their production capabilities.
- An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2-3 MeV DD energy range.
+ An additional complication is the relative paucity of high-quality, consistent cross section data for neutrons in the 2--3 MeV DD energy range.
 
@@
 
-The present work features a pair of cross section measurements for the production of two emerging non-standard medical radionuclides: the positron emitter \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and the single - photon emission computed tomography (SPECT) tracer \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The present work features a pair of cross section measurements for the production of two emerging non-standard medical radionuclides: the positron emitter \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and the single-photon emission computed tomography (SPECT) tracer \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 \ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
@@
   \autoref{tab:foil_specs} lists physical characteristics of each foil for the various irradiations.
-In each experiment, the co-loaded foils were irradiated for 3 hours at nominal operating conditions of 1.3 mA and 100 kV.
+In each experiment, the co-loaded foils were irradiated for 3 h at nominal operating conditions of 1.3 mA and 100 kV.
  After irradiation, the foils were removed and placed in front of an appropriate High-Purity Germanium (HPGe) gamma-ray detector and time-dependent decay gamma-ray spectra were collected.
@@
         \includegraphics[height=2.5in]{./figures/holder.pdf}
-        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
+        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG.}
         \label{fig:holder_a}
@@
 
-  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\   \hline
+  &  & & &  1.02 \pm 0.01 & 9.89 \pm 0.15 & 0.542 \pm 0.005  \\  \\  %\hline
 
-\multirows{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirows{2}*{\minitab[c]{99.999\%   }} & \multirows{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirows{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\
+\multirows{2}*{\minitab[c]{$^\text{nat}$Ti}}      & \multirows{2}*{\minitab[c]{99.999\%   }} & \multirows{2}*{\minitab[c]{\ce{^{47}Ti} (7.44\%)   }} & \multirows{2}*{\minitab[c]{434.7}}                                                              &   1.16 \pm 0.02 &  9.93 \pm 0.04  & 0.337 \pm 0.005 \\ %\vspace{0.5em} %\hline
 
-  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\  \hline
+  &  & & &  1.15 \pm 0.02 & 9.94 \pm 0.03 & 0.337 \pm 0.005  \\ \\ %\hline
 
-\multirows{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirows{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirows{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirows{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\
+\multirows{5}*{\minitab[c]{$^\text{nat}$In}}      & \multirows{5}*{\minitab[c]{\textgreater 99.999\%}} & \multirows{5}*{\minitab[c]{\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)}} & \multirows{5}*{\minitab[c]{317.6}}                                                              & 0.49 \pm 0.02*  & 9.75 \pm 0.09* & 0.248 \pm 0.005* \\  %\vspace{0.5em} %\hline
 
@@
 % 2.18 to 2.78 MeV  (Liskien thick-target coefficient corrections to above)
-2.18 to 2.78 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
+2.18 to 2.78 MeV, over an angular range of 0--180\si{\degree}\ \degree\ in the lab frame-of-reference with respect to the incident deuteron beam.
 This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.
@@
 
-Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\degree)
+Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\si{\degree}\ \degree)
 % the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
@@
 This spectrum, peaked around 2.777 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
- As expected, the  production target is the dominant source of scatter - approximately 0.78\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.
+ As expected, the  production target is the dominant source of scatter --- approximately 0.78\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.
 
@@
 \label{tab:decay_props}
-\begin{tabular}{@{}cccc@{}}
+\begin{tabular}{@{}llll@{}}
 \toprule
 Nuclide & \begin{tabular}[c]{@{}c@{}}Gamma-Ray \\ Energy (keV)\end{tabular} & Intensity (\%) & $t_{1/2}$        \\ \midrule
-\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2 $\pm$ 0.4        & 12.701 h   \\
-\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3 $\pm$ 0.4      & 3.3492 d   \\
-\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94 $\pm$ 0.17    & 99.476 m  \\
-\ce{^{115m}In} \cite{Hansen1974} & 336.241                                                           & 45.9 $\pm$ 0.1      & 4.486 h    \\
-\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2 $\pm$ 0.4      & 54.29 m   \\ \bottomrule
+\ce{^{64}Cu} \cite{Singh2007}    & 511.0                                                             & 35.2\,$\pm$\,0.4        & 12.701 h   \\
+\ce{^{47}Sc} \cite{Burrows2007}    & 159.381                                                           & 68.3\,$\pm$\,0.4      & 3.3492 d   \\
+\ce{^{113m}In} \cite{Blachot2010a}  & 391.698                                                           & 64.94\,$\pm$\,0.17    & 99.476 m  \\
+\ce{^{115m}In} \cite{Hansen1974} & 336.241                                                           & 45.9\,$\pm$\,0.1      & 4.486 h    \\
+\ce{^{116m}In} \cite{Blachot2010}  & 416.90                                                            & 27.2\,$\pm$\,0.4      & 54.29 m   \\ \bottomrule
 \end{tabular}
@@
 For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 minute half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
-The foils were counted together again after approximately 4 hours of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
+This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 min half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
+The foils were counted together again after approximately 4 h of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
 % Example spectra for each production pathway can be seen in Figures \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
@@
 
-To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15 - 30 minute intervals.
+To verify that each peak corresponds to the assigned decay product, spectra were acquired in a sequence of 15--30 min intervals.
 The resulting time series displayed in Figures \ref{fig:decay_curves}a - \ref{fig:decay_curves}d allow the fitting of exponential decay functions for each nuclide and comparison of the measured half-life with literature values.
@@
     \caption{Decay curves used to verify photopeak transition assignment.
-(a) Decay curve for the isomeric transition of \ce{^{115m}In}, (b) decay curve for the isomeric transition of \ce{^{113m}In}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
+(a) Decay curve for the isomeric transition of \ce{^{115m}In} \cite{Hansen1974}, (b) decay curve for the isomeric transition of \ce{^{113m}In} \cite{Blachot2010a}, (c) decay curve for the $\beta^-$ decay of \ce{^{116}In} \cite{Blachot2010}, and (d) decay curve for the $\beta^+$ decay of \ce{^{64}Cu} \cite{Singh2007}.}
      \label{fig:decay_curves}
@@
 Counting Time, $t_c$ (s)               & 91188        & 54008       & 54002 & 86424    & 93631   \\ 
-Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665 $\pm$ 1490 & 76321 $\pm$ 275 & 39895 $\pm$ 201 & 2122 $\pm$ 55 & 55102 $\pm$ 268   \\ 
-Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382 $\pm$ 171    & 890 $\pm$ 40    & 3505 $\pm$ 54 &    \hrulefill       &  \hrulefill      \\ 
-Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055 $\pm$ 643   & 12852 $\pm$ 118 & 27164 $\pm$ 159 &    \hrulefill       &   \hrulefill     \\ 
-Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877 $\pm$ 83 & 5544 $\pm$ 257 \\ \bottomrule
+Photopeak Counts, 336 keV (\ce{^{115m}In}) & 113665\,$\pm$\,1490 & 76321\,$\pm$\,275 & 39895\,$\pm$\,201 & 2122\,$\pm$\,55 & 55102\,$\pm$\,268   \\ 
+Photopeak Counts, 391 keV (\ce{^{113m}In}) & 3382\,$\pm$\,171    & 890\,$\pm$\,40    & 3505\,$\pm$\,54 &    \hrulefill       &  \hrulefill      \\ 
+Photopeak Counts, 511 keV (\ce{^{64}Cu})   & 16055\,$\pm$\,643   & 12852\,$\pm$\,118 & 27164\,$\pm$\,159 &    \hrulefill       &   \hrulefill     \\ 
+Photopeak Counts, 159 keV (\ce{^{47}Sc})   &   \hrulefill            &    \hrulefill         &   \hrulefill    & 3877\,$\pm$\,83 & 5544\,$\pm$\,257 \\ \bottomrule
 \end{tabular}%
@@
  In order to determine this angle it is necessary to measure the lateral location of the beam with respect to the sample location.
- This centroid position of the beam was measured using a 3 x 3 array of 0.5 cm diameter indium foils.
+ This centroid position of the beam was measured using a 3 $\times$ 3 array of 0.5 cm diameter indium foils.
  The relative activity of these foils was then determined via post-irradiation counting of the \ce{^{115m}In} isomer ($t_{1/2}$ = 4.486 h) \cite{Blachot2012}.
@@
  Based on these values we are able to verify that the beam was indeed vertically centered on the middle of the zinc and titanium samples,  with a slight asymmetry of the neutron flux in the horizontal direction, accounted for in MCNP6 modeling of the energy-differential neutron flux.
-This small asymmetry likely contributes to the effective energy bin being lower than the 2.78 MeV expected for 0\degree\ neutron emission angle in \autoref{fig:scatt_angle}.
+This small asymmetry likely contributes to the effective energy bin being lower than the 2.78 MeV expected for 0\si{\degree}\ \degree\ neutron emission angle in \autoref{fig:scatt_angle}.
 
@@
 In addition to the \ce{^{115}In}(n,n')\ce{^{115m}In} reference cross section, the \ce{^{115}In}(n,$\gamma$)\ce{^{116m}In}  ($t_{1/2}$ = 54.29 min \cite{Blachot2010}) activity can be used to determine the  \ce{^{64}Zn}(n,p) and \ce{^{47}Ti}(n,p) cross section.
- The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately 2,000 times greater than at 2.7 MeV  \cite{Capote2012,zsolnay2012technical}.
+ The capture activity is potentially subject to contamination from lower energy, especially thermal, \enquote{room return} neutrons since the (n,$\gamma$) cross section at 25 meV is approximately 2000 times greater than at 2.7 MeV  \cite{Capote2012,zsolnay2012technical}.
 
@@
  However, the MCNP6 simulations shown in \autoref{fig:mcnp_flux} indicate that the difference in the flux that the two foils are subjected to is less than 1\%, negligible compared to other sources of systematic uncertainty.
- Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 hour and 99.476 minute half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, make indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
+ Other monitor foils could be used instead of indium, with \ce{^{58}Ni}(n,p)\ce{^{58}Co} (\ce{^{58}Co} $t_{1/2}$ = 70.86 d \cite{Nesaraja2010}) being one possible candidate, but the 4.486 h and 99.476 min half-lives of the \ce{^{115m}In} and \ce{^{113m}In} isomers \cite{Blachot2012,Blachot2010a}, respectively, make indium a better candidate for measuring the production of radionuclides with lifetimes much less than 71 days.
 The largest source of uncertainty in energy window arises from uncertainties in the actual dimension of the deuteron beam on the production target.
@@
 % h                                 & $\sigma$($E_n$ = 2.7645 MeV) (mb)                                                                     \\ \midrule
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{113}In}) & \begin{tabular}[c]{@{}c@{}}45.953 $\pm$ 3.351, \\ 46.493 $\pm$ 2.805, \\ 46.9 $\pm$ 3.189\end{tabular}  \\
-% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}49.716 $\pm$ 3.335, \\ 49.011 $\pm$ 2.698, \\ XXXX $\pm$ XXXXXX\end{tabular} \\
-% \ce{^{47}Ti}(n,p)\ce{^{47}Sc} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}25.901 $\pm$ 1.7089, \\ XXXXX $\pm$ XXXXX\end{tabular}                   \\ \bottomrule
+% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{113}In}) & \begin{tabular}[c]{@{}c@{}}45.953\,$\pm$\,3.351, \\ 46.493\,$\pm$\,2.805, \\ 46.9\,$\pm$\,3.189\end{tabular}  \\
+% \ce{^{64}Zn}(n,p)\ce{^{64}Cu} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}49.716\,$\pm$\,3.335, \\ 49.011\,$\pm$\,2.698, \\ XXXX\,$\pm$\,XXXXXX\end{tabular} \\
+% \ce{^{47}Ti}(n,p)\ce{^{47}Sc} (relative to \ce{^{115}In}) & \begin{tabular}[c]{@{}c@{}}25.901\,$\pm$\,1.7089, \\ XXXXX\,$\pm$\,XXXXX\end{tabular}                   \\ \bottomrule
 % \end{tabular}
@@
 Figures \ref{fig:sc_xs} and \ref{fig:cu_xs_zoom} present the determined cross sections for  production of  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu}  relative to literature data retrieved from EXFOR \cite{Otuka2014272,PhysRev.114.565,doi:10.1143/JPSJ.17.1215,paulsen1967cross,doi:10.1139/p72-336,Smith1975,King1979,Hussain1983,Ikeda1991,Shimizu2004543,PhysRev.126.271,Armitage1967,Ikeda1990,Senga2000,Shimizu2004975}.
-The weighted average of the measurements give   49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) and 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26 $\pm$  0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
+The weighted average of the measurements give   49.3\,$\pm$\,2.6 mb (relative to \ce{^{113}In}) and 46.4\,$\pm$\,1.7 mb (relative to \ce{^{115}In})   for \ce{^{64}Zn}(n,p)\ce{^{64}Cu},   and 26.26\,$\pm$\, 0.82 mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
 The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section measured in this work is consistent with  other literature results, but with a smaller uncertainty (\textless 5\%).
@@
 In this case, it is useful to introduce a neutron utilization factor ($\eta_x$).
-$\eta_x$ is the constant of proportionality between $R_n$, the neutron source output (in neutrons/second), and the saturation activity:
+$\eta_x$ is the constant of proportionality between $R_n$, the neutron source output (in neutrons/s), and the saturation activity:
 
@@
 
- \section{Conclusion and Future Work}
+ \section{Conclusion and future work}
 
@@
 The cross sections were measured with less than  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}.
-The measured values of  26.26 $\pm$  0.82 mb and  49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
+The measured values of  26.26\,$\pm$\, 0.82 mb and  49.3\,$\pm$\,2.6 mb (relative to \ce{^{113}In}) or 46.4\,$\pm$\,1.7 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements.
 
@@
 % In closing, we have measured the \ce{^{64}Cu}(n,p) and \ce{^{47}Ti}(n,p) cross sections for 2.765 MeV incident neutrons.
- It is worth noting that at the time of publication, the  HFNG is now operating at close to 10$^9$ n/sec, with
+ It is worth noting that at the time of publication, the  HFNG is now operating at close to 10$^9$ n/s, with
 a clear path towards 10$^{10}$.

### 2018-04-18 nb_px_paper/cover_letter.tex
Updated paper title for journal submission. Submitted this commit to NIM-B.

@@
 
-\begin{letter}{Editorial Board \\
+\begin{letter}{Dr. Mark Breese, or the Editorial Board \\
 Nuclear Instruments and Methods in Physics Research Section B: \\
@@
 
-\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40--90 MeV) on natural Nb}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.
+\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Excitation functions for (p,x) reactions of niobium (E$_{\text{p}}$ = 40--90 MeV):  development of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as an intermediate-energy proton monitor}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.
 This manuscript describes an original work conducted by myself, the first and corresponding author, along with my co-authors and collaborators Lee A.
@@
 If I may make one personal request, it would mean a great deal to me if the processing of this manuscript can be expedited in any way, to be able to get it to the referees as quickly as possible without any loss of integrity to the review process.
-I am in my last several months of my PhD studies, and if this manuscript is able to be accepted by 10 June 2018, I will be able to include it as part of my doctoral dissertation.
+I am in my last several months of my PhD studies, and if this manuscript is able to be accepted for the July 2018 issue of NIM B, I will be able to include it as part of my doctoral dissertation.
 Along with many rounds of revisions with my co-authors, we have put great effort into producing what we consider a manuscript of significant merit to the field, which provides an example of rigorous analysis and uncertainty quantification for cross section data with wide-ranging applications.

### 2018-04-18 nb_px_paper/arxiv/nb_body_text.tex
Made subdirectory for arXiv submission, modified manuscript source to accommodate the upload requirements.

--- 2018-04-06 nb_px_paper/nb_body_text.tex
@@
  \centering
- \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{./figures/IMG_1975.JPG}
+ \includegraphics[width=0.5\linewidth,clip=true,trim=13cm 0cm 3cm 6cm]{IMG_1975.JPG}
  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
@@
  \centering
- \includegraphics[width=6in]{./figures/sample_gspec.pdf}
+ \includegraphics[width=6in]{sample_gspec.pdf}
  % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
@@
  \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.5\linewidth]{./figures/variation_curve-crop.pdf}
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{variation_curve.pdf}
+ \includegraphics[width=0.5\linewidth]{variation_curve-crop.pdf}
 
@@
 %         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \subfigimg[width=0.5\textwidth]{a)}{./figures/336keV_curve_new.pdf}{50}
+% %         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \subfigimg[width=0.5\textwidth]{a)}{336keV_curve_new.pdf}{50}
 % %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 % %          
-%          \subfigimg[width=0.5\textwidth]{b)}{./figures/391keV_curve_new.pdf}{50}
+%          \subfigimg[width=0.5\textwidth]{b)}{391keV_curve_new.pdf}{50}
 % %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=0.5\textwidth]{b)}{./figures/after_minimization_plot.pdf}{50}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[scale=0.6]{391keV_curve2.png}
+        \subfigimg[width=0.5\textwidth]{b)}{after_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\linewidth]{a)}{Na22_activity_compare.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=0.5\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[scale=0.6]{391keV_curve2.png}
+        \subfigimg[width=0.5\linewidth]{b)}{Na24_activity_compare.pdf}{180}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{after_minimization_plot_alt.pdf}{80}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=0.5\textwidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
+%         \includegraphics[width=\columnwidth]{Capture.PNG}
+%         \includegraphics[scale=0.6]{391keV_curve2.png}
+        \subfigimg[width=0.5\textwidth]{b)}{after_subtraction_plot.pdf}{80}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
@@
  \centering
- \includegraphics[width=0.5\linewidth]{./figures/Nb_ptallies.pdf}
+ \includegraphics[width=0.5\linewidth]{Nb_ptallies.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
@@
  \centering
- \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
+ \includegraphics[width=0.5\linewidth]{fluence_plot.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
@@
  \centering
- \includegraphics[width=0.5\linewidth]{./figures/86Y.pdf}
+ \includegraphics[width=0.5\linewidth]{86Y.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
@@
  \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
+ \includegraphics[width=0.5\linewidth]{90Mo.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
@@
  \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
+ \includegraphics[width=0.5\linewidth]{90Nb.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298

### 2018-05-04 nb_px_paper/nb_body_text.tex
Corrected Gafchromic film type for the Nb paper.  Merge into revisions from journal, when they arrive.

@@
 The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT), revealing the spatial profile of the beam entering and exiting the stack.}
 \label{tab:stack_table}

### 2018-05-09 fe_px_paper/fe_body_text.tex
Finished gamma spec section of the draft.

@@
-\section{\label{sec:level1}First-level heading}
+\section{\label{sec:intro_fe}Introduction}
 
-This sample document demonstrates proper use of REV\TeX~4.1 (and
-\LaTeXe) in mansucripts prepared for submission to APS
-journals. Further information can be found in the REV\TeX~4.1
-documentation included in the distribution or available at
-\url{http://authors.aps.org/revtex4/}.
+Blah blah blah
 
-When commands are referred to in this example file, they are always
-shown with their required arguments, using normal \TeX{} format. In
-this format, \verb+#1+, \verb+#2+, etc. stand for required
-author-supplied arguments to commands. For example, in
-\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
-author's section heading, and in \verb+\title{#1}+ the \verb+#1+
-stands for the title text of the paper.
+% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
+% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
+% Change up the next sentance a bit
+Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
+% \cite{Qaim201731}. 
+% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease.
 
-Line breaks in section headings at all levels can be introduced using
-\textbackslash\textbackslash. A blank input line tells \TeX\ that the
-paragraph has ended. Note that top-level section headings are
-automatically uppercased. If a specific letter or word should appear in
-lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
-in the word ``via'' above.
+% This sample document demonstrates proper use of REV\TeX~4.1 (and
+% \LaTeXe) in mansucripts prepared for submission to APS
+% journals. Further information can be found in the REV\TeX~4.1
+% documentation included in the distribution or available at
+% \url{http://authors.aps.org/revtex4/}.
+% 
+% When commands are referred to in this example file, they are always
+% shown with their required arguments, using normal \TeX{} format. In
+% this format, \verb+#1+, \verb+#2+, etc. stand for required
+% author-supplied arguments to commands. For example, in
+% \verb+\section{#1}+ the \verb+#1+ stands for the title text of the
+% author's section heading, and in \verb+\title{#1}+ the \verb+#1+
+% stands for the title text of the paper.
+% 
+% Line breaks in section headings at all levels can be introduced using
+% \textbackslash\textbackslash. A blank input line tells \TeX\ that the
+% paragraph has ended. Note that top-level section headings are
+% automatically uppercased. If a specific letter or word should appear in
+% lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
+% in the word ``via'' above.
 
-\subsection{\label{sec:level2}Second-level heading: Formatting}
+\section{\label{sec:experimental_fe}Experimental Methods and Materials}
 
-This file may be formatted in either the \texttt{preprint} or
-\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
-Either format may be used for submission purposes. \texttt{letter} sized paper should
-be used when submitting to APS journals.
+The work described herein follows the  methods utilized in our recent work and established by Graves \etal\ 
+% for the measurement of cross sections in stacked target irradiations   
+for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018,Graves2016}.
+Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
 
-\subsubsection{Wide text (A level-3 head)}
-The \texttt{widetext} environment will make the text the width of the
-full page, as on page~\pageref{eq:wideeq}. (Note the use the
-\verb+\pageref{#1}+ command to refer to the page number.) 
-\paragraph{Note (Fourth-level head is run in)}
-The width-changing commands only take effect in two-column formatting. 
-There is no effect if text is in a single column.
+\comment{Do we really need to cite Alex's thesis?}
 
-\subsection{\label{sec:citeref}Citations and References}
-A citation in text uses the command \verb+\cite{#1}+ or
-\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
-An entry in the bibliography is a reference to another document.
+\subsection{\label{sec:target_design_fe}Stacked-target design}
 
-\subsubsection{Citations}
-Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
-the entire repertoire of commands in that package are available for your document;
-see the \verb+natbib+ documentation for further details. Please note that
-REV\TeX\ requires version 8.31a or later of \verb+natbib+.
+\comment{Update these energies, post-analysis}
 
-\paragraph{Syntax}
-The argument of \verb+\cite+ may be a single \emph{key}, 
-or may consist of a comma-separated list of keys.
-The citation \emph{key} may contain 
-letters, numbers, the dash (-) character, or the period (.) character. 
-New with natbib 8.3 is an extension to the syntax that allows for 
-a star (*) form and two optional arguments on the citation key itself.
-The syntax of the \verb+\cite+ command is thus (informally stated)
-\begin{quotation}\flushleft\leftskip1em
-\verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
-\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
-\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
-\end{quotation}\noindent
-where \emph{optarg+key} signifies 
-\begin{quotation}\flushleft\leftskip1em
-\emph{key}, or\\
-\texttt{*}\emph{key}, or\\
-\texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
-\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
-\texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
-\end{quotation}\noindent
-where \emph{pre} and \emph{post} is whatever text you wish to place 
-at the beginning and end, respectively, of the bibliographic reference
-(see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
-(Keep in mind that no automatic space or punctuation is applied.)
-It is highly recommended that you put the entire \emph{pre} or \emph{post} portion 
-within its own set of braces, for example: 
-\verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
-The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.
+A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
+One stack covers the \textred{55--20}\,MeV range and the other covers \textred{25--5}\,MeV, to minimize the systematic uncertainties associated with degradation of beam energy.
+In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
+% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
+% For targets, a
+A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%\cmmnt{, \textred{lot \#T23A035}}), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%\cmmnt{, \textred{lot \#M06C032}}), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%\cmmnt{, \textred{lot \#N26B062}}) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) targets were used.
+In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
+Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
+% , along with the propagated uncertainty in areal density.
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
+The sealed foils were mounted over the hollow center of a 1.5875 mm-thick aluminum frame.
+Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
+% One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
+% These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
+% These six foil packet bundles were inserted into one of six  
+The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
+% has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
+% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+% After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
+The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.
 
-The star (*) modifier to the \emph{key} signifies that the reference is to be 
-merged with the previous reference into a single bibliographic entry, 
-a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]). 
-When references are merged in this way, they are separated by a semicolon instead of 
-the period (full stop) that would otherwise appear.
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{./figures/SAM_2494.JPG}
+ % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
+ \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack, before it was mounted in the beamline.
+The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor is visible at the front of the stack.}
+\end{figure}
 
-\paragraph{Eliding repeated information}
-When a reference is merged, some of its fields may be elided: for example, 
-when the author matches that of the previous reference, it is omitted. 
-If both author and journal match, both are omitted.
-If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
-as exemplified by Ref.~[\onlinecite{epr}]. 
-These rules embody common editorial practice in APS and AIP journals and will only
-be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.
+% Separate tables
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{Specifications of the  target stack design in the present work.
+The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here.
+The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
+Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
+% \label{tab:fe_stack_table}
+% \small
+% \begin{tabular}{@{}llll@{}}
+% \toprule
+% % Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
+% Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
+% SS profile monitor SS-5 & 130.94 \mmicro m                                              & 100.57                                                                      & 0.17                                                                      \\
+% Fe-08                   & 26.25 \mmicro m                                               & 19.69                                                                       & 0.17                                                                      \\
+% Ti-14                   & 25.01 \mmicro m                                               & 10.87                                                                       & 0.36                                                                      \\
+% Cu-14                   & 24.01 \mmicro m                                               & 17.49                                                                       & 0.40                                                                      \\
+% Al Degrader E-09        & 256.5 \mmicro m                                               & --                                                                          & --                                                                        \\
+% Fe-09                   & 26.5 \mmicro m                                                & 19.90                                                                       & 0.09                                                                      \\
+% Ti-15                   & 23.81 \mmicro m                                               & 10.97                                                                       & 0.11                                                                      \\
+% Cu-15                   & 21.81 \mmicro m                                               & 17.63                                                                       & 0.46                                                                      \\
+% Al Degrader H-01        & 127.49 \mmicro m                                              & --                                                                          & --                                                                        \\
+% Fe-10                   & 26.5 \mmicro m                                                & 19.84                                                                       & 0.11                                                                      \\
+% Ti-16                   & 24.6 \mmicro m                                                & 10.96                                                                       & 0.32                                                                      \\
+% Cu-16                   & 22.01 \mmicro m                                               & 17.22                                                                       & 0.25                                                                      \\
+% Fe-11                   & 27.26 \mmicro m                                               & 19.96                                                                       & 0.17                                                                      \\
+% Ti-17                   & 25.01 \mmicro m                                               & 10.88                                                                       & 0.25                                                                      \\
+% Cu-17                   & 29 \mmicro m                                                  & 21.91                                                                       & 0.33                                                                      \\
+% Fe-12                   & 27.01 \mmicro m                                               & 20.03                                                                       & 0.12                                                                      \\
+% Ti-18                   & 25.01 \mmicro m                                               & 11.00                                                                       & 0.87                                                                      \\
+% Cu-18                   & 28.75 \mmicro m                                               & 22.33                                                                       & 0.14                                                                      \\
+% Fe-013                  & 26.25 \mmicro m                                               & 20.05                                                                       & 0.16                                                                      \\
+% Ti-19                   & 26.6 \mmicro m                                                & 11.01                                                                       & 0.22                                                                      \\
+% Cu-19                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.19                                                                      \\
+% Fe-14                   & 25.75 \mmicro m                                               & 20.11                                                                       & 0.19                                                                      \\
+% Ti-20                   & 27.01 \mmicro m                                               & 11.06                                                                       & 0.35                                                                      \\
+% Cu-20                   & 28.26 \mmicro m                                               & 22.34                                                                       & 0.28                                                                      \\
+% SS profile monitor SS-6 & 131.5 \mmicro m                                               & 100.99                                                                      & 0.17                                                                      \\
+%  \bottomrule
+% \end{tabular}
+% \end{table}
+% 
+% 
+% 
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{Specifications of the  target stack design in the present work.
+The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here.
+The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
+Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
+% \label{tab:fe_stack_table2}
+% \small
+% \begin{tabular}{@{}llll@{}}
+% \toprule
+% % Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
+% Target layer       & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured areal\\density (mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Areal density \\ uncertainty (\%)\end{tabular} \\ \midrule
+% SS profile monitor SS-3 & 130.9 \mmicro m                                               & 100.48                                                                      & 0.17                                                                      \\
+% Fe-01                   & 25.75 \mmicro m                                               & 20.22                                                                       & 0.21                                                                      \\
+% Ti-01                   & 25.88 \mmicro m                                               & 11.09                                                                       & 0.16                                                                      \\
+% Cu-01                   & 28.81 \mmicro m                                               & 22.40                                                                       & 0.11                                                                      \\
+% Al Degrader A-1         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-02                   & 25.5 \mmicro m                                                & 19.91                                                                       & 0.13                                                                      \\
+% Ti-02                   & 25.74 \mmicro m                                               & 10.94                                                                       & 0.24                                                                      \\
+% Cu-02                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.40                                                                      \\
+% Al Degrader A-2         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-03                   & 25.25 \mmicro m                                               & 20.00                                                                       & 0.27                                                                      \\
+% Ti-03                   & 25.91 \mmicro m                                               & 11.25                                                                       & 0.15                                                                      \\
+% Cu-03                   & 28.86 \mmicro m                                               & 22.49                                                                       & 0.20                                                                      \\
+% Al Degrader C-1         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-04                   & 25.25 \mmicro m                                               & 19.93                                                                       & 0.33                                                                      \\
+% Ti-04                   & 25.84 \mmicro m                                               & 10.91                                                                       & 0.18                                                                      \\
+% Cu-04                   & 28.78 \mmicro m                                               & 22.38                                                                       & 0.29                                                                      \\
+% Al Degrader C-2         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-05                   & 25.64 \mmicro m                                               & 20.02                                                                       & 0.24                                                                      \\
+% Ti-05                   & 25.86 \mmicro m                                               & 10.99                                                                       & 0.30                                                                      \\
+% Cu-05                   & 28.77 \mmicro m                                               & 22.35                                                                       & 0.12                                                                      \\
+% Al Degrader C-3         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-06                   & 25.75 \mmicro m                                               & 20.21                                                                       & 0.26                                                                      \\
+% Ti-06                   & 25.5 \mmicro m                                                & 11.15                                                                       & 0.23                                                                      \\
+% Cu-06                   & 28.83 \mmicro m                                               & 22.43                                                                       & 0.10                                                                      \\
+% Al Degrader C-4         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-07                   & 25.76 \mmicro m                                               & 19.93                                                                       & 0.19                                                                      \\
+% Ti-07                   & 25.75 \mmicro m                                               & 11.17                                                                       & 0.33                                                                      \\
+% Cu-07                   & 28.76 \mmicro m                                               & 22.34                                                                       & 0.24                                                                      \\
+% Al Degrader H-02        & 127.04 \mmicro m                                              & 34.51                                                                       & 0.20                                                                      \\
+% SS profile monitor SS-4 & 131.21 \mmicro m                                              & 101.25                                                                      & 0.16                                                                     \\
+%  \bottomrule
+% \end{tabular}
+% \end{table}
 
-\paragraph{The options of the cite command itself}
-Please note that optional arguments to the \emph{key} change the reference in the bibliography, 
-not the citation in the body of the document. 
-For the latter, use the optional arguments of the \verb+\cite+ command itself:
-\verb+\cite+ \texttt{*}\allowbreak
-\texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
-\texttt{[}\emph{post-cite}\texttt{]}\allowbreak
-\verb+{+\emph{key-list}\verb+}+.
+% Combined table
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Specifications of the 25\,MeV and 55\,MeV target stack designs in the present work.
+The proton beam enters the stack upstream of the SS-5 and SS-3 profile monitors, respectively, and is transported through the stack in the order presented here.
+The 6061 aluminum degraders have a measured density of approximately 2.69 g/cm$^3$.
+Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
+A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}
+\label{tab:fe_stack_table}
+\small
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}llll|llll@{}}
+\toprule
+% Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
+25\,MeV Target layer            & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured\\areal density\\(mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Uncertainty \\ in areal\\ density  (\%)\end{tabular} & 55\,MeV Target layer            & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured\\areal density\\(mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Uncertainty \\ in areal\\ density  (\%)\end{tabular} \\
+\midrule
+SS profile monitor SS-5 & 130.94 \mmicro m                                              & 100.57                                                                      & 0.17                                                                      & SS profile monitor SS-3 & 130.9 \mmicro m                                               & 100.48                                                                      & 0.17                                                                      \\
+Fe-08                   & 26.25 \mmicro m                                               & 19.69                                                                       & 0.17                                                                      & Fe-01                   & 25.75 \mmicro m                                               & 20.22                                                                       & 0.21                                                                      \\
+Ti-14                   & 25.01 \mmicro m                                               & 10.87                                                                       & 0.36                                                                      & Ti-01                   & 25.88 \mmicro m                                               & 11.09                                                                       & 0.16                                                                      \\
+Cu-14                   & 24.01 \mmicro m                                               & 17.49                                                                       & 0.40                                                                      & Cu-01                   & 28.81 \mmicro m                                               & 22.40                                                                       & 0.11                                                                      \\
+Al Degrader E-09        & 256.5 \mmicro m                                               & --                                                                          & --                                                                        & Al Degrader A-1         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
+Fe-09                   & 26.5 \mmicro m                                                & 19.90                                                                       & 0.09                                                                      & Fe-02                   & 25.5 \mmicro m                                                & 19.91                                                                       & 0.13                                                                      \\
+Ti-15                   & 23.81 \mmicro m                                               & 10.97                                                                       & 0.11                                                                      & Ti-02                   & 25.74 \mmicro m                                               & 10.94                                                                       & 0.24                                                                      \\
+Cu-15                   & 21.81 \mmicro m                                               & 17.63                                                                       & 0.46                                                                      & Cu-02                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.40                                                                      \\
+Al Degrader H-01        & 127.09 \mmicro m                                              & --                                                                          & --                                                                        & Al Degrader A-2         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
+Fe-10                   & 26.5 \mmicro m                                                & 19.84                                                                       & 0.11                                                                      & Fe-03                   & 25.25 \mmicro m                                               & 20.00                                                                       & 0.27                                                                      \\
+Ti-16                   & 24.6 \mmicro m                                                & 10.96                                                                       & 0.32                                                                      & Ti-03                   & 25.91 \mmicro m                                               & 11.25                                                                       & 0.15                                                                      \\
+Cu-16                   & 22.01 \mmicro m                                               & 17.22                                                                       & 0.25                                                                      & Cu-03                   & 28.86 \mmicro m                                               & 22.49                                                                       & 0.20                                                                      \\
+Fe-11                   & 27.26 \mmicro m                                               & 19.96                                                                       & 0.17                                                                      & Al Degrader C-1         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+Ti-17                   & 25.01 \mmicro m                                               & 10.88                                                                       & 0.25                                                                      & Fe-04                   & 25.25 \mmicro m                                               & 19.93                                                                       & 0.33                                                                      \\
+Cu-17                   & 29 \mmicro m                                                  & 21.91                                                                       & 0.33                                                                      & Ti-04                   & 25.84 \mmicro m                                               & 10.91                                                                       & 0.18                                                                      \\
+Fe-12                   & 27.01 \mmicro m                                               & 20.03                                                                       & 0.12                                                                      & Cu-04                   & 28.78 \mmicro m                                               & 22.38                                                                       & 0.29                                                                      \\
+Ti-18                   & 25.01 \mmicro m                                               & 11.00                                                                       & 0.87                                                                      & Al Degrader C-2         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+Cu-18                   & 28.75 \mmicro m                                               & 22.33                                                                       & 0.14                                                                      & Fe-05                   & 25.64 \mmicro m                                               & 20.02                                                                       & 0.24                                                                      \\
+Fe-013                  & 26.25 \mmicro m                                               & 20.05                                                                       & 0.16                                                                      & Ti-05                   & 25.86 \mmicro m                                               & 10.99                                                                       & 0.30                                                                      \\
+Ti-19                   & 26.6 \mmicro m                                                & 11.01                                                                       & 0.22                                                                      & Cu-05                   & 28.77 \mmicro m                                               & 22.35                                                                       & 0.12                                                                      \\
+Cu-19                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.19                                                                      & Al Degrader C-3         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+Fe-14                   & 25.75 \mmicro m                                               & 20.11                                                                       & 0.19                                                                      & Fe-06                   & 25.75 \mmicro m                                               & 20.21                                                                       & 0.26                                                                      \\
+Ti-20                   & 27.01 \mmicro m                                               & 11.06                                                                       & 0.35                                                                      & Ti-06                   & 25.5 \mmicro m                                                & 11.15                                                                       & 0.23                                                                      \\
+Cu-20                   & 28.26 \mmicro m                                               & 22.34                                                                       & 0.28                                                                      & Cu-06                   & 28.83 \mmicro m                                               & 22.43                                                                       & 0.10                                                                      \\
+SS profile monitor SS-6 & 131.5 \mmicro m                                               & 100.99                                                                      & 0.17                                                                      & Al Degrader C-4         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+                        &                                                               &                                                                             &                                                                           & Fe-07                   & 25.76 \mmicro m                                               & 19.93                                                                       & 0.19                                                                      \\
+                        &                                                               &                                                                             &                                                                           & Ti-07                   & 25.75 \mmicro m                                               & 11.17                                                                       & 0.33                                                                      \\
+                        &                                                               &                                                                             &                                                                           & Cu-07                   & 28.76 \mmicro m                                               & 22.34                                                                       & 0.24                                                                      \\
+                        &                                                               &                                                                             &                                                                           & Al Degrader H-02        & 127.04 \mmicro m                                              & --\cmmnt{34.51}                                                                       & --\cmmnt{0.20}                                                                      \\
+                        &                                                               &                                                                             &                                                                           & SS profile monitor SS-4 & 131.21 \mmicro m                                              & 101.25                                                                      & 0.16                                                                     \\
+ \bottomrule
+\end{tabular}
+}
+\end{table}
+
+Both target stacks were assembled and separately irradiated at the  Lawrence Berkeley National Laboratory  (LBNL), using the 88-Inch Cyclotron, a  K=140 sector-focused cyclotron.
+The 25\,MeV stack was irradiated for approximately 20\,minutes with a nominal current of 100\,nA,  for an anticipated integral current of 31.61\,nAh. 
+The 55\,MeV stack was irradiated for approximately 10\,minutes with a nominal current of 120\,nA,  for an anticipated integral current of 20.78\,nAh. 
+The beam current, measured using a current integrator on the electrically-isolated beamline, remained stable under these conditions for the duration of each irradiation.
+The proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 1.5\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
+Following end-of-bombardment (EoB), each stack was removed from the beamline and disassembled.
+All activated foils were transported to a counting lab for gamma spectrometry, which started approximately 30\,minutes following the end of each irradiation.
+
+% The \texttt{widetext} environment will make the text the width of the
+% full page, as on page~\pageref{eq:wideeq}. (Note the use the
+% \verb+\pageref{#1}+ command to refer to the page number.) 
+% \paragraph{Note (Fourth-level head is run in)}
+% The width-changing commands only take effect in two-column formatting. 
+% There is no effect if text is in a single column.
+
+\subsection{\label{sec:spectroscopy_fe}Quantification of induced activities}
+
+% \comment{Get detector specs from Alex}
+
+% For consistency, a
+A single detector was used in this measurement, an ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector.
+The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
+Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy and efficiency for each position.
+The foils were counted  for a period of 4 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities.
+% An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
+For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks \cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma ray spectra \cite{Aarnio2001}.
+% , which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
+%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
+
+% Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
+The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products, using calibrated detector efficiencies and gamma-ray intensities for each transition.
+% and  corrections for gamma-ray attenuation within each foil packet
+% The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
+The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
+Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database  \cite{berger2011xcom}.
+% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
+% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
+% activity for each gamma-ray possesses a 
+The total propagated uncertainty in  activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
+
+As in our previous work, these activities used to calculate cross sections, and are differentiated between cumulative and independent \cite{Voyles2018}.
+For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
+% In addition, 
+Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
+Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, that  independent cross sections may be reported \cite{bateman1910solution,Cetnar2006}.
+
+% Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly by decay down a mass chain.
+% To this end, it is useful to differentiate between the types of cross sections reported in this work. 
+% For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
+% % In addition, 
+% Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
+% For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
+% 
+% 
+% 
+% % To convert these activities into cross sections, c
+% Corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB, from the measured activities.
+% The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
+% For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
+% % \begin{equation}
+% % A\pp{t} = A_0 e^{-\lambda t}
+% % \end{equation}
+% Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
+% As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of \ref{sec:fe_data}.
+% In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
+% \begin{equation}
+% A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_{i,0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
+% \end{equation}
+% where $j$ refers to a precursor nucleus populating a specific end-product.  
+% While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
+% \begin{equation}
+% A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
+% \end{equation}
+% In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
+% After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
+
+% A citation in text uses the command \verb+\cite{#1}+ or
+% \verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
+% An entry in the bibliography is a reference to another document.
+
+\subsection{\label{sec:dosimetry_fe}Proton fluence determination}
+
+Blah blah blah
+
+% Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
+% the entire repertoire of commands in that package are available for your document;
+% see the \verb+natbib+ documentation for further details. Please note that
+% REV\TeX\ requires version 8.31a or later of \verb+natbib+.
+
+\subsection{\label{sec:proton_transport_fe}Proton transport calculations}
+
+Blah blah blah
+
+\subsection{\label{sec:calcs_sec_fe}Calculation of measured cross sections}
+
+Blah blah blah
+
+\section{\label{sec:results_fe}Results and Discussion}
+
+Blah blah blah
+
+ \section{\label{sec:conclusions_fe}Conclusions}
+
+ Blah blah blah
+
+% We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
+% Nearly all cross sections have been reported with higher precision than previous measurements.
+% We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
+% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+% Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
+
+% 
+% \paragraph{Syntax}
+% The argument of \verb+\cite+ may be a single \emph{key}, 
+% or may consist of a comma-separated list of keys.
+% The citation \emph{key} may contain 
+% letters, numbers, the dash (-) character, or the period (.) character. 
+% New with natbib 8.3 is an extension to the syntax that allows for 
+% a star (*) form and two optional arguments on the citation key itself.
+% The syntax of the \verb+\cite+ command is thus (informally stated)
+% \begin{quotation}\flushleft\leftskip1em
+% \verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
+% \verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
+% \verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
+% \end{quotation}\noindent
+% where \emph{optarg+key} signifies 
+% \begin{quotation}\flushleft\leftskip1em
+% \emph{key}, or\\
+% \texttt{*}\emph{key}, or\\
+% \texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
+% \texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
+% \texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
+% \end{quotation}\noindent
+% where \emph{pre} and \emph{post} is whatever text you wish to place 
+% at the beginning and end, respectively, of the bibliographic reference
+% % (see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
+% (Keep in mind that no automatic space or punctuation is applied.)
+% It is highly recommended that you put the entire \emph{pre} or \emph{post} portion 
+% within its own set of braces, for example: 
+% \verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
+% The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.
+% 
+% The star (*) modifier to the \emph{key} signifies that the reference is to be 
+% merged with the previous reference into a single bibliographic entry, 
+% % a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]). 
+% When references are merged in this way, they are separated by a semicolon instead of 
+% the period (full stop) that would otherwise appear.
+% 
+% \paragraph{Eliding repeated information}
+% When a reference is merged, some of its fields may be elided: for example, 
+% when the author matches that of the previous reference, it is omitted. 
+% If both author and journal match, both are omitted.
+% If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
+% % as exemplified by Ref.~[\onlinecite{epr}]. 
+% These rules embody common editorial practice in APS and AIP journals and will only
+% be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.
+% 
+% \paragraph{The options of the cite command itself}
+% Please note that optional arguments to the \emph{key} change the reference in the bibliography, 
+% not the citation in the body of the document. 
+% For the latter, use the optional arguments of the \verb+\cite+ command itself:
+% \verb+\cite+ \texttt{*}\allowbreak
+% \texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
+% \texttt{[}\emph{post-cite}\texttt{]}\allowbreak
+% \verb+{+\emph{key-list}\verb+}+.

### 2018-05-12 nb_px_paper/Response_to_Reviewers.tex
Changed title and some conclusion langauge, following reviewer feedback.  Resubmitted as 1st revision.

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage[ampersand]{easylist}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{amsmath}

\newfloat{figure}{htbp}{figs}

% \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
\newcommand{\colornote}[1]{\textcolor{red}{#1}}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\pp}[1]{\left( #1\right)}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Mark Breese, PhD \\
Editor \\
Nuclear Instruments and Methods in Physics Research Section B: \\
Beam Interactions with Materials and Atoms}

\begin{flushleft}
{\large\bf Andrew S. Voyles}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill The University of California, Berkeley \\
\hfill 1106B Etcheverry Hall, Berkeley, CA  94720-1730 \\
\hfill (850) 281-0217 or (510) 486-7310 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Dr. Breese,}

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Excitation functions for (p,x) reactions of niobium in the energy range of E\texorpdfstring{$_{\text{p}}$\,=\,40--90\,}{Ep = 40--90 }MeV}}  for publication in Nuclear Instruments and Methods in Physics Research Section B.  Please find my responses detailed in \colornote{red text.}

  \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.  We would especially like to thank the referees for their thorough reading and critique, which has made it a better paper. Their comments were very constructive and pointed out some valuable improvements.

  Please find the feedback following here, and our revised manuscript attached.

  Sincerely yours,\\ \\ \\ \\ Andrew S. Voyles

% \closing{Sincerely yours,}

  \vfill

 \pagebreak

 Reviewer \#1:

 Authors have reported excitation function of the proton induced nuclear reactions on niobium. Details on experimental techniques, data analysis and error calculations related to cross section measurements are given.

The work is interesting to get standard reaction, isotope production and radiation safety analysis. The results will rich the data bank. Authors emphasized on the 93Nb(p,4n)90Mo reaction because of its importance as monitor reaction.

However, this work reported cross sections only at six energies, which are also not consistent with the model calculations in many cases. The results of this work are not sufficient to extract standard data as well as to establish 93Nb(p,4n)90Mo as monitor reaction. Therefore, title of the paper should be changed to \enquote{Excitation functions for (p,xn) reactions of niobium in the energy range of Ep= 40-90 MeV}.

 \colornote{We thank the reviewer for their thoughtful comments, and the excellent suggestion for shifting the title to reflect the broader scope of work covered by this manuscript.  We would, however, respectfully suggest that the title should become \enquote{Excitation functions for (p,x) reactions on niobium in the energy range of Ep= 40-90 MeV}, as \enquote{(p,xn)} typically refers to reactions where only neutrons are secondaries, and many of the reactions we measured  include charged particles in the exit channel.}

%   \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

As mentioned in section 2, authors have performed a single irradiation. Therefore, in section 4 (Conclusion), "\ldots 38 measurements of cross sections\ldots." and "\ldots five independent measurements of isomer \ldots." are wrong. It should be corrected.

\colornote{We  thank the reviewer for their  correction, as our language incorrectly implied multiple measurements instead of multiple reported cross sections arising from a single measurement. We have corrected this language to "\ldots  measurements of 38 cross sections\ldots." and "\ldots  independent measurements of five isomer \ldots."}

The manuscript in well written and I would like to recommend this paper to accept for publication in NIMB after the above corrections.

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2018-05-12 nb_px_paper/nb_body_text.tex
Changed title and some conclusion langauge, following reviewer feedback.  Resubmitted as 1st revision.

@@
 
-We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
+We present here a set of measurements of 38 cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as  independent measurements of five isomer branching ratios.
 Nearly all cross sections have been reported with higher precision than previous measurements.

### 2018-05-12 nb_px_paper/nb_px_paper.tex
Pushing fix for missing /mmicro macro?
Changed title and some conclusion langauge, following reviewer feedback.  Resubmitted as 1st revision.

@@
 %% Give the name of the journal
-\journalname{Nuclear Instruments and Methods in Physics Research B}
+\journalname{Nuclear Instrum. and Methods in Phys. Res. B}
 
@@
 
+% Sick of fighting siunitx - consistent text micro symbol
+% DO NOT uncomment this!!! or else broken unicode (Âţ)
+% \sisetup{math-micro=\text{µ},text-micro=µ}
+% \si\micro
+\newcommand{\mmicro}{\si\micro}
+
+\usepackage{adjustbox}
+
 \makeatletter
@@
 % %%
-\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}
+
+% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}
+\title{Excitation functions for (p,x) reactions of niobium in the energy range of E\texorpdfstring{$_{\text{p}}$\,=\,40--90\,}{Ep = 40--90 }MeV}
+% ):  development of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as an intermediate-energy proton monitor}
 
@@
 This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
-This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy
+This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy.
 Additional support has been provided by the U.S. Nuclear Regulatory Commission.

### 2018-05-28 nb_px_paper/nb_abstract_text.tex
Incorporated changes from journal proof production.

@@
 % , Cu, and Al monitor 
-foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
+foils was irradiated with the 100\,MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
 % A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
 % The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
-A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
+A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90\,MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
 % The measurements are 
@@
 % \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
-\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
+\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
 % \textred{

### 2018-05-28 nb_px_paper/nb_body_text.tex
Incorporated changes from journal proof production.

@@
 % in the field's array of
-by low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerators, 
+by low- (E \textless\ 30\,MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200\,MeV / A) accelerators, 
 % capabilities, which routinely produce many of the staple medical radionuclides, such as 
@@
 % in particular seeks to improve this range of options by 
-is an attempt to characterize a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory,
+is an attempt to characterize a new monitor reaction for  proton beams in excess of 40\,MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory,
 % IPF
@@
 Care should also be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
-For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
+For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52\,keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
 % Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
@@
 % allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
-and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production.
+and seven strong, distinct gamma lines (notably its 122.370\,keV [$I_\gamma = 64 \pm 3\%$] and 257.34\,keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production.
 In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.
@@
 via the $^\text{nat}$Nb(p,x) reaction. 
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90\,MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
 % These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}).
@@
 In addition to providing a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in g$_{9/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
-Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
+Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
 These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$\,m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$\,d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$\,h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$\,d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$\,h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$\,h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$\,h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$\,m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$\,h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.
@@
 % For targets, a
-A series of nominal 25 \mmicro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \mmicro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \mmicro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used (all from Alfa Aesar, Ward Hill, MA, 01835, USA) targets were used.
-Six foils of each metal were cut down to 2.5 x 2.5 cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
+A series of nominal 25 \mmicro m \ce{^{nat}Nb} foils (99.8\%, lot \#T23A035), 25 \mmicro m \ce{^{nat}Al} foils (99.999\%, lot \#M06C032), and 50 \mmicro m \ce{^{nat}Cu} foils (99.9999\%, lot \#N26B062) were used as targets (all from Alfa Aesar, Ward Hill, MA, 01835, USA).
+Six foils of each metal were cut down to 2.5 $\times$ 2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
 Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
 % , along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
-The sealed foils were mounted over the hollow center of a 1.575 mm-thick plastic frame.
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
+The sealed foils were mounted over the hollow center of a 1.575\,mm-thick plastic frame.
 One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
@@
 % These six foil packet bundles were inserted into one of six  
-The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
+The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64\,mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
 % At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT), revealing the spatial profile of the beam entering and exiting the stack.
@@
 This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
-The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \mmicro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
-The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3 minutes into irradiation.
-The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100 MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1 MeV --- this energy profile was used for all later analysis.
+The stack was irradiated for approximately 2\,h with a nominal current of 1\,mA, using a 50 \mmicro s pulse at a frequency of 2\,Hz, for an anticipated integral current of 205.9 nAh.
+The beam current, measured using an inductive pickup, remained stable under these conditions for the duration of the irradiation, with the exception of approximately 70\,s of downtime, which occurred approximately 3\,min into irradiation.
+The proton beam incident upon the stack's Inconel beam entrance window had an average energy of 100\,MeV determined via time-of-flight, with an approximately Gaussian energy distribution width of 0.1\,MeV --- this energy profile was used for all later analysis.
 At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
-The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectrometry, which started approximately 6 hours following end-of-bombardment.
+The activated foils were cleaned of all surface contamination, and transported to a counting lab for gamma spectrometry, which started approximately 6\,h following end-of-bombardment.
 
@@
 A single detector was used in this measurement, an ORTEC GEM Series (model \#GEM10P4-70)  High-Purity Germanium (HPGe) detector.
-The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
-Samples were counted at fixed positions ranging 4.5--83.5  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
-The foils were counted  for a period of 2 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities,  with dead time never exceeding 5\%.
+The detector is a mechanically-cooled coaxial p-type HPGe with a 1\,mm aluminum window, and a 49.2\,mm diameter, 27.9\,mm long crystal.
+Samples were counted at fixed positions ranging 4.5--83.5\,cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy, efficiency, and pileup calibrations for each position.
+The foils were counted  for a period of 2\,weeks following end-of-bombardment (EoB), to accurately quantify all induced activities,  with dead time never exceeding 5\%.
 An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
@@
 % For reference, t
-The nuclear decay data used in this work is tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+The nuclear decay data used in this work is tabulated in Tables \ref{tab:nudat_table_monitors} and \ref{tab:nudat_table_nb} of \ref{data}.
 Data for photon attenuation coefficients were taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
 % As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
-Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
+Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2\,weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
 % activity for each gamma-ray possesses a 
@@
 % \end{equation}
-Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
-As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
+Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as  well.
+As with the gamma-ray intensities, all lifetimes used in this work are tabulated in Tables \ref{tab:nudat_table_monitors} and \ref{tab:nudat_table_nb} of \ref{data}.
 In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
@@
 The ability to model the full energy distribution in each target position is vital for stacked target irradiations, due to the progressively larger energy straggling towards the rear of the stack.
-The initial proton beam has a finite energy spread (an approximately 0.1 MeV Gaussian width at 100 MeV), and since stopping power for charged particles is inversely proportional to their energy, the low-energy tail of the energy distribution is degraded more in each stack element than the high-energy tail.
+The initial proton beam has a finite energy spread (an approximately 0.1\,MeV Gaussian width at 100\,MeV), and since stopping power for charged particles is inversely proportional to their energy, the low-energy tail of the energy distribution is degraded more in each stack element than the high-energy tail.
 This effect compounds  towards the rear of the stack, creating a significantly broadened low-energy tail, and a progressively larger net shift of the centroid to a lower energy. 
@@
 % This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to 
-significantly greater areal density of the thick 6061 aluminum degraders as compared to the other stack elements (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$),
+significantly greater areal density of the thick 6061 aluminum degraders as compared to the other stack elements (nominal 3--5\,mg/cm$^2$, relative to nominal 1000--1400\,mg/cm$^2$),
 % As such
@@
 This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
-The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position.
-This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
+The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34\,MeV protons entering the last energy position.
+This is approximately 2\,MeV lower than the nominal MCNP6 simulations, and approximately 3\,MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the 6061 aluminum degraders.
 This energy corresponds to a 6061 aluminum areal density of 2.52\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
@@
 The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is supported by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.
-
 % These compensating factors  contribute to 
@@
 At lower energies, the magnitude of \ce{^{nat}Al}(p,x)\ce{^{22}Na} is large compared to \ce{^{nat}Si}(p,x)\ce{^{22}Na}, which is why the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor agrees in fluence at the 40 (and almost at the 50) MeV position.
-At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90 MeV.
+At higher energies, the apparent \ce{^{nat}Al}(p,x)\ce{^{22}Na} activity begins to diverge from the IAEA expected activities as     \ce{^{nat}Si}(p,x)\ce{^{22}Na} production begins to open up,  which accounts for the nearly 50\% apparent excess fluence in \ce{^{22}Na} between 60--90\,MeV.
 For  \ce{^{24}Na} production, we see  similar behavior, with only a minor increase in apparent \ce{^{24}Na} activity,  since the observed \ce{^{nat}Si}(p,x)\ce{^{24}Na} yield remains consistently low in magnitude.
@@
 Uncertainty in proton fluence  is likewise calculated by error propagation of the fluence values  at each energy position.
-These weighted-mean fluences are  plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both  MCNP6 transport 
+These weighted-mean fluences are  plotted  in \autoref{fig:fluence_plot}, along with the estimated fluence according to both  MCNP6 transport 
 % model, as well as 
@@
 Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.
-These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by  IPF upstream current monitors.
+These models are used purely to provide an extrapolation from the 90\,MeV energy position back to the \enquote{front} of the stack at 100\,MeV, to compare with the nominal fluence measured by  IPF upstream current monitors.
 % This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
@@
 Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
-While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
+While thin ($\approx$ 22\,mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
 % cross sections, 
@@
 where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
-The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
-The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).
+The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3\,min into irradiation.
+The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60\,s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).
 
@@
 
-Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40--90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
+Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40--90\,MeV region, as recorded in \autoref{tab:cu_rp_table}.
 For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
@@
 The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90 MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
+Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
 Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
@@
 % This work reports the first experimental measurement of
-this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region, 
+this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
 % It also represents  the first measurement of 
@@
 
-Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
-This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
+This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
 % The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
@@
 \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
-Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
-This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.
+Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
+Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
+This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
 
@@
 Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
-The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58 MeV, and varies from 45--75 at the 70--90 MeV positions.
-This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately five-fold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
+This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
 
@@
 
-The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70 MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
+The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70\,MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
 The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
-The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50 MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
+The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50\,MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
 In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011 \cite{Titarenko2011}.
@@
 
-We present here a set of measurements of 38 cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as  independent measurements of five isomer branching ratios.
+We present here a set of measurements of 38 cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90\,MeV, as well as  independent measurements of five isomer branching ratios.
 Nearly all cross sections have been reported with higher precision than previous measurements.

### 2018-06-21 nb_px_paper/arxiv/nb_body_text.tex
Updated Nb arXiv to final published version.

@@
 % These six foil packet bundles were inserted into one of six  
-The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
+The box, seen in \autoref{fig:target_stack}, is machined from 6061 aluminum alloy, has a thin (0.64\,mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
+% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT), revealing the spatial profile of the beam entering and exiting the stack.
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
@@
 
-We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
+We present here a set of measurements of 38 cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90\,MeV, as well as  independent measurements of five isomer branching ratios.
 Nearly all cross sections have been reported with higher precision than previous measurements.

### 2018-07-17 fe_px_paper/fe_body_text.tex
Finished 1st draft through proton fluence section.

@@
 % for the measurement of cross sections in stacked target irradiations   
-for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018,Graves2016}.
+for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018a,Graves2016}.
 Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
@@
 The 6061 aluminum degraders have a measured density of approximately 2.69 g/cm$^3$.
-Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
+Their areal densities were determined using the variance minimization techniques described  in this work  and our earlier paper \cite{Voyles2018a}.
+% the earlier paper by Graves \etal\ \cite{Graves2016}.
 A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}
@@
 The beam current, measured using a current integrator on the electrically-isolated beamline, remained stable under these conditions for the duration of each irradiation.
-The proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 1.5\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
+The proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
 Following end-of-bombardment (EoB), each stack was removed from the beamline and disassembled.
@@
 The foils were counted  for a period of 4 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities.
+An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec_femn}.
 % An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
@@
 
-As in our previous work, these activities used to calculate cross sections, and are differentiated between cumulative and independent \cite{Voyles2018}.
+As in our previous work, these activities used to calculate cross sections, and are differentiated between cumulative and independent \cite{Voyles2018a}.
 For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
@@
 Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, that  independent cross sections may be reported \cite{bateman1910solution,Cetnar2006}.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=6in]{./figures/AP161219_Fe01_10cm.png}
+ % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
+ \caption{\textred{Replace this figure!!!}  A gamma spectrum collected from an activated Fe foil at approximately \textred{80 MeV}.
+While the majority of observed reaction products are visible in this spectrum,  the \ce{^{51}Cr}, \ce{^{52m}Mn}, and \ce{^{52g}Mn} decay lines, which form the   primary reaction channels of interest, are  clearly isolated from surrounding peaks.}
+ \label{fig:gspec_femn}
+\end{figure}
 
@@
 
-Blah blah blah
+In addition to the stack's overall beam current measurements using  beamline current integrators, thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Fe} targets at each energy position, to monitor beam current at each position within the stack.
+% These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
+The IAEA-recommended \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V},  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions were used for  proton fluence measurement
+% , using values  
+% and uncertainties 
+% from the 2017 IAEA re-evaluation  
+\cite{Hermanne2018}.
+% The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
+As in our previous work, the integral form of the well-known activation equation was used to  determine proton fluence ($I \Delta t $),
+% in each monitor foil
+in order to account for energy loss across each monitor foil:
+\begin{equation}
+I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
+\end{equation}
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  rom the 2017 IAEA re-evaluation  \cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
 

### 2018-07-19 fe_px_paper/fe_body_text.tex
Finished 1st draft through xs calculation section.

@@
 Cu-18                   & 28.75 \mmicro m                                               & 22.33                                                                       & 0.14                                                                      & Fe-05                   & 25.64 \mmicro m                                               & 20.02                                                                       & 0.24                                                                      \\
-Fe-013                  & 26.25 \mmicro m                                               & 20.05                                                                       & 0.16                                                                      & Ti-05                   & 25.86 \mmicro m                                               & 10.99                                                                       & 0.30                                                                      \\
+Fe-13                  & 26.25 \mmicro m                                               & 20.05                                                                       & 0.16                                                                      & Ti-05                   & 25.86 \mmicro m                                               & 10.99                                                                       & 0.30                                                                      \\
 Ti-19                   & 26.6 \mmicro m                                                & 11.01                                                                       & 0.22                                                                      & Cu-05                   & 28.77 \mmicro m                                               & 22.35                                                                       & 0.12                                                                      \\
@@
 \end{equation}
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  rom the 2017 IAEA re-evaluation  \cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation  \cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
 
@@
 
-Blah blah blah
+Estimates of the proton beam energy for preliminary stack designs were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
+However, the more rigorous Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, to determine the full proton energy and fluence distribution for each foil   \cite{Goorley2012}.
+$10^8$ source protons were used for all MCNP simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
+As with the determination of proton fluence in monitor foils, the progressively increasing energy straggle towards the rear of each stack is accounted for using the differential proton fluence from MCNP simulation of proton transport.
+These energy distributions $\frac{d\phi}{dE}$ are used to calculate a flux-weighted average proton  energy $\langle E \rangle$, which accounts for the slowing-down of protons within a foil (particularly in the low-energy stack) and reports the effective  energy centroid for each foil:
+\begin{equation}
+\langle E \rangle = \dfrac{{\displaystyle\int E \dfrac{d\phi}{dE} dE}}{{\displaystyle\int \dfrac{d\phi}{dE} dE}}
+\end{equation}
+To report a complete description of the representative energy for each foil, a bin width is provided through the  energy uncertainty, calculated as the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution for each foil.
+
+To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, the \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments \cite{Voyles2018a,Graves2016}.
+This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions used in this work should all be consistent at each energy position.
+Assuming that the recommended monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, residual disagreement in the  observed proton fluences is thus primarily due to poorly characterized stopping power in simulations, or a systematic error in the
+% stack design, namely, the
+areal densities of the stack components. 
+This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
+
+When performing  a variance minimization, it is important to apply this variation of effective areal density  to the stack components which  have the most significant impact on beam degradation, as any systematic error in the areal densities used for these components will cause a disagreement in the observed fluences.
+For the 55\,MeV stack, the aluminum degraders are used for variance minimization, as they make up more than 80\% of the areal density of the stack, and this play the largest role in beam degradation.
+% 
+% Update this post-results!
+% 
+% Delete  the paragraph break!
+%
+
+\textred{Update this post-results!}
+For the 25\,MeV stack, the Kapton tape was chosen for variance minimization, as the foil packets themselves are responsible for the majority of beam degradation.
+While it only makes up approximately 20\% of the low-energy stack's areal density, the Kapton surrounding each foil packet has a greater areal density than the foil itself.
+In addition, it is far easier to directly characterize the areal density of the metallic foils than it is for the Kapton, resulting in only an approximate value for the latter.
+This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but the stopping power of the Kapton at this energy range may cause as much as a loss of 0.5\,MeV by the rear of this stack, making the precise areal density a source of significant uncertainty.
+
+In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
+For the 25\,MeV stack, the areal density of the E-09 and H-01 aluminum degraders was taken from that reached in the minimization of the 55\,MeV stack.
+Using this value, the areal density of each of the  Kapton tape  layers  were likewise varied uniformly   by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
+These lowest energy positions were chosen as  minimization candidates, as they are the most sensitive to systematic uncertainties in stack design, due to the compounded effect of proton stopping powers.
+In the 25\,MeV stack, activity was not seen in gamma spectrometry for the lowest-energy (Ti-20, Cu-20) monitor foils, implying that the beam was stopped at some point in between Fe-14 and Ti-20.
+This observation is conclusive proof that  the true areal densities of the stack components differs from nominally measured values (primarily for the difficult-to-characterize Kapton tape), as transport calculations using nominal areal densities predict that the beam should exit the stack (at the SS-6 profile monitor) with an energy of approximately 7\,MeV.
+As a result, this position was not used for minimization, with the Ti-19 and Cu-19 position being the lowest-energy reliable monitor foils in the stack.
+The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average \textred{41.34\,MeV} protons entering the last energy position of the 55\,MeV stack.
+This is approximately \textred{2\,MeV} lower than the nominal MCNP6 simulations, and approximately \textred{3\,MeV} lower than nominal A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
+This energy corresponds to an aluminum areal density of \textred{2.52\%} greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
+Similarly, for the 25\,Me stack, variance minimization converges on  flux-weighted average \textred{41.34\,MeV} protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately \textred{2\,MeV} lower than the nominal MCNP6 simulations, and approximately \textred{3\,MeV} lower than nominal A\&Z calculations.
+This energy corresponds to a Kapton tape areal density of \textred{2.52\%} greater than nominal measurements.
+The impact of this variance minimization for improving disagreement in proton fluence is  clearly  seen in   \autoref{fig:fe_variance_mins}.
+
+\begin{figure}
+    \centering
+    \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+         \label{fig:before_minimization}
+   \hspace{-5pt}}%
+     \subfloat{
+        \centering
+
+%         \subfigimg[width=0.5\textwidth]{b)}{./figures/after_minimization_plot.pdf}{50}
+        \subfigimg[width=0.5\textwidth]{b)}{./figures/current_norm_az.pdf}{50}
+         %         \refstepcounter{subfigure}
+         \label{fig:after_minimization}
+   \hspace{-5pt}}%
+    \caption{\textred{Update this figure!!!} Results of variance minimization through enhancement of the effective areal density of the  aluminum degraders by \textred{2.52\%} (55\,MeV stack) and Kapton tape by \textred{2.52\%} (25\,MeV stack).
+A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
+%     Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
+     \label{fig:fe_variance_mins}
+\end{figure}
+
+An enhanced version of the final \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reaction fluences is shown in \autoref{fig:fe_fluence_plot}.
+% Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
+The uncertainty-weighted mean  for the two \ce{^{nat}Cu}(p,x) and two \ce{^{nat}Ti}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Cu and Ti foils, respectively, and the uncertainty-weighted mean  for all four monitor channels was used to determine the final fluence assignments for the Fe foils.
+Uncertainty in proton fluence  is  calculated by error propagation of the fluence values  at each energy position.
+These weighted-mean fluences are  plotted  in \autoref{fig:fe_fluence_plot}, along with the estimated fluence according to both  MCNP6 transport 
+and an uncertainty-weighted linear $\chi^2$ fit to the individual monitor channel fluence measurements.
+\textred{Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.}
+These models are used purely to provide an extrapolation from the highest-energy position back to the \enquote{front} of each stack, to compare with the nominal fluence measured by  the beamline current integrators.
+% This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
+% As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
+% The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections
+
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{./figures/Nb_ptallies.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
+The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
+As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
+%  \label{fig:Nb_ptallies}
+% \end{figure}
+
+\begin{figure}
+ \centering
+%  \includegraphics[width=0.5\linewidth]{./figures/fe_fluence_plot.pdf}
+ \includegraphics[width=0.5\linewidth]{./figures/current_norm_az.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{\textred{Update this figure!!!} Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.
+%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
+%   A clear loss of 
+  The fluence  drops by approximately \textred{7.2--8.9\%} from the incident fluence of \textred{196.9--198.8 nAh} over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.}
+%   This is due to a combination of beam utilization, as well as scattering.}
+ \label{fig:fe_fluence_plot}
+\end{figure}
 
@@
 
-Blah blah blah
+Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed (p,x) reactions.
+While thin ($\approx$ 10--20\,mg/cm$^2$)  foils were irradiated to minimize the energy bins of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
+% cross sections, 
+over the energy distribution subtended by each foil, as seen in \autoref{fig:Fe_ptallies}.
+For both the cumulative and independent activities quantified, cross sections were calculated as:
+\begin{equation}
+\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
+\end{equation}
+where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
+The beam current, measured using a current integrator connected to the electrically-isolated target box, remained stable for the duration of the irradiation.
+The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 30\,s, to account for any minor transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fe_fluence_plot}).
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{./figures/Fe_mcnp_spectrum.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{\textred{Add 25\,MeV stack tallies here!
+} Final variance minimized incident proton energy distributions for the Fe foils, as simulated in MCNP6.
+The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
+As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
+ \label{fig:Fe_ptallies}
+\end{figure}
 

### 2018-07-20 fe_px_paper/fe_body_text.tex
Finished 1st draft of results and conclusions sections.

@@
 for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018a,Graves2016}.
-Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
+% 
+% Make sure to add this back in for the journal article
+% 
+% 
+% Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
 
-\comment{Do we really need to cite Alex's thesis?}
+% \comment{Do we really need to cite Alex's thesis?}
 
@@
  \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack, before it was mounted in the beamline.
-The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor is visible at the front of the stack.}
+The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
 \end{figure}
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{../nb_px_paper/figures/before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 
-Blah blah blah
+\subsection{Measurement of nuclear excitation functions}
+
+After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
+With the exception of two foils (Cu-20 and Ti-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
+% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
+This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Fe-14 and Ti-20.
+Using the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of \textred{198.8$\pm$6.7\,nAh} was calculated to be incident upon the 55\,MeV target stack using the MCNP6 fluence model, and a  fluence of \textred{196.9$\pm$11.3\,nAh} using the linear fit model.
+Similarly, for the 25\,MeV stack, a fluence of \textred{198.8$\pm$6.7\,nAh} was calculated to be incident upon the 55\,MeV target stack using the MCNP6 fluence model, and a  fluence of \textred{196.9$\pm$11.3\,nAh} using the linear fit model.
+\textred{All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the beamline current integrators.}
+\textred{As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.}
+This incident fluence dropped by approximately \textred{8.9\% to  180.9$\pm$5.4\,nAh (and by 7.2\% to  182.7$\pm$13.5\,nAh using the linear fit model)} over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Voyles2018a,Graves2016}.
+This loss of fluence is due to a combination of 
+% beam utilization for the various 
+(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
+
+Using the final proton fluence at each energy position, cross sections for  \textred{(list of residual products)} were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils in the \textred{0--55\,MeV} region, as recorded in \autoref{tab:fe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Cu} foils, the (p,x) cross sections for  \textred{(list of residual products)} were extracted, as recorded in \autoref{tab:cufe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Ti} foils, the (p,x) cross sections for  \textred{(list of residual products)} were extracted, as recorded in \autoref{tab:ti_rp_table}.
+In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \textred{\ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb}} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
+Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity \textred{($\pm$3--7\%), proton fluence ($\pm$4--6\%), and foil areal density ($\pm$0.1--0.6\%).}
+% \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Fe}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+\label{tab:fe_rp_table}
+\small
+% \resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+% \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
+% \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
+% \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
+% \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
+% \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
+% \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
+% \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
+% \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
+% \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
+% \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
+\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
+\end{tabular}
+% }
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+\label{tab:cufe_rp_table}
+\small
+% \resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+% \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
+% \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
+% \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
+% \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
+% \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
+% \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
+% \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
+% \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
+% \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
+% \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
+\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
+\end{tabular}
+% }
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+\label{tab:ti_rp_table}
+\small
+% Disable next line for journal submission
+% \resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+% \ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
+% \ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
+% \ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
+% \ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
+% \ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
+% \ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
+% \ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
+% \ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
+% \ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
+% \ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
+% \ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
+\ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
+\end{tabular}
+% }
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
+\label{tab:fe_ibr_table}
+\small
+% \resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllll@{}}
+\toprule
+                               & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
+E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
+E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
+\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
+\end{tabular}
+% }
+\end{table}
+
+\textred{Placeholder text follows...fill in actual discussion of results...}
+
+These results have several notable features.
+The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
+Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
+Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
+Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
+
+% Furthermore, t
+This work presents the first measurements of several observables in 
+% these mass regions.
+% This work reports the first experimental measurement of
+this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
+% It also represents  the first measurement of 
+the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
+The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
+Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
+% (${^{1}/_{2}}^{-}$)
+% ($\sfrac{1}{2}^-$) 
+isomer branching ratio via \ce{^{nat}Nb}(p,x).
+
+\textted{Comment on details of 51/52Mn production here...}
+
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
+This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
+% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
+\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
+% , which makes activity quantification trivial.
+% In addition, 
+\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
+Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
+Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
+This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
+
+\textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
+
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
+These include the non-standard positron emitters 
+\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
+\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
+% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
+and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
+Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
+The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
+This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+
+\subsection{Comparison of reaction modeling with experimental results}
+
+% In this work
+As mentioned before, cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
+This, in turn, offers the opportunity to 
+% use these data to gain insight into 
+gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
+The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
+The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
+The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
+% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
+
+The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
+% \cite{add_level_density_models_here}. 
+The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
+% \cite{add_level_density_models_here}.
+The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
+All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
+
+% \def\arraystretch{1.5}
+\begin{table}
+ \caption{Default settings for the reactions codes}
+ \label{tab:defaults}
+ \resizebox{\textwidth}{!}{%
+\begin{tabular}{ c c c c}
+
+ \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
+ EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
+ TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
+  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
+
+\end{tabular}
+}
+\end{table}
+
+% The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
+% Only total channel residual 
+Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
+% that have only one reaction channel, and that are 
+and at least 1\% of the total reaction cross section.
+% are discussed in detail. 
+% Residual production
+Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
+% the compound portion of the cross section
+being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
+% Some residuals, such as 
+Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
+% Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
+% Very small channels, 
+We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
+% are excluded because the modeling of their cross sections is 
+because their behavior is extremely sensitive  to  more dominant  channels.
+The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
+
+The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70\,MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
+The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
+The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50\,MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
+In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011 \cite{Titarenko2011}.
+
+The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
+TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
+EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{../nb_px_paper/figures/86Y.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
+ \label{fig:86Y}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{../nb_px_paper/figures/90Mo.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
+ \label{fig:90Mo}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\linewidth]{../nb_px_paper/figures/90Nb.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
+ \label{fig:90Nb}
+\end{figure}
+
+In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
+For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
+For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
+
+The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
+For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
+The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
+\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
 
@@
 
- Blah blah blah
+We present here a set of measurements of \textred{38} cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of \textred{five} isomer branching ratios.
+Nearly all cross sections have been reported with higher precision than previous measurements.
+\textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
+% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for V \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
+Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
 

### 2018-07-21 fe_px_paper/fe_body_text.tex
Finished 1st draft of acknowledgements section.
Finished most of 1st draft of intro section.

@@
 
-Blah blah blah
-
+The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides \cite{Qaim201731}. 
+The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives \cite{Mulford2005,Muller2014}.
+While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production.
 % The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
@@
 % Change up the next sentance a bit
-Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
+% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
 % \cite{Qaim201731}. 
 % Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
+One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications \cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
+In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET \cite{Graves2016}.
+As part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
+This was carried out in a  thin-foil stacked-target experiment, using proton irradiation of natural iron foils with titanium and copper monitor foils.
+While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons   \cite{Graves2016}.
+
+Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element, biologically relevant, and essential in trace quantities. 
+Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA, with high biostability at neutral pH \cite{Graves2015}.
+
+paraphrase more of graves talk on mn applicatiosn here...
+
+manganese is chelated well by DOTA , and has been shown to image antobodies for more than a week ofater administration
+
+longer useful imaging time than Zr89 PET
+
+While these efforts have been targeted towards the production cross section of the \ce{^{51,52g,52m}Mn} PET isotopes (as well as other emerging medical radionuclides), these measurements offer insight into the spin distribution of excited nuclear states, in the 5--55 MeV range.
+
+% In addition to the interest in the production of 51,52Mn for PET research, this experiment offered an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52g}Mn} (t½ =5.591±0.003 d; Jπ =6+) to \ce{^{52m}Mn} (t½ =21.1±0.2 m; Jπ =2+) ratio [5].
+A set of measured cross sections for the various natFe(p,x), natTi(p,x), and natCu(p,x) reactions between 5–55 MeV, as well as independent measurements of isomer branching ratios, are reported.
+% Figure 3 shows the 52mMn(2+)/52gMn(6+) isomer-to-ground state branching ratio for the naFe(p,αn) reaction, calculated using TALYS-v1.8 over the 20 - 55 MeV range spanned by the foil stack.
+It is possible to use this measurement to infer the spin cut-off σ2, the width of the angular momentum distribution of the level density [6], [7].
+The isomer-to-ground state ratio lends insight into equilibrium / pre-equilibrium nature of reactions in this energy region, useful when attempting to minimize dose from an unwanted isomer/ground state of a medical radionuclide.
+
+These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but also as new measurements to improve the reliability of the range of modern reaction modeling codes.
+In addition, these experiments provide valuable insight into the challenges and unexpected nuances involved in precision cross section data measurements.
 
@@
 
-\textted{Comment on details of 51/52Mn production here...}
+\textred{Comment on details of 51/52Mn production here...}
 

### 2018-07-22 fe_px_paper/fe_body_text.tex
Finished 1st draft of manuscript. Still finishing data analysis, but the language is good to go!

@@
 Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element, biologically relevant, and essential in trace quantities. 
-Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA, with high biostability at neutral pH \cite{Graves2015}.
+Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH \cite{Graves2015}.
+\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection \cite{Dong2015}.
+Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu} \cite{Graves2015}.
+\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging. 
+However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging \cite{Dong2015}.
+The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$ = 96.6\%, $E_{\beta\text{, avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose  \cite{Dong2015}.
+Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies \cite{Wang2017}.
+\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn}, more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
+In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications \cite{Wang2017}.
 
-paraphrase more of graves talk on mn applicatiosn here...
+% While these efforts have been targeted towards the production cross section of the \ce{^{51,52g,52m}Mn} PET isotopes (as well as other emerging medical radionuclides produced in these irradiations), these measurements offer insight into the spin distribution of excited nuclear states, in the 5--55 MeV range.
 
-manganese is chelated well by DOTA , and has been shown to image antobodies for more than a week ofater administration
+% In addition to the interest in the production of\ce{^{51,52g,52m}Mn} for PET research
 
-longer useful imaging time than Zr89 PET
+While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6+$)   ratio \cite{Dong2015,Wang2017}.
+Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
+These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in f$_{7/2}$ subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes.
+In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.
 
-While these efforts have been targeted towards the production cross section of the \ce{^{51,52g,52m}Mn} PET isotopes (as well as other emerging medical radionuclides), these measurements offer insight into the spin distribution of excited nuclear states, in the 5--55 MeV range.
-
-% In addition to the interest in the production of 51,52Mn for PET research, this experiment offered an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52g}Mn} (t½ =5.591±0.003 d; Jπ =6+) to \ce{^{52m}Mn} (t½ =21.1±0.2 m; Jπ =2+) ratio [5].
-A set of measured cross sections for the various natFe(p,x), natTi(p,x), and natCu(p,x) reactions between 5–55 MeV, as well as independent measurements of isomer branching ratios, are reported.
+% A set of measured cross sections for the various natFe(p,x), natTi(p,x), and natCu(p,x) reactions between 5–55 MeV, as well as independent measurements of isomer branching ratios, are reported.
 % Figure 3 shows the 52mMn(2+)/52gMn(6+) isomer-to-ground state branching ratio for the naFe(p,αn) reaction, calculated using TALYS-v1.8 over the 20 - 55 MeV range spanned by the foil stack.
@@
 
-These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but also as new measurements to improve the reliability of the range of modern reaction modeling codes.
-In addition, these experiments provide valuable insight into the challenges and unexpected nuances involved in precision cross section data measurements.
+% While this might seem obvious, the contributions to the slowing of the beam due to the adhesive has often been neglected in much work performed to date.
+While plays a limited role at high beam energies, it becomes increasingly important for proton energies below 25 MeV.
+
+% In addition to providing a potentially highly-valuable beam monitor, the Nb(p,x) reactions offer an opportunity to study the angular momentum deposition via pre-equilibrium reactions and the spin distribution in f$_{7/2}$ subshell nuclei via the observation of isomer-to-ground state ratios.
+
+% lee stuff:
+% 
+% In addition to the interest in the production of 51,52 Mn for PET research, this experiment offered
+% an opportunity to study the distribution of angular momentum in compound nuclear and direct
+% pre-equilibrium reactions via observation of the 52g Mn (t ½ =5.591±0.003 d; J π =6 + ) to 52m Mn
+% (t ½ =21.1±0.2 m; J π =2 + ) ratio. These results indicated were presented at the University of Oslo in
+% May 2017 5 and indicate that the constant
+% temperature nuclear level density model
+% which has had the greatest success at
+% reproducing most low-energy nuclear
+% reaction data fails to reproduce the
+% deposition of angular momentum at both
+% compound and pre-compound energies
+% (see figure 3). This result will be
+% discussed in greater detail in Mr. Andrew
+% Voyles’ doctoral dissertation, which is
+% expected to be completed by May 2018.
+% 
+% An important outcome from this work has an appreciation for the role played by the latex
+% adhesive on the Kapton tape used to contain the individual stacked targets. While this might
+% seem obvious, the contributions to the slowing of the beam due to the adhesive has been
+% neglected in work performed at LANL-IPF to date. While this is expected to play a limited role
+% at high beam energies, it becomes increasingly important for proton energies below 25 MeV.
 
@@
 
+% lee:
+% 
+% In addition to the interest in the production of 51,52 Mn for PET research, this experiment offered
+% an opportunity to study the distribution of angular momentum in compound nuclear and direct
+% pre-equilibrium reactions via observation of the 52g Mn (t ½ =5.591±0.003 d; J π =6 + ) to 52m Mn
+% (t ½ =21.1±0.2 m; J π =2 + ) ratio. These results indicated were presented at the University of Oslo in
+% May 2017 5 and indicate that the constant
+% temperature nuclear level density model
+% which has had the greatest success at
+% reproducing most low-energy nuclear
+% reaction data fails to reproduce the
+% deposition of angular momentum at both
+% compound and pre-compound energies
+% (see figure 3). This result will be
+% discussed in greater detail in Mr. Andrew
+% Voyles’ doctoral dissertation, which is
+% expected to be completed by May 2018.
+
 These results have several notable features.
@@
  \centering
- \includegraphics[width=0.5\linewidth]{../nb_px_paper/figures/86Y.pdf}
+ \includegraphics[width=0.5\linewidth]{./figures/51Mn_px.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298

### 2018-07-22 fe_px_paper/fe_body_text.tex
Updated labeling to prepare for merge into the dissertation.

@@
 
-\comment{Update these energies, post-analysis}
+% \comment{Update these energies, post-analysis}
+\textred{Update these energies after finalizing the analysis...}
 
@@
 %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{../nb_px_paper/figures/before_minimization_plot.pdf}{50}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
          %         \refstepcounter{subfigure}
-         \label{fig:before_minimization}
+         \label{fig:fe_before_minimization}
    \hspace{-5pt}}%
@@
          %         \refstepcounter{subfigure}
-         \label{fig:after_minimization}
+         \label{fig:fe_after_minimization}
    \hspace{-5pt}}%
@@
 \small
-% \resizebox{\textwidth}{!}{%
+\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lllllll@{}}
@@
 \end{tabular}
-% }
+}
 \end{table}
@@
  \caption{Default settings for the reactions codes}
- \label{tab:defaults}
+ \label{tab:fe_defaults}
  \resizebox{\textwidth}{!}{%
@@
  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
- \label{fig:86Y}
+ \label{fig:51Mn}
 \end{figure}
@@
  \centering
- \includegraphics[width=0.5\linewidth]{../nb_px_paper/figures/90Mo.pdf}
+ \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:90Mo}
+ \label{fig:temp_90Mo}
 \end{figure}
@@
  \centering
- \includegraphics[width=0.5\linewidth]{../nb_px_paper/figures/90Nb.pdf}
+ \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:90Nb}
+ \label{fig:temp_90Nb}
 \end{figure}

### 2018-12-11 Unzueta_NIM/HFNG NIM_V2.tex
Adding source from Mauricio's HFNG NIM

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage[caption=false]{subfig}
\captionsetup{font=normalsize,labelfont={bf,sf}}

\modulolinenumbers[1]

\journal{Journal of Nuclear Instruments and Methods}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

	\begin{frontmatter}

	\title{Design, Construction, and Characterization of a Compact DD Neutron Generator Designed for $^{40}Ar/^{39}Ar$ Geochronology}
	%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
	\iffalse
	%% Group authors per affiliation:
	\author[UCB]{Mauricio Ayllon\corref{mycorrespondingauthor}}
	\ead{mayllon@berkeley.edu}
	\author[UCB]{Cory Waltz}
		\author[livermore]{Joseph Bauer}
	\author[geochronology]{Tim Becker}
	\author[UCB]{Lee Bernstein}
	\author[UCB]{Ka-Ngo Leung}
	\author[UCB]{Leo Kirsch}
	\author[geochronology]{Paul Renne}
	\author[UCB]{Karl Van Bibber}

	\cortext[mycorrespondingauthor]{Corresponding author}

	\address[UCB]{Department of Nuclear Engineering, University of California, Berkeley, CA 94720, USA}
	\address[livermore]{Lawrence Livermore National Laboratory, Livermore, CA 94550, USA}
	\address[geochronology]{Berkeley Geochronology Center, 2455 Ridge Road,Berkeley, CA 94720, USA}

	\fi

\begin{abstract}

A facility based on a next-generation, high-flux DD neutron generator has been designed, constructed, commissioned, and characterized, and is now operational at the University of California Berkeley. The generator is designed for $^{40}Ar/^{39}Ar$ dating of geological materials. However, it has served numerous other applications such as medical isotope production studies, and others are being planned. In this work, we present a description of the High Flux Neutron Generator (HFNG) that includes simulation tools, analytical treatments, and experimental validation of results. The current yield is around $10^9\ n/s$ with future development aimed at achieving an output of over $10^{10}\ n/s$. Extensive analysis was performed in order to characterize the neutron yield, flux, and energy distribution at specific locations where samples can be irradiated. A particular design feature of the HFNG is irradiation of samples internal to the cathode, just a few millimeters away from the neutron production site, thus maximizing the flux, while minimizing the total neutron fluence. Moreover, the deuterium ion beam optics was simulated and optimized with different extraction configurations so as to provide a uniform neutron flux distribution and an acceptable heat load. Finally, experiments were performed in order to validate the aforementioned analysis.

\end{abstract}

	\begin{keyword}
		DD Neutron generator\sep MCNP simulations \sep ion beam optics \sep flux quantification \sep geochronology \sep activation foils \sep COMSOL Multiphysics
	\end{keyword}

\end{frontmatter}

	\linenumbers

\section{Introduction}

Fusion-based neutron generators are used in many fields of research, education, and industry. As opposed to other neutron sources such as research reactors, neutron generators provide nearly monoenergetic neutrons, pose a lower proliferation and radiological risk, do not produce high level waste, and can be made compact and portable, among other benefits. The most common reactions for this kind of generators are shown in Equations \ref{eq:reactionDD} and \ref{eq:reactionDT}. At low energies, DT reactions benefit from a resonance near 100 keV, which allows for a higher neutron yield at a given beam current. Around this energy, the yield from a DT source is slightly more than two orders of magnitude higher than that of a DD source. However, the neutron energy is also much higher, which can be a significant disadvantage, or even inapplicable for some purposes. Moreover, tritium poses greater radiological handling and licensing challenges.

\begin{align} \label{eq:reactionDD}
&^{2}H + ^{2}H \rightarrow ^{3}He + n + 3.27\ MeV\ (50\%) \\
&^{2}H + ^{3}H \rightarrow ^{4}He + n + 17.6\ MeV \label{eq:reactionDT}
\end{align}

Neutron generators are being used for a variety of applications including activation analysis, production of radioisotopes, fast neutron imaging, oil well logging, fundamental nuclear research, nuclear data measurements, etc. The High Flux Neutron Generator (HFNG) located at the University of California, Berkeley was designed and built by the Nuclear Engineering Department and the Berkeley Geochronology Center (BGC) with a primary application being the improvement of the $^{40}Ar/^{39}Ar$ dating technique, which consists on irradiating geological samples in order to produce measurable quantities of $^{39}Ar$ through the reaction $^{39}K(n,p)^{39}Ar$. Currently, samples are sent to reactors for neutron irradiation. A local source of DD neutrons would have many advantages in addition to convenience; the lower energy monochromatic DD neutrons would result in more precise age determinations by eliminating argon recoil out of the samples, and production of confounding isotopes that accompany the use of higher energy fission neutrons \cite{geochron}.

Since its commissioning, the HFNG has been proven useful for a variety of other applications including Prompt Gamma Neutron Activation Analysis (PGNAA) for on-site gamma detector calibration, cross-section measurements of relevant radioisotopes in medicine \cite{np_paper}, study of delayed gamma rays from fission of $^{238}U$, single event upset (SEU) of CPUs to develop radiation hardened electronics, study of the behavior of NaI detectors in a neutron field, and most recently, cross-section measurements of $^{35}Cl(n,p)^{35}S$ and $^{35}Cl(n,\alpha)^{32}P$, which are of significant interest for the design of molten salt reactors.

The HFNG works by accelerating positive deuterium ions towards a titanium target electrode biased up to -120 kV. These ions embed in the target matrix forming titanium hydride ($TiD_x$) where $x$ ranges from $0$ to $2$, thus representing a target for subsequent deuterium ions impinging upon the cathode, and initiating the fusion reaction shown in Equation \ref{eq:reactionDD}. Neutrons are born at slightly different energies and relative yields with respect to the angle formed with the beam direction (taken to be $0^{\circ}$). Precise characterization of the neutron distribution and energy spectrum was crucial for several of the experiments previously outlined, requiring that simulation tools and experimental validation be developed together.

\section{Description of the Facility and the Neutron Generator}

The HFNG is designed around two radio frequency-driven multicusp ion sources that straddle a titanium copper target, as shown in Figure \ref{fig:HFNG}. This arrangement allows for doubling the deuterium current incident on the target, hence doubling the neutron flux at the sample location. This type of ion source produces positive deuterium ions by ionizing deuterium gas with an RF field of 13.56 MHz. The ions are then confined by means of neodymium magnets in copper chambers with quartz windows. The major benefit of this type of ion source is the production of predominantly monatomic deuterium ions \cite{wuThesis}, which is important since heavier allotropes of deuterium achieve lower ultimate energies at specified extraction potentials. Because the DD fusion cross-section is an increasing function of the reaction energy up to about 2.2 MeV (deuteron breakup energy), lower interaction energy reduces the neutron yield.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pics/cutaway}
	\caption{Cross-sectional view of the HFNG exposing the shroud, target, and ion sources.}
	\label{fig:HFNG}
\end{figure}

The target, shown in Figure \ref{fig:new_target}, is mostly made of copper due to its excellent thermal conductivity. However, copper does not form hydrides as well as titanium does \cite{CRC}. Therefore, a thin layer (120 microns) of titanium is explosion bonded onto the copper structure. The unique design of this target allows for samples to be placed very close to the neutron emitting spot ($\approx 8 mm$ relative distance), hence maximizing the neutron flux at the sample location. Active cooling with deionized water is needed in order to dissipate the heat load generated by the deuterium beam incident upon the surface of the target. The target is biased at a negative potential (up to -120 kV) in order to extract the positive deuterium ions.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pics/new_target}
	\caption{Target assembly showing the CAD design of the faceplate and the actual target soldered in place.}
	\label{fig:new_target}
\end{figure}

The target is encased in a shroud electrode biased at an even lower potential ($\Delta V=2.4\ kV$) through an arrangement of diodes in order to reverse the direction of the electric field inside this structure. The circuit diagram is shown in Figure \ref{fig:diodes}. Without a shroud, electrons that are sputtered off the titanium target after the deuterium ions impinge on the target would experience a repulsive electrostatic force that would accelerate them back towards the extraction plate causing overheating (or even melting) of surrounding structures, arcing, and a very large flux of bremsstrahlung X-rays. The electric field reversal inside the shroud makes the electrons experience a force back towards the target, which makes them return to it, hence mitigating the issues mentioned above. A detailed discussion of this technique has already been published \cite{electronSup}.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/diodes3}
	\caption{Circuit schematic of the diode assembly. Note that the voltage differential between the shroud and the target can be varied from 0 to 2.4 kV.}
	\label{fig:diodes}
\end{figure}

The vacuum chamber is evacuated by a scroll pump connected in series with a turbo-pump. The scroll pump is oil-free; this is important as the HFNG produces a certain amount of tritium during operation, which readily binds with oil molecules. Furthermore, a scroll pump can be operated continuously without the risk of backstreaming fluids.

A polyethylene structure was constructed that can be assembled around the HFNG to thermalize neutrons for different types of experiments. In general, nuclear reactions of the type $(n,\gamma)$ have higher absorption cross-sections at lower energies.

There is also an external beam port aligned with the neutron emitting spot of the HFNG in order to perform experiments outside the vault. Some experiments that have been performed using the external beam line include characterization of gamma detectors in a neutron field, and prompt gamma activation analysis of various materials.

The HFNG uses a residual gas analyzer (RGA) system that allows for continuous/on-line monitoring of the gas composition inside the chamber. It serves as a leak detector as well as a reliable indicator of water vapor, which can cause a variety of problems during operation.

\section{Neutron Yield, Flux and Energy Distribution}

The neutron yield has been experimentally determined in an indirect way. Flux measurements via activation foils were carried out (Section 5) and compared to the simulations presented below. Experimental results agree with those of simulations to about 5\% at the sample holder location.

Note that a high yield neutron generator does not directly imply a high flux neutron generator. For instance, there are commercially available neutron generators with gas targets with DD neutron yields in the order of $10^{11}\ n/s$. However, the flux at any location around the target is several orders of magnitude lower and impractical for our purposes. Moreover, a neutron generator with a solid target but with a large beam spot compared to the sample also suffers from the same effect. In other words, the yield does not scale linearly with the flux when the beam spot increases. Therefore, the flux is maximized when we operate close to the heat load limit of the target. Hence, a narrow deuterium beam compared to the size of the target is desirable.

\subsection{Neutron Yield Analysis}

Some of the accelerated deuterons do not undergo fusion reactions at the energy specified by the voltage differential between the target and the plasma electrode due to two main processes: 1) deuterons slow down as they traverse the target volume before a fusion reaction occurs, and 2) the deuterium beam is not purely monatomic, which also lowers the interaction energy. Both of these processes result in a lower neutron output due to the fact that the DD fusion cross-section decreases with decreasing interaction energy. The slowing down process can be described using data for the energy loss per unit distance (stopping power) of deuterons in titanium \cite{SRIM}. Moreover, the deuterium beam is composed of monatomic, diatomic, and triatomic ion species. The heavier the species, the lower the final energy they achieve for a given target potential. For example, molecular deuterium accelerated to 100 keV will share this energy equally between the two deuterium nuclei i.e. 50 keV each. For RF ion sources, the deuterium is mostly monatomic. However, the exact composition is, for the most part, a function of the RF power. Similar ion sources have been studied \cite{multicusp2} and these reports indicate that at 1200 W (standard for the HFNG), the ratios between the three species are approximately 0.65:0.25:0.10, respectively. Even though RF ion sources produce mostly monatomic deuterium ions, the recombination process is significantly affected by the contact material. Insulators are better at hindering recombination, while conductors such as copper have much higher recombination coefficients.

The neutron yield can be approximated based on an analytical approach outlined in \cite{CRC} together with empirical data for the stopping power ($dE/dx$) of deuterons in titanium, the cross-section for the neutron-producing reaction in Equation \ref{eq:reactionDD}, the fraction of different deuterium species in the ion source, and the deuterium-to-titanium ratio in the self-loaded target, which was taken to be one-to-one for a conservative estimate. Equation \ref{eq:yield} was used to calculate the neutron yield as a function of deuteron energy, where $\phi_d$ is the deuteron flux ($cm^{-2}s^{-1}$) incident on the target, $n_d$ is the number density of deuterons in the target ($cm^{-3}$) when saturated, $\sigma(E_d)$ is the cross section for the DD neutron-producing reaction, and $dE/dx(E_d)$ is the energy loss per unit distance in titanium. Note that the lower limit of integration is taken to be zero since the Q-value of the reaction is positive. The yield calculated with this equation is an input for the MCNP \cite{MCNP} model, which calculates the neutron flux per source particle. This approach agrees with experiments relatively well, as discussed in the last section.

\begin{equation} \label{eq:yield}
Y(E_d)=\phi_d n_d \int_{0}^{E_{max}} \frac{\sigma(E_d)}{dE/dx(E_d)}dE_d
\end{equation}

\subsection{Neutron Flux and Energy Distribution}

The kinematics of the interaction between deuterons results in a variation of neutron energy as a function of angle in the lab frame. From energy and momentum conservation, the energy of the emitted neutron varies as shown in Figure \ref{fig:energy_dist}. Note that the variation can be quite significant. For instance, at zero deuteron incident kinetic energy, the energy of the emitted neutron is 2.45 MeV, while at 100 keV, the maximum is close to 2.8 MeV. The apparent violation of the conservation of energy principle is accounted for by the redistribution of the total available energy (Q-value plus incident deuteron energy) between the He-3 nucleus and the neutron.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/energy_dist}
	\caption{Neutron energy in the lab system as a function of angle.}
	\label{fig:energy_dist}
\end{figure}

The energy spectrum changes slightly as the neutron travels through the target. Therefore, different empirical correlations were found for thin and thick targets \cite{CRC}. The angular distribution is well-fitted with an expansion in Legendre polynomials, as shown in Equation \ref{eqn:energDist}. Note that this equation is valid for DD and DT reactions below $500\ keV$ for both, thin and thick targets.

\begin{equation}
E_n(E_d,\theta)=E_0+\sum_{i=1}^{n}E_i cos^i \theta
\label{eqn:energDist}
\end{equation}

The coefficients $E_i$ were determined for a few energy values only \cite{CRC}. Therefore, they were interpolated in this code using a cubic spline for any desired energy.

Furthermore, the neutron yield is also dependent on the emitted angle, and DD neutrons exhibit a larger anisotropy than DT neutrons. The highest yield in this kind of neutron generators is along the deuteron beam direction ($0^\circ$). The relative yield, defined as the total yield normalized to that at $90^{\circ}$, can be described by Equation~\ref{eqn:angDist}. This equation comes from a best fit model of the available data \cite{CRC}.

\begin{equation}
\frac{Y(\theta)}{Y(90^{\circ})}=A_0+\sum_{i=1}^{n}A_i cos^i \theta
\label{eqn:angDist}
\end{equation}

The coefficients $A_i$ were interpolated using a cubic spline for any desired voltage value. Figure~\ref{fig:yield} shows the relative yield distribution in the lab frame for various voltages.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{pics/rel_yield} 
		\caption{Relative neutron yield for different accelerating voltages (DD reactions).}
		\label{fig:yield}
	\end{center}
\end{figure}

We developed an MCNP model of the generator and surrounding structures. The neutron source is modeled according to experimental data obtained from \cite{Cross_sections}. The main purpose of such a model is to obtain the flux and energy distributions at different irradiation locations. The titanium target is considered to be ``thick'' in the sense that all accelerated deuterons either interact or stop within the target; deuterons penetrate the target a maximum of just under 1 micron at 120 kV, while the titanium layer is several hundred micrometers thick. The types of neutron sources considered in the MCNP model were point-like, disk, and Gaussian shaped, with the latter being the more accurate representation of the actual source (single-hole extraction). The code developed allows for different input parameters to be modified according to the experiment being performed. Such parameters include the acceleration voltage, the deuterium ion current, the atomic deuterium ion fraction in the plasma, the beam diameter, and the Gaussian profile of the beam. These results are shown in Figure \ref{fig:source_definitions}. Note that there is no significant difference among the three different source definitions for this specific case. However, if the irradiation location or the size of the samples change, it is important to re-check that these definitions agree.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/comp_sources_log}
	\caption{MCNP simulations for different source definitions in terms of energy distribution at the center of the sample holder location. Units on the y-axis are normalized per source neutron.}
	\label{fig:source_definitions}
\end{figure}

In order to take advantage of the variation of neutron energy as a function of angle, a L-shaped sample holder was designed and machined so that samples can be located in such a way as to span neutron energies between 2.4 - 2.8 MeV at 100 kV extraction voltage, as shown in Figure \ref{fig:L_holder}. This arrangement is particularly interesting for cross section measurements at different neutron energies. It has been used for $^{35}Cl(n,p)$ and $^{35}Cl(n,\alpha)$ reaction cross section measurements. The size of the energy window depends on the size of the sample, and MCNP simulations should be performed in order to quantify this energy spread. The sample slot located at $98^{\circ}$ allows for a ``clean'' neutron beam, which means that there is virtually no structural material in between the sample and the neutron emitting spot. This arrangement allows for a more narrow energy distribution, but at the expense of a reduced neutron flux due to the $1/r^2$ dependence and the kinematics of the reaction, as shown in Figure \ref{fig:yield}.

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{pics/L_holder_ang2}
	\caption{Sample holder that allows for irradiation of samples at different neutron energies. The values shown correspond to a 100 kV extraction voltage.}
	\label{fig:L_holder}
\end{figure}

\section{Ion Beam Extraction Analysis}

The deuterium beam is extracted from the plasma electrode of the ion source through either one or multiple apertures. The configuration and design of such an extraction mechanism largely determines the beam profile. Precise knowledge and control of the ion optics is necessary in order to 1) achieve a uniform beam profile on the surface of the target and 2) prevent the localized temperature to reach $\sim 200^{\circ}\ C$ \cite{AANG}. The first requirement ensures that the resulting neutron flux is also uniform over the sample to be irradiated, which is essential for several experiments such as the irradiation of geological samples \cite{geochron}. The second requirement has to do with the fact that deuterium degases from titanium around this temperature, which results in a lower neutron output. Moreover, if the heat load surpasses a certain value determined by the specific target configuration, the target can be eroded and destroyed.

The optimum beam spot size varies according to the application of the neutron generator. For example, a very small spot size is needed for fast neutron imaging because it enhances the sharpness of the image \cite{adams}. However, this requirement limits the beam current the target can handle, which in turn, limits the neutron yield at a given acceleration voltage. The HFNG allows for a variety of (exchangeable) extraction plate designs that result in different beam profiles depending on the application. Extensive analysis and modeling was performed for a single extraction aperture of 0.262 cm in diameter and a multiple-hole extraction plate.

A flat plasma meniscus at extraction is desired in order to achieve a uniform beam profile \cite{CoryThesis}. However, precise modeling of the plasma meniscus is complicated due to all the variables involved and the imperfect fidelity of plasma physics simulations (specially near plasma boundaries). Moreover, slight changes in electron temperature and ion density in the plasma affect the shape of the plasma meniscus, as determined by Bohm's Equation \cite{plasma}. Nevertheless, as the diameter of the extraction aperture decreases, the effects of the plasma meniscus on the resulting beam profile are greatly reduced, and at very small ($\sim 1\ mm$) apertures, the extracted beam is barely affected by focusing or defocusing effects due to the shape of the plasma meniscus.

The finite-element software package Comsol Multiphysics was used in order to simulate the ion beam trajectory for a single extraction aperture nozzle of 0.262 cm diameter and a 19-hole extraction electrode (each 1 mm id diameter), as shown in Figure \ref{fig:single_vs_mult}. The geometry of the setup is accurately represented as it is imported from a CAD program. The assumptions built into the simulations are as follows.

1) Ions are extracted from a flat plasma meniscus, which is a reasonably good assumption because of the small size of the extraction aperture and when operated near the Child-Langmuir limit.

2) All ions are born with the same speed and with a perpendicular velocity to the surface of the plasma. Even though the energy of the ions in the plasma follows the Maxwell-Boltzmann distribution, this assumption encompasses the overall behavior of the beam as it travels to the target.

Figure \ref{fig:beam_spread} shows the electric potential and the simulated particle trajectories at a target bias and beam current of 100 kV and 1.4 mA, respectively. Note in Figure \ref{subfig:beam_spread} that the equipotential lines near extraction result in a slightly focusing field. This is due to the geometry of our setup that required the ion source to be recessed back a certain distance in order to achieve the desired current density, reduce the maximum electric field in that region, and allow for the beam to spread so the heat flux on the surface becomes acceptable.

\begin{figure}
	\centering
	\subfloat[\label{subfig:beam_spread}]{\includegraphics[width=0.55\textwidth]{pics/beam}}
	\hfill
	\subfloat[\label{subfig:beam_in_shroud}]{\includegraphics[width=0.445\textwidth]{pics/beam_shroud}}
	\caption{Comsol simulation of electric field and deuteron beam trajectory at 100 kV and 1.4 mA.}
	\label{fig:beam_spread}
\end{figure}

The resulting beam spot size and heat deposition on the target are shown in Figure \ref{fig:beam_spot2}. Note that the beam profile in a) is not uniform across the target, and there is localized heating (and neutron production) near the edges. Therefore, a convex-shaped extraction nozzle was designed, whose purpose is to counteract the focusing electric field experienced near the aperture. The nozzle design is shown in Figure \ref{fig:beam_spot2} b) and c). Note the defocusing effect of the nozzle due to the fact that the equipotential lines are slightly convex downstream of the beam path. The beam spot is not only more uniform, but it is also spread throughout a larger area, which reduces the heat load on the target.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/beam_spot2}
	\caption{Beam spreading by modification of the extraction plate: a) flat extraction, b) and c) convex extraction, d) burn mark on target.}
	\label{fig:beam_spot2}
\end{figure}

Experimental results show a high degree of consistency with simulations based on the beam spot size (diffuse burn mark measured to be around 10 mm), and the resulting neutron flux distribution, as detailed in Chapter 5.

\subsection{Multiple-Hole Extraction System}

The uniformity of the beam spot and further spread of impingement area can be achieved by different means. For instance, an Einzel lens configuration, i.e. one or more extraction plates located downstream of the beam and biased at different potentials can give further control of the beam envelope. One of the downsides of such an arrangement is the higher degree of complexity added to the design, which stems from biasing, insulating, and properly installing these plates inside the vacuum chamber. Another option is the use of multiple apertures in the plasma electrode. Figure \ref{fig:CAD_extraction} shows an optimized design of a 19-hole extraction plate arranged in a hexagonal pattern, which was chosen in order to optimize the packing fraction and the uniformity of the beam.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pics/CAD_plate2}
	\caption{CAD drawing of an optimized 19-hole extraction plate.}
	\label{fig:CAD_extraction}
\end{figure}

In order to approximate the maximum beam current that can be extracted from each individual hole, the Child Langmuir law was employed, which sets a limit for the extractable current through an aperture assuming the system is space charge limited (enough ions are available in the ion source). This treatment was derived only for beam extraction between parallel plates, but serves as a good approximation for our purposes. Figure \ref{fig:child_lang} shows the maximum theoretical beam current that can be extracted as a function of the aperture diameter for the HFNG geometry at 100 kV. Because it is in our interest to keep the diameter of the apertures small, we chose a diameter of $1\ mm$, through which it is possible to draw a current of $\approx 0.196\ mA$. Therefore, for the 19-hole plate arrangement, it is theoretically possible to draw up to $3.7\ mA$, or a total of $7.4\ mA$ if both ion sources are used. This current value is an approximation, but it serves as a conservative input parameter for the ion beam simulations. In fact, the observed current limit was 3.5 mA, confirming the validity of this approximation.

 \begin{figure}
 	\centering
 	\includegraphics[width=0.7\textwidth]{pics/childLang}
 	\caption{Maximum extractable current according to Child Langmuir law for the HFNG geometry at 100 kV.}
 	\label{fig:child_lang}
 \end{figure}

Simulations show a more uniform beam profile near the center and a larger impingement area, which translates into a lower heat flux than that of a single hole even at higher current values. Beam current can be further increased by adding more holes or by increasing the size of the holes. The increase in current can be limited by the maximum number of holes that can be drilled on the plate or by the increase in chamber pressure due to a larger open area between the ion source and the rest of the vacuum chamber. The latter could make the gas pressure too high for optimum operation.

The geometry of the HFNG is such that there exists a focusing electric field at extraction, as shown in Figure \ref{fig:beam_spread}. Therefore, off-centered beamlets experience a focusing force, which depends on their location with respect to the center. For instance, beamlets further away from the center experience a stronger focusing force because the equipotential lines are more concave in that region. Therefore, multiple-extraction hole systems produce a convergent beam envelope. In contrast, a single hole in the center produces a divergent beam envelope, as shown in Figure \ref{fig:single_vs_mult}. The reason for this spread is somewhat due to space charge. However, the main reason is the initial focusing provided by the extraction hole itself, which causes deuterons to cross over and then diverge. This phenomenon is depicted in Figure \ref{fig:cross_over}. Essentially, each extracting aperture acts as a non-linear electrostatic lens with spherical aberration (not focused to a point) \cite{Plasma}.

\begin{figure}
	\centering
	\includegraphics[height=0.6\textwidth]{pics/cross_over_comp}
	\caption{Simulation of deuteron trajectories near extraction. Note the convergent field (b) that provides the initial focusing force that is ultimately responsible for the spreading of the beam.}
	\label{fig:cross_over}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/single_vs_mult2}
	\caption{The beam envelope for a single beam located at the center is divergent while that of multiple holes is convergent.}
	\label{fig:single_vs_mult}
\end{figure}

If there were no spacer, the beamlets would not experience a focusing force and the beam envelope would be divergent, as shown in Figure \ref{fig:spacer_vs_noSpacer}. However, at such a close distance ($\approx 7\ cm$ from the target), the individual beamlets would not spread enough and the heat deposition per beamlet would be unacceptable.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pics/spacer_vs_noSpacer2}
	\caption{Beam envelope with spacer (top), and without spacer (bottom), showing the effect of the spacer, which gives an additional standoff of 7 cm; the spacer also introduces a focusing field.}
	\label{fig:spacer_vs_noSpacer}
\end{figure}

Simulations were performed in order to optimize the hole pattern distribution. The design curve shown in Figure \ref{fig:designC} shows the beamlet center at the target as a function of the beamlet location at the extraction plate. The dashed line shows the hypothetical case in which there is no focusing field and the beamlets are perfectly horizontal.

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/designC}
	\caption{Design curve used to estimate the center of the individual deuterium beamlets on the target. The dashed curve is for the case with no spacer (linear) and the solid curve for the current configuration.}
	\label{fig:designC}
\end{figure}

The optimization process focused on two parameters: reduction of heat flux on the target surface, and uniformity of the heat flux distribution, which translates into a more uniform (flat) neutron flux distribution at the sample location.

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/twoBeams}
	\caption{Comsol simulation results showing the center and outermost beamlets. The latter was placed so as to achieve a flat profile.}
	\label{fig:two_beams}
\end{figure}

Figure \ref{fig:two_beams} shows the 2D beam profiles of the center beamlet and the outermost beamlet. The latter was placed 9.8 mm from the center in order to achieve a flat beam profile on the target. The intermediate hole was placed in such a way that its corresponding beamlet would hit the target exactly midway between the other two. This location was calculated (from the design curve) to be 5.1 mm from the center. The resulting heat flux distribution is shown Figure \ref{fig:heat maps} (right). Note that evenly spaced extraction apertures result in a non-uniform distribution due to the uneven focusing effect explained previously. A design leading to an unacceptable heat profile is shown in Figure \ref{fig:heat maps} (left).

\begin{figure}
	\centering
	\includegraphics[height=0.6\textwidth]{pics/comparisonHeatMaps_plates2}
	\caption{Power density on the target for a non-optimized design (left) and a design optimized according to the design curve shown in Figure \ref{fig:designC}. }
	\label{fig:heat maps}
\end{figure}

Note that even though the spacing between the holes is larger on the optimized extraction plate design ($d \approx 2 \ cm$), the resulting beam profile on the target is similar in size as the non-optimized design ($d\approx 1.1 \ cm$), but with a higher degree of uniformity and reduced heat flux. Experimental tests validate these simulations, as shown in the experimental validation section.

\subsection{Heat Transfer Analysis}

The heat flux distribution on the target surface was modeled in Comsol using the heat transfer in solids module coupled with the turbulent flow module. Further details about the heat transfer analysis on the target can be found in \cite{CoryThesis}. Figure \ref{fig:temp_comsol} shows the temperature distribution on the surface of the target for three different beam profiles: single hole, non-optimized multiple-hole, and optimized multiple-hole extraction plate. Note that the three of them show maximum temperature values below the degassing temperature of hydrogen in titanium ($\approx 230\ ^{\circ}C)$. However, the simulations do not account for the inter-metallic phases between the copper and the titanium, or the bonding process itself. Experimentally, it was found that the neutron yield is lower in the case of diffusion bonding compared to the explosion bonded material. This might indicate that the latter has better heat transfer properties. Moreover, variations in the titanium thickness an purity of the metal can also affect the neutron yield. The thinner the titanium layer, the better the heat transfer properties of the target. The disadvantage of having a very thin titanium layer is that the target has a shorter lifetime due to ion sputtering.

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/temp_profiles2}
	\caption{Temperature maps on the target for different extraction plates a) single-hole b) multiple-hole, non-optimized, c) Multiple-hole optimized. Maximum temperature values are $104^{\circ}C$,  $155^{\circ}C$,  $114^{\circ}C$, respectively}
	\label{fig:temp_comsol}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/TiCu2}
	\caption{Metallographic test on the HFNG target showing the intermetallic phases between copper and titanium.}
	\label{fig:TiCu}
\end{figure}

Figure \ref{fig:TiCu} shows a metallographic test of the diffusion bonded target. Note that there is a region of about 25 $\mu m$ in the copper-titanium interface with two visible phases (CuTi intermetallics), which is difficult to include in the simulations and their effect on the heat transfer is unknown. However, the titanium thickness in the simulated model can be increased by that amount in order to remain conservative. Experimentally, it was determined that there is some overheating of the target in the case of the non-optimized extraction plate. This was evidenced by the initial increase in neutron dose rate rapidly followed by a decrease rate. The neutron yield in this case was similar to that of the single-hole extraction plate. However, the optimized geometry allows for an increase in neutron yield by a factor of $\approx 2.5$, which is expected from Equation \ref{eq:yield}.

\section{Experimental Validation of the Neutron Flux and Deuteron Beam Profile}

The neutron flux was experimentally determined by neutron activation analysis of nine natural indium foils arranged in a $3\times3$ array at the sample holder location shown in Figure \ref{fig:flux_map}. Indium is a soft metal that can be easily cut or machined to the desired size and shape. The foils were cut in the form of thin disks of about 0.9 cm in diameter. The isotope In-115 has a long lived ($t_{1/2}=4.486\ h$) isomer that decays by the emission of a 336 keV gamma ray to the ground state; this metastable state is populated by the reaction

\begin{equation} \nonumber
^{115}In(n,n')^{115m}In
\label{eqn:In115m}
\end{equation}

The nine indium foil arrangement allows for precise determination of the beam spot location with respect to the samples to be irradiated. Hence, the energy window can be well characterized for any given experiment. Further details on the flux measurements can be found in \cite{np_paper}.

The flux map for an experiment carried out at 100 kV and 1.4 mA is shown in Figure\ref{fig:flux_map}. Based on this experiment, it was determined that the center foil was located 0.5 mm above and 3.7 mm to the right relative to the center of where the deuterium ion beam strikes the surface of the target.

\begin{figure}
	\centering
		\includegraphics[width=0.9\textwidth]{pics/flux_map}
	\caption{Foil locations compared to the beam center.}
	\label{fig:flux_map}
\end{figure}

The multiple-hole extraction system was also tested and the results were compared to simulations. Figure \ref{fig:chamfered} shows the non-optimized beam spot on the target. Note that the hot spots (darker) can be observed exactly where simulations show they would be, as shown in Figure \ref{fig:heat maps} (a). The irregular pattern is due to an attempt to remedy the situation by chamfering a few holes on the vacuum side to about $60^{\circ}$ in order to achieve an arrangement closer to a pierce-like angle geometry, and thus reducing the heat flux by spreading the individual beamlets. However, the chamfering also enlarged the holes, leading to increased current in the beamlets, counteracting the intended reduction.

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{pics/chamfered}
	\caption{Non-optimized design with a few chamfered holes and the corresponding beam spot.}
	\label{fig:chamfered}
\end{figure}

Figure \ref{fig:optimized_notChamfered} shows the beam spot of the optimized extraction plate. Note that the beam size is accurately predicted by simulations, and it is similar in size as the non-optimized plate. The neutron flux at the central location was increased by a factor of 3.5 with such an arrangement.

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{pics/optimized_notChamfered}
	\caption{Optimized design and resulting beam spot.}
	\label{fig:optimized_notChamfered}
\end{figure}

The variations in color due to the deuterium beam on the surface of the titanium are an indication of the amount of hydrogen absorbed. We noticed that after a few minutes of irradiation, the color was black while after a long time (hours) of irradiation, the color becomes light gray.

\section{Conclusions and Outlook}

The HFNG is a multi-purpose versatile neutron generator that has been well characterized in terms of flux and energy distribution. Reliable simulation tools were developed coupled with experimental validation of the parameters of interest. Simulations included beam optics, heat transfer, neutron flux and energy distribution.

Moreover, neutron reflection studies are being investigated in order to increase the neutron fluence in the sample location. Heavy elements such as lead provide good reflection properties minimizing the energy loss per collision, which translates into an overall lower degradation of the energy spectrum.

The heat removal capability of the target is one of the most important limiting parameters for neutron flux increase since hydrogen degases from titanium if high enough temperatures are achieved. Moreover, the neutron spot size must remain small for the flux to increase linearly with current. It is possible to increase the yield by spreading the beam spot, but that would not correspond to a linear increase in flux.

\section{Acknowledgments}

We gratefully acknowledge a grant from the University of California Office of the President.

Work supported by NSF Grant No. EAR-0960138, U.S. DOE LBNL Contract No. DE- AC02-05CH11231, and U.S. DOE LLNL Contract No. DE-AC52-07NA27344.

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2018-12-11 Unzueta_NIM/HFNG NIM_Voyles_edits.tex
Adding source from Mauricio's HFNG NIM

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{gensymb}
\usepackage{siunitx}
\usepackage[caption=false]{subfig}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage [autostyle, english = american]{csquotes}

\usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% \usepackage{fixltx2e}
% \usepackage{refcount}
% \usepackage{siunitx}
% \usepackage{lastpage}
% \usepackage{textcomp}
\usepackage{mathtools}

\usepackage{xfrac}
% \usepackage{lmodern}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
\usepackage{listings}
\usepackage{mcode}
% \usepackage{longtable}
% \usepackage{subcaption}
% \usepackage{booktabs,siunitx}
\usepackage{gensymb}
% \usepackage[normalem]{ulem}

% \usepackage{mathtools, cuted}

% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{color}

% \usepackage[colorinlistoftodos]{todonotes}

% \usepackage[section]{placeins}
% \usepackage{multirow}

% \usepackage{lineno}

\captionsetup{font=normalsize,labelfont={bf,sf}}

\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}

\modulolinenumbers[1]

\journal{Journal of Nuclear Instruments and Methods}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

	\begin{frontmatter}

	\title{Design, construction, and characterization of a compact DD neutron generator designed for $^{40}Ar/^{39}Ar$ geochronology}
	%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
	\iffalse
	%% Group authors per affiliation:
	\author[UCB]{Mauricio Ayllon\corref{mycorrespondingauthor}}
	\ead{mayllon@berkeley.edu}
	\author[UCB]{Cory Waltz}
		\author[livermore]{Joseph Bauer}
	\author[geochronology]{Tim Becker}
	\author[UCB]{Lee Bernstein}
	\author[UCB]{Ka-Ngo Leung}
	\author[UCB]{Leo Kirsch}
	\author[geochronology]{Paul Renne}
	\author[UCB]{Karl Van Bibber}

	\cortext[mycorrespondingauthor]{Corresponding author}

	\address[UCB]{Department of Nuclear Engineering, University of California, Berkeley, CA 94720, USA}
	\address[livermore]{Lawrence Livermore National Laboratory, Livermore, CA 94550, USA}
	\address[geochronology]{Berkeley Geochronology Center, 2455 Ridge Road,Berkeley, CA 94720, USA}

	\fi

\begin{abstract}

A  next-generation, high-flux, compact DD neutron generator has been designed, commissioned, and characterized, and is now operational in a new facility  at the University of California, Berkeley. The generator, originally designed for $^{40}Ar/^{39}Ar$ dating of geological materials, has since served numerous additional applications, including medical isotope production studies, with others  planned for the near future. In this work, we present an overview of the High Flux Neutron Generator (HFNG) which includes simulation tools, analytical treatments, and experimental validation of results. The generator's current neutron yield is approximately $10^9$ n/s, with future development aimed at achieving an output of more than $10^{10}$ n/s. Extensive analysis was performed in order to characterize the neutron yield, flux, and energy distribution at specific locations where samples may be loaded for irradiation. A notable design feature of the HFNG is the possibility for  sample  irradiation internal to the cathode, just a few millimeters away from the neutron production site, thus maximizing the flux, while minimizing the total neutron fluence. Moreover, the deuterium ion beam optics were  and optimized by simulation for various extraction configurations, so as to provide a uniform neutron flux distribution and an acceptable heat load. Finally, experiments were performed in order to benchmark the modeling and characterization of HFNG operation.

\comment{Paper's title capitalization changed to reflect NIM standards.}

\comment{Unsure what you mean by \enquote{simulation tools}  (\enquote{...which includes simulation tools, analytical treatments... }).  Please clarify.}

\comment{Define ``a few'' mm - it should be something like 8mm, if I recall.}

\end{abstract}

	\begin{keyword}
		DD Neutron generator\sep MCNP simulations \sep ion beam optics \sep flux quantification \sep geochronology \sep activation foils \sep COMSOL Multiphysics
	\end{keyword}

\end{frontmatter}

	\linenumbers

\section{Introduction}

Fusion-based neutron generators are used in many fields of research, education, and industry. As opposed to many other neutron sources, such as thermal reactors, neutron generators provide nearly monoenergetic neutrons, pose a lower proliferation risk, do not produce high-level waste, and can be made compact and portable. The most common reactions for such a generator are shown in Equations \ref{eq:reactionDD} (\enquote{DD}) and \ref{eq:reactionDT} (\enquote{DT}). At low energies, DT reactions benefit from a resonance near 100 keV, which allows for a higher neutron yield at a given beam current. Around this energy, the neutron yield from a DT source is approximately  a factor of 80  greater than that of a DD source. \comment{This figure needs a citation, search in EXFOR/elsewhere.} However, the DT neutron energy spectrum is also much higher, which can be a significant disadvantage \comment{How?  Give an example or two.}, or even inapplicable for some purposes \comment{Again, be specific.  Give an example.}. Moreover, tritium poses greater radiological handling and licensing challenges.

\begin{align} \label{eq:reactionDD}
&^{2}H +\ ^{2}H \rightarrow\ ^{3}He + n + 3.27\ MeV\ (50\%) \\
&^{2}H +\ ^{3}H \rightarrow\ ^{4}He + n + 17.6\ MeV \label{eq:reactionDT}
\end{align}

Neutron generators are commonly used for a variety of applications including activation analysis, radioisotope production, fast neutron imaging, oil well logging, fundamental nuclear research, and nuclear data measurements \comment{You should probably cite a source or two to back up this claim}. The High Flux Neutron Generator (HFNG), located at the University of California, Berkeley, was designed and built by the Department of Nuclear Engineering  and the Berkeley Geochronology Center (BGC), with  primary application in the improvement of the $^{40}$Ar/$^{39}$Ar dating technique, which consists of irradiating geological samples in order to produce measurable quantities of $^{39}$Ar through the  $^{39}$K(n,p)$^{39}$Ar reaction. Currently, these samples must be  sent away to thermal reactors for neutron irradiation. A local source of DD neutrons would have many advantages in addition to convenience; the lower-energy quasi-monoenergetic DD neutrons would result in more precise age determinations by eliminating argon recoil out of the samples, in addition to reduced production of confounding isotopes which accompany irradiation via the use of higher-energy fission neutrons \cite{geochron}.

\comment{I'd check on this claim of reduced contaminant isotopes relative to fission neutrons.  DD will give roughly 2.2-2.8 MeV neutrons, whereas only about 15\% of watt spectrum neutrons are born above 3 MeV.  I don't think its the high-energy fission neutrons which are the problem, but the massive amount of thermals, which will produce a ton of unwanted (n,$\gamma$) activities.  Check this either way.}

Since its commissioning, the HFNG has been proven useful for a variety of additional applications including Prompt Gamma Neutron Activation Analysis (PGNAA) for on-site gamma detector calibration, cross-section measurements for emerging medical radioisotopes \cite{np_paper} \comment{Cite the n,p paper here, and make sure to update the paper's metadata: (\url{http://linkinghub.elsevier.com/retrieve/pii/S0168583X17308145})}, the study of delayed fission gamma rays in  $^{238}$U, inducing single event upsets (SEU) in CPUs for development of radiation hardened electronics, the study of  NaI detector response in neutron fields, and, most recently, cross-section measurements of $^{35}$Cl(n,p)$^{35}$S and $^{35}$Cl(n,$\alpha)^{32}$P, which are of significant interest for the design of molten salt reactors. \comment{I'd check with the people involved in each of these projects, to see if they have any citeable works for here.  In particular, I'm pretty sure Batch has a conference proceeding / publication for the Cl cross section work, and Leo has talked about the U238 fission gammas.}

The HFNG operates by accelerating positive deuterium ions towards a titanium target electrode biased at a -120 kV potential. These ions embed in the target matrix forming titanium deuteride ($TiD_x$, where $x$ ranges from $1$ to $2$), \comment{$x$=0 would just be titanium metal. Also, deuteride is the ionic name for $^2$H, hydride specifically applies to $^1$H.} forming an implanted target for subsequent deuterium ions incident upon the cathode to initiate the DD fusion reaction shown in Equation \ref{eq:reactionDD}. Neutrons are born with a well-characterized distribution of energies and relative yields with respect to the angle formed with the incident beam (taken to be $0^{\circ}$) \comment{Cite the Liskien \& Paulsen paper here, too}. Precise characterization of the neutron spectrum spectrum throughout the HFNG was crucial for  the applications previously outlined, requiring that simulation tools and experimental validation be developed together.

\section{Description of the Facility and the Neutron Generator}

The HFNG is designed around two radio frequency (RF)-driven multicusp ion sources which straddle a titanium-coated copper target, as shown in Figure \ref{fig:HFNG}. This arrangement allows for doubling the deuterium current incident upon the target, which effectively doubles the neutron fluence at the sample location \comment{Flux should be a vector quantify, fluence is scalar}. This type of ion source, based upon similar designs developed at the Lawrence Berkeley National Laboratory, produces positive deuterium ions by ionizing deuterium gas with an RF field of 13.56 MHz \comment{Cite the Q. Ji paper here:  dx.doi.org/10.1063/1.3267832}. The ions are confined by means of neodymium magnets in copper chambers with quartz windows. The major benefit of this  ion source design is the production of predominantly monatomic deuterium ions \cite{wuThesis},  since diatomic deuterium ions achieve lower ultimate energies at specified extraction potentials, reducing neutron yields. \comment{Other than D2 ions, what other allotropes are we concerned with?  If thats the only one, list it instead of saying ``heavier allotropes.''} Because the DD fusion cross-section is a monotonically increasing function of the incident deuteron energy up to approximately 2.2 MeV (the deuteron breakup energy), lower bias voltages  reduce the neutron yield.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/cutaway}
	\caption{Cross-sectional view of the HFNG exposing the shroud, target, extraction plate, and ion sources. \comment{Provide a reference length scale for this schematic, and possibly enlarge it a bit - it's hard to see at its current size, and the design is far more important here than the (n,p) NIM. Also, make sure that this is the ``final/optimized'' design you present later on.}}
	\label{fig:HFNG}
\end{figure}

The target, shown in Figure \ref{fig:new_target}, is primarily composed of copper due to its excellent thermal conductivity. However, copper does not form hydrides as well as titanium, so a thin layer (120 microns) of titanium is explosion-bonded onto the copper structure to enhance deuteride implantation \cite{CRC}. The unique design of this target allows for samples to be placed very close to the neutron production surface ($\approx 8$ mm separation), maximizing the neutron flux at the sample location. Active internal cooling with deionized water is necessary to dissipate the heat load generated by the deuterium beam incident upon the surface of the target. The target is biased at a negative potential (up to -120 kV) in order to extract the positive deuterium ions.

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{pics/new_target}
	\caption{Target assembly showing the CAD design of the faceplate and the actual target soldered in place. The gray titanium-coated copper production surface is visible in the center of the target, and cooling lines for deionized water are seen on the sides of the target. \comment{Feel free to modify this, but it needs a bit more explanation of what is visible in the target.  also needs to be enlarged}}
	\label{fig:new_target}
\end{figure}

The target is encased in a shroud electrode biased at an even lower potential ($\Delta V=2.4\ kV$) through an arrangement of diodes in order to reverse the direction of the electric field inside this structure. The circuit diagram is shown in Figure \ref{fig:diodes}. Without a shroud, electrons that are backscattered off of the titanium target by the deuterium ions would experience a repulsive electrostatic force, accelerating them back towards the extraction plate to cause arcing,  overheating (or even melting) of surrounding structures, and a very large flux of bremsstrahlung. The electric field reversal inside the shroud makes the electrons experience an attractive force which guides them back towards the target, mitigating the issues mentioned above. A detailed discussion of this technique has already been published \cite{electronSup}.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/diodes3}
	\caption{Circuit schematic of the diode assembly, for typical operation at a -XXXXX V bias potential. Note that the voltage differential between the shroud and the target can be varied from 0 to 2.4 kV. \comment{I thought we typically run at -120 kV?  Make sure that the values you quote in this diagram are consistent with normal operating conditions.}}
	\label{fig:diodes}
\end{figure}

The HFNG's internal vacuum chamber is evacuated by a scroll pump connected in series with a turbopump, designed to operate at an internal pressure of XXXXXX  \comment{List what a typical range of operating pressure is.}. The scroll pump is oil-free; since the HFNG produces a finite amount (approximately XXXXX uCi / hour of operation) of tritium during operation, which readily binds to oil molecules, oil-free pumps help minimize dispersible tritium contamination. \comment{Have we measured what typical tritium levels are produced duirng operation?  nCi / hr?  uCi/hr?  You say that a certain amount is produced, you need to quantify that here.} Furthermore, a scroll pump can be operated continuously without the risk of backstreaming fluids. The HFNG uses a residual gas analyzer (RGA) system that allows for continuous, on-line monitoring of the gas composition inside the chamber. It serves as both a leak detector, as well as a reliable indicator of water vapor, which causes a variety of problems during operation.  \comment{Like what?  Briefly describe the problems caused by water vapor.}

In addition to this standard internal irradiation, two alternative modes operation are presently available, providing the possibility to use the HFNG to provide a range of alternative neutron energy distributions for various applications.    A polyethylene structure was constructed and can be assembled around the HFNG to thermalize DD neutrons while maintaining high flux for internal irradiation \comment{Quote the flux/fluence we see for thermal poly operation.}. In general, neutron capture cross-sections follow a $1/v$ trend  at lower energies. In this mode of operation, the HFNG can be used as a compact alternative to thermal reactors for  $(n,\gamma)$ activation studies and isotope production.  \comment{I would insert a picture of both the poly shield, as well as the external beamline cage.  Later on, it would be well worth your while to include neutron spectra for each.  If this article is announcing the possibility to operate the HFNG in these 2 modes, we definitely need to have figures/results describing their characterization.}

Additionally, there is an external beam port which can be aligned at 90\degree\ ($\approx$2.45 MeV neutrons) with respect to the production surface  of the HFNG in order to perform experiments outside the vault. \comment{Correct me if I'm wrong, but wouldnt it be aligned with the 90-degree neutron production angle?  The neutrons are emitted in 4$\pi$, but mostly forward focused, so the beam port should just let through whatever solid angle it subtends?  Doubel check the energies I list here.} This port is connected to a shielded beam dump and allows for both collimated beams of fast neutrons, as well as a thermal spectrum, using a polyethylene plug in the beam port. A number of experiments  have already been performed using the external beam line, including characterization of gamma detectors in a neutron field, and prompt gamma activation analysis of various materials, with more planned for the future.

\comment{I provided a starting point, but for both the thermal shield and the external beam line, you need to explain WHY they are useful, not just list that they exist. }

\section{Modeling of Neutron Yield, Flux, and Energy Distribution}

\comment{The text starting off this section \enquote{The neutron yield has been experimentally determined...} isn;t appropriate to start off a section, as it is more of a conclusion / result.  I moved it to the conclusions instead. }

\subsection{Neutron Yield Analysis}

At the ion energy specified by the bias voltage, a fraction of the accelerated deuterons do not undergo DD fusion due to two main processes: 1) deuterons slow down as they traverse the target volume before a fusion reaction occurs, and 2) the deuterium ion beam is not purely monatomic, which also lowers the interaction energy \comment{Not sure what you mean by ``lowers the interaction energy.'' Please explain and reword.}. Both of these processes result in a lower neutron yield due to the fact that the DD fusion cross-section decreases with decreasing deuteron ion energy. This slowing  process can be described using data for the energy loss per unit distance (stopping power) of deuterons in titanium \cite{SRIM}. Additionally, the deuterium beam is composed of monatomic (D$^+$), diatomic (D$_2^+$), and triatomic (D$_3^+$) ion species. For heavier  species, the final energy they achieve for a given target potential is lower. For example, molecular (diatomic) deuterium accelerated to 100 keV will share this energy equally between the two deuterium nuclei, \emph{i.e.}, each ion has an energy of 50 keV. For RF ion sources, the deuterium is strongly monatomic, however, the exact composition is, for the most part, a function of the RF power. \comment{Why?  Explain, and provide sources.}  Similar ion source designs have been characterized \cite{multicusp2},  indicating that at 1200 W (standard for the HFNG), the ratios between the three species are approximately 0.65:0.25:0.10, respectively. Even though RF ion sources produce mostly monatomic deuterium ions, the recombination process is significantly affected by the contact material.
\comment{Provide a source!} Insulators are better at hindering recombination, while conductors such as copper have much higher recombination coefficients.   \comment{Provide a source!}

The neutron yield can be approximated based on an analytical approach outlined in \cite{CRC}, together with empirical data for the stopping power ($dE/dx$) of deuterons in titanium, the cross-section for the neutron-producing DD reaction, the fraction of different deuterium species in the ion source, and the deuterium-to-titanium ratio in the self-loaded target, which was taken to be one-to-one for a conservative estimate. \comment{Is this  a mass ratio?  Atom ratio?  Specify.} Equation \ref{eq:yield} was used to estimate the neutron yield as a function of deuteron energy ($E_d$), where $\phi_d$ is the deuteron flux (cm$^{-2}$s$^{-1}$) incident on the target, $n_d$ is the number density of deuterons in the target (cm$^{-3}$) when saturated, $\sigma(E_d)$ is the cross section for the DD neutron-producing reaction (mb?), and $dE/dx(E_d)$ is the energy loss per unit distance in titanium. Note that the lower limit of integration is taken to be zero since the Q-value of the reaction is positive. This estimated yield  is an input for the MCNP \cite{MCNP} model, which calculates the neutron flux per source deuteron.

\comment{If the flux profile comes from MCNP, and you use the resulting yield as MCNP input, isn;t that a circular system?  This needs a lot of work to clarify what you refer to.}

\comment{Where do you get each of these quantities from?  Please specify.  I assume flux comes from MCNP, cross section from Liskien-Paulsen, stopping power from SRIM.  Cite each here after you mention them, for clarity.}

\comment{How do you determine when the the target is saturated? and how you measure the number density at that point?  REALLY elaborate on that here.}

This approach agrees with experiments relatively well, as discussed in the last section.  
\comment{You can't just say ``relatively well'' - provide a concrete number, and consider moving discussion of results to later on, since you are here describing the input of modeling, not necessarily results yet.}

\begin{equation} \label{eq:yield}
Y(E_d)=\phi_d n_d \int_{0}^{E_{max}} \frac{\sigma(E_d)}{dE/dx(E_d)}dE_d
\end{equation}

\subsection{Neutron Flux and Energy Distribution}

The kinematics of the 2-body interaction between deuterons results in a well-characterized variation of neutron energy as a function of angle in the lab frame \comment{Provide source!  Likely Liskien-Paulsen}. This neutron energy-angle variation is seen for a range of ion energies in Figure \ref{fig:energy_dist}, clearly displaying that this variation is quite significant. For instance, at zero deuteron incident kinetic energy, the energy of the emitted neutron is 2.45 MeV, while at 100 keV, the maximum is close to 2.8 MeV. The apparent violation of  conservation of energy  is accounted for by the redistribution of the total excitation energy (Q-value plus incident deuteron energy) between the $^3$He nucleus and the neutron.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/energy_dist}
	\caption{Neutron energy in the lab system as a function of angle. With increasing ion energy, a wider spread in neutron energy is seen over the 0-180\degree\ range. \comment{If this is Liskien-Paulsen data, it needs to be cited here in teh caption, too.}}
	\label{fig:energy_dist}
\end{figure}

The energy spectrum changes slightly as the neutron travels through the target, \comment{What do you mean it ``changes slightly''?  Does it broaden? Dampen? Be specific. } leading to different empirical correlations  for thin and thick targets \cite{CRC}. \comment{Need to define thin vs thick target.  Give ranges in mg/cm$^2$.} The angular distribution is well-fitted with an expansion in Legendre polynomials, as shown in Equation \ref{eqn:energDist}. Note that this equation is valid for DD and DT reactions below $500$ keV deuteron energy for both thin and thick targets.

\begin{equation}
E_n(E_d,\theta)=E_0+\sum_{i=1}^{n}E_i cos^i \theta
\label{eqn:energDist}
\end{equation}

The coefficients $E_i$ were determined for a few energy values of deuteron energy \cite{CRC}. Therefore, they were interpolated in this code using a cubic spline to be applicable for a wider range of desired energy. \comment{Which code are you refrring to?  This is the first tiem you mention any code.  Please explain in-text.} Furthermore, the neutron yield is also dependent on the emitted angle, and DD neutrons exhibit a larger anisotropy than DT neutrons. \comment{Why?  Explain and provide sources.} The yield in this design of DD neutron generators is forward-focused, with the maximum yield in the direction of the incident deuteron beam  ($0^\circ$). The relative yield, defined as the total yield normalized to that at $90^{\circ}$, can be described by Equation~\ref{eqn:angDist}, a best-fit model of the available data \cite{CRC}.

\begin{equation}
\frac{Y(\theta)}{Y(90^{\circ})}=A_0+\sum_{i=1}^{n}A_i cos^i \theta
\label{eqn:angDist}
\end{equation}

\comment{Why do you choose to normalize to the 90\degree\ yield?  Please explain, and, if its an arbitrary choice, describe why you chose 90\degree\ over, say, 0\degree.}

The coefficients $A_i$ were interpolated using a cubic spline for various deuteron energies, with the resulting relative yield distributions in the lab frame  shown in Figure~\ref{fig:yield}.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{pics/rel_yield} 
		\caption{Relative neutron yield for different accelerating voltages. Neutron yield becomes increasingly more pronounced with larger voltage at forward and backward angles. \comment{In figure captions, you need to provide more than a description of what is in the figure, give commentary on its significance also.  Also, you use RY($\theta$) on the axis label here, but Y($\theta$) in \ref{eqn:angDist} - be consistent. }}
		\label{fig:yield}
	\end{center}
\end{figure}

\comment{Need to specifiy the version of MCNP you used, and cite its tech doc.}

An MCNP model of the generator and surrounding structures was developed, with the neutron source  modeled according to experimental data obtained from \cite{Cross_sections}. The primary purpose of such a model is to obtain the flux and energy distributions at different irradiation locations. The titanium target is considered to be ``thick'' in the sense that all accelerated deuterons either interact or stop within the target; deuterons penetrate the target a maximum of just under 1 micron at 120 kV \comment{You need a source for that}, while the titanium layer is several hundred microns thick. The types of neutron sources considered in the MCNP model were point-like, disk \comment{Specify diameter}, and Gaussian shaped \comment{Specify centroid and 1-$\sigma$ width}, with the latter being the most accurate representation of the actual source (single-hole extraction) \comment{What are you basing this ``most accurate'' claim on?  Benchmarking?  Back up your claim.}. The model  allows for different input parameters to be modified according to the experiment being performed. These tunable parameters include the acceleration voltage, the deuterium ion current, the atomic deuterium ion fraction in the plasma, the beam diameter, and the Gaussian profile of the beam. The resulting neutron energy distributions for each source definition are shown in Figure \ref{fig:source_definitions}. Note that there is no significant difference among the three different source definitions. \comment{to back up this claim, you really should provide a residuals plot, since at the current scaling of the figure, you can't look for any systematic differences.} However, if the irradiation location or the size of the samples change, it is important to re-check that these definitions are still consistent.  \comment{Why would you expect them to agree?}

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/comp_sources_log}
	\caption{MCNP-simulated energy distributions  at the center of the sample holder location for different source definitions. Flux units on the y-axis are normalized per source neutron. \comment{Your y-axis has no label, the units alone are insufficient. For the disk and Gaussian sources, you have to provide the parameters you used for each sources - diameter, and centroid and width, respectively. In the legend, capitalize the entries, and don't abbreviate Gaussian.  Also, you should comment on what causes the feature near 1.7 MeV.}}
	\label{fig:source_definitions}
\end{figure}

\comment{Make sure to comment on the paucity of thermal neutrons in this spectrum, and the importance of this for preventing unwanted (n,$\gamma$) contamination. You'll want to point back to this later in your results.}

In order to take advantage of the variation of neutron energy as a function of angle, an L-shaped sample holder, shown in Figure \ref{fig:L_holder}, was designed so that multiple samples can be loaded  to span neutron energies between 2.4 - 2.8 MeV at 100 kV extraction voltage. This arrangement is particularly interesting for cross section measurements, as it permits measurement at different neutron energies in a single irradiation. It has been used for $^{35}$Cl(n,p) and $^{35}$Cl(n,$\alpha)$ reaction cross section measurements. \comment{Check with Batch to see if he has anything we can cite for now, even if its just a conferenece talk.} The size of the energy window depends on the size of the sample, and MCNP simulations should be performed in order to estimate this energy spread. The sample slot located at $98.1^{\circ}$ allows for a ``clean'' neutron beam, which means that there is virtually no structural material in between the sample and the neutron production surface. This arrangement allows for a more narrow energy distribution (since no scattering occurs on structural materials), but at the expense of a reduced neutron flux due to the $1/r^2$ dependence and the kinematics of the reaction yield, as shown in Figure \ref{fig:yield}.

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{pics/L_holder_ang2}
	\caption{Sample holder that allows for irradiation of samples at different neutron energies. The energies shown correspond to a 100 kV extraction voltage. \comment{For teh leftmost two slots, it looks like they shoudl also be 54.8\degree\ and 76.7\degree\ positions, but you should label them such for clarity. Also, provide (eitehr  in the caption or drawn on with an arrow), dimensions for the holder - l x w x h, and sample slot diameter. In subfigure b), make the energy points larger and bolder. }}
	\label{fig:L_holder}
\end{figure}

\section{Ion Beam Extraction Analysis}

The deuterium beam is extracted from the plasma electrode of the ion source through either a single or multiple apertures. The configuration and design of such an extraction mechanism largely determines the beam profile. Precise knowledge and control of the ion optics is necessary in order to 1) achieve a uniform beam profile on the surface of the target and 2) prevent the localized temperature from reaching $\approx 200^{\circ}\ C$ \cite{AANG}. The first requirement ensures that the resulting neutron flux is also uniform over the sample to be irradiated, which is essential for  experiments such as the irradiation of geological samples \cite{geochron}. The second requirement has to do with the fact that implanted deuterium degases from titanium at XXXXX  \comment{Provide actual degassing temperature value here, and provide citation for it. You use 230 C later on, but 200 C.  Which is it?  Be consistent.}, which results in a lower neutron output. Moreover, if the heat load surpasses a certain value determined by the specific target configuration, the target can be eroded and destroyed. \comment{Give a ballpark value of this criticla failure heat load.}

The optimum beam spot diameter varies according to the application of the neutron generator. For example, a very small spot size (approximately XXX - YYY mm) \comment{fill in values.  When would larger spot size be advantageous?} is needed for fast neutron imaging as it enhances the sharpness of the image \cite{adams}. However, this requirement limits the beam current the target can handle, which, in turn, limits the neutron yield at a given acceleration voltage. The HFNG is designed for a variety of exchangeable extraction plate designs, which result in different beam profiles depending on the application. Extensive analysis and modeling were performed for a single extraction aperture of 0.262 cm in diameter and a multiple-hole extraction plate. \comment{Describe the process that led to the selection of this diameter.}

A flat plasma meniscus at extraction is desired in order to achieve a uniform beam profile \cite{CoryThesis}. However, precise modeling of the plasma meniscus is complicated due to the complex geometry of the HFNG and imperfect fidelity of plasma physics simulations (especially near plasma boundaries). Moreover, slight changes in electron temperature and ion density in the plasma significantly affect the shape of the plasma meniscus, as determined by Bohm's Equation \cite{plasma}. \comment{You refer to the Bohm equation here, include it in the text.} As the diameter of the extraction aperture decreases, the effects of the plasma meniscus shape on the resulting beam profile are greatly reduced, to the point that, at very small ($\approx 1\ mm$) apertures, the extracted beam is barely affected by focusing or defocusing effects.

The finite-element software package COMSOL Multiphysics \comment{Corrected capitalization to match the company. Please specify version and provide citation.} was used to simulate the ion beam trajectory for a single extraction aperture nozzle of 0.262 cm diameter and a 19-hole extraction electrode (each 1 mm internal diameter), as shown in Figure \ref{fig:single_vs_mult}. \comment{Again, you need to explain where the choice of these diameters and number of holes came from.  Iterative modeling> Cory's thesis?  Please specify.} The geometry of the setup is consistently represented in COMSOL, as it is imported from the CAD designs used for machining the HFNG's structural components. The assumptions built into the simulations are as follows:

1) Ions are extracted from a flat plasma meniscus, which is a reasonably good assumption because of the small size of the extraction aperture and when operated near the Child-Langmuir limit. \comment{Need a citation for Child-Langmuir law.}

2) All ions are born with the same speed and with a perpendicular velocity to the surface of the plasma. Even though the energy of the ions in the plasma follows a Maxwell-Boltzmann distribution, this assumption encompasses the overall behavior of the beam as it travels to the target.

Figure \ref{fig:beam_spread} shows the electric potential and the simulated particle trajectories at a target bias and beam current of 100 kV and 1.4 mA, respectively. Note in Figure \ref{subfig:beam_spread} that the equipotential lines near extraction result in a slightly focusing field. This is due to the HGNG geometry, which requires that the ion source to be recessed back a certain distance in order to achieve the desired current density, reduce the maximum electric field in that region, and allow for the beam to spread so the heat flux on the surface remains within acceptable limits of approximately XXXX.  \comment{Clarify what ``that region'' refers to, and giev a ballpark heat limit.}

\begin{figure}
	\centering
	\subfloat[\label{subfig:beam_spread}]{\includegraphics[width=0.55\textwidth]{pics/beam}}
	\hfill
	\subfloat[\label{subfig:beam_in_shroud}]{\includegraphics[width=0.445\textwidth]{pics/beam_shroud}}
	\caption{Comsol simulation of electric field and deuteron beam trajectory at 100 kV and 1.4 mA. \comment{Make a brief comment to indicate which direction corresponds to the RF source vs the target, to show perspective.  Repeat the comment about the apparent focusing field.}}
	\label{fig:beam_spread}
\end{figure}

The resulting beam spot size and heat deposition on the target are shown in Figure \ref{fig:beam_spot2}. Note that the beam profile in a) is non-uniform across the target, and  localized heating (and neutron production) is observed near the edges. Therefore, a convex-shaped extraction nozzle was designed, whose purpose is to counteract the focusing electric field experienced near the aperture. The nozzle design is shown in Figure \ref{fig:beam_spot2} b) and c). \comment{You mention the convex nozzle, but don;t describe its pitch / the forward and back diameters.  Please elaborate more detail regarding the shape of the nozzle, how you got to that particular design, and provide these numbers in the caption for Fig 9.} Note the defocusing effect of the nozzle due to the fact that the equipotential lines are slightly convex downstream of the beam path. The beam spot is not only more uniform, but it is also spread throughout a larger area, which reduces the heat load on the target.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{pics/beam_spot2}
	\caption{Beam spreading by modification of the single  0.262 cm diameter extraction plate nozzle: a) flat extraction, b) \& c) convex extraction, d) burn mark on target.\comment{Confirm that this is teh correct diamater in the caption, and describe / label the convex nozzle geometry. }}
	\label{fig:beam_spot2}
\end{figure}

Experimental results show a high degree of consistency with simulations based on the beam spot size (diffuse burn mark measured to be around 10 mm), and the resulting neutron flux distribution, as detailed in Chapter 5.

\comment{This claim is more appropriate to be included in the validation / section 5.  Consider moving it there, and expand on this.  What does ``high degree of consistency'' mean?  Elaborate and use numbers.}

\subsection{Multiple-Hole Extraction System}

\comment{You give the multi-hole plate its own subsection, create one for the single-hole plate also.}

The uniformity of the beam spot and further spread of heat load can be achieved by alternative means than optimizing a single extraction nozzle. For instance, an Einzel lens configuration, \emph{i.e.}, one or more extraction plates located downstream of the beam and biased at different potentials, can give further control of the beam envelope. One of the downsides of such an arrangement is the higher degree of complexity added to the design, which stems from biasing, insulating, and properly installing these plates inside the vacuum chamber. Another option is the use of multiple apertures in the plasma electrode. Figure \ref{fig:CAD_extraction} shows an optimized design of a 19-hole extraction plate arranged in a hexagonal pattern, which was chosen in order to optimize the packing fraction and the uniformity of the beam.

\comment{Why does optimizing packing fraction matter?  Explain.}

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pics/CAD_plate2}
	\caption{CAD drawing of the optimized 19-hole extraction plate. \comment{Good reference scale.  Mention the diameter of the individual holes.}}
	\label{fig:CAD_extraction}
\end{figure}

In order to approximate the maximum beam current that can be extracted from each individual hole, the Child-Langmuir law was employed, which sets a limit for the extractable current through an aperture assuming the system is space charge-limited (enough ions are available in the ion source). This treatment was derived only for beam extraction between parallel plates, but serves as a good approximation for our purposes. \comment{Why? How do you know it to still be applicable?} Figure \ref{fig:child_lang} shows the maximum theoretical beam current that can be extracted as a function of the aperture diameter for the HFNG geometry at 100 kV. \comment{Where does this data coem from? Child-Langmuir law? Explain and provide a citation.} Because it desirable to keep the diameter of the apertures small \comment{Why, if you could get more current extracted?  Elaborate a bit briefly on the tradeoff, and how to find a ``sweet spot''.}, we chose a diameter of $1\ mm$, through which it is possible to draw a current of $\approx 0.196$ mA. Therefore, for the 19-hole plate arrangement, it is theoretically possible to draw up to $3.7$ mA, or a total of $7.4$ mA if both ion sources are used. This current  is an approximation, but it serves as a conservative input parameter for  ion beam simulations. In fact, the observed current limit was 3.5 mA, confirming the validity of this approximation. \comment{Nice!}

 \begin{figure}
 	\centering
 	\includegraphics[width=0.7\textwidth]{pics/childLang}
 	\caption{Maximum extractable current according to Child Langmuir law for the HFNG geometry at 100 kV. \comment{Provide citation for Child-Langmuir here.}}
 	\label{fig:child_lang}
 \end{figure}

Simulations show a more uniform beam profile near the center and a larger impingement area, which translates into a lower heat flux than that of a single hole even at higher current values. Beam current can be further increased by adding more holes or by increasing the diameter of the holes. The increase in current can be limited by the maximum number of holes that can be drilled on the plate or by the increase in chamber pressure due to a larger open area between the ion source and the rest of the vacuum chamber. The latter could raise the gas pressure too high for optimum operation. \comment{What pressure limit would this be?}

The geometry of the HFNG is such that there exists a focusing electric field at extraction, as shown in Figure \ref{fig:beam_spread}. Therefore, off-centered beamlets experience a focusing force, which depends on their location with respect to the center. For instance, beamlets further away from the center experience a stronger focusing force because the equipotential lines are more concave in that region. Therefore, multiple-extraction hole systems produce a convergent beam envelope. In contrast, a single hole in the center produces a divergent beam envelope, as shown in Figure \ref{fig:single_vs_mult}. The reason for this spread is partially due to space charge effects, but is primarily due to the initial focusing provided by the extraction hole itself, which causes deuterons to cross over and then diverge. This phenomenon is depicted in Figure \ref{fig:cross_over}. \comment{Not sure if Fig 12 shows this clearly or not.} Essentially, each extracting aperture acts as a non-linear electrostatic lens with spherical aberration (not focused to a point) \cite{Plasma}.

\comment{This citation appears to be broken in your google drive version.}

\begin{figure}
	\centering
	\includegraphics[height=0.6\textwidth]{pics/cross_over_comp}
	\caption{Simulation of deuteron trajectories near extraction. Note the convergent field (b) that provides the initial focusing force that is ultimately responsible for the spreading of the beam. \comment{Figure is a bit unclear as to what it actually shows.  Label or describe where extraction, the ion sourecs and the target are, to illustrate the convergence, as its unclear currently.}}
	\label{fig:cross_over}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/single_vs_mult2}
	\caption{The beam envelope for a single beam, a),  located at the center is divergent while that of multiple holes, b), is convergent.}
	\label{fig:single_vs_mult}
\end{figure}

\comment{What is this spacer?  This is the first time you mention it, so you need to first descrobe what it is, what it does, dimensions, materials, etc.}

If there were no spacer, the beamlets would not experience a focusing force and the beam envelope would be divergent, as shown in Figure \ref{fig:spacer_vs_noSpacer}. However, at such a close distance ($\approx$ 7 cm from the target), the individual beamlets would not spread enough and the heat deposition per beamlet would be unacceptable.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pics/spacer_vs_noSpacer2}
	\caption{Beam envelope with spacer (top), and without spacer (bottom), showing the effect of the spacer, which gives an additional standoff of 7 cm; the spacer also introduces a focusing field.}
	\label{fig:spacer_vs_noSpacer}
\end{figure}

\comment{Im confused as to what you mean by beamlet center. Please explain before using teh term.  Is it the centroid of the overall beam pattern formed by all the beamlets?  Please elaborate.  Also, pick eitehr ``beamlet center'' or ``beam center'', and be consistent - see Fig 15 x- and y-axis label.}

Simulations were performed in order to optimize the hole pattern distribution. The design curve shown in Figure \ref{fig:designC} shows the beamlet center at the target as a function of the beamlet location at the extraction plate. The dashed line shows the hypothetical case in which there is no focusing field and the beamlets are perfectly horizontal.

\comment{What do you mean by perfectly horizontal?  The individual beamlets without a spacer should be divergent, I think.}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/designC}
	\caption{Design curve used to estimate the center of the individual deuterium beamlets on the target. The dashed curve is for the case with no spacer (linear) and the solid curve for the current configuration. \comment{Where does this data come from?  You never describe it anywhere, and it definitely needs to eb added.  Experimental measurement?  Simulation?  If it is simulation, how did you verify / benchmark that the simulations were reliable for the generation of this design curve?  These questions MUST be addressed. Why does teh solid line have uncertainties plotted, but the dashed line does not?  be consistent, and add uncertainties to the dashed line.}}
	\label{fig:designC}
\end{figure}

The optimization process focused on two parameters: reduction of heat flux on the target surface, and uniformity of the heat flux distribution, which translates into a more uniform  neutron flux distribution at the sample location.

\comment{Why was two rings of nozzles chosen?  Why not 3, or using the number of rings as a design parameter? The motivation behind this decision needs to be made explicitly clear in the text.}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/twoBeams}
	\caption{Comsol simulation results showing the center and outermost beamlets. The latter was placed so as to achieve a flat profile.}
	\label{fig:two_beams}
\end{figure}

\comment{By ``outermost beamlet'', do you mean the beamlet in the outer ring of nozzles?  Please make this more clear.}

Figure \ref{fig:two_beams} shows the 2D beam profiles of the center beamlet and the outermost beamlet. The latter was placed 9.8 mm from the center in order to achieve a flat beam profile on the target. 
\comment{Is this distance a center-to-center distance, or edge-to-edge? Is it a gap distance, or a pitch? Please make clear.}
\comment{Also, you show this figure, but don't comment on it.  You need to provide some commentary as to the significance of this figure, and what it tells you.}
The intermediate hole was placed in such a way that its corresponding beamlet would hit the target exactly midway between the other two. This location was calculated (from the design curve) to be 5.1 mm from the center. \comment{Again, specify center-to-center or edge-to-edge.} The resulting heat flux distribution is shown Figure \ref{fig:heat maps} (right). Note that evenly spaced extraction apertures result in a non-uniform distribution due to the uneven focusing effect explained previously. A design leading to an unacceptable heat profile is shown in Figure \ref{fig:heat maps} (left).

\comment{This paragraph needs a lot of work and clarification.  You say that the optimized design intermediate beamlets would hit the target exactly midway between the other two, but then turn around and say that evenly spaced extraction apertures result in a non-uniform distribution.  These two statements seem to contradict, so you need to further explain and reconcile them. Also, throughout this work (I've brought it a up a few times now), you keep referencing unacceptable heat loads, or critical failure heat loads, but you have yet to specify a number for this value.  Please give a ballpark number, and stick to it throughout. You also give no information about the pith and nozzle diameter used for it, so the reader has no information about how sensitive the nozzle layout is to heat load, since there is a significant difference seen in the two heat flux maps. This sense of sensitivity needs to be communicated, to show how close or far apart these two designs are in phase space.  Please rework all of this extensively.}

\begin{figure}
	\centering
	\includegraphics[height=0.6\textwidth]{pics/comparisonHeatMaps_plates2}
	\caption{Power density on the target for a non-optimized design (left) and a design optimized according to the design curve shown in Figure \ref{fig:designC}. \comment{See previous comment.  You need to give soem basic info (nozzle pitch and diameter), and comment on the reduced heat flux, removal of hot spots, spread of heat flux over larger area, more uniform heat flux, etc..}}
	\label{fig:heat maps}
\end{figure}

Note that even though the spacing between the holes is larger on the optimized extraction plate design ($d \approx 2 \ cm$), the resulting beam profile on the target is comparable in size as the non-optimized design ($d\approx 1.1 \ cm$), but with a higher degree of uniformity and reduced heat flux. Experimental tests validate these simulations, as shown in the experimental validation section.

\comment{Good.  Consider adding a brief comment of the \% difference in beam profile size, as well as a metric to describe the difference in uniformity between the two.}

\subsection{Heat Transfer Analysis}

The heat flux distribution on the target surface was modeled in COMSOL using its heat transfer in solids module coupled with the turbulent flow module. \comment{What about the (admittedly very low pressure) residual gas?  Does this heat TX model account for passive convection to the residual gas?  This needs to be commented on.} Further details about the target's heat transfer analysis may be found in \cite{CoryThesis}. Figure \ref{fig:temp_comsol} shows the temperature distribution on the surface of the target for three different beam profiles: single hole, non-optimized multiple-hole, and optimized multiple-hole extraction plate. \comment{You should reiterate the design specs of each here:  nozzle(s) diameter, and pitch.} Note that all plate designs show a maximum temperature below the degassing temperature of hydrogen in titanium ($\approx 230\ ^{\circ}C)$ \comment{You need to provide a citation for this value!}. However, the simulations do not account for the inter-metallic phases between the copper and the titanium, or the bonding process itself. Experimentally, it was found that the neutron yield is lower in the case of diffusion bonding compared to the explosion bonded material. This would seem to indicate that the latter has better heat transfer properties, but XXXXXX. \comment{Briefly comment again on why better heat TX improves neutron yield, and also provide another possible explanation for the differenec between the two bonding methods.} Additionally, variations in  titanium thickness and the purity of the metal affect the neutron yield -  thinner titanium layers have better  heat transfer properties in the target. \comment{Why is this?  Explain and provide sources.  Also, give rough figures of merit, e. g., a reduction in titanium thickness of 5\% improves heat transfer by 10\%.  Find actual numbers and insert them, and provide a counterargument for going too thin`- insufficient thickness for titanium to implant, I would assume.  You make a claim that thinner targets are better, so you need to back that up with ballpark numbers to illustrate how strong of an effect it is.} The disadvantage of having a very thin (less than XXXX mm) titanium layer is that the target has a shorter lifetime due to ion sputtering.  \comment{Fill in values, provide approximate target lifetime for this minimum thickness.  Wouldn't an incredibly thin target also be insufficient to have Ti implant, dramatically lowering neutron yield, since titanium is far better of a getter for hydrogen than copper?}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/temp_profiles2}
	\caption{Temperature maps on the target for different extraction plates a) single-hole b) multiple-hole, non-optimized, c) Multiple-hole optimized. Maximum temperature values are $104^{\circ}C$,  $155^{\circ}C$,  $114^{\circ}$C, respectively.  \comment{Very good.}}
	\label{fig:temp_comsol}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[height=0.5\textwidth]{pics/TiCu2}
	\caption{Metallographic cross-section of the HFNG target, clearly showing the Cu$_\text{x}$Ti$_\text{y}$ intermetallic phases between copper and titanium. \comment{You use $\micro$m in the text as a length scale, but inches here.  Pick one and be consistent for both.  I would go with $\micro$m.}}
	\label{fig:TiCu}
\end{figure}

Figure \ref{fig:TiCu} shows a metallographic  cross-section of the diffusion bonded target. Note that there is a region of about 25 $\micro$m in the copper-titanium interface with two visible phases (Cu$_\text{x}$Ti$_\text{y}$ intermetallics), which is difficult to include in the simulations and their effect on the heat transfer is unknown. \comment{This seems like a MAJOR red flag for a reviewer. You can actually fairly easily estimate the relative Cu/Ti composition, using an SEM / electron backscatter spectrometer, to gauge the relative abundance of Ti/Cu in each of the phases. Hosemann has such a capability, and we had to use it in 120.  I agree that the impact of this layer should be minor, but this seems to me like something that absolutely could not be published without addressing. I would see if you can use Hosemann's SEM (or have one of his grad students do it) to get this ratio in each phase, and incorporate it into you modeling.  This seems absolutely necessary.} However, the titanium thickness in the simulated model can be increased by that amount in order to remain conservative. \comment{Not necessarily conservative, as you;ve already noted before that its thermal and deuteride forming properties are significantly different than copper.  The impact should be minor, but we need to address this.} Experimentally, it was determined that there is some overheating of the target in the case of the non-optimized extraction plate. This was evidenced by the initial increase in neutron dose rate rapidly followed by a decrease in dose rate. \comment{This does not follow.  How does overhetaing lead to increased neutron yield, then reduced yield?  please explain in text.} The neutron yield in this case was similar to that of the single-hole extraction plate. However, the optimized geometry \comment{single-hole or multi-hole?  Please clarify.} allows for an increase in neutron yield by a factor of $\approx 2.5$, which is expected from Equation \ref{eq:yield}.

\comment{Your last sentence here doesn't make sense.  What parameter in Eqn 3 is being increased by the optimized design causing this factor of 2.5 increase in neutron yield?  Reword the sentence and be more specific, your logic doesn't follow.}

\section{Experimental Validation of the Neutron Flux and Deuteron Beam Profile}

The neutron flux was experimentally determined through neutron irradiation \comment{Neutron activtaion analysis typically refers more to (n,$\gamma$) analysis of abundance in a sample, and doesn't really precisely apply here.} of nine natural indium foils arranged in a $3\times3$ array at the sample holder location, as shown in Figure \ref{fig:flux_map}. \comment{Do you have a picture of the 3x3 sample holder? I think it would eb useful to include here, too.} Indium is a soft metal which can be easily cut into foils approximately 0.9 cm in diameter and XXX mm thick  \comment{Fill in thickness values.}. The naturally-occurring isotope $^{115}$In has a long-lived ($^{115\text{m}}$In t$_{1/2}=4.486 \pm 0.004$ h, IT=95.0 $\pm$ 0.7 \% to $^{115}$In \cite{Blachot2012}) \comment{Always cite the more recent NDS evaluation when quoting a half-life.  Use \url{http://linkinghub.elsevier.com/retrieve/pii/S0090375212000683} here.} isomer which decays by the emission of a 336.241 keV gamma ray to its ground state; this isomer is populated by the inelastic scattering reaction $^{115}$In(n,n')$^{115\text{m}}$In.
% \begin{equation} \nonumber
% ^{115}In(n,n')^{115m}In
% \label{eqn:In115m}
% \end{equation}
The nine indium foil arrangement allows for  \comment{With only 3 pixels in each axis, we can't really call it ``precise.''} determination of the beam spot location with respect to the 9 irradiated samples. Through the combination of MCNP modeling of neutron transport and  decay spectroscopy of the activated indium foils, the energy window and flux distribution subtended by each of the foils can be well-characterized for a given target configuration. Further details on the flux characterization can be found in the recent work of A.S. Voyles \emph{et al.} \cite{np_paper}.

The flux map for an irradiation carried out at 100 kV and 1.4 mA is shown in Figure\ref{fig:flux_map}. Based on this beam profile, simulated using XXXXXXXX, it was determined that the central foil in this 3 x 3 array was located 0.5 mm above and 3.7 mm to the right, relative to the center of the deuterium ion beam..

\comment{Describe source of data for beam profile/}

\begin{figure}
	\centering
		\includegraphics[width=0.9\textwidth]{pics/flux_map}
	\caption{3 x 3  indium foil locations superimposed over the beam center for XXXXX extraction plate; beam profile data calculated using XXXXXXX. The beam center is clearly vertically centered on the middle of the loaded samples, with a slight asymmetry of the neutron flux in the horizontal direction. \comment{Is teh black dot the location of the single nozzle? If so, comment on this in the caption.  You need a length/distance scale included for this figure, either one of the foils, or for the width of the whole thing.  Why are the foils drawn as pixel maps?  The activation of each foil is an integral measurement, so we can't really subdivide them.  Remove the internal grid markers.  Where does the data for the beam profile come from?  You need to describe that in both the text, and briefly comment in the caption.  The beam profile clearly has a color scale, you need to include that scale in this figure.}}
	\label{fig:flux_map}
\end{figure}

The multiple-hole extraction system was also validated in a similar fashion. \comment{You had mentioned that it was also compared to simulations.  Where is teh figure (comparable to Fig 20) illustrating the results of the simulations?  You can't just say that you compared your experimental results to simulations without showing proof.} Figure \ref{fig:chamfered} shows the non-optimized beam spot on the target. \comment{Briefly mention the nozzle diameter and pitch info again here.} Note that the hot spots (darker) can be observed exactly where simulations show they would be, as shown in Figure \ref{fig:heat maps} (a).  \comment{You should remove the referenec to Fig 17a here, and instead put another figure here (similar to Fig 20), overlaying the location of the multi nozzles over your calculated heat map and the 3x3 foils, like Fig 20.  This would be far more useful, and would condense all this information nicely, rather than forcing the reader to flip back and forth.} The irregular pattern is due to an attempt to remedy the situation by chamfering a few holes on the vacuum side to about $60^{\circ}$ in order to achieve an arrangement closer to a pierce-like \comment{What does this mean?  the description of pierce-like is too vague to determine what you mean to say.} angle geometry, and thus reducing the heat flux by spreading the individual beamlets. However,  chamfering  enlarges the holes, leading to increased current in the modified beamlets, counteracting the intended reduction and instead increasing the size of hot spots.

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{pics/chamfered}
	\caption{Non-optimized design with a few chamfered holes and the corresponding beam spot. The hot spots formed by increased heat load are clearly visible as darkened spots.  The chamfered nozzles appear to increase the intensity and size of these hot spots, rather than making the heat load more uniform.}
	\label{fig:chamfered}
\end{figure}

Figure \ref{fig:optimized_notChamfered} shows the beam spot of the optimized extraction plate. \comment{Briefly mention the nozzle diameter and pitch info again here.} Note that the beam size is accurately predicted by simulations, and it is similar in size to the non-optimized plate.  \comment{Same issue again. You refer to simulations accurately predicting experiments, but don't show any proof here.  Make a figure here, like for the non-optimized design, (similar to Fig 20), overlaying the location of the multi nozzles over your calculated heat map and the 3x3 foils, like Fig 20.  } The neutron flux at the central location was increased by a factor of 3.5 with such an arrangement.  \comment{Where does this number come from?  You can't just pull it out of the air, you must show how you calculated / measured it.}

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{pics/optimized_notChamfered}
	\caption{Optimized design and resulting beam spot. Compared to Figure  \ref{fig:chamfered}, hot spots are almost completely eliminated, and a far more uniform heat pattern is visible.}
	\label{fig:optimized_notChamfered}
\end{figure}

The variations in color due to the deuterium beam on the surface of the titanium are an indication of the amount of hydrogen absorbed. \comment{How do you know this? What is the mechanism for the color change?  Explain, and   cite a source.} Within a few minutes of the end of irradiation, the color was black, but faded to a  light gray after several hours since the end of irradiation.  \comment{A figure showing the difference in time would be highly valuable here, since you only mention this phenomenon in passing.}

\section{Conclusions and Outlook}

The HFNG is a multi-purpose, versatile neutron generator which has been well-characterized in terms of flux and energy distribution. Reliable simulation tools have been developed and benchmarked through experimental validation of the generator operation. These tools include modeling of the HFNG beam optics, heat transfer, neutron flux, and neutron energy distribution. Neutron yield and energy distribution has been independently experimentally determined  via indium activation foils. Experimental validation agrees with the simulations described here to within approximately 5\% at the sample holder location.

Moreover, neutron reflection studies are being investigated in order to increase the neutron fluence in the sample location. Dense compounds such as lead or calcium carbonate act as efficient neutron reflectors, minimizing the neutron energy loss per collision, which prevents significant moderation of the overall energy spectrum.

The heat removal capability of the HFNG target is one of the most important limiting parameters for increasing the generator's current neutron flux, since hydrogen degases from the titanium  target without sufficient heat transfer. Moreover, the neutron spot size must remain small \comment{Provide an estimate of how large is acceptable} for the flux to increase linearly with current. \comment{This is not the best place in the paper to make this claim for the first time.  Bring it up back in the target design sections, and provide a sourec here and there for this claim, since you never brought this up before.} While it is possible to increase the yield by intentionally spreading the beam spot, this would correspond to a nonlinear increase in flux, which complicates modeling of higher-current designs.

\comment{I think you need to expand the outlook here with more concrete goals for how to continue to imrprove the design, and give commentary on other potential applications for the generator. In particular, point out the potential capabilities of it if we could run DT in a similar design.}

It is important to note that a high yield neutron generator does not imply  high flux. For instance, commercially available gas-target neutron generators  with DD neutron yields on the order of $10^{11}$\ n/s \comment{DEFINITELY need to cite 1-2 sources for this claim}. However, the flux at any location around the target is several orders of magnitude lower and impractical for  purposes of geochronology. Moreover, a neutron generator with a solid target but a large beam spot relative to the sample also suffers from the same effect, as the sample is geometrically able to utilize only a fraction of the neutrons produced. In other words, the yield does not scale linearly with  flux as the beam spot increases. \comment{How does it scale, then?  Inversely?  Please elaborate.} For an ideal generator, the flux utilization is maximized when operating close to the heat load limit of the target, \comment{``Therefore'' doesn;t make sense to start this off, as you haven't mentioned heat load limits anywhere else in this paragraph.} with samples located as close to the neutron production surface as possible, and with  a narrow deuterium beam relative to the size of the target.

\comment{I would highly encourage you to read more about teh utilization  factor in our recent (n,p) NIM and elaborate on more of that here, in teh context of the design specifics.}

\section{Acknowledgments}

We gratefully acknowledge a grant from the University of California Office of the President.

Work supported by NSF Grant No. EAR-0960138, U.S. DOE LBNL Contract No. DE- AC02-05CH11231, and U.S. DOE LLNL Contract No. DE-AC52-07NA27344.

\section*{References}

\comment{If you submit to NIM, you need to use the elsarticle-num bibliography style.}

\comment{All paper titles listed here have incprrect capitalization - everything is lowercase, aside from teh very first letter.}

\comment{Check your bib file - several entries here appear broken.  [2] is missing my last name and needs to be updated with the volume and page numbers, [5] is missing a last name, [7] is missing a paper title, [8] is missing the author list (\url{https://doi.org/10.13182/NT11-135})}

\comment{When you use \emph{et al.}, it always comes after listing the 3rd author in a list of 3+ authors.  Using the elsarticle-num style should help here, but double check.}

\bibliographystyle{elsarticle-num}

% \bibliography{mybibfile}

\end{document}

### 2018-12-11 First_np_Paper/np_body_text.tex
Pushing minor edits made to the HFNG (n,p) paper during my dissertation editing

@@
 For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities.
-This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 min half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that in turn produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
+This is due to the fact that the contaminant \ce{^{115}In}(n,$\gamma$) reaction results in the production of \ce{^{116m}In} which has a 54 min half-life and results in the production of 1097 keV (58.5\% branching), 1293 keV (84.8\% branching) and 2112 keV (15.09\% branching) gamma-rays that, in turn, produce a significant number of 511 keV gammas from pair-production followed by annihilation \cite{Blachot2010}.
 The foils were counted together again after approximately 4 h of separate collection, to allow for nearly all of the produced \ce{^{116}In} to decay.
 % Example spectra for each production pathway can be seen in Figures \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.
-Example spectra for each production pathway can be seen in Figures \autoref{fig:main_spectra}a and \autoref{fig:main_spectra}b.
+Example spectra for each production pathway can be seen in  
+% Figures 
+\autoref{fig:main_spectra}a and \autoref{fig:main_spectra}b.
 
@@
 An optimal design for the neutron generator would also allow for the possibility of reflecting fast neutrons back onto the target to maximize their utilization for radionuclide production.
- This sort of \enquote{flux trap} has been used for the production of radionuclides in reactors, but has not to date been optimized for use with fast neutrons  at DD and/or DT neutron sources.
+ This sort of \enquote{flux trap} has been used for the production of radionuclides in reactors, but has not, to date, been optimized for use with fast neutrons  at DD and/or DT neutron sources.
  The HFNG, with its self-loading target and \enquote{flux trap} geometry, has many features that make it well-suited for such isotope production purpose.
@@
 Assuming a neutron flux of  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target, masses of 0.533 g of natural zinc and 0.337 g of natural titanium, and cross sections of 47.5 mb for \ce{^{64}Zn}(n,p)\ce{^{64}Cu}   and 26.26  mb for  \ce{^{47}Ti}(n,p)\ce{^{47}Sc}, theoretical saturation activities for current operation at the time of this work are estimated to be 1.5 kBq of \ce{^{64}Cu} and 0.11 kBq of \ce{^{47}Sc}.
-This falls short of the mCi (37 MBq) level required for commercial application by a factor of 3-4 orders of magnitude, but with the operation of the second deuterium ion source, increased current, and fast neutron reflection, this goal may  well be within reach.
+This falls short of the mCi (37 MBq) level required for commercial application by a factor of 3-4 orders of magnitude, but,  with the operation of the second deuterium ion source, increased current, and fast neutron reflection, this goal may  well be within reach.
 By increasing the activation target thickness to 1 cm (a factor of 10), switching to DT operation (a factor of 80), increasing current and running the second ion source (a factor of 60), and relying upon the higher (n,p) cross section at DT energies (a factor of approximately 3), we believe saturation activities of approximately 6 mCi of \ce{^{64}Cu} and 0.5 mCi of \ce{^{47}Sc} can be achieved.
@@
  While this is not consistent with the average neutron energy at the target location (2.76$^{+0.01}_{-0.02}$ MeV), the fact that it was close indicates the paucity of thermal neutrons in this central location.
- This in turn highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
+ This, in turn, highlights the usefulness of such compact DD-neutron sources  for producing \enquote{clean} activities via the (n,p) channel.  
 The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.

### 2018-12-11 nb_px_paper/nb_body_text.tex
Adjusting size of large tables in the Nb paper to fit in the margins of my dissertation.
Pushing minor edits made to the IPF Nb(p,x) paper during my dissertation editing

@@
 After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
-The specifications of the target stack design for this work is presented in \autoref{tab:stack_table}.
+The specifications of the target stack design for this work are presented in \autoref{tab:stack_table}.
 
@@
 % For reference, t
-The nuclear decay data used in this work is tabulated in Tables \ref{tab:nudat_table_monitors} and \ref{tab:nudat_table_nb} of \ref{data}.
+The nuclear decay data used in this work are tabulated in Tables \ref{tab:nudat_table_monitors} and \ref{tab:nudat_table_nb} of \autoref{data}.
 Data for photon attenuation coefficients were taken from the XCOM photon cross sections database  \cite{berger2011xcom}.
@@
 (\autoref{fig:Na_activity_compare}).
-Since no evaluated  cross section data exists in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exists),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na},
+Since no evaluated  cross section data exist in this energy region  for  \ce{^{28}Si}(p,x)\ce{^{22}Na}  (and only minimal \ce{^{nat}Si} data exist),  the TENDL-2015 library is used to estimate the expected relative EoB activities for \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na},
 % in comparison with the
@@
 % In principle, it would be possible  to 
-we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the apparent \ce{^{22,24}Na}  activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the Al monitor reactions, shown
+we can subtract  the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the apparent \ce{^{22,24}Na}  activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the Al monitor reactions, shown
 % The results of this  may be seen 
@@
 % Disable next line for journal submission
-% \resizebox{\textwidth}{!}{%
+\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lllllll@{}}
@@
 % \cite{add_level_density_models_here}.
-The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
+The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  affected by the discrete levels chosen for the normalization.
 All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.

### 2018-12-14 nuclear_data_needs/nuclear_data_needs.tex
Initial template for the Nuclear Data Needs review

% template.tex, dated April 5 2013
% This is a template file for Annual Reviews 1 column Journals
%
% Compilation using ar-1col.cls' - version 1.0, Aptara Inc.
% (c) 2013 AR
%
% Steps to compile: latex latex latex
%
% For tracking purposes => this is v1.0 - Apr. 2013

\documentclass[letterpaper]{ar-1col}
\usepackage[numbers]{natbib}

\usepackage[american]{babel}
% \usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% \usepackage{fixltx2e}
% \usepackage{refcount}
% \usepackage{siunitx}
% \usepackage{lastpage}
% \usepackage{textcomp}
\usepackage{mathtools}

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
% \usepackage{microtype}
\usepackage{listings}
% \usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% \usepackage{longtable}
% \usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}
\usepackage[normalem]{ulem}

% \usepackage{mathtools, cuted}

% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% \usepackage{color}

\usepackage[colorinlistoftodos]{todonotes}

% \usepackage[section]{placeins}
% \usepackage{multirow}

% \usepackage{lineno}

\usepackage{graphicx}% Include figure files
% \usepackage{dcolumn}% Align table columns on decimal point

% Sin and Cos with auto-parentheses 
\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
\newcommand{\expp}[1]{\exp{\left( #1\right)}}
\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
\newcommand{\pp}[1]{\left( #1\right)}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\norm}[1]{\lVert #1 \rVert}

\newcommand{\textred}[1]{\textcolor{red}{ #1}}
\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}

\newcommand{\cmmnt}[1]{}

\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}

\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}

\newcommand{\etal}{\emph{et\,al.}}

% Tweak sim for better inline text tilde
\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}

% \sisetup{separate-uncertainty=true,table-space-text-post = *}

\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}

% \newcounter{subfigure}[figure]

\newcommand{\subfigimg}[4][,]{%
  \setbox1=\hbox{\noindent\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
  \phantom{\usebox1}% Insert appropriate spcing
}
% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}

\usepackage{subfig}
% Remove a), b), etc labels from subfigs
\captionsetup[subfigure]{labelformat=empty}

% Sick of fighting siunitx - consistent text micro symbol
% DO NOT uncomment this!!! or else broken unicode (Âţ)
% \sisetup{math-micro=\text{µ},text-micro=µ}
% \si\micro
\newcommand{\mmicro}{\si\micro}

% \usepackage{adjustbox}

\makeatletter
% Make common definition of mean
\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}

\makeatother

\hyphenation{gamma-rays}

\setcounter{secnumdepth}{4}

% 
% 
% 
% Journal template info
% 
% 
% 
% 
% 
% 
% 
%

% Metadata Information
\jname{Xxxx. Xxx. Xxx. Xxx.}
\jvol{AA}
\jyear{YYYY}
\doi{10.1146/((please add article doi))}

% Document starts
\begin{document}

% Page header
\markboth{Author et al.}{Short title}

% Title
\title{Our Future Nuclear Data Needs}

%Authors, affiliations address.
\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid XXX Younes$^6$
\affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
\affil{$^2$Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
\affil{$^3$Brookhaven National Laboratory, Upton, NY 11973, USA}
\affil{$^4$Arjan's affiliations}
\affil{$^5$Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
\affil{$^6$Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}

%Abstract
\begin{abstract}
Abstract text, approximately 150 words. 
\end{abstract}

%Keywords, etc.
\begin{keywords}
keywords, separated by comma, no full stop, lowercase
\end{keywords}
\maketitle

%Table of Contents
\tableofcontents

% Heading 1
\section{INTRODUCTION}
Please begin the main text of your article here.

%Heading 1
\section{FIRST-LEVEL HEADING}
This is dummy text. 
% Heading 2
\subsection{Second-Level Heading}
This is dummy text. This is dummy text. This is dummy text. This is dummy text.

% Heading 3
\subsubsection{Third-Level Heading}
This is dummy text. This is dummy text. This is dummy text. This is dummy text.

% Heading 4
\paragraph{Fourth-Level Heading} Fourth-level headings are placed as part of the paragraph.

%Example of a Figure
\section{ELEMENTS\ OF\ THE\ MANUSCRIPT} 
\subsection{Figures}Figures should be cited in the main text in chronological order. This is dummy text with a citation to the first figure (\textbf{Figure \ref{fig1}}). Citations to \textbf{Figure \ref{fig1}} (and other figures) will be bold.

\begin{figure}[h]
\includegraphics[width=3in]{SampleFigure.pdf}
\caption{Figure caption with descriptions of parts a and b}
\label{fig1}
\end{figure}

% Example of a Table
\subsection{Tables} Tables should also be cited in the main text in chronological order (\textbf {Table \ref{tab1}}).

\begin{table}[h]
\tabcolsep7.5pt
\caption{Table caption}
\label{tab1}
\begin{center}
\begin{tabular}{@{}l|c|c|c|c@{}}
\hline
Head 1 &&&&Head 5\\
{(}units)$^{\rm a}$ &Head 2 &Head 3 &Head 4 &{(}units)\\
\hline
Column 1 &Column 2 &Column3$^{\rm b}$ &Column4 &Column\\
Column 1 &Column 2 &Column3 &Column4 &Column\\
Column 1 &Column 2 &Column3 &Column4 &Column\\
Column 1 &Column 2 &Column3 &Column4 &Column\\
\hline
\end{tabular}
\end{center}
\begin{tabnote}
$^{\rm a}$Table footnote; $^{\rm b}$second table footnote.
\end{tabnote}
\end{table}

% Example of lists
\subsection{Lists and Extracts} Here is an example of a numbered list:
% \begin{enumerate}
% \item List entry number 1,
% \item List entry number 2,
% \item List entry number 3,\item List entry number 4, and
% \item List entry number 5.
% \end{enumerate}

% Here is an example of a extract.
% \begin{extract}
% This is an example text of quote or extract.
% This is an example text of quote or extract.
% \end{extract}

\subsection{Sidebars and Margin Notes}
% Margin Note
\begin{marginnote}[]
\entry{Term A}{definition}
\entry{Term B}{definition}
\entry{Term C}{defintion}
\end{marginnote}

\begin{textbox}[h]\section{SIDEBARS}
Sidebar text goes here.
\subsection{Sidebar Second-Level Heading}
More text goes here.\subsubsection{Sidebar third-level heading}
Text goes here.\end{textbox}

\subsection{Equations}
% Example of a single-line equation
\begin{equation}
a = b \ {\rm ((Single\ Equation\ Numbered))}
\end{equation}
%Example of multiple-line equation
Equations can also be multiple lines as shown in Equations 2 and 3.
\begin{eqnarray}
c = 0 \ {\rm ((Multiple\  Lines, \ Numbered))}\\
ac = 0 \ {\rm ((Multiple \ Lines, \ Numbered))}
\end{eqnarray}

% Summary Points
\begin{summary}[SUMMARY POINTS]
\begin{enumerate}
\item Summary point 1. These should be full sentences.
\item Summary point 2. These should be full sentences.
\item Summary point 3. These should be full sentences.
\item Summary point 4. These should be full sentences.
\end{enumerate}
\end{summary}

% Future Issues
\begin{issues}[FUTURE ISSUES]
\begin{enumerate}
\item Future issue 1. These should be full sentences.
\item Future issue 2. These should be full sentences.
\item Future issue 3. These should be full sentences.
\item Future issue 4. These should be full sentences.
\end{enumerate}
\end{issues}

%Disclosure
\section*{DISCLOSURE STATEMENT}
If the authors have noting to disclose, the following statement will be used: The authors are not aware of any affiliations, memberships, funding, or financial holdings that
might be perceived as affecting the objectivity of this review.

% Acknowledgements
\section*{ACKNOWLEDGMENTS}
Acknowledgements, general annotations, funding.

% References
%
% Margin notes within bibliography
\section*{LITERATURE\ CITED}

To download the appropriate bibliography style file, please see \url{http://www.annualreviews.org/page/authors/author-instructions/preparing/latex}.

\noindent
Please see the Style Guide document for instructions on preparing your Literature Cited.

The citations should be numbered in order of appearance. For example:

% 
% 
% \begin{verbatim}
% \begin{thebibliography}{96}
% \expandafter\ifx\csname
% natexlab\endcsname\relax\def\natexlab#1{#1}\fi
% 
% \bibitem{Glashow:1961tr}
% Glashow SL. \textit{Nucl. Phys.} 22:579 (1961)
% 
% \bibitem{Weinberg:1967tq}
% Weinberg S. \textit{Phys. Rev. Lett.} 19:1264 (1967)
% 
% \bibitem{Salam}
% Salam A.  In \textit{Elementary Particle Theory: Relativistic
% Groups and Analyticity. Proceedings of the 8th Nobel Symposium},
% ed. N~Svartholm, p. 367. Stockholm: Almqvist \& Wiksell (1968)
% \bibitem{Fritzsch:1973pi}
% Fritzsch H, Gell-Mann M, Leutwyler H. \textit{Phys. Lett.} \textit{B} 47:365
% (1973)
% 
% \bibitem{Gross:1973id}
% Gross DJ, Wilczek F. \textit{Phys. Rev. Lett.} 30:1343 (1973)
% 
% \bibitem{Politzer:1973fx}
% Politzer HD. \textit{Phys. Rev. Lett.} 30:1346 (1973)
% 
% \bibitem{Kronfeld:2010bx}
% Kronfeld AS, Quigg C. \textit{Am. J. Phys.} 78:1081 (2010)
% 
% \bibitem{Langacker:2010}
% Langacker P. \textit{The Standard Model and Beyond. Series in
% High Energy Physics, Cosmology, and Gravitation}. Boca Raton:
% CRC/Taylor \& Francis (2010)
% 
% \bibitem{GT2}
% Quigg C. \textit{Gauge Theories of the Strong, Weak, and
% Electromagnetic Interactions}. Princeton, NJ: Princeton
% Univ. Press. 2nd ed. (2013)
% 
% \bibitem{MattS}
% Schwartz MD. \textit{Quantum Field Theory and the Standard Model}.
% Cambridge, UK: Cambridge Univ. Press (2013)
% 
% \bibitem{DynSM}
% Donoghue JF, Golowich E, Holstein BR. \textit{Dynamics of the
% Standard Model}. Cambridge, UK/New York: Cambridge
% Univ. Press. 2nd ed. (2014)
% \end{thebibliography}
% \end{verbatim}

This coding results in the following formatted bibliography:

\begin{thebibliography}{96}
\expandafter\ifx\csname
natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem{Glashow:1961tr}
Glashow SL. \textit{Nucl. Phys.} 22:579 (1961)

\bibitem{Weinberg:1967tq}
Weinberg S. \textit{Phys. Rev. Lett.} 19:1264 (1967)

\bibitem{Salam}
Salam A.  In \textit{Elementary Particle Theory: Relativistic
Groups and Analyticity. Proceedings of the 8th Nobel Symposium},
ed. N~Svartholm, p. 367. Stockholm: Almqvist \& Wiksell
 (1968)
\bibitem{Fritzsch:1973pi}
Fritzsch H, Gell-Mann M, Leutwyler H. \textit{Phys. Lett.} \textit{B} 47:365
(1973)

\bibitem{Gross:1973id}
Gross DJ, Wilczek F. \textit{Phys. Rev. Lett.} 30:1343 (1973)

\bibitem{Politzer:1973fx}
Politzer HD. \textit{Phys. Rev. Lett.} 30:1346 (1973)

\bibitem{Kronfeld:2010bx}
Kronfeld AS, Quigg C. \textit{Am. J. Phys.} 78:1081 (2010)

\bibitem{Langacker:2010}
Langacker P. \textit{The Standard Model and Beyond. Series in
High Energy Physics, Cosmology, and Gravitation}. Boca Raton:
CRC/Taylor \& Francis (2010)

\bibitem{GT2}
Quigg C. \textit{Gauge Theories of the Strong, Weak, and
Electromagnetic Interactions}. Princeton, NJ: Princeton
Univ. Press. 2nd ed. (2013)

\bibitem{MattS}
Schwartz MD. \textit{Quantum Field Theory and the Standard Model}.
Cambridge, UK: Cambridge Univ. Press (2013)

\bibitem{DynSM}
Donoghue JF, Golowich E, Holstein BR. \textit{Dynamics of the
Standard Model}. Cambridge, UK/New York: Cambridge
Univ. Press. 2nd ed. (2014)

\end{thebibliography}

% \end{thebibliography}

\end{document}

### 2018-12-15 nuclear_data_needs/nuclear_data_needs.tex
Patched ar-1col.cls to fix xcolor warnings
Added in the bibtex file, starting text conversion

@@
 % \usepackage{amsmath}
-\usepackage[version=3]{mhchem} 
-% \usepackage{fixltx2e}
-% \usepackage{refcount}
-% \usepackage{siunitx}
-% \usepackage{lastpage}
-% \usepackage{textcomp}
-\usepackage{mathtools}
-
-\usepackage{xfrac}
-\usepackage{lmodern}
+% \usepackage[version=3]{mhchem} 
+% % \usepackage{fixltx2e}
+% % \usepackage{refcount}
+% % \usepackage{siunitx}
+% % \usepackage{lastpage}
+% % \usepackage{textcomp}
+% \usepackage{mathtools}
+% 
+% \usepackage{xfrac}
+% \usepackage{lmodern}
 \usepackage[hidelinks]{hyperref}
-% \usepackage{cool}
-% \usepackage{cancel}
-% \usepackage{microtype}
-\usepackage{listings}
-% \usepackage{mcode}
+% % \usepackage{cool}
+% % \usepackage{cancel}
+% % \usepackage{microtype}
+% \usepackage{listings}
+% % \usepackage{mcode}
 \usepackage [autostyle, english = american]{csquotes}
-% \usepackage{longtable}
-% \usepackage{subcaption}
-\usepackage{booktabs,siunitx}
-\usepackage{gensymb}
-\usepackage[normalem]{ulem}
+% % \usepackage{longtable}
+% % \usepackage{subcaption}
+% \usepackage{booktabs,siunitx}
+% \usepackage{gensymb}
+% \usepackage[normalem]{ulem}
 
 % \usepackage{mathtools, cuted}
+\usepackage{wrapfig}
 
@@
 
-\usepackage[colorinlistoftodos]{todonotes}
+% \usepackage[colorinlistoftodos]{todonotes}
 
@@
 
+% \usepackage[style=base]{caption}
 \usepackage{subfig}
@@
 \captionsetup[subfigure]{labelformat=empty}
+% \captionsetup{style=base}
 
@@
 
-\makeatletter
-% Make common definition of mean
-\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}
-
-\makeatother
+% \makeatletter
+% % Make common definition of mean
+% \newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}
+% 
+% \makeatother
 
@@
 
-\setcounter{secnumdepth}{4}
+% \setcounter{secnumdepth}{4}
 
@@
 % Page header
-\markboth{Author et al.}{Short title}
+\markboth{Bernstein et al.}{Our Future Nuclear Data Needs}
 
@@
 %Authors, affiliations address.
-\author{Lee A.
-Bernstein$^{1,2}$, David A.
-Brown$^3$, \\Arjan J.
-Koning$^4$, Brad T.
-Rearden$^5$,  \\Catherine E.
-Romano$^5$, Alejandro A.
-Sonzogni$^3$, Andrew S.
-Voyles$^{1,2}$, and Walid XXX Younes$^6$
+\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^6$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 \section{INTRODUCTION}
-Please begin the main text of your article here.
+
+\subsection{The Two Faces of Nuclear Data}
+
+Low-energy nuclear science (LENS) \enquote{straddles the fence} between curiosity- and application-driven pursuits.
+On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
+LENS also plays an important role in nuclear astrophysics, improving models of stellar energy generation and allowing isotopic abundances to be used to inform models of the astrophysical environments where heavy nuclei are formed.
+On the applied side, a well-quantified knowledge of low-lying nuclear structure and reactions is needed to model energy generation and isotope production for medical and industrial uses and for the national security and counter-proliferation communities.
+
+One hallmark of LENS is that most theoretical descriptions are descriptive rather than rigorously predictive at the level of accuracy and over the entire range of energies etc.
+needed for real world applications.
+As a result, targeted measurements coupled to a data evaluation process are used to produce databases of recommended values that can be employed by the user communities.
+The evaluation processes range from close adherence to experimental results in the case of low energy nuclear structure and decay data, to experiment-guided modeling in the case of nuclear reactions.
+This work is carried out by subject matter experts who usually come from the field utilizing the data who spend many years studying under experienced evaluators in order to develop the highly-specialized skills they need.
+
+This manuscript will start with a description of the nuclear data evaluation process, and the organizations organization that carry it out.
+It will then describe ways to improve the modeling of (n,x) reactions on nuclides important for applications.
+Following this will be a discussion of needs for specific applications including national security/non-proliferation, medical isotope production and nuclear energy.
+It will end with a discussion of the future of nuclear data featuring  a new, Nuclear Data Interagency Working Group that that is formulating a national nuclear data plan to address high-priority needs for applied nuclear science and technology.
+
+\subsection{The Nuclear Data Pipeline}
+
+\begin{wrapfigure}{r}{0.4\textwidth}
+\centering
+\includegraphics[width=0.4\textwidth]{pipeline_cropped.pdf}
+\caption{\label{fig:pipeline}The nuclear data pipeline.}
+\end{wrapfigure}
+
+Before diving into the data needs, it is instructive to understand the \enquote{Nuclear Data Pipeline} that takes experimental or theoretical results and prepares them for use in applications.
+This process is illustrated in \autoref{fig:pipeline} and is roughly grouped into four steps: 1) compilation, 2) evaluation, 3) processing, and 4) validation.
+This process ends with the users and their application, but actually begins with the performance of carefully-designed measurements with well-defined uncertainties.
+Given this, it behooves those funding or performing the original experiment to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
+For example, if a new result forces changes to data formats (step 2) or processing (step 3) or to application codes (step 4 \& eventual user), this fact should be considered when developing a new activity.
+
+The first step in the Pipeline is compilation and it begins with potentially the most important database: Nuclear Science References (NSR) \cite{NSR}.
+NSR contains references to published works from major LENS journals as well as internal reports from labs throughout the world and serves as the start point for the data evaluation process.
+Descriptive keywords are assigned to these articles by individuals with LENS backgrounds, enabling the use of this information in later portions of the evaluation process.
+
+Following this, the data from the primary references contained in NSR, including both mean values and uncertainties, are extracted in numerical form and compiled into one of two databases depending on whether the data is primarily regarding nuclear structure and decay or nuclear reaction data.
+This step may also include tracking down unpublished data from original sources before that data is lost.
+
+The nuclear structure compilation database is called the Experimental Unevaluated Nuclear Data List (XUNDL) \cite{XUN}.
+The nuclear data in XUNDL is organized by nuclide, meaning that a single publication could lead to the production of more than one XUNDL dataset.
+Each XUNDL dataset is treated as a “stand-alone” work and is not required to agree with existing, evaluated nuclear data for the nuclide it concerns.
+However, during XUNDL compilation basic consistency checks are performed and any internal inconsistencies are pointed out to the author to allow them be reconciled in the database.
+XUNDL is used by both nuclear structure evaluators to aid in their work and by nuclear structure researchers as a quick way to get access to data from current publications in order to guide their own research.
+
+The nuclear reaction compilation database is referred to as Experimental Nuclear Reaction Data library (EXFOR) \cite{EXF}.
+This includes not only reaction cross sections, but also related data such as fission yields, resonance integrals, polarization data and more.
+Given the wide range of data types present in EXFOR there is significantly less error checking than what is performed during in XUNDL compilation.
+However, an online visualization tool is provided to allow users to plot and manipulate the data.
+EXFOR is used by both nuclear reaction evaluators and the nuclear reaction research and application community.
+
+The next step in the process is evaluation itself.
+In the case of nuclear structure data this involves reconciling multiple types data sets (e.g., prompt gamma and particle spectra, decay data etc.) and deriving a recommended set of adopted values.
+This data forms the basis of the Evaluated Nuclear Structure Data File (ENSDF) \cite{tepel1984ensdf}.
+While most of the ENSDF evaluation is performed in the US, there is a significant and growing component coming from evaluators throughout the world.
+The governing body that determines the rules for the evaluation process is the Nuclear Structure and Decay Data Network administered by the International Atomic Energy Agency (IAEA-NSDD).
+
+In the case of nuclear reaction data, the process is markedly different.
+The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the Evaluated Nuclear Data File \cite{Chadwick2011}.
+Most of the effort put into the production of ENDF is provided by applications-oriented users due to its importance to national security, international counter-proliferation and nuclear energy.
+A consequence of this application focus is that the vast majority of the data in ENDF concerns neutron-induced reactions at either thermal (25 meV), fast fission or 14.1 MeV.
+This has profound implications for isotope production since many of the nuclides are produced through charged-particle induced reactions.
+
+While ENSDF and ENDF contain a vast quantity of nuclear data, there are significant amounts of nuclear data that are either not contained in them because they “fall between” nuclear structure and nuclear reactions, or they are present in a format that is not well-suited to their use in applications.
+Examples of this include the recently updated Atlas of Neutron Resonances \cite{Mug18} which contains neutron capture resonance widths, centroids and cross sections and the Evaluated Gamma Activation File of (EGAF) capture gamma-rays \cite{Fir15} and the Atlas of Inelastic Scattering of Reactor Fast Neutron \cite{Hur18}.
+Another very important nuclear data resource for applications is the Reference Input Parameter Library (RIPL) \cite{Capote2009} which contains both discrete (distilled from ENSDF) and continuous (Nuclear Level Densities and Gamma-strength function) nuclear structure data needed for accurate reaction modeling.
+
+Evaluations in hand, we must now process the data into a form suitable for use in a particular application.
+This is a surprisingly non-trivial part of the process, requiring a deep knowledge of the physics used in the evaluation process, the formatting limitations of intermediate data formats, and the capabilities of downstream codes that will use the nuclear data.
+Processing is also needed for the validation of nuclear reaction data using the integral benchmarks described below.
+Another role of processing is in the creation of application-specific databases, such as the Medical Internal Radiation Dose (MIRD) \cite{MIRD} database used to guide medical treatment and diagnosis.
+
+The final step in the Pipeline is validation.
+In this step, we use user codes and user-defined problems to validate that the data performs as expected.
+The class of user problems we most rely on are so-called “integral benchmark” data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
+The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neuron loss (k­eff) is known to several significant figures.
+However, there are many other kinds of integral benchmarks used to test neutron interaction data alone, including reaction rate measurements and 14 MeV and fission spectrum transmission experiments, and many more for other forms of nuclear data.
+
+There are multiple ways to interact with the nuclear data evaluation process along the way, including through web interfaces hosted by the National Nuclear Data Center \cite{NNDC} and the IAEA Nuclear Data Section \cite{IAEA-NDS}, a smartphone based application \cite{IAEA-APP} and publication in peer-reviewed journals including Nuclear Data Sheets \cite{NDS} and Atomic Data and Nuclear Data Tables \cite{ATNDT}.
+
+Many different government agencies support nuclear data evaluation activities, including several components of the Department of Energy National Nuclear Security Agency (DOE-NNSA) and the National Criticality Safety Program (NCSP).
+However, the primary domestic organization responsible for organizing the evaluation process is US Nuclear Data Program (USNDP) in the DOE Nuclear Physics office (DOE-NP).
+The USNDP is headquartered at the National Nuclear Data Center at Brookhaven National Lab and includes centers at Argonne, Oak Ridge, Los Alamos and Lawrence Livermore National Labs, as well as joint lab/university programs at North Carolina State University/Triangle University Nuclear Lab, Michigan State University/National Superconducting Cyclotron Lab and the University of California/Lawrence Berkeley National Laboratory.
+
+\subsection{International Collaboration}
+
+Much of the work of nuclear data evaluation takes place as a part of international collaborations covered under the Organization of Economic Cooperation and Development’s Nuclear Energy Agency (NEA) and the International Atomic Energy Agency (IAEA).
+The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
+
+A powerful instrument of WPEC to drive progress in nuclear data is the so-called Subgroup (SG): members of WPEC identify a common area in nuclear data that requires improvement, and if enough support from the various data library projects is present, a Subgroup is formed.
+Subgroups typically operate on a 3-5 year time frame. Recent successful examples of WPEC subgroups, which specific relevance to the US, are large-scale horizontal efforts like CIELO (SG40), on worldwide nuclear data evaluation for the most important fission energy related materials.
+The CIELO initiative has for example led to new ENDF/B-VIII.0 evaluations for 235,238U, 56Fe and 16O among others, and the Generalized Nuclear Database Structure (GNDS) format (SG38) \cite{SG38}, or more specific efforts like covariance adjustment for improvement of nuclear data files (SG39) \cite{SG39}.
+
+WPEC also hosts long-term Expert Groups, and current groups are working on the development of the Generalized Nuclear Database Structure (GNDS) format, to provide a data library interface between nuclear physics and applications more modern than the ENDF-6 format, and the High-Priority Request List which assembles the most important nuclear data requests from applications in a unified format, to stimulate experimentalists and evaluators to provide these data.
+A full list of past and current subgroups of WPEC is available at Ref.
+\cite{WPEC}.
+ 
+The International Atomic Energy Agency (IAEA) covers the interests of its 170 member states.
+The main task of the IAEA Nuclear Data Section is to provide fundamental nuclear data bases for basic and applied use, with data originating from experiments and theoretical simulations and covering both nuclear structure and nuclear reaction data.
+An important collaboration coordinated by the IAEA is the Nuclear Reaction Data Center Network, which is responsible for keeping the EXFOR database of experimental nuclear reaction data up to date.
+NNDC is responsible for the US input to the database.
+
+In addition, the IAEA organizes Coordinated Research Projects (CRP) and technical meetings as instruments to align international nuclear data efforts towards the production of validated databases ready for applied use.  Examples of recent and current CRP's include a 2018 venture centered on nuclear data for primary radiation damage has been completed, an ongoing effort to improve nuclear model parameters for fission reaction calculations by modern nuclear model codes such as EMPIRE \cite{Her07}, CCONE \cite{Iwa16}, COH3 \cite{Kaw10} and TALYS \cite{Kon08} is ongoing, and an effort to create a first-ever evaluated database of radiative strength.
+In 2019, a CRP on fission yields will start which aims to produce updated fission yield libraries for the major actinides to respond to requests from reactor technology, safeguards and non-proliferation.
+
+Nuclear data evaluations of neutron-induced reactions for fission applications are covered by the International Nuclear Data Evaluation Network (INDEN), an IAEA initiative which continues the CIELO efforts of the NEA for differential nuclear data developments, and evaluations, for the most important materials relevant for fission technology.
+Other long term projects are the nuclear structure and decay data network NSDD, nuclear data for medical isotope production, with emphasis on data needs for monitor reactions and accelerator, neutron standards and the Fusion Evaluated Nuclear Data Library FENDL.
+
+\section{IMPROVED (N,X) REACTION MODELING: A CROSSCUTTING NEED}
+
+Accurate, physics-based modeling of neutron-induced reactions, particularly on the “Big 3” (235,238U and 239Pu) are key to virtually all nuclear science and technology applications.
+While a great deal of effort has been made to improve (n,f) data, a fundamental understanding of this most important of reaction mechanisms remain elusive.
+Furthermore, since fission leads to the production of neutrons with energies up to several MeV, elastic and inelastic scattering also play a critical role.
+Unfortunately, efforts to improve neutron scattering data has tended to “take a back seat” to fission due to a deficit of high-quality experimental data.
+Lastly, while all modeling of (n,x) reactions requires a good understanding of unbound nuclear states populated in (n,x) reactions, it remains one of the least understood topics in LENS.
+In this section we explore all three of these topics these “crosscutting” topics and present plans to improve them.
+
+\subsection{A Deeper Understanding of Fission}
+
+Not all fission data needed in nuclear physics applications can be readily measured in the laboratory.
+In many cases, the targets may be too-short lived, the analysis might yield unacceptably large uncertainties, or separate measurements of the same quantity may produce discrepant results.
+As with other reaction data, fission evaluation proceeds through the use of a model designed to reproduce the data as closely as possible.
+However, in the case of fission, we still lack a predictive theoretical framework to match all types of measured data within experimental errors.
+A truly predictive theory of fission will require advances in theoretical techniques and computational machinery, along with improved experimental data.
+
+For fission theory, we can make a distinction in practice between description of the fission process up to scission (pre-scission physics), and the events that follow scission (post-scission physics).
+Eventually, one could envision a comprehensive model that accurately follows the entire fission process from the formation of the parent nucleus to the last decays of the final product nuclei within a single internally consistent theoretical framework.
+Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes.
+A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Moller2015} with random-walk dynamics \cite{Wa17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Sch16}, FIFRELIN \cite{Lit15}, CGMF \cite{Kaw10}, and FREYA \cite{Ran09,Ver18}.
+
+The division between pre- and post-scission physics in modeling efforts suggests a corresponding division in nuclear data needs to improve our understanding of the fission process.
+Post-scission observables are generally easier to measure, and include the properties of fission fragments and products and of the neutrons and gamma rays they emit.
+Recently, Bertsch et al.
+\cite{Ber15} have suggested a subset of fission data that tend to have relatively small uncertainties and could therefore be used to test and validate fission models.
+These data consist of fission barriers, fragment mass distributions, fragment total kinetic energies, spontaneous-fission lifetimes, and fission isomer excitation energies.
+In addition to these quantities, the angular distribution of fission fragments can also provide useful information about the angular momentum of the fissioning nucleus and further constrain model calculations.
+
+In addition to standard experiments looking at individual fission properties, multi-parameter measurements that give a comprehensive view of a fission event should be pursued as facilities and detectors improve.
+Ideally, a multi-parameter experiment would record all possible fission observables (e.g., fragment charge, mass, and energy distributions as well as neutron and gamma spectra and multiplicities) on an event-by-event basis, thereby making it possible to reconstruct the state of the nucleus at scission.
+In practice, each additional observable reduces statistics, making such measurements exceedingly challenging.
+Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process although they carry large uncertainties and suffer from various ambiguities and limitations.
+These include measurements of scission neutrons \cite{Pe09}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}.
+Probes of pre-scission physics can provide unique insights into the details of the fission process, and are therefore extremely valuable to fission theory.
+
+Both pre-scission and post-scission theory and data will be needed to reach a satisfactory understanding of the fission process, and thereby make reliable predictions of nuclear quantities that cannot be measured in the laboratory.
+Pre-scission models can provide input to post-scission models wherever the data are lacking, and post-scission models can be used to improve pre-scission calculations using a wealth of available experimental data.
+The ultimate goal for theorists, a comprehensive description of fission starting from protons, neutrons, and their interactions that provides accurate values for all fission data of interest, remains elusive.
+Many questions about the fission process remain open, such as: how the initial partition of energy between kinetic and internal excitation occurs, what the relevant collective and single-particle degrees of freedom are near scission, and how they evolve and couple throughout the process?
+Lastly, how can we best quantify uncertainties (both epistemic and aleatory) in fission calculations?
 
@@
 %Example of a Figure
-\section{ELEMENTS\ OF\ THE\ MANUSCRIPT} 
-\subsection{Figures}Figures should be cited in the main text in chronological order.
+% \section{ELEMENTS\ OF\ THE\ MANUSCRIPT} 
+% \subsection{Figures}Figures should be cited in the main text in chronological order.
 This is dummy text with a citation to the first figure (\textbf{Figure \ref{fig1}}).
 Citations to \textbf{Figure \ref{fig1}} (and other figures) will be bold.
-
-\begin{figure}[h]
-\includegraphics[width=3in]{SampleFigure.pdf}
-\caption{Figure caption with descriptions of parts a and b}
-\label{fig1}
-\end{figure}
-
-% Example of a Table
-\subsection{Tables} Tables should also be cited in the main text in chronological order (\textbf {Table \ref{tab1}}).
-
-\begin{table}[h]
-\tabcolsep7.5pt
-\caption{Table caption}
-\label{tab1}
-\begin{center}
-\begin{tabular}{@{}l|c|c|c|c@{}}
-\hline
-Head 1 &&&&Head 5\\
-{(}units)$^{\rm a}$ &Head 2 &Head 3 &Head 4 &{(}units)\\
-\hline
-Column 1 &Column 2 &Column3$^{\rm b}$ &Column4 &Column\\
-Column 1 &Column 2 &Column3 &Column4 &Column\\
-Column 1 &Column 2 &Column3 &Column4 &Column\\
-Column 1 &Column 2 &Column3 &Column4 &Column\\
-\hline
-\end{tabular}
-\end{center}
-\begin{tabnote}
-$^{\rm a}$Table footnote; $^{\rm b}$second table footnote.
-\end{tabnote}
-\end{table}
-
-% Example of lists
-\subsection{Lists and Extracts} Here is an example of a numbered list:
+% 
+% \begin{figure}[h]
+% \includegraphics[width=3in]{SampleFigure.pdf}
+% \caption{Figure caption with descriptions of parts a and b}
+% \label{fig1}
+% \end{figure}
+% 
+% % Example of a Table
+% \subsection{Tables} Tables should also be cited in the main text in chronological order (\textbf {Table \ref{tab1}}).
+% 
+% \begin{table}[h]
+% \tabcolsep7.5pt
+% \caption{Table caption}
+% \label{tab1}
+% \begin{center}
+% \begin{tabular}{@{}l|c|c|c|c@{}}
+% \hline
+% Head 1 &&&&Head 5\\
+% {(}units)$^{\rm a}$ &Head 2 &Head 3 &Head 4 &{(}units)\\
+% \hline
+% Column 1 &Column 2 &Column3$^{\rm b}$ &Column4 &Column\\
+% Column 1 &Column 2 &Column3 &Column4 &Column\\
+% Column 1 &Column 2 &Column3 &Column4 &Column\\
+% Column 1 &Column 2 &Column3 &Column4 &Column\\
+% \hline
+% \end{tabular}
+% \end{center}
+% \begin{tabnote}
+% $^{\rm a}$Table footnote; $^{\rm b}$second table footnote.
+% \end{tabnote}
+% \end{table}
+% 
+% % Example of lists
+% \subsection{Lists and Extracts} Here is an example of a numbered list:
+% % \begin{enumerate}
+% % \item List entry number 1,
+% % \item List entry number 2,
+% % \item List entry number 3,\item List entry number 4, and
+% % \item List entry number 5.
+% % \end{enumerate}
+% 
+% % Here is an example of a extract.
+% % \begin{extract}
+% % This is an example text of quote or extract.
+% % This is an example text of quote or extract.
+% % \end{extract}
+% 
+% \subsection{Sidebars and Margin Notes}
+% % Margin Note
+% \begin{marginnote}[]
+% \entry{Term A}{definition}
+% \entry{Term B}{definition}
+% \entry{Term C}{defintion}
+% \end{marginnote}
+% 
+% \begin{textbox}[h]\section{SIDEBARS}
+% Sidebar text goes here.
+% \subsection{Sidebar Second-Level Heading}
+% More text goes here.\subsubsection{Sidebar third-level heading}
+% Text goes here.\end{textbox}
+% 
+% 
+% 
+% \subsection{Equations}
+% % Example of a single-line equation
+% \begin{equation}
+% a = b \ {\rm ((Single\ Equation\ Numbered))}
+% \end{equation}
+% %Example of multiple-line equation
+% Equations can also be multiple lines as shown in Equations 2 and 3.
+% \begin{eqnarray}
+% c = 0 \ {\rm ((Multiple\  Lines, \ Numbered))}\\
+% ac = 0 \ {\rm ((Multiple \ Lines, \ Numbered))}
+% \end{eqnarray}
+% 
+% % Summary Points
+% \begin{summary}[SUMMARY POINTS]
 % \begin{enumerate}
-% \item List entry number 1,
-% \item List entry number 2,
-% \item List entry number 3,\item List entry number 4, and
-% \item List entry number 5.
+% \item Summary point 1. These should be full sentences.
+% \item Summary point 2. These should be full sentences.
+% \item Summary point 3. These should be full sentences.
+% \item Summary point 4. These should be full sentences.
 % \end{enumerate}
-
-% Here is an example of a extract.
-% \begin{extract}
-% This is an example text of quote or extract.
-% This is an example text of quote or extract.
-% \end{extract}
-
-\subsection{Sidebars and Margin Notes}
-% Margin Note
-\begin{marginnote}[]
-\entry{Term A}{definition}
-\entry{Term B}{definition}
-\entry{Term C}{defintion}
-\end{marginnote}
-
-\begin{textbox}[h]\section{SIDEBARS}
-Sidebar text goes here.
-\subsection{Sidebar Second-Level Heading}
-More text goes here.\subsubsection{Sidebar third-level heading}
-Text goes here.\end{textbox}
-
-\subsection{Equations}
-% Example of a single-line equation
-\begin{equation}
-a = b \ {\rm ((Single\ Equation\ Numbered))}
-\end{equation}
-%Example of multiple-line equation
-Equations can also be multiple lines as shown in Equations 2 and 3.
-\begin{eqnarray}
-c = 0 \ {\rm ((Multiple\  Lines, \ Numbered))}\\
-ac = 0 \ {\rm ((Multiple \ Lines, \ Numbered))}
-\end{eqnarray}
-
-% Summary Points
-\begin{summary}[SUMMARY POINTS]
-\begin{enumerate}
-\item Summary point 1. These should be full sentences.
-\item Summary point 2. These should be full sentences.
-\item Summary point 3. These should be full sentences.
-\item Summary point 4. These should be full sentences.
-\end{enumerate}
-\end{summary}
-
-% Future Issues
-\begin{issues}[FUTURE ISSUES]
-\begin{enumerate}
-\item Future issue 1. These should be full sentences.
-\item Future issue 2. These should be full sentences.
-\item Future issue 3. These should be full sentences.
-\item Future issue 4. These should be full sentences.
-\end{enumerate}
-\end{issues}
+% \end{summary}
+% 
+% % Future Issues
+% \begin{issues}[FUTURE ISSUES]
+% \begin{enumerate}
+% \item Future issue 1. These should be full sentences.
+% \item Future issue 2. These should be full sentences.
+% \item Future issue 3. These should be full sentences.
+% \item Future issue 4. These should be full sentences.
+% \end{enumerate}
+% \end{issues}
 
@@
 
-To download the appropriate bibliography style file, please see \url{http://www.annualreviews.org/page/authors/author-instructions/preparing/latex}.
+\bibliographystyle{ar-style5}
 
-\noindent
-Please see the Style Guide document for instructions on preparing your Literature Cited.
-
-The citations should be numbered in order of appearance. For example:
-
-% 
-% 
-% \begin{verbatim}
-% \begin{thebibliography}{96}
-% \expandafter\ifx\csname
-% natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-% 
-% \bibitem{Glashow:1961tr}
-% Glashow SL. \textit{Nucl. Phys.} 22:579 (1961)
-% 
-% \bibitem{Weinberg:1967tq}
-% Weinberg S. \textit{Phys. Rev. Lett.} 19:1264 (1967)
-% 
-% \bibitem{Salam}
-% Salam A.  In \textit{Elementary Particle Theory: Relativistic
-% Groups and Analyticity. Proceedings of the 8th Nobel Symposium},
-% ed. N~Svartholm, p. 367. Stockholm: Almqvist \& Wiksell (1968)
-% \bibitem{Fritzsch:1973pi}
-% Fritzsch H, Gell-Mann M, Leutwyler H. \textit{Phys. Lett.} \textit{B} 47:365
-% (1973)
-% 
-% \bibitem{Gross:1973id}
-% Gross DJ, Wilczek F. \textit{Phys. Rev. Lett.} 30:1343 (1973)
-% 
-% \bibitem{Politzer:1973fx}
-% Politzer HD. \textit{Phys. Rev. Lett.} 30:1346 (1973)
-% 
-% \bibitem{Kronfeld:2010bx}
-% Kronfeld AS, Quigg C. \textit{Am. J. Phys.} 78:1081 (2010)
-% 
-% \bibitem{Langacker:2010}
-% Langacker P. \textit{The Standard Model and Beyond. Series in
-% High Energy Physics, Cosmology, and Gravitation}. Boca Raton:
-% CRC/Taylor \& Francis (2010)
-% 
-% \bibitem{GT2}
-% Quigg C. \textit{Gauge Theories of the Strong, Weak, and
-% Electromagnetic Interactions}. Princeton, NJ: Princeton
-% Univ. Press. 2nd ed. (2013)
-% 
-% \bibitem{MattS}
-% Schwartz MD. \textit{Quantum Field Theory and the Standard Model}.
-% Cambridge, UK: Cambridge Univ. Press (2013)
-% 
-% \bibitem{DynSM}
-% Donoghue JF, Golowich E, Holstein BR. \textit{Dynamics of the
-% Standard Model}. Cambridge, UK/New York: Cambridge
-% Univ. Press. 2nd ed. (2014)
-% \end{thebibliography}
-% \end{verbatim}
-
-This coding results in the following formatted bibliography:
-
-\begin{thebibliography}{96}
-\expandafter\ifx\csname
-natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem{Glashow:1961tr}
-Glashow SL. \textit{Nucl. Phys.} 22:579 (1961)
-
-\bibitem{Weinberg:1967tq}
-Weinberg S. \textit{Phys. Rev. Lett.} 19:1264 (1967)
-
-\bibitem{Salam}
-Salam A.  In \textit{Elementary Particle Theory: Relativistic
-Groups and Analyticity. Proceedings of the 8th Nobel Symposium},
-ed. N~Svartholm, p. 367. Stockholm: Almqvist \& Wiksell
- (1968)
-\bibitem{Fritzsch:1973pi}
-Fritzsch H, Gell-Mann M, Leutwyler H. \textit{Phys. Lett.} \textit{B} 47:365
-(1973)
-
-\bibitem{Gross:1973id}
-Gross DJ, Wilczek F. \textit{Phys. Rev. Lett.} 30:1343 (1973)
-
-\bibitem{Politzer:1973fx}
-Politzer HD. \textit{Phys. Rev. Lett.} 30:1346 (1973)
-
-\bibitem{Kronfeld:2010bx}
-Kronfeld AS, Quigg C. \textit{Am. J. Phys.} 78:1081 (2010)
-
-\bibitem{Langacker:2010}
-Langacker P. \textit{The Standard Model and Beyond. Series in
-High Energy Physics, Cosmology, and Gravitation}. Boca Raton:
-CRC/Taylor \& Francis (2010)
-
-\bibitem{GT2}
-Quigg C. \textit{Gauge Theories of the Strong, Weak, and
-Electromagnetic Interactions}. Princeton, NJ: Princeton
-Univ. Press. 2nd ed. (2013)
-
-\bibitem{MattS}
-Schwartz MD. \textit{Quantum Field Theory and the Standard Model}.
-Cambridge, UK: Cambridge Univ. Press (2013)
-
-\bibitem{DynSM}
-Donoghue JF, Golowich E, Holstein BR. \textit{Dynamics of the
-Standard Model}. Cambridge, UK/New York: Cambridge
-Univ. Press. 2nd ed. (2014)
-
-\end{thebibliography}
+\bibliography{../../library}
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Fixed page margins (somewhat_

@@
 
-\documentclass[letterpaper]{ar-1col}
+\documentclass[letterpaper,draft]{ar-1col}
 \usepackage[numbers]{natbib}
+\usepackage[left=35mm,top=26mm,right=26mm,bottom=15mm]{geometry}
 
@@
 % \usepackage{xfrac}
-% \usepackage{lmodern}
+\usepackage{lmodern}
 \usepackage[hidelinks]{hyperref}
@@
 % \usepackage[style=base]{caption}
-\usepackage{subfig}
+% \usepackage{subfig}
 % Remove a), b), etc labels from subfigs
-\captionsetup[subfigure]{labelformat=empty}
+% \captionsetup[subfigure]{labelformat=empty}
 % \captionsetup{style=base}
@@
 \begin{abstract}
-Abstract text, approximately 150 words. 
+A well-established knowledge of nuclear phenomena including fission, reaction cross sections, and structure/decay properties, is critical for applications ranging from the design of new reactors, to non-proliferation, to the production of radioisotopes for the diagnosis and treatment of illness.
+However, the lack of a well-quantified, predictive theoretical capability means that most nuclear observables must be measured directly in order to “calibrate” empirical models, which, in turn, provide the data needed for these applications.
+In many cases there is either a lack of the data needed to guide the models, or the results of the different measurements are discrepant.
+This has led to the development of evaluation methodologies to provide recommended values and uncertainties.
+In this article we present the nuclear data evaluation process and the international community that carries it out.
+We then discuss new measurements and improved theory and/or modeling needed to address future challenges in applied nuclear science.
 \end{abstract}
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
-\centering
-\includegraphics[width=0.4\textwidth]{pipeline_cropped.pdf}
-\caption{\label{fig:pipeline}The nuclear data pipeline.}
-\end{wrapfigure}
-
 Before diving into the data needs, it is instructive to understand the \enquote{Nuclear Data Pipeline} that takes experimental or theoretical results and prepares them for use in applications.
@@
 Descriptive keywords are assigned to these articles by individuals with LENS backgrounds, enabling the use of this information in later portions of the evaluation process.
+
+\begin{wrapfigure}{r}{0.4\textwidth}
+\centering
+\includegraphics[width=0.4\textwidth]{pipeline_cropped.pdf}
+\caption{\label{fig:pipeline}The nuclear data pipeline.}
+\end{wrapfigure}
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished through section 2.1.  Dumping rest of text in

@@
 % \usepackage{amsmath}
-% \usepackage[version=3]{mhchem} 
+\usepackage[version=3]{mhchem} 
 % % \usepackage{fixltx2e}
@@
 % % \usepackage{cancel}
-% % \usepackage{microtype}
+\usepackage{microtype}
 % \usepackage{listings}
@@
 
+% \makeatletter
+%  \def\@textbottom{\vskip \z@ \@plus 1pt}
+%  \let\@texttop\relax
+% \makeatother
+
 % Document starts
@@
 A well-established knowledge of nuclear phenomena including fission, reaction cross sections, and structure/decay properties, is critical for applications ranging from the design of new reactors, to non-proliferation, to the production of radioisotopes for the diagnosis and treatment of illness.
-However, the lack of a well-quantified, predictive theoretical capability means that most nuclear observables must be measured directly in order to “calibrate” empirical models, which, in turn, provide the data needed for these applications.
+However, the lack of a well-quantified, predictive theoretical capability means that most nuclear observables must be measured directly in order to \enquote{calibrate} empirical models, which, in turn, provide the data needed for these applications.
 In many cases there is either a lack of the data needed to guide the models, or the results of the different measurements are discrepant.
@@
 The nuclear data in XUNDL is organized by nuclide, meaning that a single publication could lead to the production of more than one XUNDL dataset.
-Each XUNDL dataset is treated as a “stand-alone” work and is not required to agree with existing, evaluated nuclear data for the nuclide it concerns.
+Each XUNDL dataset is treated as a \enquote{stand-alone} work and is not required to agree with existing, evaluated nuclear data for the nuclide it concerns.
 However, during XUNDL compilation basic consistency checks are performed and any internal inconsistencies are pointed out to the author to allow them be reconciled in the database.
@@
 
-While ENSDF and ENDF contain a vast quantity of nuclear data, there are significant amounts of nuclear data that are either not contained in them because they “fall between” nuclear structure and nuclear reactions, or they are present in a format that is not well-suited to their use in applications.
+While ENSDF and ENDF contain a vast quantity of nuclear data, there are significant amounts of nuclear data that are either not contained in them because they \enquote{fall between} nuclear structure and nuclear reactions, or they are present in a format that is not well-suited to their use in applications.
 Examples of this include the recently updated Atlas of Neutron Resonances \cite{Mug18} which contains neutron capture resonance widths, centroids and cross sections and the Evaluated Gamma Activation File of (EGAF) capture gamma-rays \cite{Fir15} and the Atlas of Inelastic Scattering of Reactor Fast Neutron \cite{Hur18}.
@@
 In this step, we use user codes and user-defined problems to validate that the data performs as expected.
-The class of user problems we most rely on are so-called “integral benchmark” data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
-The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neuron loss (k­eff) is known to several significant figures.
+The class of user problems we most rely on are so-called \enquote{integral benchmark} data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
+The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss ($k_{eff}$) is known to several significant figures.
 However, there are many other kinds of integral benchmarks used to test neutron interaction data alone, including reaction rate measurements and 14 MeV and fission spectrum transmission experiments, and many more for other forms of nuclear data.
 
-There are multiple ways to interact with the nuclear data evaluation process along the way, including through web interfaces hosted by the National Nuclear Data Center \cite{NNDC} and the IAEA Nuclear Data Section \cite{IAEA-NDS}, a smartphone based application \cite{IAEA-APP} and publication in peer-reviewed journals including Nuclear Data Sheets \cite{NDS} and Atomic Data and Nuclear Data Tables \cite{ATNDT}.
+There are multiple ways to interact with the nuclear data evaluation process along the way, including through web interfaces hosted by the National Nuclear Data Center \cite{NNDC} and the IAEA Nuclear Data Section \cite{IAEA-NDS}, a smartphone-based application \cite{IAEA-APP} and publication in peer-reviewed journals including Nuclear Data Sheets \cite{NDS} and Atomic Data and Nuclear Data Tables \cite{ATNDT}.
 
@@
 
-Much of the work of nuclear data evaluation takes place as a part of international collaborations covered under the Organization of Economic Cooperation and Development’s Nuclear Energy Agency (NEA) and the International Atomic Energy Agency (IAEA).
+Much of the work of nuclear data evaluation takes place as a part of international collaborations covered under the Organization of Economic Cooperation and Development's Nuclear Energy Agency (NEA) and the International Atomic Energy Agency (IAEA).
 The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
@@
 A powerful instrument of WPEC to drive progress in nuclear data is the so-called Subgroup (SG): members of WPEC identify a common area in nuclear data that requires improvement, and if enough support from the various data library projects is present, a Subgroup is formed.
-Subgroups typically operate on a 3-5 year time frame. Recent successful examples of WPEC subgroups, which specific relevance to the US, are large-scale horizontal efforts like CIELO (SG40), on worldwide nuclear data evaluation for the most important fission energy related materials.
-The CIELO initiative has for example led to new ENDF/B-VIII.0 evaluations for 235,238U, 56Fe and 16O among others, and the Generalized Nuclear Database Structure (GNDS) format (SG38) \cite{SG38}, or more specific efforts like covariance adjustment for improvement of nuclear data files (SG39) \cite{SG39}.
+Subgroups typically operate on a 3-5 year time frame.
+Recent successful examples of WPEC subgroups, with specific relevance to the US, are large-scale horizontal efforts like CIELO (SG40), on worldwide nuclear data evaluation for the most important fission energy related materials.
+The CIELO initiative has, for example, led to new ENDF/B-VIII.0 evaluations for \ce{^{235,238}U}, \ce{^{56}Fe} and \ce{^{16}O} among others, and the Generalized Nuclear Database Structure (GNDS) format (SG38) \cite{SG38}, or more specific efforts like covariance adjustment for improvement of nuclear data files (SG39) \cite{SG39}.
 
@@
 
-In addition, the IAEA organizes Coordinated Research Projects (CRP) and technical meetings as instruments to align international nuclear data efforts towards the production of validated databases ready for applied use.  Examples of recent and current CRP's include a 2018 venture centered on nuclear data for primary radiation damage has been completed, an ongoing effort to improve nuclear model parameters for fission reaction calculations by modern nuclear model codes such as EMPIRE \cite{Her07}, CCONE \cite{Iwa16}, COH3 \cite{Kaw10} and TALYS \cite{Kon08} is ongoing, and an effort to create a first-ever evaluated database of radiative strength.
+In addition, the IAEA organizes Coordinated Research Projects (CRP) and technical meetings as instruments to align international nuclear data efforts towards the production of validated databases ready for applied use.
+Examples of recent and current CRP's include a 2018 venture centered on nuclear data for primary radiation damage has been completed, an ongoing effort to improve nuclear model parameters for fission reaction calculations by modern nuclear model codes such as EMPIRE \cite{Herman2007}, CCONE \cite{Iwa16}, COH3 \cite{KAWANO2010} and TALYS \cite{Koning2012} is ongoing, and an effort to create a first-ever evaluated database of radiative strength.
 In 2019, a CRP on fission yields will start which aims to produce updated fission yield libraries for the major actinides to respond to requests from reactor technology, safeguards and non-proliferation.
@@
 
-Accurate, physics-based modeling of neutron-induced reactions, particularly on the “Big 3” (235,238U and 239Pu) are key to virtually all nuclear science and technology applications.
+Accurate, physics-based modeling of neutron-induced reactions, particularly on the \enquote{Big 3} (\ce{^{235,238}U} and \ce{^{239}Pu}) are key to virtually all nuclear science and technology applications.
 While a great deal of effort has been made to improve (n,f) data, a fundamental understanding of this most important of reaction mechanisms remain elusive.
 Furthermore, since fission leads to the production of neutrons with energies up to several MeV, elastic and inelastic scattering also play a critical role.
-Unfortunately, efforts to improve neutron scattering data has tended to “take a back seat” to fission due to a deficit of high-quality experimental data.
+Unfortunately, efforts to improve neutron scattering data has tended to \enquote{take a back seat} to fission due to a deficit of high-quality experimental data.
 Lastly, while all modeling of (n,x) reactions requires a good understanding of unbound nuclear states populated in (n,x) reactions, it remains one of the least understood topics in LENS.
-In this section we explore all three of these topics these “crosscutting” topics and present plans to improve them.
+In this section we explore all three of these  \enquote{crosscutting} topics and present plans to improve them.
 
@@
 Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes.
-A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Moller2015} with random-walk dynamics \cite{Wa17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Sch16}, FIFRELIN \cite{Lit15}, CGMF \cite{Kaw10}, and FREYA \cite{Ran09,Ver18}.
+A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{Wa17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Sch16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.
 
@@
 In practice, each additional observable reduces statistics, making such measurements exceedingly challenging.
-Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process although they carry large uncertainties and suffer from various ambiguities and limitations.
+Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process, although they carry large uncertainties and suffer from various ambiguities and limitations.
 These include measurements of scission neutrons \cite{Pe09}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}.
@@
 
-%Heading 1
-\section{FIRST-LEVEL HEADING}
-This is dummy text. 
-% Heading 2
-\subsection{Second-Level Heading}
-This is dummy text. This is dummy text. This is dummy text. This is dummy text.
+\subsection{Improved \ce{^{235,238}U} and \ce{^{239}Pu}(n,n') data for neutron transport}
 
-% Heading 3
-\subsubsection{Third-Level Heading}
-This is dummy text. This is dummy text. This is dummy text. This is dummy text.
+Elastic and inelastic scattering have a profound effect on neutron populations in any nuclear application by changing the directions and energies of the neutrons in the system.
+However, improvements in neutron scattering data have hampered by the fact that they do not produce easily measured signals like fission, or a radiochemical observable like neutron capture.
+The result has been significant disagreements between different reaction evaluations.
+These disagreements manifest themselves as compensating errors that are resistant to the validation process.
+This issue has been recognized by the nuclear data community since the early days of the WPEC \cite{Row89} and more recently by Maslov \cite{Mas11}.
 
-% Heading 4
-\paragraph{Fourth-Level Heading} Fourth-level headings are placed as part of the paragraph.
+One compelling example of compensating errors involves the Jezebel 239Pu critical assembly (PMF1).
+Models of Jezebel using LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) reproduce a unity value of keff to better than 1 part in 104.
+However, when the authors substituted one nuclear quantity one quantity at a time between the two databases, the value of keff varied considerably.
+The greatest changes came from changing the elastic and inelastic scattering cross sections, which led to changes in the keff of -500 pcm and +704 pcm respectively.
+This is shown in Fig.
+2 to the right.
+Similar examples of such compensating errors were also seen in earlier work by Bauge \cite{Bau12}.
+
+A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: 1H, 16O, 56Fe, 235,238U and 239Pu in order to address the issue of compensating errors.
+Recently, this list has been expanded to include 14,15N, 9Be, 23Na, 59Co, 58Ni, 238-242Pu.
+
+CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n’) on the “Big 3” Actinide, leading to “significant differences amongst the evaluations for 239Pu in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.” \cite{Cha14}.
+The 239Pu data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Bat69, And61}.
+The case is similar for 235U where they note that differences for En > 50 keV “have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.”
+
+One significant source of (n,xn) partial cross section data from 1997 to 2003 was the GEANIE collaboration (Germanium Array for Neutron-Induced Excitations) at the Los Alamos Neutron Science Center/Weapons Neutron Research (LANSCE/WNR) facility.
+While the primary goal of the GEANIE collaboration was the determination of the 239Pu(n,2n) cross section \cite{Ber02}, it resulted in the publication of more than two dozen papers over the course of more than 15 years.
+Experiments were run on all three of the major Actinides: 235U \cite{You01}, 239Pu \cite{Ber02} and 238U \cite{Fot04}.
+It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial -ray cross sections.
+
+The need for new scattering data has motivated many new experiments.
+This has included energy-differential/angle-integrated measurements of the 238U(n,n’) cross section using the GELINA spallation neutron source in Geel Belgium by Bacquias et al., \cite{Nem13} and quasi-angle-differential measurements using the Rensselaer Polytechnic Institute Linac by Daskalakis et al., \cite{Das14}.
+
+The ideal way to improve (n,n’) data on the 235,238U and 239Pu would be to perform measurements of the scattered neutron in coincidence with transitions emitted by the excited nucleus.
+In the case of the Actinides this will potentially require the observation of conversion electrons given that the lowest transitions in all actinides are almost entirely converted.
+Unfortunately, neutron beams usually have quite low intensity, with a fluence in the fast (1-10 MeV) region between 103 and 107 n/s/cm2 at the target location.
+Furthermore, many spallation neutron sources have a significant high energy spectral component that can cause inter-element scattering in a neutron scintillator array rendering precise determination of the scattered neutron energy hard to  perform.
+However, intense limited-energy neutron sources based on thick-target deuteron breakup \cite{Har18} and forward-fitting techniques developed for use at spallation neutron sources \cite{Kee18} off an opportunity to perform neutron-gamma coincident measurements in the fast fission energy spectrum.
+These techniques could provide valuable data to improve nuclear data evaluations of inelastic scattering, even on targets where fission is an open channel.
+
+\subsection{Improved treatment of continuum nuclear data properties}
+
+Information regarding states in the unresolved continuum region above the particle separation energy is of central importance to accurately modeling the competition between particle and gamma-ray emission.
+The most important of these are the nuclear level density (NLD) as a function of energy, spin and parity, and the radiative strength function (RSF), which describes the ability of excited nuclear matter to absorb or emit photons.
+A number of recent studies have shown the importance of the RSF to modeling (n,) reactions for neutrons with energies between 1 and 100 keV, which corresponds to the spectrum at the site of neutron capture nucleosynthesis in stars \cite{Lar10, Lar15} and energy generation in fast reactors and nuclear security applications.
+
+Over the past several years’ work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of “scissors” collective mode throughout the Actinide mass region near the valley of stability including 238U, 239,240,242Pu and 232Th \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
+
+Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter () of the form:
+
+		(1)
+
+where U is roughly the Ex minus the pairing gap , a is the level density parameter, A is the nuclear mass and is the asymptotic level density value one would obtain in the absence of any shell effects.
+
+There is a great deal uncertainty in the magnitude of the spin cut-off parameter.
+This is a significant issue since a good knowledge of the J distribution is needed to accurately model the neutron vs.
+-ray emission probability in nuclear reactions.
+This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in 95Mo well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
+
+(n,n’) provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
+Figure 4 shows the ratio of the partial cross section for the population of the  level in 238U(n,n’) as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
+The solid line shows the case where a constant temperature level density is assumed and the spin cut-off parameter was varied from 75% to 125% of its “normal” value given by the equation (3) above.
+The ratio decreases by nearly a factor of 2 with increasing energy.
+In contrast, the dashed line shows the ratio of the  population of the  state when the LD and RSF from the recent Oslo measurements \cite{Gut13a} is divided by the results obtained using the default Gilbert and Cameron in TALYS.
+In this case the ratio decreases by nearly a factor of 2.
+Similar behavior is seen in the partial cross sections for other off-yrast levels as well.
+
+Information regarding the J-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
+This method has been used in Hg and Au by Chakravarty \cite{Cha92} and more recently by Sudar in Hg and Pt \cite{Sud06}.
+Figure 5 shows this for the case of 52mMn(Jπ=2+)/52gMn(Jπ=6+) ratio populated via 56Fe(p,n) measured via stacked target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
+It should be noted that both the (n,n’) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in Section II.B above, and a program of cross section measurements in support of medical isotope production described in sections IV below.
+This reflects the interdependency between nuclear data over a wide range of applications.
+
+\section{NATIONAL SECURITY AND NON-PROLIFERATION}
+
+\subsection{Interpreting the reactor anti-neutrino spectrum}
+
+One canonical example of a non-proliferation activity where improvements in multiple cross-cutting areas of nuclear data are needed is the interpretation of the anti-neutrino spectrum from the prompt decay of fission fragments in the core of a nuclear reactor.
+Nuclear reactors are prolific sources of electron antineutrinos, producing about 1021 antineutrinos per second for a typical power reactor.
+These electron antineutrinos are produced by the beta-minus decay of the more than 800 neutron-rich fission fragments, which are the debris from the main source of energy generation in a reactor, the neutron induced fission of actinide nuclides.
+These antineutrinos are also the only radiation escaping from the vessel of a safely operating nuclear reactor, making them ideally suited for reactor monitoring, even in the event that the actor operating the reactor refuses to cooperate with the international community.
+Recent technological advancements in electron antineutrino detection has made another dream a reality, monitoring the performance of nuclear reactors and tracking 239Pu for non-proliferation treaty verification.
+The WATCHMAN experiment in the UK has just started to explore this field \cite{Cha18}.
+Furthermore, the possible use of antineutrino detectors for the detection of nuclear explosions has been discussed \cite{CarAx}.
+
+Nuclear reactors have also been an essential tool to study the weak interaction.
+Their large antineutrino flux was capitalized by Cowan and Reines to discover antineutrinos in 1956 \cite{Cow56}, more than 25 years after they were first hypothesized by Pauli in 1930 to explain the continuum electron spectra observed following beta-minus decay.
+In the last few years, the transformation of electron antineutrinos into the other two flavors was beautifully measured by three large-scale experimental efforts, Daya Bay \cite{An16}, Double Chooz \cite{Abe12} and RENO \cite{Cho16}.
+These experiments also confirmed a deficit of antineutrinos of about 5-9% at short distances that had been revealed in a 2011 re-analysis of the conversion procedure to obtain antineutrino spectra from the measured electron spectra \cite{Men11}.
+
+This intriguing deficit, as well as a spectrum distortion, has triggered a new generation of very-short distance reactor experiments, such as NEOS (Korea) \cite{Ko17}, DANSS (Russia) \cite{AleAx}, STEREO (France) \cite{AllAx}, PROSPECT (USA) \cite{Ash16}, and SoLid (Belgium) \cite{Kal17}, whose first results are beginning to be made public.
+There are no signs of slowing down in the field of nuclear reactor antineutrinos, as the largest experiment to date, JUNO designed to measure the neutrino mass hierarchy should be ready for data taking by 2021 \cite{SalAx}.
+JUNO will feature a 20 Million-Ton detector at 80 km from A 27 GW nuclear power plant in China.
+
+The antineutrino spectrum produced in a nuclear reactor is calculated as the sum of the spectra produced by each of the nuclear fuels, 235,238U and 239,241Pu, weighted by the respective fission fractions \cite{Vog81}.
+The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the ‘summation method’.
+Alternatively, for 235U and 239,241Pu the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.
+The current best predictions for the 235U and 239,241Pu are those by Huber \cite{Hub11} using the conversion method, while for 238U is that by Mueller et al.
+\cite{Mue11} using a hybrid conversion-summation method.
+
+The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{20}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
+There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
+Also planned are measurements of beta shape factors as well as a new IAEA Coordinated Research Project to evaluate fission yields.
+Another issue affecting the summation method is the lack of fission yield correlation matrices in the evaluated fission data libraries.
+As a result, uncertainties cannot be fully computed.
+There has been some progress in this area, for instance, the ongoing OECD-NEA subgroup 44 will incorporate this topic \cite{SobXX}.
+
+The summation method has been recently applied in two different situations.
+First, it has been shown that the Daya Bay fuel evolution data \cite{An17} can be explained by summation calculations including an anomaly of about 4% \cite{Hay18}.
+Second, a novel method to analyze the Daya Bay spectrum revealed the signature of 4 individual fission products, while the same method applied to the electron spectra revealed two additional fission products \cite{Son18}.
+
+The conversion method is not fully free of issues, either.
+To start, it is based on a single set of measurements; also, its most basic premise, the description of a level to level spectrum using a particular formalism has not been tested as highly precise measurements of electron spectra for fission products above the inverse beta decay cross section threshold have not been published.
+As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
+A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6%/MeV could explain the anomaly.
+
+Given the dependence of the antineutrino signal on both decay and fission product yield data a series of sensitivity study-guided integral experiments, along the lines of critical assembly integral benchmarks, to validate the underlying nuclear data would provide a strong constraint on the underlying data.
+One approach would involve irradiating fissile and fissionable samples in facilities with well-understood neutron spectra and comparing the observed delayed gamma-rays to a modeled spectrum produced using the Fission Induced Electromagnetic Response (FIER) code developed at Berkeley \cite{Mat18}.
+FIER convolves fission product yield distributions and decay data to predict the gamma-ray spectrum after neutron irradiation.
+The first example of its use involving a comparison to the delayed gamma-ray spectrum from a 235U foil irradiated in the Godiva critical assembly indicated several cases were the underlying fission yields or decay data required improvement.
+
+These experiments would involve a sample of depleted 238U since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the 238U(n,f) yields.
+These measurements could be performed at the Godiva in the same fashion as the 235U irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Har18} and the High Flux Neutron Generator at UC-Berkeley \cite{All18} and compare the results to the FIER predictions to inform both the fission yield and decay data for 238U(n,f).
+
+\subsection{Improved (n,x) data for active interrogation}
+
+An invaluable tool for determining the presence of fissile materials for non-proliferation involves prompt neutron- and gamma-ray spectroscopy coupled to a DT neutron sources with associated particle imaging (DT-API).
+DT-API sources allow tracking of the trajectory of individual neutrons, thereby greatly decreasing background from scattered neutrons.
+The signal from DT-API generators includes long-chain gamma-ray emission from multiple fission events \cite{Pra12,Nak10} as well as prompt gamma- and neutron scattering on a wide range of low- and high-Z materials.
+
+The interpretation of this data requires detailed knowledge of both the double-differential neutron scattering and gamma-ray production cross sections from fast down to thermal neutron energies.
+The Evaluated Gamma Activation File \cite{Fir14} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.
+At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78} which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18} offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.
+
+A program of measurements of gammas emitted from both discrete and QC states would require a relatively modest effort to set in place.
+The data from these measurements could then be used to guide physics-based reaction model, such as the COH, TALYS or EMPIRE to ensure that the total gamma-ray production cross section is consistent with the total capture and scattering cross sections themselves.
+
+\section{ISOTOPE PRODUCTION}
+
+The high energy density and wide range of decay lifetimes and chemical properties of radionuclides near the nuclear valley of stability make them an extremely versatile tool for applications ranging from the diagnosis and treatment of illness, to nuclear non-proliferation and environmental studies to powering spacecraft to explore the outer reaches of the solar system and beyond.
+Furthermore, given that there are hundreds of unstable nuclei with lifetimes in excess of 1 hour and less than 100 years between Hydrogen and Californium, it is clear that we have barely scratched the surface of potential applications.
+However, there are significant uncertainties in both the reactions used to produce these radionuclides and/or the intensities and energies of their decay radiation.
+There have been numerous papers produced over the past 5 years detailing some of the nuclear data needs associated with producing radionuclides for applications.
+For a comprehensive listing of nuclear data needs associated with radionuclides we refer the reader to the summary whitepaper from the Nuclear Data Needs and Capabilities for Applications Workshop held in Berkeley in 2015 \cite{Ndn15}, particularly the reactions and isotopes listed in Appendix B.
+Additional guidance regarding nuclear data needs for medical isotopes can be found in a recent series of IAEA studies \cite{Iae675,Iae596,Iae591} as well as an exhaustive paper from Qaim et al.
+\cite{Qai17}.
+Over 20 million nuclear medicine procedures are performed each year in the United States \cite{Met09}, with the vast majority involving imaging.
+99mTc (t½= 6.0067(5) hour), which decays predominately via the emission of single 140 keV gamma-ray, is used in 80% of of these procedures.
+99mTc is produced via 235U(n,f).
+However, this approach is less than ideal due to the increasing age of many reactors \cite{Qai12} and a nuclear weapons proliferation risk associated with reactors utilizing Highly-Enriched Uranium (HEU).
+As a result, alternative 99mTc production pathways, as well as studies of the associated production of long-lived impurities \cite{Upd13}, are under consideration \cite{Rut09}.
+Other imaging radionuclides include 18F (t½= 109.771(20) min) which is used in Positron Emission Tomography (PET) which is produced locally via the 18O(p,n) reaction, 82Rb (t½=1.2575(2) min) which is used in cardiac imaging and 68Ga  (t½= 67.71(8) min).
+The short half-lives of 82Rb and 68Ga necessitate that they be extracted from a longer-lived radioactive parent nuclide generator whose longer half-lives of 270.93(13) and 25.35(3) days respectively, allow them to be produced at regional facilities and distributed to medical facilities throughout the world.
+In addition to imaging, a large number of therapeutic radiopharmaceuticals are in use or under development for cancer treatment.
+The principle behind therapeutic radionuclide cancer therapy involves depositing a targeted dose, e.g., energy per unit mass, to a tumor cell that capable of producing damage to multiple strands of DNA, from which the cell cannot recover.
+The ideal dose delivery involves radiation with a high Linear Energy Transfer (LET).
+While some - nuclides are already in use, such as 177Lu (t½= 6.6475(20) days), the relatively long range of -particles makes them less favorable than other modes of radioactive decay.
+These include Auger/Coster-Kronig electron-emitters which typically have a range of less than 1 µm, or -particles emitters which have ranges of 2-10 µm.
+There is a particularly large amount of interest in alpha-emitting nucleus 225Ac.
+225Ac is particularly well-suited for medical applications in that it has a long-enough lifetime (t½= 10.0(1) days) to facilitate its incorporation into targeting molecules, and its daughters then decay relatively rapidly (t1/2<3.2 hours) to stable products, minimizing concurrent dose to healthy tissue.
+Other promising alpha-therapeutic radionuclides include 211At, 212Pb/212Bi, 213Bi, 226Th and 227Th have all been identified as high priority topics by the most recent Nuclear Science Advisory Committee’s Long Range Plan on Isotope Production \cite{Nsa15}.
+A particularly promising approach nuclear medical treatment modality involves coupling a pair of chemically similar radioisotopes including of a therapeutic nuclide capable of delivering a high localized radiation dose and a chemically-identical isotope that emits a positron for PET or a gamma suitable for single photon emission computed tomography (SPECT) imaging.
+One such promising “theranostic” pair involves the PET isotope 134Ce (t½= 3.16(4) days) combined with 225Ac.
+A recent NSAC report \cite{Nsa15} highlights additional pairs of isotopes that have potential uses as theranostic agents.
+As mentioned above, most of these promising radionuclides are made at a few regional facilities.
+These include the Isotope Production Facility at Los Alamos National Lab (IPF-LANL), the Brookhaven Linac Isotope Production facility at Brookhaven National Lab (BLIP-BNL) in the United States, the TRIUMF in Canada and iThemba labs in South Africa \cite{Iae675,Nsa15}.
+In a compelling example of the synergy between fundamental nuclear research and societal benefit, LANL-IPF and BLIP-BNL operate symbiotically with the Los Alamos Neutron Science Center at LANL and the Relativistic Heavy Ion Collider at BNL.
+This dual-use approach provides an inexpensive, reliable source of radionuclides needed for the development of new drugs through a public-private partnership.
+All of these regional sources utilize high-energy (≥100 MeV) (p,x) reactions on stable targets.
+In addition to producing the radionuclides of interest these reactions create a large flux of “secondary” spallation protons and neutrons that can in turn initiate nuclear reactions providing either a useful alternative source of valuable radionuclide or a troublesome chemically-identical contaminant.
+The secondary neutron flux is particularly important since the lack of electronic stopping for neutrons makes them advantageous for radionuclide production \cite{Voy18a}.
+The energy spectrum of secondary neutrons from IPF was recently measured using spectral unfolding \cite{Mos16} and for thick target deuteron break-up on beryllium at the LBNL 88-Inch cyclotron \cite{Har18} via a secondary time-of-flight technique.
+A number of therapeutic radionuclides can potentially be produced via secondary neutron-induced (n,p) reactions.
+Examples of possible targets include 32S, 47Ti, natZn (for the production of 64.67Cu), 105Pd, 149Sm, 175Lu, and 177Hf.
+In addition, the production of alpha-emitting radionuclides such as 225Ac, 223Ra, and 227Th using neutrons has yet to be explored.
+Unfortunately, accurate modeling of these high-energy reactions is notoriously difficult.
+Figures 7 shows a comparison between cross sections for the production of 225Ac from (n,x) reactions on 232Th calculated with the reaction codes typically used to predict isotope production.
+This includes EMPIRE-3.2.3, CoH 3.5.1, ALICE-2017, the TENDL-2011 and TENDL-2017 libraries produced using TALYS, as well as the most recent version of the code (TALYS 1.9) \cite{cite-talys} and the European Activation File (EAF-2010).
+Differences on the order of 50-100% are often seen.
+These large uncertainties in reaction modeling means that direct measurement of the reaction cross sections themselves are needed in order to design targets capable of efficient, low-contamination radionuclides.
+Fortunately, most of the reactions of interest take place on stable targets and are therefore experimentally accessible.
+The preferred method for measuring these cross sections involves foil activation, in which one or more well-characterized thin foil(s) is/are irradiated and the residual radioactivity are quantified through off-line alpha, beta, gamma, or electron spectroscopy \cite{Gra16, Voy18b}.
+The uncertainty in the deduced cross section depends strongly on the accurate characterization of the target material (which is often challenging to produce), the spectroscopic assaying techniques used and precise determination of the incident particle flux and
+The flux is typically determined using a well-known monitor reaction on a co-irradiated foil that leads to the production of an easily quantified long-lived residual nucleus.
+However, for both charged-particle and neutron-induced reactions, there relatively few monitor reactions that can be applied in the low to intermediate energy regimes of 30-70 MeV.
+The situation is worse above 70 MeV monitor reactions where values free from the potential influence of secondary neutron contributions are even harder to come by.
+Knowledge of these cross sections as a function of the incident particle energy is central to the isotope production, with recent efforts focused on developing the 93Nb(p,4n)90Mo (t½= 5.56(9) hours) as a monitor reaction \cite{Voy18b, Kim18}.
+
+\section{NUCLEAR ENERGY}
+
+Reliable modeling and simulation predictions of nuclear energy systems is essential to the design, licensing, and operation of nuclear power stations, as well as the fuel cycle facilities for enrichment and material processing, fuel fabrication, transportation and storage.
+Additional predictive calculations are required for spent fuel characterization for storage, transportation and disposal as well as hardware activation and radiation shielding and personnel protection.
+Nuclear data and their uncertainties are required for a wide range of calculations including:
+Reactor core and fuel design,
+Safety parameter assessment,
+Criticality safety,
+Shielding,
+Material damage in structures,
+Decay heat at reactor shut-down,
+Decay heat in storage and transportation,
+Mass flow in the fuel cycle, and
+Material safeguards.
+
+The nuclear physics of these systems are inferred from nuclear data for neutron reaction cross sections, fission spectra, neutron multiplicity, fission product yields, decay constants, branching ratios, gamma yields, delayed neutron precursors, and more.
+For light water reactors (LWRs), nuclear data have been used, tested, and often tuned, over many decades to provide acceptable results, and there is an abundance of documented benchmark quality experiments and plant operation data for the validation of common scenarios.
+However, for new applications such as fuels and materials in advanced reactors, accident tolerant fuels, high burnup fuel, and spent fuel repository scenarios, there are many needs to improve nuclear data and assess the availability of benchmark experiments that could be applied for testing and validation.
+
+One artifact of the nuclear data tuning process, described in previous reference to the work by Bauge, is that confidence is reduced for use of data for applications other than the those for which the evaluations were tuned.
+Where fission and capture reactions are modified to ensure that the integral value of keff is maintained, little confidence remains in the independent use of the fission cross section itself, which is essential to the prediction of reactor power distributions.
+These power distributions are essential to the prediction of peak fuel temperatures during a reactor transient to ensure that the fuel does not exceed thermal limits that are set to ensure that fuel integrity is not compromised.
+Reduced confidence in the fission cross section can have real consequences in the allowed power level and operating regimes for these systems.
+
+In a study conducted by SG46, it was found that many individual reactions were modified by several percent from ENDF/B-VII.1 to ENDF/B-VIII.0 with some examples shown in Figure 8. (ref. Palmiotti)
+
+Figure 6. SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides.
+
+Many of these advanced systems also require so called high-assay low enriched uranium (HA-LEU), which has a 235U enrichment >5% and <20% by mass, were the current fleet of LWRs utilize enrichments of 5% or less.
+With few benchmarks experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where 1H, 16O, 235U, 238U and others are applied simultaneously in the calculation of the integral keff response.
+Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20% enriched 235U in the form of UF6 using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
+A swing in keff of 450 pcm is observed.
+Future investigation and validation are required to gain confidence in either calculation.
+
+Many nuclear data needs have been identified that are important for design and operating analysis for these advanced systems including:.
+
+Improving our knowledge of the 238U inelastic scattering cross section.
+238U(n,n’) is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
+The 40% uncertainty in  this cross section in ENDF/B-VII.1 propagates to an uncertainty of 1.5% k in the criticality state of a sodium fast reactor (i.e.
+at the 2 level, keff could range from 0.97 to 1.03 based on this uncertainty prediction).
+(ref.
+to Touran)
+Changes in the 35Cl(n,p) cross section from the 2006 release of ENDF/B-VII.0 to the 2011 release of ENDF/B-VII.1 are causing a 2-3% k change in reactivity (i.e.
+keff changes from 1.00 to 1.02) in molten salt reactors.
+This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
+Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
+Updates from ENDF/B-VII.0 to ENDF/B-VII.1 lead to a 1% k change in reactivity for the High Temperature engineering Test Reactor (HTTR), which lead to calculations better matching experimental values.
+Proposed updates to the graphite thermal scattering data for the pending ENDF/B-VIII.0 release have been demonstrated to cause a 2% k change in reactivity for the TREAT M8CAL benchmark.
+(ref.
+to Hawari)
+There are no cross-section data that represent the effect of the molecular bonds for thermal neutron scattering in molten salts, such as FLiBe, leading to a computational bias of unknown magnitude in all reactor design calculations.
+For comparison, the molecular bonds in water vs.
+Polyethylene can lead to a computation bias of 1-2% k.
+In addition, the molecular bond effect is temperature dependent and this phenomenon is not well studied or understood.
+A recently developed benchmark experiment evaluation of the Molten Salt Reactor Experiment (MSRE) which consisted of uranium fuel FLiBe molten salt flowing through graphite channels demonstrates a bias of 1.3% k from the experimental value.
+(ref.
+Fratoni)
+Nuclear data for heavy actinides that will buildup in molten salt reactors and high burnup fuel are poorly quantified and benchmark data are rare, so these effects are almost completely unknown.
+Uncertainties provided with ENDF in the form of cross section covariance data are often not mature and may or may not represent the true uncertainty in the nuclear data.
+For the recent ENDF/B-VIII.0 release, the readme file provided by the National Nuclear Data Center (NNDC) provides a disclaimer warning against the use of covariance data without applying a sensitivity/uncertainty approach to adjust the uncertainties for application specific analysis using relevant benchmark experiments.
+This specialized process is generally not available to users and presents many complicated aspects even for experts in the field, leaving a large gap between data provided by nuclear data evaluators and those useful for application in safety and design calculations.
+Nuclear data for depletion, activation, and decay calculations are gathered from many different sources, not only ENDF but also the Evaluated Nuclear Structure Data Files (ENDSF) as well as the Joint European Fission Fusion (JEFF) library, which often have differing representations of the same data.
+The process of sorting through the data to correct inconsistencies and benchmark the consolidated library against benchmark experiments is complex.
+Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
+
+The generation and distribution of nuclear data as well as the benchmarking of the performance of codes and data is a global effort.
+In the US, nuclear data are generated by teams supported by DOE-NP and NNSA.
+These teams gather at the NNDC CSEWG meetings to create and test the ENDF libraries prior to distribution.
+These teams advocate for improved performance for their own applications, but because nuclear energy interests are not well represented at the review meetings, the impact of updates to nuclear data and associated uncertainty information on nuclear energy applications is often overlooked.
+
+\section{FUTURE DIRECTIONS IN NUCLEAR DATA}
+
+In recent years there has been a growing recognition of the need to develop a plan that addresses nuclear data needs from measurement through, compilation and evaluation in an organized, multi-agency fashion.
+This process started in July 2014 with the first review of the US Nuclear Data Program, which is administered through the Nuclear Physics office in the US Department of Energy (DOE-NP), in nearly two decades.
+The review stated that experimental efforts to address gaps in nuclear data are within the scope of the USNDP program resulting in  DOE-NP requesting that a Nuclear Data Needs and Capabilities for Applications Workshop (NDNCA) be organized to compile a listing of nuclear data needed for nuclear energy, national security and isotope production.
+NDNCA was held in Berkeley in May 2015 \cite{} and a whitepaper delineating these needs was released 5 months later.
+The whitepaper provides a long and comprehensive list of nuclear data needs, both cross-cutting and application specific, that has served as the basis for multiple subsequent roadmapping efforts.
+
+Following NDNCA, Dr.
+Catherine Romano, working with the DOE-NP and the NNSA office on counter-proliferation research and development (NA-22), organized a grassroots “Nuclear Data Working Group” (NDWG) comprised of subject matter experts selected by program managers from DOE-NP, DOE-Nuclear Energy, the Isotopes Program, the Department of Homeland Security and the several offices within the National Nuclear Security Administration to identify a “roadmap” to address the most important and crosscutting nuclear data needs including all steps in the nuclear data pipeline from measurement through compilation, evaluation and processing.
+The NDWG presented their results to participating program managers as well as other interested agencies during the Nuclear Data Exchange Meeting (NDEM) in April 2016.
+The scope of the recommended work included:
+1. infrastructure modernization, 
+2. expanded covariance data, 
+3. inelastic scatter on 235U, 238U and 239Pu, 
+4. gamma emission data, 
+5. fission yields, and 
+6. renewed nuclear data target production capabilities.
+The NDEM provided a venue for valuable discussions between the nuclear data community and program managers and the tasks required to provide evaluated nuclear data to the database.
+
+In response to the plan presented by the NDWG, the program managers formed their own Nuclear Data Inter-Agency Working Group (NDIAWG) to pursue a collaborative effort to address several of these high-profile nuclear data needs in a cooperative fashion.
+The NDIAWG issued two Funding Opportunity Announcements in 2017 and 2018 that led to a total of 11 new projects covering topics from improving fission fragment yield and gamma-ray decay data to measuring specific high-priority cross sections for isotope production and neutron transport for nuclear reactors.
+
+A key element of the NDIAWG process is ensuring that the efforts to address these nuclear data needs result in user impact.
+This is accomplished by reviewing the progress made via recurring interagency workshops.
+These workshops initially served as roadmapping discussions where the nuclear data users explained their needs, and the nuclear data community agreed upon a best path forward.
+Now that several projects are underway, the workshops also serve as a project review.
+The first of these was the Nuclear Data Roadmapping Enhancement Workshop (NDREW) held in Washington DC in January 2018, which focused on nuclear data needs relevant to non-proliferation \cite{Ndr18} and resulted in a nuclear data roadmap for NNSA, DNN R\&D.
+The second of these, a Workshop on Applied Nuclear Data Activities (WANDA) is planned for January 2019 in Washington DC and will cover topics relevant to nuclear energy, isotope production, safeguards and the medical community.
+
+The NDIWG process reflects a growing recognition that improved nuclear data is essential to a wide range of human endeavors that transcend the needs of any one societal need or governmental mission.
+Its goal is the development of a new, multi-agency national plan to address nuclear data needs in a coherent way.
+This plan, which is being developed in partnership with international collaborators at the IAEA and the OECD-NEA represents a new paradigm for collaborative research.
+% 
+% %Heading 1
+% \section{FIRST-LEVEL HEADING}
+% This is dummy text. 
+% % Heading 2
+% \subsection{Second-Level Heading}
+% This is dummy text. This is dummy text. This is dummy text. This is dummy text.
+% 
+% % Heading 3
+% \subsubsection{Third-Level Heading}
+% This is dummy text. This is dummy text. This is dummy text. This is dummy text. 
+% 
+% % Heading 4
+% \paragraph{Fourth-Level Heading} Fourth-level headings are placed as part of the paragraph.
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished through section 2.2

@@
 \centering
-\includegraphics[width=0.4\textwidth]{pipeline_cropped.pdf}
+\includegraphics[width=0.39\textwidth]{pipeline_cropped.pdf}
 \caption{\label{fig:pipeline}The nuclear data pipeline.}
@@
 
-The nuclear reaction compilation database is referred to as Experimental Nuclear Reaction Data library (EXFOR) \cite{EXF}.
+The nuclear reaction compilation database is referred to as the Experimental Nuclear Reaction Data library (EXFOR) \cite{EXF}.
 This includes not only reaction cross sections, but also related data such as fission yields, resonance integrals, polarization data and more.
@@
 Elastic and inelastic scattering have a profound effect on neutron populations in any nuclear application by changing the directions and energies of the neutrons in the system.
-However, improvements in neutron scattering data have hampered by the fact that they do not produce easily measured signals like fission, or a radiochemical observable like neutron capture.
+However, improvements in neutron scattering data have been hampered by the fact that they do not produce easily measured signals like fission, or a radiochemical observable like neutron capture.
 The result has been significant disagreements between different reaction evaluations.
@@
 
-One compelling example of compensating errors involves the Jezebel 239Pu critical assembly (PMF1).
-Models of Jezebel using LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) reproduce a unity value of keff to better than 1 part in 104.
-However, when the authors substituted one nuclear quantity one quantity at a time between the two databases, the value of keff varied considerably.
-The greatest changes came from changing the elastic and inelastic scattering cross sections, which led to changes in the keff of -500 pcm and +704 pcm respectively.
-This is shown in Fig.
-2 to the right.
+One compelling example of compensating errors involves the Jezebel \ce{^{239}Pu} critical assembly (PMF1).
+Models of Jezebel using LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) reproduce a unity value of $k_{eff}$ to better than 1 part in 104.
+However, when the authors substituted one nuclear quantity one quantity at a time between the two databases, the value of $k_{eff}$ varied considerably.
+The greatest changes came from changing the elastic and inelastic scattering cross sections, which led to changes in the $k_{eff}$ of -500 pcm and +704 pcm, respectively.
+This is shown in \autoref{fig:rotated_swings}.
 Similar examples of such compensating errors were also seen in earlier work by Bauge \cite{Bau12}.
 
-A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: 1H, 16O, 56Fe, 235,238U and 239Pu in order to address the issue of compensating errors.
-Recently, this list has been expanded to include 14,15N, 9Be, 23Na, 59Co, 58Ni, 238-242Pu.
+\begin{figure}
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.5\linewidth]{rotated_swings.pdf}
 
-CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n’) on the “Big 3” Actinide, leading to “significant differences amongst the evaluations for 239Pu in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.” \cite{Cha14}.
-The 239Pu data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Bat69, And61}.
-The case is similar for 235U where they note that differences for En > 50 keV “have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.”
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Simulations of criticality $k_{eff}$ for \ce{^{239}Pu} for the fast assembly Jezebel, PMF-1.
+This figure shows that both LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) predict similar $k_{eff}$ values, but do so for very different reasons.
+The changes in criticality are evident when individual cross section channels are substituted between the two evaluations.
+The shaded region shows the  resulting range of values for $k_{eff}$.}
+ \label{fig:rotated_swings}
+\end{figure}
 
-One significant source of (n,xn) partial cross section data from 1997 to 2003 was the GEANIE collaboration (Germanium Array for Neutron-Induced Excitations) at the Los Alamos Neutron Science Center/Weapons Neutron Research (LANSCE/WNR) facility.
-While the primary goal of the GEANIE collaboration was the determination of the 239Pu(n,2n) cross section \cite{Ber02}, it resulted in the publication of more than two dozen papers over the course of more than 15 years.
-Experiments were run on all three of the major Actinides: 235U \cite{You01}, 239Pu \cite{Ber02} and 238U \cite{Fot04}.
-It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial -ray cross sections.
+A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: \ce{^{1}H}, \ce{^{16}O}, \ce{^{56}Fe}, \ce{^{235,238}U} and \ce{^{239}Pu} in order to address the issue of compensating errors.
+Recently, this list has been expanded to include \ce{^{14,15}N}, \ce{^{9}Be}, \ce{^{23}Na}, \ce{^{59}Co}, \ce{^{58}Ni}, \ce{^{238-242}Pu}.
+
+CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n') on the \enquote{Big 3} Actinides, leading to \enquote{significant differences amongst the evaluations for \ce{^{239}Pu} in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.} \cite{Cha14}.
+The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Bat69, And61}.
+The case is similar for \ce{^{235}U} where they note that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}
+
+One significant source of (n,xn$\gamma$) partial cross section data from 1997 to 2003 was the GEANIE collaboration (Germanium Array for Neutron-Induced Excitations) at the Los Alamos Neutron Science Center/Weapons Neutron Research (LANSCE/WNR) facility.
+While the primary goal of the GEANIE collaboration was the determination of the \ce{^{239}Pu}(n,2n) cross section \cite{Ber02}, it resulted in the publication of more than two dozen papers over the course of more than 15 years.
+Experiments were run on all three of the major Actinides: \ce{^{235}U} \cite{You01}, \ce{^{239}Pu} \cite{Ber02} and \ce{^{238}U} \cite{Fot04}.
+It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial $\gamma$-ray cross sections.
 
 The need for new scattering data has motivated many new experiments.
-This has included energy-differential/angle-integrated measurements of the 238U(n,n’) cross section using the GELINA spallation neutron source in Geel Belgium by Bacquias et al., \cite{Nem13} and quasi-angle-differential measurements using the Rensselaer Polytechnic Institute Linac by Daskalakis et al., \cite{Das14}.
+This has included energy-differential/angle-integrated measurements of the \ce{^{238}U}(n,n') cross section using the GELINA spallation neutron source in Geel Belgium by Bacquias et al., \cite{Nem13} and quasi-angle-differential measurements using the Rensselaer Polytechnic Institute Linac by Daskalakis et al., \cite{Das14}.
 
-The ideal way to improve (n,n’) data on the 235,238U and 239Pu would be to perform measurements of the scattered neutron in coincidence with transitions emitted by the excited nucleus.
+The ideal way to improve (n,n') data on the \ce{^{235,238}U} and \ce{^{239}Pu} would be to perform measurements of the scattered neutron in coincidence with transitions emitted by the excited nucleus.
 In the case of the Actinides this will potentially require the observation of conversion electrons given that the lowest transitions in all actinides are almost entirely converted.
-Unfortunately, neutron beams usually have quite low intensity, with a fluence in the fast (1-10 MeV) region between 103 and 107 n/s/cm2 at the target location.
-Furthermore, many spallation neutron sources have a significant high energy spectral component that can cause inter-element scattering in a neutron scintillator array rendering precise determination of the scattered neutron energy hard to  perform.
-However, intense limited-energy neutron sources based on thick-target deuteron breakup \cite{Har18} and forward-fitting techniques developed for use at spallation neutron sources \cite{Kee18} off an opportunity to perform neutron-gamma coincident measurements in the fast fission energy spectrum.
+Unfortunately, neutron beams usually have quite low intensity, with a fluence in the fast (1--10 MeV) region between $10^3$ and $10^7$ n/s/cm$^2$ at the target location.
+Furthermore, many spallation neutron sources have a significant high-energy spectral component that can cause inter-element scattering in a neutron scintillator array rendering precise determination of the scattered neutron energy difficult to  perform.
+However, intense limited-energy neutron sources based on thick-target deuteron breakup \cite{Harrig2018} and forward-fitting techniques developed for use at spallation neutron sources \cite{Kee18} off an opportunity to perform neutron-gamma coincident measurements in the fast fission energy spectrum.
 These techniques could provide valuable data to improve nuclear data evaluations of inelastic scattering, even on targets where fission is an open channel.
@@
 The most important of these are the nuclear level density (NLD) as a function of energy, spin and parity, and the radiative strength function (RSF), which describes the ability of excited nuclear matter to absorb or emit photons.
-A number of recent studies have shown the importance of the RSF to modeling (n,) reactions for neutrons with energies between 1 and 100 keV, which corresponds to the spectrum at the site of neutron capture nucleosynthesis in stars \cite{Lar10, Lar15} and energy generation in fast reactors and nuclear security applications.
+A number of recent studies have shown the importance of the RSF to modeling (n,) reactions for neutrons with energies between 1 and 100 keV, which corresponds to the spectrum at the site of neutron capture nucleosynthesis in stars \cite{PhysRevC.82.014318, Lar15} and energy generation in fast reactors and nuclear security applications.
 
-Over the past several years’ work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of “scissors” collective mode throughout the Actinide mass region near the valley of stability including 238U, 239,240,242Pu and 232Th \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
+Over the past several years' work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including 238U, 239,240,242Pu and 232Th \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
 
@@
 
-(n,n’) provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
-Figure 4 shows the ratio of the partial cross section for the population of the  level in 238U(n,n’) as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
-The solid line shows the case where a constant temperature level density is assumed and the spin cut-off parameter was varied from 75% to 125% of its “normal” value given by the equation (3) above.
+(n,n') provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
+Figure 4 shows the ratio of the partial cross section for the population of the  level in 238U(n,n') as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
+The solid line shows the case where a constant temperature level density is assumed and the spin cut-off parameter was varied from 75% to 125% of its \enquote{normal} value given by the equation (3) above.
 The ratio decreases by nearly a factor of 2 with increasing energy.
@@
 Figure 5 shows this for the case of 52mMn(Jπ=2+)/52gMn(Jπ=6+) ratio populated via 56Fe(p,n) measured via stacked target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
-It should be noted that both the (n,n’) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in Section II.B above, and a program of cross section measurements in support of medical isotope production described in sections IV below.
+It should be noted that both the (n,n') and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in Section II.B above, and a program of cross section measurements in support of medical isotope production described in sections IV below.
 This reflects the interdependency between nuclear data over a wide range of applications.
@@
 The antineutrino spectrum produced in a nuclear reactor is calculated as the sum of the spectra produced by each of the nuclear fuels, 235,238U and 239,241Pu, weighted by the respective fission fractions \cite{Vog81}.
-The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the ‘summation method’.
+The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the ‘summation method'.
 Alternatively, for 235U and 239,241Pu the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.
@@
 
-\subsection{Improved (n,x) data for active interrogation}
+\subsection{Improved (n,x$\gamma$) data for active interrogation}
 
@@
 Furthermore, given that there are hundreds of unstable nuclei with lifetimes in excess of 1 hour and less than 100 years between Hydrogen and Californium, it is clear that we have barely scratched the surface of potential applications.
+
 However, there are significant uncertainties in both the reactions used to produce these radionuclides and/or the intensities and energies of their decay radiation.
@@
 \cite{Qai17}.
+
 Over 20 million nuclear medicine procedures are performed each year in the United States \cite{Met09}, with the vast majority involving imaging.
-99mTc (t½= 6.0067(5) hour), which decays predominately via the emission of single 140 keV gamma-ray, is used in 80% of of these procedures.
+99mTc (t$_{1/2}$= 6.0067(5) hour), which decays predominately via the emission of single 140 keV gamma-ray, is used in 80\% of of these procedures.
 99mTc is produced via 235U(n,f).
@@
 As a result, alternative 99mTc production pathways, as well as studies of the associated production of long-lived impurities \cite{Upd13}, are under consideration \cite{Rut09}.
-Other imaging radionuclides include 18F (t½= 109.771(20) min) which is used in Positron Emission Tomography (PET) which is produced locally via the 18O(p,n) reaction, 82Rb (t½=1.2575(2) min) which is used in cardiac imaging and 68Ga  (t½= 67.71(8) min).
+Other imaging radionuclides include 18F (t$_{1/2}$= 109.771(20) min) which is used in Positron Emission Tomography (PET) which is produced locally via the 18O(p,n) reaction, 82Rb (t$_{1/2}$=1.2575(2) min) which is used in cardiac imaging and 68Ga  (t$_{1/2}$= 67.71(8) min).
 The short half-lives of 82Rb and 68Ga necessitate that they be extracted from a longer-lived radioactive parent nuclide generator whose longer half-lives of 270.93(13) and 25.35(3) days respectively, allow them to be produced at regional facilities and distributed to medical facilities throughout the world.
+
 In addition to imaging, a large number of therapeutic radiopharmaceuticals are in use or under development for cancer treatment.
@@
 The ideal dose delivery involves radiation with a high Linear Energy Transfer (LET).
-While some - nuclides are already in use, such as 177Lu (t½= 6.6475(20) days), the relatively long range of -particles makes them less favorable than other modes of radioactive decay.
+While some - nuclides are already in use, such as 177Lu (t$_{1/2}$= 6.6475(20) days), the relatively long range of -particles makes them less favorable than other modes of radioactive decay.
 These include Auger/Coster-Kronig electron-emitters which typically have a range of less than 1 µm, or -particles emitters which have ranges of 2-10 µm.
+
 There is a particularly large amount of interest in alpha-emitting nucleus 225Ac.
-225Ac is particularly well-suited for medical applications in that it has a long-enough lifetime (t½= 10.0(1) days) to facilitate its incorporation into targeting molecules, and its daughters then decay relatively rapidly (t1/2<3.2 hours) to stable products, minimizing concurrent dose to healthy tissue.
-Other promising alpha-therapeutic radionuclides include 211At, 212Pb/212Bi, 213Bi, 226Th and 227Th have all been identified as high priority topics by the most recent Nuclear Science Advisory Committee’s Long Range Plan on Isotope Production \cite{Nsa15}.
+225Ac is particularly well-suited for medical applications in that it has a long-enough lifetime (t$_{1/2}$= 10.0(1) days) to facilitate its incorporation into targeting molecules, and its daughters then decay relatively rapidly (t1/2<3.2 hours) to stable products, minimizing concurrent dose to healthy tissue.
+Other promising alpha-therapeutic radionuclides include 211At, 212Pb/212Bi, 213Bi, 226Th and 227Th have all been identified as high priority topics by the most recent Nuclear Science Advisory Committee's Long Range Plan on Isotope Production \cite{Nsa15}.
+
 A particularly promising approach nuclear medical treatment modality involves coupling a pair of chemically similar radioisotopes including of a therapeutic nuclide capable of delivering a high localized radiation dose and a chemically-identical isotope that emits a positron for PET or a gamma suitable for single photon emission computed tomography (SPECT) imaging.
-One such promising “theranostic” pair involves the PET isotope 134Ce (t½= 3.16(4) days) combined with 225Ac.
+One such promising \enquote{theranostic} pair involves the PET isotope 134Ce (t$_{1/2}$= 3.16(4) days) combined with 225Ac.
 A recent NSAC report \cite{Nsa15} highlights additional pairs of isotopes that have potential uses as theranostic agents.
+
 As mentioned above, most of these promising radionuclides are made at a few regional facilities.
@@
 This dual-use approach provides an inexpensive, reliable source of radionuclides needed for the development of new drugs through a public-private partnership.
+
 All of these regional sources utilize high-energy (≥100 MeV) (p,x) reactions on stable targets.
-In addition to producing the radionuclides of interest these reactions create a large flux of “secondary” spallation protons and neutrons that can in turn initiate nuclear reactions providing either a useful alternative source of valuable radionuclide or a troublesome chemically-identical contaminant.
+In addition to producing the radionuclides of interest these reactions create a large flux of \enquote{secondary} spallation protons and neutrons that can in turn initiate nuclear reactions providing either a useful alternative source of valuable radionuclide or a troublesome chemically-identical contaminant.
 The secondary neutron flux is particularly important since the lack of electronic stopping for neutrons makes them advantageous for radionuclide production \cite{Voy18a}.
@@
 In addition, the production of alpha-emitting radionuclides such as 225Ac, 223Ra, and 227Th using neutrons has yet to be explored.
+
 Unfortunately, accurate modeling of these high-energy reactions is notoriously difficult.
@@
 This includes EMPIRE-3.2.3, CoH 3.5.1, ALICE-2017, the TENDL-2011 and TENDL-2017 libraries produced using TALYS, as well as the most recent version of the code (TALYS 1.9) \cite{cite-talys} and the European Activation File (EAF-2010).
-Differences on the order of 50-100% are often seen.
+Differences on the order of 50--100\% are often seen.
+
 These large uncertainties in reaction modeling means that direct measurement of the reaction cross sections themselves are needed in order to design targets capable of efficient, low-contamination radionuclides.
 Fortunately, most of the reactions of interest take place on stable targets and are therefore experimentally accessible.
+
 The preferred method for measuring these cross sections involves foil activation, in which one or more well-characterized thin foil(s) is/are irradiated and the residual radioactivity are quantified through off-line alpha, beta, gamma, or electron spectroscopy \cite{Gra16, Voy18b}.
 The uncertainty in the deduced cross section depends strongly on the accurate characterization of the target material (which is often challenging to produce), the spectroscopic assaying techniques used and precise determination of the incident particle flux and
+
 The flux is typically determined using a well-known monitor reaction on a co-irradiated foil that leads to the production of an easily quantified long-lived residual nucleus.
@@
 The situation is worse above 70 MeV monitor reactions where values free from the potential influence of secondary neutron contributions are even harder to come by.
-Knowledge of these cross sections as a function of the incident particle energy is central to the isotope production, with recent efforts focused on developing the 93Nb(p,4n)90Mo (t½= 5.56(9) hours) as a monitor reaction \cite{Voy18b, Kim18}.
+Knowledge of these cross sections as a function of the incident particle energy is central to the isotope production, with recent efforts focused on developing the 93Nb(p,4n)90Mo (t$_{1/2}$= 5.56(9) hours) as a monitor reaction \cite{Voy18b, Kim18}.
 
@@
 One artifact of the nuclear data tuning process, described in previous reference to the work by Bauge, is that confidence is reduced for use of data for applications other than the those for which the evaluations were tuned.
-Where fission and capture reactions are modified to ensure that the integral value of keff is maintained, little confidence remains in the independent use of the fission cross section itself, which is essential to the prediction of reactor power distributions.
+Where fission and capture reactions are modified to ensure that the integral value of $k_{eff}$ is maintained, little confidence remains in the independent use of the fission cross section itself, which is essential to the prediction of reactor power distributions.
 These power distributions are essential to the prediction of peak fuel temperatures during a reactor transient to ensure that the fuel does not exceed thermal limits that are set to ensure that fuel integrity is not compromised.
@@
 Many of these advanced systems also require so called high-assay low enriched uranium (HA-LEU), which has a 235U enrichment >5% and <20% by mass, were the current fleet of LWRs utilize enrichments of 5% or less.
-With few benchmarks experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where 1H, 16O, 235U, 238U and others are applied simultaneously in the calculation of the integral keff response.
+With few benchmarks experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where 1H, 16O, 235U, 238U and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
 Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20% enriched 235U in the form of UF6 using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
-A swing in keff of 450 pcm is observed.
+A swing in $k_{eff}$ of 450 pcm is observed.
 Future investigation and validation are required to gain confidence in either calculation.
@@
 Improving our knowledge of the 238U inelastic scattering cross section.
-238U(n,n’) is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
+238U(n,n') is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
 The 40% uncertainty in  this cross section in ENDF/B-VII.1 propagates to an uncertainty of 1.5% k in the criticality state of a sodium fast reactor (i.e.
-at the 2 level, keff could range from 0.97 to 1.03 based on this uncertainty prediction).
+at the 2 level, $k_{eff}$ could range from 0.97 to 1.03 based on this uncertainty prediction).
 (ref.
@@
 Changes in the 35Cl(n,p) cross section from the 2006 release of ENDF/B-VII.0 to the 2011 release of ENDF/B-VII.1 are causing a 2-3% k change in reactivity (i.e.
-keff changes from 1.00 to 1.02) in molten salt reactors.
+$k_{eff}$ changes from 1.00 to 1.02) in molten salt reactors.
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
@@
 Following NDNCA, Dr.
-Catherine Romano, working with the DOE-NP and the NNSA office on counter-proliferation research and development (NA-22), organized a grassroots “Nuclear Data Working Group” (NDWG) comprised of subject matter experts selected by program managers from DOE-NP, DOE-Nuclear Energy, the Isotopes Program, the Department of Homeland Security and the several offices within the National Nuclear Security Administration to identify a “roadmap” to address the most important and crosscutting nuclear data needs including all steps in the nuclear data pipeline from measurement through compilation, evaluation and processing.
+Catherine Romano, working with the DOE-NP and the NNSA office on counter-proliferation research and development (NA-22), organized a grassroots \enquote{Nuclear Data Working Group} (NDWG) comprised of subject matter experts selected by program managers from DOE-NP, DOE-Nuclear Energy, the Isotopes Program, the Department of Homeland Security and the several offices within the National Nuclear Security Administration to identify a \enquote{roadmap} to address the most important and crosscutting nuclear data needs including all steps in the nuclear data pipeline from measurement through compilation, evaluation and processing.
 The NDWG presented their results to participating program managers as well as other interested agencies during the Nuclear Data Exchange Meeting (NDEM) in April 2016.

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished through section 2

@@
 
-\subsection{Improved \ce{^{235,238}U} and \ce{^{239}Pu}(n,n') data for neutron transport}
+\subsection{Improved \ce{^{235,238}U} and \ce{^{239}Pu}(n,n') data for neutron transport}\label{sec:n_transport}
 
@@
 %  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.5\linewidth]{rotated_swings.pdf}
+ \includegraphics[width=0.8\linewidth]{rotated_swings.pdf}
 
@@
 The most important of these are the nuclear level density (NLD) as a function of energy, spin and parity, and the radiative strength function (RSF), which describes the ability of excited nuclear matter to absorb or emit photons.
-A number of recent studies have shown the importance of the RSF to modeling (n,) reactions for neutrons with energies between 1 and 100 keV, which corresponds to the spectrum at the site of neutron capture nucleosynthesis in stars \cite{PhysRevC.82.014318, Lar15} and energy generation in fast reactors and nuclear security applications.
+A number of recent studies have shown the importance of the RSF to modeling (n,$\gamma$) reactions for neutrons with energies between 1 and 100 keV, which corresponds to the spectrum at the site of neutron capture nucleosynthesis in stars \cite{PhysRevC.82.014318, Lar15} and energy generation in fast reactors and nuclear security applications.
 
-Over the past several years' work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including 238U, 239,240,242Pu and 232Th \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
+Over the past several years, work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including \ce{^{238}U}, \ce{^{239,240,242}Pu} and \ce{^{232}Th} \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
 
-Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter () of the form:
+Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter ($\sigma$) of the form:
+\begin{equation}\label{eqn:spin_cutoff}
+\sigma\pp{E_x}=0.01389 \dfrac{A^{5/3}}{\widetilde{a}}\sqrt{aU}
+\end{equation}
+where $U$ is roughly the $E_x$ minus the pairing gap $\Delta$, $a$ is the level density parameter, $A$ is the nuclear mass and $\widetilde{a}$ is the asymptotic level density value one would obtain in the absence of any shell effects.
 
-		(1)
+There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
+This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs.
+$\gamma$-ray emission probability in nuclear reactions.
+This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
 
-where U is roughly the Ex minus the pairing gap , a is the level density parameter, A is the nuclear mass and is the asymptotic level density value one would obtain in the absence of any shell effects.
+\begin{figure}
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.7\linewidth]{fig3.pdf}
 
-There is a great deal uncertainty in the magnitude of the spin cut-off parameter.
-This is a significant issue since a good knowledge of the J distribution is needed to accurately model the neutron vs.
--ray emission probability in nuclear reactions.
-This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in 95Mo well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Ratio of the \ce{^{238}U}(n,n') cross section to the state calculated using TALYS for two different sets of input parameters as a function of incident neutron energy.
+The solid line shows the ratio where spin cutoff has been scaled to $\pm$25\% of its default value.
+The dashed line shows the case where the default value calculated using LD Model 1 (Gilbert and Cameron) is divided by the value obtained using the data from Guttormsen \cite{Gut13a}.}
+ \label{fig:oslo_ld_plot}
+\end{figure}
 
-(n,n') provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
-Figure 4 shows the ratio of the partial cross section for the population of the  level in 238U(n,n') as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
-The solid line shows the case where a constant temperature level density is assumed and the spin cut-off parameter was varied from 75% to 125% of its \enquote{normal} value given by the equation (3) above.
+(n,n'$\gamma$) provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
+\autoref{fig:oslo_ld_plot} shows the ratio of the partial cross section for the population of the  level in \ce{^{238}U}(n,n') as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
+The solid line shows the case where a constant temperature level density is assumed and the spin cut-off parameter was varied from 75\% to 125\% of its \enquote{normal} value given by \autoref{eqn:spin_cutoff} above.
 The ratio decreases by nearly a factor of 2 with increasing energy.
@@
 
-Information regarding the J-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
-This method has been used in Hg and Au by Chakravarty \cite{Cha92} and more recently by Sudar in Hg and Pt \cite{Sud06}.
-Figure 5 shows this for the case of 52mMn(Jπ=2+)/52gMn(Jπ=6+) ratio populated via 56Fe(p,n) measured via stacked target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
-It should be noted that both the (n,n') and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in Section II.B above, and a program of cross section measurements in support of medical isotope production described in sections IV below.
+\begin{figure}
+    \centering
+%     \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{isomer_curves.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+%          \label{fig:before_minimization}
+   \hspace{-5pt}%
+%      \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[width=0.5\textwidth]{}{ldmodels.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         %         \refstepcounter{subfigure}
+%          \label{fig:after_minimization}
+   \hspace{-5pt}%
+    \caption{Predictions of the production of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) isomer-to-ground state ratio as a function of energy for the Gilbert and Cameron level density (left) and using the 6 level density models available in TALYS (right).
+}
+     \label{fig:fe_isomer_plots}
+\end{figure}
+
+Information regarding the $J$-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
+This method has been used in Hg and Au by Chakravarty \cite{PhysRevC.45.1171} and more recently by Sudar in Hg and Pt \cite{PhysRevC.73.034613}.
+\autoref{fig:fe_isomer_plots} shows this for the case of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) ratio populated via \ce{^{56}Fe}(p,$\alpha$n) measured via stacked-target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
+
+It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
 This reflects the interdependency between nuclear data over a wide range of applications.
@@
 
-\section{ISOTOPE PRODUCTION}
+\section{ISOTOPE PRODUCTION}\label{sec:isotope_production}
 

### 2018-12-16 nuclear_data_needs/fig3_plot.m

@@ -1,0 +1,18 @@
+clear all; clc;
+
+load data_p.mat
+
+plot(data_p(:,3),data_p(:,4),'-',data_p(:,1),data_p(:,2),'k--','linewidth',2)
+
+xlim([1 7])
+ylim([0 2])
+
+% ht = title('$^{\mathrm{nat}}$Ti(p,x)$^{48}$Sc');
+hx = xlabel('Neutron Energy (MeV)');
+hy = ylabel('Ratio');
+hl1 = legend({'GC LD','Oslo LD vs. GC LD'},'FontSize',12,'location','best');
+set([hx,hy,hl1],'Interpreter','latex')
+
+export_fig ./fig3.pdf -pdf -transparent
+
+print('./fig3', '-dpng', '-r300');

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished throug section 3.1

@@
 One canonical example of a non-proliferation activity where improvements in multiple cross-cutting areas of nuclear data are needed is the interpretation of the anti-neutrino spectrum from the prompt decay of fission fragments in the core of a nuclear reactor.
-Nuclear reactors are prolific sources of electron antineutrinos, producing about 1021 antineutrinos per second for a typical power reactor.
+Nuclear reactors are prolific sources of electron antineutrinos, producing about $10^{21}$ antineutrinos per second for a typical power reactor.
 These electron antineutrinos are produced by the beta-minus decay of the more than 800 neutron-rich fission fragments, which are the debris from the main source of energy generation in a reactor, the neutron induced fission of actinide nuclides.
 These antineutrinos are also the only radiation escaping from the vessel of a safely operating nuclear reactor, making them ideally suited for reactor monitoring, even in the event that the actor operating the reactor refuses to cooperate with the international community.
-Recent technological advancements in electron antineutrino detection has made another dream a reality, monitoring the performance of nuclear reactors and tracking 239Pu for non-proliferation treaty verification.
+Recent technological advancements in electron antineutrino detection has made another dream a reality, monitoring the performance of nuclear reactors and tracking \ce{^{239}Pu} for non-proliferation treaty verification.
 The WATCHMAN experiment in the UK has just started to explore this field \cite{Cha18}.
@@
 In the last few years, the transformation of electron antineutrinos into the other two flavors was beautifully measured by three large-scale experimental efforts, Daya Bay \cite{An16}, Double Chooz \cite{Abe12} and RENO \cite{Cho16}.
-These experiments also confirmed a deficit of antineutrinos of about 5-9% at short distances that had been revealed in a 2011 re-analysis of the conversion procedure to obtain antineutrino spectra from the measured electron spectra \cite{Men11}.
+These experiments also confirmed a deficit of antineutrinos of about 5--9\% at short distances that had been revealed in a 2011 re-analysis of the conversion procedure to obtain antineutrino spectra from the measured electron spectra \cite{Men11}.
 
 This intriguing deficit, as well as a spectrum distortion, has triggered a new generation of very-short distance reactor experiments, such as NEOS (Korea) \cite{Ko17}, DANSS (Russia) \cite{AleAx}, STEREO (France) \cite{AllAx}, PROSPECT (USA) \cite{Ash16}, and SoLid (Belgium) \cite{Kal17}, whose first results are beginning to be made public.
-There are no signs of slowing down in the field of nuclear reactor antineutrinos, as the largest experiment to date, JUNO designed to measure the neutrino mass hierarchy should be ready for data taking by 2021 \cite{SalAx}.
+There are no signs of slowing down in the field of nuclear reactor antineutrinos, as the largest experiment to date, JUNO, designed to measure the neutrino mass hierarchy, should be ready for data taking by 2021 \cite{SalAx}.
 JUNO will feature a 20 Million-Ton detector at 80 km from A 27 GW nuclear power plant in China.
 
-The antineutrino spectrum produced in a nuclear reactor is calculated as the sum of the spectra produced by each of the nuclear fuels, 235,238U and 239,241Pu, weighted by the respective fission fractions \cite{Vog81}.
-The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the ‘summation method'.
-Alternatively, for 235U and 239,241Pu the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.
-The current best predictions for the 235U and 239,241Pu are those by Huber \cite{Hub11} using the conversion method, while for 238U is that by Mueller et al.
+The antineutrino spectrum produced in a nuclear reactor is calculated as the sum of the spectra produced by each of the nuclear fuels, \ce{^{235,238}U} and \ce{^{239,241}Pu}, weighted by the respective fission fractions \cite{Vog81}.
+The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the \enquote{summation method}.
+Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.
+The current best predictions for  \ce{^{235}U} and \ce{^{239,241}Pu} are those by Huber \cite{Hub11} using the conversion method, while for \ce{^{238}U} is that by Mueller et al.
 \cite{Mue11} using a hybrid conversion-summation method.
@@
 The summation method has been recently applied in two different situations.
-First, it has been shown that the Daya Bay fuel evolution data \cite{An17} can be explained by summation calculations including an anomaly of about 4% \cite{Hay18}.
+First, it has been shown that the Daya Bay fuel evolution data \cite{An17} can be explained by summation calculations including an anomaly of about 4\% \cite{Hay18}.
 Second, a novel method to analyze the Daya Bay spectrum revealed the signature of 4 individual fission products, while the same method applied to the electron spectra revealed two additional fission products \cite{Son18}.
@@
 The conversion method is not fully free of issues, either.
-To start, it is based on a single set of measurements; also, its most basic premise, the description of a level to level spectrum using a particular formalism has not been tested as highly precise measurements of electron spectra for fission products above the inverse beta decay cross section threshold have not been published.
+To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay cross section threshold have not been published.
 As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
-A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6%/MeV could explain the anomaly.
+A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6\%/MeV could explain the anomaly.
 
-Given the dependence of the antineutrino signal on both decay and fission product yield data a series of sensitivity study-guided integral experiments, along the lines of critical assembly integral benchmarks, to validate the underlying nuclear data would provide a strong constraint on the underlying data.
-One approach would involve irradiating fissile and fissionable samples in facilities with well-understood neutron spectra and comparing the observed delayed gamma-rays to a modeled spectrum produced using the Fission Induced Electromagnetic Response (FIER) code developed at Berkeley \cite{Mat18}.
+Given the dependence of the antineutrino signal on both decay and fission product yield data, a series of sensitivity study-guided integral experiments, along the lines of critical assembly integral benchmarks, are needed to validate the underlying nuclear data would provide a strong constraint on the underlying data.
+One approach would involve irradiating fissile and fissionable samples in facilities with well-understood neutron spectra and comparing the observed delayed gamma-rays to a modeled spectrum produced using the Fission Induced Electromagnetic Response (FIER) code developed at Berkeley \cite{Matthews2018}.
 FIER convolves fission product yield distributions and decay data to predict the gamma-ray spectrum after neutron irradiation.
-The first example of its use involving a comparison to the delayed gamma-ray spectrum from a 235U foil irradiated in the Godiva critical assembly indicated several cases were the underlying fission yields or decay data required improvement.
+The first example of its use involving a comparison to the delayed gamma-ray spectrum from a \ce{^{235}U} foil irradiated in the Godiva critical assembly indicated several cases were the underlying fission yields or decay data required improvement.
 
-These experiments would involve a sample of depleted 238U since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the 238U(n,f) yields.
-These measurements could be performed at the Godiva in the same fashion as the 235U irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Har18} and the High Flux Neutron Generator at UC-Berkeley \cite{All18} and compare the results to the FIER predictions to inform both the fission yield and decay data for 238U(n,f).
+These experiments would involve a sample of depleted \ce{^{238}U} since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the \ce{^{238}U}(n,f) yields.
+These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{All18} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).
 
@@
 99mTc (t$_{1/2}$= 6.0067(5) hour), which decays predominately via the emission of single 140 keV gamma-ray, is used in 80\% of of these procedures.
-99mTc is produced via 235U(n,f).
+99mTc is produced via \ce{^{235}U}(n,f).
 However, this approach is less than ideal due to the increasing age of many reactors \cite{Qai12} and a nuclear weapons proliferation risk associated with reactors utilizing Highly-Enriched Uranium (HEU).
@@
 
-Many of these advanced systems also require so called high-assay low enriched uranium (HA-LEU), which has a 235U enrichment >5% and <20% by mass, were the current fleet of LWRs utilize enrichments of 5% or less.
-With few benchmarks experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where 1H, 16O, 235U, 238U and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
-Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20% enriched 235U in the form of UF6 using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
+Many of these advanced systems also require so called high-assay low enriched uranium (HA-LEU), which has a \ce{^{235}U} enrichment >5\% and <20\% by mass, were the current fleet of LWRs utilize enrichments of 5\% or less.
+With few benchmarks experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where 1H, 16O, \ce{^{235}U}, \ce{^{238}U} and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
+Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of UF6 using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
 A swing in $k_{eff}$ of 450 pcm is observed.
@@
 
-Improving our knowledge of the 238U inelastic scattering cross section.
-238U(n,n') is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
-The 40% uncertainty in  this cross section in ENDF/B-VII.1 propagates to an uncertainty of 1.5% k in the criticality state of a sodium fast reactor (i.e.
+Improving our knowledge of the \ce{^{238}U} inelastic scattering cross section.
+\ce{^{238}U}(n,n') is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
+The 40\% uncertainty in  this cross section in ENDF/B-VII.1 propagates to an uncertainty of 1.5\% k in the criticality state of a sodium fast reactor (i.e.
 at the 2 level, $k_{eff}$ could range from 0.97 to 1.03 based on this uncertainty prediction).
@@
 to Touran)
-Changes in the 35Cl(n,p) cross section from the 2006 release of ENDF/B-VII.0 to the 2011 release of ENDF/B-VII.1 are causing a 2-3% k change in reactivity (i.e.
+Changes in the 35Cl(n,p) cross section from the 2006 release of ENDF/B-VII.0 to the 2011 release of ENDF/B-VII.1 are causing a 2-3\% k change in reactivity (i.e.
 $k_{eff}$ changes from 1.00 to 1.02) in molten salt reactors.
@@
 Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
-Updates from ENDF/B-VII.0 to ENDF/B-VII.1 lead to a 1% k change in reactivity for the High Temperature engineering Test Reactor (HTTR), which lead to calculations better matching experimental values.
-Proposed updates to the graphite thermal scattering data for the pending ENDF/B-VIII.0 release have been demonstrated to cause a 2% k change in reactivity for the TREAT M8CAL benchmark.
+Updates from ENDF/B-VII.0 to ENDF/B-VII.1 lead to a 1\% k change in reactivity for the High Temperature engineering Test Reactor (HTTR), which lead to calculations better matching experimental values.
+Proposed updates to the graphite thermal scattering data for the pending ENDF/B-VIII.0 release have been demonstrated to cause a 2\% k change in reactivity for the TREAT M8CAL benchmark.
 (ref.
@@
 For comparison, the molecular bonds in water vs.
-Polyethylene can lead to a computation bias of 1-2% k.
+Polyethylene can lead to a computation bias of 1-2\% k.
 In addition, the molecular bond effect is temperature dependent and this phenomenon is not well studied or understood.
-A recently developed benchmark experiment evaluation of the Molten Salt Reactor Experiment (MSRE) which consisted of uranium fuel FLiBe molten salt flowing through graphite channels demonstrates a bias of 1.3% k from the experimental value.
+A recently developed benchmark experiment evaluation of the Molten Salt Reactor Experiment (MSRE) which consisted of uranium fuel FLiBe molten salt flowing through graphite channels demonstrates a bias of 1.3\% k from the experimental value.
 (ref.
@@
 2. expanded covariance data, 
-3. inelastic scatter on 235U, 238U and 239Pu, 
+3. inelastic scatter on \ce{^{235}U}, \ce{^{238}U} and 239Pu, 
 4. gamma emission data, 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished through section 3

@@
 
-An invaluable tool for determining the presence of fissile materials for non-proliferation involves prompt neutron- and gamma-ray spectroscopy coupled to a DT neutron sources with associated particle imaging (DT-API).
+An invaluable tool for determining the presence of fissile materials for non-proliferation involves prompt neutron- and gamma-ray spectroscopy coupled to a DT neutron source with associated particle imaging (DT-API).
 DT-API sources allow tracking of the trajectory of individual neutrons, thereby greatly decreasing background from scattered neutrons.
@@
 The Evaluated Gamma Activation File \cite{Fir14} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.
-At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78} which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18} offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.
+At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78}, which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18}, offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished through section 5

@@
 Nuclear data and their uncertainties are required for a wide range of calculations including:
-Reactor core and fuel design,
-Safety parameter assessment,
-Criticality safety,
-Shielding,
-Material damage in structures,
-Decay heat at reactor shut-down,
-Decay heat in storage and transportation,
-Mass flow in the fuel cycle, and
-Material safeguards.
+\begin{itemize}
+  \item Reactor core and fuel design,
+  \item Safety parameter assessment,
+  \item Criticality safety,
+  \item Shielding,
+  \item Material damage in structures,
+  \item Decay heat at reactor shut-down,
+  \item Decay heat in storage and transportation,
+  \item Mass flow in the fuel cycle, and
+  \item Material safeguards.
+\end{itemize}
 
-The nuclear physics of these systems are inferred from nuclear data for neutron reaction cross sections, fission spectra, neutron multiplicity, fission product yields, decay constants, branching ratios, gamma yields, delayed neutron precursors, and more.
-For light water reactors (LWRs), nuclear data have been used, tested, and often tuned, over many decades to provide acceptable results, and there is an abundance of documented benchmark quality experiments and plant operation data for the validation of common scenarios.
+The nuclear physics of these systems are inferred from (n,x) cross sections, fission spectra, neutron multiplicity, fission product yields, decay constants, branching ratios, gamma yields, delayed neutron precursors, and more.
+For light water reactors (LWRs), nuclear data have been used, tested, and often \enquote{tuned}, over many decades to provide acceptable results, and there is an abundance of documented benchmark quality experiments and plant operation data for the validation of common scenarios.
 However, for new applications such as fuels and materials in advanced reactors, accident tolerant fuels, high burnup fuel, and spent fuel repository scenarios, there are many needs to improve nuclear data and assess the availability of benchmark experiments that could be applied for testing and validation.
 
-One artifact of the nuclear data tuning process, described in previous reference to the work by Bauge, is that confidence is reduced for use of data for applications other than the those for which the evaluations were tuned.
+One artifact of the nuclear data tuning process is a reduction in confidence due to compensating errors.
 Where fission and capture reactions are modified to ensure that the integral value of $k_{eff}$ is maintained, little confidence remains in the independent use of the fission cross section itself, which is essential to the prediction of reactor power distributions.
-These power distributions are essential to the prediction of peak fuel temperatures during a reactor transient to ensure that the fuel does not exceed thermal limits that are set to ensure that fuel integrity is not compromised.
+These power distributions are essential to the prediction of peak fuel temperatures during a reactor transient to ensure that the fuel does not exceed thermal limits that are set to ensure fuel integrity.
 Reduced confidence in the fission cross section can have real consequences in the allowed power level and operating regimes for these systems.
 
-In a study conducted by SG46, it was found that many individual reactions were modified by several percent from ENDF/B-VII.1 to ENDF/B-VIII.0 with some examples shown in Figure 8. (ref. Palmiotti)
+In a study conducted by SG46, it was found that many individual reactions were modified by several percent from ENDF/B-VII.1 to ENDF/B-VIII.0 with some examples shown in \autoref{fig:ne_plots}.
 
-Figure 6. SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides.
+\begin{figure}
+    \centering
+%     \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{u235.png}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+%          \label{fig:before_minimization}
+   \hspace{-5pt}%
+%      \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[width=0.5\textwidth]{}{u238.png}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         %         \refstepcounter{subfigure}
+%          \label{fig:after_minimization}
+   \hspace{-5pt}%\\
+       \centering
+%     \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{pu239_1.png}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+%          \label{fig:before_minimization}
+   \hspace{-5pt}%
+%      \subfloat{
+        \centering
+%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+        \subfigimg[width=0.5\textwidth]{}{pu239_2.png}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+         %         \refstepcounter{subfigure}
+%          \label{fig:after_minimization}
+   \hspace{-5pt}%
+    \caption{SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
+     \label{fig:ne_plots}
+\end{figure}
 
-Many of these advanced systems also require so called high-assay low enriched uranium (HA-LEU), which has a \ce{^{235}U} enrichment >5\% and <20\% by mass, were the current fleet of LWRs utilize enrichments of 5\% or less.
-With few benchmarks experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where 1H, 16O, \ce{^{235}U}, \ce{^{238}U} and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
-Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of UF6 using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
+Many of these advanced systems also require so-called high-assay low enriched uranium (HA-LEU), which has a \ce{^{235}U} enrichment \textgreater5\% and \textless20\% by mass, where the current fleet of LWRs utilize enrichments of 5\% or less.
+With few benchmark experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where \ce{^{1}H}, \ce{^{16}O}, \ce{^{235}U}, \ce{^{238}U} and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
+Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
 A swing in $k_{eff}$ of 450 pcm is observed.
@@
 
-Many nuclear data needs have been identified that are important for design and operating analysis for these advanced systems including:.
-
-Improving our knowledge of the \ce{^{238}U} inelastic scattering cross section.
+Many nuclear data needs have been identified that are important for design and operating analysis for these advanced systems including:
+\begin{itemize}
+  \item Improving our knowledge of the \ce{^{238}U}(n,n')cross section.
 \ce{^{238}U}(n,n') is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
-The 40\% uncertainty in  this cross section in ENDF/B-VII.1 propagates to an uncertainty of 1.5\% k in the criticality state of a sodium fast reactor (i.e.
-at the 2 level, $k_{eff}$ could range from 0.97 to 1.03 based on this uncertainty prediction).
-(ref.
-to Touran)
-Changes in the 35Cl(n,p) cross section from the 2006 release of ENDF/B-VII.0 to the 2011 release of ENDF/B-VII.1 are causing a 2-3\% k change in reactivity (i.e.
-$k_{eff}$ changes from 1.00 to 1.02) in molten salt reactors.
+The 40\% uncertainty in this cross section in ENDF/B-VII.1 propagates to an uncertainty of 1.5\%$\Delta k$ in the criticality state of a sodium fast reactor (i.e.
+at the 2$\sigma$ level, $k_{eff}$ could range from 0.97 to 1.03 based on this uncertainty prediction) \cite{touran2016sensitivities}.
+  \item Improved knowledge of the \ce{^{35}Cl}(n,p) cross section.
+Changes from the 2006 release of ENDF/B-VII.0 to the 2011 release of ENDF/B-VII.1 are causing a 2-3\%$\Delta k$ change in reactivity in molten salt reactors.
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
-Updates from ENDF/B-VII.0 to ENDF/B-VII.1 lead to a 1\% k change in reactivity for the High Temperature engineering Test Reactor (HTTR), which lead to calculations better matching experimental values.
-Proposed updates to the graphite thermal scattering data for the pending ENDF/B-VIII.0 release have been demonstrated to cause a 2\% k change in reactivity for the TREAT M8CAL benchmark.
-(ref.
-to Hawari)
-There are no cross-section data that represent the effect of the molecular bonds for thermal neutron scattering in molten salts, such as FLiBe, leading to a computational bias of unknown magnitude in all reactor design calculations.
-For comparison, the molecular bonds in water vs.
-Polyethylene can lead to a computation bias of 1-2\% k.
-In addition, the molecular bond effect is temperature dependent and this phenomenon is not well studied or understood.
-A recently developed benchmark experiment evaluation of the Molten Salt Reactor Experiment (MSRE) which consisted of uranium fuel FLiBe molten salt flowing through graphite channels demonstrates a bias of 1.3\% k from the experimental value.
-(ref.
-Fratoni)
-Nuclear data for heavy actinides that will buildup in molten salt reactors and high burnup fuel are poorly quantified and benchmark data are rare, so these effects are almost completely unknown.
-Uncertainties provided with ENDF in the form of cross section covariance data are often not mature and may or may not represent the true uncertainty in the nuclear data.
+\textred{Lee - we should add some language here referencing Batch's work on this.}
+  \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
+Updates from ENDF/B-VII.0 to ENDF/B-VII.1 lead to a 1\%$\Delta k$ change in reactivity for the High Temperature Engineering Test Reactor (HTTR), leading to the calculations better matching experimental values.
+Proposed updates to the graphite thermal scattering data for the ENDF/B-VIII.0 release have been demonstrated to cause a 2\%$\Delta k$ change in reactivity for the TREAT M8CAL benchmark \cite{hawarithermal}.
+  \item Thermal neutron scattering in molten salts, such as FLiBe.
+There are no cross-section data that represent the effect of the molecular bonds, leading to a computational bias of unknown magnitude in all reactor design calculations.
+The molecular bonds in water vs.
+Polyethylene can lead to a computation bias of 1-2\%$\Delta k$.
+In addition, this effect is temperature dependent and is not well studied or understood.
+A recently developed benchmark experiment evaluation of the Molten Salt Reactor Experiment which consisted of uranium fuel FLiBe molten salt flowing through graphite channels demonstrates a bias of over 1\%$\Delta k$ from the experimental value \cite{shenzero}, with other presented results showing biases over 3\%$\Delta k$
+  \item (n,x) reactions on heavy actinides that will buildup in molten salt reactors and high burnup fuel are poorly quantified and benchmark data are rare, so these effects are almost completely unknown.
+  \item Uncertainties provided with ENDF in the form of cross section covariance data are often not mature and may or may not represent the true uncertainty in the nuclear data.
 For the recent ENDF/B-VIII.0 release, the readme file provided by the National Nuclear Data Center (NNDC) provides a disclaimer warning against the use of covariance data without applying a sensitivity/uncertainty approach to adjust the uncertainties for application specific analysis using relevant benchmark experiments.
 This specialized process is generally not available to users and presents many complicated aspects even for experts in the field, leaving a large gap between data provided by nuclear data evaluators and those useful for application in safety and design calculations.
-Nuclear data for depletion, activation, and decay calculations are gathered from many different sources, not only ENDF but also the Evaluated Nuclear Structure Data Files (ENDSF) as well as the Joint European Fission Fusion (JEFF) library, which often have differing representations of the same data.
+  \item Nuclear data are gathered from many different sources, not only ENDF but also the ENSDF as well as the Joint European Fission Fusion (JEFF) library, which often have differing representations of the same data.
 The process of sorting through the data to correct inconsistencies and benchmark the consolidated library against benchmark experiments is complex.
-Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
+  \item Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
+\end{itemize}
 
@@
 In the US, nuclear data are generated by teams supported by DOE-NP and NNSA.
-These teams gather at the NNDC CSEWG meetings to create and test the ENDF libraries prior to distribution.
-These teams advocate for improved performance for their own applications, but because nuclear energy interests are not well represented at the review meetings, the impact of updates to nuclear data and associated uncertainty information on nuclear energy applications is often overlooked.
+These teams gather at the Cross Section Evaluation Working Group meetings to create and test the ENDF libraries prior to distribution.
+They advocate for improved performance for their own applications, but because nuclear energy interests are not well represented at the review meetings, the impact of updates to nuclear data and associated uncertainty information on nuclear energy applications is often overlooked.
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished through section 6

@@
 %Authors, affiliations address.
-\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^6$
+\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^6$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^7$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
 \affil{$^2$Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
-\affil{$^3$Brookhaven National Laboratory, Upton, NY 11973, USA}
-\affil{$^4$Arjan's affiliations}
-\affil{$^5$Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^6$Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
+\affil{$^3$National Nuclear Data Center, Brookhaven National Laboratory, Upton, NY 11973, USA}
+\affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
+\affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^6$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^7$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
 
@@
 \begin{keywords}
-keywords, separated by comma, no full stop, lowercase
+\textred{Add keywords here!}  keywords, separated by comma, no full stop, lowercase
 \end{keywords}
@@
 This process started in July 2014 with the first review of the US Nuclear Data Program, which is administered through the Nuclear Physics office in the US Department of Energy (DOE-NP), in nearly two decades.
-The review stated that experimental efforts to address gaps in nuclear data are within the scope of the USNDP program resulting in  DOE-NP requesting that a Nuclear Data Needs and Capabilities for Applications Workshop (NDNCA) be organized to compile a listing of nuclear data needed for nuclear energy, national security and isotope production.
-NDNCA was held in Berkeley in May 2015 \cite{} and a whitepaper delineating these needs was released 5 months later.
+The review stated that experimental efforts to address gaps in nuclear data are within the scope of the USNDP program, resulting in  DOE-NP requesting that a Nuclear Data Needs and Capabilities for Applications Workshop (NDNCA) be organized to compile a listing of nuclear data needed for nuclear energy, national security and isotope production.
+NDNCA was held in Berkeley in May 2015  and a whitepaper delineating these needs was released 5 months later \cite{bernstein2015nuclear}.
 The whitepaper provides a long and comprehensive list of nuclear data needs, both cross-cutting and application specific, that has served as the basis for multiple subsequent roadmapping efforts.
@@
 The scope of the recommended work included:
-1. infrastructure modernization, 
-2. expanded covariance data, 
-3. inelastic scatter on \ce{^{235}U}, \ce{^{238}U} and 239Pu, 
-4. gamma emission data, 
-5. fission yields, and 
-6. renewed nuclear data target production capabilities.
+\begin{enumerate}
+  \item infrastructure modernization, 
+  \item expanded covariance data, 
+  \item inelastic scatter on \ce{^{235}U}, \ce{^{238}U} and 239Pu, 
+  \item gamma emission data, 
+  \item fission yields, and 
+  \item renewed nuclear data target production capabilities.
+\end{enumerate}  
 The NDEM provided a venue for valuable discussions between the nuclear data community and program managers and the tasks required to provide evaluated nuclear data to the database.
@@
 \section*{DISCLOSURE STATEMENT}
-If the authors have noting to disclose, the following statement will be used: The authors are not aware of any affiliations, memberships, funding, or financial holdings that
-might be perceived as affecting the objectivity of this review.
+\textred{If the authors have noting to disclose, the following statement will be used: The authors are not aware of any affiliations, memberships, funding, or financial holdings that
+might be perceived as affecting the objectivity of this review. }
 
@@
 \section*{ACKNOWLEDGMENTS}
-Acknowledgements, general annotations, funding.
+Work at Brookhaven National Laboratory was sponsored by the Office of Nuclear Physics, Office of Science of the U.S.
+Department of Energy under Contract \# DE-AC02-98CH10886 with Brookhaven Science Associates, LLC.
+
+The authors acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics.
+
+Work at Lawrence Berkeley National Laboratory has been carried out  under the auspices of the U.S.
+Department of Energy by  Lawrence Berkeley National Laboratory and the U.S.
+Nuclear Data Program under contract \# DE-AC02-05CH11231.
+This work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
+
+\textred{EVERYONE - Please provide me snippets of any other Acknowledgements you want included!}
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Finished LaTeX convserion of first draft!  Sending to Lee for comments.

@@
 
-\documentclass[letterpaper,draft]{ar-1col}
+\documentclass[letterpaper]{ar-1col}
+% \documentclass[letterpaper,draft]{ar-1col}
 \usepackage[numbers]{natbib}
@@
 % % \usepackage{refcount}
-% % \usepackage{siunitx}
+\usepackage{siunitx}
 % % \usepackage{lastpage}
@@
     \centering
-%     \subfloat{
+    \begin{minipage}{0.5\textwidth}
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{isomer_curves.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         %         \refstepcounter{subfigure}
-%          \label{fig:before_minimization}
-   \hspace{-5pt}%
-%      \subfloat{
+        \includegraphics[width=0.97\textwidth]{isomer_curves.pdf} % first figure itself
+%         \caption{first figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.5\textwidth}
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=0.5\textwidth]{}{ldmodels.pdf}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         %         \refstepcounter{subfigure}
-%          \label{fig:after_minimization}
-   \hspace{-5pt}%
+        \includegraphics[width=0.97\textwidth]{ldmodels.pdf} % second figure itself
+%         \caption{second figure}
+    \end{minipage}
     \caption{Predictions of the production of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) isomer-to-ground state ratio as a function of energy for the Gilbert and Cameron level density (left) and using the 6 level density models available in TALYS (right).
@@
 \end{figure}
+
+% \begin{figure}
+%     \centering
+% %     \subfloat{
+% %         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \hspace{-5pt}
+%         \includegraphics[width=0.3\textwidth]{isomer_curves.pdf} \includegraphics[width=0.3\textwidth]{ldmodels.pdf}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+%          %         \refstepcounter{subfigure}
+% %          \label{fig:before_minimization}
+% %    \hspace{-5pt}%
+% %      \subfloat{
+% %         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+% %         \includegraphics[width=0.3\textwidth]{ldmodels.pdf}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+%          %         \refstepcounter{subfigure}
+% %          \label{fig:after_minimization}
+% %    \hspace{-5pt}%
+%     \caption{Predictions of the production of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) isomer-to-ground state ratio as a function of energy for the Gilbert and Cameron level density (left) and using the 6 level density models available in TALYS (right).
+}
+%      \label{fig:fe_isomer_plots}
+% \end{figure}
 
@@
 
+\textred{We seem to have plenty of space - should we add the FIER plot back in?}
+
 These experiments would involve a sample of depleted \ce{^{238}U} since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the \ce{^{238}U}(n,f) yields.
@@
 
-The high energy density and wide range of decay lifetimes and chemical properties of radionuclides near the nuclear valley of stability make them an extremely versatile tool for applications ranging from the diagnosis and treatment of illness, to nuclear non-proliferation and environmental studies to powering spacecraft to explore the outer reaches of the solar system and beyond.
+The high energy density and wide range of decay lifetimes and chemical properties of radionuclides near the nuclear valley of stability make them an extremely versatile tool for applications ranging from the diagnosis and treatment of illness, to nuclear non-proliferation and environmental studies, to powering spacecraft to explore the outer reaches of the solar system and beyond.
 Furthermore, given that there are hundreds of unstable nuclei with lifetimes in excess of 1 hour and less than 100 years between Hydrogen and Californium, it is clear that we have barely scratched the surface of potential applications.
@@
 There have been numerous papers produced over the past 5 years detailing some of the nuclear data needs associated with producing radionuclides for applications.
-For a comprehensive listing of nuclear data needs associated with radionuclides we refer the reader to the summary whitepaper from the Nuclear Data Needs and Capabilities for Applications Workshop held in Berkeley in 2015 \cite{Ndn15}, particularly the reactions and isotopes listed in Appendix B.
+For a comprehensive listing of nuclear data needs associated with radionuclides we refer the reader to the summary whitepaper from the Nuclear Data Needs and Capabilities for Applications Workshop held in Berkeley in 2015 \cite{bernstein2015nuclear}, particularly the reactions and isotopes listed in Appendix B.
 Additional guidance regarding nuclear data needs for medical isotopes can be found in a recent series of IAEA studies \cite{Iae675,Iae596,Iae591} as well as an exhaustive paper from Qaim et al.
-\cite{Qai17}.
+\cite{Qaim201731}.
 
 Over 20 million nuclear medicine procedures are performed each year in the United States \cite{Met09}, with the vast majority involving imaging.
-99mTc (t$_{1/2}$= 6.0067(5) hour), which decays predominately via the emission of single 140 keV gamma-ray, is used in 80\% of of these procedures.
-99mTc is produced via \ce{^{235}U}(n,f).
+\ce{^{99m}Tc} ($t_{1/2}$ = 6.0067(5) hour), which decays predominately via the emission of single 140 keV gamma-ray, is used in 80\% of of these procedures.
+\ce{^{99m}Tc} is produced via \ce{^{235}U}(n,f).
 However, this approach is less than ideal due to the increasing age of many reactors \cite{Qai12} and a nuclear weapons proliferation risk associated with reactors utilizing Highly-Enriched Uranium (HEU).
-As a result, alternative 99mTc production pathways, as well as studies of the associated production of long-lived impurities \cite{Upd13}, are under consideration \cite{Rut09}.
-Other imaging radionuclides include 18F (t$_{1/2}$= 109.771(20) min) which is used in Positron Emission Tomography (PET) which is produced locally via the 18O(p,n) reaction, 82Rb (t$_{1/2}$=1.2575(2) min) which is used in cardiac imaging and 68Ga  (t$_{1/2}$= 67.71(8) min).
-The short half-lives of 82Rb and 68Ga necessitate that they be extracted from a longer-lived radioactive parent nuclide generator whose longer half-lives of 270.93(13) and 25.35(3) days respectively, allow them to be produced at regional facilities and distributed to medical facilities throughout the world.
+As a result, alternative \ce{^{99m}Tc} production pathways, as well as studies of the associated production of long-lived impurities \cite{Updegraff2013}, are under consideration \cite{Rut09}.
+
+Other imaging radionuclides are used in Positron Emission Tomography (PET), which is now so commonplace that
+there are numerous companies   providing production capabilities built around low-energy \enquote{medical cyclotrons.} 
+The utility of PET imaging, combined with the recent rise in multimodal PET/MRI and PET/CT imaging,  has
+led to significant interest in the development of other $\beta^+$ emitting radionuclides.
+These include \ce{^{18}F} ($t_{1/2}$ = 109.771(20) min), which is produced locally via the \ce{^{18}O}(p,n) reaction, \ce{^{82}Rb} ($t_{1/2}$ = 1.2575(2) min), which is used in cardiac imaging, and \ce{^{68}Ga}  ($t_{1/2}$ = 67.71(8) min), which is used in the detection of a wide range of tumors.
+The short half-lives of \ce{^{82}Rb} and \ce{^{68}Ga} necessitate that they be extracted from a longer-lived radioactive parent nuclide generator whose longer half-lives of 270.93(13) and 25.35(3) days, respectively, allow them to be produced at regional facilities and distributed to medical facilities throughout the world.
 
 In addition to imaging, a large number of therapeutic radiopharmaceuticals are in use or under development for cancer treatment.
-The principle behind therapeutic radionuclide cancer therapy involves depositing a targeted dose, e.g., energy per unit mass, to a tumor cell that capable of producing damage to multiple strands of DNA, from which the cell cannot recover.
+The principle behind therapeutic radionuclide cancer therapy involves depositing a targeted dose, e.g., energy per unit mass, to a tumor cell,  capable of producing damage to multiple strands of DNA, from which the cell cannot recover.
 The ideal dose delivery involves radiation with a high Linear Energy Transfer (LET).
-While some - nuclides are already in use, such as 177Lu (t$_{1/2}$= 6.6475(20) days), the relatively long range of -particles makes them less favorable than other modes of radioactive decay.
-These include Auger/Coster-Kronig electron-emitters which typically have a range of less than 1 µm, or -particles emitters which have ranges of 2-10 µm.
+While some $\beta^-$ nuclides are already in use, such as \ce{^{177}Lu} ($t_{1/2}$ = 6.6475(20) days), the relatively long range of $\beta^-$-particles makes them less favorable than other modes of radioactive decay.
+These include Auger/Coster-Kronig electron-emitters, which typically have a range of less than 1 \mmicro m, or $\alpha$-particle emitters, which have ranges of 2--10 \mmicro m.
 
-There is a particularly large amount of interest in alpha-emitting nucleus 225Ac.
-225Ac is particularly well-suited for medical applications in that it has a long-enough lifetime (t$_{1/2}$= 10.0(1) days) to facilitate its incorporation into targeting molecules, and its daughters then decay relatively rapidly (t1/2<3.2 hours) to stable products, minimizing concurrent dose to healthy tissue.
-Other promising alpha-therapeutic radionuclides include 211At, 212Pb/212Bi, 213Bi, 226Th and 227Th have all been identified as high priority topics by the most recent Nuclear Science Advisory Committee's Long Range Plan on Isotope Production \cite{Nsa15}.
+There is a particularly large amount of interest in the alpha-emitting radionuclide \ce{^{225}Ac}.
+\ce{^{225}Ac} is particularly well-suited for medical applications in that it has a sufficiently long lifetime ($t_{1/2}$ = 10.0(1) days) to facilitate its incorporation into targeting molecules, and its daughters then decay relatively rapidly ($t_{1/2}<$ 3.2 hours) to stable products, minimizing concurrent dose to healthy tissue.
+Other promising alpha-therapeutic radionuclides include \ce{^{211}At}, \ce{^{212}Pb}/\ce{^{212}Bi}, \ce{^{213}Bi}, \ce{^{226}Th} and \ce{^{227}Th}, and have all been identified as high priority topics by the most recent Nuclear Science Advisory Committee's Long Range Plan on Isotope Production \cite{NSACIsotopesSubcommittee2015}.
 
-A particularly promising approach nuclear medical treatment modality involves coupling a pair of chemically similar radioisotopes including of a therapeutic nuclide capable of delivering a high localized radiation dose and a chemically-identical isotope that emits a positron for PET or a gamma suitable for single photon emission computed tomography (SPECT) imaging.
-One such promising \enquote{theranostic} pair involves the PET isotope 134Ce (t$_{1/2}$= 3.16(4) days) combined with 225Ac.
-A recent NSAC report \cite{Nsa15} highlights additional pairs of isotopes that have potential uses as theranostic agents.
+A particularly promising  nuclear medical treatment modality involves coupling a pair of chemically similar radioisotopes including of a therapeutic nuclide capable of delivering a highly localized radiation dose and a chemically-identical isotope that emits a positron for PET or a gamma suitable for single photon emission computed tomography (SPECT) imaging.
+Examples of these \enquote{theranostic pairs} include \ce{^{188}Pt} or \ce{^{191}Pt} for use in imaging, together with \ce{^{193m}Pt}, \ce{^{195m}Pt}, and \ce{^{197}Pt}, which all have  therapeutic potential.
+Another such promising  pair involves the PET isotope \ce{^{134}Ce} ($t_{1/2}$ = 3.16(4) days) combined with \ce{^{225}Ac}.
+A recent NSAC report \cite{NSACIsotopesSubcommittee2015} highlights additional pairs of isotopes that have potential uses as theranostic agents.
 
 As mentioned above, most of these promising radionuclides are made at a few regional facilities.
-These include the Isotope Production Facility at Los Alamos National Lab (IPF-LANL), the Brookhaven Linac Isotope Production facility at Brookhaven National Lab (BLIP-BNL) in the United States, the TRIUMF in Canada and iThemba labs in South Africa \cite{Iae675,Nsa15}.
+These include the Isotope Production Facility at Los Alamos National Lab (IPF-LANL), the Brookhaven Linac Isotope Production facility at Brookhaven National Lab (BLIP-BNL) in the United States, the TRIUMF laboratory in Canada and iThemba LABS in South Africa \cite{Iae675,NSACIsotopesSubcommittee2015}.
 In a compelling example of the synergy between fundamental nuclear research and societal benefit, LANL-IPF and BLIP-BNL operate symbiotically with the Los Alamos Neutron Science Center at LANL and the Relativistic Heavy Ion Collider at BNL.
@@
 
-All of these regional sources utilize high-energy (≥100 MeV) (p,x) reactions on stable targets.
+All of these regional sources utilize high-energy ($\geq$ 100 MeV) (p,x) reactions on stable targets.
 In addition to producing the radionuclides of interest these reactions create a large flux of \enquote{secondary} spallation protons and neutrons that can in turn initiate nuclear reactions providing either a useful alternative source of valuable radionuclide or a troublesome chemically-identical contaminant.
-The secondary neutron flux is particularly important since the lack of electronic stopping for neutrons makes them advantageous for radionuclide production \cite{Voy18a}.
-The energy spectrum of secondary neutrons from IPF was recently measured using spectral unfolding \cite{Mos16} and for thick target deuteron break-up on beryllium at the LBNL 88-Inch cyclotron \cite{Har18} via a secondary time-of-flight technique.
+The secondary neutron flux is particularly important since the lack of electronic stopping for neutrons makes them advantageous for radionuclide production \cite{Voyles2017}.
+The energy spectrum of secondary neutrons from IPF was recently measured using spectral unfolding \cite{Mos16} and for thick-target deuteron break-up on beryllium at the LBNL 88-Inch cyclotron \cite{Harrig2018} via a secondary time-of-flight technique.
 A number of therapeutic radionuclides can potentially be produced via secondary neutron-induced (n,p) reactions.
-Examples of possible targets include 32S, 47Ti, natZn (for the production of 64.67Cu), 105Pd, 149Sm, 175Lu, and 177Hf.
-In addition, the production of alpha-emitting radionuclides such as 225Ac, 223Ra, and 227Th using neutrons has yet to be explored.
+Examples of possible targets include \ce{^{32}S}, \ce{^{47}Ti}, \ce{^{nat}Zn} (for the production of \ce{^{64,67}Cu}), \ce{^{105}Pd}, \ce{^{149}Sm}, \ce{^{175}Lu}, and \ce{^{177}Hf}.
+In addition, the production of alpha-emitting radionuclides such as \ce{^{225}Ac}, \ce{^{223}Ra}, and \ce{^{227}Th} using neutrons has yet to be explored.
+
+\begin{figure}
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.7\linewidth]{225Ac.pdf}
+
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Predictions of several major reaction model codes for the (n,x) reactions leading to the production of \ce{^{225}Ac}.  Differences of up to an order of magnitude are commonly seen.    }
+ \label{fig:ithemba_plot}
+\end{figure}
 
 Unfortunately, accurate modeling of these high-energy reactions is notoriously difficult.
-Figures 7 shows a comparison between cross sections for the production of 225Ac from (n,x) reactions on 232Th calculated with the reaction codes typically used to predict isotope production.
-This includes EMPIRE-3.2.3, CoH 3.5.1, ALICE-2017, the TENDL-2011 and TENDL-2017 libraries produced using TALYS, as well as the most recent version of the code (TALYS 1.9) \cite{cite-talys} and the European Activation File (EAF-2010).
+\autoref{fig:ithemba_plot} shows a comparison between cross sections for the production of \ce{^{225}Ac} from (n,x) reactions on \ce{^{232}Th} calculated with the reaction codes typically used to predict isotope production.
+This includes EMPIRE-3.2.3 \cite{Herman2013}, CoH 3.5.1 \cite{KAWANO2010}, ALICE-2017 \cite{Blann1996}, the TENDL-2011 and TENDL-2017 libraries produced using TALYS \cite{Rochman2017}, as well as the most recent version of the code (TALYS 1.9) \cite{Koning2012} and the European Activation File (EAF-2010) \cite{Forrest2005}.
 Differences on the order of 50--100\% are often seen.
 
-These large uncertainties in reaction modeling means that direct measurement of the reaction cross sections themselves are needed in order to design targets capable of efficient, low-contamination radionuclides.
+These large uncertainties in reaction modeling means that direct measurement of the reaction cross sections themselves are needed in order to design targets capable of efficiently producing low-contamination radionuclides.
 Fortunately, most of the reactions of interest take place on stable targets and are therefore experimentally accessible.
 
-The preferred method for measuring these cross sections involves foil activation, in which one or more well-characterized thin foil(s) is/are irradiated and the residual radioactivity are quantified through off-line alpha, beta, gamma, or electron spectroscopy \cite{Gra16, Voy18b}.
-The uncertainty in the deduced cross section depends strongly on the accurate characterization of the target material (which is often challenging to produce), the spectroscopic assaying techniques used and precise determination of the incident particle flux and
+The preferred method for measuring these cross sections involves foil activation, in which one or more well-characterized thin foil(s) is/are irradiated and the residual radioactivities are quantified through off-line alpha, beta, gamma, or electron spectroscopy \cite{Voyles2018a,Graves2016}.
+The uncertainty in the deduced cross section depends strongly on the accurate characterization of the target material (which is often challenging to produce), the spectroscopic assaying techniques used and precise determination of the incident particle flux.
+Access to well-characterized nuclear data can be useful in reducing the first two sources of uncertainty.
 
-The flux is typically determined using a well-known monitor reaction on a co-irradiated foil that leads to the production of an easily quantified long-lived residual nucleus.
-However, for both charged-particle and neutron-induced reactions, there relatively few monitor reactions that can be applied in the low to intermediate energy regimes of 30-70 MeV.
-The situation is worse above 70 MeV monitor reactions where values free from the potential influence of secondary neutron contributions are even harder to come by.
-Knowledge of these cross sections as a function of the incident particle energy is central to the isotope production, with recent efforts focused on developing the 93Nb(p,4n)90Mo (t$_{1/2}$= 5.56(9) hours) as a monitor reaction \cite{Voy18b, Kim18}.
+The flux is typically determined using a well-characterized monitor reaction on a co-irradiated foil that leads to the production of an easily quantified, long-lived residual nucleus.
+However, for both charged-particle and neutron-induced reactions, there relatively few monitor reactions that can be applied in the low- to intermediate-energy regimes of 30--70 MeV.
+The situation is worse above 70 MeV, where monitor reactions  free from the potential influence of secondary neutron contributions are even harder to come by.
+Knowledge of these cross sections as a function of the incident particle energy is essential to  isotope production, with recent efforts focused on developing  \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} ($t_{1/2}$= 5.56(9) hours) as a monitor reaction reaction suitable for use at regional isotope production facilities \cite{Voyles2018a, Kim2018}.
 
@@
     \centering
-%     \subfloat{
+    \begin{minipage}{0.5\textwidth}
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{u235.png}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         %         \refstepcounter{subfigure}
-%          \label{fig:before_minimization}
-   \hspace{-5pt}%
-%      \subfloat{
+        \includegraphics[width=0.97\textwidth]{u235.png} % first figure itself
+%         \caption{first figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.5\textwidth}
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=0.5\textwidth]{}{u238.png}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         %         \refstepcounter{subfigure}
-%          \label{fig:after_minimization}
-   \hspace{-5pt}%\\
+        \includegraphics[width=0.97\textwidth]{u238.png} % second figure itself
+%         \caption{second figure}
+    \end{minipage}
+    \\
     \centering
-%     \subfloat{
+    \begin{minipage}{0.5\textwidth}
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{pu239_1.png}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-         %         \refstepcounter{subfigure}
-%          \label{fig:before_minimization}
-   \hspace{-5pt}%
-%      \subfloat{
+        \includegraphics[width=0.97\textwidth]{pu239_1.png} % first figure itself
+%         \caption{first figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.5\textwidth}
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-        \subfigimg[width=0.5\textwidth]{}{pu239_2.png}{50}
-%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-         %         \refstepcounter{subfigure}
-%          \label{fig:after_minimization}
-   \hspace{-5pt}%
+        \includegraphics[width=0.97\textwidth]{pu239_2.png} % second figure itself
+%         \caption{second figure}
+    \end{minipage}
     \caption{SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
@@
 \end{figure}
+
+% \begin{figure}
+%     \centering
+% %     \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{u235.png}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+%          %         \refstepcounter{subfigure}
+% %          \label{fig:before_minimization}
+%    \hspace{-5pt}%
+% %      \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+%         \subfigimg[width=0.5\textwidth]{}{u238.png}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+%          %         \refstepcounter{subfigure}
+% %          \label{fig:after_minimization}
+%    \hspace{-5pt}%\\
+%        \centering
+% %     \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+%         \hspace{-5pt}\subfigimg[width=0.5\textwidth]{}{pu239_1.png}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+%          %         \refstepcounter{subfigure}
+% %          \label{fig:before_minimization}
+%    \hspace{-5pt}%
+% %      \subfloat{
+%         \centering
+% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
+% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
+%         \subfigimg[width=0.5\textwidth]{}{pu239_2.png}{50}
+% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
+%          %         \refstepcounter{subfigure}
+% %          \label{fig:after_minimization}
+%    \hspace{-5pt}%
+%     \caption{SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
+%      \label{fig:ne_plots}
+% \end{figure}
 

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Added missing references, cleaned up a few things

@@
 % % \usepackage{cancel}
-\usepackage{microtype}
+% \usepackage{microtype}
 % \usepackage{listings}
@@
 \hyphenation{gamma-rays}
+\hyphenation{Spec-tro-met-ers}
 
 % \setcounter{secnumdepth}{4}
+
+% Remove overfull hbox warnings in bibliography
+\usepackage{etoolbox}
+\apptocmd{\sloppy}{\vbadness 10000\relax}{}{}
+% \emergencystretch=1em
+
+\pdfminorversion=7
 
@@
 Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes.
-A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{Wa17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Sch16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.
+A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{War17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Schm16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.
 
@@
 Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process, although they carry large uncertainties and suffer from various ambiguities and limitations.
-These include measurements of scission neutrons \cite{Pe09}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}.
+These include measurements of scission neutrons \cite{Petrov2009}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}.
 Probes of pre-scission physics can provide unique insights into the details of the fission process, and are therefore extremely valuable to fission theory.
@@
 
-\subsection{Improved \ce{^{235,238}U} and \ce{^{239}Pu}(n,n') data for neutron transport}\label{sec:n_transport}
+\subsection{Improved \texorpdfstring{\ce{^{235,238}U}}{235,238U} and \texorpdfstring{\ce{^{239}Pu}}{239Pu}(n,n') data for neutron transport}\label{sec:n_transport}
 
@@
 CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n') on the \enquote{Big 3} Actinides, leading to \enquote{significant differences amongst the evaluations for \ce{^{239}Pu} in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.} \cite{Cha14}.
-The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Bat69, And61}.
+The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Batchelor1969, Andreev1961}.
 The case is similar for \ce{^{235}U} where they note that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}
@@
 The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the \enquote{summation method}.
-Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.
+Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fei82,Sch85,Hah89}.
 The current best predictions for  \ce{^{235}U} and \ce{^{239,241}Pu} are those by Huber \cite{Hub11} using the conversion method, while for \ce{^{238}U} is that by Mueller et al.
@@
 
-The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{20}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
+The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{Fal12}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
 There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
@@
 These experiments would involve a sample of depleted \ce{^{238}U} since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the \ce{^{238}U}(n,f) yields.
-These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{All18} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).
+These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{ayllon2018design} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).
 
-\subsection{Improved (n,x$\gamma$) data for active interrogation}
+\subsection{Improved (n,x\texorpdfstring{$\gamma$}{ gamma}) data for active interrogation}
 
@@
 The interpretation of this data requires detailed knowledge of both the double-differential neutron scattering and gamma-ray production cross sections from fast down to thermal neutron energies.
-The Evaluated Gamma Activation File \cite{Fir14} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.
+The Evaluated Gamma Activation File \cite{Fir15} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.
 At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78}, which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18}, offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.
@@
 
+\emergencystretch=2em
+
 \bibliographystyle{ar-style5}

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Merged in Lee's comments.  Added conclusion section and the title page keywords.

@@
 \begin{keywords}
-\textred{Add keywords here!}  keywords, separated by comma, no full stop, lowercase
+nuclear data,  structure,  reactions, evaluation, fission, medical Isotopes, nuclear energy, nonproliferation, inelastic scattering, level density, radiative strength, $\beta$-decay, reactor antineutrinos
 \end{keywords}
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
+\begin{wrapfigure}{r}{0.39\textwidth}
 \centering
-\includegraphics[width=0.39\textwidth]{pipeline_cropped.pdf}
+\includegraphics[width=0.38\textwidth]{pipeline_cropped.pdf}
 \caption{\label{fig:pipeline}The nuclear data pipeline.}
@@
 Furthermore, many spallation neutron sources have a significant high-energy spectral component that can cause inter-element scattering in a neutron scintillator array rendering precise determination of the scattered neutron energy difficult to  perform.
-However, intense limited-energy neutron sources based on thick-target deuteron breakup \cite{Harrig2018} and forward-fitting techniques developed for use at spallation neutron sources \cite{Kee18} off an opportunity to perform neutron-gamma coincident measurements in the fast fission energy spectrum.
+However, intense limited-energy neutron sources based on thick-target deuteron breakup \cite{Harrig2018} and forward-fitting techniques developed for use at spallation neutron sources \cite{Kee18} offer an opportunity to perform neutron-gamma coincident measurements in the fast fission energy spectrum.
 These techniques could provide valuable data to improve nuclear data evaluations of inelastic scattering, even on targets where fission is an open channel.
@@
 
-The NDIWG process reflects a growing recognition that improved nuclear data is essential to a wide range of human endeavors that transcend the needs of any one societal need or governmental mission.
+The NDIAWG process reflects a growing recognition that improved nuclear data is essential to a wide range of human endeavors that transcend the needs of any one societal need or governmental mission.
 Its goal is the development of a new, multi-agency national plan to address nuclear data needs in a coherent way.
 This plan, which is being developed in partnership with international collaborators at the IAEA and the OECD-NEA represents a new paradigm for collaborative research.
+
+\section{CONCLUSION \texorpdfstring{---}{-} RETAINING AND TRAINING A SKILLED NUCLEAR DATA WORKFORCE}
+
+A robust nuclear data evaluation process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
+However, it takes many years of post-Ph.D.
+experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
+It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
+As more and more of the research in the United States moves over to a project-driven model, it is imperative that sponsors coordinate their efforts to ensure that there is no loss of talent in the field.
+The NDIAWG discussed above is a significant step to help address these issues in a systematic fashion.
+
+Furthermore, nuclear data evaluation is an \emph{aging} field, with the mean age of an evaluator in the US being well-over 50.
+It is essential that the next generation of nuclear data evaluators be recruited and trained while the current set of experienced individuals are still active in the field.
+This is particularly challenging since there is, \emph{per se}, no graduate education program in nuclear data evaluation, and the vast majority of the centers with evaluation expertise are not associated with degree-granting institutions.
+
+Perhaps one of the \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
+This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR/CSISRS library are to be taken seriously, discarded or normalized to newer standards.
+This sort of a \enquote{hybrid} individual would be capable of providing not only good mean values, but also the well-quantified uncertainties (including covariances) that are needed for most applications.
+A concerted effort on the part of both academia and the international research community is needed to ensure that talented early-career individuals with the right combination of interest and inclination be afforded the opportunity to get trained by an \enquote{international village} of evaluators and application subject matter experts.
+
+In closing, it is worth noting that the dramatic increase in computational capabilities over the past several decades allows for the sort of detailed calculations needed to fulfill the promise of many applications, \emph{provided that the correct evaluated data is available}.
+Recent efforts in the US offer the promise of a national nuclear data plan to provide the needed data.
+If these efforts are maintained it could help herald in a world with a new sense of safety from enhanced nonproliferation capabilities, a new source of safe, carbon-neutral energy and a new class of radio-pharmaceuticals to diagnose and treat illness.
+
 % 

### 2018-12-17 nuclear_data_needs/nuclear_data_needs.tex
Broke up sentences to one per line, for easier editing

@@
 WPEC also hosts long-term Expert Groups, and current groups are working on the development of the Generalized Nuclear Database Structure (GNDS) format, to provide a data library interface between nuclear physics and applications more modern than the ENDF-6 format, and the High-Priority Request List which assembles the most important nuclear data requests from applications in a unified format, to stimulate experimentalists and evaluators to provide these data.
-A full list of past and current subgroups of WPEC is available at Ref.
-\cite{WPEC}.
+A full list of past and current subgroups of WPEC is available at Ref. \cite{WPEC}.
 
@@
 Post-scission observables are generally easier to measure, and include the properties of fission fragments and products and of the neutrons and gamma rays they emit.
-Recently, Bertsch et al.
-\cite{Ber15} have suggested a subset of fission data that tend to have relatively small uncertainties and could therefore be used to test and validate fission models.
+ Recently, Bertsch et al. \cite{Ber15} have suggested a subset of fission data that tend to have relatively small uncertainties and could therefore be used to test and validate fission models.
 These data consist of fission barriers, fragment mass distributions, fragment total kinetic energies, spontaneous-fission lifetimes, and fission isomer excitation energies.
@@
 There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
-This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs.
-$\gamma$-ray emission probability in nuclear reactions.
+ This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs. $\gamma$-ray emission probability in nuclear reactions.
  This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
@@
 
+\begin{figure}[b]
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.7\linewidth]{667_before_alt.png}
+
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Difference in the FIER-predicted and observed yield of \ce{^{132}I} as a function of time for a \ce{^{235}U} sample irradiated at the GODIVA critical assembly taken from \cite{Matthews2018}.
+}
+ \label{fig:fier_plot}
+\end{figure}
+
 Given the dependence of the antineutrino signal on both decay and fission product yield data, a series of sensitivity study-guided integral experiments, along the lines of critical assembly integral benchmarks, are needed to validate the underlying nuclear data would provide a strong constraint on the underlying data.
@@
  The first example of its use involving a comparison to the delayed gamma-ray spectrum from a \ce{^{235}U} foil irradiated in the Godiva critical assembly indicated several cases were the underlying fission yields or decay data required improvement.
-
-\textred{We seem to have plenty of space - should we add the FIER plot back in?}
+One example, where the yield of the \ce{^{132}I} needed to be adjusted upward by 0.24$\sigma$, is shown in \autoref{fig:fier_plot}.
 
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-\textred{Lee - we should add some language here referencing Batch's work on this.}
+Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \cite{Bat18}.
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
@@
 There are no cross-section data that represent the effect of the molecular bonds, leading to a computational bias of unknown magnitude in all reactor design calculations.
-The molecular bonds in water vs.
-Polyethylene can lead to a computation bias of 1-2\%$\Delta k$.
+The molecular bonds in water vs. Polyethylene can lead to a computation bias of 1-2\%$\Delta k$.
  In addition, this effect is temperature dependent and is not well studied or understood.
@@
 A robust nuclear data evaluation process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
-However, it takes many years of post-Ph.D.
-experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
+ However, it takes many years of post-Ph.D. experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
  It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
@@
 \section*{DISCLOSURE STATEMENT}
-\textred{If the authors have noting to disclose, the following statement will be used: The authors are not aware of any affiliations, memberships, funding, or financial holdings that
-might be perceived as affecting the objectivity of this review. }
+The authors are not aware of any affiliations, memberships, funding, or financial holdings that
+might be perceived as affecting the objectivity of this review.
 

### 2018-12-17 nuclear_data_needs/nuclear_data_needs.tex
Added new 239pu_nn figure

@@
 %Authors, affiliations address.
-\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^6$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^7$
+\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^6$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 \affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
-\affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^6$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^7$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
+% \affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^5$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^6$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
 
@@
 
+\begin{figure}[b]
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.7\linewidth]{rotated_swings.pdf}
+
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Simulations of criticality $k_{eff}$ for \ce{^{239}Pu} for the fast assembly Jezebel, PMF-1.
+This figure shows that both LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) predict similar $k_{eff}$ values, but do so for very different reasons.
+The changes in criticality are evident when individual cross section channels are substituted between the two evaluations.
+ The shaded region shows the  resulting range of values for $k_{eff}$.}
+ \label{fig:rotated_swings}
+\end{figure}
+
 Elastic and inelastic scattering have a profound effect on neutron populations in any nuclear application by changing the directions and energies of the neutrons in the system.
@@
 
-\begin{figure}
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.8\linewidth]{rotated_swings.pdf}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Simulations of criticality $k_{eff}$ for \ce{^{239}Pu} for the fast assembly Jezebel, PMF-1.
-This figure shows that both LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) predict similar $k_{eff}$ values, but do so for very different reasons.
-The changes in criticality are evident when individual cross section channels are substituted between the two evaluations.
- The shaded region shows the  resulting range of values for $k_{eff}$.}
- \label{fig:rotated_swings}
-\end{figure}
-
 A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: \ce{^{1}H}, \ce{^{16}O}, \ce{^{56}Fe}, \ce{^{235,238}U} and \ce{^{239}Pu} in order to address the issue of compensating errors.
@@
  Experiments were run on all three of the major Actinides: \ce{^{235}U} \cite{You01}, \ce{^{239}Pu} \cite{Ber02} and \ce{^{238}U} \cite{Fot04}.
+ GEANIE produced the first high-resolution partial $\gamma$-ray cross section data on the \enquote{Big 3}.
+This includes one of the first results for \ce{^{239}Pu}(n,n'$\gamma$), shown in \autoref{fig:239pu_nn_cropped}  together with calculations using the CoH reaction modeling code developed by Toshihiko Kawano.
+% It should be noted that the GEANIE data was angle-integrated with respect to the outgoing neutron, limiting its value for neutron transport modeling.
  It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial $\gamma$-ray cross sections.
+
+\begin{figure}[t]
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.6\linewidth]{239pu_nn_cropped.pdf}
+
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{A selection of the \ce{^{239}Pu}(n,n'$\gamma$) partial $\gamma$-ray cross sections from \cite{Ber00} for the two transitions de-exciting the ${^5/_2}^{+}$ level at $E_x=$285.46 keV.}
+ \label{fig:239pu_nn_cropped}
+\end{figure}
 
@@
 Over the past several years, work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including \ce{^{238}U}, \ce{^{239,240,242}Pu} and \ce{^{232}Th} \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
-
 Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter ($\sigma$) of the form:
@@
 
-There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
- This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs. $\gamma$-ray emission probability in nuclear reactions.
- This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
-
 \begin{figure}
@@
 %  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.7\linewidth]{fig3.pdf}
+ \includegraphics[width=0.55\linewidth]{fig3.pdf}
 
@@
 
+There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
+ This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs. $\gamma$-ray emission probability in nuclear reactions.
+ This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
+
 (n,n'$\gamma$) provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
@@
  Similar behavior is seen in the partial cross sections for other off-yrast levels as well.
+
+Information regarding the $J$-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
+ This method has been used in Hg and Au by Chakravarty \cite{PhysRevC.45.1171} and more recently by Sudar in Hg and Pt \cite{PhysRevC.73.034613}.
+ \autoref{fig:fe_isomer_plots} shows this for the case of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) ratio populated via \ce{^{56}Fe}(p,$\alpha$n) measured via stacked-target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
+
+It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
+ This reflects the interdependency between nuclear data over a wide range of applications.
 
@@
 % \end{figure}
-
-Information regarding the $J$-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
- This method has been used in Hg and Au by Chakravarty \cite{PhysRevC.45.1171} and more recently by Sudar in Hg and Pt \cite{PhysRevC.73.034613}.
- \autoref{fig:fe_isomer_plots} shows this for the case of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) ratio populated via \ce{^{56}Fe}(p,$\alpha$n) measured via stacked-target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
-
-It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
- This reflects the interdependency between nuclear data over a wide range of applications.
 

### 2018-12-18 nuclear_data_needs/nuclear_data_needs.tex
Updated a few references and authro affiliations

@@
 \affil{$^3$National Nuclear Data Center, Brookhaven National Laboratory, Upton, NY 11973, USA}
-\affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
+\affil{$^4$Nuclear Data Section, International Atomic Energy Agency, 1400 Vienna, Austria}
 % \affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
 \affil{$^5$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^6$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
+\affil{$^6$Lawrence Livermore National Laboratory L-414, Livermore, CA 94551, USA}}
 
@@
 In the case of nuclear reaction data, the process is markedly different.
- The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the Evaluated Nuclear Data File \cite{Chadwick2011}.
+ The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the Evaluated Nuclear Data File \cite{endf8_0}.
  Most of the effort put into the production of ENDF is provided by applications-oriented users due to its importance to national security, international counter-proliferation and nuclear energy.

### 2018-12-18 nuclear_data_needs/nuclear_data_needs.tex
Pushing Dave's comments

@@
 
+\newcommand{\keff}{k$_{\textrm{eff}}$}
+
 % 
@@
 %Authors, affiliations address.
-\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^6$
+\author{Lee A.
+Bernstein$^{1,2}$, David A.
+Brown$^3$, \\Arjan J.
+Koning$^4$, Bradley T.
+Rearden$^5$,  \\Catherine E.
+Romano$^5$, Alejandro A.
+Sonzogni$^3$, Andrew S.
+Voyles$^{1,2}$, and Walid  Younes$^6$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 Low-energy nuclear science (LENS) \enquote{straddles the fence} between curiosity- and application-driven pursuits.
- On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
+ On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) \textred{DAB: This is very restrictive!} nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
 LENS also plays an important role in nuclear astrophysics, improving models of stellar energy generation and allowing isotopic abundances to be used to inform models of the astrophysical environments where heavy nuclei are formed.
@@
 \subsection{The Nuclear Data Pipeline}
+\label{sec:pipeline}
 
@@
  This process ends with the users and their application, but actually begins with the performance of carefully-designed measurements with well-defined uncertainties.
- Given this, it behooves those funding or performing the original experiment to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
+ Given this,  those funding or performing the original experiment would be wise to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
  For example, if a new result forces changes to data formats (step 2) or processing (step 3) or to application codes (step 4 \& eventual user), this fact should be considered when developing a new activity.
@@
 In the case of nuclear reaction data, the process is markedly different.
- The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the Evaluated Nuclear Data File \cite{endf8_0}.
+ The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the one or more regional libraries such as the recently release of the Evaluated Nuclear Data File (ENDF), ENDF/B-VIII.0 \cite{endf8_0}.
  Most of the effort put into the production of ENDF is provided by applications-oriented users due to its importance to national security, international counter-proliferation and nuclear energy.
@@
  The class of user problems we most rely on are so-called \enquote{integral benchmark} data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
- The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss ($k_{eff}$) is known to several significant figures.
+ The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss (\keff) is known to several significant figures.
  However, there are many other kinds of integral benchmarks used to test neutron interaction data alone, including reaction rate measurements and 14 MeV and fission spectrum transmission experiments, and many more for other forms of nuclear data.
@@
 Much of the work of nuclear data evaluation takes place as a part of international collaborations covered under the Organization of Economic Cooperation and Development's Nuclear Energy Agency (NEA) and the International Atomic Energy Agency (IAEA).
- The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
+ The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear reaction data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
 
@@
 The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{Fal12}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
-  There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
+  There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyv\"{a}skyl\"{a} \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyv\"{a}skyl\"{a} and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
   Also planned are measurements of beta shape factors as well as a new IAEA Coordinated Research Project to evaluate fission yields.
@@
 The conversion method is not fully free of issues, either.
- To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay cross section threshold have not been published.
+ To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay (IBD) cross section threshold have not been published.
    As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
@@
 %  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.7\linewidth]{667_before_alt.png}
+ \includegraphics[width=0.7\linewidth]{667_before_v2.png}
 
@@
     \end{minipage}
-    \caption{SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
+    \caption{SG46 findings on changes in cross sections and prompt fission nubar from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
      \label{fig:ne_plots}
@@
 With few benchmark experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where \ce{^{1}H}, \ce{^{16}O}, \ce{^{235}U}, \ce{^{238}U} and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
- Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
+ Similar to the Chadwick \cite{Cha18} (see \autoref{fig:rotated_swings}) and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
 A swing in $k_{eff}$ of 450 pcm is observed.
@@
 \begin{itemize}
-  \item Improving our knowledge of the \ce{^{238}U}(n,n')cross section.
+  \item Improving our knowledge of the \ce{^{238}U}(n,n')cross section, as discussed in \autoref{sec:n_transport} previously.
   \ce{^{238}U}(n,n') is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \cite{Bat18}.
+Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \textred{\cite{Bat18}}.
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
@@
   \item Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
+\textred{In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.}
 \end{itemize}
@@
 
-A robust nuclear data evaluation process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
+A robust nuclear data process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
  However, it takes many years of post-Ph.D. experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
@@
 Perhaps one of the \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
- This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR/CSISRS library are to be taken seriously, discarded or normalized to newer standards.
+ This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR library are to be taken seriously, discarded or normalized to newer standards.
  This sort of a \enquote{hybrid} individual would be capable of providing not only good mean values, but also the well-quantified uncertainties (including covariances) that are needed for most applications.
@@
 
+This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Security,
+LLC, Lawrence Livermore National Laboratory under Contract \# DE-AC52-07NA27344.
+
 \textred{EVERYONE - Please provide me snippets of any other Acknowledgements you want included!}

### 2018-12-19 nuclear_data_needs/nuclear_data_needs.tex
Added reference for Batch's forthcoming Cl(n,p) Phys Rev C

@@
 
-\begin{figure}[b]
+\begin{figure}
  \centering
@@
 
-\begin{figure}[t]
+\begin{figure}
  \centering
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \textred{\cite{Bat18}}.
+Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \cite{Bat18}.
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.

### 2018-12-26 nuclear_data_needs/nuclear_data_needs.tex
Merged in Lee's polishing changes and Arjan's typo corrections.

@@
 Sonzogni$^3$, Andrew S.
-Voyles$^{1,2}$, and Walid  Younes$^6$
+Voyles$^{2}$, and Walid  Younes$^6$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 \affil{$^4$Nuclear Data Section, International Atomic Energy Agency, 1400 Vienna, Austria}
-% \affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
 \affil{$^5$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
@@
 A well-established knowledge of nuclear phenomena including fission, reaction cross sections, and structure/decay properties, is critical for applications ranging from the design of new reactors, to non-proliferation, to the production of radioisotopes for the diagnosis and treatment of illness.
-However, the lack of a well-quantified, predictive theoretical capability means that most nuclear observables must be measured directly in order to \enquote{calibrate} empirical models, which, in turn, provide the data needed for these applications.
+However, the lack of a well-quantified, predictive theoretical capability means that most nuclear observables must be measured directly and used to \enquote{calibrate} empirical models, which in turn, provide the data needed for these applications.
  In many cases there is either a lack of the data needed to guide the models, or the results of the different measurements are discrepant.
  This has led to the development of evaluation methodologies to provide recommended values and uncertainties.
- In this article we present the nuclear data evaluation process and the international community that carries it out.
+ In this article  the nuclear data evaluation process and the international community that carries it out are presented.
  We then discuss new measurements and improved theory and/or modeling needed to address future challenges in applied nuclear science. 
@@
 Low-energy nuclear science (LENS) \enquote{straddles the fence} between curiosity- and application-driven pursuits.
- On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) \textred{DAB: This is very restrictive!} nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
+ On the curiosity-driven side, low-energy nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
 LENS also plays an important role in nuclear astrophysics, improving models of stellar energy generation and allowing isotopic abundances to be used to inform models of the astrophysical environments where heavy nuclei are formed.
@@
  The evaluation processes range from close adherence to experimental results in the case of low energy nuclear structure and decay data, to experiment-guided modeling in the case of nuclear reactions.
-This work is carried out by subject matter experts who usually come from the field utilizing the data who spend many years studying under experienced evaluators in order to develop the highly-specialized skills they need.
+This work is carried out by subject matter experts who usually come from the field utilizing the data.
+These individuals spend many years studying under experienced evaluators in order to develop the highly-specialized skills required for the evaluation process.
 
-This manuscript will start with a description of the nuclear data evaluation process, and the organizations organization that carry it out.
- It will then describe ways to improve the modeling of (n,x) reactions on nuclides important for applications.
- Following this will be a discussion of needs for specific applications including national security/non-proliferation, medical isotope production and nuclear energy.
- It will end with a discussion of the future of nuclear data featuring  a new, Nuclear Data Interagency Working Group that that is formulating a national nuclear data plan to address high-priority needs for applied nuclear science and technology.
+This manuscript starts with a description of the nuclear data evaluation process, including the domestic and international organizations that help organize evaluation efforts.
+It  then describes ways to improve the modeling of (n,x) reactions on nuclides important for applications.
+This includes providing a better understanding of fission, improving the modeling of inelastic neutron scattering and better determining the properties of the highly-excited continuum states which determine which reactions dominate at a given excitation energy.
+ Following this is a discussion of needs for specific applications including national security/non-proliferation, medical isotope production and nuclear energy.
+ It ends by introducing a recently-formed Nuclear Data Interagency Working Group that's formulating a national plan to address high-priority needs, and by presenting ideas about how to change the way that we educate evaluators to ensure that a well-trained workforce is available to meet these important needs.
 
@@
 
-The first step in the Pipeline is compilation and it begins with potentially the most important database: Nuclear Science References (NSR) \cite{NSR}.
- NSR contains references to published works from major LENS journals as well as internal reports from labs throughout the world and serves as the start point for the data evaluation process.
-Descriptive keywords are assigned to these articles by individuals with LENS backgrounds, enabling the use of this information in later portions of the evaluation process.
-
 \begin{wrapfigure}{r}{0.39\textwidth}
@@
 \end{wrapfigure}
+
+The first step in the Pipeline is compilation and it begins with potentially the most important database: Nuclear Science References (NSR) \cite{NSR}.
+ NSR contains references to published works from major LENS journals as well as internal reports from labs throughout the world and serves as the start point for the data evaluation process.
+Descriptive keywords are assigned to these articles by individuals with LENS backgrounds, enabling the use of this information in later portions of the evaluation process.
 
@@
  However, during XUNDL compilation basic consistency checks are performed and any internal inconsistencies are pointed out to the author to allow them be reconciled in the database.
- XUNDL is used by both nuclear structure evaluators to aid in their work and by nuclear structure researchers as a quick way to get access to data from current publications in order to guide their own research.
+ XUNDL is used by both nuclear structure evaluators to aid in their work, and by nuclear structure researchers as a quick way to get access to data from current publications in order to guide their own research.
 
@@
 The next step in the process is evaluation itself.
- In the case of nuclear structure data this involves reconciling multiple types data sets (e.g., prompt gamma and particle spectra, decay data etc.) and deriving a recommended set of adopted values.
+ In the case of nuclear structure data this involves reconciling multiple data set types (e.g., prompt gamma and particle spectra, decay data etc.) and deriving a recommended set of adopted values.
  This data forms the basis of the Evaluated Nuclear Structure Data File (ENSDF) \cite{tepel1984ensdf}.
@@
 
-While ENSDF and ENDF contain a vast quantity of nuclear data, there are significant amounts of nuclear data that are either not contained in them because they \enquote{fall between} nuclear structure and nuclear reactions, or they are present in a format that is not well-suited to their use in applications.
- Examples of this include the recently updated Atlas of Neutron Resonances \cite{Mug18} which contains neutron capture resonance widths, centroids and cross sections and the Evaluated Gamma Activation File of (EGAF) capture gamma-rays \cite{Fir15} and the Atlas of Inelastic Scattering of Reactor Fast Neutron \cite{Hur18}.
+While ENSDF and ENDF contain a vast quantity of nuclear data, there are significant amounts of data that are either not contained in them because they \enquote{fall between} nuclear structure and nuclear reactions, or they are present in a format that is not well-suited to their use in applications.
+ Examples of this include the recently updated Atlas of Neutron Resonances \cite{Mug18} which contains neutron capture resonance widths, centroids and cross sections and the Evaluated Gamma Activation File of (EGAF) capture gamma-rays \cite{Fir15} and the Atlas of Inelastic Scattering of Reactor Fast Neutrons \cite{Hur18}.
  Another very important nuclear data resource for applications is the Reference Input Parameter Library (RIPL) \cite{Capote2009} which contains both discrete (distilled from ENSDF) and continuous (Nuclear Level Densities and Gamma-strength function) nuclear structure data needed for accurate reaction modeling.
 
-Evaluations in hand, we must now process the data into a form suitable for use in a particular application.
+Evaluations in hand, the data has to be processed into a form suitable for use in a particular application.
  This is a surprisingly non-trivial part of the process, requiring a deep knowledge of the physics used in the evaluation process, the formatting limitations of intermediate data formats, and the capabilities of downstream codes that will use the nuclear data.
@@
 The final step in the Pipeline is validation.
- In this step, we use user codes and user-defined problems to validate that the data performs as expected.
- The class of user problems we most rely on are so-called \enquote{integral benchmark} data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
+ In this step, user codes and user-defined problems are used to validate that the data performs as expected.
+ The class of user problems most relied on are so-called \enquote{integral benchmark} data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
  The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss (\keff) is known to several significant figures.
@@
  Subgroups typically operate on a 3-5 year time frame.
-Recent successful examples of WPEC subgroups, with specific relevance to the US, are large-scale horizontal efforts like CIELO (SG40), on worldwide nuclear data evaluation for the most important fission energy related materials.
-The CIELO initiative has, for example, led to new ENDF/B-VIII.0 evaluations for \ce{^{235,238}U}, \ce{^{56}Fe} and \ce{^{16}O} among others, and the Generalized Nuclear Database Structure (GNDS) format (SG38) \cite{SG38}, or more specific efforts like covariance adjustment for improvement of nuclear data files (SG39) \cite{SG39}.
+A recent successful example of a WPEC subgroup, with specific relevance to the US, includes the large-scale horizontal CIELO effort (SG40) on worldwide nuclear data evaluation for the most important fission energy related materials.
+The CIELO initiative has led to new ENDF/B-VIII.0 evaluations for \ce{^{235,238}U}, \ce{^{56}Fe} and \ce{^{16}O} among others.
+Other successful subgroups include one centered on developing a new Generalized Nuclear Database Structure (GNDS) format (SG38) \cite{SG38}, and one focused  on covariance adjustment for improvement of nuclear data files (SG39) \cite{SG39}.
 
-WPEC also hosts long-term Expert Groups, and current groups are working on the development of the Generalized Nuclear Database Structure (GNDS) format, to provide a data library interface between nuclear physics and applications more modern than the ENDF-6 format, and the High-Priority Request List which assembles the most important nuclear data requests from applications in a unified format, to stimulate experimentalists and evaluators to provide these data.
-A full list of past and current subgroups of WPEC is available at Ref. \cite{WPEC}.
+WPEC also hosts long-term Expert Groups.
+Current groups are working on the development of the Generalized Nuclear Database Structure (GNDS) format mentioned above that will provide a data library interface between nuclear physics and applications more modern than the ENDF-6 format, and the High-Priority Request List which assembles the most important nuclear data requests from applications in a unified format, to stimulate experimentalists and evaluators to provide these data.
+A full list of past and current subgroups of WPEC is available at Ref.
+\cite{WPEC}.
 
-The International Atomic Energy Agency (IAEA) covers the interests of its 170 member states.
-The main task of the IAEA Nuclear Data Section is to provide fundamental nuclear data bases for basic and applied use, with data originating from experiments and theoretical simulations and covering both nuclear structure and nuclear reaction data.
+A key player in nuclear data evaluation is the the International Atomic Energy Agency (IAEA), which covers the interests of its 170 member states.
+The main task of the IAEA Nuclear Data Section is to provide fundamental nuclear databases for basic and applied use, with data originating from experiments and theoretical simulations covering both nuclear structure and nuclear reaction data.
  An important collaboration coordinated by the IAEA is the Nuclear Reaction Data Center Network, which is responsible for keeping the EXFOR database of experimental nuclear reaction data up to date.
-NNDC is responsible for the US input to the database.
+The NNDC is responsible for the US input to EXFOR.
 
 In addition, the IAEA organizes Coordinated Research Projects (CRP) and technical meetings as instruments to align international nuclear data efforts towards the production of validated databases ready for applied use.
- Examples of recent and current CRP's include a 2018 venture centered on nuclear data for primary radiation damage has been completed, an ongoing effort to improve nuclear model parameters for fission reaction calculations by modern nuclear model codes such as EMPIRE \cite{Herman2007}, CCONE \cite{Iwa16}, COH3 \cite{KAWANO2010} and TALYS \cite{Koning2012} is ongoing, and an effort to create a first-ever evaluated database of radiative strength.
+ Examples of recent and current CRP's include a 2018 venture centered on nuclear data for primary radiation damage, which has been completed, an ongoing effort to improve nuclear model parameters for fission reaction calculations by modern nuclear model codes such as EMPIRE \cite{Herman2007}, CCONE \cite{Iwa16}, COH3 \cite{KAWANO2010} and TALYS \cite{Koning2012}, and an effort to create a first-ever evaluated database of radiative strength.
  In 2019, a CRP on fission yields will start which aims to produce updated fission yield libraries for the major actinides to respond to requests from reactor technology, safeguards and non-proliferation.
@@
 Eventually, one could envision a comprehensive model that accurately follows the entire fission process from the formation of the parent nucleus to the last decays of the final product nuclei within a single internally consistent theoretical framework.
-Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes.
+Such a model is not yet feasible, so different physics models are used to treat pre- and post-scission processes.
 A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{War17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Schm16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.
@@
 The division between pre- and post-scission physics in modeling efforts suggests a corresponding division in nuclear data needs to improve our understanding of the fission process.
-Post-scission observables are generally easier to measure, and include the properties of fission fragments and products and of the neutrons and gamma rays they emit.
+Post-scission observables are generally easier to measure, and include the properties of fission fragments and the neutrons and gamma rays they emit.
  Recently, Bertsch et al. \cite{Ber15} have suggested a subset of fission data that tend to have relatively small uncertainties and could therefore be used to test and validate fission models.
@@
 Pre-scission models can provide input to post-scission models wherever the data are lacking, and post-scission models can be used to improve pre-scission calculations using a wealth of available experimental data.
+
 The ultimate goal for theorists, a comprehensive description of fission starting from protons, neutrons, and their interactions that provides accurate values for all fission data of interest, remains elusive.
 Many questions about the fission process remain open, such as: how the initial partition of energy between kinetic and internal excitation occurs, what the relevant collective and single-particle degrees of freedom are near scission, and how they evolve and couple throughout the process?
-Lastly, how can we best quantify uncertainties (both epistemic and aleatory) in fission calculations?
+Lastly, a compelling questions that remains is how to best quantify uncertainties (both epistemic and aleatory) in fission calculations.
+Improved experiments and theoretical models are needed to address all of these questions, and to provide the deeper understanding of the fission process needed for most applications.
 
@@
 
-\begin{figure}
+\begin{figure}[b]
  \centering
@@
  However, improvements in neutron scattering data have been hampered by the fact that they do not produce easily measured signals like fission, or a radiochemical observable like neutron capture.
- The result has been significant disagreements between different reaction evaluations.
+ This has resulted in significant disagreements between different reaction evaluations.
  These disagreements manifest themselves as compensating errors that are resistant to the validation process.
@@
  Models of Jezebel using LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) reproduce a unity value of $k_{eff}$ to better than 1 part in 104.
- However, when the authors substituted one nuclear quantity one quantity at a time between the two databases, the value of $k_{eff}$ varied considerably.
+ However, when the authors substituted one nuclear quantity at a time between the two databases, the value of $k_{eff}$ varied considerably.
  The greatest changes came from changing the elastic and inelastic scattering cross sections, which led to changes in the $k_{eff}$ of -500 pcm and +704 pcm, respectively.
@@
 
-A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: \ce{^{1}H}, \ce{^{16}O}, \ce{^{56}Fe}, \ce{^{235,238}U} and \ce{^{239}Pu} in order to address the issue of compensating errors.
- Recently, this list has been expanded to include \ce{^{14,15}N}, \ce{^{9}Be}, \ce{^{23}Na}, \ce{^{59}Co}, \ce{^{58}Ni}, \ce{^{238-242}Pu}.
+The Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program referred to above \cite{Cha18a} was started to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: \ce{^{1}H}, \ce{^{16}O}, \ce{^{56}Fe}, \ce{^{235,238}U} and \ce{^{239}Pu} in order to address the issue of compensating errors.
+ Recently, this list has been expanded by the IAEA, via CIELO's follow-up, the International Nuclear Data Evaluation Network (INDEN), to include \ce{^{14,15}N}, \ce{^{9}Be}, \ce{^{23}Na}, \ce{^{59}Co}, \ce{^{58}Ni}, \ce{^{238-242}Pu}.
 
@@
  The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Batchelor1969, Andreev1961}.
- The case is similar for \ce{^{235}U} where they note that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}
+ The case is similar for \ce{^{235}U} where it is noted that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}
 
@@
 
-\begin{figure}
+\begin{figure}[t]
  \centering
@@
  Unfortunately, neutron beams usually have quite low intensity, with a fluence in the fast (1--10 MeV) region between $10^3$ and $10^7$ n/s/cm$^2$ at the target location.
- Furthermore, many spallation neutron sources have a significant high-energy spectral component that can cause inter-element scattering in a neutron scintillator array rendering precise determination of the scattered neutron energy difficult to  perform.
+ Furthermore, many spallation neutron sources have a significant high-energy spectral component that can cause inter-element scattering in a neutron scintillator array, rendering precise determination of the scattered neutron energy difficult to  perform.
 However, intense limited-energy neutron sources based on thick-target deuteron breakup \cite{Harrig2018} and forward-fitting techniques developed for use at spallation neutron sources \cite{Kee18} offer an opportunity to perform neutron-gamma coincident measurements in the fast fission energy spectrum.
@@
 \subsection{Improved treatment of continuum nuclear data properties}
+\label{sec:LD_RSF}
 
@@
  % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Ratio of the \ce{^{238}U}(n,n') cross section to the state calculated using TALYS for two different sets of input parameters as a function of incident neutron energy.
+ \caption{Ratio of the \ce{^{238}U}(n,n') cross sections for the first two 2$^{+}$ levels calculated using TALYS for two different sets of input parameters as a function of incident neutron energy.
 The solid line shows the ratio where spin cutoff has been scaled to $\pm$25\% of its default value.
@@
 
-(n,n'$\gamma$) provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
-\autoref{fig:oslo_ld_plot} shows the ratio of the partial cross section for the population of the  level in \ce{^{238}U}(n,n') as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
+In an interesting example of how the interconnectedness of nuclear data , it should be noted that (n,n'$\gamma$) provides a useful tool for studying the spin cut-off parameter since it proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
+\autoref{fig:oslo_ld_plot} shows the ratio of the partial cross section for the population of the first two 2$^{+}$ levels in \ce{^{238}U}(n,n') as a function of incident neutron energy calculated using the TALYS reaction code for two different choices of spin cut-off.
  The solid line shows the case where a constant temperature level density is assumed and the spin cut-off parameter was varied from 75\% to 125\% of its \enquote{normal} value given by \autoref{eqn:spin_cutoff} above.
@@
 It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
- This reflects the interdependency between nuclear data over a wide range of applications.
+ This  synergy between efforts from many applications argues for continued coordination of nuclear data activities regardless of the program they are supporting.
 
@@
 
-% \begin{figure}
-%     \centering
-% %     \subfloat{
-% %         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \hspace{-5pt}
-%         \includegraphics[width=0.3\textwidth]{isomer_curves.pdf} \includegraphics[width=0.3\textwidth]{ldmodels.pdf}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
-%          %         \refstepcounter{subfigure}
-% %          \label{fig:before_minimization}
-% %    \hspace{-5pt}%
-% %      \subfloat{
-% %         \centering
-% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-% %         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
-% %         \includegraphics[width=0.3\textwidth]{ldmodels.pdf}
-% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
-%          %         \refstepcounter{subfigure}
-% %          \label{fig:after_minimization}
-% %    \hspace{-5pt}%
-%     \caption{Predictions of the production of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) isomer-to-ground state ratio as a function of energy for the Gilbert and Cameron level density (left) and using the 6 level density models available in TALYS (right).
-}
-%      \label{fig:fe_isomer_plots}
-% \end{figure}
-
 \section{NATIONAL SECURITY AND NON-PROLIFERATION}
@@
 
-One canonical example of a non-proliferation activity where improvements in multiple cross-cutting areas of nuclear data are needed is the interpretation of the anti-neutrino spectrum from the prompt decay of fission fragments in the core of a nuclear reactor.
+One canonical example of a non-proliferation activity where improvements in multiple areas of nuclear data are needed is the interpretation of the anti-neutrino spectrum from the prompt decay of fission fragments in the core of a nuclear reactor.
 Nuclear reactors are prolific sources of electron antineutrinos, producing about $10^{21}$ antineutrinos per second for a typical power reactor.
@@
 
-The summation method has been recently applied in two different situations.
-  First, it has been shown that the Daya Bay fuel evolution data \cite{An17} can be explained by summation calculations including an anomaly of about 4\% \cite{Hay18}.
-  Second, a novel method to analyze the Daya Bay spectrum revealed the signature of 4 individual fission products, while the same method applied to the electron spectra revealed two additional fission products \cite{Son18}.
-
-The conversion method is not fully free of issues, either.
- To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay (IBD) cross section threshold have not been published.
-   As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
-    A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6\%/MeV could explain the anomaly.
-
 \begin{figure}[b]
@@
 \end{figure}
+
+The summation method has been recently applied in two different situations.
+  First, it has been shown that the Daya Bay fuel evolution data \cite{An17} can be explained by summation calculations including an anomaly of about 4\% \cite{Hay18}.
+  Second, a novel method to analyze the Daya Bay spectrum revealed the signature of 4 individual fission products, while the same method applied to the electron spectra revealed two additional fission products \cite{Son18}.
+
+The conversion method is not fully free of issues, either.
+ To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay (IBD) cross section threshold have not been published.
+   As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
+    A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6\%/MeV could explain the anomaly.
 
@@
  The data from these measurements could then be used to guide physics-based reaction model, such as the COH, TALYS or EMPIRE to ensure that the total gamma-ray production cross section is consistent with the total capture and scattering cross sections themselves.
+This effort would also dovetail nicely with measurements to improve data for inelastic scattering and continuum level properties mentioned in sections \autoref{sec:n_transport} and \autoref{sec:LD_RSF} above.
 
@@
  There have been numerous papers produced over the past 5 years detailing some of the nuclear data needs associated with producing radionuclides for applications.
-For a comprehensive listing of nuclear data needs associated with radionuclides we refer the reader to the summary whitepaper from the Nuclear Data Needs and Capabilities for Applications Workshop held in Berkeley in 2015 \cite{bernstein2015nuclear}, particularly the reactions and isotopes listed in Appendix B.
+For a comprehensive listing of nuclear data needs associated with radionuclides we refer the reader to the summary whitepaper from the Nuclear Data Needs and Capabilities for Applications Workshop held in Berkeley in 2015 \cite{bernstein2015nuclear}, particularly the reactions and isotopes listed in Appendix B of the workshop whitepaper.
  Additional guidance regarding nuclear data needs for medical isotopes can be found in a recent series of IAEA studies \cite{Iae675,Iae596,Iae591} as well as an exhaustive paper from Qaim et al.
@@
 These include \ce{^{18}F} ($t_{1/2}$ = 109.771(20) min), which is produced locally via the \ce{^{18}O}(p,n) reaction, \ce{^{82}Rb} ($t_{1/2}$ = 1.2575(2) min), which is used in cardiac imaging, and \ce{^{68}Ga}  ($t_{1/2}$ = 67.71(8) min), which is used in the detection of a wide range of tumors.
- The short half-lives of \ce{^{82}Rb} and \ce{^{68}Ga} necessitate that they be extracted from a longer-lived radioactive parent nuclide generator whose longer half-lives of 270.93(13) and 25.35(3) days, respectively, allow them to be produced at regional facilities and distributed to medical facilities throughout the world.
+ The short half-lives of  \ce{^{68}Ga} and \ce{^{82}Rb} necessitate that they be extracted from a longer-lived radioactive parent nuclide generator whose longer half-lives of 270.93(13) and 25.35(3) days for \ce{^{68}Ge} and \ce{^{82}Sr}, respectively, allow them to be produced at regional facilities and distributed to medical facilities throughout the world.
 
@@
 
-A particularly promising  nuclear medical treatment modality involves coupling a pair of chemically similar radioisotopes including of a therapeutic nuclide capable of delivering a highly localized radiation dose and a chemically-identical isotope that emits a positron for PET or a gamma suitable for single photon emission computed tomography (SPECT) imaging.
+A highly promising  nuclear medical treatment modality involves coupling a pair of chemically similar radioisotopes including of a therapeutic nuclide capable of delivering a highly localized radiation dose and a chemically-identical isotope that emits a positron for PET or a gamma suitable for single photon emission computed tomography (SPECT) imaging.
 Examples of these \enquote{theranostic pairs} include \ce{^{188}Pt} or \ce{^{191}Pt} for use in imaging, together with \ce{^{193m}Pt}, \ce{^{195m}Pt}, and \ce{^{197}Pt}, which all have  therapeutic potential.
@@
 The flux is typically determined using a well-characterized monitor reaction on a co-irradiated foil that leads to the production of an easily quantified, long-lived residual nucleus.
-However, for both charged-particle and neutron-induced reactions, there relatively few monitor reactions that can be applied in the low- to intermediate-energy regimes of 30--70 MeV.
+However, for both charged-particle and neutron-induced reactions, there are relatively few monitor reactions that can be applied in the low- to intermediate-energy regimes of 30--70 MeV.
  The situation is worse above 70 MeV, where monitor reactions  free from the potential influence of secondary neutron contributions are even harder to come by.
@@
 
-Reliable modeling and simulation predictions of nuclear energy systems is essential to the design, licensing, and operation of nuclear power stations, as well as the fuel cycle facilities for enrichment and material processing, fuel fabrication, transportation and storage.
+Reliable modeling and simulations of nuclear energy systems are essential to the design, licensing, and operation of nuclear power stations, as well as the fuel cycle facilities for enrichment and material processing, fuel fabrication, transportation and storage.
 Additional predictive calculations are required for spent fuel characterization for storage, transportation and disposal as well as hardware activation and radiation shielding and personnel protection.
@@
 
-One artifact of the nuclear data tuning process is a reduction in confidence due to compensating errors.
+One artifact of the nuclear data tuning process is the reduction in confidence due to compensating errors referred to in section \autoref{sec:n_transport} above.
 Where fission and capture reactions are modified to ensure that the integral value of $k_{eff}$ is maintained, little confidence remains in the independent use of the fission cross section itself, which is essential to the prediction of reactor power distributions.
@@
 
-Many nuclear data needs have been identified that are important for design and operating analysis for these advanced systems including:
+Many specific nuclear data needs have been identified that are important for design and operating analysis for these advanced systems including:
 \begin{itemize}
@@
   \item Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
-\textred{In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.}
+In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.
 \end{itemize}
@@
 They advocate for improved performance for their own applications, but because nuclear energy interests are not well represented at the review meetings, the impact of updates to nuclear data and associated uncertainty information on nuclear energy applications is often overlooked.
+A focus on data needed for modeling nuclear energy systems would lend confidence and support to the development of new reactors, providing a desperately-needed low-carbon energy source for society.
 
@@
   \item expanded covariance data, 
-  \item inelastic scatter on \ce{^{235}U}, \ce{^{238}U} and 239Pu, 
+  \item inelastic scattering on \ce{^{235}U}, \ce{^{238}U} and 239Pu, 
   \item gamma emission data, 
@@
  However, it takes many years of post-Ph.D. experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
- It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
+ It is therefore critical for the many programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
  As more and more of the research in the United States moves over to a project-driven model, it is imperative that sponsors coordinate their efforts to ensure that there is no loss of talent in the field.
@@
 
-Perhaps one of the \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
+Perhaps one of the most \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
  This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR library are to be taken seriously, discarded or normalized to newer standards.
@@
 In closing, it is worth noting that the dramatic increase in computational capabilities over the past several decades allows for the sort of detailed calculations needed to fulfill the promise of many applications, \emph{provided that the correct evaluated data is available}.
+This would also open the door for application of machine-learning techniques for the evaluation of both nuclear structure and reaction data.
   Recent efforts in the US offer the promise of a national nuclear data plan to provide the needed data.
@@
 \section*{ACKNOWLEDGMENTS}
-Work at Brookhaven National Laboratory was sponsored by the Office of Nuclear Physics, Office of Science of the U.S.
-Department of Energy under Contract \# DE-AC02-98CH10886 with Brookhaven Science Associates, LLC.
 
-The authors acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics.
+This manuscript was written by staff from several laboratories working under the auspices of the US Department of Energy at Lawrence Berkeley National Laboratory under Contract DE-AC02-05CH11231, Oak Ridge National Laboratory under Contract DE-AC0500OR22725, Lawrence Livermore National Laboratory under Contract DE- AC52-07NA27344 and Brookhaven National Laboratory under Contract DE-AC02-98CH10886.
 
-Work at Lawrence Berkeley National Laboratory has been carried out  under the auspices of the U.S.
-Department of Energy by  Lawrence Berkeley National Laboratory and the U.S.
-Nuclear Data Program under contract \# DE-AC02-05CH11231.
-This work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
+A portion of this work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
 
-This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Security,
-LLC, Lawrence Livermore National Laboratory under Contract \# DE-AC52-07NA27344.
-
-\textred{EVERYONE - Please provide me snippets of any other Acknowledgements you want included!}
+Lastly, we would like to thank Frank \enquote{Ted} Barnes, Timothy Hallman, and Donald Hornback in driving the establishment of the Nuclear Data Interagency Working Group (NDIAWG), which is helping promote awareness of the importance of nuclear data for applications and leading the effort to develop a national nuclear data plan in the US.
 

### 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs-121618-v1.tex
Adding old draft versions of review article

--- 2018-12-19 nuclear_data_needs/nuclear_data_needs.tex
@@
 
-\newcommand{\keff}{k$_{\textrm{eff}}$}
-
 % 
@@
 %Authors, affiliations address.
-\author{Lee A.
-Bernstein$^{1,2}$, David A.
-Brown$^3$, \\Arjan J.
-Koning$^4$, Bradley T.
-Rearden$^5$,  \\Catherine E.
-Romano$^5$, Alejandro A.
-Sonzogni$^3$, Andrew S.
-Voyles$^{1,2}$, and Walid  Younes$^6$
+\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^6$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^7$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 \affil{$^3$National Nuclear Data Center, Brookhaven National Laboratory, Upton, NY 11973, USA}
-\affil{$^4$Nuclear Data Section, International Atomic Energy Agency, 1400 Vienna, Austria}
-% \affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^5$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^6$Lawrence Livermore National Laboratory L-414, Livermore, CA 94551, USA}}
+\affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
+\affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^6$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^7$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
 
@@
 Low-energy nuclear science (LENS) \enquote{straddles the fence} between curiosity- and application-driven pursuits.
- On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) \textred{DAB: This is very restrictive!} nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
+On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
 LENS also plays an important role in nuclear astrophysics, improving models of stellar energy generation and allowing isotopic abundances to be used to inform models of the astrophysical environments where heavy nuclei are formed.
@@
 \subsection{The Nuclear Data Pipeline}
-\label{sec:pipeline}
 
@@
 This process ends with the users and their application, but actually begins with the performance of carefully-designed measurements with well-defined uncertainties.
- Given this,  those funding or performing the original experiment would be wise to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
+Given this, it behooves those funding or performing the original experiment to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
 For example, if a new result forces changes to data formats (step 2) or processing (step 3) or to application codes (step 4 \& eventual user), this fact should be considered when developing a new activity.
@@
 In the case of nuclear reaction data, the process is markedly different.
- The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the one or more regional libraries such as the recently release of the Evaluated Nuclear Data File (ENDF), ENDF/B-VIII.0 \cite{endf8_0}.
+The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the Evaluated Nuclear Data File \cite{Chadwick2011}.
 Most of the effort put into the production of ENDF is provided by applications-oriented users due to its importance to national security, international counter-proliferation and nuclear energy.
@@
 The class of user problems we most rely on are so-called \enquote{integral benchmark} data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
- The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss (\keff) is known to several significant figures.
+The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss ($k_{eff}$) is known to several significant figures.
 However, there are many other kinds of integral benchmarks used to test neutron interaction data alone, including reaction rate measurements and 14 MeV and fission spectrum transmission experiments, and many more for other forms of nuclear data.
@@
 Much of the work of nuclear data evaluation takes place as a part of international collaborations covered under the Organization of Economic Cooperation and Development's Nuclear Energy Agency (NEA) and the International Atomic Energy Agency (IAEA).
- The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear reaction data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
+The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
 
@@
 WPEC also hosts long-term Expert Groups, and current groups are working on the development of the Generalized Nuclear Database Structure (GNDS) format, to provide a data library interface between nuclear physics and applications more modern than the ENDF-6 format, and the High-Priority Request List which assembles the most important nuclear data requests from applications in a unified format, to stimulate experimentalists and evaluators to provide these data.
-A full list of past and current subgroups of WPEC is available at Ref. \cite{WPEC}.
+A full list of past and current subgroups of WPEC is available at Ref.
+\cite{WPEC}.
 
@@
 Post-scission observables are generally easier to measure, and include the properties of fission fragments and products and of the neutrons and gamma rays they emit.
- Recently, Bertsch et al. \cite{Ber15} have suggested a subset of fission data that tend to have relatively small uncertainties and could therefore be used to test and validate fission models.
+Recently, Bertsch et al.
+\cite{Ber15} have suggested a subset of fission data that tend to have relatively small uncertainties and could therefore be used to test and validate fission models.
 These data consist of fission barriers, fragment mass distributions, fragment total kinetic energies, spontaneous-fission lifetimes, and fission isomer excitation energies.
@@
 
-\begin{figure}
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.7\linewidth]{rotated_swings.pdf}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Simulations of criticality $k_{eff}$ for \ce{^{239}Pu} for the fast assembly Jezebel, PMF-1.
-This figure shows that both LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) predict similar $k_{eff}$ values, but do so for very different reasons.
-The changes in criticality are evident when individual cross section channels are substituted between the two evaluations.
- The shaded region shows the  resulting range of values for $k_{eff}$.}
- \label{fig:rotated_swings}
-\end{figure}
-
 Elastic and inelastic scattering have a profound effect on neutron populations in any nuclear application by changing the directions and energies of the neutrons in the system.
@@
 
+\begin{figure}
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.8\linewidth]{rotated_swings.pdf}
+
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Simulations of criticality $k_{eff}$ for \ce{^{239}Pu} for the fast assembly Jezebel, PMF-1.
+This figure shows that both LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) predict similar $k_{eff}$ values, but do so for very different reasons.
+The changes in criticality are evident when individual cross section channels are substituted between the two evaluations.
+The shaded region shows the  resulting range of values for $k_{eff}$.}
+ \label{fig:rotated_swings}
+\end{figure}
+
 A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: \ce{^{1}H}, \ce{^{16}O}, \ce{^{56}Fe}, \ce{^{235,238}U} and \ce{^{239}Pu} in order to address the issue of compensating errors.
@@
 Experiments were run on all three of the major Actinides: \ce{^{235}U} \cite{You01}, \ce{^{239}Pu} \cite{Ber02} and \ce{^{238}U} \cite{Fot04}.
- GEANIE produced the first high-resolution partial $\gamma$-ray cross section data on the \enquote{Big 3}.
-This includes one of the first results for \ce{^{239}Pu}(n,n'$\gamma$), shown in \autoref{fig:239pu_nn_cropped}  together with calculations using the CoH reaction modeling code developed by Toshihiko Kawano.
-% It should be noted that the GEANIE data was angle-integrated with respect to the outgoing neutron, limiting its value for neutron transport modeling.
+This includes one of the first results for $^{239}$Pu(n,n'$\gamma$), shown in \autoref{fig:239pu_nn} \cite{Ber00}.
 It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial $\gamma$-ray cross sections.
@@
 %  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.6\linewidth]{239pu_nn_cropped.pdf}
+ \includegraphics[width=0.6\linewidth]{239pu_nn.pdf}
 
  % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{A selection of the \ce{^{239}Pu}(n,n'$\gamma$) partial $\gamma$-ray cross sections from \cite{Ber00} for the two transitions de-exciting the ${^5/_2}^{+}$ level at $E_x=$285.46 keV.}
- \label{fig:239pu_nn_cropped}
+ \caption{A selection of the $^{239}$Pu(n,n' $\gamma$) partial $\gamma$-ray cross sections from [Ber00] for the two transitions de-exciting the 5/2$_{2}^{+}$ level at $E_x=$285.46 keV.  }
+ \label{fig:239pu_nn}
 \end{figure}
@@
 Over the past several years, work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including \ce{^{238}U}, \ce{^{239,240,242}Pu} and \ce{^{232}Th} \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
+
 Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter ($\sigma$) of the form:
@@
 
+There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
+This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs.
+$\gamma$-ray emission probability in nuclear reactions.
+This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
+
 \begin{figure}
@@
 %  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.55\linewidth]{fig3.pdf}
+ \includegraphics[width=0.7\linewidth]{fig3.pdf}
 
@@
 
-There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
- This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs. $\gamma$-ray emission probability in nuclear reactions.
- This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
-
 (n,n'$\gamma$) provides a useful tool for studying the spin cut-off parameter since the reactions proceed largely through the population of a compound nucleus with a relatively wide range of angular momentum.
@@
 Similar behavior is seen in the partial cross sections for other off-yrast levels as well.
-
-Information regarding the $J$-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
- This method has been used in Hg and Au by Chakravarty \cite{PhysRevC.45.1171} and more recently by Sudar in Hg and Pt \cite{PhysRevC.73.034613}.
- \autoref{fig:fe_isomer_plots} shows this for the case of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) ratio populated via \ce{^{56}Fe}(p,$\alpha$n) measured via stacked-target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
-
-It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
- This reflects the interdependency between nuclear data over a wide range of applications.
 
@@
 
+Information regarding the $J$-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
+This method has been used in Hg and Au by Chakravarty \cite{PhysRevC.45.1171} and more recently by Sudar in Hg and Pt \cite{PhysRevC.73.034613}.
+\autoref{fig:fe_isomer_plots} shows this for the case of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) ratio populated via \ce{^{56}Fe}(p,$\alpha$n) measured via stacked-target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
+
+It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
+This reflects the interdependency between nuclear data over a wide range of applications.
+
 \section{NATIONAL SECURITY AND NON-PROLIFERATION}
@@
 The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{Fal12}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
-  There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyv\"{a}skyl\"{a} \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyv\"{a}skyl\"{a} and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
+There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
 Also planned are measurements of beta shape factors as well as a new IAEA Coordinated Research Project to evaluate fission yields.
@@
 The conversion method is not fully free of issues, either.
- To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay (IBD) cross section threshold have not been published.
+To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay cross section threshold have not been published.
 As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
 A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6\%/MeV could explain the anomaly.
-
-\begin{figure}[b]
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.7\linewidth]{667_before_v2.png}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Difference in the FIER-predicted and observed yield of \ce{^{132}I} as a function of time for a \ce{^{235}U} sample irradiated at the GODIVA critical assembly taken from \cite{Matthews2018}.
-}
- \label{fig:fier_plot}
-\end{figure}
 
@@
 The first example of its use involving a comparison to the delayed gamma-ray spectrum from a \ce{^{235}U} foil irradiated in the Godiva critical assembly indicated several cases were the underlying fission yields or decay data required improvement.
-One example, where the yield of the \ce{^{132}I} needed to be adjusted upward by 0.24$\sigma$, is shown in \autoref{fig:fier_plot}.
+
+\textred{We seem to have plenty of space - should we add the FIER plot back in?}
 
@@
     \end{minipage}
-    \caption{SG46 findings on changes in cross sections and prompt fission nubar from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
+    \caption{SG46 findings on changes in cross sections from ENDF/B-VII.1 to ENDF/B-VIII.0 of key nuclides. }
      \label{fig:ne_plots}
@@
 With few benchmark experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where \ce{^{1}H}, \ce{^{16}O}, \ce{^{235}U}, \ce{^{238}U} and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
- Similar to the Chadwick \cite{Cha18} (see \autoref{fig:rotated_swings}) and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
+Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
 A swing in $k_{eff}$ of 450 pcm is observed.
@@
 \begin{itemize}
-  \item Improving our knowledge of the \ce{^{238}U}(n,n')cross section, as discussed in \autoref{sec:n_transport} previously.
+  \item Improving our knowledge of the \ce{^{238}U}(n,n')cross section.
 \ce{^{238}U}(n,n') is a limiting factor in the design of fast spectrum reactors such as those with metallic cores or chloride salts.
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \cite{Bat18}.
+Recent results from activation using a DD-neutron source \cite{voy18a} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n (MeV) < 2.7$ \cite{Bat18}.
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
@@
 There are no cross-section data that represent the effect of the molecular bonds, leading to a computational bias of unknown magnitude in all reactor design calculations.
-The molecular bonds in water vs. Polyethylene can lead to a computation bias of 1-2\%$\Delta k$.
+The molecular bonds in water vs.
+Polyethylene can lead to a computation bias of 1-2\%$\Delta k$.
 In addition, this effect is temperature dependent and is not well studied or understood.
@@
   \item Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
-\textred{In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.}
 \end{itemize}
@@
 
-A robust nuclear data process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
- However, it takes many years of post-Ph.D. experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
+A robust nuclear data evaluation process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
+However, it takes many years of post-Ph.D.
+experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
 It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
@@
 Perhaps one of the \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
- This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR library are to be taken seriously, discarded or normalized to newer standards.
+This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR/CSISRS library are to be taken seriously, discarded or normalized to newer standards.
 This sort of a \enquote{hybrid} individual would be capable of providing not only good mean values, but also the well-quantified uncertainties (including covariances) that are needed for most applications.
@@
 \section*{DISCLOSURE STATEMENT}
-The authors are not aware of any affiliations, memberships, funding, or financial holdings that
-might be perceived as affecting the objectivity of this review.
+\textred{IThe authors are not aware of any affiliations, memberships, funding, or financial holdings that might be perceived as affecting the objectivity of this review. }
 
@@
 This work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
-
-This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Security,
-LLC, Lawrence Livermore National Laboratory under Contract \# DE-AC52-07NA27344.
 

### 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs-121618.tex
Adding old draft versions of review article

--- 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs-121618-v1.tex
@@
 Experiments were run on all three of the major Actinides: \ce{^{235}U} \cite{You01}, \ce{^{239}Pu} \cite{Ber02} and \ce{^{238}U} \cite{Fot04}.
-This includes one of the first results for $^{239}$Pu(n,n'$\gamma$), shown in \autoref{fig:239pu_nn} \cite{Ber00}.
 It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial $\gamma$-ray cross sections.
-
-\begin{figure}
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.6\linewidth]{239pu_nn.pdf}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{A selection of the $^{239}$Pu(n,n' $\gamma$) partial $\gamma$-ray cross sections from [Ber00] for the two transitions de-exciting the 5/2$_{2}^{+}$ level at $E_x=$285.46 keV.  }
- \label{fig:239pu_nn}
-\end{figure}
 
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Recent results from activation using a DD-neutron source \cite{voy18a} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n (MeV) < 2.7$ \cite{Bat18}.
+Recent results from activation using a DD-neutron source \cite{voy18a} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n (MeV) < 2.7$ \cite{Bat18].
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.

### 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs.tex
Adding old draft versions of review article

--- 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs-121618.tex
@@
 % % \usepackage{cancel}
-% \usepackage{microtype}
+\usepackage{microtype}
 % \usepackage{listings}
@@
 \hyphenation{gamma-rays}
-\hyphenation{Spec-tro-met-ers}
 
 % \setcounter{secnumdepth}{4}
-
-% Remove overfull hbox warnings in bibliography
-\usepackage{etoolbox}
-\apptocmd{\sloppy}{\vbadness 10000\relax}{}{}
-% \emergencystretch=1em
-
-\pdfminorversion=7
 
@@
 \begin{keywords}
-nuclear data,  structure,  reactions, evaluation, fission, medical Isotopes, nuclear energy, nonproliferation, inelastic scattering, level density, radiative strength, $\beta$-decay, reactor antineutrinos
+\textred{nuclear data,  structure,  reactions, evaluation, fission, medical Isotopes, nuclear energy, nonproliferation, inelastic scattering, level density, radiative strength, $\beta-decay$, reactor antineutrinos}
 \end{keywords}
@@
 
-\begin{wrapfigure}{r}{0.39\textwidth}
+\begin{wrapfigure}{r}{0.4\textwidth}
 \centering
-\includegraphics[width=0.38\textwidth]{pipeline_cropped.pdf}
+\includegraphics[width=0.39\textwidth]{pipeline_cropped.pdf}
 \caption{\label{fig:pipeline}The nuclear data pipeline.}
@@
 Such a model is not yet feasible so different physics models are used to treat pre- and post-scission processes.
-A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{War17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Schm16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.
+A wide range of theoretical approaches have been developed since the late 1930's to describe pre-scission physics, including scission-point models \cite{Wil76,Lem15}, microscopic-macroscopic models \cite{Mol15} with random-walk dynamics \cite{Wa17}, Langevin dynamics \cite{Sie17}, Time-dependent Hartree-Fock and Hartree-Fock-Bogoliubov theory \cite{Koo76,Neg78,Tan15,God16}, the time-dependent superfluid local density approximation \cite{Ste11,Bul13,Ste15,Bul16}, and the time-dependent generator-coordinate method \cite{Ber91,Gou05,Rei16}.Several models have also been developed to describe post-scission physics and built into computer codes, such as GEF \cite{Sch16}, FIFRELIN \cite{Lit15}, CGMF \cite{Tal14}, and FREYA \cite{Ran09,Ver18}.
 
@@
 Finally, there are experimental measurements that directly probe the pre-scission dynamics of the fission process, although they carry large uncertainties and suffer from various ambiguities and limitations.
-These include measurements of scission neutrons \cite{Petrov2009}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}.
+These include measurements of scission neutrons \cite{Pe09}, fission time scales \cite{Jac09}, and muon-induced fission \cite{Mar80}.
 Probes of pre-scission physics can provide unique insights into the details of the fission process, and are therefore extremely valuable to fission theory.
@@
 
-\subsection{Improved \texorpdfstring{\ce{^{235,238}U}}{235,238U} and \texorpdfstring{\ce{^{239}Pu}}{239Pu}(n,n') data for neutron transport}\label{sec:n_transport}
+\subsection{Improved \ce{^{235,238}U} and \ce{^{239}Pu}(n,n') data for neutron transport}\label{sec:n_transport}
 
@@
 CIELO has relatively little energy or angle differential data to draw upon to aid in its evaluation of (n,n') on the \enquote{Big 3} Actinides, leading to \enquote{significant differences amongst the evaluations for \ce{^{239}Pu} in the fast energy range, with ENDF/B-VII.1 and JENDL-4.0 lying significantly above the JEFF-3.1 evaluation.} \cite{Cha14}.
-The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Batchelor1969, Andreev1961}.
+The \ce{^{239}Pu} data referenced in their paper are all from indirect measurements made prior to 1970 \cite{Bat69, And61}.
 The case is similar for \ce{^{235}U} where they note that differences for $E_n >$ 50 keV \enquote{have a large impact on the fast criticality (Godiva), leading to a 540 pcm swing in calculated criticality, as shown by Go Chiba \cite{Chi12}.}
@@
 The spectra for each fuel can be calculated using nuclear databases, in what is commonly known as the \enquote{summation method}.
-Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fei82,Sch85,Hah89}.
+Alternatively, for \ce{^{235}U} and \ce{^{239,241}Pu}, the spectra can also be calculated by converting the aggregate electron spectra measured at ILL in the 1980s \cite{Fel82,Sch85,Hah89}.
 The current best predictions for  \ce{^{235}U} and \ce{^{239,241}Pu} are those by Huber \cite{Hub11} using the conversion method, while for \ce{^{238}U} is that by Mueller et al.
@@
 
-The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{Fal12}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
+The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{20}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
 There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
@@
 These experiments would involve a sample of depleted \ce{^{238}U} since recent results from IBD indicate that the contribution to the observed anomaly in the antineutrino experiment can be attributed to issues with the \ce{^{238}U}(n,f) yields.
-These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{ayllon2018design} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).
+These measurements could be performed at the Godiva in the same fashion as the \ce{^{235}U} irradiation used to validate FIER, or other well-documented fast neutron facilities including the thick target deuteron break neutron source at the LBNL 88-Inch cyclotron \cite{Harrig2018} and the High Flux Neutron Generator at UC-Berkeley \cite{All18} and compare the results to the FIER predictions to inform both the fission yield and decay data for \ce{^{238}U}(n,f).
 
-\subsection{Improved (n,x\texorpdfstring{$\gamma$}{ gamma}) data for active interrogation}
+\subsection{Improved (n,x$\gamma$) data for active interrogation}
 
@@
 The interpretation of this data requires detailed knowledge of both the double-differential neutron scattering and gamma-ray production cross sections from fast down to thermal neutron energies.
-The Evaluated Gamma Activation File \cite{Fir15} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.
+The Evaluated Gamma Activation File \cite{Fir14} provides partial gamma-ray cross section data for transitions between discrete states following thermal neutron capture.
 At higher energies the Atlas of Gamma-rays from the Scattering of Reactor Fast Neutrons \cite{Dem78}, which has recently been compiled into a database and reconciled to reflect state-of-the-art gamma-ray energies from ENSDF \cite{Hur18}, offers discrete gamma-ray cross sections for irradiation with fast fission neutrons.
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Recent results from activation using a DD-neutron source \cite{voy18a} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n (MeV) < 2.7$ \cite{Bat18].
+\textred{Lee - we should add some language here referencing Batch's work on this.}
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
@@
 
-The NDIAWG process reflects a growing recognition that improved nuclear data is essential to a wide range of human endeavors that transcend the needs of any one societal need or governmental mission.
+The NDIWG process reflects a growing recognition that improved nuclear data is essential to a wide range of human endeavors that transcend the needs of any one societal need or governmental mission.
 Its goal is the development of a new, multi-agency national plan to address nuclear data needs in a coherent way.
@@
 
-\section{CONCLUSION \texorpdfstring{---}{-} RETAINING AND TRAINING A SKILLED NUCLEAR DATA WORKFORCE}
+\section{CONCLUSION - RETAINING AND TRAINING A SKILLED NUCLEAR DATA WORKFORCE}
 
@@
 However, it takes many years of post-Ph.D.
-experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
-It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
+experience to train nuclear data evaluators, and only a short break in support to lose these this work force to other pursuits.
+It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the ``Nuclear Data Pipeline'' from measuring and modeling through compilation, evaluation, validation and processing.
 As more and more of the research in the United States moves over to a project-driven model, it is imperative that sponsors coordinate their efforts to ensure that there is no loss of talent in the field.
@@
 
-Furthermore, nuclear data evaluation is an \emph{aging} field, with the mean age of an evaluator in the US being well-over 50.
+Furthermore, nuclear data evaluation is an $\it{aging}$ field, with the mean age of an evaluator in the US being well-over 50.
 It is essential that the next generation of nuclear data evaluators be recruited and trained while the current set of experienced individuals are still active in the field.
-This is particularly challenging since there is, \emph{per se}, no graduate education program in nuclear data evaluation, and the vast majority of the centers with evaluation expertise are not associated with degree-granting institutions.
+This is particularly challenging since there is $\it{per se}$ no graduate education program in nuclear data evaluation, and the vast majority of the centers with evaluation expertise are not associated with degree-granting institutions.
 
-Perhaps one of the \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
+Perhaps one of the ``endangered species'' in nuclear data is the experimental nuclear data evaluator.
 This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR/CSISRS library are to be taken seriously, discarded or normalized to newer standards.
-This sort of a \enquote{hybrid} individual would be capable of providing not only good mean values, but also the well-quantified uncertainties (including covariances) that are needed for most applications.
-A concerted effort on the part of both academia and the international research community is needed to ensure that talented early-career individuals with the right combination of interest and inclination be afforded the opportunity to get trained by an \enquote{international village} of evaluators and application subject matter experts.
+This sort of a ``hybrid'' individual would be capable of providing not only good mean values, but also the well-quantified uncertainties (including covariances) that are needed for most applications.
+A concerted effort on the part of both academia and the international research community is needed to ensure that talented early-career individuals with the right combination interest and inclination be afforded the opportunity to get trained by an ``international village'' of evaluators application subject matter experts.
 
-In closing, it is worth noting that the dramatic increase in computational capabilities over the past several decades allows for the sort of detailed calculations needed to fulfill the promise of many applications, \emph{provided that the correct evaluated data is available}.
+In closing, it is worth noting that the dramatic increase in computational capabilities over the past several decades allow for the sort of detailed calculations needed to fulfill the promise of many applications $\it{provided that the correct evaluated data is available}$.
 Recent efforts in the US offer the promise of a national nuclear data plan to provide the needed data.
@@
 \section*{DISCLOSURE STATEMENT}
-\textred{IThe authors are not aware of any affiliations, memberships, funding, or financial holdings that might be perceived as affecting the objectivity of this review. }
+\textred{If the authors have noting to disclose, the following statement will be used: The authors are not aware of any affiliations, memberships, funding, or financial holdings that
+might be perceived as affecting the objectivity of this review. }
 
@@
 
-\emergencystretch=2em
-
 \bibliographystyle{ar-style5}

### 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs_122018.tex
Adding old draft versions of review article

--- 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs-121618.tex
@@
 %Authors, affiliations address.
-\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^6$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^7$
+\author{Lee A.
+Bernstein$^{1,2}$, David A.
+Brown$^3$, \\Arjan J.
+Koning$^4$, Bradley T.
+Rearden$^5$,  \\Catherine E.
+Romano$^5$, Alejandro A.
+Sonzogni$^3$, Andrew S.
+Voyles$^{2}$, and Walid  Younes$^6$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 \affil{$^3$National Nuclear Data Center, Brookhaven National Laboratory, Upton, NY 11973, USA}
-\affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
-\affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^6$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
-\affil{$^7$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}
+\affil{$^4$Nuclear Data Section, International Atomic Energy Agency, 1400 Vienna, Austria}
+% \affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^5$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
+\affil{$^6$Lawrence Livermore National Laboratory L-414, Livermore, CA 94551, USA}}
 
@@
 Low-energy nuclear science (LENS) \enquote{straddles the fence} between curiosity- and application-driven pursuits.
-On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
+ On the curiosity-driven side, low-energy nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
 LENS also plays an important role in nuclear astrophysics, improving models of stellar energy generation and allowing isotopic abundances to be used to inform models of the astrophysical environments where heavy nuclei are formed.
@@
  This process ends with the users and their application, but actually begins with the performance of carefully-designed measurements with well-defined uncertainties.
-Given this, it behooves those funding or performing the original experiment to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
+ Given this,  those funding or performing the original experiment would be wise to understand the entire nuclear data workflow in order to ensure that new results find their way to the intended user.
  For example, if a new result forces changes to data formats (step 2) or processing (step 3) or to application codes (step 4 \& eventual user), this fact should be considered when developing a new activity.
@@
 In the case of nuclear reaction data, the process is markedly different.
-The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the Evaluated Nuclear Data File \cite{Chadwick2011}.
+ The data from EXFOR is used to guide a physics-based model calculation through a variety of variance minimization procedures, resulting in best estimates of mean values and their uncertainties, including covariances, which are put into the one or more regional libraries such as the recently release of the Evaluated Nuclear Data File (ENDF), ENDF/B-VIII.0 \cite{endf8_0}.
  Most of the effort put into the production of ENDF is provided by applications-oriented users due to its importance to national security, international counter-proliferation and nuclear energy.
@@
  The class of user problems we most rely on are so-called \enquote{integral benchmark} data that depend on many different types of data including cross sections and emitted particle spectra and are also extremely precisely known.
-The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss ($k_{eff}$) is known to several significant figures.
+ The canonical example of such a benchmark is a critical assembly, where the ratio of neutron production to neutron loss (\keff) is known to several significant figures.
  However, there are many other kinds of integral benchmarks used to test neutron interaction data alone, including reaction rate measurements and 14 MeV and fission spectrum transmission experiments, and many more for other forms of nuclear data.
@@
 Much of the work of nuclear data evaluation takes place as a part of international collaborations covered under the Organization of Economic Cooperation and Development's Nuclear Energy Agency (NEA) and the International Atomic Energy Agency (IAEA).
-The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
+ The Nuclear Energy Agency (NEA) addresses the nuclear technology interests of its 33 member states and, in the area of nuclear reaction data, the Working Party on Evaluation Coordination (WPEC) is the main forum for collaborative effort between the nuclear data library projects from the NEA countries, namely ENDF/B (United States), JENDL (Japan), JEFF (NEA), TENDL (Europe), BROND (Russia) as well as the non-OECD file project CENDL (China).
 
@@
 
-\begin{figure}
- \centering
-%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.8\linewidth]{rotated_swings.pdf}
-
- % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
- \caption{Simulations of criticality $k_{eff}$ for \ce{^{239}Pu} for the fast assembly Jezebel, PMF-1.
-This figure shows that both LANL CIELO-1 (ENDF/B-VIII.0) and CEA CIELO-2 (JEFF-3.3) predict similar $k_{eff}$ values, but do so for very different reasons.
-The changes in criticality are evident when individual cross section channels are substituted between the two evaluations.
-The shaded region shows the  resulting range of values for $k_{eff}$.}
- \label{fig:rotated_swings}
-\end{figure}
-
 A new Collaborative International Evaluated Library Organization (CIELO) Coordinated Research Program was started under the auspices of the IAEA \cite{Cha18a} to have the international nuclear data evaluation community agree on a set of evaluated cross sections and output spectra for six critically-important nuclei: \ce{^{1}H}, \ce{^{16}O}, \ce{^{56}Fe}, \ce{^{235,238}U} and \ce{^{239}Pu} in order to address the issue of compensating errors.
@@
 
-There is a great deal of uncertainty in the magnitude of the spin cut-off parameter.
-This is a significant issue since a good knowledge of the $J$ distribution is needed to accurately model the neutron vs.
-$\gamma$-ray emission probability in nuclear reactions.
-This sensitivity was shown recently by Wiedeking et al., \cite{Wie16} who showed that neutron emission from excited states in \ce{^{95}Mo} well-above the neutron separation energy populated via (d,p) was hindered for states with high angular momentum.
-
 \begin{figure}
@@
 
-Information regarding the $J$-dependence of the NLD can also be obtained through observation of the relative population of two low-lying states with very different spins via activation.
-This method has been used in Hg and Au by Chakravarty \cite{PhysRevC.45.1171} and more recently by Sudar in Hg and Pt \cite{PhysRevC.73.034613}.
-\autoref{fig:fe_isomer_plots} shows this for the case of \ce{^{52m}Mn}($J_\pi=2^+$)/\ce{^{52g}Mn}($J_\pi=6^+$) ratio populated via \ce{^{56}Fe}(p,$\alpha$n) measured via stacked-target activation at the LBNL 88-Inch cyclotron as compared to TALYS calculations for different values of the spin cut-off parameter (left) and the 6 level density models available for use in TALYS on the right.
-
-It should be noted that both the (n,n'$\gamma$) and isomer-to-ground state ratio measurements could be performed as part of a program that supports improved neutron transport as described in \autoref{sec:n_transport} above, and a program of cross section measurements in support of medical isotope production described in \autoref{sec:isotope_production} below.
-This reflects the interdependency between nuclear data over a wide range of applications.
-
 \section{NATIONAL SECURITY AND NON-PROLIFERATION}
@@
 The use of nuclear databases to calculate antineutrino spectra is considered less precise than the conversion method due to deficiencies in the underlying fission and decay data, such as beta intensities \cite{Fal12}, beta shape factors due to first-forbidden transitions \cite{Hay14}, evaluated libraries issues \cite{Son15} and fission yields \cite{Son16}.
-There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyvaskyla \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyvaskyla and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
+  There have been considerable efforts in the last few years to improve this situation, including (i) experimental campaigns in Jyv\"{a}skyl\"{a} \cite{Alg10}, ORNL \cite{Ras16} and ANL \cite{MccTBD} to obtain highly precise values of beta intensities, which have been incorporated in the ENDF/B-VIII.0 decay data sub-library; (ii) measurements of isomeric ratios in ILL, Jyv\"{a}skyl\"{a} and ANL; (iii) measurements of fission yields in GELINA \cite{Viv00}, GSI \cite{Pel17} and LANL \cite{Duk16}; (iv) a recent IAEA Coordinated Research Project on beta-delayed neutron emitters \cite{DimXX} that would improve the derivation of cumulative fission yields from independent ones.
   Also planned are measurements of beta shape factors as well as a new IAEA Coordinated Research Project to evaluate fission yields.
@@
 The conversion method is not fully free of issues, either.
-To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay cross section threshold have not been published.
+ To start, it is based on a single set of measurements; also, its most basic premise, the description of a level-to-level spectrum using a particular formalism, has not been tested, as highly precise measurements of electron spectra for fission products above the inverse beta decay (IBD) cross section threshold have not been published.
    As a result, while more precise than the summation method, it is nevertheless considerably less reliable.
     A recent article \cite{Son17} reviewed the different Fermi functions available for the calculation of spectra and showed that a linear correction factor of 6\%/MeV could explain the anomaly.
+
+\begin{figure}[b]
+ \centering
+%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
+ \includegraphics[width=0.7\linewidth]{667_before_v2.png}
+
+ % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
+ \caption{Difference in the FIER-predicted and observed yield of \ce{^{132}I} as a function of time for a \ce{^{235}U} sample irradiated at the GODIVA critical assembly taken from \cite{Matthews2018}.
+}
+ \label{fig:fier_plot}
+\end{figure}
 
@@
 With few benchmark experiments in HA-LEU enrichment range, the interplay of the cross sections for multiple nuclei become important, especially for LEU experiments where \ce{^{1}H}, \ce{^{16}O}, \ce{^{235}U}, \ce{^{238}U} and others are applied simultaneously in the calculation of the integral $k_{eff}$ response.
-Similar to the Chadwick \cite{Cha18} and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
+ Similar to the Chadwick \cite{Cha18} (see \autoref{fig:rotated_swings}) and Bauge \cite{Bau12} studies of Jezebel critical assembly, a team at ORNL preformed an investigation of a hypothetical transportation package with 20\% enriched \ce{^{235}U} in the form of \ce{UF6} using ENDF/B-VII.1 and ENDF/B-VIII.0 libraries by only exchanging the CIELO nuclides.
 A swing in $k_{eff}$ of 450 pcm is observed.
@@
 This data change will also impact repository analysis in salts and there are no benchmark experiments available for validation.
-Recent results from activation using a DD-neutron source \cite{voy18a} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n (MeV) < 2.7$ \cite{Bat18].
+Recent results from activation using a DD-neutron source \cite{Voyles2017} indicate both resonant behavior in this cross section and an average value significantly smaller value for  $2.2 < E_n \text{(MeV)} < 2.7$ \cite{Bat18}.
   \item Graphite data for high-temperature reactors as well as the Transient Reactor Test Facility (TREAT) facility have realized a number of updates that cause dramatic changes in criticality.
@@
   \item Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
+In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.
 \end{itemize}
@@
 
-A robust nuclear data evaluation process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
-However, it takes many years of post-Ph.D.
-experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
+A robust nuclear data process is needed to provide the information required for many applications ranging from nonproliferation to nuclear energy to isotope production.
+ However, it takes many years of post-Ph.D. experience to train nuclear data evaluators, and only a short break in support to lose  this work force to other pursuits.
  It is therefore critical for the many societal programs that rely on nuclear data to support individuals engaged in maintaining all functions that make up the \enquote{Nuclear Data Pipeline}, from measuring and modeling through compilation, evaluation, validation, and processing.
@@
 Perhaps one of the \enquote{endangered species} in nuclear data is the experimental nuclear data evaluator.
-This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR/CSISRS library are to be taken seriously, discarded or normalized to newer standards.
+ This isn't an experimentalist doing a new, better experiment, nor a data library creator that makes an ENDF-like library, but a person who knows which of the more than 22,000 measurements in the EXFOR library are to be taken seriously, discarded or normalized to newer standards.
  This sort of a \enquote{hybrid} individual would be capable of providing not only good mean values, but also the well-quantified uncertainties (including covariances) that are needed for most applications.
@@
 \section*{DISCLOSURE STATEMENT}
-\textred{IThe authors are not aware of any affiliations, memberships, funding, or financial holdings that might be perceived as affecting the objectivity of this review. }
+The authors are not aware of any affiliations, memberships, funding, or financial holdings that
+might be perceived as affecting the objectivity of this review.
 
@@
 
-Work at Lawrence Berkeley National Laboratory has been carried out  under the auspices of the U.S.
-Department of Energy by  Lawrence Berkeley National Laboratory and the U.S.
-Nuclear Data Program under contract \# DE-AC02-05CH11231.
-This work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
+The work by staff from several laboratories was performed under the auspices of the US Department of Energy at Oak Ridge National Laboratory under Contract DE-AC0500OR22725,  Los Alamos National Laboratory under Contract DE-AC52-06NA25396, Lawrence Livermore National Laboratory under Contract DE- AC52-07NA27344, Pacific Northwest National Laboratory under contract DE-AC05-76RLO1830, Lawrence Berkeley National Laboratory under Contract DE-AC02-05CH11231, and Brookhaven National Laboratory under Contract DE-AC02-98CH10886.
+In addition, this work was funded in part by the Consortium for Verification Technology under Department of Energy National Nuclear Security Administration award number DE-NA0002534.
+
+A portion of this work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
 
@@
 
-\bibliography{../../library}
+\bibliography{/Users/nssc/library.bib}
 

### 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs_dbrown.tex
Adding old draft versions of review article

--- 2019-01-01 nuclear_data_needs/drafts/nuclear_data_needs_122018.tex
@@
 %Authors, affiliations address.
-\author{Lee A.
-Bernstein$^{1,2}$, David A.
-Brown$^3$, \\Arjan J.
-Koning$^4$, Bradley T.
-Rearden$^5$,  \\Catherine E.
-Romano$^5$, Alejandro A.
-Sonzogni$^3$, Andrew S.
-Voyles$^{2}$, and Walid  Younes$^6$
+\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^6$
 \affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
@@
 Low-energy nuclear science (LENS) \enquote{straddles the fence} between curiosity- and application-driven pursuits.
- On the curiosity-driven side, low-energy nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
+ On the curiosity-driven side, low-energy ($E_x <$ 1--4 MeV) \textred{DAB: This is very restrictive!} nuclear structure offers a unique laboratory to examine the interplay between single-particle and collective behavior and to explore the transition from quantum to continuum behavior in a mesoscopic setting.
 LENS also plays an important role in nuclear astrophysics, improving models of stellar energy generation and allowing isotopic abundances to be used to inform models of the astrophysical environments where heavy nuclei are formed.
@@
 %  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
- \includegraphics[width=0.7\linewidth]{667_before_v2.png}
+ \includegraphics[width=0.7\linewidth]{667_before_alt.png}
 
@@
   \item Uncertainty data are not available or are incomplete for fission product yields, decay constants, and angular distributions, making it difficult to have high confidence in predicting the performance of advanced systems.
-In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.
+\textred{In the case of fission product yields, there is not even a format for covariance data in the ENDF format, harkening back to the admonition in  \autoref{sec:pipeline}.}
 \end{itemize}
@@
 
-The work by staff from several laboratories was performed under the auspices of the US Department of Energy at Oak Ridge National Laboratory under Contract DE-AC0500OR22725,  Los Alamos National Laboratory under Contract DE-AC52-06NA25396, Lawrence Livermore National Laboratory under Contract DE- AC52-07NA27344, Pacific Northwest National Laboratory under contract DE-AC05-76RLO1830, Lawrence Berkeley National Laboratory under Contract DE-AC02-05CH11231, and Brookhaven National Laboratory under Contract DE-AC02-98CH10886.
-In addition, this work was funded in part by the Consortium for Verification Technology under Department of Energy National Nuclear Security Administration award number DE-NA0002534.
+Work at Lawrence Berkeley National Laboratory has been carried out  under the auspices of the U.S.
+Department of Energy by  Lawrence Berkeley National Laboratory and the U.S.
+Nuclear Data Program under contract \# DE-AC02-05CH11231.
+This work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
 
-A portion of this work used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).
+This work was performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Security,
+LLC, Lawrence Livermore National Laboratory under Contract \# DE-AC52-07NA27344.
 
@@
 
-\bibliography{/Users/nssc/library.bib}
+\bibliography{../../library}
 

### 2019-01-04 fe_px_paper/fe_body_text.tex
Revised body through methods, added fe XS table

@@
 While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production.
+% 
+% 
+% 
 % The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
@@
 \ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection \cite{Dong2015}.
-Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu} \cite{Graves2015}.
-\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging. 
+Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}.
+\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging \cite{Graves2015}. 
 However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging \cite{Dong2015}.
@@
 Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies \cite{Wang2017}.
-\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn}, more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
+\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
 In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications \cite{Wang2017}.
@@
 
-While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6+$)   ratio \cite{Dong2015,Wang2017}.
+While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio \cite{Dong2015,Wang2017}.
 Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
-These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in f$_{7/2}$ subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes.
+These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes.
 In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.
@@
 % 
-% Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
-
-% \comment{Do we really need to cite Alex's thesis?}
+Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
 
@@
 
-% \comment{Update these energies, post-analysis}
-\textred{Update these energies after finalizing the analysis...}
-
 A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
-One stack covers the \textred{55--20}\,MeV range and the other covers \textred{25--5}\,MeV, to minimize the systematic uncertainties associated with degradation of beam energy.
+One stack covers the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
 In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
@@
 % For targets, a
-A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%\cmmnt{, \textred{lot \#T23A035}}), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%\cmmnt{, \textred{lot \#M06C032}}), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%\cmmnt{, \textred{lot \#N26B062}}) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) targets were used.
+A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
 In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
@@
 % , along with the propagated uncertainty in areal density.
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
-The sealed foils were mounted over the hollow center of a 1.5875 mm-thick aluminum frame.
+% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
+The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
+The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
 Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
-% One \ce{^{nat}Al}, one \ce{^{nat}Cu}, and one \ce{^{nat}Nb} mounted foil were bundled together using baling wire for each energy position.
-% These foil packet bundles were lowered into the beamline by inserting them into a  water-cooled production target box.
-% These six foil packet bundles were inserted into one of six  
+% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
 The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
-% has a thin (0.64 mm) Inconel beam entrance window, and  contains 6 \enquote{energy positions} for targets, formed by  5 slabs of 6061 aluminum alloy (previously characterized) which serve as proton energy degraders  between energy positions.
-% At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.
-% After loading all targets in the stack, the lid of the target box is sealed in place, using an inset o-ring to create a water-tight seal, and the box is lowered through a hot cell into the beamline, where it sits electrically isolated.
 The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.
@@
  \centering
- \includegraphics[width=0.5\linewidth]{./figures/SAM_2494.JPG}
+ \includegraphics[width=0.45\textwidth]{./figures/SAM_2494.JPG}
  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
@@
 % \usepackage{booktabs}
-\begin{table}
+\begin{table*}
 \centering
@@
 }
-\end{table}
+\end{table*}
 
@@
 The beam current, measured using a current integrator on the electrically-isolated beamline, remained stable under these conditions for the duration of each irradiation.
-The proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
+The approximately 1\,cm-diameter proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
 Following end-of-bombardment (EoB), each stack was removed from the beamline and disassembled.
@@
 
-% \comment{Get detector specs from Alex}
-
 % For consistency, a
@@
 
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.75\textwidth]{./figures/sample_gspec_fe.pdf}
+ % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
+ \caption{A gamma spectrum collected from an activated Fe foil at approximately 55\,MeV.
+Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks.
+}
+ \label{fig:gspec_femn}
+\end{figure*}
+
 % Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
@@
 % The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.
-The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
+% 
+% Re-introduce this next line for the journal version
+% 
+% 
+% The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
+The   lifetimes and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
+% \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
 Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database  \cite{berger2011xcom}.
@@
 For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
-Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, that  independent cross sections may be reported \cite{bateman1910solution,Cetnar2006}.
-
-\begin{figure}
- \centering
- \includegraphics[width=6in]{./figures/AP161219_Fe01_10cm.png}
- % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
- \caption{\textred{Replace this figure!!!}  A gamma spectrum collected from an activated Fe foil at approximately \textred{80 MeV}.
-While the majority of observed reaction products are visible in this spectrum,  the \ce{^{51}Cr}, \ce{^{52m}Mn}, and \ce{^{52g}Mn} decay lines, which form the   primary reaction channels of interest, are  clearly isolated from surrounding peaks.}
- \label{fig:gspec_femn}
-\end{figure}
+Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported \cite{bateman1910solution,Cetnar2006}.
 
@@
 
-In addition to the stack's overall beam current measurements using  beamline current integrators, thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Fe} targets at each energy position, to monitor beam current at each position within the stack.
+In addition to the stack's overall beam current measurements using  beamline current integrators, thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Fe} targets, 
+% at each energy position, 
+to monitor beam current at each position within the stack.
 % These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
@@
 \cite{Hermanne2018}.
-% The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
 As in our previous work, the integral form of the well-known activation equation was used to  determine proton fluence ($I \Delta t $),
@@
 \end{equation}
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation  \cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 10 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation  \cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
 
@@
 Estimates of the proton beam energy for preliminary stack designs were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-However, the more rigorous Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, to determine the full proton energy and fluence distribution for each foil   \cite{Goorley2012}.
-$10^8$ source protons were used for all MCNP simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
-As with the determination of proton fluence in monitor foils, the progressively increasing energy straggle towards the rear of each stack is accounted for using the differential proton fluence from MCNP simulation of proton transport.
+However, the more rigorous  transport code FLUKA-2011.2x.3 was used for simulation of the full 3-D target stack, to determine the full proton energy and fluence distribution for each foil   \cite{Bohlen2014a}.
+$10^8$ source protons were used for all FLUKA simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
+As with the determination of proton fluence in monitor foils, the progressively increasing energy straggle towards the rear of each stack is accounted for using the differential proton fluence from FLUKA simulation of proton transport.
 These energy distributions $\frac{d\phi}{dE}$ are used to calculate a flux-weighted average proton  energy $\langle E \rangle$, which accounts for the slowing-down of protons within a foil (particularly in the low-energy stack) and reports the effective  energy centroid for each foil:
@@
 \end{equation}
-To report a complete description of the representative energy for each foil, a bin width is provided through the  energy uncertainty, calculated as the full width at half maximum (FWHM) of the MCNP6-modeled energy distribution for each foil.
+To report a complete description of the representative energy for each foil, a bin width is provided through the  energy uncertainty, calculated as the full width at half maximum (FWHM) of the FLUKA-modeled energy distribution for each foil.
 
@@
 This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions used in this work should all be consistent at each energy position.
-Assuming that the recommended monitor reaction cross sections and MCNP6-modeled energy distributions are both accurate, residual disagreement in the  observed proton fluences is thus primarily due to poorly characterized stopping power in simulations, or a systematic error in the
+Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, residual disagreement in the  observed proton fluences is thus primarily due to poorly characterized stopping power in simulations, or a systematic error in the
 % stack design, namely, the
 areal densities of the stack components. 
-This disagreement is minor at the front of the stack, and gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
+This disagreement is minor at the front of the stack, but gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
 
 When performing  a variance minimization, it is important to apply this variation of effective areal density  to the stack components which  have the most significant impact on beam degradation, as any systematic error in the areal densities used for these components will cause a disagreement in the observed fluences.
-For the 55\,MeV stack, the aluminum degraders are used for variance minimization, as they make up more than 80\% of the areal density of the stack, and this play the largest role in beam degradation.
-% 
-% Update this post-results!
-% 
-% Delete  the paragraph break!
-%
-
-\textred{Update this post-results!}
+For the 55\,MeV stack, the aluminum degraders are used for variance minimization, as they make up more than 80\% of the areal density of the stack, and thus play the largest role in beam degradation.
 For the 25\,MeV stack, the Kapton tape was chosen for variance minimization, as the foil packets themselves are responsible for the majority of beam degradation.
@@
 In addition, it is far easier to directly characterize the areal density of the metallic foils than it is for the Kapton, resulting in only an approximate value for the latter.
-This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but the stopping power of the Kapton at this energy range may cause as much as a loss of 0.5\,MeV by the rear of this stack, making the precise areal density a source of significant uncertainty.
+While it might seem obvious, the contributions to the slowing of the beam due to the adhesive has often been neglected in much work performed to date. 
+This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but the stopping power of the Kapton becomes increasingly important for proton energies below approximately 25\,MeV, causing as much as a loss of 8\,MeV by the rear of this stack, making the precise areal density a source of significant uncertainty.
 
-In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
+In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  were varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
 For the 25\,MeV stack, the areal density of the E-09 and H-01 aluminum degraders was taken from that reached in the minimization of the 55\,MeV stack.
@@
 These lowest energy positions were chosen as  minimization candidates, as they are the most sensitive to systematic uncertainties in stack design, due to the compounded effect of proton stopping powers.
-In the 25\,MeV stack, activity was not seen in gamma spectrometry for the lowest-energy (Ti-20, Cu-20) monitor foils, implying that the beam was stopped at some point in between Fe-14 and Ti-20.
+In the 25\,MeV stack, activity was not seen in gamma spectrometry for the lowest-energy (Cu-20) monitor foil, implying that the beam was stopped at some point in between Ti-20 and Cu-20.
 This observation is conclusive proof that  the true areal densities of the stack components differs from nominally measured values (primarily for the difficult-to-characterize Kapton tape), as transport calculations using nominal areal densities predict that the beam should exit the stack (at the SS-6 profile monitor) with an energy of approximately 7\,MeV.
 As a result, this position was not used for minimization, with the Ti-19 and Cu-19 position being the lowest-energy reliable monitor foils in the stack.
-The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average \textred{41.34\,MeV} protons entering the last energy position of the 55\,MeV stack.
-This is approximately \textred{2\,MeV} lower than the nominal MCNP6 simulations, and approximately \textred{3\,MeV} lower than nominal A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
-This energy corresponds to an aluminum areal density of \textred{2.52\%} greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
-Similarly, for the 25\,Me stack, variance minimization converges on  flux-weighted average \textred{41.34\,MeV} protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately \textred{2\,MeV} lower than the nominal MCNP6 simulations, and approximately \textred{3\,MeV} lower than nominal A\&Z calculations.
-This energy corresponds to a Kapton tape areal density of \textred{2.52\%} greater than nominal measurements.
+% % Remove these next two liens for the journal version
+% % 
+% With the exception of two foils (Cu-20 and Ti-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
+% % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
+% This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Fe-14 and Ti-20.
+% 
+% Re-introduce the rest of this paragraph for the journal version
+% 
+% 
+The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average 22.71\,MeV protons entering the last energy position of the 55\,MeV stack.
+This is approximately 2\,MeV lower than the nominal FLUKA simulations, and approximately 2\,MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
+This energy corresponds to an aluminum areal density of 4.43\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
+Similarly, for the 25\,Me stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations, and approximately 5\,MeV lower than nominal A\&Z calculations.
+This energy corresponds to a Kapton tape areal density of 5.69\% greater than nominal measurements.
 The impact of this variance minimization for improving disagreement in proton fluence is  clearly  seen in   \autoref{fig:fe_variance_mins}.
 
-\begin{figure}
+\begin{figure*}
     \centering
@@
         \centering
-%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
-        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
+        \hspace{-5pt}\subfigimg[width=0.485\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
 %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
@@
 
-%         \subfigimg[width=0.5\textwidth]{b)}{./figures/after_minimization_plot.pdf}{50}
-        \subfigimg[width=0.5\textwidth]{b)}{./figures/current_norm_az.pdf}{50}
+        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
          %         \refstepcounter{subfigure}
@@
    \hspace{-5pt}}%
-    \caption{\textred{Update this figure!!!} Results of variance minimization through enhancement of the effective areal density of the  aluminum degraders by \textred{2.52\%} (55\,MeV stack) and Kapton tape by \textred{2.52\%} (25\,MeV stack).
+    \caption{Results of variance minimization through enhancement of the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
 A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
-%     Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
      \label{fig:fe_variance_mins}
-\end{figure}
+\end{figure*}
 
+% Re-introduce this paragraph for the journal version
+% 
 An enhanced version of the final \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reaction fluences is shown in \autoref{fig:fe_fluence_plot}.
@@
 Uncertainty in proton fluence  is  calculated by error propagation of the fluence values  at each energy position.
-These weighted-mean fluences are  plotted  in \autoref{fig:fe_fluence_plot}, along with the estimated fluence according to both  MCNP6 transport 
+These weighted-mean fluences are  plotted  in \autoref{fig:fe_fluence_plot}, along with the estimated fluence according to both  FLUKA transport 
 and an uncertainty-weighted linear $\chi^2$ fit to the individual monitor channel fluence measurements.
-\textred{Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.}
+Both models reproduce the observed fluence data consistently within uncertainty for the 55\,MeV stack, with the FLUKA model predicting a slightly greater fluence loss throughout the stack.
+However, neither model is capable of accurately modeling the rapid decrease in apparent fluence at the rear of the 25\,MeV stack.   
 These models are used purely to provide an extrapolation from the highest-energy position back to the \enquote{front} of each stack, to compare with the nominal fluence measured by  the beamline current integrators.
+% 
+% 
+% 
+% 
+% 
 % This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
@@
 %  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
-%  \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in MCNP6.
+%  \caption{Final variance minimized incident proton energy distributions for the Nb foils, as simulated in FLUKA.
 The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
@@
  \centering
-%  \includegraphics[width=0.5\linewidth]{./figures/fe_fluence_plot.pdf}
- \includegraphics[width=0.5\linewidth]{./figures/current_norm_az.pdf}
+ \includegraphics[width=0.495\textwidth]{./figures/fluence_plot.pdf}
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{\textred{Update this figure!!!} Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.
+ \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.}
 %  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
 %   A clear loss of 
-  The fluence  drops by approximately \textred{7.2--8.9\%} from the incident fluence of \textred{196.9--198.8 nAh} over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.}
+%   The fluence  drops by approximately \textred{7.2--8.9\%} from the incident fluence of \textred{196.9--198.8 nAh} over the length of each target stack, based on fluence loss models from FLUKA simulations and an empirical fit to  fluence measurements.}
 %   This is due to a combination of beam utilization, as well as scattering.}
@@
 % cross sections, 
-over the energy distribution subtended by each foil, as seen in \autoref{fig:Fe_ptallies}.
+over the energy distribution subtended by each foil.
+% Re-introduce this next line for the journal version
+% , as seen in \autoref{fig:Fe_ptallies}.
 For both the cumulative and independent activities quantified, cross sections were calculated as:
@@
 The beam current, measured using a current integrator connected to the electrically-isolated target box, remained stable for the duration of the irradiation.
-The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 30\,s, to account for any minor transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fe_fluence_plot}).
+The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 10\,s, to account for any minor transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position).
+% , as seen in \autoref{fig:fe_fluence_plot}).
 
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/Fe_mcnp_spectrum.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{\textred{Add 25\,MeV stack tallies here!
-} Final variance minimized incident proton energy distributions for the Fe foils, as simulated in MCNP6.
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{./figures/Fe_mcnp_spectrum.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{\textred{Add 25\,MeV stack tallies here!
+} Final variance minimized incident proton energy distributions for the Fe foils, as simulated in FLUKA.
 The distribution tallies in each foil are all normalized to be per source proton, which was $10^8$ in all simulations.
 As the beam is degraded, proton energy distributions become visibly broadened due to straggling, and drop in magnitude due to scattering losses.}
- \label{fig:Fe_ptallies}
-\end{figure}
+%  \label{fig:Fe_ptallies}
+% \end{figure}
 
@@
 After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
-With the exception of two foils (Cu-20 and Ti-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
+With the exception of a single foil (Cu-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
 % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
-This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Fe-14 and Ti-20.
-Using the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of \textred{198.8$\pm$6.7\,nAh} was calculated to be incident upon the 55\,MeV target stack using the MCNP6 fluence model, and a  fluence of \textred{196.9$\pm$11.3\,nAh} using the linear fit model.
-Similarly, for the 25\,MeV stack, a fluence of \textred{198.8$\pm$6.7\,nAh} was calculated to be incident upon the 55\,MeV target stack using the MCNP6 fluence model, and a  fluence of \textred{196.9$\pm$11.3\,nAh} using the linear fit model.
-\textred{All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the beamline current integrators.}
-\textred{As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.}
-This incident fluence dropped by approximately \textred{8.9\% to  180.9$\pm$5.4\,nAh (and by 7.2\% to  182.7$\pm$13.5\,nAh using the linear fit model)} over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Voyles2018a,Graves2016}.
+This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Ti-20 and Cu-20.
+Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 18.8$\pm$1.0\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$\pm$1.3\,nAh using the linear fit model.
+Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
+All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the beamline current integrators.
+As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
+This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at IPF in the past \cite{Voyles2018a,Graves2016}.
 This loss of fluence is due to a combination of 
@@
 \small
-% \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllllllllllll@{}}
 \toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-% \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
-% \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
-% \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
-% \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
-% \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
-% \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
-% \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
-% \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
-% \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
-% \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
-\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
-\end{tabular}
-% }
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:cufe_rp_table}
-\small
-% \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-% \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
-% \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
-% \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
-% \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
-% \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
-% \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
-% \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
-% \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
-% \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
-% \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
-\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
-\end{tabular}
-% }
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:ti_rp_table}
-\small
-% Disable next line for journal submission
-% \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% \ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
-% \ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
-% \ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
-% \ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
-% \ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
-% \ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
-% \ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
-% \ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
-% \ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
-% \ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
-% \ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
-\ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
-\end{tabular}
-% }
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
-\label{tab:fe_ibr_table}
-\small
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllll@{}}
-\toprule
-                               & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
-E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
-E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
-\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
+                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
+% E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+% E$_\text{p}$ (MeV)  & $53.45 \pm0.61$ & $46.63 \pm0.68$ & $38.93 \pm0.78$ & $34.62 \pm0.85$ & $29.84 \pm0.96$ & $24.4 \pm1.1$ & $22.71 \pm0.43$ & $19.36 \pm0.56$ & $17.6 \pm1.5$ & $16.54 \pm0.48$ & $14.52 \pm0.49$ & $12.11 \pm0.53$ & $9.23 \pm0.61$ & $4.10 \pm0.73$\\  \midrule
+E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\  \midrule
+\ce{^{48}Cr}\,($\sigma_c$)&	\makecell{0.1684\\$\pm$0.0064} &	\makecell{0.01310\\$\pm$0.00044} &	\makecell{0.00435\\$\pm$0.00018} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{48}V}\,($\sigma_i$)&	\makecell{6.25\\$\pm$0.28} &	\makecell{4.41\\$\pm$0.17} &	\makecell{0.513\\$\pm$0.021} &	\makecell{0.1096\\$\pm$0.0052} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{48}V}\,($\sigma_c$)&	\makecell{6.42\\$\pm$0.28} &	\makecell{4.43\\$\pm$0.17} &	\makecell{0.517\\$\pm$0.021} &	\makecell{0.1096\\$\pm$0.0052} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{49}Cr}\,($\sigma_c$)&	\makecell{1.794\\$\pm$0.071} &	\makecell{2.14\\$\pm$0.13} &	\makecell{1.197\\$\pm$0.085} &	\makecell{0.315\\$\pm$0.032} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.25} &	\makecell{15.69\\$\pm$0.32} &	\makecell{11.78\\$\pm$0.29} &	\makecell{6.15\\$\pm$0.25} &	\makecell{0.475\\$\pm$0.025} &	\makecell{0.68\\$\pm$0.10} &	\makecell{1.060\\$\pm$0.081} &	\makecell{1.967\\$\pm$0.067} &	\makecell{2.10\\$\pm$0.14} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
+\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{64.1\\$\pm$4.0} &	\makecell{75.7\\$\pm$3.3} &	\makecell{56.5\\$\pm$2.5} &	\makecell{27.6\\$\pm$1.3} &	\makecell{3.83\\$\pm$0.44} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.11} &	\makecell{0.150\\$\pm$0.026} &	\makecell{0.067\\$\pm$0.017} &	\makecell{NaN\\$\pm$0.14} &	\makecell{NaN\\$\pm$0.088} &	\makecell{NaN\\$\pm$0.045} &	-- &	--\\
+\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{75.9\\$\pm$4.0} &	\makecell{91.3\\$\pm$3.3} &	\makecell{68.3\\$\pm$2.5} &	\makecell{33.7\\$\pm$1.3} &	\makecell{4.30\\$\pm$0.44} &	\makecell{1.582\\$\pm$0.071} &	\makecell{1.760\\$\pm$0.072} &	\makecell{2.117\\$\pm$0.079} &	\makecell{2.165\\$\pm$0.096} &	\makecell{1.91\\$\pm$0.12} &	\makecell{1.450\\$\pm$0.076} &	\makecell{0.823\\$\pm$0.037} &	-- &	--\\
+\ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.685\\$\pm$0.092} &	\makecell{1.733\\$\pm$0.063} &	\makecell{1.601\\$\pm$0.057} &	\makecell{2.247\\$\pm$0.078} &	\makecell{0.770\\$\pm$0.029} &	\makecell{0.2059\\$\pm$0.0099} &	\makecell{0.1920\\$\pm$0.0096} &	\makecell{0.01297\\$\pm$0.00046} &	\makecell{0.00240\\$\pm$0.00015} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{52m}Mn}\,($\sigma_i$)&	\makecell{8.13\\$\pm$0.28} &	\makecell{9.04\\$\pm$0.28} &	\makecell{13.69\\$\pm$0.47} &	\makecell{17.86\\$\pm$0.61} &	\makecell{23.34\\$\pm$0.79} &	\makecell{11.82\\$\pm$0.41} &	\makecell{5.78\\$\pm$0.19} &	\makecell{0.0763\\$\pm$0.0026} &	\makecell{0.0756\\$\pm$0.0033} &	\makecell{0.0754\\$\pm$0.0032} &	\makecell{0.0585\\$\pm$0.0026} &	-- &	-- &	--\\
+\ce{^{52g}Mn}\,($\sigma_i$)&	\makecell{11.36\\$\pm$0.39} &	\makecell{12.82\\$\pm$0.39} &	\makecell{20.85\\$\pm$0.74} &	\makecell{28.16\\$\pm$0.98} &	\makecell{21.81\\$\pm$0.75} &	\makecell{16.32\\$\pm$0.58} &	\makecell{10.37\\$\pm$0.43} &	\makecell{0.300\\$\pm$0.011} &	\makecell{0.1113\\$\pm$0.0049} &	\makecell{0.0428\\$\pm$0.0024} &	\makecell{0.00540\\$\pm$0.00029} &	-- &	-- &	--\\
+\ce{^{52}Mn}\,($\sigma_c$)&	\makecell{13.39\\$\pm$0.54} &	\makecell{14.88\\$\pm$0.74} &	\makecell{23.0\\$\pm$1.3} &	\makecell{30.9\\$\pm$1.3} &	\makecell{31.7\\$\pm$1.2} &	\makecell{18.54\\$\pm$0.87} &	\makecell{10.57\\$\pm$0.38} &	\makecell{0.313\\$\pm$0.012} &	\makecell{0.0389\\$\pm$0.0038} &	\makecell{0.0556\\$\pm$0.0029} &	\makecell{0.0185\\$\pm$0.0012} &	-- &	-- &	--\\
+\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{128.4\\$\pm$5.0} &	\makecell{154.4\\$\pm$6.2} &	\makecell{166.7\\$\pm$7.6} &	\makecell{129.2\\$\pm$7.4} &	\makecell{42.2\\$\pm$2.4} &	\makecell{2.46\\$\pm$0.22} &	\makecell{1.10\\$\pm$0.11} &	\makecell{1.09\\$\pm$0.13} &	\makecell{1.46\\$\pm$0.14} &	\makecell{1.53\\$\pm$0.12} &	\makecell{1.362\\$\pm$0.069} &	\makecell{1.173\\$\pm$0.055} &	\makecell{0.767\\$\pm$0.033} &	\makecell{0.0500\\$\pm$0.0046}\\
+\ce{^{55}Co}\,($\sigma_i$)&	\makecell{9.25\\$\pm$0.38} &	\makecell{11.89\\$\pm$0.77} &	\makecell{15.72\\$\pm$0.80} &	\makecell{21.46\\$\pm$0.87} &	\makecell{48.4\\$\pm$2.3} &	\makecell{64.7\\$\pm$4.5} &	\makecell{61.0\\$\pm$3.5} &	\makecell{43.6\\$\pm$2.2} &	\makecell{33.2\\$\pm$2.6} &	\makecell{13.42\\$\pm$0.71} &	\makecell{0.377\\$\pm$0.021} &	\makecell{0.0436\\$\pm$0.0020} &	-- &	--\\
+\ce{^{56}Mn}\,($\sigma_c$)&	-- &	\makecell{0.494\\$\pm$0.029} &	\makecell{0.610\\$\pm$0.030} &	\makecell{0.462\\$\pm$0.037} &	\makecell{0.506\\$\pm$0.046} &	\makecell{0.405\\$\pm$0.025} &	\makecell{0.2227\\$\pm$0.0079} &	\makecell{0.0962\\$\pm$0.0035} &	\makecell{0.0326\\$\pm$0.0037} &	\makecell{0.0253\\$\pm$0.0011} &	\makecell{0.01318\\$\pm$0.00093} &	-- &	-- &	--\\
+\ce{^{56}Co}\,($\sigma_i$)&	\makecell{12.74\\$\pm$0.81} &	\makecell{15.5\\$\pm$1.1} &	\makecell{18.9\\$\pm$1.2} &	\makecell{23.6\\$\pm$1.1} &	\makecell{29.2\\$\pm$2.0} &	\makecell{47.8\\$\pm$2.0} &	\makecell{51.6\\$\pm$1.9} &	\makecell{82.6\\$\pm$3.2} &	\makecell{174.3\\$\pm$8.0} &	\makecell{197.3\\$\pm$8.4} &	\makecell{344\\$\pm$15} &	\makecell{389\\$\pm$15} &	\makecell{296\\$\pm$13} &	\makecell{2.95\\$\pm$0.28}\\
+\ce{^{57}Co}\,($\sigma_i$)&	-- &	\makecell{0.454\\$\pm$0.040} &	\makecell{0.539\\$\pm$0.052} &	\makecell{0.648\\$\pm$0.027} &	\makecell{1.170\\$\pm$0.060} &	\makecell{1.836\\$\pm$0.070} &	\makecell{2.359\\$\pm$0.086} &	\makecell{2.50\\$\pm$0.11} &	\makecell{3.17\\$\pm$0.15} &	\makecell{3.40\\$\pm$0.15} &	\makecell{5.14\\$\pm$0.26} &	\makecell{8.46\\$\pm$0.31} &	\makecell{11.81\\$\pm$0.58} &	\makecell{4.58\\$\pm$0.42}\\
+\ce{^{58m}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0427\\$\pm$0.0016} &	\makecell{0.0619\\$\pm$0.0023} &	\makecell{0.1054\\$\pm$0.0042} &	\makecell{0.1718\\$\pm$0.0078} &	\makecell{0.236\\$\pm$0.011} &	\makecell{0.239\\$\pm$0.012} &	\makecell{0.300\\$\pm$0.019} &	\makecell{0.475\\$\pm$0.026} &	\makecell{0.564\\$\pm$0.021} &	\makecell{0.490\\$\pm$0.022} &	\makecell{0.141\\$\pm$0.016}\\
+\ce{^{58g}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0884\\$\pm$0.0044} &	\makecell{0.0980\\$\pm$0.0049} &	\makecell{0.1118\\$\pm$0.0057} &	\makecell{0.1229\\$\pm$0.0062} &	\makecell{0.1484\\$\pm$0.0058} &	\makecell{0.330\\$\pm$0.020} &	\makecell{0.318\\$\pm$0.016} &	\makecell{0.919\\$\pm$0.057} &	\makecell{1.320\\$\pm$0.072} &	\makecell{1.599\\$\pm$0.097} &	\makecell{0.519\\$\pm$0.048}\\
+\ce{^{58}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.1311\\$\pm$0.0047} &	\makecell{0.1599\\$\pm$0.0055} &	\makecell{0.2172\\$\pm$0.0071} &	\makecell{0.295\\$\pm$0.010} &	\makecell{0.384\\$\pm$0.012} &	\makecell{0.569\\$\pm$0.023} &	\makecell{0.618\\$\pm$0.025} &	\makecell{1.395\\$\pm$0.062} &	\makecell{1.883\\$\pm$0.075} &	\makecell{2.09\\$\pm$0.10} &	\makecell{0.660\\$\pm$0.050}\\ \bottomrule
 \end{tabular}
@@
 \end{table}
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+% \label{tab:cufe_rp_table}
+% \small
+% % \resizebox{\textwidth}{!}{%
+% \begin{tabular}{@{}lllllll@{}}
+% \toprule
+%                             & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+% E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+% % \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
+% % \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
+% % \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
+% % \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
+% % \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
+% % \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
+% % \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
+% % \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
+% % \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
+% % \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
+% \ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
+% \end{tabular}
+% % }
+% \end{table}
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work.
+Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
+% \label{tab:ti_rp_table}
+% \small
+% % Disable next line for journal submission
+% % \resizebox{\textwidth}{!}{%
+% \begin{tabular}{@{}lllllll@{}}
+% \toprule
+%                             & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
+% E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+% % \ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
+% % \ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
+% % \ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
+% % \ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
+% % \ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
+% % \ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
+% % \ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% % \ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
+% % \ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
+% % \ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
+% % \ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
+% % \ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
+% \ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
+% \end{tabular}
+% % }
+% \end{table}
+% 
+% 
+% 
+% 
+% 
+% 
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table}
+% \centering
+% \caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
+% \label{tab:fe_ibr_table}
+% \small
+% \resizebox{\textwidth}{!}{%
+% \begin{tabular}{@{}lllllll@{}}
+% \toprule
+%                                & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
+% E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
+% \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
+% E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
+% \ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
+% \ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
+% \ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
+% \end{tabular}
+% }
+% \end{table}
+% 
+% 
+% 
+% \textred{Placeholder text follows...fill in actual discussion of results...}
+% 
+% % lee:
+% % 
+% % In addition to the interest in the production of 51,52 Mn for PET research, this experiment offered
+% % an opportunity to study the distribution of angular momentum in compound nuclear and direct
+% % pre-equilibrium reactions via observation of the 52g Mn (t ½ =5.591±0.003 d; J π =6 + ) to 52m Mn
+% % (t ½ =21.1±0.2 m; J π =2 + ) ratio. These results indicated were presented at the University of Oslo in
+% % May 2017 5 and indicate that the constant
+% % temperature nuclear level density model
+% % which has had the greatest success at
+% % reproducing most low-energy nuclear
+% % reaction data fails to reproduce the
+% % deposition of angular momentum at both
+% % compound and pre-compound energies
+% % (see figure 3). This result will be
+% % discussed in greater detail in Mr. Andrew
+% % Voyles’ doctoral dissertation, which is
+% % expected to be completed by May 2018.
+% 
+% 
+% 
+% These results have several notable features.
+% The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
+% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
+% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
+% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
+% 
+% 
+% 
+% % Furthermore, t
+% This work presents the first measurements of several observables in 
+% % these mass regions.
+% % This work reports the first experimental measurement of
+% this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
+% % It also represents  the first measurement of 
+% the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
+% The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
+% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
+% % (${^{1}/_{2}}^{-}$)
+% % ($\sfrac{1}{2}^-$) 
+% isomer branching ratio via \ce{^{nat}Nb}(p,x).
+% 
+% 
+% \textred{Comment on details of 51/52Mn production here...}
+% 
+% 
+% Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
+% This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
+% % The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
+% \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
+% % , which makes activity quantification trivial.
+% % In addition, 
+% \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
+% Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
+% Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
+% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
+% 
+% 
+% 
+% \textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
+% 
+% 
+% 
+% In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
+% These include the non-standard positron emitters 
+% \ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+% \ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
+% \ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+% \ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
+% % the $\beta^-$-therapy agent  \ce{^{64}Cu},  
+% and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
+% Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
+% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
+% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+% 
+% 
+% 
+% 
+% \subsection{Comparison of reaction modeling with experimental results}
+% 
+% 
+% 
+% % In this work
+% Cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
+% For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
+% This, in turn, offers the opportunity to 
+% % use these data to gain insight into 
+% gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
+% The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
+% The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:fe_defaults}. 
+% The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
+% % All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes. 
+% 
+% 
+% The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
+% % \cite{add_level_density_models_here}. 
+% The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
+% % \cite{add_level_density_models_here}.
+% The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
+% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes. 
+% 
+% 
+% % \def\arraystretch{1.5}
+% \begin{table}
+%  \caption{Default settings for the reactions codes}
+%  \label{tab:fe_defaults}
+%  \resizebox{\textwidth}{!}{%
+% \begin{tabular}{ c c c c}
+% 
+%  \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
+%  EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
+%  TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
+%   CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
+%   
+% \end{tabular}
+% }
+% \end{table}
+% 
+% % The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
+% % Only total channel residual 
+% Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
+% % that have only one reaction channel, and that are 
+% and at least 1\% of the total reaction cross section.
+% % are discussed in detail. 
+% % Residual production
+% Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
+% % the compound portion of the cross section
+% being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
+% % Some residuals, such as 
+% Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
+% % Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
+% % Very small channels, 
+% We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
+% % are excluded because the modeling of their cross sections is 
+% because their behavior is extremely sensitive  to  more dominant  channels.
+% The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
+% 
+% 
+% The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70\,MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
+% The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
+% The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50\,MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
+% In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011 \cite{Titarenko2011}.
+% 
+% The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
+% TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
+% EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
+% 
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{./figures/51Mn_px.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
+%  \label{fig:51Mn}
+% \end{figure}
+% 
+% 
+% 
+% 
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
+%  \label{fig:temp_90Mo}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
+%  \label{fig:temp_90Nb}
+% \end{figure}
+% 
+% 
+% 
+% 
+% In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
+% For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
+% For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
+% 
+% 
+% The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
+% For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
+% The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
+% \ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
 
-\textred{Placeholder text follows...fill in actual discussion of results...}
-
-% lee:
+%  \section{\label{sec:conclusions_fe}Conclusions}
 %  
-% In addition to the interest in the production of 51,52 Mn for PET research, this experiment offered
-% an opportunity to study the distribution of angular momentum in compound nuclear and direct
-% pre-equilibrium reactions via observation of the 52g Mn (t ½ =5.591±0.003 d; J π =6 + ) to 52m Mn
-% (t ½ =21.1±0.2 m; J π =2 + ) ratio. These results indicated were presented at the University of Oslo in
-% May 2017 5 and indicate that the constant
-% temperature nuclear level density model
-% which has had the greatest success at
-% reproducing most low-energy nuclear
-% reaction data fails to reproduce the
-% deposition of angular momentum at both
-% compound and pre-compound energies
-% (see figure 3). This result will be
-% discussed in greater detail in Mr. Andrew
-% Voyles’ doctoral dissertation, which is
-% expected to be completed by May 2018.
-
-These results have several notable features.
-The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
-Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
-Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
-
-% Furthermore, t
-This work presents the first measurements of several observables in 
-% these mass regions.
-% This work reports the first experimental measurement of
-this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
-% It also represents  the first measurement of 
-the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
-The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
-Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
-% (${^{1}/_{2}}^{-}$)
-% ($\sfrac{1}{2}^-$) 
-isomer branching ratio via \ce{^{nat}Nb}(p,x).
-
-\textred{Comment on details of 51/52Mn production here...}
-
-Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
-This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
-% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
-% , which makes activity quantification trivial.
-% In addition, 
-\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
-Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
-This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
-
-\textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
-
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard positron emitters 
-\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
-\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
-\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
-\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
-% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
-Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
-The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
-This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
-
-\subsection{Comparison of reaction modeling with experimental results}
-
-% In this work
-As mentioned before, cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
-This, in turn, offers the opportunity to 
-% use these data to gain insight into 
-gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
-The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
-The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
-The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
-% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
-% \cite{add_level_density_models_here}. 
-The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
-% \cite{add_level_density_models_here}.
-The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
-All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-% \def\arraystretch{1.5}
-\begin{table}
- \caption{Default settings for the reactions codes}
- \label{tab:fe_defaults}
- \resizebox{\textwidth}{!}{%
-\begin{tabular}{ c c c c}
-
- \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
- EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
- TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
-
-\end{tabular}
-}
-\end{table}
-
-% The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
-% Only total channel residual 
-Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
-% that have only one reaction channel, and that are 
-and at least 1\% of the total reaction cross section.
-% are discussed in detail. 
-% Residual production
-Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
-% the compound portion of the cross section
-being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
-% Some residuals, such as 
-Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
-% Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
-% Very small channels, 
-We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
-% are excluded because the modeling of their cross sections is 
-because their behavior is extremely sensitive  to  more dominant  channels.
-The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
-
-The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70\,MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
-The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
-The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50\,MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
-In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011 \cite{Titarenko2011}.
-
-The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
-TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
-EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/51Mn_px.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
- \label{fig:51Mn}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:temp_90Mo}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
- \label{fig:temp_90Nb}
-\end{figure}
-
-In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
-For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
-For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
-
-The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
-For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
-The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
-\ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
-
- \section{\label{sec:conclusions_fe}Conclusions}
-
-We present here a set of measurements of \textred{38} cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of \textred{five} isomer branching ratios.
-Nearly all cross sections have been reported with higher precision than previous measurements.
-\textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
-% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for V \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
-Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
-
-% We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
+% 
+% We present here a set of measurements of \textred{38} cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of \textred{five} isomer branching ratios.
 % Nearly all cross sections have been reported with higher precision than previous measurements.
-% We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
-% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+% \textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
+% % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for V \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
 % Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
+% 
+% 
+% % We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
+% % Nearly all cross sections have been reported with higher precision than previous measurements.
+% % We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
+% % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+% % We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
+% % Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
 

### 2019-01-05 fe_px_paper/fe_body_text.tex
Added all data tables to results

@@
 % Figure 3 shows the 52mMn(2+)/52gMn(6+) isomer-to-ground state branching ratio for the naFe(p,αn) reaction, calculated using TALYS-v1.8 over the 20 - 55 MeV range spanned by the foil stack.
-It is possible to use this measurement to infer the spin cut-off σ2, the width of the angular momentum distribution of the level density [6], [7].
+It is possible to use this measurement to infer the spin cut-off σ2, the width of the angular momentum distribution of the level density [6], [7].
 The isomer-to-ground state ratio lends insight into equilibrium / pre-equilibrium nature of reactions in this energy region, useful when attempting to minimize dose from an unwanted isomer/ground state of a medical radionuclide.
@@
 \end{table}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
 Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-% \label{tab:cufe_rp_table}
-% \small
-% % \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllll@{}}
-% \toprule
-%                             & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-% E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-% % \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
-% % \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
-% % \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
-% % \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
-% % \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
-% % \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
-% % \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
-% % \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
-% % \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
-% % \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
-% \ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
-% \end{tabular}
-% % }
-% \end{table}
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work.
+\label{tab:cufe_rp_table}
+\small
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllllllllllll@{}}
+\toprule
+                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
+E$_\text{p}$ (MeV)&	\makecell{53.04\\$\pm$0.61} &	\makecell{46.18\\$\pm$0.68} &	\makecell{38.42\\$\pm$0.79} &	\makecell{34.06\\$\pm$0.86} &	\makecell{29.21\\$\pm$0.97} &	\makecell{23.6\\$\pm$1.2} &	\makecell{21.70\\$\pm$0.33} &	\makecell{18.30\\$\pm$0.38} &	\makecell{16.6\\$\pm$1.5} &	\makecell{15.38\\$\pm$0.44} &	\makecell{13.11\\$\pm$0.49} &	\makecell{10.57\\$\pm$0.57} &	\makecell{6.90\\$\pm$0.82} &	\makecell{1.4\\$\pm$1.0}\\ \midrule
+\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{2.048\\$\pm$0.072} &	\makecell{0.408\\$\pm$0.012} &	\makecell{0.0931\\$\pm$0.0034} &	\makecell{0.0517\\$\pm$0.0017} &	\makecell{0.02233\\$\pm$0.00075} &	\makecell{0.01848\\$\pm$0.00065} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{57}Ni}\,($\sigma_c$)&	\makecell{2.107\\$\pm$0.094} &	\makecell{0.738\\$\pm$0.024} &	\makecell{0.0530\\$\pm$0.0033} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{57}Co}\,($\sigma_i$)&	\makecell{48.8\\$\pm$2.2} &	\makecell{32.2\\$\pm$1.5} &	\makecell{3.79\\$\pm$0.37} &	\makecell{1.206\\$\pm$0.046} &	\makecell{1.673\\$\pm$0.063} &	\makecell{1.053\\$\pm$0.046} &	\makecell{0.707\\$\pm$0.033} &	\makecell{0.264\\$\pm$0.025} &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{57}Co}\,($\sigma_c$)&	\makecell{50.9\\$\pm$2.2} &	\makecell{33.0\\$\pm$1.5} &	\makecell{3.84\\$\pm$0.37} &	\makecell{1.206\\$\pm$0.046} &	\makecell{1.673\\$\pm$0.063} &	\makecell{1.053\\$\pm$0.046} &	\makecell{0.707\\$\pm$0.033} &	\makecell{0.264\\$\pm$0.025} &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{60}Co}\,($\sigma_c$)&	\makecell{9.22\\$\pm$0.33} &	\makecell{7.70\\$\pm$0.25} &	\makecell{6.14\\$\pm$0.23} &	\makecell{3.12\\$\pm$0.13} &	\makecell{0.794\\$\pm$0.043} &	\makecell{0.201\\$\pm$0.014} &	\makecell{0.1252\\$\pm$0.0086} &	\makecell{0.0199\\$\pm$0.0020} &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{60}Cu}\,($\sigma_c$)&	\makecell{24.84\\$\pm$0.89} &	\makecell{16.06\\$\pm$0.52} &	\makecell{1.461\\$\pm$0.095} &	\makecell{0.578\\$\pm$0.021} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{61}Co}\,($\sigma_c$)&	\makecell{4.18\\$\pm$0.49} &	\makecell{5.69\\$\pm$0.57} &	\makecell{6.94\\$\pm$0.49} &	\makecell{6.61\\$\pm$0.60} &	\makecell{5.94\\$\pm$0.76} &	\makecell{0.872\\$\pm$0.067} &	\makecell{0.2531\\$\pm$0.0085} &	\makecell{0.1178\\$\pm$0.0043} &	\makecell{0.0411\\$\pm$0.0024} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{61}Cu}\,($\sigma_c$)&	\makecell{78\\$\pm$78} &	\makecell{101\\$\pm$101} &	\makecell{161\\$\pm$161} &	\makecell{155\\$\pm$155} &	\makecell{104\\$\pm$104} &	\makecell{7.0\\$\pm$7.0} &	\makecell{1.8\\$\pm$1.8} &	\makecell{1.2\\$\pm$1.2} &	\makecell{0.80\\$\pm$0.80} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{64}Cu}\,($\sigma_i$)&	\makecell{49.9\\$\pm$1.8} &	\makecell{52.7\\$\pm$1.8} &	\makecell{58.4\\$\pm$2.1} &	\makecell{62.4\\$\pm$2.2} &	\makecell{101.8\\$\pm$3.7} &	\makecell{145\\$\pm$11} &	\makecell{83.1\\$\pm$2.8} &	\makecell{57.0\\$\pm$1.9} &	\makecell{45.9\\$\pm$2.0} &	\makecell{22.15\\$\pm$0.92} &	-- &	-- &	-- &	--\\ \bottomrule
+\end{tabular}
+}
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work.
 Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-% \label{tab:ti_rp_table}
-% \small
-% % Disable next line for journal submission
-% % \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllll@{}}
-% \toprule
-%                             & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7}
-% E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% % \ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
-% % \ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
-% % \ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
-% % \ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
-% % \ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
-% % \ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
-% % \ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% % \ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
-% % \ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
-% % \ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
-% % \ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
-% % \ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
-% \ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
-% \end{tabular}
-% % }
-% \end{table}
-% 
-% 
-% 
-% 
-% 
-% 
-% % Please add the following required packages to your document preamble:
-% % \usepackage{booktabs}
-% \begin{table}
-% \centering
-% \caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
-% \label{tab:fe_ibr_table}
-% \small
-% \resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllll@{}}
-% \toprule
-%                                & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7}
-% E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-% \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\
-% E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
-% \ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
-% \ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
-% \ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
-% \end{tabular}
-% }
-% \end{table}
+\label{tab:ti_rp_table}
+\small
+% Disable next line for journal submission
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllllllllllll@{}}
+\toprule
+                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
+E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\  \midrule
+\ce{^{43}K}\,($\sigma_c$)&	\makecell{1.549\\$\pm$0.080} &	\makecell{0.889\\$\pm$0.056} &	\makecell{0.189\\$\pm$0.014} &	\makecell{0.0462\\$\pm$0.0035} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{44g}Sc}\,($\sigma_i$)&	\makecell{25.0\\$\pm$2.0} &	\makecell{27.0\\$\pm$1.9} &	\makecell{37.0\\$\pm$2.3} &	\makecell{52.6\\$\pm$3.9} &	\makecell{47.8\\$\pm$2.9} &	\makecell{29.9\\$\pm$2.6} &	\makecell{8.09\\$\pm$0.27} &	\makecell{3.49\\$\pm$0.13} &	\makecell{2.70\\$\pm$0.27} &	\makecell{3.02\\$\pm$0.12} &	\makecell{2.49\\$\pm$0.11} &	-- &	-- &	--\\
+\ce{^{44m}Sc}\,($\sigma_i$)&	\makecell{12.60\\$\pm$0.41} &	\makecell{12.37\\$\pm$0.36} &	\makecell{15.20\\$\pm$0.52} &	\makecell{17.78\\$\pm$0.57} &	\makecell{16.85\\$\pm$0.55} &	\makecell{8.63\\$\pm$0.30} &	\makecell{4.26\\$\pm$0.15} &	\makecell{1.451\\$\pm$0.051} &	\makecell{1.317\\$\pm$0.052} &	\makecell{1.269\\$\pm$0.049} &	\makecell{0.839\\$\pm$0.036} &	-- &	-- &	--\\
+\ce{^{44}Sc}\,($\sigma_c$)&	\makecell{37.6\\$\pm$2.1} &	\makecell{39.4\\$\pm$1.9} &	\makecell{52.2\\$\pm$2.3} &	\makecell{70.4\\$\pm$3.9} &	\makecell{64.7\\$\pm$3.0} &	\makecell{38.6\\$\pm$2.7} &	\makecell{12.35\\$\pm$0.31} &	\makecell{4.94\\$\pm$0.14} &	\makecell{4.02\\$\pm$0.27} &	\makecell{4.29\\$\pm$0.13} &	\makecell{3.33\\$\pm$0.11} &	-- &	-- &	--\\
+\ce{^{47}Sc}\,($\sigma_c$)&	\makecell{21.20\\$\pm$0.68} &	\makecell{20.45\\$\pm$0.57} &	\makecell{21.66\\$\pm$0.76} &	\makecell{23.55\\$\pm$0.75} &	\makecell{25.12\\$\pm$0.84} &	\makecell{15.63\\$\pm$0.55} &	\makecell{11.53\\$\pm$0.48} &	\makecell{5.50\\$\pm$0.20} &	\makecell{2.75\\$\pm$0.11} &	\makecell{1.569\\$\pm$0.058} &	\makecell{0.810\\$\pm$0.034} &	\makecell{0.361\\$\pm$0.012} &	\makecell{0.218\\$\pm$0.015} &	--\\
+\ce{^{48}Sc}\,($\sigma_i$)&	\makecell{1.66\\$\pm$0.10} &	\makecell{1.68\\$\pm$0.17} &	\makecell{1.29\\$\pm$0.14} &	\makecell{0.772\\$\pm$0.051} &	\makecell{0.700\\$\pm$0.052} &	\makecell{0.339\\$\pm$0.020} &	\makecell{0.318\\$\pm$0.011} &	\makecell{0.1852\\$\pm$0.0095} &	\makecell{0.135\\$\pm$0.012} &	\makecell{0.0625\\$\pm$0.0037} &	-- &	-- &	-- &	--\\ \bottomrule
+\end{tabular}
+}
+\end{table}
+
+% \ce{^{nat}Cu}(p,x)\ce{^{52}Mn}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}
+\centering
+\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x) and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
+\label{tab:fe_ibr_table}
+\small
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllllllllllllll@{}}
+\toprule
+                               & \multicolumn{14}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-15}
+E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\ \midrule
+\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.022} &	\makecell{0.414\\$\pm$0.024} &	\makecell{0.396\\$\pm$0.026} &	\makecell{0.388\\$\pm$0.021} &	\makecell{0.517\\$\pm$0.026} &	\makecell{0.420\\$\pm$0.025} &	\makecell{0.358\\$\pm$0.018} &	\makecell{0.202\\$\pm$0.010} &	\makecell{0.404\\$\pm$0.043} &	\makecell{0.638\\$\pm$0.043} &	\makecell{0.915\\$\pm$0.073} &	-- &	-- &	--\\
+\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.017} &	\makecell{0.387\\$\pm$0.020} &	\makecell{0.485\\$\pm$0.025} &	\makecell{0.583\\$\pm$0.033} &	\makecell{0.614\\$\pm$0.034} &	\makecell{0.420\\$\pm$0.026} &	\makecell{0.486\\$\pm$0.036} &	\makecell{0.341\\$\pm$0.024} &	\makecell{0.299\\$\pm$0.016} &	\makecell{0.234\\$\pm$0.015} &	\makecell{0.214\\$\pm$0.029}         \vspace{1em}     \\
+E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\ \midrule
+\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.022} &	\makecell{0.314\\$\pm$0.018} &	\makecell{0.291\\$\pm$0.016} &	\makecell{0.253\\$\pm$0.016} &	\makecell{0.260\\$\pm$0.015} &	\makecell{0.224\\$\pm$0.017} &	\makecell{0.345\\$\pm$0.015} &	\makecell{0.294\\$\pm$0.013} &	\makecell{0.328\\$\pm$0.026} &	\makecell{0.296\\$\pm$0.015} &	\makecell{0.252\\$\pm$0.014} &	-- &	-- &	--\\\bottomrule
+\end{tabular}
+}
+\end{table}
 % 

### 2019-01-05 fe_px_paper/fe_body_text.tex
Added in XS plots to appendix

@@
 The   lifetimes and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
-% \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.
+\cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
 Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database  \cite{berger2011xcom}.
@@
 
-Using the final proton fluence at each energy position, cross sections for  \textred{(list of residual products)} were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils in the \textred{0--55\,MeV} region, as recorded in \autoref{tab:fe_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Cu} foils, the (p,x) cross sections for  \textred{(list of residual products)} were extracted, as recorded in \autoref{tab:cufe_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Ti} foils, the (p,x) cross sections for  \textred{(list of residual products)} were extracted, as recorded in \autoref{tab:ti_rp_table}.
-In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \textred{\ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb}} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
+Using the final proton fluence at each energy position, cross sections for \ce{^{48}Cr}, \ce{^{48}V},  \ce{^{49}Cr}, \ce{^{51}Mn}, \ce{^{51}Cr},  \ce{^{52}Fe}, \ce{^{52m}Mn}, \ce{^{52g}Mn}, \ce{^{52}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Mn}, \ce{^{56}Co}, \ce{^{57}Co}, \ce{^{58m}Co}, \ce{^{58g}Co}, and \ce{^{58}Co}
+ were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{60}Co}, \ce{^{60}Cu}, \ce{^{61}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K}, \ce{^{44g}Sc}, \ce{^{44m}Sc}, \ce{^{44}Sc}, \ce{^{47}Sc}, and \ce{^{48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
+In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity \textred{($\pm$3--7\%), proton fluence ($\pm$4--6\%), and foil areal density ($\pm$0.1--0.6\%).}
-% \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).
 
@@
 \end{table}
+
+\textred{Placeholder text follows...fill in actual discussion of results...}
+
+% lee:
 % 
-% 
-% 
-% \textred{Placeholder text follows...fill in actual discussion of results...}
-% 
-% % lee:
-% % 
-% % In addition to the interest in the production of 51,52 Mn for PET research, this experiment offered
-% % an opportunity to study the distribution of angular momentum in compound nuclear and direct
-% % pre-equilibrium reactions via observation of the 52g Mn (t ½ =5.591±0.003 d; J π =6 + ) to 52m Mn
-% % (t ½ =21.1±0.2 m; J π =2 + ) ratio. These results indicated were presented at the University of Oslo in
-% % May 2017 5 and indicate that the constant
-% % temperature nuclear level density model
-% % which has had the greatest success at
-% % reproducing most low-energy nuclear
-% % reaction data fails to reproduce the
-% % deposition of angular momentum at both
-% % compound and pre-compound energies
-% % (see figure 3). This result will be
-% % discussed in greater detail in Mr. Andrew
-% % Voyles’ doctoral dissertation, which is
-% % expected to be completed by May 2018.
-% 
-% 
-% 
-% These results have several notable features.
-% The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
-% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
-% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
-% 
-% 
-% 
-% % Furthermore, t
-% This work presents the first measurements of several observables in 
-% % these mass regions.
-% % This work reports the first experimental measurement of
-% this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
-% % It also represents  the first measurement of 
-% the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
-% The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
-% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
-% % (${^{1}/_{2}}^{-}$)
-% % ($\sfrac{1}{2}^-$) 
-% isomer branching ratio via \ce{^{nat}Nb}(p,x).
-% 
-% 
-% \textred{Comment on details of 51/52Mn production here...}
-% 
-% 
-% Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
-% This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
-% % The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
-% \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
-% % , which makes activity quantification trivial.
-% % In addition, 
-% \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-% Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
-% Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
-% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
-% 
-% 
-% 
-% \textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
-% 
-% 
-% 
-% In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-% These include the non-standard positron emitters 
-% \ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
-% \ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
-% \ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
-% \ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
-% % the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-% and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
-% Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
-% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
-% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
-% 
-% 
-% 
-% 
+% In addition to the interest in the production of 51,52 Mn for PET research, this experiment offered
+% an opportunity to study the distribution of angular momentum in compound nuclear and direct
+% pre-equilibrium reactions via observation of the 52g Mn (t ½ =5.591±0.003 d; J π =6 + ) to 52m Mn
+% (t ½ =21.1±0.2 m; J π =2 + ) ratio. These results indicated were presented at the University of Oslo in
+% May 2017 5 and indicate that the constant
+% temperature nuclear level density model
+% which has had the greatest success at
+% reproducing most low-energy nuclear
+% reaction data fails to reproduce the
+% deposition of angular momentum at both
+% compound and pre-compound energies
+% (see figure 3). This result will be
+% discussed in greater detail in Mr. Andrew
+% Voyles’ doctoral dissertation, which is
+% expected to be completed by May 2018.
+
+These results have several notable features.
+The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
+Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
+Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
+Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
+
+% Furthermore, t
+This work presents the first measurements of several observables in 
+% these mass regions.
+% This work reports the first experimental measurement of
+this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
+% It also represents  the first measurement of 
+the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
+The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
+Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
+% (${^{1}/_{2}}^{-}$)
+% ($\sfrac{1}{2}^-$) 
+isomer branching ratio via \ce{^{nat}Nb}(p,x).
+
+\textred{Comment on details of 51/52Mn production here...}
+
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
+This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
+% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
+\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
+% , which makes activity quantification trivial.
+% In addition, 
+\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
+Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
+Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
+This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
+
+\textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
+
+In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
+These include the non-standard positron emitters 
+\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
+\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
+% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
+and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
+Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
+The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
+This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+
 % \subsection{Comparison of reaction modeling with experimental results}
@@
 
-%  \section{\label{sec:conclusions_fe}Conclusions}
-%  
-% 
-% We present here a set of measurements of \textred{38} cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of \textred{five} isomer branching ratios.
+ \section{\label{sec:conclusions_fe}Conclusions}
+
+We present here a set of measurements of 34 cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of three isomer branching ratios.
+Nearly all cross sections have been reported with higher precision than previous measurements.
+\textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
+% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
+Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
+
+% We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
 % Nearly all cross sections have been reported with higher precision than previous measurements.
-% \textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
-% % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for V \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
+% We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
+% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
 % Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
-% 
-% 
-% % We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
-% % Nearly all cross sections have been reported with higher precision than previous measurements.
-% % We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
-% % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-% % We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-% % Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
 

### 2019-01-05 fe_px_paper/fe_body_text.tex
Added 51,52Mn plots to placeholder modeling section

@@
 
-% \subsection{Comparison of reaction modeling with experimental results}
+\subsection{Comparison of reaction modeling with experimental results}
+
+Quick observations:
+
+\begin{enumerate}
+ \item Modeling on Fe is significantly better than for Cu/Ti
+ \item On the whole, ALICE seems to do the best job overall
+ \item (p,$\alpha$x) channels are done fairly well, (p,2p2nx) are worse, and (p,$\alpha$xn) are really lousy
+ \item Location and shape of rising edges/compound peaks appears much better than in the Nb IPF paper, possibly due to easier modeling in lower energy regime?
+ \item Amplitudes of excitation function are still off within factor of 2--3
+ \item Isomer branching ratios are (surprise, surprise) really bad.  Ti(p,x)\ce{^{44}Sc} is the best, but all three miss the key shape and features
+\end{enumerate}
+
+\textred{PLACEHOLDER TEXT -- }
+
+\textred{Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Suspendisse urna diam, bibendum eu venenatis sit amet, vulputate in mi.
+Sed elit ex, aliquet in pharetra efficitur, mattis vel odio.
+Donec a augue lectus.
+Vestibulum fermentum rutrum justo, non imperdiet risus iaculis vitae.
+Aliquam non quam nec dui scelerisque bibendum rhoncus sed tellus.
+Aenean fermentum ullamcorper turpis, et gravida diam feugiat a.
+Nam nec dignissim massa.
+Morbi ultrices at neque in eleifend.
+Duis non lobortis ipsum, sit amet lobortis nisl.
+In ultrices posuere volutpat.
+Nunc mattis libero porttitor tortor mollis, nec tincidunt lacus sollicitudin.
+Sed vulputate at justo quis sodales.
+Nulla risus lorem, pellentesque a mauris ornare, varius maximus nulla.
+Aliquam tempus blandit ex.
+Suspendisse quis imperdiet sapien, nec egestas magna.
+Nam eu molestie nibh.}
 % 
@@
 % All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-% 
-% 
-% % \def\arraystretch{1.5}
-% \begin{table}
-%  \caption{Default settings for the reactions codes}
-%  \label{tab:fe_defaults}
-%  \resizebox{\textwidth}{!}{%
-% \begin{tabular}{ c c c c}
-% 
-%  \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
-%  EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
-%  TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-%   CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}
-%   
-% \end{tabular}
-% }
-% \end{table}
-% 
+
+% \def\arraystretch{1.5}
+\begin{table}
+ \caption{Default settings for the reactions codes}
+ \label{tab:fe_defaults}
+ \resizebox{\textwidth}{!}{%
+\begin{tabular}{ c c c c}
+
+ \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
+ EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
+ TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
+  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
+  ALICE-2017\cite{Blann1996}     &   \textred{?????}    &   \textred{?????}    &   \textred{?????}
+
+\end{tabular}
+}
+\end{table}
+
 % % The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
@@
 % EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
-% 
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\linewidth]{./figures/51Mn_px.pdf}
-%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
-%  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{86}Y} cross section, with the \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel visibly peaking at approximately \mbox{70 MeV}.}
-%  \label{fig:51Mn}
-% \end{figure}
-% 
-% 
-% 
-% 
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\linewidth]{./figures/90Mo.pdf}
-%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
-%  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Mo} cross section, with the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
-%  \label{fig:temp_90Mo}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\linewidth]{./figures/90Nb.pdf}
-%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
-%  \caption{Measured \ce{^{93}Nb}(p,x)\ce{^{90}Nb} cross section, with the \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} reaction channel visibly peaking at approximately \mbox{50 MeV}.}
-%  \label{fig:temp_90Nb}
-% \end{figure}
-% 
-% 
-% 
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
+ \label{fig:51Mn}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/52mMn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+ \label{fig:temp_52mMn}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+ \label{fig:temp_52Mn}
+\end{figure}
+
 % 

### 2019-01-07 fe_px_paper/fe_body_text.tex
Added discussion of possible Fe monitor reactions

@@
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).
 
@@
 
-\textred{Placeholder text follows...fill in actual discussion of results...}
+% \textred{Placeholder text follows...fill in actual discussion of results...}
 
@@
 These results have several notable features.
-The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
-Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
-Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
-Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
+The various \ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
+While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
+Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
+% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the
+reactions presented here.
+% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
+% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
 
@@
 % This work reports the first experimental measurement of
-this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
+this mass region, including the \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region,
 % It also represents  the first measurement of 
-the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
-The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
-Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
+the independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
+The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr},\ce{^{52g}Mn},\ce{^{58g}Co} cross sections.
+% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
 % (${^{1}/_{2}}^{-}$)
 % ($\sfrac{1}{2}^-$) 
-isomer branching ratio via \ce{^{nat}Nb}(p,x).
+% isomer branching ratio via \ce{^{nat}Nb}(p,x).
+
+% \textred{Comment on possible monitor reactions  here...}
+
+Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
+In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe} \cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and lifetime.
+Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr} \cite{Dong2014}) has a convenient lifetime and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
+This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
 

### 2019-01-07 fe_px_paper/fe_body_text.tex
Added discussion of isotope production

@@
 
-\textred{Comment on details of 51/52Mn production here...}
+\textred{All: feel free to add additional details of 51/52Mn production here...}
 
-Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
-This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reaction below 70\,MeV to date, with cross sections measured  at the 4--9\% uncertainty level.
+This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr \cite{Klein2000}.
+However, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for clean production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
+In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house of this short-lived ($t_{1/2}=46.2\pm0.1$ m \cite{Wang2017}) radionuclide.
+To increase yields, an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons.
+
+Likewise, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
+Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%) \cite{Graves2015,Wooten2015}.
+\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
+Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn}, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
+It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d \cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m \cite{Dong2015}) can be easily separated through the difference in lifetime, to avoid the unfavorable gammas produced by the isomer.
+However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$\pm$0.008\,h \cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator.
+Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
+
+% step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
 % The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
-\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
+% \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
 % , which makes activity quantification trivial.
 % In addition, 
-\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
-Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
-Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
-This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
+% \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
+% Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
+% Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
+% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.
 
-\textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
+% \textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
 
-In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
+In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
 These include the non-standard positron emitters 
-\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
-\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009},
-\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
-\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
+\ce{^{44}Sc} \cite{Muller2013,Filosofov2010,Qaim2011}
+% \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
+\ce{^{55}Co} \cite{Thisgaard2011,Zaman1996,Hermanne2000a}
+\ce{^{61}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+\ce{^{61}Cu} \cite{Szelecsenyi2005a,Fukumura2004}
+\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
+% \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
+% \ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+% \ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
 % the $\beta^-$-therapy agent  \ce{^{64}Cu},  
-and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
-Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x).
-The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
-This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+and the $\beta^-$-therapeutic agent 
+\ce{^{47}Sc} \cite{Muller2014,Deilami-nezhad2016}.
+% and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
+Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x).
+% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
+% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
 

### 2019-01-08 fe_px_paper/fe_body_text.tex
Updated abstract and conclusion. Sending to co-authors for revision

@@
 % Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
+Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work \cite{Voyles2018a}.
+No cross sections are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
 
@@
 Nearly all cross sections have been reported with higher precision than previous measurements.
-\textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
+We report the first measurements  for $\leq$70\,MeV protons  of the  \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions, as well as the first measurement of the independent cross sections for    \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
 % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
@@
 Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
-
-% We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
-% Nearly all cross sections have been reported with higher precision than previous measurements.
-% We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
-% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
-% Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
 

### 2019-01-11 fe_px_paper/fe_body_text.tex
Merged in Amanda's early edits

@@
 
-The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides \cite{Qaim201731}. 
-The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives \cite{Mulford2005,Muller2014}.
+The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
+The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives\,\cite{Mulford2005,Muller2014}.
 While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production.
@@
 % 
-% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}.
+% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue\,\cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose\,\cite{Muller2014,Bentzen2005,Srivastava2012}.
 % Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.
@@
 % Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
-% \cite{Qaim201731}. 
+%\,\cite{Qaim201731}. 
 % Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
-One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications \cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
-In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET \cite{Graves2016}.
+One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
+In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.
 As part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
 This was carried out in a  thin-foil stacked-target experiment, using proton irradiation of natural iron foils with titanium and copper monitor foils.
-While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons   \cite{Graves2016}.
+While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.
 
-Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element, biologically relevant, and essential in trace quantities. 
-Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH \cite{Graves2015}.
-\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection \cite{Dong2015}.
+Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element that is biologically relevant and essential in trace quantities. 
+Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
+\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection\,\cite{Dong2015}.
 Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}.
-\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging \cite{Graves2015}. 
-However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging \cite{Dong2015}.
-The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$ = 96.6\%, $E_{\beta\text{, avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose  \cite{Dong2015}.
-Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies \cite{Wang2017}.
+\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
+However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
+The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
+Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies\,\cite{Wang2017}.
 \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
-In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications \cite{Wang2017}.
+In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications\,\cite{Wang2017}.
 
@@
 
-While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio \cite{Dong2015,Wang2017}.
-Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
+While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
+Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region\,\cite{PhysRevC.73.034613,PhysRevC.45.1171}.
 These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes.
@@
 % for the measurement of cross sections in stacked target irradiations   
-for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018a,Graves2016}.
+for monitor reaction characterization of beam energy and fluence in stacked target irradiations\,\cite{Voyles2018a,Graves2016}.
 % 
@@
 % 
-Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.
+Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here\,\cite{springer2017investigation}.
 
@@
 In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
-% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}.
+% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}.
 % For targets, a
@@
 The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$.
-Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}.
+Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\\,\cite{Graves2016}.
 At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
@@
 The 6061 aluminum degraders have a measured density of approximately 2.69 g/cm$^3$.
-Their areal densities were determined using the variance minimization techniques described  in this work  and our earlier paper \cite{Voyles2018a}.
-% the earlier paper by Graves \etal\ \cite{Graves2016}.
+Their areal densities were determined using the variance minimization techniques described  in this work  and an earlier paper\,\cite{Voyles2018a}.
+% the earlier paper by Graves \etal\\,\cite{Graves2016}.
 A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}
@@
 % An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks \cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma ray spectra \cite{Aarnio2001}.
-% , which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
+For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
+% , which has been shown to perform best in comparisons with other common analysis codes\,\cite{Jackman2014}.
 %, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.
@@
 \cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
-Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database  \cite{berger2011xcom}.
+Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
 % As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
@@
 
-As in our previous work, these activities used to calculate cross sections, and are differentiated between cumulative and independent \cite{Voyles2018a}.
+As in our previous work, these activities are used to calculate cross sections, and are differentiated between cumulative and independent\,\cite{Voyles2018a}.
 For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
@@
 For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
-Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported \cite{bateman1910solution,Cetnar2006}.
+Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported\,\cite{bateman1910solution,Cetnar2006}.
 
@@
 % As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of \ref{sec:fe_data}.
-% In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
+% In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation\,\cite{bateman1910solution,Cetnar2006}:
 % \begin{equation}
@@
 \end{equation}
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 10 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation  \cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 10 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation\,\cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
 
@@
 
-Estimates of the proton beam energy for preliminary stack designs were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-However, the more rigorous  transport code FLUKA-2011.2x.3 was used for simulation of the full 3-D target stack, to determine the full proton energy and fluence distribution for each foil   \cite{Bohlen2014a}.
+Estimates of the proton beam energy for preliminary stack designs were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism\,\cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
+However, the more rigorous  transport code FLUKA-2011.2x.3 was used for simulation of the full 3-D target stack, to determine the full proton energy and fluence distribution for each foil\,\cite{Bohlen2014a}.
 $10^8$ source protons were used for all FLUKA simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
@@
 
-To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, the \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments \cite{Voyles2018a,Graves2016}.
+To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, the \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments\,\cite{Voyles2018a,Graves2016}.
 This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions used in this work should all be consistent at each energy position.
@@
 The uncertainty-weighted mean  for the two \ce{^{nat}Cu}(p,x) and two \ce{^{nat}Ti}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Cu and Ti foils, respectively, and the uncertainty-weighted mean  for all four monitor channels was used to determine the final fluence assignments for the Fe foils.
-Uncertainty in proton fluence  is  calculated by error propagation of the fluence values  at each energy position.
+Uncertainty in each final proton fluence  is  calculated by error propagation of the individual monitor channel fluence values  at each energy position.
 These weighted-mean fluences are  plotted  in \autoref{fig:fe_fluence_plot}, along with the estimated fluence according to both  FLUKA transport 
@@
 After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
-With the exception of a single foil (Cu-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
+With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
 % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
@@
 As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at IPF in the past \cite{Voyles2018a,Graves2016}.
+This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at IPF in the past\,\cite{Voyles2018a,Graves2016}.
 This loss of fluence is due to a combination of 
@@
 
-Using the final proton fluence at each energy position, cross sections for \ce{^{48}Cr}, \ce{^{48}V},  \ce{^{49}Cr}, \ce{^{51}Mn}, \ce{^{51}Cr},  \ce{^{52}Fe}, \ce{^{52m}Mn}, \ce{^{52g}Mn}, \ce{^{52}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Mn}, \ce{^{56}Co}, \ce{^{57}Co}, \ce{^{58m}Co}, \ce{^{58g}Co}, and \ce{^{58}Co}
+Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
  were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{60}Co}, \ce{^{60}Cu}, \ce{^{61}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K}, \ce{^{44g}Sc}, \ce{^{44m}Sc}, \ce{^{44}Sc}, \ce{^{47}Sc}, and \ce{^{48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
 In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
-Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
+Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
 The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllllllllllll@{}}
+% \begin{tabular}{@{}lllllllllllllll@{}}
+\begin{tabular}{@{}ccccccccccccccc@{}}
 \toprule
@@
 \ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.25} &	\makecell{15.69\\$\pm$0.32} &	\makecell{11.78\\$\pm$0.29} &	\makecell{6.15\\$\pm$0.25} &	\makecell{0.475\\$\pm$0.025} &	\makecell{0.68\\$\pm$0.10} &	\makecell{1.060\\$\pm$0.081} &	\makecell{1.967\\$\pm$0.067} &	\makecell{2.10\\$\pm$0.14} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
-\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{64.1\\$\pm$4.0} &	\makecell{75.7\\$\pm$3.3} &	\makecell{56.5\\$\pm$2.5} &	\makecell{27.6\\$\pm$1.3} &	\makecell{3.83\\$\pm$0.44} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.11} &	\makecell{0.150\\$\pm$0.026} &	\makecell{0.067\\$\pm$0.017} &	\makecell{NaN\\$\pm$0.14} &	\makecell{NaN\\$\pm$0.088} &	\makecell{NaN\\$\pm$0.045} &	-- &	--\\
-\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{75.9\\$\pm$4.0} &	\makecell{91.3\\$\pm$3.3} &	\makecell{68.3\\$\pm$2.5} &	\makecell{33.7\\$\pm$1.3} &	\makecell{4.30\\$\pm$0.44} &	\makecell{1.582\\$\pm$0.071} &	\makecell{1.760\\$\pm$0.072} &	\makecell{2.117\\$\pm$0.079} &	\makecell{2.165\\$\pm$0.096} &	\makecell{1.91\\$\pm$0.12} &	\makecell{1.450\\$\pm$0.076} &	\makecell{0.823\\$\pm$0.037} &	-- &	--\\
+\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{64.1\\$\pm$4.0} &	\makecell{75.7\\$\pm$3.3} &	\makecell{56.5\\$\pm$2.5} &	\makecell{27.6\\$\pm$1.3} &	\makecell{3.83\\$\pm$0.44} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.11} &	\makecell{0.150\\$\pm$0.026} &	\makecell{0.067\\$\pm$0.017} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{75.9\\$\pm$4.0} &	\makecell{91.3\\$\pm$3.3} &	\makecell{68.3\\$\pm$2.5} &	\makecell{33.7\\$\pm$1.3} &	\makecell{4.30\\$\pm$0.44} &	\makecell{1.582\\$\pm$0.071} &	\makecell{1.760\\$\pm$0.072} &	\makecell{2.117\\$\pm$0.079} &	\makecell{2.165\\$\pm$0.096} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
 \ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.685\\$\pm$0.092} &	\makecell{1.733\\$\pm$0.063} &	\makecell{1.601\\$\pm$0.057} &	\makecell{2.247\\$\pm$0.078} &	\makecell{0.770\\$\pm$0.029} &	\makecell{0.2059\\$\pm$0.0099} &	\makecell{0.1920\\$\pm$0.0096} &	\makecell{0.01297\\$\pm$0.00046} &	\makecell{0.00240\\$\pm$0.00015} &	-- &	-- &	-- &	-- &	--\\
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllllllllllllll@{}}
+% \begin{tabular}{@{}lllllllllllllll@{}}
+\begin{tabular}{@{}ccccccccccccccc@{}}
 \toprule
                             & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
-E$_\text{p}$ (MeV)&	\makecell{53.04\\$\pm$0.61} &	\makecell{46.18\\$\pm$0.68} &	\makecell{38.42\\$\pm$0.79} &	\makecell{34.06\\$\pm$0.86} &	\makecell{29.21\\$\pm$0.97} &	\makecell{23.6\\$\pm$1.2} &	\makecell{21.70\\$\pm$0.33} &	\makecell{18.30\\$\pm$0.38} &	\makecell{16.6\\$\pm$1.5} &	\makecell{15.38\\$\pm$0.44} &	\makecell{13.11\\$\pm$0.49} &	\makecell{10.57\\$\pm$0.57} &	\makecell{6.90\\$\pm$0.82} &	\makecell{1.4\\$\pm$1.0}\\ \midrule
+E$_\text{p}$ (MeV)&	\makecell{53.04\\$\pm$0.61} &	\makecell{46.18\\$\pm$0.68} &	\makecell{38.42\\$\pm$0.79} &	\makecell{34.06\\$\pm$0.86} &	\makecell{29.21\\$\pm$0.97} &	\makecell{23.6\\$\pm$1.2} &	\makecell{21.70\\$\pm$0.33} &	\makecell{18.30\\$\pm$0.38} &	\makecell{16.6\\$\pm$1.5} &	\makecell{15.38\\$\pm$0.44} &	\makecell{13.11\\$\pm$0.49} &	\makecell{10.57\\$\pm$0.57} &	\makecell{6.90\\$\pm$0.82} &	\makecell{1.4\\$\pm$1.3}\\ \midrule
 \ce{^{54}Mn}\,($\sigma_i$)&	\makecell{2.048\\$\pm$0.072} &	\makecell{0.408\\$\pm$0.012} &	\makecell{0.0931\\$\pm$0.0034} &	\makecell{0.0517\\$\pm$0.0017} &	\makecell{0.02233\\$\pm$0.00075} &	\makecell{0.01848\\$\pm$0.00065} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
@@
 % Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
-Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work \cite{Voyles2018a}.
-No cross sections are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
+Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work\,\cite{Voyles2018a}.
+No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
 
@@
 Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
-In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe} \cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
 It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and lifetime.
-Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr} \cite{Dong2014}) has a convenient lifetime and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
+Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient lifetime and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
 This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
@@
 This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
-\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr \cite{Klein2000}.
-However, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for clean production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
-In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house of this short-lived ($t_{1/2}=46.2\pm0.1$ m \cite{Wang2017}) radionuclide.
-To increase yields, an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons.
+\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr\,\cite{Klein2000}.
+% However, 
+\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for clean production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
+In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house production of this short-lived ($t_{1/2}=46.2\pm0.1$ m\,\cite{Wang2017}) radionuclide.
+To increase yields over \ce{^{nat}Fe}(p,x), an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons, without opening the additional manganese exit channels accessible on a natural target.
 
 Likewise, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
-Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%) \cite{Graves2015,Wooten2015}.
+Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%)\,\cite{Graves2015,Wooten2015}.
 \ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
 Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn}, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
-It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d \cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m \cite{Dong2015}) can be easily separated through the difference in lifetime, to avoid the unfavorable gammas produced by the isomer.
-However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$\pm$0.008\,h \cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator.
+It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in lifetime, to avoid the unfavorable gammas produced by the isomer.
+However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$\pm$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator.
 Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
@@
 These include the non-standard positron emitters 
-\ce{^{44}Sc} \cite{Muller2013,Filosofov2010,Qaim2011}
-% \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-\ce{^{55}Co} \cite{Thisgaard2011,Zaman1996,Hermanne2000a}
-\ce{^{61}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
-\ce{^{61}Cu} \cite{Szelecsenyi2005a,Fukumura2004}
-\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
-% \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
-% \ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
-% \ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
+\ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
+%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
+\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}
+\ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+\ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
+\ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
+% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
+% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
 % the $\beta^-$-therapy agent  \ce{^{64}Cu},  
 and the $\beta^-$-therapeutic agent 
-\ce{^{47}Sc} \cite{Muller2014,Deilami-nezhad2016}.
-% and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
+\ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
+% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
 Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x).
-% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
-% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.
+% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co}\,\cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
+% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
 
@@
 % The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
-% % \cite{add_level_density_models_here}. 
-% The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
-% % \cite{add_level_density_models_here}.
+% %\,\cite{add_level_density_models_here}. 
+% The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it\,\cite{Capote2009}.
+% %\,\cite{add_level_density_models_here}.
 % The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
@@
 % The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70\,MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
-% The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.} \cite{MICHEL1997153}. 
+% The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.}\,\cite{MICHEL1997153}. 
 % The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50\,MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
-% In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011 \cite{Titarenko2011}.
+% In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011\,\cite{Titarenko2011}.
 % 
@@
 % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
-We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
-Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
+We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,MeV for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
+Finally, this work provides another example of the current issues with modeling of  stopping power in stacked target charged particle irradiation experiments, corrected using variance minimization techniques.
+% usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
 

### 2019-05-28 fe_px_paper/fe_body_text.tex
Updated text and figures using the corrected statistical uncertainty analysis

@@
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$4--9\%), and foil areal density ($\pm$0.1--0.3\%).
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
 
@@
 E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\  \midrule
-\ce{^{48}Cr}\,($\sigma_c$)&	\makecell{0.1684\\$\pm$0.0064} &	\makecell{0.01310\\$\pm$0.00044} &	\makecell{0.00435\\$\pm$0.00018} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{48}V}\,($\sigma_i$)&	\makecell{6.25\\$\pm$0.28} &	\makecell{4.41\\$\pm$0.17} &	\makecell{0.513\\$\pm$0.021} &	\makecell{0.1096\\$\pm$0.0052} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{48}V}\,($\sigma_c$)&	\makecell{6.42\\$\pm$0.28} &	\makecell{4.43\\$\pm$0.17} &	\makecell{0.517\\$\pm$0.021} &	\makecell{0.1096\\$\pm$0.0052} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{49}Cr}\,($\sigma_c$)&	\makecell{1.794\\$\pm$0.071} &	\makecell{2.14\\$\pm$0.13} &	\makecell{1.197\\$\pm$0.085} &	\makecell{0.315\\$\pm$0.032} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.25} &	\makecell{15.69\\$\pm$0.32} &	\makecell{11.78\\$\pm$0.29} &	\makecell{6.15\\$\pm$0.25} &	\makecell{0.475\\$\pm$0.025} &	\makecell{0.68\\$\pm$0.10} &	\makecell{1.060\\$\pm$0.081} &	\makecell{1.967\\$\pm$0.067} &	\makecell{2.10\\$\pm$0.14} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
-\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{64.1\\$\pm$4.0} &	\makecell{75.7\\$\pm$3.3} &	\makecell{56.5\\$\pm$2.5} &	\makecell{27.6\\$\pm$1.3} &	\makecell{3.83\\$\pm$0.44} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.11} &	\makecell{0.150\\$\pm$0.026} &	\makecell{0.067\\$\pm$0.017} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{75.9\\$\pm$4.0} &	\makecell{91.3\\$\pm$3.3} &	\makecell{68.3\\$\pm$2.5} &	\makecell{33.7\\$\pm$1.3} &	\makecell{4.30\\$\pm$0.44} &	\makecell{1.582\\$\pm$0.071} &	\makecell{1.760\\$\pm$0.072} &	\makecell{2.117\\$\pm$0.079} &	\makecell{2.165\\$\pm$0.096} &	\makecell{1.981\\$\pm$0.063} &	\makecell{1.456\\$\pm$0.044} &	\makecell{0.584\\$\pm$0.025} &	-- &	--\\
-\ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.685\\$\pm$0.092} &	\makecell{1.733\\$\pm$0.063} &	\makecell{1.601\\$\pm$0.057} &	\makecell{2.247\\$\pm$0.078} &	\makecell{0.770\\$\pm$0.029} &	\makecell{0.2059\\$\pm$0.0099} &	\makecell{0.1920\\$\pm$0.0096} &	\makecell{0.01297\\$\pm$0.00046} &	\makecell{0.00240\\$\pm$0.00015} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{52m}Mn}\,($\sigma_i$)&	\makecell{8.13\\$\pm$0.28} &	\makecell{9.04\\$\pm$0.28} &	\makecell{13.69\\$\pm$0.47} &	\makecell{17.86\\$\pm$0.61} &	\makecell{23.34\\$\pm$0.79} &	\makecell{11.82\\$\pm$0.41} &	\makecell{5.78\\$\pm$0.19} &	\makecell{0.0763\\$\pm$0.0026} &	\makecell{0.0756\\$\pm$0.0033} &	\makecell{0.0754\\$\pm$0.0032} &	\makecell{0.0585\\$\pm$0.0026} &	-- &	-- &	--\\
-\ce{^{52g}Mn}\,($\sigma_i$)&	\makecell{11.36\\$\pm$0.39} &	\makecell{12.82\\$\pm$0.39} &	\makecell{20.85\\$\pm$0.74} &	\makecell{28.16\\$\pm$0.98} &	\makecell{21.81\\$\pm$0.75} &	\makecell{16.32\\$\pm$0.58} &	\makecell{10.37\\$\pm$0.43} &	\makecell{0.300\\$\pm$0.011} &	\makecell{0.1113\\$\pm$0.0049} &	\makecell{0.0428\\$\pm$0.0024} &	\makecell{0.00540\\$\pm$0.00029} &	-- &	-- &	--\\
-\ce{^{52}Mn}\,($\sigma_c$)&	\makecell{13.39\\$\pm$0.54} &	\makecell{14.88\\$\pm$0.74} &	\makecell{23.0\\$\pm$1.3} &	\makecell{30.9\\$\pm$1.3} &	\makecell{31.7\\$\pm$1.2} &	\makecell{18.54\\$\pm$0.87} &	\makecell{10.57\\$\pm$0.38} &	\makecell{0.313\\$\pm$0.012} &	\makecell{0.0389\\$\pm$0.0038} &	\makecell{0.0556\\$\pm$0.0029} &	\makecell{0.0185\\$\pm$0.0012} &	-- &	-- &	--\\
-\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{128.4\\$\pm$5.0} &	\makecell{154.4\\$\pm$6.2} &	\makecell{166.7\\$\pm$7.6} &	\makecell{129.2\\$\pm$7.4} &	\makecell{42.2\\$\pm$2.4} &	\makecell{2.46\\$\pm$0.22} &	\makecell{1.10\\$\pm$0.11} &	\makecell{1.09\\$\pm$0.13} &	\makecell{1.46\\$\pm$0.14} &	\makecell{1.53\\$\pm$0.12} &	\makecell{1.362\\$\pm$0.069} &	\makecell{1.173\\$\pm$0.055} &	\makecell{0.767\\$\pm$0.033} &	\makecell{0.0500\\$\pm$0.0046}\\
-\ce{^{55}Co}\,($\sigma_i$)&	\makecell{9.25\\$\pm$0.38} &	\makecell{11.89\\$\pm$0.77} &	\makecell{15.72\\$\pm$0.80} &	\makecell{21.46\\$\pm$0.87} &	\makecell{48.4\\$\pm$2.3} &	\makecell{64.7\\$\pm$4.5} &	\makecell{61.0\\$\pm$3.5} &	\makecell{43.6\\$\pm$2.2} &	\makecell{33.2\\$\pm$2.6} &	\makecell{13.42\\$\pm$0.71} &	\makecell{0.377\\$\pm$0.021} &	\makecell{0.0436\\$\pm$0.0020} &	-- &	--\\
-\ce{^{56}Mn}\,($\sigma_c$)&	-- &	\makecell{0.494\\$\pm$0.029} &	\makecell{0.610\\$\pm$0.030} &	\makecell{0.462\\$\pm$0.037} &	\makecell{0.506\\$\pm$0.046} &	\makecell{0.405\\$\pm$0.025} &	\makecell{0.2227\\$\pm$0.0079} &	\makecell{0.0962\\$\pm$0.0035} &	\makecell{0.0326\\$\pm$0.0037} &	\makecell{0.0253\\$\pm$0.0011} &	\makecell{0.01318\\$\pm$0.00093} &	-- &	-- &	--\\
-\ce{^{56}Co}\,($\sigma_i$)&	\makecell{12.74\\$\pm$0.81} &	\makecell{15.5\\$\pm$1.1} &	\makecell{18.9\\$\pm$1.2} &	\makecell{23.6\\$\pm$1.1} &	\makecell{29.2\\$\pm$2.0} &	\makecell{47.8\\$\pm$2.0} &	\makecell{51.6\\$\pm$1.9} &	\makecell{82.6\\$\pm$3.2} &	\makecell{174.3\\$\pm$8.0} &	\makecell{197.3\\$\pm$8.4} &	\makecell{344\\$\pm$15} &	\makecell{389\\$\pm$15} &	\makecell{296\\$\pm$13} &	\makecell{2.95\\$\pm$0.28}\\
-\ce{^{57}Co}\,($\sigma_i$)&	-- &	\makecell{0.454\\$\pm$0.040} &	\makecell{0.539\\$\pm$0.052} &	\makecell{0.648\\$\pm$0.027} &	\makecell{1.170\\$\pm$0.060} &	\makecell{1.836\\$\pm$0.070} &	\makecell{2.359\\$\pm$0.086} &	\makecell{2.50\\$\pm$0.11} &	\makecell{3.17\\$\pm$0.15} &	\makecell{3.40\\$\pm$0.15} &	\makecell{5.14\\$\pm$0.26} &	\makecell{8.46\\$\pm$0.31} &	\makecell{11.81\\$\pm$0.58} &	\makecell{4.58\\$\pm$0.42}\\
-\ce{^{58m}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0427\\$\pm$0.0016} &	\makecell{0.0619\\$\pm$0.0023} &	\makecell{0.1054\\$\pm$0.0042} &	\makecell{0.1718\\$\pm$0.0078} &	\makecell{0.236\\$\pm$0.011} &	\makecell{0.239\\$\pm$0.012} &	\makecell{0.300\\$\pm$0.019} &	\makecell{0.475\\$\pm$0.026} &	\makecell{0.564\\$\pm$0.021} &	\makecell{0.490\\$\pm$0.022} &	\makecell{0.141\\$\pm$0.016}\\
-\ce{^{58g}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0884\\$\pm$0.0044} &	\makecell{0.0980\\$\pm$0.0049} &	\makecell{0.1118\\$\pm$0.0057} &	\makecell{0.1229\\$\pm$0.0062} &	\makecell{0.1484\\$\pm$0.0058} &	\makecell{0.330\\$\pm$0.020} &	\makecell{0.318\\$\pm$0.016} &	\makecell{0.919\\$\pm$0.057} &	\makecell{1.320\\$\pm$0.072} &	\makecell{1.599\\$\pm$0.097} &	\makecell{0.519\\$\pm$0.048}\\
-\ce{^{58}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.1311\\$\pm$0.0047} &	\makecell{0.1599\\$\pm$0.0055} &	\makecell{0.2172\\$\pm$0.0071} &	\makecell{0.295\\$\pm$0.010} &	\makecell{0.384\\$\pm$0.012} &	\makecell{0.569\\$\pm$0.023} &	\makecell{0.618\\$\pm$0.025} &	\makecell{1.395\\$\pm$0.062} &	\makecell{1.883\\$\pm$0.075} &	\makecell{2.09\\$\pm$0.10} &	\makecell{0.660\\$\pm$0.050}\\ \bottomrule
+\ce{^{48}Cr}\,($\sigma_c$)&	\makecell{0.172\\$\pm$0.011} &	\makecell{0.01376\\$\pm$0.00080} &	\makecell{0.00435\\$\pm$0.00029} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{48}V}\,($\sigma_i$)&	\makecell{6.38\\$\pm$0.43} &	\makecell{4.64\\$\pm$0.29} &	\makecell{0.513\\$\pm$0.035} &	\makecell{0.1096\\$\pm$0.0080} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{48}V}\,($\sigma_c$)&	\makecell{6.55\\$\pm$0.43} &	\makecell{4.65\\$\pm$0.29} &	\makecell{0.517\\$\pm$0.035} &	\makecell{0.1096\\$\pm$0.0080} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{49}Cr}\,($\sigma_c$)&	\makecell{1.83\\$\pm$0.12} &	\makecell{2.25\\$\pm$0.18} &	\makecell{1.20\\$\pm$0.11} &	\makecell{0.315\\$\pm$0.036} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.74} &	\makecell{15.69\\$\pm$0.94} &	\makecell{11.78\\$\pm$0.77} &	\makecell{6.15\\$\pm$0.41} &	\makecell{0.475\\$\pm$0.039} &	\makecell{0.679\\$\pm$0.047} &	\makecell{1.060\\$\pm$0.063} &	\makecell{1.97\\$\pm$0.15} &	\makecell{2.10\\$\pm$0.17} &	\makecell{1.98\\$\pm$0.19} &	\makecell{1.46\\$\pm$0.13} &	\makecell{0.584\\$\pm$0.041} &	-- &	--\\
+\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{65.9\\$\pm$5.8} &	\makecell{81.0\\$\pm$5.9} &	\makecell{56.5\\$\pm$4.5} &	\makecell{27.6\\$\pm$2.3} &	\makecell{3.83\\$\pm$0.35} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.13} &	\makecell{0.150\\$\pm$0.049} &	\makecell{0.110\\$\pm$0.024} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{77.6\\$\pm$5.7} &	\makecell{96.7\\$\pm$5.8} &	\makecell{68.3\\$\pm$4.4} &	\makecell{33.7\\$\pm$2.3} &	\makecell{4.30\\$\pm$0.35} &	\makecell{1.58\\$\pm$0.11} &	\makecell{1.76\\$\pm$0.11} &	\makecell{2.12\\$\pm$0.13} &	\makecell{2.21\\$\pm$0.17} &	\makecell{1.98\\$\pm$0.19} &	\makecell{1.46\\$\pm$0.13} &	\makecell{0.584\\$\pm$0.041} &	-- &	--\\
+\ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.74\\$\pm$0.17} &	\makecell{1.82\\$\pm$0.11} &	\makecell{1.60\\$\pm$0.10} &	\makecell{2.25\\$\pm$0.15} &	\makecell{0.770\\$\pm$0.052} &	\makecell{0.206\\$\pm$0.015} &	\makecell{0.192\\$\pm$0.013} &	\makecell{0.01297\\$\pm$0.00075} &	\makecell{0.00242\\$\pm$0.00021} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{52m}Mn}\,($\sigma_i$)&	\makecell{8.29\\$\pm$0.52} &	\makecell{9.49\\$\pm$0.54} &	\makecell{13.69\\$\pm$0.88} &	\makecell{17.9\\$\pm$1.2} &	\makecell{23.3\\$\pm$1.5} &	\makecell{11.82\\$\pm$0.74} &	\makecell{5.78\\$\pm$0.33} &	\makecell{0.0763\\$\pm$0.0044} &	\makecell{0.0763\\$\pm$0.0057} &	\makecell{0.0754\\$\pm$0.0061} &	\makecell{0.0585\\$\pm$0.0052} &	-- &	-- &	--\\
+\ce{^{52g}Mn}\,($\sigma_i$)&	\makecell{11.58\\$\pm$0.72} &	\makecell{13.46\\$\pm$0.76} &	\makecell{20.8\\$\pm$1.3} &	\makecell{28.2\\$\pm$1.8} &	\makecell{21.8\\$\pm$1.5} &	\makecell{16.3\\$\pm$1.0} &	\makecell{10.37\\$\pm$0.64} &	\makecell{0.300\\$\pm$0.017} &	\makecell{0.1124\\$\pm$0.0085} &	\makecell{0.0428\\$\pm$0.0038} &	\makecell{0.00540\\$\pm$0.00050} &	-- &	-- &	--\\
+\ce{^{52}Mn}\,($\sigma_c$)&	\makecell{13.66\\$\pm$0.90} &	\makecell{15.6\\$\pm$1.1} &	\makecell{23.0\\$\pm$1.8} &	\makecell{30.9\\$\pm$2.1} &	\makecell{31.7\\$\pm$2.2} &	\makecell{18.5\\$\pm$1.3} &	\makecell{10.57\\$\pm$0.62} &	\makecell{0.313\\$\pm$0.019} &	\makecell{0.0393\\$\pm$0.0045} &	\makecell{0.0556\\$\pm$0.0048} &	\makecell{0.0185\\$\pm$0.0019} &	-- &	-- &	--\\
+\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{131.0\\$\pm$8.5} &	\makecell{162\\$\pm$10} &	\makecell{167\\$\pm$12} &	\makecell{129\\$\pm$10} &	\makecell{42.2\\$\pm$3.4} &	\makecell{2.46\\$\pm$0.25} &	\makecell{1.10\\$\pm$0.13} &	\makecell{1.09\\$\pm$0.14} &	\makecell{1.47\\$\pm$0.17} &	\makecell{1.53\\$\pm$0.16} &	\makecell{1.36\\$\pm$0.12} &	\makecell{1.133\\$\pm$0.080} &	\makecell{0.747\\$\pm$0.075} &	\makecell{0.0600\\$\pm$0.0080}\\
+\ce{^{55}Co}\,($\sigma_i$)&	\makecell{9.43\\$\pm$0.63} &	\makecell{12.5\\$\pm$1.0} &	\makecell{15.7\\$\pm$1.2} &	\makecell{21.5\\$\pm$1.5} &	\makecell{48.4\\$\pm$3.6} &	\makecell{64.7\\$\pm$5.6} &	\makecell{61.0\\$\pm$4.5} &	\makecell{43.6\\$\pm$3.0} &	\makecell{33.6\\$\pm$3.4} &	\makecell{13.4\\$\pm$1.2} &	\makecell{0.377\\$\pm$0.035} &	\makecell{0.0421\\$\pm$0.0029} &	-- &	--\\
+\ce{^{56}Mn}\,($\sigma_c$)&	-- &	\makecell{0.518\\$\pm$0.039} &	\makecell{0.610\\$\pm$0.044} &	\makecell{0.462\\$\pm$0.045} &	\makecell{0.506\\$\pm$0.054} &	\makecell{0.405\\$\pm$0.033} &	\makecell{0.223\\$\pm$0.013} &	\makecell{0.0962\\$\pm$0.0056} &	\makecell{0.0329\\$\pm$0.0043} &	\makecell{0.0253\\$\pm$0.0021} &	\makecell{0.0132\\$\pm$0.0014} &	-- &	-- &	--\\
+\ce{^{56}Co}\,($\sigma_i$)&	\makecell{13.0\\$\pm$1.1} &	\makecell{16.3\\$\pm$1.4} &	\makecell{18.9\\$\pm$1.6} &	\makecell{23.6\\$\pm$1.7} &	\makecell{29.2\\$\pm$2.6} &	\makecell{47.8\\$\pm$3.2} &	\makecell{51.6\\$\pm$3.0} &	\makecell{82.6\\$\pm$5.0} &	\makecell{176\\$\pm$13} &	\makecell{197\\$\pm$16} &	\makecell{344\\$\pm$30} &	\makecell{376\\$\pm$24} &	\makecell{288\\$\pm$29} &	\makecell{3.54\\$\pm$0.47}\\
+\ce{^{57}Co}\,($\sigma_i$)&	-- &	\makecell{0.476\\$\pm$0.047} &	\makecell{0.539\\$\pm$0.060} &	\makecell{0.648\\$\pm$0.044} &	\makecell{1.170\\$\pm$0.090} &	\makecell{1.84\\$\pm$0.12} &	\makecell{2.36\\$\pm$0.14} &	\makecell{2.50\\$\pm$0.16} &	\makecell{3.20\\$\pm$0.25} &	\makecell{3.40\\$\pm$0.28} &	\makecell{5.14\\$\pm$0.47} &	\makecell{8.18\\$\pm$0.52} &	\makecell{11.5\\$\pm$1.2} &	\makecell{5.49\\$\pm$0.73}\\
+\ce{^{58m}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0427\\$\pm$0.0028} &	\makecell{0.0619\\$\pm$0.0042} &	\makecell{0.1054\\$\pm$0.0069} &	\makecell{0.172\\$\pm$0.011} &	\makecell{0.236\\$\pm$0.015} &	\makecell{0.241\\$\pm$0.019} &	\makecell{0.300\\$\pm$0.028} &	\makecell{0.475\\$\pm$0.044} &	\makecell{0.545\\$\pm$0.035} &	\makecell{0.477\\$\pm$0.049} &	\makecell{0.170\\$\pm$0.025}\\
+\ce{^{58g}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0884\\$\pm$0.0066} &	\makecell{0.0980\\$\pm$0.0074} &	\makecell{0.1118\\$\pm$0.0082} &	\makecell{0.1229\\$\pm$0.0084} &	\makecell{0.1484\\$\pm$0.0090} &	\makecell{0.333\\$\pm$0.028} &	\makecell{0.318\\$\pm$0.027} &	\makecell{0.919\\$\pm$0.090} &	\makecell{1.276\\$\pm$0.096} &	\makecell{1.56\\$\pm$0.17} &	\makecell{0.623\\$\pm$0.083}\\
+\ce{^{58}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.1311\\$\pm$0.0072} &	\makecell{0.1599\\$\pm$0.0086} &	\makecell{0.217\\$\pm$0.011} &	\makecell{0.295\\$\pm$0.014} &	\makecell{0.384\\$\pm$0.018} &	\makecell{0.574\\$\pm$0.034} &	\makecell{0.618\\$\pm$0.039} &	\makecell{1.39\\$\pm$0.10} &	\makecell{1.82\\$\pm$0.10} &	\makecell{2.04\\$\pm$0.18} &	\makecell{0.792\\$\pm$0.086}\\ \bottomrule
 \end{tabular}
@@
 E$_\text{p}$ (MeV)&	\makecell{53.04\\$\pm$0.61} &	\makecell{46.18\\$\pm$0.68} &	\makecell{38.42\\$\pm$0.79} &	\makecell{34.06\\$\pm$0.86} &	\makecell{29.21\\$\pm$0.97} &	\makecell{23.6\\$\pm$1.2} &	\makecell{21.70\\$\pm$0.33} &	\makecell{18.30\\$\pm$0.38} &	\makecell{16.6\\$\pm$1.5} &	\makecell{15.38\\$\pm$0.44} &	\makecell{13.11\\$\pm$0.49} &	\makecell{10.57\\$\pm$0.57} &	\makecell{6.90\\$\pm$0.82} &	\makecell{1.4\\$\pm$1.3}\\ \midrule
-\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{2.048\\$\pm$0.072} &	\makecell{0.408\\$\pm$0.012} &	\makecell{0.0931\\$\pm$0.0034} &	\makecell{0.0517\\$\pm$0.0017} &	\makecell{0.02233\\$\pm$0.00075} &	\makecell{0.01848\\$\pm$0.00065} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{57}Ni}\,($\sigma_c$)&	\makecell{2.107\\$\pm$0.094} &	\makecell{0.738\\$\pm$0.024} &	\makecell{0.0530\\$\pm$0.0033} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{57}Co}\,($\sigma_i$)&	\makecell{48.8\\$\pm$2.2} &	\makecell{32.2\\$\pm$1.5} &	\makecell{3.79\\$\pm$0.37} &	\makecell{1.206\\$\pm$0.046} &	\makecell{1.673\\$\pm$0.063} &	\makecell{1.053\\$\pm$0.046} &	\makecell{0.707\\$\pm$0.033} &	\makecell{0.264\\$\pm$0.025} &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{57}Co}\,($\sigma_c$)&	\makecell{50.9\\$\pm$2.2} &	\makecell{33.0\\$\pm$1.5} &	\makecell{3.84\\$\pm$0.37} &	\makecell{1.206\\$\pm$0.046} &	\makecell{1.673\\$\pm$0.063} &	\makecell{1.053\\$\pm$0.046} &	\makecell{0.707\\$\pm$0.033} &	\makecell{0.264\\$\pm$0.025} &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{60}Co}\,($\sigma_c$)&	\makecell{9.22\\$\pm$0.33} &	\makecell{7.70\\$\pm$0.25} &	\makecell{6.14\\$\pm$0.23} &	\makecell{3.12\\$\pm$0.13} &	\makecell{0.794\\$\pm$0.043} &	\makecell{0.201\\$\pm$0.014} &	\makecell{0.1252\\$\pm$0.0086} &	\makecell{0.0199\\$\pm$0.0020} &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{60}Cu}\,($\sigma_c$)&	\makecell{24.84\\$\pm$0.89} &	\makecell{16.06\\$\pm$0.52} &	\makecell{1.461\\$\pm$0.095} &	\makecell{0.578\\$\pm$0.021} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{61}Co}\,($\sigma_c$)&	\makecell{4.18\\$\pm$0.49} &	\makecell{5.69\\$\pm$0.57} &	\makecell{6.94\\$\pm$0.49} &	\makecell{6.61\\$\pm$0.60} &	\makecell{5.94\\$\pm$0.76} &	\makecell{0.872\\$\pm$0.067} &	\makecell{0.2531\\$\pm$0.0085} &	\makecell{0.1178\\$\pm$0.0043} &	\makecell{0.0411\\$\pm$0.0024} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{61}Cu}\,($\sigma_c$)&	\makecell{78\\$\pm$78} &	\makecell{101\\$\pm$101} &	\makecell{161\\$\pm$161} &	\makecell{155\\$\pm$155} &	\makecell{104\\$\pm$104} &	\makecell{7.0\\$\pm$7.0} &	\makecell{1.8\\$\pm$1.8} &	\makecell{1.2\\$\pm$1.2} &	\makecell{0.80\\$\pm$0.80} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{64}Cu}\,($\sigma_i$)&	\makecell{49.9\\$\pm$1.8} &	\makecell{52.7\\$\pm$1.8} &	\makecell{58.4\\$\pm$2.1} &	\makecell{62.4\\$\pm$2.2} &	\makecell{101.8\\$\pm$3.7} &	\makecell{145\\$\pm$11} &	\makecell{83.1\\$\pm$2.8} &	\makecell{57.0\\$\pm$1.9} &	\makecell{45.9\\$\pm$2.0} &	\makecell{22.15\\$\pm$0.92} &	-- &	-- &	-- &	--\\ \bottomrule
+\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{2.09\\$\pm$0.13} &	\makecell{0.428\\$\pm$0.024} &	\makecell{0.0931\\$\pm$0.0061} &	\makecell{0.0517\\$\pm$0.0033} &	\makecell{0.0223\\$\pm$0.0015} &	\makecell{0.0185\\$\pm$0.0012} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{57}Ni}\,($\sigma_c$)&	\makecell{2.15\\$\pm$0.15} &	\makecell{0.775\\$\pm$0.045} &	\makecell{0.0530\\$\pm$0.0044} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{57}Co}\,($\sigma_i$)&	\makecell{49.8\\$\pm$3.4} &	\makecell{33.8\\$\pm$2.3} &	\makecell{3.79\\$\pm$0.42} &	\makecell{1.206\\$\pm$0.080} &	\makecell{1.67\\$\pm$0.11} &	\makecell{1.053\\$\pm$0.072} &	\makecell{0.707\\$\pm$0.046} &	\makecell{0.264\\$\pm$0.027} &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{57}Co}\,($\sigma_c$)&	\makecell{51.9\\$\pm$3.4} &	\makecell{34.6\\$\pm$2.3} &	\makecell{3.84\\$\pm$0.42} &	\makecell{1.206\\$\pm$0.080} &	\makecell{1.67\\$\pm$0.11} &	\makecell{1.053\\$\pm$0.072} &	\makecell{0.707\\$\pm$0.046} &	\makecell{0.264\\$\pm$0.027} &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{60}Co}\,($\sigma_c$)&	\makecell{9.41\\$\pm$0.59} &	\makecell{8.08\\$\pm$0.47} &	\makecell{6.14\\$\pm$0.40} &	\makecell{3.12\\$\pm$0.22} &	\makecell{0.794\\$\pm$0.063} &	\makecell{0.201\\$\pm$0.017} &	\makecell{0.125\\$\pm$0.010} &	\makecell{0.0199\\$\pm$0.0022} &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{60}Cu}\,($\sigma_c$)&	\makecell{25.3\\$\pm$1.6} &	\makecell{16.86\\$\pm$0.97} &	\makecell{1.46\\$\pm$0.12} &	\makecell{0.578\\$\pm$0.038} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
+\ce{^{61}Co}\,($\sigma_c$)&	\makecell{4.26\\$\pm$0.54} &	\makecell{5.98\\$\pm$0.66} &	\makecell{6.94\\$\pm$0.62} &	\makecell{6.61\\$\pm$0.70} &	\makecell{5.94\\$\pm$0.83} &	\makecell{0.872\\$\pm$0.081} &	\makecell{0.253\\$\pm$0.014} &	\makecell{0.1178\\$\pm$0.0069} &	\makecell{0.0415\\$\pm$0.0035} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{61}Cu}\,($\sigma_c$)&	\makecell{79.7\\$\pm$5.1} &	\makecell{106.4\\$\pm$6.4} &	\makecell{161\\$\pm$11} &	\makecell{155\\$\pm$10} &	\makecell{104.1\\$\pm$7.2} &	\makecell{6.97\\$\pm$0.52} &	\makecell{1.84\\$\pm$0.13} &	\makecell{1.195\\$\pm$0.080} &	\makecell{0.809\\$\pm$0.069} &	-- &	-- &	-- &	-- &	--\\
+\ce{^{64}Cu}\,($\sigma_i$)&	\makecell{50.9\\$\pm$3.2} &	\makecell{55.4\\$\pm$3.2} &	\makecell{58.4\\$\pm$3.8} &	\makecell{62.4\\$\pm$4.1} &	\makecell{101.8\\$\pm$6.8} &	\makecell{145\\$\pm$14} &	\makecell{83.1\\$\pm$4.7} &	\makecell{57.0\\$\pm$3.3} &	\makecell{46.4\\$\pm$3.5} &	\makecell{22.2\\$\pm$1.8} &	-- &	-- &	-- &	--\\ \bottomrule
 \end{tabular}
@@
 E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\  \midrule
-\ce{^{43}K}\,($\sigma_c$)&	\makecell{1.549\\$\pm$0.080} &	\makecell{0.889\\$\pm$0.056} &	\makecell{0.189\\$\pm$0.014} &	\makecell{0.0462\\$\pm$0.0035} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{44g}Sc}\,($\sigma_i$)&	\makecell{25.0\\$\pm$2.0} &	\makecell{27.0\\$\pm$1.9} &	\makecell{37.0\\$\pm$2.3} &	\makecell{52.6\\$\pm$3.9} &	\makecell{47.8\\$\pm$2.9} &	\makecell{29.9\\$\pm$2.6} &	\makecell{8.09\\$\pm$0.27} &	\makecell{3.49\\$\pm$0.13} &	\makecell{2.70\\$\pm$0.27} &	\makecell{3.02\\$\pm$0.12} &	\makecell{2.49\\$\pm$0.11} &	-- &	-- &	--\\
-\ce{^{44m}Sc}\,($\sigma_i$)&	\makecell{12.60\\$\pm$0.41} &	\makecell{12.37\\$\pm$0.36} &	\makecell{15.20\\$\pm$0.52} &	\makecell{17.78\\$\pm$0.57} &	\makecell{16.85\\$\pm$0.55} &	\makecell{8.63\\$\pm$0.30} &	\makecell{4.26\\$\pm$0.15} &	\makecell{1.451\\$\pm$0.051} &	\makecell{1.317\\$\pm$0.052} &	\makecell{1.269\\$\pm$0.049} &	\makecell{0.839\\$\pm$0.036} &	-- &	-- &	--\\
-\ce{^{44}Sc}\,($\sigma_c$)&	\makecell{37.6\\$\pm$2.1} &	\makecell{39.4\\$\pm$1.9} &	\makecell{52.2\\$\pm$2.3} &	\makecell{70.4\\$\pm$3.9} &	\makecell{64.7\\$\pm$3.0} &	\makecell{38.6\\$\pm$2.7} &	\makecell{12.35\\$\pm$0.31} &	\makecell{4.94\\$\pm$0.14} &	\makecell{4.02\\$\pm$0.27} &	\makecell{4.29\\$\pm$0.13} &	\makecell{3.33\\$\pm$0.11} &	-- &	-- &	--\\
-\ce{^{47}Sc}\,($\sigma_c$)&	\makecell{21.20\\$\pm$0.68} &	\makecell{20.45\\$\pm$0.57} &	\makecell{21.66\\$\pm$0.76} &	\makecell{23.55\\$\pm$0.75} &	\makecell{25.12\\$\pm$0.84} &	\makecell{15.63\\$\pm$0.55} &	\makecell{11.53\\$\pm$0.48} &	\makecell{5.50\\$\pm$0.20} &	\makecell{2.75\\$\pm$0.11} &	\makecell{1.569\\$\pm$0.058} &	\makecell{0.810\\$\pm$0.034} &	\makecell{0.361\\$\pm$0.012} &	\makecell{0.218\\$\pm$0.015} &	--\\
-\ce{^{48}Sc}\,($\sigma_i$)&	\makecell{1.66\\$\pm$0.10} &	\makecell{1.68\\$\pm$0.17} &	\makecell{1.29\\$\pm$0.14} &	\makecell{0.772\\$\pm$0.051} &	\makecell{0.700\\$\pm$0.052} &	\makecell{0.339\\$\pm$0.020} &	\makecell{0.318\\$\pm$0.011} &	\makecell{0.1852\\$\pm$0.0095} &	\makecell{0.135\\$\pm$0.012} &	\makecell{0.0625\\$\pm$0.0037} &	-- &	-- &	-- &	--\\ \bottomrule
+\ce{^{43}K}\,($\sigma_c$)&	\makecell{1.55\\$\pm$0.11} &	\makecell{0.889\\$\pm$0.067} &	\makecell{0.189\\$\pm$0.017} &	\makecell{0.0462\\$\pm$0.0042} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- \\
+\ce{^{44g}Sc}\,($\sigma_i$)&	\makecell{25.0\\$\pm$2.4} &	\makecell{27.0\\$\pm$2.2} &	\makecell{37.0\\$\pm$2.9} &	\makecell{52.6\\$\pm$4.8} &	\makecell{47.8\\$\pm$3.9} &	\makecell{29.9\\$\pm$3.0} &	\makecell{8.09\\$\pm$0.45} &	\makecell{3.49\\$\pm$0.20} &	\makecell{2.70\\$\pm$0.31} &	\makecell{3.02\\$\pm$0.23} &	\makecell{2.49\\$\pm$0.21} &	-- &	-- &	-- \\
+\ce{^{44m}Sc}\,($\sigma_i$)&	\makecell{12.60\\$\pm$0.72} &	\makecell{12.37\\$\pm$0.63} &	\makecell{15.20\\$\pm$0.93} &	\makecell{17.8\\$\pm$1.1} &	\makecell{16.8\\$\pm$1.1} &	\makecell{8.63\\$\pm$0.53} &	\makecell{4.26\\$\pm$0.24} &	\makecell{1.451\\$\pm$0.082} &	\makecell{1.317\\$\pm$0.088} &	\makecell{1.269\\$\pm$0.095} &	\makecell{0.839\\$\pm$0.070} &	--  &	-- &	-- \\
+\ce{^{44}Sc}\,($\sigma_c$)&	\makecell{37.6\\$\pm$2.5} &	\makecell{39.4\\$\pm$2.3} &	\makecell{52.2\\$\pm$3.1} &	\makecell{70.4\\$\pm$4.9} &	\makecell{64.7\\$\pm$4.0} &	\makecell{38.6\\$\pm$3.1} &	\makecell{12.35\\$\pm$0.51} &	\makecell{4.94\\$\pm$0.22} &	\makecell{4.02\\$\pm$0.32} &	\makecell{4.29\\$\pm$0.25} &	\makecell{3.33\\$\pm$0.22} &	-- &	-- &	-- \\
+\ce{^{47}Sc}\,($\sigma_c$)&	\makecell{21.2\\$\pm$1.2} &	\makecell{20.5\\$\pm$1.0} &	\makecell{21.7\\$\pm$1.3} &	\makecell{23.5\\$\pm$1.4} &	\makecell{25.1\\$\pm$1.6} &	\makecell{15.63\\$\pm$0.97} &	\makecell{11.53\\$\pm$0.70} &	\makecell{5.50\\$\pm$0.32} &	\makecell{2.75\\$\pm$0.18} &	\makecell{1.57\\$\pm$0.12} &	\makecell{0.810\\$\pm$0.067} &	\makecell{0.361\\$\pm$0.021} &	\makecell{0.218\\$\pm$0.023} &	-- \\
+\ce{^{48}Sc}\,($\sigma_i$)&	\makecell{1.66\\$\pm$0.13} &	\makecell{1.68\\$\pm$0.19} &	\makecell{1.29\\$\pm$0.15} &	\makecell{0.772\\$\pm$0.065} &	\makecell{0.700\\$\pm$0.064} &	\makecell{0.339\\$\pm$0.026} &	\makecell{0.318\\$\pm$0.018} &	\makecell{0.185\\$\pm$0.013} &	\makecell{0.135\\$\pm$0.014} &	\makecell{0.0625\\$\pm$0.0055} &	-- &	-- &	-- &	-- \\ \bottomrule
 \end{tabular}
@@
 E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\ \midrule
-\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.022} &	\makecell{0.414\\$\pm$0.024} &	\makecell{0.396\\$\pm$0.026} &	\makecell{0.388\\$\pm$0.021} &	\makecell{0.517\\$\pm$0.026} &	\makecell{0.420\\$\pm$0.025} &	\makecell{0.358\\$\pm$0.018} &	\makecell{0.202\\$\pm$0.010} &	\makecell{0.404\\$\pm$0.043} &	\makecell{0.638\\$\pm$0.043} &	\makecell{0.915\\$\pm$0.073} &	-- &	-- &	--\\
-\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.017} &	\makecell{0.387\\$\pm$0.020} &	\makecell{0.485\\$\pm$0.025} &	\makecell{0.583\\$\pm$0.033} &	\makecell{0.614\\$\pm$0.034} &	\makecell{0.420\\$\pm$0.026} &	\makecell{0.486\\$\pm$0.036} &	\makecell{0.341\\$\pm$0.024} &	\makecell{0.299\\$\pm$0.016} &	\makecell{0.234\\$\pm$0.015} &	\makecell{0.214\\$\pm$0.029}         \vspace{1em}     \\
+\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.038} &	\makecell{0.414\\$\pm$0.037} &	\makecell{0.396\\$\pm$0.040} &	\makecell{0.388\\$\pm$0.037} &	\makecell{0.517\\$\pm$0.049} &	\makecell{0.420\\$\pm$0.040} &	\makecell{0.358\\$\pm$0.029} &	\makecell{0.202\\$\pm$0.017} &	\makecell{0.404\\$\pm$0.056} &	\makecell{0.638\\$\pm$0.076} &	\makecell{0.92\\$\pm$0.12} &	-- &	-- &	--\\
+\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.028} &	\makecell{0.387\\$\pm$0.034} &	\makecell{0.485\\$\pm$0.040} &	\makecell{0.583\\$\pm$0.047} &	\makecell{0.614\\$\pm$0.049} &	\makecell{0.420\\$\pm$0.041} &	\makecell{0.486\\$\pm$0.055} &	\makecell{0.341\\$\pm$0.040} &	\makecell{0.299\\$\pm$0.026} &	\makecell{0.234\\$\pm$0.031} &	\makecell{0.214\\$\pm$0.039}\\         \vspace{1em}     \\
 E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\ \midrule
-\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.022} &	\makecell{0.314\\$\pm$0.018} &	\makecell{0.291\\$\pm$0.016} &	\makecell{0.253\\$\pm$0.016} &	\makecell{0.260\\$\pm$0.015} &	\makecell{0.224\\$\pm$0.017} &	\makecell{0.345\\$\pm$0.015} &	\makecell{0.294\\$\pm$0.013} &	\makecell{0.328\\$\pm$0.026} &	\makecell{0.296\\$\pm$0.015} &	\makecell{0.252\\$\pm$0.014} &	-- &	-- &	--\\\bottomrule
+\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.029} &	\makecell{0.314\\$\pm$0.024} &	\makecell{0.291\\$\pm$0.025} &	\makecell{0.253\\$\pm$0.023} &	\makecell{0.260\\$\pm$0.023} &	\makecell{0.224\\$\pm$0.023} &	\makecell{0.345\\$\pm$0.024} &	\makecell{0.294\\$\pm$0.021} &	\makecell{0.328\\$\pm$0.034} &	\makecell{0.296\\$\pm$0.028} &	\makecell{0.252\\$\pm$0.027} &	-- &	-- &	--\\ \bottomrule
 \end{tabular}
@@
 Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
-In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
 It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and lifetime.
@@
 
-Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reaction below 70\,MeV to date, with cross sections measured  at the 4--9\% uncertainty level.
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
 This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
@@
 
-\textred{PLACEHOLDER TEXT -- }
+The measured cross sections were compared to the predictions by the reaction codes TALYS, EMPIRE, CoH, ALICE, and by the calculations in the TENDL database.
+The codes were all run on their default settings, in order to assess their predictive capabilities for the casual user.
+The default settings for the optical models and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
+The level density models for each are as follows.
+For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
+In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
+This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
+This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
+Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.
 
-\textred{Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Suspendisse urna diam, bibendum eu venenatis sit amet, vulputate in mi.
-Sed elit ex, aliquet in pharetra efficitur, mattis vel odio.
-Donec a augue lectus.
-Vestibulum fermentum rutrum justo, non imperdiet risus iaculis vitae.
-Aliquam non quam nec dui scelerisque bibendum rhoncus sed tellus.
-Aenean fermentum ullamcorper turpis, et gravida diam feugiat a.
-Nam nec dignissim massa.
-Morbi ultrices at neque in eleifend.
-Duis non lobortis ipsum, sit amet lobortis nisl.
-In ultrices posuere volutpat.
-Nunc mattis libero porttitor tortor mollis, nec tincidunt lacus sollicitudin.
-Sed vulputate at justo quis sodales.
-Nulla risus lorem, pellentesque a mauris ornare, varius maximus nulla.
-Aliquam tempus blandit ex.
-Suspendisse quis imperdiet sapien, nec egestas magna.
-Nam eu molestie nibh.}
+For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
+For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
+The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
+ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
+As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
+EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
+This is seen again in the  \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, where the first peak is well-modeled by TALYS and TENDL, but  rises much more rapidly than the data would support above 50\,MeV.
+CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct shape.
+Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section, the effect of spin distributions in highly-excited nuclear states can be studied.
+The measured data suggests that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 80\% at the peak energy.
+All three codes predict about 50\%, which indicates that the isomer feeding is not well-modeled.
+It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.
+In the other isomer-to-ground state ratio measured for Fe,  \ce{^{nat}Fe}(p,x)\ce{^{58}Co}, the opposite is seen -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
+Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling.
+However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
+
 % 
@@
   CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
-  ALICE-2017\cite{Blann1996}     &   \textred{?????}    &   \textred{?????}    &   \textred{?????}
+  ALICE-2017\cite{Blann1996}     &   \textred{Nadasen\cite{Nadasen1981}}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
 
@@
  \centering
+ \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+ \label{fig:temp_52Mn}
+\end{figure}
+
+\begin{figure}
+ \centering
  \includegraphics[width=0.5\textwidth]{./figures/52mMn.pdf}
@@
  \label{fig:temp_52mMn}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
- \label{fig:temp_52Mn}
 \end{figure}

### 2019-06-04 fe_px_paper/fe_body_text.tex
Incorporated Lee's 1st-round comments through Section 1

@@
 
-The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
-The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives\,\cite{Mulford2005,Muller2014}.
+The next generation of nuclear medicine 
+% would appear to be based upon 
+is likely to involve the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
+% The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  
+These make possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives, and informing researchers in their quest to develop new treatments\,\cite{Mulford2005,Muller2014}.
 While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production.
@@
 % Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
-One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
+One particular group of  emerging radionuclides are 
+% the various 
+positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
 In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.
-As part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
-This was carried out in a  thin-foil stacked-target experiment, using proton irradiation of natural iron foils with titanium and copper monitor foils.
-While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.
-
-Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element that is biologically relevant and essential in trace quantities. 
+
+However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies \cite{voinov, tavukcu}.
+% As 
+Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
+This was carried out 
+% in a
+using the thin-foil stacked-target technique to study proton-induced reactions on 
+% experiment, using proton irradiation of 
+natural iron foils with titanium and copper monitor foils.
+% While recent work has been performed in the 40--100\,MeV energy region, t
+This work seeks to complement 
+% these measurements 
+earlier measurements at 40--100\,MeV proton beam energies and extend them down to reaction thresholds, in order to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.
+Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.
+
+Manganese radionuclides are desirable for radiopharmaceutical applications, as 
+% manganese is a 
+the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
 Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
 \ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection\,\cite{Dong2015}.
-Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}.
-\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
-However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
-The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
-Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies\,\cite{Wang2017}.
-\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
-In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications\,\cite{Wang2017}.
+% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
+making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging\,\cite{Dong2015}.  . 
+Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}.
+However, its  long lifetime and unfavorable high-energy decay gamma-rays 
+% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
+make it undesirable for clinical applications.
+% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
+The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min)
+% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
+makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
+% Another emerging manganese radionuclide is 
+In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), 
+% whose short lifetime makes it 
+is more clinically suitable for rapid metabolic studies\,\cite{Wang2017}.
+% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
+% In addition, 
+\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging,\cite{Wang2017}.
 
@@
 
-While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
+% While these efforts have been motivated by the production cross section of the
+In addition to their interest for PET studies, the \ce{^{51,52g,52m}Mn} excitation functions 
+% radionuclides for PET studies, this experiment 
+offer an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
 Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region\,\cite{PhysRevC.73.034613,PhysRevC.45.1171}.
-These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes.
-In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.
+These measurements also provide an opportunity to benchmark 
+% a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve
+the predictive capabilities of  reaction modeling codes used for nuclear reaction evaluations and the way in which they implement the underlying physical reaction mechanisms.  
+% codes. 
+% In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.
 
@@
 A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
-One stack covers the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
+One stack covered the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
 In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  

### 2019-06-05 fe_px_paper/fe_body_text.tex
Merging Lee's 1st-round comments, up through section 2

@@
 
-A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
-One stack covered the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
-In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
+A pair of target stacks were constructed for this work.
+% , due to the large energy range desired to be spanned.
+One stack covered the 55--20\,MeV range and the other  25--0\,MeV, in order to minimize the systematic uncertainties associated with significant degradation of beam energy, and
+% In addition, the complementary  energy  of the  stacks helps build confidence  through 
+includes multiple overlapping measurements between 20--25\,MeV to build confidence in the results. 
 % A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}.
@@
 A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
-In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
-Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
+In each stack, seven foils 
+% of each metal 
+were cut down to 2.5$\times$2.5\,cm squares and spatially characterized 
+% --- for each foil, length and width measurements were taken 
+at four different locations using a digital caliper and micrometer (Mitutoyo America Corp.).
+% , thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and 
+Four mass measurements were performed using an analytical balance 
+% after cleaning the foils with isopropyl alcohol.
+% Using these length, width, and mass readings, the 
+in order to determine their areal density. 
+% and its uncertainty 
+% (in mg/cm$^2$).
+% for each foil was calculated.
 % , along with the propagated uncertainty in areal density.
 % The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
-The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
+The foils were  sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape 
+% --- each piece of tape consists 
+consisting of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
 The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
-Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
+Plates of 6061 aluminum alloy  served as proton energy degraders  between energy positions.
 % One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
@@
 \caption{Specifications of the 25\,MeV and 55\,MeV target stack designs in the present work.
-The proton beam enters the stack upstream of the SS-5 and SS-3 profile monitors, respectively, and is transported through the stack in the order presented here.
-The 6061 aluminum degraders have a measured density of approximately 2.69 g/cm$^3$.
+The proton beam enters the stack upstream of the SS-5 and SS-3 profile monitors, respectively, and travels through the stack in the order presented here.
+The 6061 aluminum degraders have a measured density of approximately 2.68 $\pm$ 0.03 g/cm$^3$.
 Their areal densities were determined using the variance minimization techniques described  in this work  and an earlier paper\,\cite{Voyles2018a}.
@@
 
-Both target stacks were assembled and separately irradiated at the  Lawrence Berkeley National Laboratory  (LBNL), using the 88-Inch Cyclotron, a  K=140 sector-focused cyclotron.
-The 25\,MeV stack was irradiated for approximately 20\,minutes with a nominal current of 100\,nA,  for an anticipated integral current of 31.61\,nAh. 
-The 55\,MeV stack was irradiated for approximately 10\,minutes with a nominal current of 120\,nA,  for an anticipated integral current of 20.78\,nAh. 
-The beam current, measured using a current integrator on the electrically-isolated beamline, remained stable under these conditions for the duration of each irradiation.
+Both target stacks were 
+% assembled and 
+separately irradiated at the  Lawrence Berkeley National Laboratory  (LBNL)
+% , using the 
+88-Inch Cyclotron, a  K=140 sector-focused cyclotron \cite{7999622}.
+The 25\,MeV stack was irradiated for approximately 20\,minutes at a nominal current of 100\,nA,  for an  integral current of 31.61\,nAh, measured using a current integrator on the electrically-isolated beamline.
+The 55\,MeV stack was irradiated for approximately 10\,minutes at a nominal current of 120\,nA,  for an  integral current of 20.78\,nAh. 
+The beam current
+% , measured using a current integrator on the electrically-isolated beamline, 
+remained stable under these conditions for the duration of each irradiation.
 The approximately 1\,cm-diameter proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
@@
 % For consistency, a
-A single detector was used in this measurement, an ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector.
-The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
+A single 
+% detector was used in this measurement, an 
+ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector was used to determine the activities in each target.
+% The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
 Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy and efficiency for each position.
-The foils were counted  for a period of 4 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities.
-An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec_femn}.
+The foils were counted  for 
+% a period of 
+4 weeks following end-of-bombardment (EoB).
+% , to accurately quantify all induced activities.
+An example of one of the gamma-ray spectra collected 
+% in such a fashion 
+is shown in \autoref{fig:gspec_femn}.
 % An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
-For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
+% For all spectra collected, n
+Net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
 % , which has been shown to perform best in comparisons with other common analysis codes\,\cite{Jackman2014}.
@@
 % Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
-The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products, using calibrated detector efficiencies and gamma-ray intensities for each transition.
+The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products.
+% , using calibrated detector efficiencies and gamma-ray intensities for each transition.
 % and  corrections for gamma-ray attenuation within each foil packet
@@
 
-As in our previous work, these activities are used to calculate cross sections, and are differentiated between cumulative and independent\,\cite{Voyles2018a}.
-For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
+As in our previous work, these activities were used to calculate 
+% cross sections, and are differentiated between 
+cumulative and independent cross sections\,\cite{Voyles2018a}.
+For the first observable product nuclide in a mass chain, its (p,x) cross section is reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
 % In addition, 
-Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.
+Cumulative cross sections are reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections  ($\sigma_i$) corresponding to a single exit channel are reported,
+% allowing for determination of the independent production via subtraction  and 
+facilitating comparison to reaction model calculations.  
 Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported\,\cite{bateman1910solution,Cetnar2006}.
@@
 
-In addition to the stack's overall beam current measurements using  beamline current integrators, thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Fe} targets, 
+In addition to 
+% the stack's overall 
+measuring beam current  using  a current integrator, thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Fe} targets, 
 % at each energy position, 
@@
 % These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
-The IAEA-recommended \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V},  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions were used for  proton fluence measurement
+The IAEA-recommended \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V},  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions were used 
+% for  proton fluence measurement 
 % , using values  
@@
 Estimates of the proton beam energy for preliminary stack designs were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism\,\cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
-However, the more rigorous  transport code FLUKA-2011.2x.3 was used for simulation of the full 3-D target stack, to determine the full proton energy and fluence distribution for each foil\,\cite{Bohlen2014a}.
-$10^8$ source protons were used for all FLUKA simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.
-As with the determination of proton fluence in monitor foils, the progressively increasing energy straggle towards the rear of each stack is accounted for using the differential proton fluence from FLUKA simulation of proton transport.
-These energy distributions $\frac{d\phi}{dE}$ are used to calculate a flux-weighted average proton  energy $\langle E \rangle$, which accounts for the slowing-down of protons within a foil (particularly in the low-energy stack) and reports the effective  energy centroid for each foil:
+However, the 
+% more rigorous  
+transport code FLUKA-2011.2x.3 was used for simulation of the full 3-D target stack and to determine the full proton energy and fluence distribution for each foil\,\cite{Bohlen2014a}. 
+$10^8$ source protons were used for all FLUKA simulations, 
+% which places the 
+yielding a statistical uncertainty 
+% in proton energy distributions at 
+of less than 0.01\%.
+As with the determination of proton fluence in the monitor foils, the progressively increasing energy straggle towards the rear of each stack is accounted for using 
+% the differential proton fluence from 
+FLUKA.
+% simulation of proton transport.
+These energy distributions $\frac{d\phi}{dE}$ were used to calculate a flux-weighted average proton  energy $\langle E \rangle$, which accounts for the slowing-down of protons within a foil (particularly in the low-energy stack) and reports the effective  energy centroid for each foil:
 \begin{equation}
@@
 
-To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, the \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments\,\cite{Voyles2018a,Graves2016}.
-This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions used in this work should all be consistent at each energy position.
-Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, residual disagreement in the  observed proton fluences is thus primarily due to poorly characterized stopping power in simulations, or a systematic error in the
+% To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
+The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments\,\cite{Voyles2018a,Graves2016}.
+This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
+% used in this work 
+should all be consistent at each 
+% energy 
+position.
+% Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, 
+Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
 % stack design, namely, the
 areal densities of the stack components. 
-This disagreement is minor at the front of the stack, but gets progressively worse as the beam is degraded, due to the compounded effect of systematic uncertainties in stack areal densities.
-
-When performing  a variance minimization, it is important to apply this variation of effective areal density  to the stack components which  have the most significant impact on beam degradation, as any systematic error in the areal densities used for these components will cause a disagreement in the observed fluences.
-For the 55\,MeV stack, the aluminum degraders are used for variance minimization, as they make up more than 80\% of the areal density of the stack, and thus play the largest role in beam degradation.
+This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties in stack areal densities.
+
+When performing  a variance minimization, it is important to apply this variation of effective areal density  to the stack components which  have the most significant impact on beam energy loss.
+% degradation, as any systematic error in the areal densities used for these components will cause a disagreement in the observed fluences.
+% For the 55\,MeV stack
+Therefore, the aluminum degraders are used for variance minimization for the 55\,MeV stack, as they make up more than 80\% of the areal density of the stack.
+% , and thus play the largest role in beam degradation.
 For the 25\,MeV stack, the Kapton tape was chosen for variance minimization, as the foil packets themselves are responsible for the majority of beam degradation.
@@
 While it might seem obvious, the contributions to the slowing of the beam due to the adhesive has often been neglected in much work performed to date. 
-This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but the stopping power of the Kapton becomes increasingly important for proton energies below approximately 25\,MeV, causing as much as a loss of 8\,MeV by the rear of this stack, making the precise areal density a source of significant uncertainty.
+This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but 
+% the stopping power of the Kapton 
+becomes increasingly important for proton energies below approximately 25\,MeV, causing as much as a loss of 8\,MeV by the rear of this stack, making the precise areal density a source of significant uncertainty.
 
 In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  were varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
-For the 25\,MeV stack, the areal density of the E-09 and H-01 aluminum degraders was taken from that reached in the minimization of the 55\,MeV stack.
-Using this value, the areal density of each of the  Kapton tape  layers  were likewise varied uniformly   by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
-These lowest energy positions were chosen as  minimization candidates, as they are the most sensitive to systematic uncertainties in stack design, due to the compounded effect of proton stopping powers.
+For the 25\,MeV stack, the areal density reached in the minimization of the 55\,MeV stack was used for  the E-09 and H-01 aluminum degraders
+% was taken from that reached in the minimization of the 55\,MeV stack.
+% Using this value, 
+and the areal density of each of the  Kapton tape  layers  were 
+% likewise 
+varied 
+% uniformly   
+by 
+% a factor of up to 
+$\pm$25\%
+% of nominal values
+, to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
+These 
+% lowest energy 
+positions were chosen as  minimization candidates, as they are the most sensitive to systematic uncertainties in stack design.
+% , due to the compounded effect of proton stopping powers.
 In the 25\,MeV stack, activity was not seen in gamma spectrometry for the lowest-energy (Cu-20) monitor foil, implying that the beam was stopped at some point in between Ti-20 and Cu-20.
-This observation is conclusive proof that  the true areal densities of the stack components differs from nominally measured values (primarily for the difficult-to-characterize Kapton tape), as transport calculations using nominal areal densities predict that the beam should exit the stack (at the SS-6 profile monitor) with an energy of approximately 7\,MeV.
+This observation 
+% is conclusive proof 
+indicates that  the true areal densities of the stack components differ from nominally measured values (primarily for the difficult-to-characterize Kapton tape), as transport calculations using nominal areal densities predict that the beam should exit the stack
+% (at the SS-6 profile monitor) 
+with an energy of approximately 7\,MeV.
 As a result, this position was not used for minimization, with the Ti-19 and Cu-19 position being the lowest-energy reliable monitor foils in the stack.
@@
 This is approximately 2\,MeV lower than the nominal FLUKA simulations, and approximately 2\,MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
-This energy corresponds to an aluminum areal density of 4.43\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
-Similarly, for the 25\,Me stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations, and approximately 5\,MeV lower than nominal A\&Z calculations.
-This energy corresponds to a Kapton tape areal density of 5.69\% greater than nominal measurements.
+This energy corresponds to an aluminum areal density of 4.43\% greater than nominal measurements, and 
+% serves as a lump correction 
+corrects for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
+Similarly, for the 25\,MeV stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations, and approximately 5\,MeV lower than nominal A\&Z calculations.
+This energy corresponds to a Kapton tape areal density of 5.69\% greater than nominal measurements, which is completely reasonable given the lack of areal density data from the manufacturer.
 The impact of this variance minimization for improving disagreement in proton fluence is  clearly  seen in   \autoref{fig:fe_variance_mins}.

### 2019-06-05 fe_px_paper/fe_body_text.tex
Merging the rest of Lee's 1st-round comments,  up through early section 3

@@
 % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
-This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Ti-20 and Cu-20.
+This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
+% the first 
+evidence 
+% (before gamma-ray spectrometry) 
+that the beam was stopped in the stack between Ti-20 and Cu-20.
+% , producing a Bragg peak at this location.  
 Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 18.8$\pm$1.0\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$\pm$1.3\,nAh using the linear fit model.
 Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
-All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the beamline current integrators.
+All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
+% beamline 
+current integrators.
 As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at IPF in the past\,\cite{Voyles2018a,Graves2016}.
+This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
 This loss of fluence is due to a combination of 

### 2019-06-05 fe_px_paper/fe_body_text.tex
Testing pushing for overleaf collaboration with Lee
Fixing small typo

@@
 Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
-\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection\,\cite{Dong2015}.
+\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
+% \,\cite{Dong2015}.
 % Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
-making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging\,\cite{Dong2015}.  . 
+making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging\,\cite{Dong2015}.  
 Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}.

### 2019-06-12 fe_px_paper/fe_body_text.tex
Adding missing references. Adding test code to look for bib file in multiple locations for Overleaf compatibility.

@@
 
-However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies \cite{voinov, tavukcu}.
+However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.
 % As 

### 2019-06-28 fe_px_paper/fe_body_text.tex
Merged in all of Shamsu's comments.  Sending to coauthors for review!

@@
 The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
-The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.
-
-\begin{figure}
+The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table} of Appendix \ref{sec:fe_stack_design}.
+
+\begin{figure}[ht]
  \centering
@@
 
-% Combined table
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table*}
-\centering
-\caption{Specifications of the 25\,MeV and 55\,MeV target stack designs in the present work.
+% % Combined table
+% % Please add the following required packages to your document preamble:
+% % \usepackage{booktabs}
+% \begin{table*}
+% \centering
+% \caption{Specifications of the 25\,MeV and 55\,MeV target stack designs in the present work.
 The proton beam enters the stack upstream of the SS-5 and SS-3 profile monitors, respectively, and travels through the stack in the order presented here.
@@
 Their areal densities were determined using the variance minimization techniques described  in this work  and an earlier paper\,\cite{Voyles2018a}.
-% the earlier paper by Graves \etal\\,\cite{Graves2016}.
-A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}
-\label{tab:fe_stack_table}
-\small
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}llll|llll@{}}
-\toprule
-% Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
-25\,MeV Target layer            & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured\\areal density\\(mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Uncertainty \\ in areal\\ density  (\%)\end{tabular} & 55\,MeV Target layer            & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured\\areal density\\(mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Uncertainty \\ in areal\\ density  (\%)\end{tabular} \\
-\midrule
-SS profile monitor SS-5 & 130.94 \mmicro m                                              & 100.57                                                                      & 0.17                                                                      & SS profile monitor SS-3 & 130.9 \mmicro m                                               & 100.48                                                                      & 0.17                                                                      \\
-Fe-08                   & 26.25 \mmicro m                                               & 19.69                                                                       & 0.17                                                                      & Fe-01                   & 25.75 \mmicro m                                               & 20.22                                                                       & 0.21                                                                      \\
-Ti-14                   & 25.01 \mmicro m                                               & 10.87                                                                       & 0.36                                                                      & Ti-01                   & 25.88 \mmicro m                                               & 11.09                                                                       & 0.16                                                                      \\
-Cu-14                   & 24.01 \mmicro m                                               & 17.49                                                                       & 0.40                                                                      & Cu-01                   & 28.81 \mmicro m                                               & 22.40                                                                       & 0.11                                                                      \\
-Al Degrader E-09        & 256.5 \mmicro m                                               & --                                                                          & --                                                                        & Al Degrader A-1         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
-Fe-09                   & 26.5 \mmicro m                                                & 19.90                                                                       & 0.09                                                                      & Fe-02                   & 25.5 \mmicro m                                                & 19.91                                                                       & 0.13                                                                      \\
-Ti-15                   & 23.81 \mmicro m                                               & 10.97                                                                       & 0.11                                                                      & Ti-02                   & 25.74 \mmicro m                                               & 10.94                                                                       & 0.24                                                                      \\
-Cu-15                   & 21.81 \mmicro m                                               & 17.63                                                                       & 0.46                                                                      & Cu-02                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.40                                                                      \\
-Al Degrader H-01        & 127.09 \mmicro m                                              & --                                                                          & --                                                                        & Al Degrader A-2         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
-Fe-10                   & 26.5 \mmicro m                                                & 19.84                                                                       & 0.11                                                                      & Fe-03                   & 25.25 \mmicro m                                               & 20.00                                                                       & 0.27                                                                      \\
-Ti-16                   & 24.6 \mmicro m                                                & 10.96                                                                       & 0.32                                                                      & Ti-03                   & 25.91 \mmicro m                                               & 11.25                                                                       & 0.15                                                                      \\
-Cu-16                   & 22.01 \mmicro m                                               & 17.22                                                                       & 0.25                                                                      & Cu-03                   & 28.86 \mmicro m                                               & 22.49                                                                       & 0.20                                                                      \\
-Fe-11                   & 27.26 \mmicro m                                               & 19.96                                                                       & 0.17                                                                      & Al Degrader C-1         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
-Ti-17                   & 25.01 \mmicro m                                               & 10.88                                                                       & 0.25                                                                      & Fe-04                   & 25.25 \mmicro m                                               & 19.93                                                                       & 0.33                                                                      \\
-Cu-17                   & 29 \mmicro m                                                  & 21.91                                                                       & 0.33                                                                      & Ti-04                   & 25.84 \mmicro m                                               & 10.91                                                                       & 0.18                                                                      \\
-Fe-12                   & 27.01 \mmicro m                                               & 20.03                                                                       & 0.12                                                                      & Cu-04                   & 28.78 \mmicro m                                               & 22.38                                                                       & 0.29                                                                      \\
-Ti-18                   & 25.01 \mmicro m                                               & 11.00                                                                       & 0.87                                                                      & Al Degrader C-2         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
-Cu-18                   & 28.75 \mmicro m                                               & 22.33                                                                       & 0.14                                                                      & Fe-05                   & 25.64 \mmicro m                                               & 20.02                                                                       & 0.24                                                                      \\
-Fe-13                  & 26.25 \mmicro m                                               & 20.05                                                                       & 0.16                                                                      & Ti-05                   & 25.86 \mmicro m                                               & 10.99                                                                       & 0.30                                                                      \\
-Ti-19                   & 26.6 \mmicro m                                                & 11.01                                                                       & 0.22                                                                      & Cu-05                   & 28.77 \mmicro m                                               & 22.35                                                                       & 0.12                                                                      \\
-Cu-19                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.19                                                                      & Al Degrader C-3         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
-Fe-14                   & 25.75 \mmicro m                                               & 20.11                                                                       & 0.19                                                                      & Fe-06                   & 25.75 \mmicro m                                               & 20.21                                                                       & 0.26                                                                      \\
-Ti-20                   & 27.01 \mmicro m                                               & 11.06                                                                       & 0.35                                                                      & Ti-06                   & 25.5 \mmicro m                                                & 11.15                                                                       & 0.23                                                                      \\
-Cu-20                   & 28.26 \mmicro m                                               & 22.34                                                                       & 0.28                                                                      & Cu-06                   & 28.83 \mmicro m                                               & 22.43                                                                       & 0.10                                                                      \\
-SS profile monitor SS-6 & 131.5 \mmicro m                                               & 100.99                                                                      & 0.17                                                                      & Al Degrader C-4         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
-                        &                                                               &                                                                             &                                                                           & Fe-07                   & 25.76 \mmicro m                                               & 19.93                                                                       & 0.19                                                                      \\
-                        &                                                               &                                                                             &                                                                           & Ti-07                   & 25.75 \mmicro m                                               & 11.17                                                                       & 0.33                                                                      \\
-                        &                                                               &                                                                             &                                                                           & Cu-07                   & 28.76 \mmicro m                                               & 22.34                                                                       & 0.24                                                                      \\
-                        &                                                               &                                                                             &                                                                           & Al Degrader H-02        & 127.04 \mmicro m                                              & --\cmmnt{34.51}                                                                       & --\cmmnt{0.20}                                                                      \\
-                        &                                                               &                                                                             &                                                                           & SS profile monitor SS-4 & 131.21 \mmicro m                                              & 101.25                                                                      & 0.16                                                                     \\
- \bottomrule
-\end{tabular}
-}
-\end{table*}
+% % the earlier paper by Graves \etal\\,\cite{Graves2016}.
+% A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}
+% \label{tab:fe_stack_table}
+% \small
+% \resizebox{\textwidth}{!}{%
+% \begin{tabular}{@{}llll|llll@{}}
+% \toprule
+% % Target Layer       & Nominal Thickness & Measured thickness (mg/cm\textasciicircum 2) & Thickness Uncertainty (\%) \\ \midrule
+% 25\,MeV Target layer            & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured\\areal density\\(mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Uncertainty \\ in areal\\ density  (\%)\end{tabular} & 55\,MeV Target layer            & \begin{tabular}[c]{@{}l@{}}Measured \\ thickness\end{tabular} & \begin{tabular}[c]{@{}l@{}}Measured\\areal density\\(mg/cm$^2$)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Uncertainty \\ in areal\\ density  (\%)\end{tabular} \\
+% \midrule
+% SS profile monitor SS-5 & 130.94 \mmicro m                                              & 100.57                                                                      & 0.17                                                                      & SS profile monitor SS-3 & 130.9 \mmicro m                                               & 100.48                                                                      & 0.17                                                                      \\
+% Fe-08                   & 26.25 \mmicro m                                               & 19.69                                                                       & 0.17                                                                      & Fe-01                   & 25.75 \mmicro m                                               & 20.22                                                                       & 0.21                                                                      \\
+% Ti-14                   & 25.01 \mmicro m                                               & 10.87                                                                       & 0.36                                                                      & Ti-01                   & 25.88 \mmicro m                                               & 11.09                                                                       & 0.16                                                                      \\
+% Cu-14                   & 24.01 \mmicro m                                               & 17.49                                                                       & 0.40                                                                      & Cu-01                   & 28.81 \mmicro m                                               & 22.40                                                                       & 0.11                                                                      \\
+% Al Degrader E-09        & 256.5 \mmicro m                                               & --                                                                          & --                                                                        & Al Degrader A-1         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-09                   & 26.5 \mmicro m                                                & 19.90                                                                       & 0.09                                                                      & Fe-02                   & 25.5 \mmicro m                                                & 19.91                                                                       & 0.13                                                                      \\
+% Ti-15                   & 23.81 \mmicro m                                               & 10.97                                                                       & 0.11                                                                      & Ti-02                   & 25.74 \mmicro m                                               & 10.94                                                                       & 0.24                                                                      \\
+% Cu-15                   & 21.81 \mmicro m                                               & 17.63                                                                       & 0.46                                                                      & Cu-02                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.40                                                                      \\
+% Al Degrader H-01        & 127.09 \mmicro m                                              & --                                                                          & --                                                                        & Al Degrader A-2         & 2.24 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-10                   & 26.5 \mmicro m                                                & 19.84                                                                       & 0.11                                                                      & Fe-03                   & 25.25 \mmicro m                                               & 20.00                                                                       & 0.27                                                                      \\
+% Ti-16                   & 24.6 \mmicro m                                                & 10.96                                                                       & 0.32                                                                      & Ti-03                   & 25.91 \mmicro m                                               & 11.25                                                                       & 0.15                                                                      \\
+% Cu-16                   & 22.01 \mmicro m                                               & 17.22                                                                       & 0.25                                                                      & Cu-03                   & 28.86 \mmicro m                                               & 22.49                                                                       & 0.20                                                                      \\
+% Fe-11                   & 27.26 \mmicro m                                               & 19.96                                                                       & 0.17                                                                      & Al Degrader C-1         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Ti-17                   & 25.01 \mmicro m                                               & 10.88                                                                       & 0.25                                                                      & Fe-04                   & 25.25 \mmicro m                                               & 19.93                                                                       & 0.33                                                                      \\
+% Cu-17                   & 29 \mmicro m                                                  & 21.91                                                                       & 0.33                                                                      & Ti-04                   & 25.84 \mmicro m                                               & 10.91                                                                       & 0.18                                                                      \\
+% Fe-12                   & 27.01 \mmicro m                                               & 20.03                                                                       & 0.12                                                                      & Cu-04                   & 28.78 \mmicro m                                               & 22.38                                                                       & 0.29                                                                      \\
+% Ti-18                   & 25.01 \mmicro m                                               & 11.00                                                                       & 0.87                                                                      & Al Degrader C-2         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Cu-18                   & 28.75 \mmicro m                                               & 22.33                                                                       & 0.14                                                                      & Fe-05                   & 25.64 \mmicro m                                               & 20.02                                                                       & 0.24                                                                      \\
+% Fe-13                  & 26.25 \mmicro m                                               & 20.05                                                                       & 0.16                                                                      & Ti-05                   & 25.86 \mmicro m                                               & 10.99                                                                       & 0.30                                                                      \\
+% Ti-19                   & 26.6 \mmicro m                                                & 11.01                                                                       & 0.22                                                                      & Cu-05                   & 28.77 \mmicro m                                               & 22.35                                                                       & 0.12                                                                      \\
+% Cu-19                   & 28.75 \mmicro m                                               & 22.32                                                                       & 0.19                                                                      & Al Degrader C-3         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+% Fe-14                   & 25.75 \mmicro m                                               & 20.11                                                                       & 0.19                                                                      & Fe-06                   & 25.75 \mmicro m                                               & 20.21                                                                       & 0.26                                                                      \\
+% Ti-20                   & 27.01 \mmicro m                                               & 11.06                                                                       & 0.35                                                                      & Ti-06                   & 25.5 \mmicro m                                                & 11.15                                                                       & 0.23                                                                      \\
+% Cu-20                   & 28.26 \mmicro m                                               & 22.34                                                                       & 0.28                                                                      & Cu-06                   & 28.83 \mmicro m                                               & 22.43                                                                       & 0.10                                                                      \\
+% SS profile monitor SS-6 & 131.5 \mmicro m                                               & 100.99                                                                      & 0.17                                                                      & Al Degrader C-4         & 0.97 mm                                                       & --                                                                          & --                                                                        \\
+%                         &                                                               &                                                                             &                                                                           & Fe-07                   & 25.76 \mmicro m                                               & 19.93                                                                       & 0.19                                                                      \\
+%                         &                                                               &                                                                             &                                                                           & Ti-07                   & 25.75 \mmicro m                                               & 11.17                                                                       & 0.33                                                                      \\
+%                         &                                                               &                                                                             &                                                                           & Cu-07                   & 28.76 \mmicro m                                               & 22.34                                                                       & 0.24                                                                      \\
+%                         &                                                               &                                                                             &                                                                           & Al Degrader H-02        & 127.04 \mmicro m                                              & --\cmmnt{34.51}                                                                       & --\cmmnt{0.20}                                                                      \\
+%                         &                                                               &                                                                             &                                                                           & SS profile monitor SS-4 & 131.21 \mmicro m                                              & 101.25                                                                      & 0.16                                                                     \\
+%  \bottomrule
+% \end{tabular}
+% }
+% \end{table*}
 
@@
 \cite{Hermanne2018}.
-As in our previous work, the integral form of the well-known activation equation was used to  determine proton fluence ($I \Delta t $),
+Using the formalism outlined in our previous work, the integral form of the well-known activation equation was used to  determine proton fluence ($I \Delta t $),
 % in each monitor foil
-in order to account for energy loss across each monitor foil:
-\begin{equation}
-I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
-\end{equation}
+in order to account for energy loss across each monitor foil \cite{Voyles2018a}.
+% \begin{equation}
+% I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
+% \end{equation}
 The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 10 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation\,\cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
@@
 % simulation of proton transport.
-These energy distributions $\frac{d\phi}{dE}$ were used to calculate a flux-weighted average proton  energy $\langle E \rangle$, which accounts for the slowing-down of protons within a foil (particularly in the low-energy stack) and reports the effective  energy centroid for each foil:
-\begin{equation}
-\langle E \rangle = \dfrac{{\displaystyle\int E \dfrac{d\phi}{dE} dE}}{{\displaystyle\int \dfrac{d\phi}{dE} dE}}
-\end{equation}
+These energy distributions $\frac{d\phi}{dE}$ were used to calculate a flux-weighted average proton  energy $\langle E \rangle$, which accounts for the slowing-down of protons within a foil (particularly in the low-energy stack) and reports the effective  energy centroid for each foil.
+% \begin{equation}
+% \langle E \rangle = \dfrac{{\displaystyle\int E \dfrac{d\phi}{dE} dE}}{{\displaystyle\int \dfrac{d\phi}{dE} dE}}
+% \end{equation}
 To report a complete description of the representative energy for each foil, a bin width is provided through the  energy uncertainty, calculated as the full width at half maximum (FWHM) of the FLUKA-modeled energy distribution for each foil.
@@
 % , as seen in \autoref{fig:Fe_ptallies}.
-For both the cumulative and independent activities quantified, cross sections were calculated as:
-\begin{equation}
-\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
-\end{equation}
-where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
+For both the cumulative and independent activities quantified, cross sections were calculated using the formalism outlined in our previous work \cite{Voyles2018a}.
+% as:
+% \begin{equation}
+% \sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
+% \end{equation}
+% where $A_0$ is the EoB activity for the  reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
 The beam current, measured using a current integrator connected to the electrically-isolated target box, remained stable for the duration of the irradiation.
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Fe}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:fe_rp_table}
-\small
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllllllllllll@{}}
-\begin{tabular}{@{}ccccccccccccccc@{}}
-\toprule
-                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
-% E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
-% E$_\text{p}$ (MeV)  & $53.45 \pm0.61$ & $46.63 \pm0.68$ & $38.93 \pm0.78$ & $34.62 \pm0.85$ & $29.84 \pm0.96$ & $24.4 \pm1.1$ & $22.71 \pm0.43$ & $19.36 \pm0.56$ & $17.6 \pm1.5$ & $16.54 \pm0.48$ & $14.52 \pm0.49$ & $12.11 \pm0.53$ & $9.23 \pm0.61$ & $4.10 \pm0.73$\\  \midrule
-E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\  \midrule
-\ce{^{48}Cr}\,($\sigma_c$)&	\makecell{0.172\\$\pm$0.011} &	\makecell{0.01376\\$\pm$0.00080} &	\makecell{0.00435\\$\pm$0.00029} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{48}V}\,($\sigma_i$)&	\makecell{6.38\\$\pm$0.43} &	\makecell{4.64\\$\pm$0.29} &	\makecell{0.513\\$\pm$0.035} &	\makecell{0.1096\\$\pm$0.0080} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{48}V}\,($\sigma_c$)&	\makecell{6.55\\$\pm$0.43} &	\makecell{4.65\\$\pm$0.29} &	\makecell{0.517\\$\pm$0.035} &	\makecell{0.1096\\$\pm$0.0080} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{49}Cr}\,($\sigma_c$)&	\makecell{1.83\\$\pm$0.12} &	\makecell{2.25\\$\pm$0.18} &	\makecell{1.20\\$\pm$0.11} &	\makecell{0.315\\$\pm$0.036} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{51}Mn}\,($\sigma_c$)&	\makecell{11.77\\$\pm$0.74} &	\makecell{15.69\\$\pm$0.94} &	\makecell{11.78\\$\pm$0.77} &	\makecell{6.15\\$\pm$0.41} &	\makecell{0.475\\$\pm$0.039} &	\makecell{0.679\\$\pm$0.047} &	\makecell{1.060\\$\pm$0.063} &	\makecell{1.97\\$\pm$0.15} &	\makecell{2.10\\$\pm$0.17} &	\makecell{1.98\\$\pm$0.19} &	\makecell{1.46\\$\pm$0.13} &	\makecell{0.584\\$\pm$0.041} &	-- &	--\\
-\ce{^{51}Cr}\,($\sigma_i$)&	\makecell{65.9\\$\pm$5.8} &	\makecell{81.0\\$\pm$5.9} &	\makecell{56.5\\$\pm$4.5} &	\makecell{27.6\\$\pm$2.3} &	\makecell{3.83\\$\pm$0.35} &	\makecell{0.90\\$\pm$0.12} &	\makecell{0.70\\$\pm$0.13} &	\makecell{0.150\\$\pm$0.049} &	\makecell{0.110\\$\pm$0.024} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{51}Cr}\,($\sigma_c$)&	\makecell{77.6\\$\pm$5.7} &	\makecell{96.7\\$\pm$5.8} &	\makecell{68.3\\$\pm$4.4} &	\makecell{33.7\\$\pm$2.3} &	\makecell{4.30\\$\pm$0.35} &	\makecell{1.58\\$\pm$0.11} &	\makecell{1.76\\$\pm$0.11} &	\makecell{2.12\\$\pm$0.13} &	\makecell{2.21\\$\pm$0.17} &	\makecell{1.98\\$\pm$0.19} &	\makecell{1.46\\$\pm$0.13} &	\makecell{0.584\\$\pm$0.041} &	-- &	--\\
-\ce{^{52}Fe}\,($\sigma_c$)&	\makecell{2.74\\$\pm$0.17} &	\makecell{1.82\\$\pm$0.11} &	\makecell{1.60\\$\pm$0.10} &	\makecell{2.25\\$\pm$0.15} &	\makecell{0.770\\$\pm$0.052} &	\makecell{0.206\\$\pm$0.015} &	\makecell{0.192\\$\pm$0.013} &	\makecell{0.01297\\$\pm$0.00075} &	\makecell{0.00242\\$\pm$0.00021} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{52m}Mn}\,($\sigma_i$)&	\makecell{8.29\\$\pm$0.52} &	\makecell{9.49\\$\pm$0.54} &	\makecell{13.69\\$\pm$0.88} &	\makecell{17.9\\$\pm$1.2} &	\makecell{23.3\\$\pm$1.5} &	\makecell{11.82\\$\pm$0.74} &	\makecell{5.78\\$\pm$0.33} &	\makecell{0.0763\\$\pm$0.0044} &	\makecell{0.0763\\$\pm$0.0057} &	\makecell{0.0754\\$\pm$0.0061} &	\makecell{0.0585\\$\pm$0.0052} &	-- &	-- &	--\\
-\ce{^{52g}Mn}\,($\sigma_i$)&	\makecell{11.58\\$\pm$0.72} &	\makecell{13.46\\$\pm$0.76} &	\makecell{20.8\\$\pm$1.3} &	\makecell{28.2\\$\pm$1.8} &	\makecell{21.8\\$\pm$1.5} &	\makecell{16.3\\$\pm$1.0} &	\makecell{10.37\\$\pm$0.64} &	\makecell{0.300\\$\pm$0.017} &	\makecell{0.1124\\$\pm$0.0085} &	\makecell{0.0428\\$\pm$0.0038} &	\makecell{0.00540\\$\pm$0.00050} &	-- &	-- &	--\\
-\ce{^{52}Mn}\,($\sigma_c$)&	\makecell{13.66\\$\pm$0.90} &	\makecell{15.6\\$\pm$1.1} &	\makecell{23.0\\$\pm$1.8} &	\makecell{30.9\\$\pm$2.1} &	\makecell{31.7\\$\pm$2.2} &	\makecell{18.5\\$\pm$1.3} &	\makecell{10.57\\$\pm$0.62} &	\makecell{0.313\\$\pm$0.019} &	\makecell{0.0393\\$\pm$0.0045} &	\makecell{0.0556\\$\pm$0.0048} &	\makecell{0.0185\\$\pm$0.0019} &	-- &	-- &	--\\
-\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{131.0\\$\pm$8.5} &	\makecell{162\\$\pm$10} &	\makecell{167\\$\pm$12} &	\makecell{129\\$\pm$10} &	\makecell{42.2\\$\pm$3.4} &	\makecell{2.46\\$\pm$0.25} &	\makecell{1.10\\$\pm$0.13} &	\makecell{1.09\\$\pm$0.14} &	\makecell{1.47\\$\pm$0.17} &	\makecell{1.53\\$\pm$0.16} &	\makecell{1.36\\$\pm$0.12} &	\makecell{1.133\\$\pm$0.080} &	\makecell{0.747\\$\pm$0.075} &	\makecell{0.0600\\$\pm$0.0080}\\
-\ce{^{55}Co}\,($\sigma_i$)&	\makecell{9.43\\$\pm$0.63} &	\makecell{12.5\\$\pm$1.0} &	\makecell{15.7\\$\pm$1.2} &	\makecell{21.5\\$\pm$1.5} &	\makecell{48.4\\$\pm$3.6} &	\makecell{64.7\\$\pm$5.6} &	\makecell{61.0\\$\pm$4.5} &	\makecell{43.6\\$\pm$3.0} &	\makecell{33.6\\$\pm$3.4} &	\makecell{13.4\\$\pm$1.2} &	\makecell{0.377\\$\pm$0.035} &	\makecell{0.0421\\$\pm$0.0029} &	-- &	--\\
-\ce{^{56}Mn}\,($\sigma_c$)&	-- &	\makecell{0.518\\$\pm$0.039} &	\makecell{0.610\\$\pm$0.044} &	\makecell{0.462\\$\pm$0.045} &	\makecell{0.506\\$\pm$0.054} &	\makecell{0.405\\$\pm$0.033} &	\makecell{0.223\\$\pm$0.013} &	\makecell{0.0962\\$\pm$0.0056} &	\makecell{0.0329\\$\pm$0.0043} &	\makecell{0.0253\\$\pm$0.0021} &	\makecell{0.0132\\$\pm$0.0014} &	-- &	-- &	--\\
-\ce{^{56}Co}\,($\sigma_i$)&	\makecell{13.0\\$\pm$1.1} &	\makecell{16.3\\$\pm$1.4} &	\makecell{18.9\\$\pm$1.6} &	\makecell{23.6\\$\pm$1.7} &	\makecell{29.2\\$\pm$2.6} &	\makecell{47.8\\$\pm$3.2} &	\makecell{51.6\\$\pm$3.0} &	\makecell{82.6\\$\pm$5.0} &	\makecell{176\\$\pm$13} &	\makecell{197\\$\pm$16} &	\makecell{344\\$\pm$30} &	\makecell{376\\$\pm$24} &	\makecell{288\\$\pm$29} &	\makecell{3.54\\$\pm$0.47}\\
-\ce{^{57}Co}\,($\sigma_i$)&	-- &	\makecell{0.476\\$\pm$0.047} &	\makecell{0.539\\$\pm$0.060} &	\makecell{0.648\\$\pm$0.044} &	\makecell{1.170\\$\pm$0.090} &	\makecell{1.84\\$\pm$0.12} &	\makecell{2.36\\$\pm$0.14} &	\makecell{2.50\\$\pm$0.16} &	\makecell{3.20\\$\pm$0.25} &	\makecell{3.40\\$\pm$0.28} &	\makecell{5.14\\$\pm$0.47} &	\makecell{8.18\\$\pm$0.52} &	\makecell{11.5\\$\pm$1.2} &	\makecell{5.49\\$\pm$0.73}\\
-\ce{^{58m}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0427\\$\pm$0.0028} &	\makecell{0.0619\\$\pm$0.0042} &	\makecell{0.1054\\$\pm$0.0069} &	\makecell{0.172\\$\pm$0.011} &	\makecell{0.236\\$\pm$0.015} &	\makecell{0.241\\$\pm$0.019} &	\makecell{0.300\\$\pm$0.028} &	\makecell{0.475\\$\pm$0.044} &	\makecell{0.545\\$\pm$0.035} &	\makecell{0.477\\$\pm$0.049} &	\makecell{0.170\\$\pm$0.025}\\
-\ce{^{58g}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.0884\\$\pm$0.0066} &	\makecell{0.0980\\$\pm$0.0074} &	\makecell{0.1118\\$\pm$0.0082} &	\makecell{0.1229\\$\pm$0.0084} &	\makecell{0.1484\\$\pm$0.0090} &	\makecell{0.333\\$\pm$0.028} &	\makecell{0.318\\$\pm$0.027} &	\makecell{0.919\\$\pm$0.090} &	\makecell{1.276\\$\pm$0.096} &	\makecell{1.56\\$\pm$0.17} &	\makecell{0.623\\$\pm$0.083}\\
-\ce{^{58}Co}\,($\sigma_i$)&	-- &	-- &	-- &	\makecell{0.1311\\$\pm$0.0072} &	\makecell{0.1599\\$\pm$0.0086} &	\makecell{0.217\\$\pm$0.011} &	\makecell{0.295\\$\pm$0.014} &	\makecell{0.384\\$\pm$0.018} &	\makecell{0.574\\$\pm$0.034} &	\makecell{0.618\\$\pm$0.039} &	\makecell{1.39\\$\pm$0.10} &	\makecell{1.82\\$\pm$0.10} &	\makecell{2.04\\$\pm$0.18} &	\makecell{0.792\\$\pm$0.086}\\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:cufe_rp_table}
-\small
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllllllllllll@{}}
-\begin{tabular}{@{}ccccccccccccccc@{}}
-\toprule
-                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
-E$_\text{p}$ (MeV)&	\makecell{53.04\\$\pm$0.61} &	\makecell{46.18\\$\pm$0.68} &	\makecell{38.42\\$\pm$0.79} &	\makecell{34.06\\$\pm$0.86} &	\makecell{29.21\\$\pm$0.97} &	\makecell{23.6\\$\pm$1.2} &	\makecell{21.70\\$\pm$0.33} &	\makecell{18.30\\$\pm$0.38} &	\makecell{16.6\\$\pm$1.5} &	\makecell{15.38\\$\pm$0.44} &	\makecell{13.11\\$\pm$0.49} &	\makecell{10.57\\$\pm$0.57} &	\makecell{6.90\\$\pm$0.82} &	\makecell{1.4\\$\pm$1.3}\\ \midrule
-\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{2.09\\$\pm$0.13} &	\makecell{0.428\\$\pm$0.024} &	\makecell{0.0931\\$\pm$0.0061} &	\makecell{0.0517\\$\pm$0.0033} &	\makecell{0.0223\\$\pm$0.0015} &	\makecell{0.0185\\$\pm$0.0012} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{57}Ni}\,($\sigma_c$)&	\makecell{2.15\\$\pm$0.15} &	\makecell{0.775\\$\pm$0.045} &	\makecell{0.0530\\$\pm$0.0044} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{57}Co}\,($\sigma_i$)&	\makecell{49.8\\$\pm$3.4} &	\makecell{33.8\\$\pm$2.3} &	\makecell{3.79\\$\pm$0.42} &	\makecell{1.206\\$\pm$0.080} &	\makecell{1.67\\$\pm$0.11} &	\makecell{1.053\\$\pm$0.072} &	\makecell{0.707\\$\pm$0.046} &	\makecell{0.264\\$\pm$0.027} &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{57}Co}\,($\sigma_c$)&	\makecell{51.9\\$\pm$3.4} &	\makecell{34.6\\$\pm$2.3} &	\makecell{3.84\\$\pm$0.42} &	\makecell{1.206\\$\pm$0.080} &	\makecell{1.67\\$\pm$0.11} &	\makecell{1.053\\$\pm$0.072} &	\makecell{0.707\\$\pm$0.046} &	\makecell{0.264\\$\pm$0.027} &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{60}Co}\,($\sigma_c$)&	\makecell{9.41\\$\pm$0.59} &	\makecell{8.08\\$\pm$0.47} &	\makecell{6.14\\$\pm$0.40} &	\makecell{3.12\\$\pm$0.22} &	\makecell{0.794\\$\pm$0.063} &	\makecell{0.201\\$\pm$0.017} &	\makecell{0.125\\$\pm$0.010} &	\makecell{0.0199\\$\pm$0.0022} &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{60}Cu}\,($\sigma_c$)&	\makecell{25.3\\$\pm$1.6} &	\makecell{16.86\\$\pm$0.97} &	\makecell{1.46\\$\pm$0.12} &	\makecell{0.578\\$\pm$0.038} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
-\ce{^{61}Co}\,($\sigma_c$)&	\makecell{4.26\\$\pm$0.54} &	\makecell{5.98\\$\pm$0.66} &	\makecell{6.94\\$\pm$0.62} &	\makecell{6.61\\$\pm$0.70} &	\makecell{5.94\\$\pm$0.83} &	\makecell{0.872\\$\pm$0.081} &	\makecell{0.253\\$\pm$0.014} &	\makecell{0.1178\\$\pm$0.0069} &	\makecell{0.0415\\$\pm$0.0035} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{61}Cu}\,($\sigma_c$)&	\makecell{79.7\\$\pm$5.1} &	\makecell{106.4\\$\pm$6.4} &	\makecell{161\\$\pm$11} &	\makecell{155\\$\pm$10} &	\makecell{104.1\\$\pm$7.2} &	\makecell{6.97\\$\pm$0.52} &	\makecell{1.84\\$\pm$0.13} &	\makecell{1.195\\$\pm$0.080} &	\makecell{0.809\\$\pm$0.069} &	-- &	-- &	-- &	-- &	--\\
-\ce{^{64}Cu}\,($\sigma_i$)&	\makecell{50.9\\$\pm$3.2} &	\makecell{55.4\\$\pm$3.2} &	\makecell{58.4\\$\pm$3.8} &	\makecell{62.4\\$\pm$4.1} &	\makecell{101.8\\$\pm$6.8} &	\makecell{145\\$\pm$14} &	\makecell{83.1\\$\pm$4.7} &	\makecell{57.0\\$\pm$3.3} &	\makecell{46.4\\$\pm$3.5} &	\makecell{22.2\\$\pm$1.8} &	-- &	-- &	-- &	--\\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work.
-Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
-\label{tab:ti_rp_table}
-\small
-% Disable next line for journal submission
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllllllllllll@{}}
-\begin{tabular}{@{}ccccccccccccccc@{}}
-\toprule
-                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15}
-E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\  \midrule
-\ce{^{43}K}\,($\sigma_c$)&	\makecell{1.55\\$\pm$0.11} &	\makecell{0.889\\$\pm$0.067} &	\makecell{0.189\\$\pm$0.017} &	\makecell{0.0462\\$\pm$0.0042} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- \\
-\ce{^{44g}Sc}\,($\sigma_i$)&	\makecell{25.0\\$\pm$2.4} &	\makecell{27.0\\$\pm$2.2} &	\makecell{37.0\\$\pm$2.9} &	\makecell{52.6\\$\pm$4.8} &	\makecell{47.8\\$\pm$3.9} &	\makecell{29.9\\$\pm$3.0} &	\makecell{8.09\\$\pm$0.45} &	\makecell{3.49\\$\pm$0.20} &	\makecell{2.70\\$\pm$0.31} &	\makecell{3.02\\$\pm$0.23} &	\makecell{2.49\\$\pm$0.21} &	-- &	-- &	-- \\
-\ce{^{44m}Sc}\,($\sigma_i$)&	\makecell{12.60\\$\pm$0.72} &	\makecell{12.37\\$\pm$0.63} &	\makecell{15.20\\$\pm$0.93} &	\makecell{17.8\\$\pm$1.1} &	\makecell{16.8\\$\pm$1.1} &	\makecell{8.63\\$\pm$0.53} &	\makecell{4.26\\$\pm$0.24} &	\makecell{1.451\\$\pm$0.082} &	\makecell{1.317\\$\pm$0.088} &	\makecell{1.269\\$\pm$0.095} &	\makecell{0.839\\$\pm$0.070} &	--  &	-- &	-- \\
-\ce{^{44}Sc}\,($\sigma_c$)&	\makecell{37.6\\$\pm$2.5} &	\makecell{39.4\\$\pm$2.3} &	\makecell{52.2\\$\pm$3.1} &	\makecell{70.4\\$\pm$4.9} &	\makecell{64.7\\$\pm$4.0} &	\makecell{38.6\\$\pm$3.1} &	\makecell{12.35\\$\pm$0.51} &	\makecell{4.94\\$\pm$0.22} &	\makecell{4.02\\$\pm$0.32} &	\makecell{4.29\\$\pm$0.25} &	\makecell{3.33\\$\pm$0.22} &	-- &	-- &	-- \\
-\ce{^{47}Sc}\,($\sigma_c$)&	\makecell{21.2\\$\pm$1.2} &	\makecell{20.5\\$\pm$1.0} &	\makecell{21.7\\$\pm$1.3} &	\makecell{23.5\\$\pm$1.4} &	\makecell{25.1\\$\pm$1.6} &	\makecell{15.63\\$\pm$0.97} &	\makecell{11.53\\$\pm$0.70} &	\makecell{5.50\\$\pm$0.32} &	\makecell{2.75\\$\pm$0.18} &	\makecell{1.57\\$\pm$0.12} &	\makecell{0.810\\$\pm$0.067} &	\makecell{0.361\\$\pm$0.021} &	\makecell{0.218\\$\pm$0.023} &	-- \\
-\ce{^{48}Sc}\,($\sigma_i$)&	\makecell{1.66\\$\pm$0.13} &	\makecell{1.68\\$\pm$0.19} &	\makecell{1.29\\$\pm$0.15} &	\makecell{0.772\\$\pm$0.065} &	\makecell{0.700\\$\pm$0.064} &	\makecell{0.339\\$\pm$0.026} &	\makecell{0.318\\$\pm$0.018} &	\makecell{0.185\\$\pm$0.013} &	\makecell{0.135\\$\pm$0.014} &	\makecell{0.0625\\$\pm$0.0055} &	-- &	-- &	-- &	-- \\ \bottomrule
-\end{tabular}
-}
-\end{table}
-
-% \ce{^{nat}Cu}(p,x)\ce{^{52}Mn}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}
-\centering
-\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x) and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
-\label{tab:fe_ibr_table}
-\small
-\resizebox{\textwidth}{!}{%
-% \begin{tabular}{@{}lllllllllllllll@{}}
-\begin{tabular}{@{}ccccccccccccccc@{}}
-\toprule
-                               & \multicolumn{14}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-15}
-E$_\text{p}$ (MeV)&	\makecell{53.45\\$\pm$0.61} &	\makecell{46.63\\$\pm$0.68} &	\makecell{38.93\\$\pm$0.78} &	\makecell{34.62\\$\pm$0.85} &	\makecell{29.84\\$\pm$0.96} &	\makecell{24.4\\$\pm$1.1} &	\makecell{22.71\\$\pm$0.43} &	\makecell{19.36\\$\pm$0.56} &	\makecell{17.6\\$\pm$1.5} &	\makecell{16.54\\$\pm$0.48} &	\makecell{14.52\\$\pm$0.49} &	\makecell{12.11\\$\pm$0.53} &	\makecell{9.23\\$\pm$0.61} &	\makecell{4.10\\$\pm$0.73}\\ \midrule
-\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.038} &	\makecell{0.414\\$\pm$0.037} &	\makecell{0.396\\$\pm$0.040} &	\makecell{0.388\\$\pm$0.037} &	\makecell{0.517\\$\pm$0.049} &	\makecell{0.420\\$\pm$0.040} &	\makecell{0.358\\$\pm$0.029} &	\makecell{0.202\\$\pm$0.017} &	\makecell{0.404\\$\pm$0.056} &	\makecell{0.638\\$\pm$0.076} &	\makecell{0.92\\$\pm$0.12} &	-- &	-- &	--\\
-\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.028} &	\makecell{0.387\\$\pm$0.034} &	\makecell{0.485\\$\pm$0.040} &	\makecell{0.583\\$\pm$0.047} &	\makecell{0.614\\$\pm$0.049} &	\makecell{0.420\\$\pm$0.041} &	\makecell{0.486\\$\pm$0.055} &	\makecell{0.341\\$\pm$0.040} &	\makecell{0.299\\$\pm$0.026} &	\makecell{0.234\\$\pm$0.031} &	\makecell{0.214\\$\pm$0.039}\\         \vspace{1em}     \\
-E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\ \midrule
-\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.029} &	\makecell{0.314\\$\pm$0.024} &	\makecell{0.291\\$\pm$0.025} &	\makecell{0.253\\$\pm$0.023} &	\makecell{0.260\\$\pm$0.023} &	\makecell{0.224\\$\pm$0.023} &	\makecell{0.345\\$\pm$0.024} &	\makecell{0.294\\$\pm$0.021} &	\makecell{0.328\\$\pm$0.034} &	\makecell{0.296\\$\pm$0.028} &	\makecell{0.252\\$\pm$0.027} &	-- &	-- &	--\\ \bottomrule
-\end{tabular}
-}
-\end{table}
+\input{./fe_body_tables}
 
@@
 
-Quick observations:
-
-\begin{enumerate}
- \item Modeling on Fe is significantly better than for Cu/Ti
- \item On the whole, ALICE seems to do the best job overall
- \item (p,$\alpha$x) channels are done fairly well, (p,2p2nx) are worse, and (p,$\alpha$xn) are really lousy
- \item Location and shape of rising edges/compound peaks appears much better than in the Nb IPF paper, possibly due to easier modeling in lower energy regime?
- \item Amplitudes of excitation function are still off within factor of 2--3
- \item Isomer branching ratios are (surprise, surprise) really bad.  Ti(p,x)\ce{^{44}Sc} is the best, but all three miss the key shape and features
-\end{enumerate}
+% Quick observations:
+% 
+% \begin{enumerate}
+%  \item Modeling on Fe is significantly better than for Cu/Ti
+%  \item On the whole, ALICE seems to do the best job overall
+%  \item (p,$\alpha$x) channels are done fairly well, (p,2p2nx) are worse, and (p,$\alpha$xn) are really lousy
+%  \item Location and shape of rising edges/compound peaks appears much better than in the Nb IPF paper, possibly due to easier modeling in lower energy regime?
+%  \item Amplitudes of excitation function are still off within factor of 2--3
+%  \item Isomer branching ratios are (surprise, surprise) really bad.  Ti(p,x)\ce{^{44}Sc} is the best, but all three miss the key shape and features
+% \end{enumerate}
 
@@
   CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
-  ALICE-2017\cite{Blann1996}     &   \textred{Nadasen\cite{Nadasen1981}}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
+  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
 

### 2019-07-10 fe_px_paper/fe_body_text.tex
Merging in Shamsu's 2nd-round comments

@@
 the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
-Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
+Manganese possesses well-established biochemistry, and has been proven to be chelated well by the complexing agent DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
 \ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
@@
 Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}.
-However, its  long lifetime and unfavorable high-energy decay gamma-rays 
+However, its  long half-life and unfavorable high-energy decay gamma-rays 
 % (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
@@
 % Another emerging manganese radionuclide is 
-In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), 
+In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV), 
 % whose short lifetime makes it 
@@
 % 
-Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here\,\cite{springer2017investigation}.
+Preliminary results  were reported in a Master's thesis \cite{springer2017investigation}, here we report the final analysis of that work.
+% of one co-author, but the conclusive results of this work are described here\,\cite{springer2017investigation}.  
+Unless otherwise stated, all values are presented herein as mean $\pm$ SD, or as the calculated result $\pm$ half the width of a 68\% confidence interval.
 
@@
 % In addition, the complementary  energy  of the  stacks helps build confidence  through 
-includes multiple overlapping measurements between 20--25\,MeV to build confidence in the results. 
+includes multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
+% to build confidence in the results. 
 % A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}.
@@
 % The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
-The   lifetimes and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
+The   half-lives and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
 \cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
@@
 Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 18.8$\pm$1.0\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$\pm$1.3\,nAh using the linear fit model.
-Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
+Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 
+% 55\,MeV 
+target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
 All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
@@
 Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
- were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, as recorded in \autoref{tab:fe_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, as recorded in \autoref{tab:cufe_rp_table}.
-For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, as recorded in \autoref{tab:ti_rp_table}.
-In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
+ were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, presented in \autoref{tab:fe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, 
+% as recorded 
+presented in \autoref{tab:cufe_rp_table}.
+For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, 
+% as recorded 
+presented in \autoref{tab:ti_rp_table}.
+In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
@@
 Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
-In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long lifetime permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
-It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and lifetime.
-Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient lifetime and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
+In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
+Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
 This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
@@
 Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn}, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
-It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in lifetime, to avoid the unfavorable gammas produced by the isomer.
+It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer.
 However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$\pm$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator.

### 2019-07-10 fe_px_paper/fe_body_text.tex
Merged in Stephen's 1st round comments

@@
 
-The next generation of nuclear medicine 
-% would appear to be based upon 
-is likely to involve the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
-% The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  
-These make possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives, and informing researchers in their quest to develop new treatments\,\cite{Mulford2005,Muller2014}.
-While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production.
+Clinical practice of nuclear medicine is rapidly growing with the inclusion of a broader array of radiopharmaceuticals. 
+Future growth is anticipated, given the pre-clinical success of many  new and emerging radionuclides. 
+Although the physical and chemical properties of these novel radionuclides tend to be
+% The next generation of nuclear medicine 
+% % would appear to be based upon 
+% is likely to involve the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
+% % The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  
+% These make possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives, and informing researchers in their quest to develop new treatments\,\cite{Mulford2005,Muller2014}.
+% While the chemical and radioactive decay properties of many of these radionuclides are 
+well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
 % 
@@
 % Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
-One particular group of  emerging radionuclides are 
+One particular set of  emerging radionuclides are 
 % the various 
 positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
-In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.
-
-However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.
+In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in quantitative PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.
+
+% However, the m
+Modeling of nuclear reactions in 
+% this 
+the A=40--70 mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.
 % As 
-Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
+Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on natural iron.
 This was carried out 
@@
 % While recent work has been performed in the 40--100\,MeV energy region, t
-This work seeks to complement 
+This work 
+% seeks to 
+complements 
 % these measurements 
-earlier measurements at 40--100\,MeV proton beam energies and extend them down to reaction thresholds, in order to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.
+earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.
 Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.
@@
 Manganese possesses well-established biochemistry, and has been proven to be chelated well by the complexing agent DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
-\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
+\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV\,\cite{Dong2015}) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
 % \,\cite{Dong2015}.
 % Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
-making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging\,\cite{Dong2015}.  
+making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging.  
 Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}.
@@
 % Another emerging manganese radionuclide is 
-In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV), 
+In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{Wang2017}), 
 % whose short lifetime makes it 
-is more clinically suitable for rapid metabolic studies\,\cite{Wang2017}.
+is more clinically suitable for rapid metabolic studies.
 % \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
 % In addition, 
-\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging,\cite{Wang2017}.
+\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging.
+% ,\cite{Wang2017}.
 
@@
 % activity for each gamma-ray possesses a 
-The total propagated uncertainty in  activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.
+EoB activities were determined by $\chi^2$-fitting of all observed decay gammas for a product to the decay curve.
+The total  uncertainty in  activity is the propagated sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration,  uncertainty in the gamma-ray branching ratio data, and uncertainty in photon attenuation coefficients (taken as~5\%).
 
@@
    \hspace{-5pt}}%
-    \caption{Results of variance minimization through enhancement of the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
+    \caption{Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
 A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
@@
 After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
-With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
+With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling, off-gassing of oxides, and the formation of gaseous short-lived beta activities in the tape.
 % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
@@
 Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
 
@@
 This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
-
-\textred{All: feel free to add additional details of 51/52Mn production here...}
+Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds of nearly 20\,MeV.
+This provides some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region, which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.
+
+% \textred{All: feel free to add additional details of 51/52Mn production here...}
 
@@
 % This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
+The one exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
+While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
+The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.
 
@@
 For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
+The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
+As a result, this analysis is useful for a qualitative comparison of predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
+% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
 For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
@@
 Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling.
-However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
+% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
 

### 2019-10-07 fe_px_paper/fe_body_text.tex
Merged in Jon Engle's, Jon Morrell's, and Public Utterance comments.

@@
 % While the chemical and radioactive decay properties of many of these radionuclides are 
-well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
+well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate 
+% large-scale   
+production. 
 % 
@@
 positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
-In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in quantitative PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.
-
+In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in quantitative positron emission tomography (PET) studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.
+
+Manganese radionuclides are desirable for radiopharmaceutical applications, as 
+% manganese is a 
+% the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
+% Manganese 
+they possess well-established biochemistry, and have been 
+% proven to be 
+chelated 
+% well 
+by the complexing agent DOTA for tracking monoclonal antibodies with high biostability at neutral pH\,\cite{Graves2015}.
+\ce{^{52}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV\,\cite{Dong2015}) has been shown to be useful for immuno-PET applications, 
+% with its rapid blood clearance 
+offering the possibility for imaging within minutes of injection,
+% \,\cite{Dong2015}.
+% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
+% making it more useful 
+making it highly suitable for pre-clinical imaging as a longer-lived complement   to the more established immuno-PET agents \ce{^{89}Zr} and   \ce{^{64}Cu}.  
+% Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}.
+However, its  long half-life and unfavorable high-energy decay gamma-rays 
+% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
+make it undesirable for clinical applications.
+% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
+The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$~\pm~$0.2\,min)
+% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
+makes production and handling difficult, and with a  high-intensity gamma emission (1434.06\,keV, $I_\gamma = 98.2~\pm~0.5\%$),  
+\ce{^{52m}Mn} is similarly undesirable for clinical applications\,\cite{Dong2015}.
+% contributes significantly to patient dose\,\cite{Dong2015}.
+% Another emerging manganese radionuclide is 
+In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$~\pm~$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{Wang2017}), 
+% whose short lifetime makes it 
+is more clinically suitable for rapid metabolic studies.
+% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
+% In addition, 
+\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$~\pm~$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910~\pm~0.010\%$] line), making it the best choice of these radionuclides for clinical imaging.
+% ,\cite{Wang2017}.
+
+Developing production of these radionuclides requires well-characterized cross section data, or predictive models when such data have not been measured.   
 % However, the m
@@
 % As 
-Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on natural iron.
-This was carried out 
+Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has
+% performed a   measurement of 
+measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on natural iron.
+% This was carried out 
 % in a
-using the thin-foil stacked-target technique to study proton-induced reactions on 
+% using 
+We used the thin-foil stacked-target technique to study proton-induced reactions on 
 % experiment, using proton irradiation of 
-natural iron foils with titanium and copper monitor foils.
+% natural iron foils 
+iron foils of natural isotopic abundance with titanium and copper monitor foils.
 % While recent work has been performed in the 40--100\,MeV energy region, t
@@
 earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.
-Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.
-
-Manganese radionuclides are desirable for radiopharmaceutical applications, as 
-% manganese is a 
-the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
-Manganese possesses well-established biochemistry, and has been proven to be chelated well by the complexing agent DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
-\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV\,\cite{Dong2015}) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
-% \,\cite{Dong2015}.
-% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
-making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging.  
-Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}.
-However, its  long half-life and unfavorable high-energy decay gamma-rays 
-% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
-make it undesirable for clinical applications.
-% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
-The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min)
-% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
-makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
-% Another emerging manganese radionuclide is 
-In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{Wang2017}), 
-% whose short lifetime makes it 
-is more clinically suitable for rapid metabolic studies.
-% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
-% In addition, 
-\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging.
-% ,\cite{Wang2017}.
+Furthermore, 
+% we are able to use a portion of the data we measured to gain insight into the role of 
+we used our measured data to probe the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.
 
@@
 % radionuclides for PET studies, this experiment 
-offer an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
+offer an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
 Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region\,\cite{PhysRevC.73.034613,PhysRevC.45.1171}.
@@
 % 
-Preliminary results  were reported in a Master's thesis \cite{springer2017investigation}, here we report the final analysis of that work.
+Preliminary results  were reported in a Master's thesis \cite{springer2017investigation}; here we report the final analysis of that work.
 % of one co-author, but the conclusive results of this work are described here\,\cite{springer2017investigation}.  
@@
 
-A pair of target stacks were constructed for this work.
+We constructed a pair of target stacks 
+% were constructed 
+for this work,
 % , due to the large energy range desired to be spanned.
-One stack covered the 55--20\,MeV range and the other  25--0\,MeV, in order to minimize the systematic uncertainties associated with significant degradation of beam energy, and
+one stack covering the 55--20\,MeV range and the other  25--0\,MeV.
+% , in order to 
+This minimized the systematic uncertainties associated with significant degradation of beam energy, and
 % In addition, the complementary  energy  of the  stacks helps build confidence  through 
-includes multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
+included multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
 % to build confidence in the results. 
@@
 % One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
-The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
-The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table} of Appendix \ref{sec:fe_stack_design}.
+The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy and mounts on the end of an electrically-isolated beamline.
+The specifications of both target stacks 
+% designs for this work are presented 
+are in \autoref{tab:fe_stack_table} of Appendix \ref{sec:fe_stack_design}.
 
@@
  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
- \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack, before it was mounted in the beamline.
+ \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack.
+%  , before it was mounted in the beamline. 
  The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
@@
 88-Inch Cyclotron, a  K=140 sector-focused cyclotron \cite{7999622}.
-The 25\,MeV stack was irradiated for approximately 20\,minutes at a nominal current of 100\,nA,  for an  integral current of 31.61\,nAh, measured using a current integrator on the electrically-isolated beamline.
-The 55\,MeV stack was irradiated for approximately 10\,minutes at a nominal current of 120\,nA,  for an  integral current of 20.78\,nAh. 
+The 25\,MeV stack was irradiated for 
+% approximately 
+20\,minutes at a nominal current of 100\,nA,  for an  integral current of 31.61\,nAh, measured using a current integrator on the electrically-isolated beamline. 
+The 55\,MeV stack was irradiated for 
+% approximately 
+10\,minutes at a nominal current of 120\,nA,  for an  integral current of 20.78\,nAh. 
 The beam current
@@
 Following end-of-bombardment (EoB), each stack was removed from the beamline and disassembled.
-All activated foils were transported to a counting lab for gamma spectrometry, which started approximately 30\,minutes following the end of each irradiation.
+All activated foils were transported to a counting lab for gamma spectrometry, which started approximately 20\,minutes following the end of each irradiation.
 
@@
 % The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
-Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy and efficiency for each position.
+Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector.
+% , with a series of standard calibration sources used to determine energy and efficiency for each position.
 The foils were counted  for 
 % a period of 
-4 weeks following end-of-bombardment (EoB).
+4 weeks following 
+% end-of-bombardment.
+(EoB).
 % , to accurately quantify all induced activities.
@@
 % For all spectra collected, n
-Net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
+Net peak areas were fitted using the 
+% gamma spectrometry analysis 
+code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
 % , which has been shown to perform best in comparisons with other common analysis codes\,\cite{Jackman2014}.
@@
  % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
- \caption{A gamma spectrum collected from an activated Fe foil at approximately 55\,MeV.
+ \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment.
 Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks.
@@
 \cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
-Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
+Corrections (typically \textless0.2\%) for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
 % As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
@@
 cumulative and independent cross sections\,\cite{Voyles2018a}.
-For the first observable product nuclide in a mass chain, its (p,x) cross section is reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
+% For the first observable product nuclide in a mass chain
+For the first product nuclide in a mass chain with observable decay gammas, its (p,x) cross section is reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus.
 % In addition, 
 Cumulative cross sections are reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
-For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections  ($\sigma_i$) corresponding to a single exit channel are reported,
+For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections  ($\sigma_i$) corresponding to a single 
+% exit channel 
+residual product are reported, 
 % allowing for determination of the independent production via subtraction  and 
@@
 
-In addition to 
+% In addition to 
 % the stack's overall 
-measuring beam current  using  a current integrator, thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Fe} targets, 
+% measuring beam current  using  a current integrator, t
+Thin \ce{^{nat}Ti} and \ce{^{nat}Cu} foils  
+% included along with the \ce{^{nat}Fe} targets, 
 % at each energy position, 
-to monitor beam current at each position within the stack.
+were co-irradiated to measure beam current at each position within the stack.
 % These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
@@
 \cite{Hermanne2018}.
+Systematically enhanced fluence from \ce{^{nat}Ti}(p,x)\ce{^{48}Sc} co-production was avoided by only using the 928.327, 944.130, and 2240.396\,keV decay gammas  from \ce{^{48}V}.
 Using the formalism outlined in our previous work, the integral form of the well-known activation equation was used to  determine proton fluence ($I \Delta t $),
@@
 % To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
-The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments\,\cite{Voyles2018a,Graves2016}.
+The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
 This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
@@
 % Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, 
-Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
-% stack design, namely, the
-areal densities of the stack components. 
-This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties in stack areal densities.
+% Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
+% % stack design, namely, the
+% areal densities of the stack components. 
+This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties.
+% in stack areal densities.
 
@@
 In addition, it is far easier to directly characterize the areal density of the metallic foils than it is for the Kapton, resulting in only an approximate value for the latter.
-While it might seem obvious, the contributions to the slowing of the beam due to the adhesive has often been neglected in much work performed to date. 
+% While it might seem obvious, t
+The contributions to the slowing of the beam due to the adhesive have often been neglected in much work performed to date. 
 This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but 
 % the stopping power of the Kapton 
-becomes increasingly important for proton energies below approximately 25\,MeV, causing as much as a loss of 8\,MeV by the rear of this stack, making the precise areal density a source of significant uncertainty.
-
-In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  were varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
+becomes increasingly important for proton energies below 
+% approximately 
+25\,MeV, causing as much as an additional loss of 8\,MeV  by the time it reaches the end of the stack.
+% by the rear of this stack.
+% , making the precise areal density a source of significant uncertainty.
+
+In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  was varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
 For the 25\,MeV stack, the areal density reached in the minimization of the 55\,MeV stack was used for  the E-09 and H-01 aluminum degraders
@@
 % Using this value, 
-and the areal density of each of the  Kapton tape  layers  were 
+and the areal density of each of the  Kapton tape  layers  was 
 % likewise 
@@
 % a factor of up to 
-$\pm$25\%
+$\pm$25\%, 
 % of nominal values
-, to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
+to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
 These 
 % lowest energy 
-positions were chosen as  minimization candidates, as they are the most sensitive to systematic uncertainties in stack design.
+positions were chosen as  minimization candidates as they are the most sensitive to systematic uncertainties in stack design.
 % , due to the compounded effect of proton stopping powers.
@@
 The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average 22.71\,MeV protons entering the last energy position of the 55\,MeV stack.
-This is approximately 2\,MeV lower than the nominal FLUKA simulations, and approximately 2\,MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
-This energy corresponds to an aluminum areal density of 4.43\% greater than nominal measurements, and 
+This is approximately 2\,MeV lower than the 
+% nominal 
+FLUKA simulations, and approximately 2\,MeV lower than 
+% nominal 
+A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
+This energy corresponds to an aluminum areal density  4.43\% greater than 
+% nominal 
+measurements and 
 % serves as a lump correction 
-corrects for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.
+corrects for other minor systematic uncertainties in stack design.
+% , including stack areal densities and incident beam energy.
 Similarly, for the 25\,MeV stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations, and approximately 5\,MeV lower than nominal A\&Z calculations.
@@
     \caption{Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
-A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.}
+A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
+Open data points represent the 25\,MeV stack, and closed data points represent the 55\,MeV stack.}
      \label{fig:fe_variance_mins}
@@
  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.}
+ \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.
+Open data points represent the 25\,MeV stack, and closed data points represent the 55\,MeV stack.}
 %  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
@@
 
-Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed (p,x) reactions.
-While thin ($\approx$ 10--20\,mg/cm$^2$)  foils were irradiated to minimize the energy bins of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged
+Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate 
+% the final 
+cross sections for 
+% the various 
+observed (p,x) reactions.
+While thin ($\approx$ 10--20\,mg/cm$^2$)  foils were irradiated to minimize the energy bins of these cross section measurements, 
+% it is important to note that 
+all cross sections reported here are flux-averaged  
 % cross sections, 
@@
 % , as seen in \autoref{fig:Fe_ptallies}.
-For both the cumulative and independent activities quantified, cross sections were calculated using the formalism outlined in our previous work \cite{Voyles2018a}.
+% For both the cumulative and independent activities quantified, cross sections were calculated using the formalism outlined in our previous work \cite{Voyles2018a}.
 % as:
@@
 
-After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
-With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling, off-gassing of oxides, and the formation of gaseous short-lived beta activities in the tape.
+After irradiation, all foils were 
+% confirmed to 
+still sealed in their Kapton packets, verifying that no activation products were lost due to packet failure.
+% and dispersal.
+With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of 
+% thermal swelling, 
+off-gassing of oxides and the formation of gaseous short-lived beta activities in the tape.
 % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
@@
 % , producing a Bragg peak at this location.  
-Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 18.8$\pm$1.0\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$\pm$1.3\,nAh using the linear fit model.
-Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 
+Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh
+% 18.8$\pm$1.0\,nAh
+was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
+Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
+% 33.2$\pm$4.7\,nAh
+was calculated to be incident upon the 
 % 55\,MeV 
-target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
-All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
+target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
+% 37.0$\pm$9.3\,nAh using the linear fit model.
+% All of these 
+Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
 % beamline 
 current integrators.
+However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
+This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of secondary protons not seen in the activation data.
 As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
+This incident fluence dropped by approximately 
+% 9.5\% to  17.0$\pm$2.4\,nAh (and by 
+8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
 This loss of fluence is due to a combination of 
@@
 These results have several notable features.
-The various \ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
+The 
+% various 
+\ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
+% the body of measurements in the 
+literature,  but have been measured nearly exclusively with the highest precision to date.
 While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
@@
 Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
-In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
 It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
-Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
+Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
 This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
@@
 % However, 
-\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for clean production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
-In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house production of this short-lived ($t_{1/2}=46.2\pm0.1$ m\,\cite{Wang2017}) radionuclide.
+\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for 
+% clean 
+production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
+In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house production of this short-lived ($t_{1/2}=46.2~\pm~0.1$ m\,\cite{Wang2017}) radionuclide.
 To increase yields over \ce{^{nat}Fe}(p,x), an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons, without opening the additional manganese exit channels accessible on a natural target.
@@
 Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn}, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
-It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer.
-However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$\pm$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator.
+It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer.
+However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$~\pm~$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator\,\cite{Blauenstein1997}.
 Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
@@
 % This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
-The one exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
+The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
 While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
@@
 \subsection{Comparison of reaction modeling with experimental results}
+
+% \def\arraystretch{1.5}
+\begin{table}
+ \caption{Default settings for the reactions codes}
+ \label{tab:fe_defaults}
+ \resizebox{\textwidth}{!}{%
+\begin{tabular}{ c c c c}
+
+ \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
+ EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
+ TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
+  CoH-3.5.3\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
+  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
+
+\end{tabular}
+}
+\end{table}
 
@@
 Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section, the effect of spin distributions in highly-excited nuclear states can be studied.
-The measured data suggests that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 80\% at the peak energy.
+The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 80\% at the peak energy.
 All three codes predict about 50\%, which indicates that the isomer feeding is not well-modeled.
@@
 % All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-% \def\arraystretch{1.5}
-\begin{table}
- \caption{Default settings for the reactions codes}
- \label{tab:fe_defaults}
- \resizebox{\textwidth}{!}{%
-\begin{tabular}{ c c c c}
-
- \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
- EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
- TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
-  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
-
-\end{tabular}
-}
-\end{table}
 

### 2019-10-25 fe_px_paper/cover_letter.tex
Removed Alex as co-author. Implemented all Public Utterance changes and submitted to PRC!

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{booktabs,siunitx}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{
% Dr. Mark Breese, or the 
Editorial Board \\
Physical Review C}

\begin{flushleft}
{\large\bf Andrew S. Voyles, Ph.D.}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
% \hfill The University of California, Berkeley \\
\hfill Lawrence Berkeley National Laboratory \\
\hfill Building 088-163D  |  M/S 88R0192, Berkeley, CA  94720-1730 \\
% \hfill (presently) +47 486 43 444 \\ 
\hfill  +1 (850) 281-0217 (mobile) or +1 (510) 486-7310 (office) 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{To whom it may concern:}

  \renewcommand*{\thefootnote}{\alph{footnote}}

\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in Physical Review C. 
% We are confident that it will interest your audience. 
This manuscript describes an original work conducted by myself, the first and corresponding author, along with my co-authors and collaborators Amanda M. Lewis\footnotemark[1], Jonathan T. Morrell\footnotemark[1], M. Shamsuzzoha Basunia\footnotemark[2], Lee A. Bernstein\footnotemark[1]\footnotemark[2], 
% Eva R. Birnbaum\footnotemark[3], 
Jonathan W. Engle\footnotemark[3], Stephen A. Graves\footnotemark[4], and Eric F. Matthews\footnotemark[1].
% ,  and Alexander Springer\footnotemark[1].
% Toshihiko Kawano\footnotemark[6],  and Francois M. Nortier\footnotemark[3].

\footnotetext[1]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
\footnotetext[2]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
% \footnotetext[3]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
\footnotetext[3]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
\footnotetext[4]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
% \footnotetext[6]{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}

\noindent This work described in this manuscript is a measurement of 34 unique excitation functions spanning  from threshold up to 55 MeV for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reactions, along with 3 independent measurements of isomer branching ratios for pairs of radioisotope isomer/ground states populated in this mass region. This is part of a recent, ongoing effort at UC Berkeley and Lawrence Berkeley National Laboratory to address the gaps in existing nuclear data which have been identified by the applications community, focusing in particular on the production of novel and emerging medical radioisotopes. The primary motivation for this work is to provide the most comprehensive characterization to date of the \ce{Fe}(p,x)\ce{^{51m,52m,52g}Mn} reactions, as these radionuclides have been proposed as a suite of valuable emerging medical radionuclides for PET-based medical imaging with improved resolution.  However, as proton-induced reaction data in this mass region is poorly-characterized, this measurement offers a valuable opportunity to study these underlying physical reaction mechanisms through the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions. Additionally, this measurement provides a benchmark across a wide range of mass and energy for a suite of commonly-used reaction modeling codes, to illustrate deficiencies in the predictive capabilities of these codes, and provide experimental data to help tune them.

% \pagebreak

% which have been proposed as a new monitor reaction standard for the in-beam measurement  of proton fluence in energetic (\textgreater 40 MeV) proton beams.

\noindent The methodology used to measure these cross sections involved a stacked-target activation of thin (25 \SI{}{\micro\meter}) metal foils,  at the Lawrence Berkeley National Laboratory's 88-Inch Cyclotron. Target foils of natural iron metal were irradiated with nominal 55~MeV and 25~MeV proton beams, along with copper and titanium monitor foils at each energy position.   This stack design allows for measurement of cross sections at multiple energies within a single irradiation. This technique is widely-used for measurements of excitation functions, with multiple measurements of the sort having been previously published in PRC, both recently and historically\footnotemark[5]\footnotemark[6]\footnotemark[7]\footnotemark[8]. 
Our work also makes use of the ``variance minimization'' techniques described in our recent work\footnotemark[10] to significantly reduce the systematic uncertainties associated with energy assignment, typical in many stacked-target irradiations.

\footnotetext[5]{J.W. Engle, \emph{et. al.}, PRC 88.1 (2013): 014604.}
\footnotetext[6]{A. Belhout, \emph{et. al.}, PRC 76.3, (2007): 034607.}
\footnotetext[7]{R.L. Brodzinski, \emph{et. al.}, PRC  4.4 (1971): 1257--1265.}
\footnotetext[8]{H.R. Heydegger, \emph{et. al.}, PRC 6.4, (1972):  1235--1240.}
\footnotetext[9]{E. Lamere, \emph{et. al.}, PRC 100.3 (2019):034614.}
\footnotetext[10]{A.S. Voyles, \emph{et. al.},  NIM B: 429, pp. 53–74, Aug. 2018, doi:10.1016/j.nimb.2018.05.028.}

\noindent Several major novel contributions are reported in the present work. Most notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction below 60~MeV to date, with cross sections measured  at the 6--10\% uncertainty level. 
% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.
% In addition, the \ce{^{nat}Nb}(p,x) measurements in this work fill in the extremely sparse data in this energy region, and have been measured with the highest precision relative to existing literature data. 
Indeed, nearly all cross sections 
% for both \ce{^{nat}Nb}(p,x) and \ce{^{nat}Cu}(p,x) 
have been reported with higher precision than previous measurements.
We also report  the first measurements of the independent cross sections for \ce{^{nat}Fe}(p,x)\ce{^{49,51}Cr}, \ce{^{51,52m,52g,56}Mn}, and \ce{^{58m,58g}Co}. 
% All of the models failed to reproduce the isomer-to-ground state ratio for 
% first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
We  use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for the $E_p$~\textless~55\,MeV region in \ce{^{nat}Fe}(p,x),  \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reactions.
% Finally, we present evidence for \ce{^{22,24}Na} contamination of the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reaction channels, due to activation of silicon via \ce{^{nat}Si}(p,x)\ce{^{22,24}Na}  in the silicone-based adhesive used for sealing foils.
% This phenomenon has been observed as an unattributable systematic enhancement of apparent \ce{^{22,24}Na}-based fluence monitors in prior work. 
% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid unintentionally reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
% Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

%%

% Furthermore, this work presents the first measurements of several observables in these mass regions.
% This work reports the first experimental measurement of the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90 MeV region.
% It also represents  the first measurement of the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, as well as the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
% The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} ($\sfrac{9}{2}^+$) / \ce{^{85\text{g}}Y}  ($\sfrac{1}{2}^-$) isomer branching ratio via \ce{^{nat}Nb}(p,x).

% Notably, this work serves as the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100 MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
% This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100 MeV.
% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
% \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed, which makes activity quantification trivial.
% In addition, \ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
% Finally, the production of \ce{^{90}Mo}  in the 40--90 MeV region is quite strong, with a peak cross section of approximately 120 mb.
% Combining the reaction yield and gamma abundance, the use of approximately 23 mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90 MeV region.
% This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24 hours in duration.

%%

\noindent The attached manuscript is an original work which bears no significant overlap with any journal or conference papers published by any of the authors herein, aside from extending the energy range of our earlier \ce{^{nat}Cu}(p,x) measurements  down to reaction thresholds\footnotemark[9]. 
Previous measurements exist in the literature for approximately half of the cross sections presented in this work, though our measurements nearly exclusively have the highest precision to date.
% in the energy region for this work. 
The   most recent previous measurements of the \ce{^{nat}Fe}(p,x) reactions are generally by S.A. Graves, \emph{et. al.}\footnotemark[11], the most recent previous measurements of the \ce{^{nat}Cu}(p,x) reactions are generally from our earlier work\footnotemark[10], and the most recent previous measurements of the \ce{^{nat}Ti}(p,x) reactions are generally by E. Garrido, \emph{et. al.}\footnotemark[12].

While I defer to your judgment in the selection of potential reviewers, if there is any difficulty in finding suitable reviewers, several notable experts have been proposed as potential reviewers for this manuscript: 
% Md. Uddin of the Atomic Energy Research Establishment, Bangladesh (\url{md.shuzauddin@yahoo.com}), 
Steve Wender of Los Alamos National Laboratory  (\url{wender@lanl.gov}), Ron Nelson of Los Alamos National Laboratory  	   (\url{rnelson@lanl.gov	}), Steven Yates of the University of Kentucky	  (\url{yates@uky.edu	}), Arjan Plompen of the Belgian Joint Research Centre	   (\url{Arjan.Plompen@ec.europa.eu	}), Roland Beyer of Helmholtz-Zentrum Dresden-Rossendorf	  (\url{roland.beyer@hzdr.de	}), and Zsolt Revay of the Technical University of Munich	  (\url{zsolt.revay@frm2.tum.de	}).  All of these individuals are highly experienced in the nuclear data community, and have many years of experience in nuclear reaction evaluation and cross section measurements.
% 
% As a physicist with a background in ion beam interactions and accelerator physics, I believe that Mark Breese would be the best-qualified editor to handle this paper during the review process. In addition, I have worked with him previously for the publication of a recent article\footnotemark[11], and had a very smooth experience - it would be a pleasure to work with him once more. However, a
Any of the editorial staff with the technical background to properly evaluate the manuscript would be welcome on our end.  This would primarily involve a familiarity with activation experiments and nuclear spectroscopy.

\footnotetext[11]{S.A. Graves, \emph{et. al.}, NIM B: 386, 44--53 (2016), doi:10.1016/j.nimb.2016.09.018}
\footnotetext[12]{E. Garrido, \emph{et. al.}, NIM B: 383 Supplement C, 191--212 (2016), doi:10.1016/j.nimb.2016.07.011}
% \footnotetext[9]{Y.E. Titarenko, \emph{et. al.}, Phys. At. Nucl., 74, 4, 537 (2011), doi:10.1134/S106377881104017X}
% \footnotetext[10]{G.F. Steyn, \emph{et. al.},  J. Korean Phys. Soc., 59, 23, 1991--1994 (2011), doi:10.3938/jkps.59.1991}
% \footnotetext[11]{A.S. Voyles, \emph{et. al.}, NIM B: 410, 230--239, (2017) doi:10.1016/j.nimb.2017.08.021}

% If I may make one personal request, it would mean a great deal to me if the processing of this manuscript can be expedited in any way, to be able to get it to the referees as quickly as possible without any loss of integrity to the review process. 
% I am in my last several months of my PhD studies, and if this manuscript is able to be accepted for the July 2018 issue of NIM B, I will be able to include it as part of my doctoral dissertation.
% Along with many rounds of revisions with my co-authors, we have put great effort into producing what we consider a manuscript of significant merit to the field, which provides an example of rigorous analysis and uncertainty quantification for cross section data with wide-ranging applications.

Please find our manuscript attached.  I hope that this work will be deemed of sufficient merit and interest to be published in PRC, and I look forward to working with the editorial staff if this is the case.

\closing{Sincerely yours,}

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2019-10-25 fe_px_paper/fe_body_text.tex
Removed Alex as co-author. Implemented all Public Utterance changes and submitted to PRC!

@@
 % performed a   measurement of 
-measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on natural iron.
+measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on Fe.
+% natural iron.
 % This was carried out 
@@
 % natural iron foils 
-iron foils of natural isotopic abundance with titanium and copper monitor foils.
+% iron 
+Fe foils of natural isotopic abundance with 
+% titanium 
+Ti and 
+% copper 
+Cu monitor foils.
 % While recent work has been performed in the 40--100\,MeV energy region, t
@@
 However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
-This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of secondary protons not seen in the activation data.
+This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of lower-energy secondary protons not seen in the activation data.
 As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.

### 2020-01-03 fe_px_paper/cover_letter.tex
Added data availability statement. Modified template and submitted to EPJ-A.

@@
 Editorial Board \\
-Physical Review C}
+European Physical Journal A}
 
@@
 
-\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in Physical Review C. 
+\noindent I am writing to submit an original manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in European Physical Journal A. 
 % We are confident that it will interest your audience. 
@@
 % Toshihiko Kawano\footnotemark[6],  and Francois M. Nortier\footnotemark[3].
+In the spirit of full disclosure, this manuscript was previously submitted for publication in PRC in October 2019, and was declined for peer review after a two month delay.
+As a result, it is no longer under consideration for publication in PRC, nor in any other journal.
 
@@
 This stack design allows for measurement of cross sections at multiple energies within a single irradiation.
-This technique is widely-used for measurements of excitation functions, with multiple measurements of the sort having been previously published in PRC, both recently and historically\footnotemark[5]\footnotemark[6]\footnotemark[7]\footnotemark[8].
+This technique is widely-used for measurements of excitation functions, with multiple measurements of the sort having been previously published in the literature, both recently and historically\footnotemark[5]\footnotemark[6]\footnotemark[7]\footnotemark[8].
 Our work also makes use of the ``variance minimization'' techniques described in our recent work\footnotemark[10] to significantly reduce the systematic uncertainties associated with energy assignment, typical in many stacked-target irradiations.
@@
 Please find our manuscript attached.
-I hope that this work will be deemed of sufficient merit and interest to be published in PRC, and I look forward to working with the editorial staff if this is the case.
+I hope that this work will be deemed of sufficient merit and interest to be published in EPJ-A, and I look forward to working with the editorial staff if this is the case.
 

### 2020-01-03 fe_px_paper/fe_body_text.tex
Added data availability statement. Modified template and submitted to EPJ-A.

@@
 % designs for this work are presented 
-are in \autoref{tab:fe_stack_table} of Appendix \ref{sec:fe_stack_design}.
+are in \autoref{tab:fe_stack_table} of 
+% Appendix 
+\ref{sec:fe_stack_design}.
 
@@
 In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
-Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
+Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
+% Appendices 
+\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
 The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
@@
 
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
+ \label{fig:51Mn}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+ \label{fig:temp_52Mn}
+\end{figure}
+
 For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
- \label{fig:51Mn}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
- \label{fig:temp_52Mn}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[h]
  \centering

### 2020-05-13 fe_px_paper/fe_body_text.tex
Pulling fixes to EPJ template from the Np paper.

@@
 We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,MeV for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
+This work offers a clear warning against unchecked use of  such default calculations, even if performed with the latest developments in nuclear reaction modeling codes. 
+For work requiring even modest accuracy (say 20\%) in their default predictive capabilities, these codes clearly cannot be used to satisfaction.   
 Finally, this work provides another example of the current issues with modeling of  stopping power in stacked target charged particle irradiation experiments, corrected using variance minimization techniques.

### 2020-12-03 fe_px_paper/Response_to_Reviewers.tex
Preparation for 2nd round PU review

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage[ampersand]{easylist}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{amsmath}

\newfloat{figure}{htbp}{figs}

% \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
\newcommand{\colornote}[1]{\textcolor{red}{#1}}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\pp}[1]{\left( #1\right)}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Dr. Jose Benlliure \\
Editor \\
European Physical Journal A}

\begin{flushleft}
{\large\bf Andrew S. Voyles, Ph.D.}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
% \hfill The University of California, Berkeley \\
\hfill Lawrence Berkeley National Laboratory \\
\hfill Building 088-163D  |  M/S 88R0192, Berkeley, CA  94720-1730 \\
% \hfill (presently) +47 486 43 444 \\ 
\hfill  +1 (850) 281-0217 (mobile) or +1 (510) 486-7310 (office) 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Dr. Benlliure,}

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in European Physical Journal A.  Please find my responses detailed in \colornote{red text.}

  \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.  We would especially like to thank the referees for their thorough reading and critique, which has made it a better paper. Their comments were very constructive and pointed out some valuable improvements.

  Please find the feedback following here, and our revised manuscript attached.

  Sincerely yours,\\ \\ \\ \\ Andrew S. Voyles

% \closing{Sincerely yours,}

  \vfill

 \pagebreak

 Referee \#1:

Authors have measured cross sections of the natFe(p,x), natCu(p,x) and natTi(p,x) reactions and done
model calculations using several codes with default parameters. No meaning of model calculations using
default parameter, author should adjust input parameter to fit experimental data.
It seems the paper related to measure cross sections for production of medical isotopes via proton
induced reactions on natFe, which play role to optimize production route; impurities, optimum energy
window, yield, etc. In this paper the above objects are not clearly presented. I would like to suggest to
calculate integral yields and discuss in details.
No meaning of the natCu(p,x) and natTi(p,x) reactions cross section measurements except monitor
reactions. Excitation functions of the monitor reactions induced on Cu and Ti should be determined and
compared with the IAEA recommended curve, which confirms experimental techniques and beam
parameters. Therefore, other reactions from Cu and Ti monitor should be omitted from the paper.

%   \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

Few more comments:

1. P-2, line-15, ‘...........our measured data to probe the role of angular momentum...’.It should
clear and details in discussion.

2. Sample size 2.5 cm x2.5 cm is too large. What is the benefit of such sample size?

3. The notifications ’25 MeV stack’ and ’55 MeV stack’ are not correct.

4. Fig.1 is not special. Setup of 88-inch cyclotron is well characterized. The Fig. 1 should be
omitted.

5. In Fig.2, peak should be identified by energy and nuclide, not by symbol.

6. In Fig.3, why the trend of one stack is different from other.

7. EoB should be replaced by EOB.

8. What is the meaning of value in bracket in Tables.

9. P-8, line 44, ‘The natFe, natCu and natTi(p,x)......’ is not proper writing.

10. Both the numerical values for all investigated reactions should be given in Table and discussed in
details. But author did not discuss details for the reactions in Appendix.

Furthermore, the English and Writing as well as presentation is very poor. I can not recommend for
publication in the present form. It should be revised.

 \colornote{We thank the reviewer for their thoughtful comments....\\\\ ???????}

\pagebreak

 Referee \#2:

The paper \enquote{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV} describes three (six) comprehensive measurement campaigns obtaining data for the production of radioactive nuclides produced by the interaction of protons with natural iron, copper and titanium. The purpose is the determination of accurate excitation curves in support of investigations into alternative or optimized routes for the production of medical radionuclides. The authors use state of the art methods that are described in some detail in this paper and in some further detail in earlier papers involving some of the authors. Two stacks were irradiated for each material at two different energies 55 MeV and 25 MeV. Proton energy is further varied by energy loss straggling in the stack allowing up to 14 different energies from 4 to 53 MeV. The issues with this method concern the proper estimates of average proton energy per foil and the actual flux spectrum. The method is corrected/calibrated using monitor foils with well-determined cross sections but different energy dependence. The spread in results for these monitor foils has to be minimized by the estimates of proton energy and proton fluence spectra. Two methods are used. The first involves the use of FLUKA, a well-known simulation code with a long record of use in a variety of problems. The other method is not clearly described. The uncertain foil thicknesses (Al degraders, and kapton for 25 MeV) were adjusted to minimize the variation in fluence estimates from the one but last stack of monitor foils. The success of the method is demonstrated in Figure 3.
Provided the comments below are clarified, a large number of important new results are obtained. For reactions studied earlier, the accuracy is better than previous single measurements and the agreement with earlier results is good. There are a large number of reaction channels with first data (9 excitation curves, 7 for cross sections and 2 for branching ratios). By itself, these excellent new data obtained by careful experimental methods warrant accepting this publication, after taking care of the modifications suggested below. The paper further offers a clear warning against unchecked use of model calculations, even if performed with the latest developments in nuclear modelling codes. For work requiring even modest accuracy (say 20\%), these codes cannot be used to satisfaction. This warning may be more clearly highlighted in the conclusions of this paper.

\colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

Improve the description of the fitting method for minimizing the variance in the experimental fluence. The method is not clear now. Does this use AZ stopping powers and some semi-analytical approach? Expressions used?

\colornote{We thank you for raising this point, and apologize for this being unclear - we attempted to avoid duplication of much of the extensive discussion for this technique, as detailed in our previous work. We have now expanded upon this discussion in section 2.4, to make our methods more clear.  \\\\In short, FLUKA transport simulations were performed multiple times, globally perturbing the effective areal density (as a correction for the FLUKA stopping power model) of the aluminum degraders. Since each energy compartment, containing a Ti , Fe, and  Cu foil, within our stack has 4 independent monitor reactions, the perturbation in degrader density seeks to find which iteration minimizes the standard deviation of these 4 measurements, as the energy spectra from this iteration will best reproduce the IAEA-recommended monitor standard data. Since the thresholds and peaks of these different monitor reactions occur at different energies, a larger variance will be seen as the energy assignments are further away from those that reproduce the IAEA monitor data.  This is shown in a simple example in the attached figure.  So, no expressions are used here - simply finding the iteration which minimizes the standard deviation of the monitor reaction fluences.}

\begin{figure}
 \centering
 \includegraphics[width=0.7\textwidth]{./minimize_fluka_55.pdf}
 % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
%  \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment. Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks. }
%  \label{fig:gspec_femn}
\end{figure}

\colornote{Additionally, I removed the language in this section comparing the minimization results between AZ calculations and FLUKA, as well as Figure 4, which attempted to visually convey this, but I fear caused more confusion than it helped.  Most of the information needed is found in Figure 3B already, so this also helps avoid unnecessary duplication. Since we do not use the linear fit, AZ fluences estimates, or the FLUKA fluence model for any of our actual analysis,  having these in here might have partly led to the confusion.  Of all of this, only the FLUKA energy spectra (which lead to fluences when normalizing to IAEA monitor data) is actually used in our analysis, so I cut the rest to avoid any confusion in the final manuscript.  I hope that helps clarify things for you!}

The 55 MeV and 25 MeV irradiations have overlap: some energies are covered by both irradiations. This can be used to check the consistency of the methods used. However, the results do not clarify which results were obtained with which irradiation so that the reader cannot assert this consistency. Please, clearly specify which data were obtained from each of the two irradiations and show how consistent these are. A new plot or table may be necessary.

\colornote{We thank you for this very thoughtful suggestion. Running two overlapping stacks to build confidence through consistency was our goal for this, but the assignment of each foil to a stack is not clear, as you point out.  Tables 1--4, containing all of the measured cross section and ratio data, have all had a new row added, clearly designating the foil corresponding to each proton energy.}

The discussion speaks about the natural iron results in some detail, but almost nothing is said about the irradiations of natural copper and titanium. Please expand the discussion to obtain a fair description of all results.

I strongly suggest creating three figures in the main text, one for each of the irradiate materials (i.e. take these out of the annex). They should support the discussion about the results. In principle, a discussion should follow the pattern: short statements about the comparison to earlier work by channel, short statements about the agreement with models by channel; overall agreement to earlier data and to particular models. Of course, a grouped approach can be taken (several channels of a given nature). Separate messages about the data and their agreement with model estimates from the potential use of the results. Usefulness of the results should be either in the introduction or in an outlook at the end. There is also where implications should be highlighted (outlook at the end of the paper).

Highlight clearly in the conclusions that model estimates are inadequate for even modest accuracy targets (like 20\%).

\colornote{We thank your for making this important point particularly clear. This point is a vital takeaway from this work, which was not made explicit enough, but has now been more directly addressed in the conclusions.}

If each activation foil is covered on both sides with kapton adhesive then this could be more clearly explained by either a drawing or the explicit mention of this in the tables describing the stacks.Please make this very explicit and mention clearly the best estimates for composition and thickness of these foils.

\colornote{We thank your for this point.  The language in section 2.1 has been updated to reflect this, and a short statement to this effect has been added to the caption of Table 6.}

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2020-12-03 fe_px_paper/fe_body_text.tex
Preparation for 2nd round PU review

@@
 % The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
-The foils were  sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape 
-% --- each piece of tape consists 
+The foils were  sealed into \enquote{packets} between two pieces of  3M 5413-Series Kapton polyimide film tape,  
+each piece of tape 
 consisting of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
@@
  \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment.
-Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks.
+Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Mn} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks.
 }
@@
 % To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
-The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
+The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used here to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
 This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
@@
 % in stack areal densities.
+As in  our prior work, variance minimization treats the effective density of a sensitive set of stack components (such as degraders) as a free parameter in proton transport calculations, to optimize agreement with the IAEA-recommended charged particle monitor standards.
+Across multiple iterations of these simulations, this parameter is uniformly varied to find the energy spectra for each foil which minimizes the standard deviation  of the multiple measurements of proton fluence in a stack compartment.
+The lowest energy position of a stack is often chosen for this, as it is the most sensitive to perturbations of the transport calculations.
+It is important to note that this technique does not imply that the measured density of the stack components is incorrect --- rather, it is used as a surrogate to correct for poorly-characterized stopping power and other systematic uncertainties.
 
@@
 % While it might seem obvious, t
-The contributions to the slowing of the beam due to the adhesive have often been neglected in much work performed to date. 
+The contributions to the slowing of the beam due to the tape's adhesive have often been neglected in much work performed to date. 
 This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but 
@@
 
-In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  was varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
+In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  was varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of measured
+% nominal 
+values, to find the effective density which minimized variance in the measured proton fluence for the four monitor reactions at the lowest energy position (Ti-07, Cu-07).
 For the 25\,MeV stack, the areal density reached in the minimization of the 55\,MeV stack was used for  the E-09 and H-01 aluminum degraders
@@
 % Using this value, 
-and the areal density of each of the  Kapton tape  layers  was 
+and the areal density of each of the  Kapton tape  layers (both adhesive and backing)  was 
 % likewise 
@@
 % of nominal values
-to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
+to find the effective density which minimized variance in the measured proton fluence for the two monitor reactions at the next-to-lowest energy position (Ti-19, Cu-19).
 These 
@@
 % is conclusive proof 
-indicates that  the true areal densities of the stack components differ from nominally measured values (primarily for the difficult-to-characterize Kapton tape), as transport calculations using nominal areal densities predict that the beam should exit the stack
+indicates that  the stopping power characterization
+% true areal densities of
+for the stack components 
+% differs from nominally measured values 
+(primarily for the difficult-to-characterize Kapton tape) is significantly underestimated, as transport calculations using nominal areal densities predict that the beam should exit the stack 
 % (at the SS-6 profile monitor) 
@@
 %
+
 The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average 22.71\,MeV protons entering the last energy position of the 55\,MeV stack.
 This is approximately 2\,MeV lower than the 
+nominal 
+FLUKA simulations,
+% , and approximately 2\,MeV lower than 
 % nominal 
-FLUKA simulations, and approximately 2\,MeV lower than 
+% A\&Z calculations, both of 
+which used the 
 % nominal 
-A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
+2.68\,g/cm$^3$ measured density of the  aluminum degraders.
 This energy corresponds to an aluminum areal density  4.43\% greater than 
@@
 % serves as a lump correction 
-corrects for other minor systematic uncertainties in stack design.
+corrects for stopping power characterization and other minor systematic uncertainties in stack design.
 % , including stack areal densities and incident beam energy.
-Similarly, for the 25\,MeV stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations, and approximately 5\,MeV lower than nominal A\&Z calculations.
+Similarly, for the 25\,MeV stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations.
+% , and approximately 5\,MeV lower than nominal A\&Z calculations.
 This energy corresponds to a Kapton tape areal density of 5.69\% greater than nominal measurements, which is completely reasonable given the lack of areal density data from the manufacturer.
@@
 A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
-Open data points represent the 25\,MeV stack, and closed data points represent the 55\,MeV stack.}
+Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack.}
      \label{fig:fe_variance_mins}
@@
 % 
-An enhanced version of the final \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reaction fluences is shown in \autoref{fig:fe_fluence_plot}.
+% An enhanced version of the final \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reaction fluences is shown in \autoref{fig:fe_fluence_plot}.
 % Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
-The uncertainty-weighted mean  for the two \ce{^{nat}Cu}(p,x) and two \ce{^{nat}Ti}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Cu and Ti foils, respectively, and the uncertainty-weighted mean  for all four monitor channels was used to determine the final fluence assignments for the Fe foils.
-Uncertainty in each final proton fluence  is  calculated by error propagation of the individual monitor channel fluence values  at each energy position.
-These weighted-mean fluences are  plotted  in \autoref{fig:fe_fluence_plot}, along with the estimated fluence according to both  FLUKA transport 
-and an uncertainty-weighted linear $\chi^2$ fit to the individual monitor channel fluence measurements.
-Both models reproduce the observed fluence data consistently within uncertainty for the 55\,MeV stack, with the FLUKA model predicting a slightly greater fluence loss throughout the stack.
-However, neither model is capable of accurately modeling the rapid decrease in apparent fluence at the rear of the 25\,MeV stack.   
-These models are used purely to provide an extrapolation from the highest-energy position back to the \enquote{front} of each stack, to compare with the nominal fluence measured by  the beamline current integrators.
+The correlated uncertainty-weighted mean  for the two \ce{^{nat}Cu}(p,x) and two \ce{^{nat}Ti}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Cu and Ti foils, respectively, and the correlated uncertainty-weighted mean  for all four monitor channels was used to determine the final fluence assignments for the Fe foils.
+This correlated uncertainty-weighted mean was calculated as:
+\begin{equation} \label{eq:weighted_average_beamcurrent}
+    \langle I \rangle  = \frac{ \sum_{i,j} I_j  \left( \mathbf{V}^{-1}_{ij}  \right) }{\sum_{i,j}  \left( \mathbf{V}^{-1}_{ij}  \right)} 
+\end{equation}
+Uncertainty in each final proton fluence  is  calculated by error propagation of the individual monitor channel fluence values  at each energy position:
+\begin{equation}
+    \label{eq:corrWeight}
+    \delta_{\langle I \rangle} = \sqrt{\frac{ 1}{\sum_{i,j}  \left( \mathbf{V}^{-1}_{ij}  \right)}} 
+\end{equation}
+Each element $ij$ of the covariance matrix is calculated using the robust
+sandwich estimator  \cite{huber1967behavior}:
+\begin{equation}
+    \label{eq:Vij}
+    \mathbf{V}_{ij} = \mathrm{Cov}[I_i, I_j] = \sum_{\beta} \frac{\partial I}{\partial \beta_i} \delta_{\beta_i} \mathrm{Corr}[\beta_i, \beta_j] \delta_{\beta_j} \frac{\partial I}{\partial \beta_j}
+\end{equation}
+where $i,j$ are the monitor reactions in a given compartment, and $\beta \in [A_0$, $\rho \Delta r$, $\lambda$, $\Delta t_{irr}$, $\int \sigma(E) \frac{d\phi}{dE}dE$]. 
+% $\Sigma_{\beta_{ij}}$ is the correlation matrix for each $\beta$. 
+$A_0$ is assumed to be 30\% correlated for all reactions, $\rho \Delta r$ is assumed to be 100\% correlated for reactions from the same monitor foil, $\lambda$ is assumed to be uncorrelated, $\Delta t_{irr}$ is assumed to be 100\% correlated, and $\int \sigma(E) \frac{d\phi}{dE}dE$ is assumed to be 30\% correlated for reactions from the same monitor foil.
+
+% Uncertainty in each final proton fluence  is  calculated by error propagation of the individual monitor channel fluence values  at each energy position.
+% These weighted-mean fluences are  plotted  in \autoref{fig:fe_fluence_plot}, along with the estimated fluence according to both  FLUKA transport 
+% and an uncertainty-weighted linear $\chi^2$ fit to the individual monitor channel fluence measurements.
+% Both models reproduce the observed fluence data consistently within uncertainty for the 55\,MeV stack, with the FLUKA model predicting a slightly greater fluence loss throughout the stack.
+% However, neither model is capable of accurately modeling the rapid decrease in apparent fluence at the rear of the 25\,MeV stack.   
+% These models are used purely to provide an extrapolation from the highest-energy position back to the \enquote{front} of each stack, to compare with the nominal fluence measured by  the beamline current integrators.
 % 
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=0.495\textwidth]{./figures/fluence_plot.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.
+% \begin{figure}
+%  \centering
+%  \includegraphics[width=0.495\textwidth]{./figures/fluence_plot.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions.
 Open data points represent the 25\,MeV stack, and closed data points represent the 55\,MeV stack.}
-%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
-%   A clear loss of 
-%   The fluence  drops by approximately \textred{7.2--8.9\%} from the incident fluence of \textred{196.9--198.8 nAh} over the length of each target stack, based on fluence loss models from FLUKA simulations and an empirical fit to  fluence measurements.}
-%   This is due to a combination of beam utilization, as well as scattering.}
- \label{fig:fe_fluence_plot}
-\end{figure}
+% %  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
+% %   A clear loss of 
+% %   The fluence  drops by approximately \textred{7.2--8.9\%} from the incident fluence of \textred{196.9--198.8 nAh} over the length of each target stack, based on fluence loss models from FLUKA simulations and an empirical fit to  fluence measurements.}
+% %   This is due to a combination of beam utilization, as well as scattering.}
+%  \label{fig:fe_fluence_plot}
+% \end{figure}
 
@@
 \ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
-Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn}, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
+Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn} and long-lived Co radiocontaminants, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
 It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer.
@@
 % \def\arraystretch{1.5}
-\begin{table}
+\begin{table*}
  \caption{Default settings for the reactions codes}

### 2020-12-04 fe_px_paper/fe_body_text.tex
Added extra Fe results discussion

@@
 
-\subsection{Measurement of nuclear excitation functions}
+% \subsection{Measurement of nuclear excitation functions}
 
@@
 % , producing a Bragg peak at this location.  
-Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh
-% 18.8$\pm$1.0\,nAh
-was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
-Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
-% 33.2$\pm$4.7\,nAh
-was calculated to be incident upon the 
-% 55\,MeV 
-target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
-% 37.0$\pm$9.3\,nAh using the linear fit model.
-% All of these 
-Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
-% beamline 
-current integrators.
-However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
-This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of lower-energy secondary protons not seen in the activation data.
-As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
-This incident fluence dropped by approximately 
-% 9.5\% to  17.0$\pm$2.4\,nAh (and by 
-8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
-This loss of fluence is due to a combination of 
-% beam utilization for the various 
-(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
+% Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh
+% % 18.8$\pm$1.0\,nAh
+% was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
+% Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
+% % 33.2$\pm$4.7\,nAh
+% was calculated to be incident upon the 
+% % 55\,MeV 
+% target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
+% % 37.0$\pm$9.3\,nAh using the linear fit model.
+% % All of these 
+% Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
+% % beamline 
+% current integrators.
+% However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
+% This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of lower-energy secondary protons not seen in the activation data.
+% As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
+% This incident fluence dropped by approximately 
+% % 9.5\% to  17.0$\pm$2.4\,nAh (and by 
+% 8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
+% This loss of fluence is due to a combination of 
+% % beam utilization for the various 
+% (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
 
@@
 presented in \autoref{tab:ti_rp_table}.
-In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
-Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
-% Appendices 
-\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
+In addition, as there exist a number of isomers with 
+% radioactive 
+unstable ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
+% Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
+% % Appendices 
+% \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
 The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
@@
 \input{./fe_body_tables}
+
+The measured cross sections were compared to the predictions by the reaction codes TALYS, EMPIRE, CoH, ALICE, and by the calculations in the TENDL database.
+The codes were all explicitly run using their default parameters, for two primary motivations. 
+First, this  assesses their claims of  predictive capabilities  --- many \enquote{casual} users (i.e., outside of data evaluation) will likely not make significant adjustments to the massively multi-parameter physics models used in these codes, nor should they need to, due to an expectation of reasonable accuracy in these results.
+Indeed, TALYS and TENDL  are routinely used for modeling cross sections in initial target designs for isotope production applications.
+Second, our recent work has shown that  arbitrary parameter optimization (tuning to provide a best fit to a single reaction channel)  often provides non-unique solutions, causing neighboring reaction channels (e.g., (p,4n) vs.
+(p,p3n)) to suffer \cite{fox2020investigating}.
+Without a global physical basis for optimization (as in the process of reaction evaluation), an unchecked fit to experimental data offers no insight for reaction modeling, and may propagate to highly non-physical results for  competing channels.
+% in order to assess their predictive capabilities for the casual user.
+% The explicit use of default parameters was chosen for two reasons ---
+
+The default settings for the optical models and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
+The level density models for each are as follows.
+For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
+In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
+This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
+This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
+Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.
+The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
+As a result, this analysis is useful for a qualitative comparison of default predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
 
@@
 
+% \subsection{Comparison of reaction modeling with experimental results}
+
+% \def\arraystretch{1.5}
+\begin{table*}
+ \caption{Default settings for the reactions codes}
+ \label{tab:fe_defaults}
+ \resizebox{\textwidth}{!}{%
+\begin{tabular}{ c c c c}
+
+ \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
+ EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
+ TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
+  CoH-3.5.3\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
+  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
+
+\end{tabular}
+}
+\end{table*}
+
 These results have several notable features.
@@
 No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
-
-% Furthermore, t
-This work presents the first measurements of several observables in 
-% these mass regions.
-% This work reports the first experimental measurement of
-this mass region, including the \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region,
-% It also represents  the first measurement of 
-the independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
-The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr},\ce{^{52g}Mn},\ce{^{58g}Co} cross sections.
-% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
-% (${^{1}/_{2}}^{-}$)
-% ($\sfrac{1}{2}^-$) 
-% isomer branching ratio via \ce{^{nat}Nb}(p,x).
-
-% \textred{Comment on possible monitor reactions  here...}
-
-Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
-In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
-It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
-Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
-This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
-Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds of nearly 20\,MeV.
-This provides some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region, which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.
-
-% \textred{All: feel free to add additional details of 51/52Mn production here...}
-
-Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
-This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+Discussion of notable reaction channels follows here, and 
+comparisons  of the
+remaining measured cross sections and isomer branching ratios with modeling results and literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
+% Appendices 
+\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
+
+% Quick observations:
+% 
+% \begin{enumerate}
+%  \item Modeling on Fe is significantly better than for Cu/Ti
+%  \item On the whole, ALICE seems to do the best job overall
+%  \item (p,$\alpha$x) channels are done fairly well, (p,2p2nx) are worse, and (p,$\alpha$xn) are really lousy
+%  \item Location and shape of rising edges/compound peaks appears much better than in the Nb IPF paper, possibly due to easier modeling in lower energy regime?
+%  \item Amplitudes of excitation function are still off within factor of 2--3
+%  \item Isomer branching ratios are (surprise, surprise) really bad.  Ti(p,x)\ce{^{44}Sc} is the best, but all three miss the key shape and features
+% \end{enumerate}
+
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section}
+
+This work presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction in this energy region.
+However, below the 24.1\,MeV threshold for \ce{^{56}Fe}(p,x)\ce{^{51}Mn}, the single measurement of \ce{^{54}Fe}(p,x)\ce{^{51}Mn} from Levkovski can be renormalized by isotopic abundance, and is consistent  with the present work \cite{levkovski1991cross}.
+For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
+The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
+ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
+As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
+EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
+ \label{fig:51Mn}
+\end{figure}
+
 \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr\,\cite{Klein2000}.
@@
 
-Likewise, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn} cross sections}
+
+% \begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+%  \label{fig:temp_52Mn}
+% \end{figure}
+
+% \begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{./figures/52mMn.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+%  \label{fig:temp_52mMn}
+% \end{figure}
+
+\begin{figure*}
+    \centering
+    \subfloat{
+        \centering
+        \hspace{-5pt}\subfigimg[width=0.485\textwidth]{\hspace{4.5cm}a)}{./figures/52Mn.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+         \label{fig:temp_52Mn}
+   \hspace{-5pt}}%
+     \subfloat{
+        \centering
+
+        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/52mMn.pdf}{50}
+         %         \refstepcounter{subfigure}
+         \label{fig:temp_52mMn}
+   \hspace{-5pt}}%
+    \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.
+b) Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+     \label{fig:discussion_52Mn}
+\end{figure*}
+
+This work presents the first measurement of several observables in this energy region, including the first independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the first measurement of \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+Cumulative  \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn} reaction measurements exist in earlier work, but  this work presents the most well-characterized measurement  below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
+This work is consistent with the general body of previous cumulative \ce{^{52g}Mn} measurements, with the exception of work from Williams, Lagunas-Solar, and Barchuk, all of which have shown discrepancies with prior data in other reaction channels measured here \cite{barchuk1987excitation,Lagunas-Solar1979a,PhysRev.162.1055}.
+
+% Cutting as part of results reorganization
+%
+% For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
+% The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
+% As a result, this analysis is useful for a qualitative comparison of default predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
+% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
+% For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
+% The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
+% ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
+% As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
+% EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
+% This is seen again in the  
+For the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, seen in Figure \autoref{fig:temp_52Mn},  the first peak is well-modeled by TALYS and TENDL, but  rises much more rapidly than the data would support above 50\,MeV.
+CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct shape.
+Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section, seen in Figure \autoref{fig:temp_52mMn}, the effect of spin distributions in highly-excited nuclear states can be studied.
+The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 50\% at the peak energy.
+TALYS predictions show approximately 1.5$\sigma$ agreement with this measurement, but CoH significantly overestimates this ratio at all energies, and EMPIRE overestimates as well in the pre-equilibrium tail,
+% All three codes predict about 50\%, 
+which indicates that the isomer feeding is not well-modeled in these codes.
+It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.
+
+% 
+% In the other isomer-to-ground state ratio measured for Fe,  \ce{^{nat}Fe}(p,x)\ce{^{58}Co}, the opposite is seen -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
+% Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling.
+% % However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
+
+% Likewise, 
+Like \ce{^{51}Mn}, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
 Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%)\,\cite{Graves2015,Wooten2015}.
@@
 However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$~\pm~$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator\,\cite{Blauenstein1997}.
-Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
+
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Fe}(p,x)\ce{^{56,58}Co} cross sections}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/58Co_IBR.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), with the \ce{^{58}Fe}(p,n)\ce{^{58m}Co} reaction channel visibly peaking at approximately \mbox{20 MeV}.}
+ \label{fig:58Co_IBR}
+\end{figure}
+
+This work presents the first measurements of several observables in 
+% these mass regions.
+% This work reports the first experimental measurement of
+this energy region, including the measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
+the independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), seen in \autoref{fig:58Co_IBR}.
+The cumulative cross sections from these data are both consistent with, and higher-precision than, existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} cross sections, as well as the large body of measurements for \ce{^{nat}Fe}(p,x)\ce{^{56}Co}.
+
+Despite being weakly-fed, EMPIRE, CoH, and TALYS/TENDL all do an excellent job of reproducing earlier work and this measurement, for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
+This holds for both the shape and magnitude of each excitation function, though CoH overestimates the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} peak magnitude by approximately 30\%, despite matching the rising and falling edges of the curve.
+However, for both the \ce{^{nat}Fe}(p,x)\ce{^{56,58g}Co} channels, ALICE underestimates the magnitude of the rising edge and compound peak by nearly 50\%, though it shows the best agreement of these codes with the magnitude of the pre-equilibrium tails for these channels.
+Additionally, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\%, and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work.
+% In 
+As opposed to the other isomer-to-ground state ratio measured for Fe,  the opposite is seen for \ce{^{nat}Fe}(p,x)\ce{^{58}Co} -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
+Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling, or an underestimation of high-spin transfer in pre-equilibrium neutron emission.
+% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
+
+Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
+In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
+Given that \ce{^{nat}Cu}(p,x)\ce{^{56}Co} is an established monitor reaction, it seems likely that an evaluation of \ce{^{nat}Fe}(p,x)\ce{^{56}Co} as a monitor standard could provide a useful complement to existing low-to-intermediate energy monitor reactions.
+A similar argument can also be applied to \ce{^{nat}Fe}(p,x)\ce{^{58}Co}, which is another established copper monitor reaction product.
+While this channel shares many of the same attractive features as \ce{^{nat}Fe}(p,x)\ce{^{56}Co}, the weak feeding of \ce{^{58}Co} makes this far less of an attractive option in comparison.
+
+In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications,
+including the non-standard positron emitter 
+% \ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
+%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
+\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}.
+% \ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+% \ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
+% \ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
+% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
+% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
+% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
+% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
+% and the $\beta^-$-therapeutic agent 
+% \ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
+% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
+Production of this radionuclide offerss no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
+The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
+While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
+The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.
+
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Fe}(p,x)\ce{^{49, 51}Cr} cross sections}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/51Cr_ind.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.}
+ \label{fig:51Cr_ind}
+\end{figure}
+
+This work presents the first measurement of \ce{^{nat}Fe}(p,x)\ce{^{49}Cr} and  the first independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} in this energy region, seen in \autoref{fig:51Cr_ind}.
+The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} cross sections, and with improved precision.
+As seen in other channels, the work of Williams and Schoen \cite{PhysRev.162.1055,Schoen1979a} are both significantly lower in magnitude, and with cross sections peaking approximately 5\,MeV higher than body of other measurements.
+While the \ce{^{51}Cr} decay data used in these experiments (Williams: $t_{1/2}=27.8$ d, $I_\gamma$=9\%, Schoen: $t_{1/2}=27.71$ d, $I_\gamma$=10.2\%) differ slightly from those used here ($t_{1/2}=27.704(3)$ d, $I_\gamma$=9.910(10)\% \cite{Wang2017}), these differences do not account for the approximately 50\% smaller peak cross section reported by Williams, and approximately 30\%  smaller for Schoen.
+Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation, possibly suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was not considered.
+
+For both the  \ce{^{49,51}Cr} channels, the shape is well-modeled by all codes in the energy range covered in this measurement, though ALICE appears to peak approximately 3\,MeV higher than the other codes.
+For \ce{^{49}Cr}, ALICE and CoH both overestimate the magnitude of this channel by approximately 30\%, ALICE overestimates  by approximately 350\%, while TALYS and TENDL underestimate the magnitude by approximately 50\%.
+Weakly-fed channels such as \ce{^{49}Cr} are often sensitive, as the modeling of more strongly-fed channels tends to impose strong constraints upon the magnitude of remaining channels.
+Modeling of \ce{^{51}Cr} shows improved agreement in magnitude --- CoH and ALICE are consistent at the 1$\sigma$ level, EMPIRE overestimates the peak by approximately 25\%, and TALYS/TENDL underestimate the peak by approximately 60\%.
+However, this level of disagreement is more concerning than for \ce{^{49}Cr}, due to the strong feeding of this channel.
+This observation provides a clear illustration that both TALYS/TENDL tend to either match or significantly underestimate, but never overestimate, the magnitude of many reaction channels below 70\,MeV seen in this work.
+Since the sum of all channel cross sections are constrained by the total reaction cross section, this would suggest that TALYS is either overestimating the feeding of channels with stable residual nuclei, or the elastic/inelastic channels.
+
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Fe}(p,x)\ce{^{54, 56}Mn} cross sections}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/54Mn.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} independent cross section, with the \ce{^{56}Fe}(p,2pn)\ce{^{54}Mn}/\ce{^{57}Fe}(p,2p2n)\ce{^{54}Mn} reaction channels visibly peaking at approximately \mbox{40 MeV}.}
+ \label{fig:54Mn}
+\end{figure}
+
+This work presents the first measurements the \ce{^{nat}Fe}(p,x)\ce{^{56}Mn} reaction below 70\,MeV.
+Additionally, we report the highest precision measurement of \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} in this energy region.
+This measurement is consistent with earlier work aside from the globally-discrepant Williams data, as discussed previously.
+Modeling of these channels presents a counterpoint to the \ce{^{51,52}Mn} results discussed earlier - \ce{^{54}Mn} is   well-modeled by CoH, TENDL, and TALYS, though EMPIRE overestimates the peak cross section by approximately 25\%, and ALICE underestimates by the same, in addition to peaking approximately 3\,MeV higher.
+The weakly-fed \ce{^{56}Mn} is poorly modeled in comparison, with CoH, EMPIRE, and ALICE failing to match neither the shape nor magnitude of the excitation function, though TALYS/TENDL matches both.
+While the poorly-modeled \ce{^{51,52}Mn} channels are dominated by alpha particle emission,  \ce{^{54}Mn} production is more characterized by the the emission of the constituent protons and neutrons.
+Since TALYS, TENDL, and CoH exhibited poor predictive power for \ce{^{51,52}Mn}, but reproduced \ce{^{54}Mn} well, this observation would suggest that the alpha optical models employed in these codes are underestimating the strength of alpha emission in this energy region.
+
+% % Cutting as part of results reorganization
+% %
+% % Furthermore, t
+% This work presents the first measurements of several observables in 
+% % these mass regions.
+% % This work reports the first experimental measurement of
+% this mass region, 
+% % including the \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, 
+% % \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  
+% % \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, 
+% % and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
+% % It also represents  the first measurement of 
+% the independent cross sections for      
+% % \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, 
+% % \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, 
+% % and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).  
+% % The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr},\ce{^{52g}Mn},\ce{^{58g}Co} cross sections.
+% % Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
+% % (${^{1}/_{2}}^{-}$)
+% % ($\sfrac{1}{2}^-$) 
+% % isomer branching ratio via \ce{^{nat}Nb}(p,x).
+
+% \textred{Comment on possible monitor reactions  here...}
+
+% In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+% It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
+Similarly to \ce{^{56}Co},  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  offers another interesting possibility as a \ce{^{nat}Fe}(p,x) monitor reaction.
+This radionuclide ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
+This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
+Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds of nearly 20\,MeV.
+This provides some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region, which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.
+
+% \textred{All: feel free to add additional details of 51/52Mn production here...}
+
+% Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
+% This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+% 
+% 
+% 
+% Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
 
@@
 % \textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}
+
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Ti}(p,x)\ce{^{54, 56}}????? cross sections}
 
@@
 % This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
-The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
-While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
-The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.
-
-\subsection{Comparison of reaction modeling with experimental results}
-
-% \def\arraystretch{1.5}
-\begin{table*}
- \caption{Default settings for the reactions codes}
- \label{tab:fe_defaults}
- \resizebox{\textwidth}{!}{%
-\begin{tabular}{ c c c c}
-
- \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
- EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
- TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-  CoH-3.5.3\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
-  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
-
-\end{tabular}
-}
-\end{table*}
-
-% Quick observations:
-% 
-% \begin{enumerate}
-%  \item Modeling on Fe is significantly better than for Cu/Ti
-%  \item On the whole, ALICE seems to do the best job overall
-%  \item (p,$\alpha$x) channels are done fairly well, (p,2p2nx) are worse, and (p,$\alpha$xn) are really lousy
-%  \item Location and shape of rising edges/compound peaks appears much better than in the Nb IPF paper, possibly due to easier modeling in lower energy regime?
-%  \item Amplitudes of excitation function are still off within factor of 2--3
-%  \item Isomer branching ratios are (surprise, surprise) really bad.  Ti(p,x)\ce{^{44}Sc} is the best, but all three miss the key shape and features
-% \end{enumerate}
-
-The measured cross sections were compared to the predictions by the reaction codes TALYS, EMPIRE, CoH, ALICE, and by the calculations in the TENDL database.
-The codes were all run on their default settings, in order to assess their predictive capabilities for the casual user.
-The default settings for the optical models and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
-The level density models for each are as follows.
-For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
-In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
-This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
-This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
-Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
- \label{fig:51Mn}
-\end{figure}
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
- \label{fig:temp_52Mn}
-\end{figure}
-
-For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
-The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
-As a result, this analysis is useful for a qualitative comparison of predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
-% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
-For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
-The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
-ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
-As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
-EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
-This is seen again in the  \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, where the first peak is well-modeled by TALYS and TENDL, but  rises much more rapidly than the data would support above 50\,MeV.
-CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct shape.
-Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section, the effect of spin distributions in highly-excited nuclear states can be studied.
-The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 80\% at the peak energy.
-All three codes predict about 50\%, which indicates that the isomer feeding is not well-modeled.
-It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.
-In the other isomer-to-ground state ratio measured for Fe,  \ce{^{nat}Fe}(p,x)\ce{^{58}Co}, the opposite is seen -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
-Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling.
-% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
-
-% 
-% 
-% 
-% % In this work
-% Cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
-% For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.
-% This, in turn, offers the opportunity to 
-% % use these data to gain insight into 
-% gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
-% The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
-% The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:fe_defaults}. 
-% The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
-% % All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes. 
-% 
-% 
-% The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
-% %\,\cite{add_level_density_models_here}. 
-% The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it\,\cite{Capote2009}.
-% %\,\cite{add_level_density_models_here}.
-% The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.
-% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.
-
-% % The modeling of several of the \ce{^{93}Nb} residual production cross sections are studied in detail here. 
-% % Only total channel residual 
-% Given the large number of exit channels in this data set, we will limit our discussion to  cross sections for the production of a specific residual nucleus with experimental data through the full rise and fall of the peak,
-% % that have only one reaction channel, and that are 
-% and at least 1\% of the total reaction cross section.
-% % are discussed in detail. 
-% % Residual production
-% Exit channel cross sections that do not exhibit the full rise and fall of the peak, which is identified as 
-% % the compound portion of the cross section
-% being dominated by the formation of a compound nucleus, do not provide enough information to analyze the calculations.
-% % Some residuals, such as 
-% Residual nuclei like \ce{^{88}Zr} that can be produced by multiple reaction channels, such as (p,$\alpha$2n) and by (p,2p4n)  are also not discussed in depth. 
-% % Both compound peaks are seen in the data and cannot be separated, so such residuals are not included in the detailed analysis.
-% % Very small channels, 
-% We exclude reactions with cross sections with peak values less than 1\% of the total reaction cross section 
-% % are excluded because the modeling of their cross sections is 
-% because their behavior is extremely sensitive  to  more dominant  channels.
-% The three residual nuclei that meet all of the above criteria for which there is an independent measurement of the residual production cross section are \ce{^{86}Y}, \ce{^{90}Mo}, and \ce{^{90}Nb}.
-% 
-% 
-% The \ce{^{93}Nb}(p,$\alpha$p3n)\ce{^{86}Y} reaction channel, which peaks at approximately \mbox{70\,MeV}, is well within the compound regime for the entire energy region of this experiment (\autoref{fig:86Y}).
-% The data collected on this residual is consistent with the one other data set available, taken in 1997 by Michel \emph{et al.}\,\cite{MICHEL1997153}. 
-% The \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} and \ce{^{93}Nb}(p,p3n)\ce{^{90}Nb} channels both peak early in the energy region, around 50\,MeV, and the data clearly show the full rise, peak, and fall of the compound cross section (\autoref{fig:90Mo} \& \ref{fig:90Nb}).
-% In both of these channels, this data  is consistent with the data by Titarenko \emph{et al.} in 2011\,\cite{Titarenko2011}.
-% 
-% The \ce{^{90}Nb} production cross section exhibits a persistent pre-equilibrium \enquote{tail} that keeps the channel open  well after the compound cross section has fallen away. 
-% TALYS, TENDL, and CoH seem to have the correct shape for this pre-equilibrium cross section, with magnitudes that are just slightly too low.
-% EMPIRE, however, does not level off  as much as the data and the other codes are seen to, and misses the high-energy data points.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/52mMn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
- \label{fig:temp_52mMn}
-\end{figure}
-
-% 
-% In all three channels, the TALYS, TENDL, and CoH calculations rise, peak, and fall at lower energies than the data, while EMPIRE calculates the peak to occur at higher energies.
-% For \ce{^{90}Mo}, the EMPIRE peak is representative of the data.
-% For \ce{^{86}Y} and \ce{^{90}Nb}, the peak is missed by all three  of the codes.
-% 
-% 
-% The magnitudes of the TALYS and TENDL calculations are consistently too low in the three channels studied here. 
-% For \ce{^{86}Y}, CoH and EMPIRE also predict smaller cross sections than the data would suggest, which may be influenced by incorrect modeling of other, stronger, channels.
-% The magnitude of the peak in the CoH calculation for \ce{^{90}Mo}  is consistent  with the data, while EMPIRE predicts a cross section that is approximately the same magnitude as that of TALYS.
-% \ce{^{90}Nb} is one of the strongest measured channels, approximately 10\% of the total reaction cross section, and the values from the three codes are all consistent, but  too small, in magnitude.
+% The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
+% While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
+% The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.
 
@@
 % usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
+
+Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
+This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+
+Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
 

### 2020-12-06 fe_px_paper/Response_to_Reviewers.tex
Restructing of results section

@@
 \let\raggedleft\raggedright                % needed to get date flush left
+\date{13 May, 2020}
 
@@
 
+  \colornote{Lee - should we make any comments about the hostility and unhelpful/incorrect comment from Reviewer 1 here?}
+
   Please find the feedback following here, and our revised manuscript attached.
@@
 
+ \colornote{We thank the reviewer for their thoughtful comments....\\\\ ???????}
+
 %   \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript.
@@
 
+\colornote{Uncertainties are listed in the least significant digit (NDS Style), that is, 131.0(85)\,mb  means 131.0 $\pm$ 8.5\,mb.
+Clarification to this effect has been added to the caption of all tables.}
+
 9. P-8, line 44, ‘The natFe, natCu and natTi(p,x)......’ is not proper writing.
@@
 
+\colornote{We thank your for this important feedback.
+We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data.
+As the large volume of cross section data we reported here  impacts  many applications,  we have added this new discussion to help show the importance of these results.}
+
 Furthermore, the English and Writing as well as presentation is very poor. I can not recommend for
 publication in the present form. It should be revised.
-
- \colornote{We thank the reviewer for their thoughtful comments....\\\\ ???????}
 
@@
 
+\colornote{We thank your for this important feedback.
+We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data.
+Your point that this new data warrants publication was very well-received, and we have added this new discussion to help show the importance of these results.}
+
 Highlight clearly in the conclusions that model estimates are inadequate for even modest accuracy targets (like 20\%).

### 2020-12-06 fe_px_paper/fe_body_text.tex
Restructing of results section

@@
 comparisons  of the
-remaining measured cross sections and isomer branching ratios with modeling results and literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
+remaining measured cross sections 
+% and isomer branching ratios 
+with modeling results and literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
 % Appendices 
-\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
+\ref{sec:fe_xs_figures}.
+% and \ref{sec:fe_ibr_figures}.
 
@@
 
-        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/52mMn.pdf}{50}
+        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/52Mn_IBR.pdf}{50}
          %         \refstepcounter{subfigure}
@@
     \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.
-b) Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
+b) Measured  \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).}
      \label{fig:discussion_52Mn}
 \end{figure*}
+
+Measured \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), with the \ce{^{58}Fe}(p,n)\ce{^{58m}Co} reaction channel visibly peaking at approximately \mbox{20 MeV}.
 
@@
 
-\subsection{\ce{^{nat}Ti}(p,x)\ce{^{54, 56}}????? cross sections}
-
-In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
-These include the non-standard positron emitters 
+\subsection{\ce{^{nat}Cu}(p,x)\ce{^{60,61,64}Cu} cross sections}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/64Cu.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} independent cross section, with the \ce{^{65}Cu}(p,pn)\ce{^{64}Cu} reaction channels visibly peaking at approximately \mbox{25 MeV}.}
+ \label{fig:64Cu}
+\end{figure}
+
+As with many \ce{^{nat}Cu}(p,x) channels, these reactions have been previously measured in our earlier work, but this measurement extends these cross sections down to reaction thresholds, and reports cross sections for many of the short-lived products unable to be observed previously, such as \ce{^{60}Cu} \cite{Voyles2018a}.
+For \ce{^{nat}Cu}(p,x)\ce{^{60,61,64}Cu}, the measurements presented here are consistent with earlier work (aside from that of Williams \cite{PhysRev.162.1055}, as discussed earlier), and are generally the highest-precision measurements to date.
+
+As we reported previously, modeling of \ce{^{nat}Cu}(p,x) reactions is poor in this energy region, despite the relative ease of only two stable target isotopes in copper.
+For \ce{^{60}Cu}, all codes fail to predict the magnitude and shape of the channel, and tend to place the peak approximately 5\,MeV lower than observed.
+Similar behavior is observed in the strongly-fed \ce{^{61}Cu}, though not to the same degree --- the peak shift is approximately 3\,MeV, but the shape predictions are more physical, despite a suppression of the pre-equilibrium tail in  EMPIRE.
+\ce{^{64}Cu} modeling appears to be the best of these channels, with all codes matching the overall shape, but only EMPIRE predicting the rapid rise and fall of the compound peak, compared to the smoother behavior of the other codes.
+Unlike ALICE and EMPIRE, CoH, TALYS, and TENDL all do a successful job of modeling the shape of the (p,pn) pre-equilibrium tail, with this channel showing the best predictive power of the \ce{^{nat}Cu}(p,x) reactions.
+As seen with ALICE for \ce{^{61}Cu}/\ce{^{64}Cu}, the alternating underestimation/overestimation across channels for a single code points to competition between neighboring reaction channels as a common issue in this mass region.
+
+As with the other foils in this experiment, \ce{^{nat}Cu}(p,x)  has  yielded measurements of  a number of additional  medical  radionuclides,  including the non-standard positron emitters 
+\ce{^{57}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
+\ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}, and
+\ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017}.
+However, production of these radionuclides  offers no major advantages over established  pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Cu}(p,x).
+
+% discussion should follow the pattern:
+% short statements about the comparison to earlier work by channel, short statements
+% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.
+
+\subsection{\ce{^{nat}Ti}(p,x)\ce{^{44,47,48}Sc} cross sections}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.5\textwidth]{./figures/44Sc_IBR.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Measured \ce{^{44\text{m}}Sc} ($6^+$) / \ce{^{44\text{g}}Sc}  ($2^+$)  isomer branching ratios via \ce{^{nat}Ti}(p,x).}
+ \label{fig:44Sc_IBR}
+\end{figure}
+
+Due in part to the long-standing use of Ti as a monitor foil,  \ce{^{nat}Ti}(p,x) reactions are better-characterized than many  natural targets.
+While the focus of this work is on the production of \ce{^{51,52}Mn}  and other \ce{^{nat}Fe}(p,x) channels, the cross sections reported here offer improvements to prior work, particularly for the several Sc radionuclides observed.
+For all of the \ce{^{nat}Ti}(p,x)\ce{^{44,47,48}Sc} channels, this work is consistent with all prior data, and is generally the highest-precision measurement to date.
+This work additionally  extends the \ce{^{44g}Sc} excitation function to the highest energy to date.
+
+Perhaps due to the abundance of reaction data available, modeling of these channels is markedly improved  in comparison to the \ce{^{nat}Fe}(p,x) channels discussed previously.
+For \ce{^{44m}Sc}, the shape of the excitation function is well-modeled by EMPIRE, CoH, TALYS, and TENDL, though all of these codes place the compound peak approximately 4\,MeV lower than observed.
+Additionally, EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
+Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but signficantly underestimated by EMPIRE and CoH.
+The same modeling trend is observed for \ce{^{44m}Sc}, though no judgment can be made for the pre-equilibrium tail, due to a paucity of data above 50\,MeV.
+This is reflected in the measured isomer branching ratios for \ce{^{44}Sc}, seen in \autoref{fig:44Sc_IBR}.
+Above 23\,MeV, TALYS/TENDL both reproduce the present work, as well as earlier measurements, suggesting that angular momentum transfer in the pre-equilibrium regime is being well-modeled, but that the total feeding of the \ce{^{44}Sc} channel is  underestimated.
+A similar argument holds for EMPIRE, which reproduces the isomer branching from threshold up to 35\,MeV.
+However, CoH fails to reproduce either the channel magnitude or the isomer ratio, suggesting a more fundamental issue with the modeling of this channel. 
+\ce{^{47}Sc} presents a very opposed situation, despite an abundance of reaction data and strong feeding of the channel.
+All codes fail to reproduce either the shape or magnitude of this channel, with only CoH able to predict the compound peak,  and failing to model the pre-equilibrium tail.
+As a cumulative reaction channel, it is unclear whether this failure arises from modeling of any \ce{^{47}Ca} decay precursors, or the competition between  \ce{^{48}Ti}(p,20)\ce{^{47}Sc} / \ce{^{49}Ti}(p,2pn)\ce{^{47}Sc} / \ce{^{50}Ti}(p,$\alpha$)\ce{^{47}Sc} channels.
+Modeling of \ce{^{48}Sc} is lacking, with only TALYS/TENDL matching the shape of the excitation, and all codes failing to reproduce the magnitude of the channel.
+
+As with \ce{^{58m}Co} measurements, the titanium activation has  yielded measurements of  a number of additional  medical  radionuclides,  including the non-standard positron emitter
 \ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
 %\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
-\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}
-\ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
-\ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
-\ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
 % \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
@@
 % and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
-Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x).
+Production of \ce{^{44}Sc} offers no major advantages over established \ce{^{44}Ca}(p,n) / \ce{^{44}Ca}(d,2n) / \ce{^{45}Sc}(p,2n)\ce{^{44}Ti} $\xrightarrow[]{\epsilon}$ \ce{^{44}Sc} pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Ti}(p,x).
+Since high-specific activity \ce{^{47}Sc} production routes are limited (with  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} as one of few potential candidates), alternative pathways are greatly desired by the community.
+However, \ce{^{nat}Ti}(p,x) is clearly no compelling alternative if high specific activity is required, due to the inability to avoid co-production of long-lived Sc radiocontaminants, even with prudent selection of a beam energy window.
 % The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co}\,\cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
@@
 We report the first measurements  for $\leq$70\,MeV protons  of the  \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions, as well as the first measurement of the independent cross sections for    \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
+Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV, as well as the potential for \ce{^{nat}Fe}(p,x)\ce{^{54}Mn},\ce{^{56}Co} as future monitor reactions.
 % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
@@
 % usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
-
-Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
-This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
-
-Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.
+% 
+% Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
+% This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+%
 

### 2020-12-08 fe_px_paper/Response_to_Reviewers.tex
Adding Lee's first part of comments

@@
   \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.
-We would especially like to thank the referees for their thorough reading and critique, which has made it a better paper.
+We would especially like to thank  referee \#2 for their thorough reading and critique, which has made it a better paper.
 Their comments were very constructive and pointed out some valuable improvements.
+Referee \#1 had a number of comments which were either unhelpful, or factually inaccurate.
+Nevertheless, their helpful suggestions were implemented, and responses to the remaining points are enclosed.
 
-  \colornote{Lee - should we make any comments about the hostility and unhelpful/incorrect comment from Reviewer 1 here?}
+%   \colornote{Lee - should we make any comments about the hostility and unhelpful/incorrect comment from Reviewer 1 here?}
 
@@
 
- \colornote{We thank the reviewer for their thoughtful comments....\\\\ ???????}
+ \colornote{We thank the reviewer for their thoughtful comments, in particular the suggestion to add integral yield calculations.  All comments have been addressed below:}
 
@@
 
+\colornote{Additional discussion of the implications of these results on the treatment of angular momentum in reaction modeling has been added throughout the paper. }
+
 2. Sample size 2.5 cm x2.5 cm is too large. What is the benefit of such sample size?
 
+\colornote{Since the beam (approximately 8 mm diameter) is  much smaller than this, we operate our irradiation in the \enquote{underfilled} regime --- hence, we can use areal density to calculate the cross section.
+This standard approach minimizes any deviations from point geometry during the gamma assay of foils.
+}
+
 3. The notifications ’25 MeV stack’ and ’55 MeV stack’ are not correct.
+
+\colornote{Two separate irradiations were performed at incident proton energies of 25 and 55 MeV respectively.
+The stack design was described on page 2, line 37, and this process was described in the paragraph beginning on page 2, line 50.
+}
 
@@
 
+\colornote{Per your suggestion, this figure has been removed.}
+
 5. In Fig.2, peak should be identified by energy and nuclide, not by symbol.
+
+\colornote{This figure has been updated, replacing the legend with energy / decay mode / $E_\gamma$ for each decay line.}
 
@@
 
+\colornote{The abrupt change in the post-minimization value at the energies where the two individual stacks overlap can be attributed to the to the relatively large energy straggle at the back of the high energy stack.
+The \enquote{jump} between stacks in the old Fig.
+3 /  new Fig.
+2 arises from the fact that the stacks were exposed to a different integral fluence.}
+
 7. EoB should be replaced by EOB.
+
+\colornote{All instances have been replaced.}
 
@@
 
+\colornote{The language has been updated here to better distinguish these separate reaction groups.}
+
 10. Both the numerical values for all investigated reactions should be given in Table and discussed in
@@
 
-\colornote{We thank your for this important feedback.
+\colornote{We thank you for this important feedback.
 We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data.
@@
 \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript.
-It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}
+It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.
+All comments have been well-received, and implemented.
+}
 
@@
 
-\colornote{We thank you for this very thoughtful suggestion.
+\colornote{This is a  very thoughtful suggestion.
 Running two overlapping stacks to build confidence through consistency was our goal for this, but the assignment of each foil to a stack is not clear, as you point out.
-Tables 1--4, containing all of the measured cross section and ratio data, have all had a new row added, clearly designating the foil corresponding to each proton energy.}
+Tables 1--4, containing all of the measured cross section and ratio data, have all had a new row added, clearly designating the foil corresponding to each proton energy.
+Additionally, the figure itself has an updated legend to clearly reflect this.}
 
@@
 
-\colornote{We thank your for this important feedback.
+\colornote{This is very important feedback!
 We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data.
@@
 
-\colornote{We thank your for making this important point particularly clear.
-This point is a vital takeaway from this work, which was not made explicit enough, but has now been more directly addressed in the conclusions.}
+\colornote{We thank you for making this important point particularly clear.
+This point is a vital takeaway from this work, which was not made explicitly enough, but has now been more directly addressed in the conclusions.}
 
@@
 
-\colornote{We thank your for this point.  The language in section 2.1 has been updated to reflect this, and a short statement to this effect has been added to the caption of Table 6.}
+\colornote{The language in section 2.1 has been updated to reflect this, and a short statement to this effect has been added to the caption of Table 6.}
 

### 2020-12-08 fe_px_paper/fe_body_text.tex
Adding Lee's first part of comments

@@
 % Another emerging manganese radionuclide is 
-In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$~\pm~$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{Wang2017}), 
+In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$~\pm~$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{PhysRevC.96.014613,Wang2017}), 
 % whose short lifetime makes it 
@@
 % As 
-Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has
+Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs \cite{Bernstein2019a}, our group has
 % performed a   measurement of 
@@
 
+Two separate irradiations were performed at incident proton energies of 25 and 55 MeV, respectively.
 We constructed a pair of target stacks 
@@
 % One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
-The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy and mounts on the end of an electrically-isolated beamline.
+The target box
+% , seen in \autoref{fig:fe_target_stack}, 
+is machined from 6061 aluminum alloy and mounts on the end of a beamline,  electrically-isolated  for the purposes of current monitoring.
 The specifications of both target stacks 
@@
 
-\begin{figure}[ht]
- \centering
- \includegraphics[width=0.45\textwidth]{./figures/SAM_2494.JPG}
- % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
- \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack.
-%  , before it was mounted in the beamline. 
- The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
-\end{figure}
+% \begin{figure}[ht]
+%  \centering
+%  \includegraphics[width=0.45\textwidth]{./figures/SAM_2494.JPG}
+%  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
+%  \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack.
+% %  , before it was mounted in the beamline. 
+%  The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
+% \end{figure}
 
@@
 Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\\,\cite{Graves2016}.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EOB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
 % \label{tab:fe_stack_table}
@@
 Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\\,\cite{Graves2016}.
-At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
+At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EOB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}
 % \label{tab:fe_stack_table2}
@@
 % % the earlier paper by Graves \etal\\,\cite{Graves2016}.
-% A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}
+% A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EOB).}
 % \label{tab:fe_stack_table}
@@
 The approximately 1\,cm-diameter proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
-Following end-of-bombardment (EoB), each stack was removed from the beamline and disassembled.
+Following end-of-bombardment (EOB), each stack was removed from the beamline and disassembled.
 All activated foils were transported to a counting lab for gamma spectrometry, which started approximately 20\,minutes following the end of each irradiation.
@@
 % end-of-bombardment.
-(EoB).
+EOB.
 % , to accurately quantify all induced activities.
@@
 The   half-lives and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
-\cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
+\cite{PhysRevC.96.014613,Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
 Corrections (typically \textless0.2\%) for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
-% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
-% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
+% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EOB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
+% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EOB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
 % activity for each gamma-ray possesses a 
-EoB activities were determined by $\chi^2$-fitting of all observed decay gammas for a product to the decay curve.
+EOB activities were determined by $\chi^2$-fitting of all observed decay gammas for a product to the decay curve.
 The total  uncertainty in  activity is the propagated sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration,  uncertainty in the gamma-ray branching ratio data, and uncertainty in photon attenuation coefficients (taken as~5\%).
@@
 % % To convert these activities into cross sections, c
-% Corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB, from the measured activities.
-% The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
-% For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
+% Corrections must be made for the decay of the various reaction products during the time between EOB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EOB, from the measured activities.
+% The use of  multiple gamma-rays at multiple points after EOB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
+% For the case of cumulative cross sections, EOB activities were quantified by fitting the activities observed at multiple time points $t$ (since EOB) to the well-known radioactive decay law.
 % % \begin{equation}
@@
 % % \end{equation}
-% Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
+% Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EOB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
 % As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of \ref{sec:fe_data}.
-% In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation\,\cite{bateman1910solution,Cetnar2006}:
+% In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EOB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation\,\cite{bateman1910solution,Cetnar2006}:
 % \begin{equation}
@@
 % where $j$ refers to a precursor nucleus populating a specific end-product.  
-% While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
+% While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EOB activities in a mass chain, simplifying to:
 % \begin{equation}
@@
 % \end{equation}
-% In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
-% After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
+% In these cases, the previously-quantified EOB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
+% After quantifying the cumulative EOB activities at the top of a mass chain and all subsequent independent EOB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
 
@@
 % \end{equation}
-The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EoB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 10 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation\,\cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
+The propagated uncertainty in proton fluence is calculated as the quadrature sum of (1) the uncertainty in quantified EOB activity, (2) uncertainty in the duration of irradiation (conservatively estimated at 10 s, to account for any transient changes in beam current), (3) uncertainty in foil areal density, (4) uncertainty in monitor product half-life (included, but normally negligible), (5) uncertainty in IAEA recommended cross section (using values  from the 2017 IAEA re-evaluation\,\cite{Hermanne2018}), and (6) uncertainty in differential proton fluence (from transport simulations).
 
@@
 % areal densities of the stack components. 
-This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties.
+This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic errors.
 % in stack areal densities.
@@
    \hspace{-5pt}}%
-    \caption{Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
+    \caption{Proton fluence at various positions in both the 55\,MeV and 25\,MeV target stacks as determined by the Ti and Cu monitor foils before (left) and after (right) variance minimization.
+Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack.
+The abrupt change in the post-minimization value at the energies where the two stacks overlap can be attributed to the to the relatively large energy straggle at the back of the high energy stack.}
+%     Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
 A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.
@@
 
-Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate 
+Using the quantified EOB activities along with the variance-minimized proton fluence, it is possible to calculate 
 % the final 
@@
 % \end{equation}
-% where $A_0$ is the EoB activity for the  reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
+% where $A_0$ is the EOB activity for the  reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
 The beam current, measured using a current integrator connected to the electrically-isolated target box, remained stable for the duration of the irradiation.
-The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 10\,s, to account for any minor transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position).
+The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EOB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 10\,s, to account for any minor transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position).
 % , as seen in \autoref{fig:fe_fluence_plot}).
@@
 % \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
-The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
+The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EOB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).
 
@@
 The measured cross sections were compared to the predictions by the reaction codes TALYS, EMPIRE, CoH, ALICE, and by the calculations in the TENDL database.
-The codes were all explicitly run using their default parameters, for two primary motivations. 
-First, this  assesses their claims of  predictive capabilities  --- many \enquote{casual} users (i.e., outside of data evaluation) will likely not make significant adjustments to the massively multi-parameter physics models used in these codes, nor should they need to, due to an expectation of reasonable accuracy in these results.
-Indeed, TALYS and TENDL  are routinely used for modeling cross sections in initial target designs for isotope production applications.
-Second, our recent work has shown that  arbitrary parameter optimization (tuning to provide a best fit to a single reaction channel)  often provides non-unique solutions, causing neighboring reaction channels (e.g., (p,4n) vs.
+The codes were all explicitly run using their default parameters.
+% , for two primary motivations. 
+% First, this  assesses their claims of  predictive capabilities  --- many \enquote{casual} users (i.e., outside of data evaluation) will likely not make significant adjustments to the massively multi-parameter physics models used in these codes, nor should they need to, due to an expectation of reasonable accuracy in these results.
+% Indeed, TALYS and TENDL  are routinely used for modeling cross sections in initial target designs for isotope production applications.
+% Second,
+In contrast, TENDL was developed through a parameter optimization process, and is routinely used for modeling cross sections in initial target designs for isotope production applications.  
+Our recent work has shown that  arbitrary parameter optimization (tuning to provide a best fit to a single reaction channel)  often provides non-unique solutions, causing neighboring reaction channels (e.g., (p,4n) vs.
 (p,p3n)) to suffer \cite{fox2020investigating}.
-Without a global physical basis for optimization (as in the process of reaction evaluation), an unchecked fit to experimental data offers no insight for reaction modeling, and may propagate to highly non-physical results for  competing channels.
+% Without a global physical basis for optimization (as in the process of reaction evaluation), an unchecked fit to experimental data offers no insight for reaction modeling, and may propagate to highly non-physical results for  competing channels.
+A full optimization of the reaction modeling is beyond the scope of this paper.  
+However, a  comparison between measured, evaluated, and default calculations for the major channel cross sections serves to highlight the relative fidelity of all three approaches.  
 % in order to assess their predictive capabilities for the casual user.
 % The explicit use of default parameters was chosen for two reasons --- 
-
-The default settings for the optical models and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
-The level density models for each are as follows.
-For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
-In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
-This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
-This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
-Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.
-The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
+%
+The default settings for the level density models, optical models, and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
+% The level density models for each are as follows.
+% For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
+% In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
+% This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
+% This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
+% Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.
+% The 
+It should be noted that the use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, 
+% by propagating the difficulties inherent in modeling a wide 
+due to the larger number  of reaction channels that can contribute to the production of any given residual nucleus.
+% , to multiple target isotopes.
 As a result, this analysis is useful for a qualitative comparison of default predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
@@
  \resizebox{\textwidth}{!}{%
-\begin{tabular}{ c c c c}
-
- \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
- EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
- TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
-  CoH-3.5.3\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} \\
-  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a}
+\begin{tabular}{ c c c c c}
+
+ \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model} & \underline{Level Density Model} \\ 
+ EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook} &  Enhanced Generalized Superfluid\cite{Giardina2002}.
+\\
+ TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}  & Gilbert-Cameron\cite{Gilbert2011} \\
+  CoH-3.5.3\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010} &  Gilbert-Cameron  \\
+  ALICE-2017\cite{Blann1996}     &   Nadasen\cite{Nadasen1981}    &  Parabolic Diffuse-Well\cite{Thomas1959}    &   Berman-Fultz Lorentzian\cite{Berman1975a} & Kataria-Rarnamurthy-Kapoor\cite{Kataria1978,Kataria1990}
 
@@
 
+\begin{figure}
+ \centering
+ \includegraphics[width=0.65\textwidth]{./figures/Fe_Physical_Yields.pdf}
+ % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+ \caption{Integral thick target yields for \ce{^{nat}Fe}(p,x)\ce{^{51,52m,52g,54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{55,56,57,58m}Mn}, including indirect production routes.
+Yields are specified in units of MBq/C \cite{Otuka2015}, and  represent physical yields (also known as instantaneous production rates).
+1 MBq/C= 0.0036 MBq/$\mmicro$Ah.}
+ \label{fig:yields}
+\end{figure}
+
 These results have several notable features.
@@
 % various 
-\ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
+\ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
 % the body of measurements in the 
@@
 Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work\,\cite{Voyles2018a}.
-No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
+% No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but t
+This serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence if one were to use the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
 Discussion of notable reaction channels follows here, and 
@@
 % and \ref{sec:fe_ibr_figures}.
+Physical yield curves have additionally been calculated,  from logarithmic interpolation of the excitation functions presented in this work, as seen in \autoref{fig:yields}.
+All yields are specified in the recommended units of MBq/C \cite{Otuka2015}, and  represent the instantaneous production rates.
+These curves show that production of medically-valuable radionuclides at low-to-intermediate energies by \ce{^{nat}Fe}(p,x) is potentially viable, but is dependent upon  the required radionuclidic purity on a case-by-case basis.
 
@@
 This work presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction in this energy region.
-However, below the 24.1\,MeV threshold for \ce{^{56}Fe}(p,x)\ce{^{51}Mn}, the single measurement of \ce{^{54}Fe}(p,x)\ce{^{51}Mn} from Levkovski can be renormalized by isotopic abundance, and is consistent  with the present work \cite{levkovski1991cross}.
-For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
-The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
+However, below the 24.1\,MeV threshold for \ce{^{56}Fe}(p,x)\ce{^{51}Mn}, the single measurement of \ce{^{54}Fe}(p,x)\ce{^{51}Mn} from Levkovski can be renormalized by isotopic abundance (and an additional -18\% due to an error in the monitor data adopted in the measurement), and is consistent  with the present work \cite{levkovski1991cross}.
+For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by the default calculation performed with  EMPIRE, CoH, and ALICE.
+Interestingly, the higher-energy reactions on the higher mass Fe isotopes, are better matched by  EMPIRE and CoH.
 ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
 As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
-EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
+The untuned EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
 
@@
 
-\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr\,\cite{Klein2000}.
+It should be noted that  \ce{Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr\,\cite{Klein2000}.
 % However, 
@@
 
-        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/52Mn_IBR.pdf}{50}
+        \subfigimg[width=0.485\textwidth]{b)}{./figures/52Mn_IBR.pdf}{50}
          %         \refstepcounter{subfigure}
@@
 
-Measured \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), with the \ce{^{58}Fe}(p,n)\ce{^{58m}Co} reaction channel visibly peaking at approximately \mbox{20 MeV}.
+% Measured \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), with the \ce{^{58}Fe}(p,n)\ce{^{58m}Co} reaction channel visibly peaking at approximately \mbox{20 MeV}.
 
@@
 This work is consistent with the general body of previous cumulative \ce{^{52g}Mn} measurements, with the exception of work from Williams, Lagunas-Solar, and Barchuk, all of which have shown discrepancies with prior data in other reaction channels measured here \cite{barchuk1987excitation,Lagunas-Solar1979a,PhysRev.162.1055}.
+
+The \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) ratio seen in Figure \autoref{fig:temp_52mMn} shows significant deviation from all of the reaction models and the TENDL database near threshold, indicating potential issues with transmission particle transmission coefficients arising from the optical model.
+Above threshold the values are are all in keeping with the TENDL and default TALYS calculations and differ significantly from both the default CoH and EMPIRE calculations, indicating potential issues with the angular momentum dependence of the level density.
 
@@
 CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct shape.
-Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section, seen in Figure \autoref{fig:temp_52mMn}, the effect of spin distributions in highly-excited nuclear states can be studied.
+Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section
+% , seen in Figure \autoref{fig:temp_52mMn}
+, the effect of spin distributions in the unresolved discrete
+% highly-excited nuclear states 
+can be studied.
 The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 50\% at the peak energy.
@@
 which indicates that the isomer feeding is not well-modeled in these codes.
-It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.
+% It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.
 
@@
 While the \ce{^{51}Cr} decay data used in these experiments (Williams: $t_{1/2}=27.8$ d, $I_\gamma$=9\%, Schoen: $t_{1/2}=27.71$ d, $I_\gamma$=10.2\%) differ slightly from those used here ($t_{1/2}=27.704(3)$ d, $I_\gamma$=9.910(10)\% \cite{Wang2017}), these differences do not account for the approximately 50\% smaller peak cross section reported by Williams, and approximately 30\%  smaller for Schoen.
-Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation, possibly suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was not considered.
+Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation, possibly suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was either not considered, or mis-calculated \cite{Basunia2020}.
+% was not considered.
 
@@
 Similarly to \ce{^{56}Co},  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  offers another interesting possibility as a \ce{^{nat}Fe}(p,x) monitor reaction.
-This radionuclide ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
+This radionuclide ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV).
+% , and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
 This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
@@
 For \ce{^{nat}Cu}(p,x)\ce{^{60,61,64}Cu}, the measurements presented here are consistent with earlier work (aside from that of Williams \cite{PhysRev.162.1055}, as discussed earlier), and are generally the highest-precision measurements to date.
+As part of this work, a discrepancy, outside reported uncertainties, has been observed between the accepted and measured  values of the intensity ratio of the 283 keV and  656 keV decay lines in \ce{^{61}Cu}, and is detailed in a forthcoming manuscript.
 
@@
 
+% \textred{ As shown in Fig.
+6, the bell-like shape of the cross section in the (p,n) reaction is mainly determined by Q-values of the (p,n) and (p,pn) reactions and level densities of nuclei as follows; Threshold of the (p,n) cross section is determined by the Q-value of the (p,n) reaction.
+The Q-value of the (p,pn) reaction determines decline and peak of the (p,n) cross section.
+The height of the (p,n) cross section is governed by the probabilities of the exit channels from the compound nucleus, namely (p,gamma), (p,n), (p,alpha) and (p,pn).
+These probabilities are connected to the level densities of the nuclei in the exit channels.
+Additionally, the (p,2n) and (p,p2n) reactions compete mainly with the (p,pn) one.}
+
  \section{\label{sec:conclusions_fe}Conclusions}
@@
 % We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
+
 We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,MeV for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
+Across the channels studied here, there exists a clear trend of modeling codes failing to reproduce observed reaction thresholds, suggesting an underlying problem with the transmission coefficients utilized in these models.
+While no model globally succeeds in these channels,   TALYS and TENDL generally perform best with the lower-energy \enquote{compound} reactions but, like all models, do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
+This illustrates the importance of a well-characterized level density model for predictive power, with the \enquote{simple} Gilbert-Cameron model, with no energy-dependent spin parameter,  outperforming in the modeling of the pre-equilibrium regime.
+
+It is important to note that overall, modeling succeeds best where experimental data exist, underpinning the need for measurement of all observed reaction channels in experiments.
 This work offers a clear warning against unchecked use of  such default calculations, even if performed with the latest developments in nuclear reaction modeling codes. 

### 2020-12-17 fe_px_paper/fe_body_text.tex
Merging in Lee's feedback on the fe paper

@@
 
-This work presents the first measurement of several observables in this energy region, including the first independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the first measurement of \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+This work presents the first measurement of several observables in this energy region, including independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the  \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  as well as extending the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
 Cumulative  \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn} reaction measurements exist in earlier work, but  this work presents the most well-characterized measurement  below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
@@
 Above threshold the values are are all in keeping with the TENDL and default TALYS calculations and differ significantly from both the default CoH and EMPIRE calculations, indicating potential issues with the angular momentum dependence of the level density.
-
 % Cutting as part of results reorganization
@@
 % This is seen again in the  
-For the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, seen in Figure \autoref{fig:temp_52Mn},  the first peak is well-modeled by TALYS and TENDL, but  rises much more rapidly than the data would support above 50\,MeV.
-CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct shape.
+For the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, seen in Figure \autoref{fig:temp_52Mn},  the  peak  at lower energy, which is largely attributable to the \ce{^{56}Fe}(p,p$\alpha$) channel, is well-modeled by TALYS and TENDL.
+However, the production of \ce{^{52}Mn}  rises much more rapidly than the data would support above 50\,MeV, suggesting an overestimation of the \ce{^{56}Fe}(p,3p2n) contribution.  
+CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct overall energy dependence.
+
 Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section
@@
 , the effect of spin distributions in the unresolved discrete
-% highly-excited nuclear states 
-can be studied.
+% highly-excited nuclear 
+states can be studied.
 The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 50\% at the peak energy.
@@
 % Likewise, 
-Like \ce{^{51}Mn}, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
+% Like \ce{^{51}Mn}, 
+\ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
 Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%)\,\cite{Graves2015,Wooten2015}.
-\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
+\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the lower radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
 Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn} and long-lived Co radiocontaminants, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
-It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer.
+It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the
+% unfavorable gammas 
+hard 1434\,keV gamma-ray produced by the isomer. 
 However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$~\pm~$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator\,\cite{Blauenstein1997}.
@@
 % This work reports the first experimental measurement of
-this energy region, including the measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
-the independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), seen in \autoref{fig:58Co_IBR}.
+this energy region, including the 
+% measurement of the 
+\ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
+the independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), seen in \autoref{fig:58Co_IBR}.
 The cumulative cross sections from these data are both consistent with, and higher-precision than, existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} cross sections, as well as the large body of measurements for \ce{^{nat}Fe}(p,x)\ce{^{56}Co}.
 
-Despite being weakly-fed, EMPIRE, CoH, and TALYS/TENDL all do an excellent job of reproducing earlier work and this measurement, for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
-This holds for both the shape and magnitude of each excitation function, though CoH overestimates the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} peak magnitude by approximately 30\%, despite matching the rising and falling edges of the curve.
-However, for both the \ce{^{nat}Fe}(p,x)\ce{^{56,58g}Co} channels, ALICE underestimates the magnitude of the rising edge and compound peak by nearly 50\%, though it shows the best agreement of these codes with the magnitude of the pre-equilibrium tails for these channels.
-Additionally, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\%, and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work.
+While it is dangerous to use weak channels to guide reaction modeling,
+% Despite being weakly-fed, 
+EMPIRE and TALYS/TENDL all reproduce earlier work and this measurement reasonably well ($\pm$10\%), for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
+This holds for both the shape and magnitude of each excitation function.
+CoH overestimates the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} peak magnitude by approximately 30\% and  \ce{^{nat}Fe}(p,x)\ce{^{56}Co}  by approximately 10\%, despite matching the rising and falling edges of the curve.
+For both the \ce{^{nat}Fe}(p,x)\ce{^{56,58g}Co} channels, ALICE underestimates the magnitude of the rising edge and compound peak by nearly 50\%, though it shows the best agreement of these codes with the magnitude of the pre-equilibrium tails for these channels.
+
+However, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\%, and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work.
 % In 
 As opposed to the other isomer-to-ground state ratio measured for Fe,  the opposite is seen for \ce{^{nat}Fe}(p,x)\ce{^{58}Co} -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
-Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling, or an underestimation of high-spin transfer in pre-equilibrium neutron emission.
+Given that the level density model was the same for all of the product nuclei, it points to issues in  the spin distribution of the initial population of the residual nucleus 
+% as the main problem with modeling, or an underestimation of high-spin transfer 
+in the pre-equilibrium neutron emission.
 % However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
 
-Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
-In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
-It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
+The \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channel ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})
+% Several of the activities produced via \ce{^{nat}Fe}(p,x)  
+could be useful as an experimental monitor reaction  due to its high intensity and production of long-lived residual products that produce bright decay gamma-rays. 
+% In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target.
+% It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
 Given that \ce{^{nat}Cu}(p,x)\ce{^{56}Co} is an established monitor reaction, it seems likely that an evaluation of \ce{^{nat}Fe}(p,x)\ce{^{56}Co} as a monitor standard could provide a useful complement to existing low-to-intermediate energy monitor reactions.
@@
 
-In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications,
+In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded production cross section  measurements of  a number of additional  emerging radionuclides with medical applications,
 including the non-standard positron emitter 
@@
 The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
-While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
+While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, lowering the  co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
 The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.
@@
 
-\begin{figure}[h]
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/51Cr_ind.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.}
+% \begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{./figures/51Cr_ind.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.}
+%  \label{fig:51Cr_ind}
+% \end{figure}
+
+\begin{figure*}
+    \centering
+    \subfloat{
+        \centering
+        \hspace{-5pt}\subfigimg[width=0.485\textwidth]{\hspace{4.5cm}a)}{./figures/49Cr.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+         \label{fig:fig49Cr}
+   \hspace{-5pt}}%
+     \subfloat{
+        \centering
+
+        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/51Cr_ind.pdf}{50}
+         %         \refstepcounter{subfigure}
+         \label{fig:fig51Cr}
+   \hspace{-5pt}}%
+    \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{49}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$p3n)\ce{^{49}Cr}/\ce{^{54}Fe}(p,3p3n)\ce{^{49}Cr} reaction channels visibly peaking at approximately \mbox{48 MeV}.
+b) Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.}
      \label{fig:51Cr_ind}
-\end{figure}
+\end{figure*}
 
@@
 As seen in other channels, the work of Williams and Schoen \cite{PhysRev.162.1055,Schoen1979a} are both significantly lower in magnitude, and with cross sections peaking approximately 5\,MeV higher than body of other measurements.
-While the \ce{^{51}Cr} decay data used in these experiments (Williams: $t_{1/2}=27.8$ d, $I_\gamma$=9\%, Schoen: $t_{1/2}=27.71$ d, $I_\gamma$=10.2\%) differ slightly from those used here ($t_{1/2}=27.704(3)$ d, $I_\gamma$=9.910(10)\% \cite{Wang2017}), these differences do not account for the approximately 50\% smaller peak cross section reported by Williams, and approximately 30\%  smaller for Schoen.
-Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation, possibly suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was either not considered, or mis-calculated \cite{Basunia2020}.
+While the \ce{^{51}Cr} decay data used in these experiments (Williams: $t_{1/2}=27.8$ d, $I_\gamma$=9\%, Schoen: $t_{1/2}=27.71$ d, $I_\gamma$=10.2\%) differ slightly from those used here ($t_{1/2}=27.704(3)$ d, $I_\gamma$=9.910(10)\% \cite{Wang2017}), these differences do not account for the approximately 50\% smaller peak cross section reported by Williams, and  30\%  smaller for Schoen.
+Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation,  suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was either not considered, or mis-calculated \cite{Basunia2020}.
 % was not considered.
@@
 For \ce{^{49}Cr}, ALICE and CoH both overestimate the magnitude of this channel by approximately 30\%, ALICE overestimates  by approximately 350\%, while TALYS and TENDL underestimate the magnitude by approximately 50\%.
-Weakly-fed channels such as \ce{^{49}Cr} are often sensitive, as the modeling of more strongly-fed channels tends to impose strong constraints upon the magnitude of remaining channels.
+% Weakly-fed channels such as \ce{^{49}Cr} are often sensitive, as the modeling of more strongly-fed channels tends to impose strong constraints upon the magnitude of remaining channels.
+However, it should be noted that weakly-produced nuclides should not be used to guide reaction modeling due to their sensitivity to stronger reaction channels.
 Modeling of \ce{^{51}Cr} shows improved agreement in magnitude --- CoH and ALICE are consistent at the 1$\sigma$ level, EMPIRE overestimates the peak by approximately 25\%, and TALYS/TENDL underestimate the peak by approximately 60\%.
@@
 
-\begin{figure}[h]
- \centering
- \includegraphics[width=0.5\textwidth]{./figures/54Mn.pdf}
- % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
- \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} independent cross section, with the \ce{^{56}Fe}(p,2pn)\ce{^{54}Mn}/\ce{^{57}Fe}(p,2p2n)\ce{^{54}Mn} reaction channels visibly peaking at approximately \mbox{40 MeV}.}
+% \begin{figure}[h]
+%  \centering
+%  \includegraphics[width=0.5\textwidth]{./figures/54Mn.pdf}
+%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
+%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} independent cross section, with the \ce{^{56}Fe}(p,2pn)\ce{^{54}Mn}/\ce{^{57}Fe}(p,2p2n)\ce{^{54}Mn} reaction channels visibly peaking at approximately \mbox{40 MeV}.}
+%  \label{fig:54Mn}
+% \end{figure}
+
+\begin{figure*}
+    \centering
+    \subfloat{
+        \centering
+        \hspace{-5pt}\subfigimg[width=0.485\textwidth]{\hspace{4.5cm}a)}{./figures/54Mn.pdf}{50}
+%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
+         %         \refstepcounter{subfigure}
+         \label{fig:fig54Mn}
+   \hspace{-5pt}}%
+     \subfloat{
+        \centering
+
+        \subfigimg[width=0.485\textwidth]{b)}{./figures/56Mn.pdf}{50}
+         %         \refstepcounter{subfigure}
+         \label{fig:fig56Mn}
+   \hspace{-5pt}}%
+    \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} independent cross section, with the sum of the \ce{^{56}Fe}(p,2pn)\ce{^{54}Mn} and \ce{^{57}Fe}(p,2p2n)\ce{^{54}Mn} reaction channels visibly peaking at approximately \mbox{40 MeV}.
+b) Measured \ce{^{nat}Fe}(p,x)\ce{^{56}Mn} independent cross section, with the \ce{^{57}Fe}(p,2p)\ce{^{56}Mn}/\ce{^{58}Fe}(p,2pn)\ce{^{56}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV} and \mbox{40 MeV}, respectively.}
      \label{fig:54Mn}
-\end{figure}
+\end{figure*}
 
@@
 This measurement is consistent with earlier work aside from the globally-discrepant Williams data, as discussed previously.
-Modeling of these channels presents a counterpoint to the \ce{^{51,52}Mn} results discussed earlier - \ce{^{54}Mn} is   well-modeled by CoH, TENDL, and TALYS, though EMPIRE overestimates the peak cross section by approximately 25\%, and ALICE underestimates by the same, in addition to peaking approximately 3\,MeV higher.
+Modeling of these channels presents a counterpoint to the \ce{^{51,52}Mn} results discussed earlier --- \ce{^{54}Mn} is   well-modeled by CoH, TENDL, and TALYS, though EMPIRE overestimates the peak cross section by approximately 25\%, and ALICE underestimates by the same, in addition to peaking approximately 3\,MeV higher.
 The weakly-fed \ce{^{56}Mn} is poorly modeled in comparison, with CoH, EMPIRE, and ALICE failing to match neither the shape nor magnitude of the excitation function, though TALYS/TENDL matches both.
@@
 % It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life.
-Similarly to \ce{^{56}Co},  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  offers another interesting possibility as a \ce{^{nat}Fe}(p,x) monitor reaction.
-This radionuclide ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV).
+Similarly to \ce{^{56}Co},  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  offers another interesting possibility as a \ce{^{nat}Fe}(p,x) monitor reaction,
+with a long half-life 
+% This radionuclide 
+($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}),
+% has a convenient half-life and 
+strong cross section (approximately 160\,mb near 40\,MeV), and a uniquely-produced daughter nuclide.
 % , and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
-This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.
-Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds of nearly 20\,MeV.
-This provides some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region, which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.
+This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via  high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}).
+% produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section. 
+Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds,
+% of nearly 20\,MeV, 
+providing some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region.
+% , which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.
 
@@
 
-As we reported previously, modeling of \ce{^{nat}Cu}(p,x) reactions is poor in this energy region, despite the relative ease of only two stable target isotopes in copper.
-For \ce{^{60}Cu}, all codes fail to predict the magnitude and shape of the channel, and tend to place the peak approximately 5\,MeV lower than observed.
-Similar behavior is observed in the strongly-fed \ce{^{61}Cu}, though not to the same degree --- the peak shift is approximately 3\,MeV, but the shape predictions are more physical, despite a suppression of the pre-equilibrium tail in  EMPIRE.
-\ce{^{64}Cu} modeling appears to be the best of these channels, with all codes matching the overall shape, but only EMPIRE predicting the rapid rise and fall of the compound peak, compared to the smoother behavior of the other codes.
+As we reported previously, modeling of \ce{^{nat}Cu}(p,x) reactions is poor in this energy region.
+% , despite the relative ease of only two stable target isotopes in copper.
+For \ce{^{60}Cu}, all codes fail to predict the magnitude and shape of the channel, with a peak approximately 5\,MeV lower than observed.
+Similar behavior is observed in the strongly-fed \ce{^{61}Cu},
+% , though not to the same degree --- 
+with the peak shifted approximately 3\,MeV lower.
+% , but the shape predictions are more physical, despite a suppression of the pre-equilibrium tail in  EMPIRE.
+\ce{^{64}Cu} modeling appears to be the best of these channels, with all codes matching the overall shape, but only EMPIRE predicting the rapid rise and fall of the compound peak.
+% , compared to the smoother behavior of the other codes.
 Unlike ALICE and EMPIRE, CoH, TALYS, and TENDL all do a successful job of modeling the shape of the (p,pn) pre-equilibrium tail, with this channel showing the best predictive power of the \ce{^{nat}Cu}(p,x) reactions.
@@
 
-As with the other foils in this experiment, \ce{^{nat}Cu}(p,x)  has  yielded measurements of  a number of additional  medical  radionuclides,  including the non-standard positron emitters 
+% As with the other foils in this experiment, 
+\ce{^{nat}Cu}(p,x)  also  yielded measurements of  a number of additional  medical  radionuclides,  including the non-standard positron emitters 
 \ce{^{57}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
@@
 
-Due in part to the long-standing use of Ti as a monitor foil,  \ce{^{nat}Ti}(p,x) reactions are better-characterized than many  natural targets.
+% Due in part to the long-standing use of Ti as a monitor foil,  \ce{^{nat}Ti}(p,x) reactions are better-characterized than many  natural targets.
 While the focus of this work is on the production of \ce{^{51,52}Mn}  and other \ce{^{nat}Fe}(p,x) channels, the cross sections reported here offer improvements to prior work, particularly for the several Sc radionuclides observed.
@@
 
-Perhaps due to the abundance of reaction data available, modeling of these channels is markedly improved  in comparison to the \ce{^{nat}Fe}(p,x) channels discussed previously.
-For \ce{^{44m}Sc}, the shape of the excitation function is well-modeled by EMPIRE, CoH, TALYS, and TENDL, though all of these codes place the compound peak approximately 4\,MeV lower than observed.
-Additionally, EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
+% Perhaps due to the abundance of reaction data available, 
+The modeling of these channels is markedly improved  in comparison to the \ce{^{nat}Fe}(p,x) channels discussed previously.
+For \ce{^{44m}Sc}, 
+% the shape of the excitation function is well-modeled by EMPIRE, CoH, TALYS, and TENDL, though 
+all  codes place the compound peak approximately 4\,MeV lower than observed, and EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
 Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but signficantly underestimated by EMPIRE and CoH.
-The same modeling trend is observed for \ce{^{44m}Sc}, though no judgment can be made for the pre-equilibrium tail, due to a paucity of data above 50\,MeV.
-This is reflected in the measured isomer branching ratios for \ce{^{44}Sc}, seen in \autoref{fig:44Sc_IBR}.
+The same modeling trend is observed for \ce{^{44m}Sc}, 
+% though no judgment can be made for the pre-equilibrium tail, due to a paucity of data above 50\,MeV.
+and reflected in the measured isomer branching ratios for \ce{^{44}Sc}, seen in \autoref{fig:44Sc_IBR}.
 Above 23\,MeV, TALYS/TENDL both reproduce the present work, as well as earlier measurements, suggesting that angular momentum transfer in the pre-equilibrium regime is being well-modeled, but that the total feeding of the \ce{^{44}Sc} channel is  underestimated.
-A similar argument holds for EMPIRE, which reproduces the isomer branching from threshold up to 35\,MeV.
-However, CoH fails to reproduce either the channel magnitude or the isomer ratio, suggesting a more fundamental issue with the modeling of this channel. 
+A similar argument holds for EMPIRE, which reproduces the isomer branching  up to 35\,MeV.
+However, CoH fails to reproduce either the channel magnitude or the isomer ratio,
+% , suggesting a more fundamental issue with the modeling of this channel. 
 \ce{^{47}Sc} presents a very opposed situation, despite an abundance of reaction data and strong feeding of the channel.
@@
 % and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
-Production of \ce{^{44}Sc} offers no major advantages over established \ce{^{44}Ca}(p,n) / \ce{^{44}Ca}(d,2n) / \ce{^{45}Sc}(p,2n)\ce{^{44}Ti} $\xrightarrow[]{\epsilon}$ \ce{^{44}Sc} pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Ti}(p,x).
+% Production of \ce{^{44}Sc} 
+However, this route offers no major advantages over established \ce{^{44}Ca}(p,n) / \ce{^{44}Ca}(d,2n) / \ce{^{45}Sc}(p,2n)\ce{^{44}Ti} $\xrightarrow[]{\epsilon}$ \ce{^{44}Sc} pathways,
+% , with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Ti}(p,x). 
 Since high-specific activity \ce{^{47}Sc} production routes are limited (with  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} as one of few potential candidates), alternative pathways are greatly desired by the community.
-However, \ce{^{nat}Ti}(p,x) is clearly no compelling alternative if high specific activity is required, due to the inability to avoid co-production of long-lived Sc radiocontaminants, even with prudent selection of a beam energy window.
+However, \ce{^{nat}Ti}(p,x) is clearly not a compelling alternative if high specific activity is required, due to the inability to avoid co-production of long-lived Sc radiocontaminants.
+% , even with prudent selection of a beam energy window.
 % The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co}\,\cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.

### 2020-12-22 fe_px_paper/fe_body_text.tex
Adding Fe paper pre-PU changes

@@
 Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack.
-The abrupt change in the post-minimization value at the energies where the two stacks overlap can be attributed to the to the relatively large energy straggle at the back of the high energy stack.}
+The abrupt change in the post-minimization value at the energies where the two stacks overlap can be attributed to the relatively large energy straggle at the back of the high energy stack.}
 %     Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack).
@@
 % and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
-Production of this radionuclide offerss no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
+Production of this radionuclide offers no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
 The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
@@
 all  codes place the compound peak approximately 4\,MeV lower than observed, and EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
-Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but signficantly underestimated by EMPIRE and CoH.
+Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but significantly underestimated by EMPIRE and CoH.
 The same modeling trend is observed for \ce{^{44m}Sc}, 

### 2021-01-19 fe_px_paper/fe_body_text.tex
Merging in PU edits to revised draft.

@@
 % Manganese 
-they possess well-established biochemistry, and have been 
+they possess well-established biochemistry and have been 
 % proven to be 
@@
 
-Developing production of these radionuclides requires well-characterized cross section data, or predictive models when such data have not been measured.   
+Developing production of these radionuclides requires well-characterized cross section data or predictive models when such data have not been measured.   
 % However, the m
@@
 facilitating comparison to reaction model calculations.  
-Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported\,\cite{bateman1910solution,Cetnar2006}.
+Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors so that  independent cross sections may be reported\,\cite{bateman1910solution,Cetnar2006}.
 
@@
 % These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
-The IAEA-recommended \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V},  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions were used 
+The International Atomic Energy Agency (IAEA)-recommended \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V},  \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions were used
 % for  proton fluence measurement 
@@
 transport code FLUKA-2011.2x.3 was used for simulation of the full 3-D target stack and to determine the full proton energy and fluence distribution for each foil\,\cite{Bohlen2014a}. 
-$10^8$ source protons were used for all FLUKA simulations, 
+All FLUKA simulations used $10^8$ source protons, 
 % which places the 
@@
 % areal densities of the stack components. 
-This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic errors.
+This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack due to the compounded effect of systematic errors.
 % in stack areal densities.
@@
 % For the 55\,MeV stack
-Therefore, the aluminum degraders are used for variance minimization for the 55\,MeV stack, as they make up more than 80\% of the areal density of the stack.
+Therefore, the aluminum degraders are used for variance minimization for the 55\,MeV stack as they make up more than 80\% of the areal density of the stack.
 % , and thus play the largest role in beam degradation.
-For the 25\,MeV stack, the Kapton tape was chosen for variance minimization, as the foil packets themselves are responsible for the majority of beam degradation.
+For the 25\,MeV stack, the Kapton tape was chosen for variance minimization as the foil packets themselves are responsible for the majority of beam degradation.
 While it only makes up approximately 20\% of the low-energy stack's areal density, the Kapton surrounding each foil packet has a greater areal density than the foil itself.
@@
 % nominal 
-values, to find the effective density which minimized variance in the measured proton fluence for the four monitor reactions at the lowest energy position (Ti-07, Cu-07).
+values to find the effective density which minimized variance in the measured proton fluence for the four monitor reactions at the lowest energy position (Ti-07, Cu-07).
 For the 25\,MeV stack, the areal density reached in the minimization of the 55\,MeV stack was used for  the E-09 and H-01 aluminum degraders
@@
 \end{equation}
-where $i,j$ are the monitor reactions in a given compartment, and $\beta \in [A_0$, $\rho \Delta r$, $\lambda$, $\Delta t_{irr}$, $\int \sigma(E) \frac{d\phi}{dE}dE$]. 
+where $i$ and $j$ are the monitor reactions in a given compartment, and $\beta \in [A_0$, $\rho \Delta r$, $\lambda$, $\Delta t_{irr}$, $\int \sigma(E) \frac{d\phi}{dE}dE$]. 
 % $\Sigma_{\beta_{ij}}$ is the correlation matrix for each $\beta$. 
@@
 % and dispersal.
-With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of 
+With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer caused by a combination of 
 % thermal swelling, 
@@
 Our recent work has shown that  arbitrary parameter optimization (tuning to provide a best fit to a single reaction channel)  often provides non-unique solutions, causing neighboring reaction channels (e.g., (p,4n) vs.
-(p,p3n)) to suffer \cite{fox2020investigating}.
+(p,p3n)), to suffer \cite{fox2020investigating}.
 % Without a global physical basis for optimization (as in the process of reaction evaluation), an unchecked fit to experimental data offers no insight for reaction modeling, and may propagate to highly non-physical results for  competing channels.
@@
 % The 
-It should be noted that the use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, 
+It should be noted that the use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a} 
 % by propagating the difficulties inherent in modeling a wide 
@@
 This serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence if one were to use the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
-Discussion of notable reaction channels follows here, and 
+Discussion of notable reaction channels follows here and 
 comparisons  of the
@@
 % and \ref{sec:fe_ibr_figures}.
-Physical yield curves have additionally been calculated,  from logarithmic interpolation of the excitation functions presented in this work, as seen in \autoref{fig:yields}.
-All yields are specified in the recommended units of MBq/C \cite{Otuka2015}, and  represent the instantaneous production rates.
+Physical yield curves have additionally been calculated  from logarithmic interpolation of the excitation functions presented in this work, as seen in \autoref{fig:yields}.
+All yields are specified in the recommended units of MBq/C \cite{Otuka2015} and  represent the instantaneous production rates.
 These curves show that production of medically-valuable radionuclides at low-to-intermediate energies by \ce{^{nat}Fe}(p,x) is potentially viable, but is dependent upon  the required radionuclidic purity on a case-by-case basis.
@@
 However, below the 24.1\,MeV threshold for \ce{^{56}Fe}(p,x)\ce{^{51}Mn}, the single measurement of \ce{^{54}Fe}(p,x)\ce{^{51}Mn} from Levkovski can be renormalized by isotopic abundance (and an additional -18\% due to an error in the monitor data adopted in the measurement), and is consistent  with the present work \cite{levkovski1991cross}.
-For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by the default calculation performed with  EMPIRE, CoH, and ALICE.
-Interestingly, the higher-energy reactions on the higher mass Fe isotopes, are better matched by  EMPIRE and CoH.
-ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
+For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL and over-predicted by the default calculation performed with  EMPIRE, CoH, and ALICE.
+Interestingly, the higher-energy reactions on the higher mass Fe isotopes are better matched by  EMPIRE and CoH.
+ALICE overpredicts the production of \ce{^{51}Mn} in both peaks and appears to peak at too high an energy.
 As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
@@
 In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house production of this short-lived ($t_{1/2}=46.2~\pm~0.1$ m\,\cite{Wang2017}) radionuclide.
-To increase yields over \ce{^{nat}Fe}(p,x), an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons, without opening the additional manganese exit channels accessible on a natural target.
+To increase yields over \ce{^{nat}Fe}(p,x), an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons without opening the additional manganese exit channels accessible on a natural target.
 
@@
 
-This work presents the first measurement of several observables in this energy region, including independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the  \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  as well as extending the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
+This work presents the first measurement of several observables in this energy region including independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the  \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  as well as extending the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.
 Cumulative  \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn} reaction measurements exist in earlier work, but  this work presents the most well-characterized measurement  below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
@@
 % Despite being weakly-fed, 
-EMPIRE and TALYS/TENDL all reproduce earlier work and this measurement reasonably well ($\pm$10\%), for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
+EMPIRE and TALYS/TENDL all reproduce earlier work and this measurement reasonably well ($\pm$10\%) for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
 This holds for both the shape and magnitude of each excitation function.
@@
 
-However, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\%, and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work.
+However, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\% and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work.
 % In 
@@
 
-As with many \ce{^{nat}Cu}(p,x) channels, these reactions have been previously measured in our earlier work, but this measurement extends these cross sections down to reaction thresholds, and reports cross sections for many of the short-lived products unable to be observed previously, such as \ce{^{60}Cu} \cite{Voyles2018a}.
+As with many \ce{^{nat}Cu}(p,x) channels, these reactions have been previously measured in our earlier work, but this measurement extends these cross sections down to reaction thresholds and reports cross sections for many of the short-lived products unable to be observed previously, such as \ce{^{60}Cu} \cite{Voyles2018a}.
 For \ce{^{nat}Cu}(p,x)\ce{^{60,61,64}Cu}, the measurements presented here are consistent with earlier work (aside from that of Williams \cite{PhysRev.162.1055}, as discussed earlier), and are generally the highest-precision measurements to date.
@@
 While the focus of this work is on the production of \ce{^{51,52}Mn}  and other \ce{^{nat}Fe}(p,x) channels, the cross sections reported here offer improvements to prior work, particularly for the several Sc radionuclides observed.
-For all of the \ce{^{nat}Ti}(p,x)\ce{^{44,47,48}Sc} channels, this work is consistent with all prior data, and is generally the highest-precision measurement to date.
+For all of the \ce{^{nat}Ti}(p,x)\ce{^{44,47,48}Sc} channels, this work is consistent with all prior data and is generally the highest-precision measurement to date.
 This work additionally  extends the \ce{^{44g}Sc} excitation function to the highest energy to date.
@@
 A similar argument holds for EMPIRE, which reproduces the isomer branching  up to 35\,MeV.
-However, CoH fails to reproduce either the channel magnitude or the isomer ratio,
+However, CoH fails to reproduce either the channel magnitude or the isomer ratio.
 % , suggesting a more fundamental issue with the modeling of this channel. 
 \ce{^{47}Sc} presents a very opposed situation, despite an abundance of reaction data and strong feeding of the channel.
-All codes fail to reproduce either the shape or magnitude of this channel, with only CoH able to predict the compound peak,  and failing to model the pre-equilibrium tail.
+All codes fail to reproduce either the shape or magnitude of this channel, with only CoH able to predict the compound peak but unble to model the pre-equilibrium tail.
 As a cumulative reaction channel, it is unclear whether this failure arises from modeling of any \ce{^{47}Ca} decay precursors, or the competition between  \ce{^{48}Ti}(p,20)\ce{^{47}Sc} / \ce{^{49}Ti}(p,2pn)\ce{^{47}Sc} / \ce{^{50}Ti}(p,$\alpha$)\ce{^{47}Sc} channels.
@@
 % Production of \ce{^{44}Sc} 
-However, this route offers no major advantages over established \ce{^{44}Ca}(p,n) / \ce{^{44}Ca}(d,2n) / \ce{^{45}Sc}(p,2n)\ce{^{44}Ti} $\xrightarrow[]{\epsilon}$ \ce{^{44}Sc} pathways,
+However, this route offers no major advantages over established \ce{^{44}Ca}(p,n) / \ce{^{44}Ca}(d,2n) / \ce{^{45}Sc}(p,2n)\ce{^{44}Ti} $\xrightarrow[]{\epsilon}$ \ce{^{44}Sc} pathways.
 % , with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Ti}(p,x). 
@@
 While no model globally succeeds in these channels,   TALYS and TENDL generally perform best with the lower-energy \enquote{compound} reactions but, like all models, do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
-This illustrates the importance of a well-characterized level density model for predictive power, with the \enquote{simple} Gilbert-Cameron model, with no energy-dependent spin parameter,  outperforming in the modeling of the pre-equilibrium regime.
+This illustrates the importance of a well-characterized level density model for predictive power, as the \enquote{simple} Gilbert-Cameron model, lacking an energy-dependent spin parameter,  outperforms in the modeling of the pre-equilibrium regime.
 
